### 2017-08-08 Masterarbeit - Latex/Masterarbeit - Lydia Buntrock - v1.tex
master thesis preversion
Former-commit-id: 6eacc1d3d034d233a58b3b5a30041781f9d678a8

\input{arbeit-vorlage-praeambel.tex} % Importiere die Einstellungen aus der Präambel
% hier beginnt der eigentliche Inhalt

\author{Lydia Buntrock}
\title{Masterarbeit}
\date{April 2014}

\begin{document}
  % Titelseite
  \begin{titlepage}
    \pagestyle{empty}
  	\begin{center}
      {\Large Freie Universität Berlin}\\
    	\begin{Huge}
      	Fachbereich Mathematik und Informatik\\
      	\vspace{3mm}
    	\end{Huge}
    	\vspace{20mm}
    	\begin{Large}
    	    \textbf{Origins of Parasitism}\\
          (Likelihood, parsimony and other algorithms for ancectral state reconstruction)\\
    	\end{Large}
    	\vspace{8mm}
      Version 1\\
      8.8.2017\\
    	\vspace{2cm}
    	Lydia Buntrock \\
      E-Mail: info@irallia.de\\
     	\vspace{5cm}
    	\textbf{Betreuer:}\\
      Prof. Dr. rer. nat. Emanuel Heitlinger\\
      \& \\
      Dr. Bernhard Y. Renard\\
  	\end{center}
  	\clearpage
  \end{titlepage}

  \tableofcontents
  \clearpage

  %-------------------------------------------------------------------------------------------------------------------------------------------------------------
  %-------------------------------------------------------------------------------------------------------------------------------------------------------------
  %-------------------------------------------------------------------------------------------------------------------------------------------------------------

  \chapter{Introduction}
    \begin{lecture}
      (21.4.17)
    \end{lecture}
    Related to computational systems biology\\
    Molecular biology
    \begin{itemize}
      \item Biological macromolecules
      \item Macromolecular interactions
      \item Pathways, networks, systems
    \end{itemize}
    (Subfields: pathway informatics, systems informatics)
    \begin{definition}
      \textbf{Systems biology:} Understand how components of a biological system interact to perform complex biological function.
    \end{definition}
    Challenges:
    \begin{itemize}
      \item Different levels of complexity
      \begin{itemize}
        \item Many components, huge amount of data, non-trivial interactions
      \end{itemize}
      \item Intuitive reasoning not sufficient
      \item Need for mathematical and computational models and tools
    \end{itemize}
    $\rightarrow$ Predictive biology\\
    \textbf{Research cycle}
    \todo{Research cycle...}\\

    Network topology
    \begin{itemize}
      \item Graph-based modeling
      \item Stoichiometric / constaint-based modeling
    \end{itemize}
    Network dynamics
    \begin{itemize}
      \item Continuous modeling
      \item Discrete modeling
      \item Stochastic modeling
      \item Hybrid modeling
    \end{itemize}

    \textbf{Important issues}
    \begin{itemize}
      \item Abstraction vs. precision
      \item Quantitative vs. qualitative
      \item Determinisitc vy. Non-deterministic
    \end{itemize}

    \textbf{Outline}
    \begin{enumerate}
      \item Continuous models
      \item Discrete models
      \item Constraint-based models
      \item Stochastic and hybrid models
    \end{enumerate}

  %-------------------------------------------------------------------------------------------------------------------------------------------------------------
  \chapter{Chemical kinetics}
    \begin{lecture}
      (21.4.17)
    \end{lecture}
    \section{Modeling simple reactions}
      $X, Y, \dots $ chemical species \\
      $x(t), y(t), \dots $ concentrations \\
      $\dot{x} = \dot{x}(t) = \frac{\mathrm d x}{\mathrm d t} (t)$ \\
      Modeling assumption: Reaction rate is propotional to the product of the reaction concentrations. \\
      Decay: $X -k-> \dot , \dot{x}=-kx$ (1) \\
      Transformation: $X -k-> Y, \dot{x}=-kx, \dot{y}=kx$ (2) \\
      Dissociation: $Z -k-> X+Y, \dot{z}=-kz, \dot{x}=kz, \dot{y}=kz$ \\
      Biomolecular reaction: $X+Y -k-> Z, \dot{z}=kxy, \dot{x}=-kxy = \dot{y}$ (z is a biolinear function, because it is linear in x and y) \\
      Reversible reaction: $X+Y <-k^-, k^+ -> Z, \dot{z}=k^+ xy-k^- z, \dot{x} = k^- z-k^+ xy = \dot{y}$ \\
      Dimerization: $X+X <-…-> Y [2X <-> Y]$ \\
      $\dot{x} = -2k^+ x^2 + 2k^- y$ \\
      $\dot{y} = -k^+ x^2 - k^- y$ \\
      *k stands for kinetic parameter \\

    \section{Chemical reaction networks}

    \begin{lecture}
      (24.4.17)
    \end{lecture}
    \begin{example}
      $n_S=3$ species: $S_1=H, S_2=0, S_3=H_2O$ \\
      $n_r=2$ reactions: $R_1: \underbrace{2H}_{\alpha_11} + \underbrace{O}_{\alpha_21} \longrightarrow \underbrace{H_2O}_{\beta_31}$
      $R_2: \underbrace{H_2O}_{\alpha_32} \underbrace{2H}_{\beta_12} + \underbrace{O}_{\beta_22}$
      $\Gamma = \bordermatrix{
        ~ & R_1 & R_2 \cr
        H & -2 & +2 \cr
        O & -1 & +1 \cr
        H_2O & +1 & -1 \cr}
      = \begin{pmatrix}
        k_1[H]^2[O] \\ k_2[H_2O]
      \end{pmatrix}$ \\
      $S(t) =
       \begin{pmatrix}
        S_1(t) \\ S_2(t) \\ S_3(t)
       \end{pmatrix}
       =
      \begin{pmatrix}
        [H] \\ [O] \\ [H_2O]
      \end{pmatrix}$ \\
      $R_1(S) = k_1[H]*[H]*[O] = [H]^2[O]$ \\
      $R_2(S) = k_2[H_2O]$ \\
      ...\\
      $\frac{\mathrm d S}{\mathrm d t} = \Gamma * R(S)$
      $\frac{\mathrm d [H]}{\mathrm d t} = -2k_1 [H]^2[O]+2k_2[H_2O]$ \\
      $\frac{\mathrm d [O]}{\mathrm d t} = -k_1 [H]^2[O]+k_2[H_2O]$ \\
      $\frac{\mathrm d [H_2O]}{\mathrm d t} = k_1 [H]^2[O]-k_2[H_2O]$ \\
    \end{example}

    bis Folie 2008...

    \begin{example}
      $\dot{x} = -kx, x(0)=1 (\dot{x}(t) = -kx(t))$ \\
      $n=1$: \\
      Assume $k=-2$ \todo{picture} \\
      $n=2$: \\
      $\dot{x}_1 = x_1+x_2$
      $\dot{x}_2 = x_1-x_2$
      $x(0)= (1 1)$
    \end{example}

    \begin{example}
      \todo{example via computation... see programm}
    \end{example}
    \begin{lecture}
      (24.4.17)
    \end{lecture}
    \subsection{Phase space}
      Autonomous equation $\dot{x}=f(x)$, with $x \in D \subseteq \mathbb{R}^n$. \\
      D is called \textbf{phase space}. \\
      $x(t) = (x1(t), \dots ,xn(t))$ is called \textbf{phase point}. \\
      When t varies, x(t) will move through phase space \textbf{trajectory} / \textbf{orbit} \\
      $f(x)$ can be interpreted as velocity vector. \\
      If the existence and uniqueness theorem applies, trajectories in phase space never intersect.
    \subsection{Steady states}
      \textbf{Nullcline}: $N_i = {x \in D | \dot{x}_i = f_i(x) = 0}$, for $i = 1, \dots , n$. \\
      A point $a \in D$ with $f(a) = 0$ (i.e., $f_i(a) = \dot{x}_i = 0, \forall i = 1, \dots ,n)$
      is called a \textbf{critical/singular/equilibrium point} or a \textbf{steady state}. \\
      It corresponds to the \textbf{equilibrium} or \textbf{stationary solution}
      $x(t) = a, \forall t$. \\
      It follows from the existence and uniqueness theorem that a steady state can never
      be reached from outside in finite time (otherwise two solutions would intersect).
  \subsection{Attractors and periodic solutions}
    A critical point $x = a$ of the equation $\dot{x} = f(x)$ is called a
    \textbf{positive attractor} if there exists a neighborhood
    $\omega a \subseteq \mathbb{R}^n$ of a such that
    $x(0) \in \Omega a implies lim_{t \rightarrow \infty} x(t) = a$. \\
    If this property holds for $t \rightarrow - \infty$, then $x = a$ is called a
    \textbf{negative attractor}.\\
    A solution $x(t)$ of $\dot{x} = f(x)$ is called \textbf{periodic} if there exists
    $T > 0$ such that $x(t + T) = x(t), \forall t \in \mathbb{R}$.
    \begin{lemma}
      Periodic solutions correspond to closed trajectories in phase space and vice versa.
    \end{lemma}
    A \textbf{limit cycle} is an isolated closed trajectory. \textbf{Isolated}
    means that neighboring trajectories are not closed; they spiral either toward
    or away from the limit cycle. \\
    \todo{picture 8}

\end{document}

### 2017-08-08 Masterarbeit - Latex/Masterarbeit - Lydia Buntrock - v1.tex
structure of thesis
Former-commit-id: e501cf46647ac9106bd758e40a98b88a2d61978f

@@
 \author{Lydia Buntrock}
-\title{Masterarbeit}
-\date{April 2014}
+\title{master thesis}
+\date{August 2017}
 
@@
 
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%--------------------------------------------------------------------------------------------------- 
+\chapter*{Abstract}
+  The abstract is a concise and accurate summary of the scholarly work described in the document. It 
+  states the problem, the methods of investigation, and the general conclusions, and should not 
+  contain tables, graphs, complex equations, or illustrations. There is a single scholarly abstract 
+  for the entire work, and it must not exceed 350 words in length.
+
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%--------------------------------------------------------------------------------------------------- 
+\chapter*{Summary}
+  1 page presenting the research problem, the main results, conclusion and how the thesis advances 
+  the field. \\
+  The lay or public summary explains the key goals and contributions of the research/scholarly work 
+  in terms that can be understood by the general public. It must not exceed 150 words in length.
+
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%--------------------------------------------------------------------------------------------------- 
+\chapter*{Foreword}
+  Acknowledgement to those who have helped you. \\
+  A foreword (one of the most often misspelled words in the language) is most often written by 
+    someone other than the author: an expert in the field, a writer of a similar book, etc. 
+    Forewords help the publisher at the level of marketing: An opening statement by an eminent and 
+    well-published author gives them added credibility in pitching the book to bookstores. Forewords 
+    help the author by putting a stamp of approval on their work.
+
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%--------------------------------------------------------------------------------------------------- 
+\chapter*{Preface}
+  The Preface must include a statement indicating the student's contribution to the following:
+  \begin{itemize}
+    \item Identification and design of the research program,
+    \item Performance of the various parts of the research, and
+    \item Analysis of the research data.
+  \end{itemize}
+  Certain additional elements may also be required, as specified below.
+  \begin{itemize}
+    \item If any of the work presented in the thesis has led to any publications or submissions, all 
+      of these must be listed in the Preface. Bibliographic details should include the title of the 
+      article and the name of the publisher (if the article has been accepted or published), and the 
+      chapter(s) of the thesis in which the associated work is located.
+    \item If the work includes publications or material submitted for publication, the statement 
+      described above must detail the relative contributions of all collaborators and co-authors 
+      (including supervisors and members of the supervisory committee) and state the proportion of 
+      research and writing conducted by the student. For further details, see “Including Published 
+      Material in a Thesis or Dissertation”.
+    \item If the work includes other scholarly artifacts (such as film and other audio, visual, and 
+      graphic representations, and application-oriented documents such as policy briefs, curricula, 
+      business plans, computer and web tools, pages, and applications, etc.), all of these must be 
+      listed in the Preface (with bibliographical information, if applicable).
+    \item If ethics approval was required for the research, the Preface must name the responsible 
+      UBC Research Ethics Board, and report the project title(s) and the Certificate Number(s) of 
+      the Ethics Certificate(s) applicable to the project.
+  \end{itemize}
+  In a thesis where the research was not subject to ethics review, produced no publications, and was 
+    designed, carried out, and analyzed by the student alone, the text of the Preface may be very 
+    brief. Samples are available on this website and in the University Library's online repository 
+    of accepted theses. \\
+  The content of the Preface must be verified by the student's supervisor, whose endorsement must 
+    appear on the final Thesis/Dissertation Approval form. \\
+  Acknowledgements, introductory material, and a list of publications do not belong in the Preface. 
+    Please put them respectively in the Acknowledgements section, the first section of the thesis, 
+    and the appendices. \\
+
+  A preface is best understood, I believe, as standing outside the book proper and being about the 
+    book. In a preface an author explains briefly why they wrote the book, or how they came to write 
+    it. They also often use the preface to establish their credibility, indicating their experience 
+    in the topic or their professional suitability to address such a topic. Sometimes they 
+    acknowledge those who inspired them or helped them (though these are often put into a separate 
+    Acknowledgments section). Using an old term from the study of rhetoric, a preface is in a sense 
+    an “apology”: an explanation or defense.
+
 \tableofcontents
@@
 
-  %-------------------------------------------------------------------------------------------------------------------------------------------------------------
-  %-------------------------------------------------------------------------------------------------------------------------------------------------------------
-  %-------------------------------------------------------------------------------------------------------------------------------------------------------------
+6. LIST OF TABLES (REQUIRED IF DOCUMENT HAS TABLES) \\
+7. LIST OF FIGURES (REQUIRED IF DOCUMENT HAS FIGURES) \\
+8. LIST OF ILLUSTRATIONS (REQUIRED IF DOCUMENT HAS ILLUSTRATIONS) \\
+9. LISTS OF SYMBOLS, ABBREVIATIONS OR OTHER (ADVISABLE IF APPLICABLE) \\
+10. GLOSSARY (OPTIONAL) \\
+11. ACKNOWLEDGEMENTS (OPTIONAL) \\
+  Students may include a brief statement acknowledging the contribution to their research and 
+    studies from various sources, including (but not limited  to) \\
 
+  Their research supervisor and committee, \\
+  Funding agencies, \\
+  Professional or community collaborators, \\
+  Fellow students, and \\
+  Family and friends. \\
+
+12. DEDICATION (OPTIONAL) (Widmung) \\
+
+13. DOCUMENT BODY \\
+  The text of the thesis must contain the following elements, presented to conform to the standards 
+    and expectations of the relevant academic discipline. In some cases, the ordering of these 
+    ingredients may differ from the one shown here. \\
+
+  A. Introduction. The thesis must clearly state its theme, hypotheses and/or goals (sometimes 
+    called “the research question(s)”), and provide sufficient background information to enable a 
+    non-specialist scholar to understand them. It must contain a thorough review of relevant 
+    literature, perhaps in a separate chapter. \\
+
+  B. Research/Scholarship Chapters. The account of the scholarly work should be presented in a 
+    manner suitable for the field. It should be complete, systematic, and sufficiently detailed to 
+    enable a reader to understand how the data were gathered and analyzed, and how to apply similar 
+    methods in another study. Notation and formatting must be consistent throughout the thesis, 
+    including units of measure, abbreviations, and the numbering scheme for tables, figures, 
+    footnotes, and citations. One or more chapters may consist of material published (or submitted
+    for publication) elsewhere, or other artifacts (e.g., film, application-oriented documents) 
+    placed in a scholarly context. See “Including Published Material in a Thesis or Dissertation” 
+    for additional details. \\
+
+  C. Conclusion. In this section the student must demonstrate his/her mastery of the field and 
+    describe the work's overall contribution to the broader discipline in context. A strong 
+    conclusion includes the following:
+    \begin{itemize}
+      \item Conclusions regarding the goals or hypotheses presented in the Introduction,
+      \item Reflective analysis of the scholarly work and its conclusions in light of current 
+        knowledge in the field,
+      \item Comments on the significance and contribution of the scholarship reported,
+      \item Comments on strengths and limitations of the research/scholarship,
+      \item Discussion of any potential applications of the findings, and
+      \item A description of possible future research directions, drawing on the work reported.
+    \end{itemize}
+    A submission's success in addressing the expectations above is appropriately judged by experts 
+      in the relevant discipline. Students should rely on their research supervisors and committee 
+      members for guidance. Doctoral students should also take into account the expectations 
+      articulated in the University's “Instructions for Preparing the External Examiner's Report”.
+
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%--------------------------------------------------------------------------------------------------- 
 \chapter{Introduction}
-    \begin{lecture}
-      (21.4.17)
-    \end{lecture}
-    Related to computational systems biology\\
-    Molecular biology
+  On the first page, you should present
   \begin{itemize}
-      \item Biological macromolecules
-      \item Macromolecular interactions
-      \item Pathways, networks, systems
+    \item The area of research (e.g. implementation of information systems)
+    \item The most relevant previous findings in this area
+    \item Your research problem and why this is worthwhile studying
+    \item The objective of the thesis: how far you hope to advance knowledge in the field
   \end{itemize}
-    (Subfields: pathway informatics, systems informatics)
-    \begin{definition}
-      \textbf{Systems biology:} Understand how components of a biological system interact to perform complex biological function.
-    \end{definition}
-    Challenges:
+  Target group \\
+  To whom are you writing, what do you assume that the reader know? A normal target groupd would be 
+    new Master students. \\
+  Personal motivation \\
+  Why did you choose this topic? \\
+  Research method in brief \\
+  How will you find out? \\
+  Structure of the report \\
+  A paragraph about each chapter. What is the main contribution of the chapter? How do they relate? \\
+
+  If a preface is about the book as a book, the introduction is about the content of the book. 
+    Sometimes it is as simple as that: It introduces what is covered in the book. Other times it 
+    introduces by setting the overall themes of the book, or by establishing definitions and 
+    methodology that will be used throughout the book. Scholarly writers sometimes use the 
+    introduction to tell their profession how the book should be viewed academically (that is, they 
+    position the book as a particular approach within a discipline or part of a discipline). This 
+    latter material is appropriate for a preface, as well. The point is that it should appear in the 
+    preface or the introduction, not both. \\
+  I helped authors with the front end of their books in two recent cases by refining for them the 
+    differences between these rubrics of foreword, preface, and introduction. Because these books 
+    were very practical books, I also introduced the rubric of “How to Use This Book.” \\
+  Not only did these authors take several stabs at describing their book’s contents via their 
+    preface and introduction, they actually tried one more time in their first chapter. \\
+  In both cases I set up three rubrics for the front end of the book: Preface, How to Use This Book, 
+    and Introduction. I then put like with like. I sorted out the various descriptions of why the 
+    book had been written and placing them under the heading “Preface.” I found sentences that dealt 
+    with the use of the book and placed them under the heading of “How to Use This Book.” I took the 
+    various explanations of what the reader was going to read and placed them under the heading of 
+    “Introduction.” I also, in one case, deleted the repeated material in the first chapter, and in 
+    the other case, moved the repeated material from the first chapter to the Introduction, 
+    replacing a less-well-stated introductory comment there. \\
+  In both instances the authors felt that I had waved a magic wand over the material. They felt a 
+    sense of satisfaction, knowing that their manuscripts now clearly explained to the reader why 
+    they wrote their book, how it was to be used, and the details of what it covered. \\
+  What about you and your manuscript? I believe the above definitions and distinctions may alleviate 
+    the anxiety you likely feel as a writer. You are anxious to be clear, you want to feel justified 
+    in addressing readers with your content, you want to establish your credibility, and you want to 
+    set the parameters of your time together. Keep in mind that your anxiety may be what is causing 
+    your own confusion at the beginning of a book. If unaddressed, it will cause confusion in your 
+    readers. \\
+  So just calm down and sort through your material as described above. You may be surprised to find 
+    that the exercise does something else for you, revealing a better way for you to construct, or 
+    reconstruct, the rest of your manuscript!
+
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%--------------------------------------------------------------------------------------------------- 
+\chapter{CRelated literature and theoretical focus}
+  A survey of the literature (journals, conferences, book chapters) on the areas that are relevant 
+    to your research question. One section per area. \\
+  The chapter should conclude with a summary of the previous research results that you want to 
+    develop further or challenge. The summary could be presented in a model, a list of issues, etc. 
+    Each issue could be a chapter in the presentation of results. They should definitely be 
+    discussed in the discussion / conclusion of the thesis.
+
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%--------------------------------------------------------------------------------------------------- 
+\chapter{Presentation of the part of the world to be studied}
+  Which could be the health system in Mozambique, the rural areas where the telecentres are located, 
+    the financial businesses in which the accounting system you will develop will be used.
+
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%--------------------------------------------------------------------------------------------------- 
+\chapter{Method}
+  The research method by which you will investigate the world.
   \begin{itemize} 
-      \item Different levels of complexity
-      \begin{itemize}
-        \item Many components, huge amount of data, non-trivial interactions
-      \end{itemize}
-      \item Intuitive reasoning not sufficient
-      \item Need for mathematical and computational models and tools
-    \end{itemize}
-    $\rightarrow$ Predictive biology\\
-    \textbf{Research cycle}
-    \todo{Research cycle...}\\
-
-    Network topology
-    \begin{itemize}
-      \item Graph-based modeling
-      \item Stoichiometric / constaint-based modeling
-    \end{itemize}
-    Network dynamics
-    \begin{itemize}
-      \item Continuous modeling
-      \item Discrete modeling
-      \item Stochastic modeling
-      \item Hybrid modeling
+    \item A short summary of the available methods
+    \item Your choice
+    \item Detailed report of how you actually carried out your research. Presenting how you selected 
+      the people taking part is of special importance.
   \end{itemize}
 
-    \textbf{Important issues}
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%--------------------------------------------------------------------------------------------------- 
+\chapter{... Your research results (and discussion)}
+  Which could be the system you made and the reasons for various design decisions, what your 
+    interview objects said, observations of people using a computer system, stories of a development 
+    process, numeral data from a questionnaire, etc. \\
+  The discussion of the findings can be included in these chapters, or the discussion can be put in 
+    a separate chapter.  \\
+  The issues from the theory chapter (chapter 2) should be discussed here.
+
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%--------------------------------------------------------------------------------------------------- 
+\chapter{Conclusion}
+  Summary of the problem, the main findings and the discussion. Structured according to the issues 
+    in chapter 2. \\
+  Comparison with the literature presented in chapter 2: how do your results fill in, advance or 
+    contradict previously reported research? \\
+  What are the implications of your research for people working in the field that you have studies? \\
+  In which direction should further research go?  \\
+
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%--------------------------------------------------------------------------------------------------- 
+\chapter{References / BIBLIOGRAPHY}
+  A complete list of written documents you have referred to in the report. \\
+  There must be only one Bibliography or References section for the whole thesis.
+
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%--------------------------------------------------------------------------------------------------- 
+\chapter{APPENDICES}
+  Appendices must be limited to supporting material genuinely subsidiary to the main argument of the 
+    work. They must only include material that is referred to in the document. \\
+  Material suitable for inclusion in appendices includes the following:
   \begin{itemize} 
-      \item Abstraction vs. precision
-      \item Quantitative vs. qualitative
-      \item Determinisitc vy. Non-deterministic
+    \item Additional details of methodology and/or data
+    \item Diagrams of specialized equipment developed
+    \item Copies of questionnaires or surveys used in the research
+    \item Scholarly artifacts (e.g., film and other audio, visual, and graphic representations, and 
+      application-oriented documents such as policy briefs, curricula, business plans, computer and 
+      web applications, etc.) not included in the body of the thesis
   \end{itemize}
-
-    \textbf{Outline}
-    \begin{enumerate}
-      \item Continuous models
-      \item Discrete models
-      \item Constraint-based models
-      \item Stochastic and hybrid models
-    \end{enumerate}
-
-  %-------------------------------------------------------------------------------------------------------------------------------------------------------------
-  \chapter{Chemical kinetics}
-    \begin{lecture}
-      (21.4.17)
-    \end{lecture}
-    \section{Modeling simple reactions}
-      $X, Y, \dots $ chemical species \\
-      $x(t), y(t), \dots $ concentrations \\
-      $\dot{x} = \dot{x}(t) = \frac{\mathrm d x}{\mathrm d t} (t)$ \\
-      Modeling assumption: Reaction rate is propotional to the product of the reaction concentrations. \\
-      Decay: $X -k-> \dot , \dot{x}=-kx$ (1) \\
-      Transformation: $X -k-> Y, \dot{x}=-kx, \dot{y}=kx$ (2) \\
-      Dissociation: $Z -k-> X+Y, \dot{z}=-kz, \dot{x}=kz, \dot{y}=kz$ \\
-      Biomolecular reaction: $X+Y -k-> Z, \dot{z}=kxy, \dot{x}=-kxy = \dot{y}$ (z is a biolinear function, because it is linear in x and y) \\
-      Reversible reaction: $X+Y <-k^-, k^+ -> Z, \dot{z}=k^+ xy-k^- z, \dot{x} = k^- z-k^+ xy = \dot{y}$ \\
-      Dimerization: $X+X <-…-> Y [2X <-> Y]$ \\
-      $\dot{x} = -2k^+ x^2 + 2k^- y$ \\
-      $\dot{y} = -k^+ x^2 - k^- y$ \\
-      *k stands for kinetic parameter \\
-
-    \section{Chemical reaction networks}
-
-    \begin{lecture}
-      (24.4.17)
-    \end{lecture}
-    \begin{example}
-      $n_S=3$ species: $S_1=H, S_2=0, S_3=H_2O$ \\
-      $n_r=2$ reactions: $R_1: \underbrace{2H}_{\alpha_11} + \underbrace{O}_{\alpha_21} \longrightarrow \underbrace{H_2O}_{\beta_31}$
-      $R_2: \underbrace{H_2O}_{\alpha_32} \underbrace{2H}_{\beta_12} + \underbrace{O}_{\beta_22}$
-      $\Gamma = \bordermatrix{
-        ~ & R_1 & R_2 \cr
-        H & -2 & +2 \cr
-        O & -1 & +1 \cr
-        H_2O & +1 & -1 \cr}
-      = \begin{pmatrix}
-        k_1[H]^2[O] \\ k_2[H_2O]
-      \end{pmatrix}$ \\
-      $S(t) =
-       \begin{pmatrix}
-        S_1(t) \\ S_2(t) \\ S_3(t)
-       \end{pmatrix}
-       =
-      \begin{pmatrix}
-        [H] \\ [O] \\ [H_2O]
-      \end{pmatrix}$ \\
-      $R_1(S) = k_1[H]*[H]*[O] = [H]^2[O]$ \\
-      $R_2(S) = k_2[H_2O]$ \\
-      ...\\
-      $\frac{\mathrm d S}{\mathrm d t} = \Gamma * R(S)$
-      $\frac{\mathrm d [H]}{\mathrm d t} = -2k_1 [H]^2[O]+2k_2[H_2O]$ \\
-      $\frac{\mathrm d [O]}{\mathrm d t} = -k_1 [H]^2[O]+k_2[H_2O]$ \\
-      $\frac{\mathrm d [H_2O]}{\mathrm d t} = k_1 [H]^2[O]-k_2[H_2O]$ \\
-    \end{example}
-
-    bis Folie 2008...
-
-    \begin{example}
-      $\dot{x} = -kx, x(0)=1 (\dot{x}(t) = -kx(t))$ \\
-      $n=1$: \\
-      Assume $k=-2$ \todo{picture} \\
-      $n=2$: \\
-      $\dot{x}_1 = x_1+x_2$
-      $\dot{x}_2 = x_1-x_2$
-      $x(0)= (1 1)$
-    \end{example}
-
-    \begin{example}
-      \todo{example via computation... see programm}
-    \end{example}
-    \begin{lecture}
-      (24.4.17)
-    \end{lecture}
-    \subsection{Phase space}
-      Autonomous equation $\dot{x}=f(x)$, with $x \in D \subseteq \mathbb{R}^n$. \\
-      D is called \textbf{phase space}. \\
-      $x(t) = (x1(t), \dots ,xn(t))$ is called \textbf{phase point}. \\
-      When t varies, x(t) will move through phase space \textbf{trajectory} / \textbf{orbit} \\
-      $f(x)$ can be interpreted as velocity vector. \\
-      If the existence and uniqueness theorem applies, trajectories in phase space never intersect.
-    \subsection{Steady states}
-      \textbf{Nullcline}: $N_i = {x \in D | \dot{x}_i = f_i(x) = 0}$, for $i = 1, \dots , n$. \\
-      A point $a \in D$ with $f(a) = 0$ (i.e., $f_i(a) = \dot{x}_i = 0, \forall i = 1, \dots ,n)$
-      is called a \textbf{critical/singular/equilibrium point} or a \textbf{steady state}. \\
-      It corresponds to the \textbf{equilibrium} or \textbf{stationary solution}
-      $x(t) = a, \forall t$. \\
-      It follows from the existence and uniqueness theorem that a steady state can never
-      be reached from outside in finite time (otherwise two solutions would intersect).
-  \subsection{Attractors and periodic solutions}
-    A critical point $x = a$ of the equation $\dot{x} = f(x)$ is called a
-    \textbf{positive attractor} if there exists a neighborhood
-    $\omega a \subseteq \mathbb{R}^n$ of a such that
-    $x(0) \in \Omega a implies lim_{t \rightarrow \infty} x(t) = a$. \\
-    If this property holds for $t \rightarrow - \infty$, then $x = a$ is called a
-    \textbf{negative attractor}.\\
-    A solution $x(t)$ of $\dot{x} = f(x)$ is called \textbf{periodic} if there exists
-    $T > 0$ such that $x(t + T) = x(t), \forall t \in \mathbb{R}$.
-    \begin{lemma}
-      Periodic solutions correspond to closed trajectories in phase space and vice versa.
-    \end{lemma}
-    A \textbf{limit cycle} is an isolated closed trajectory. \textbf{Isolated}
-    means that neighboring trajectories are not closed; they spiral either toward
-    or away from the limit cycle. \\
-    \todo{picture 8}
+  Do not include copies of the Ethics Certificates in the Appendices. \\
+  Material supplemental to the thesis but not appropriate to include in the appendices (e.g., raw 
+    data, original plan for research and analyses) can be archived in cIRcle as Supplementary 
+    Materials.
 

### 2017-08-08 Masterarbeit - Latex/Masterarbeit - Lydia Buntrock - v1.tex
update structure
Former-commit-id: f2e49ed78ba080615cc1aca228a49230eb30c079

@@
 
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%--------------------------------------------------------------------------------------------------- 
+\chapter{Introduction}
   A. Introduction. The thesis must clearly state its theme, hypotheses and/or goals (sometimes 
@@
 
-  B. Research/Scholarship Chapters. The account of the scholarly work should be presented in a 
-    manner suitable for the field. It should be complete, systematic, and sufficiently detailed to 
-    enable a reader to understand how the data were gathered and analyzed, and how to apply similar 
-    methods in another study. Notation and formatting must be consistent throughout the thesis, 
-    including units of measure, abbreviations, and the numbering scheme for tables, figures, 
-    footnotes, and citations. One or more chapters may consist of material published (or submitted
-    for publication) elsewhere, or other artifacts (e.g., film, application-oriented documents) 
-    placed in a scholarly context. See “Including Published Material in a Thesis or Dissertation” 
-    for additional details. \\
-
-  C. Conclusion. In this section the student must demonstrate his/her mastery of the field and 
-    describe the work's overall contribution to the broader discipline in context. A strong 
-    conclusion includes the following:
-    \begin{itemize}
-      \item Conclusions regarding the goals or hypotheses presented in the Introduction,
-      \item Reflective analysis of the scholarly work and its conclusions in light of current 
-        knowledge in the field,
-      \item Comments on the significance and contribution of the scholarship reported,
-      \item Comments on strengths and limitations of the research/scholarship,
-      \item Discussion of any potential applications of the findings, and
-      \item A description of possible future research directions, drawing on the work reported.
-    \end{itemize}
-    A submission's success in addressing the expectations above is appropriately judged by experts 
-      in the relevant discipline. Students should rely on their research supervisors and committee 
-      members for guidance. Doctoral students should also take into account the expectations 
-      articulated in the University's “Instructions for Preparing the External Examiner's Report”.
-
-%---------------------------------------------------------------------------------------------------
-%---------------------------------------------------------------------------------------------------
-%--------------------------------------------------------------------------------------------------- 
-\chapter{Introduction}
   On the first page, you should present
@@
 %--------------------------------------------------------------------------------------------------- 
-\chapter{CRelated literature and theoretical focus}
+\chapter{Research/Scholarship}
+  The account of the scholarly work should be presented in a 
+    manner suitable for the field. It should be complete, systematic, and sufficiently detailed to 
+    enable a reader to understand how the data were gathered and analyzed, and how to apply similar 
+    methods in another study. Notation and formatting must be consistent throughout the thesis, 
+    including units of measure, abbreviations, and the numbering scheme for tables, figures, 
+    footnotes, and citations. One or more chapters may consist of material published (or submitted
+    for publication) elsewhere, or other artifacts (e.g., film, application-oriented documents) 
+    placed in a scholarly context. See “Including Published Material in a Thesis or Dissertation” 
+    for additional details. \\
+
+  %---------------------------------------------------------------------------------------------------
+  %--------------------------------------------------------------------------------------------------- 
+  \section{Related literature and theoretical focus}
     A survey of the literature (journals, conferences, book chapters) on the areas that are relevant 
@@
   %--------------------------------------------------------------------------------------------------- 
-%--------------------------------------------------------------------------------------------------- 
-\chapter{Presentation of the part of the world to be studied}
+  \section{Presentation of the part of the world to be studied}
     Which could be the health system in Mozambique, the rural areas where the telecentres are located, 
@@
   %--------------------------------------------------------------------------------------------------- 
-%--------------------------------------------------------------------------------------------------- 
-\chapter{Method}
+  \section{Method}
     The research method by which you will investigate the world.
@@
   %--------------------------------------------------------------------------------------------------- 
-%--------------------------------------------------------------------------------------------------- 
-\chapter{... Your research results (and discussion)}
+  \section{... Your research results (and discussion)}
     Which could be the system you made and the reasons for various design decisions, what your 
@@
 \chapter{Conclusion}
+  C. Conclusion. In this section the student must demonstrate his/her mastery of the field and 
+    describe the work's overall contribution to the broader discipline in context. A strong 
+    conclusion includes the following:
+    \begin{itemize}
+      \item Conclusions regarding the goals or hypotheses presented in the Introduction,
+      \item Reflective analysis of the scholarly work and its conclusions in light of current 
+        knowledge in the field,
+      \item Comments on the significance and contribution of the scholarship reported,
+      \item Comments on strengths and limitations of the research/scholarship,
+      \item Discussion of any potential applications of the findings, and
+      \item A description of possible future research directions, drawing on the work reported.
+    \end{itemize}
+    A submission's success in addressing the expectations above is appropriately judged by experts 
+      in the relevant discipline. Students should rely on their research supervisors and committee 
+      members for guidance. Doctoral students should also take into account the expectations 
+      articulated in the University's “Instructions for Preparing the External Examiner's Report”.
+
   Summary of the problem, the main findings and the discussion. Structured according to the issues 

### 2017-08-08 Masterarbeit - Latex/Masterarbeit - Lydia Buntrock - v1.tex
small fixes
Former-commit-id: 3d4bb5e38bbabd117673a9eb0df11fefa2e7c3e6

@@
 \chapter{Conclusion}
-  C. Conclusion. In this section the student must demonstrate his/her mastery of the field and 
+  In this section the student must demonstrate his/her mastery of the field and 
     describe the work's overall contribution to the broader discipline in context. A strong 
@@
 
-  Summary of the problem, the main findings and the discussion. Structured according to the issues 
+  (Summary of the problem, the main findings and the discussion. Structured according to the issues 
     in chapter 2. \\
@@
     contradict previously reported research? \\
-  What are the implications of your research for people working in the field that you have studies? \\
-  In which direction should further research go?  \\
+  What are the implications of your research for people working in the field that you have studies?)
 

### 2017-10-02 Masterarbeit - Latex/Masterarbeit - Lydia Buntrock - v2.tex
bibliography added
Former-commit-id: 02243a066b6c9ad7990762a1887b367f3ffaaf9a

--- 2017-08-08 Masterarbeit - Latex/Masterarbeit - Lydia Buntrock - v1.tex
@@
     	\begin{Large}
-    	    \textbf{Origins of Parasitism}\\
+    	    \textbf{Origins and losses of parasitism}\\
           (Likelihood, parsimony and other algorithms for ancectral state reconstruction)\\
@@
     	\vspace{8mm}
-      Version 1\\
-      8.8.2017\\
+      Version 2\\
+      2.10.2017\\
     	\vspace{2cm}
@@
       \textbf{Betreuer:}\\
+      Dr. Bernhard Y. Renard\\
+      \& \\
       Prof. Dr. rer. nat. Emanuel Heitlinger\\      
-      \& \\
-      Dr. Bernhard Y. Renard\\
   	\end{center}
@@
 \chapter*{Abstract}
-  The abstract is a concise and accurate summary of the scholarly work described in the document. It 
-  states the problem, the methods of investigation, and the general conclusions, and should not 
-  contain tables, graphs, complex equations, or illustrations. There is a single scholarly abstract 
-  for the entire work, and it must not exceed 350 words in length.
+  \todotext{The abstract} is a concise and accurate summary of the scholarly work described in the 
+  document. It states the problem, the methods of investigation, and the general conclusions, and 
+  should not contain tables, graphs, complex equations, or illustrations. There is a single 
+  scholarly abstract for the entire work, and it must not exceed 350 words in length.
 
@@
 \chapter*{Summary}
-  1 page presenting the research problem, the main results, conclusion and how the thesis advances 
-  the field. \\
+  \todotext{1 page} presenting the research problem, the main results, conclusion and how the thesis 
+  advances the field. \\
   The lay or public summary explains the key goals and contributions of the research/scholarly work 
@@
   %--------------------------------------------------------------------------------------------------- 
+  \section{Definitions}
+    \begin{definition} parsimony \cite{Cunningham1998}
+    \end{definition}
+    \begin{definition} taxonomy \\
+      Taxonomic tree – Taxonomy is the classification, identification and naming of organisms. It is 
+        usually richly informed by phylogenetics, but remains a methodologically and logically 
+        distinct discipline. The Taxonomic levels are Kingdom, Phylum, Class, Order, Family, Genus, 
+        Species and maybe some superclasses between them. \\
+      coarser classification \\
+      In each level the nodes can have more than 2 children
+    \end{definition}
+    \begin{definition} phylogeny \\
+      Phylogenetic tree – Phylogenetics is the study of evolutionary history and the relationships 
+        among individuals or groups of organisms. The result ot these analysis is a  phylogeny or 
+        phylogenetic tree. The phylogenetic tree is a hypothesis about the history of the evolutionary 
+        relationships of a group of organisms. \\
+      A perfect tree would be binary \\
+      no levels only time
+    \end{definition}
+    \begin{definition} parasite \\
+      Parasitism – Parasitism is an interaction relationship between two organisms living together in 
+        more or less intimate association in a relationship in which association is disadvantageous or 
+        destructive to one of the organisms. \\
+      http://www.ebi.ac.uk/QuickGO/term/GO:0072519 \\
+      ontology definition of the interaction 'is parasite of' from GloBI the database we use here. \\
+      exist very different types of parasites: endoparasites, broodparasitism, ... \\
+      40\% of species are parasites, but the most of them are understudied. \cite{Windsor1998}
+
+      ontology definition.. explanation... \\
+      Property Hierarchy from ontobee: \\
+      ecologically related to $\supseteq$ biotically interacts with $\supseteq$ participates in a 
+        biotic-biotic interaction with $\supseteq$ symbiotically interacts with $\supseteq$ has host 
+        $\supseteq$ hyperparasite of, pathogen of, parasite of $\supseteq$ parasitoid of, obligate 
+        parasite of, facultative parasite of, stem parasite of, root parasite of, hemiparasite of, 
+        lays eggs in, ectoparasite of, endoparasite of, mesoparasite of, kleptoparasite of
+    \end{definition}
+
+  %--------------------------------------------------------------------------------------------------- 
+  \section{Motivation}
+    study parasites:
+    \begin{itemize}
+      \item für jedes Ökosystem unentbehrlich [Marius]
+      \item Wechselwirkungen in 75\% der Verbindungen in den Nahrungsmittelbahnen [Marius]
+      \item agglomerieren Schadstoffe, binden 30 bis 50\% der Schadstoffmasse innerhalb eines Ökosystem [Marius]
+      \item Dezimierung der Bevölkerung der störenden Arten [Marius]
+    \end{itemize}
+    big data:
+    \begin{itemize}
+      \item data accumulates faster than ever. Biological data is no exception but scientists still struggle to harvest this rapidly growing pile of databases. [Marius]      
+    \end{itemize}
+    origins of parasitism: \\
+    Many studies tried to find the origins of parasitism. For example in Nematodes [14, 29], in Lice 
+      [28], in Plathylminthes [30, 31] and in Metazoa in general [32, 33, 1] scientists searched for 
+      these origins. The most recent analysis is the one from Sara Weinstein and Armand M. Kuris. 
+      They came to the conclusion that parasitism evolved at least 223 times indepedently in the 
+      kingdom of Animalia. They found most of the origins inside the phylum Arthropoda [1]. [Marius] \\
+    Wenn wir die Ursprünge des Parasitums verstehen können, können wir die Evolution von Pathogenen 
+      vorhersagen und welche genetischen Anpassungen für eine Transition vom freien Leben zu einem 
+      parasitären Lebensstil notwendig sind [21]. Es könnte sogar zu einem Punkt führen, an dem wir 
+      die Immunität gegen Antibiotika von Pathogenen vorhersagen konnten. [Marius]
+
+%---------------------------------------------------------------------------------------------------
 %---------------------------------------------------------------------------------------------------
@@
       a separate chapter.  \\
-    The issues from the theory chapter (chapter 2) should be discussed here.
+    The issues from the theory chapter 2 should be discussed here.
 
@@
 
+%-------------------------------------------------------------------------------------------------------------------------------------------------------------
+%-------------------------------------------------------------------------------------------------------------------------------------------------------------
+%-------------------------------------------------------------------------------------------------------------------------------------------------------------
+\bibliography{bibliographie}
+\bibliographystyle{alphadin}
+
 %---------------------------------------------------------------------------------------------------
@@
 %--------------------------------------------------------------------------------------------------- 
-\chapter{References / BIBLIOGRAPHY}
-  A complete list of written documents you have referred to in the report. \\
-  There must be only one Bibliography or References section for the whole thesis.
+\chapter*{Eigenständigkeitserklärung}
+  Hiermit versichere ich, dass ich die vorliegende Masterarbeit selbständig verfasst habe. \\
+  Ich versichere, dass ich keine anderen als die angegebenen Quellen benutzt und alle wörtlich oder sinngemäß aus anderen Werken übernommenen Aussagen als solche gekennzeichnet habe, und dass die eingereichte Arbeit weder vollständig noch in wesentlichen Teilen Gegenstand eines anderen Prüfungsverfahren gewesen ist.
+\\
+  \vspace{2 cm} \\
+  (Datum und Unterschrift)
+  \todo{englisch!}
 
@@
 \chapter{APPENDICES}
-  Appendices must be limited to supporting material genuinely subsidiary to the main argument of the 
-    work. They must only include material that is referred to in the document. \\
+  \todotext{Appendices} must be limited to supporting material genuinely subsidiary to the main 
+    argument of the work. They must only include material that is referred to in the document.\\
   Material suitable for inclusion in appendices includes the following:

### 2017-10-02 Masterarbeit - Latex/Masterarbeit - Lydia Buntrock - v2.tex
Foreword deleted, new subtitle, tidy up
Former-commit-id: 64ad677d07144f1eb5b647dde423c8b8a6559879

@@
     	    \textbf{Origins and losses of parasitism}\\
-          (Likelihood, parsimony and other algorithms for ancectral state reconstruction)\\
+          an analysis of the phylogenetic tree of life with a parsimony-like algorithm\\
     	\end{Large}
@@
 %--------------------------------------------------------------------------------------------------- 
-\chapter*{Foreword}
-  Acknowledgement to those who have helped you. \\
-  A foreword (one of the most often misspelled words in the language) is most often written by 
-    someone other than the author: an expert in the field, a writer of a similar book, etc. 
-    Forewords help the publisher at the level of marketing: An opening statement by an eminent and 
-    well-published author gives them added credibility in pitching the book to bookstores. Forewords 
-    help the author by putting a stamp of approval on their work.
-
-%---------------------------------------------------------------------------------------------------
-%---------------------------------------------------------------------------------------------------
-%--------------------------------------------------------------------------------------------------- 
 \chapter*{Preface}
-  The Preface must include a statement indicating the student's contribution to the following:
+  \todotext{The Preface} must include a statement indicating the student's contribution to the 
+    following:
   \begin{itemize}
@@
 \chapter{Introduction}
-  A. Introduction. The thesis must clearly state its theme, hypotheses and/or goals (sometimes 
-    called “the research question(s)”), and provide sufficient background information to enable a 
-    non-specialist scholar to understand them. It must contain a thorough review of relevant 
-    literature, perhaps in a separate chapter. \\
+  \todotext{A. Introduction.} The thesis must clearly state its theme, hypotheses and/or goals
+    (sometimes called “the research question(s)”), and provide sufficient background information to 
+    enable a non-specialist scholar to understand them. It must contain a thorough review of 
+    relevant literature, perhaps in a separate chapter. \\
 
@@
   A paragraph about each chapter. What is the main contribution of the chapter? How do they relate? \\
-
-  If a preface is about the book as a book, the introduction is about the content of the book. 
-    Sometimes it is as simple as that: It introduces what is covered in the book. Other times it 
-    introduces by setting the overall themes of the book, or by establishing definitions and 
-    methodology that will be used throughout the book. Scholarly writers sometimes use the 
-    introduction to tell their profession how the book should be viewed academically (that is, they 
-    position the book as a particular approach within a discipline or part of a discipline). This 
-    latter material is appropriate for a preface, as well. The point is that it should appear in the 
-    preface or the introduction, not both. \\
-  I helped authors with the front end of their books in two recent cases by refining for them the 
-    differences between these rubrics of foreword, preface, and introduction. Because these books 
-    were very practical books, I also introduced the rubric of “How to Use This Book.” \\
-  Not only did these authors take several stabs at describing their book’s contents via their 
-    preface and introduction, they actually tried one more time in their first chapter. \\
-  In both cases I set up three rubrics for the front end of the book: Preface, How to Use This Book, 
-    and Introduction. I then put like with like. I sorted out the various descriptions of why the 
-    book had been written and placing them under the heading “Preface.” I found sentences that dealt 
-    with the use of the book and placed them under the heading of “How to Use This Book.” I took the 
-    various explanations of what the reader was going to read and placed them under the heading of 
-    “Introduction.” I also, in one case, deleted the repeated material in the first chapter, and in 
-    the other case, moved the repeated material from the first chapter to the Introduction, 
-    replacing a less-well-stated introductory comment there. \\
-  In both instances the authors felt that I had waved a magic wand over the material. They felt a 
-    sense of satisfaction, knowing that their manuscripts now clearly explained to the reader why 
-    they wrote their book, how it was to be used, and the details of what it covered. \\
-  What about you and your manuscript? I believe the above definitions and distinctions may alleviate 
-    the anxiety you likely feel as a writer. You are anxious to be clear, you want to feel justified 
-    in addressing readers with your content, you want to establish your credibility, and you want to 
-    set the parameters of your time together. Keep in mind that your anxiety may be what is causing 
-    your own confusion at the beginning of a book. If unaddressed, it will cause confusion in your 
-    readers. \\
-  So just calm down and sort through your material as described above. You may be surprised to find 
-    that the exercise does something else for you, revealing a better way for you to construct, or 
-    reconstruct, the rest of your manuscript!
 

### 2017-10-02 Masterarbeit - Latex/Masterarbeit - Lydia Buntrock - v2.tex
add some literature
Former-commit-id: 0e68df5887343952082ce0c71c6b27525e68abba

@@
       no levels only time
+      \todo{synthesis tree} \cite{Hinchliff2015}
     \end{definition}
@@
       http://www.ebi.ac.uk/QuickGO/term/GO:0072519 \\
-      ontology definition of the interaction 'is parasite of' from GloBI the database we use here. \\
+      ontology definition of the interaction 'is parasite of' from GloBI \cite{Poelen2014} the database we use here. \\
       exist very different types of parasites: endoparasites, broodparasitism, ... \\
@@
   \section{Motivation}
+    Weinstein und Kuris Paper \cite{Weinstein2016} \\
     study parasites:

### 2017-10-26 Paper - Latex/Paper - Skizze - v1.tex
Ersten Satz der Einleitung fomuliert; einen Teil der Einleitung geschrieben.
Former-commit-id: 6bda26dbd44cea626f0cbfe5ae86687f16ae1f5a

\input{arbeit-vorlage-praeambel.tex} % Importiere die Einstellungen aus der Präambel
% hier beginnt der eigentliche Inhalt

\author{Lydia Buntrock}
\title{master thesis}
\date{August 2017}

\begin{document}
  % Titelseite
  \begin{titlepage}
    \pagestyle{empty}

    	\vspace{20mm}
    	\begin{Large}
    	    \textbf{Origins and losses of parasitism}\\
          an analysis of the phylogenetic tree of life with a parsimony-like algorithm\\
    	\end{Large}

  	\clearpage
  \end{titlepage}

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter*{Abstract}

\tableofcontents
\clearpage

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter{Introduction}
  This paper is about the further development of parsimony algorithms for non-binary trees, applied 
  to the currently largest phylogeny synthesis tree of Open Tree Of Life, with the application to 
  the ancestral state reconstruction of parasitism. \\

  Researchers of the phylogenies have been dealt with the ancenstral state reconstruction in the 60s.
  The first methods were only brute force \todo{Quelle, siehe Fitch: Camin and Sokal 1965}. Next came 
  a set of parsimony algorithms such as: Fitch-parsimony, Wagner-parsimony ... \todo{Quellen!, Jahreszahlen?}.
  With more and more data, we got new options for calculating probabilities and using next to ancestral states, given branch lengths. The likelihood based algorithms came more in interest.
  Our focus came with another 'data extension'. We wanted to work with the biggest phylogenetic tree which exists at this moment, which goes over all observed species.
  For most species there is no phylogeny, but only a taxonomic classification. So the biggest 'phylogenetic tree' is a synthesis of phylogenetic trees filled with a taxonomic tree.
  \todo{hier Quelle/Hinweis zur datenbank: Open tree of life...} This tree is not binary and therefore the developed algorithms are not directly applicable.
  We have looked at the algorithms that are generally suited to our data, to develop them further for the binary case, and finally to compare their usability with our sythesis trees.

  We have only decided on parsimony algorithms since we have no information on branch lengths and no other additional information like different transition probabilities of our states.

%-------------------------------------------------------------------------------------------------------------------------------------------------------------
%-------------------------------------------------------------------------------------------------------------------------------------------------------------
%-------------------------------------------------------------------------------------------------------------------------------------------------------------
\bibliography{bibliographie}
\bibliographystyle{alphadin}

\end{document}

### 2017-10-26 simulation/Parsimony.py
change parsimony alg; sort figures and add some new ones with the changed parsimony
Former-commit-id: 7239d49690f4a9fb11c7a810cbbc91d85e4f418f

@@ -94,24 +94,28 @@ def parsimony_final(subtree, nodelist):
     if not subtree.is_terminal():
         tags = element[3]
         if len(tags) > 1:
-            shared = False
-            # RULE 1: share any states in common -> assign shared states
-            if ('FL' in tags[0]) and ('FL' in tags[1]):
-                element[2] = 'FL'
-                # subtree._set_color('blue')
-                shared = True
-            if ('P' in tags[0]) and ('P' in tags[1]):
-                if shared:
-                    element[2] = 'FL&P'
-                    # subtree._set_color('magenta')
-                else:
-                    element[2] = 'P'
-                    # subtree._set_color('red')
-                shared = True
-            # RULE 2: no shared states -> assign union of states
-            if not shared:
-                element[2] = 'FL&P'
-                # subtree._set_color('magenta')
+            if ('FL&P') in tags[0]:
+                element[2] = tags[1]
+            else:
+                element[2] = tags[0]
+            # shared = False
+            # # RULE 1: share any states in common -> assign shared states
+            # if ('FL' in tags[0]) and ('FL' in tags[1]):
+            #     element[2] = 'FL'
+            #     # subtree._set_color('blue')
+            #     shared = True
+            # if ('P' in tags[0]) and ('P' in tags[1]):
+            #     if shared:
+            #         element[2] = 'FL&P'
+            #         # subtree._set_color('magenta')
+            #     else:
+            #         element[2] = 'P'
+            #         # subtree._set_color('red')
+            #     shared = True
+            # # RULE 2: no shared states -> assign union of states
+            # if not shared:
+            #     element[2] = 'FL&P'
+            #     # subtree._set_color('magenta')
     else:
         element[2] = element[3][0]
     # go on with children

### 2017-10-30 Paper - Latex/Paper - Skizze - v1.tex
some changes and references to the introduction
Former-commit-id: e3e9b4346751873cb77553d29d30f9bf8ec5c74a

@@
   the ancestral state reconstruction of parasitism. \\
-
-  Researchers of the phylogenies have been dealt with the ancenstral state reconstruction in the 60s.
-  The first methods were only brute force \todo{Quelle, siehe Fitch: Camin and Sokal 1965}. Next came 
-  a set of parsimony algorithms such as: Fitch-parsimony, Wagner-parsimony ... \todo{Quellen!, Jahreszahlen?}.
-  With more and more data, we got new options for calculating probabilities and using next to ancestral states, given branch lengths. The likelihood based algorithms came more in interest.
-  Our focus came with another 'data extension'. We wanted to work with the biggest phylogenetic tree which exists at this moment, which goes over all observed species.
-  For most species there is no phylogeny, but only a taxonomic classification. So the biggest 'phylogenetic tree' is a synthesis of phylogenetic trees filled with a taxonomic tree.
-  \todo{hier Quelle/Hinweis zur datenbank: Open tree of life...} This tree is not binary and therefore the developed algorithms are not directly applicable.
-  We have looked at the algorithms that are generally suited to our data, to develop them further for the binary case, and finally to compare their usability with our sythesis trees.
-
-  We have only decided on parsimony algorithms since we have no information on branch lengths and no other additional information like different transition probabilities of our states.
+  Researchers of the phylogenies have been dealt with the ancenstral state reconstruction in the 
+  60s. The first methods were only brute force \todo{Quelle, siehe Fitch: Camin and Sokal 1965}. 
+  Next came a set of parsimony algorithms such as: Fitch-parsimony \cite{Fitch1971}, 
+  Wagner-parsimony \cite{Swofford1987} ... \todo{weitere?}. \\
+  With more and more data, there is now the possibility to use more information to calculate the 
+  probabilities of the ancestral states. In addition to the states of the leaves, algorithms could 
+  also use branch lengths. The likelihood based algorithms came more in interest. \\
+  Our focus came with another 'data extension'. We wanted to work with the biggest phylogenetic tree 
+  that exists at this moment, which goes over all observed species. For most \todo{most?} species there is no 
+  phylogeny, but only a taxonomic classification. So the biggest 'phylogenetic tree' is a synthesis 
+  of phylogenetic trees filled with a taxonomic tree given by Open Tree of Life \cite{Hinchliff2015}.
+  This tree is not binary and therefore the developed algorithms are not directly applicable. \\
+  In this work, we have looked at the algorithms that are generally suited to our data, to develop 
+  them further for the not binary case, and finally to compare their usability with our sythesis 
+  tree. \\
+  We have decided to consider only parsimony algorithms since we have no information on branch 
+  lengths and no other additional information like different transition probabilities of our states.
 

### 2017-11-02 Paper - Latex/Paper - Skizze - v1.tex
add structure
Former-commit-id: 7dd5bcbcf677e6f6517ba643c1c976ebb3ded707
some disscussion points from the group meeting
Former-commit-id: b69ab5a3e13c28a27711046430cc7d10839eeb84

@@
 
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%--------------------------------------------------------------------------------------------------- 
+\chapter{Methods}
+  \section{Simulation}
+    \begin{itemize}
+      \item build random binary trees, tag these (parameters: parasites vs free-living, beta-distribution)
+      \item run fitch-parsimony, wagner-parsimony, our parsimony like algorithm
+      \item build not binary tree (poisson distribution?)
+      \item run new algorithms
+      \item compare trees (distances)
+    \end{itemize}
+  \section{Implementation}
+\chapter{Results}
+\chapter{Discussion}
+
+  Wie gut kommt unsere Simulation an die echte Datenlage heran. \\
+  Fehlerqoute der Daten an sich? \\
+  Wie gut ist unsere Datenlage? 3 mio knoten, 1.8 named species (leaf nodes), 200.000 leaf nodes mit Information. \\
+  Simulation von subtrees \\
+  Welche Teile des Baumes sind gut, an welchen muss noch viel geforscht werden. \\
+  Wieviele Origins haben wir gefunden, was bedeutet diese Zahl? \\
+
+  Parameter der Simulation:
+  \begin{itemize}
+    \item Wie ist die Verteilung der vergessenen internen Knoten? Zum Wurzelknoten hin mehr vergessen?
+    \item Wie sehen die übergangswahrscheinlichkeiten aus von P->FL und andersherum?
+    \item Verteilung Parasiten zu Freilebend zu keine Information
+  \end{itemize}
+
 %-------------------------------------------------------------------------------------------------------------------------------------------------------------

### 2017-11-15 scripts/R/rotl_test.R
R coding
Former-commit-id: 7db5915ec16e6520fe86be7991b8d85f480d8fa9

@@ -1,0 +1,56 @@
+library(rotl)
+
+print("------------------------Hyla, Salmo, Diadema, Nautilu--------------------------------")
+
+# Step 1: Matching taxonomy to the ott_id
+# taxa <-c("Ceratias", "Homo", "Molothrus")
+taxa <- c("Hyla", "Salmo", "Diadema", "Nautilus")
+# resolved_names <- tnrs_match_names(taxa)
+# To ensure that our search is limited to animal names, we could do:
+#   Check possible values using: tnrs_contexts()
+resolved_names <- tnrs_match_names(taxa, context_name = "Animals")
+resolved_names
+
+print("-------------------------------------------------------------------------------------")
+
+# Step 2: Getting the tree corresponding to our taxa
+my_tree <- tol_induced_subtree(ott_ids = resolved_names$ott_id)
+plot(my_tree, no.margin=TRUE)
+
+print("-------------------------------------------------------------------------------------")
+
+# How to change the ott ids assigned to my taxa?
+inspect(resolved_names, taxon_name = "diadema")
+resolved_names <- update(resolved_names, taxon_name = "diadema", new_row_number = 2)
+
+print("-------------------------------------------------------------------------------------")
+
+# How do I know that the taxa I’m asking for is the correct one?
+diadema_info <- taxonomy_taxon_info(631176)
+tax_rank(diadema_info)
+
+print("-------------------------------------------------------------------------------------")
+
+synonyms(diadema_info)
+
+print("-------------------------------------------------------------------------------------")
+
+# In some cases, it might also be useful to investigate the taxonomic tree descending from an ott_id to check that it’s the correct taxon and to determine the species included in the Open Tree Taxonomy:
+
+diadema_tax_tree <- taxonomy_subtree(631176)
+diadema_tax_tree
+
+print("-------------------------------------------------------------------------------------")
+
+# How do I get the tree for a particular taxonomic group?
+
+# If you are looking to get the tree for a particular taxonomic group, you need to first identify it by its node id or ott id, and then use the tol_subtree() function:
+
+mono_id <- tnrs_match_names("Monotremata")
+mono_tree <- tol_subtree(ott_id = ott_id(mono_id))
+
+## Warning in collapse_singles(tr): Dropping singleton nodes with labels:
+## Ornithorhynchidae ott344066, Ornithorhynchus ott962391, Tachyglossus
+## ott16047, Tachyglossus aculeatus ott16038
+
+plot(mono_tree)

### 2018-01-19 Paper - Latex/Paper - Skizze - v1.tex
Paper - Methods - random binary tree; tag tree

@@
   Our focus came with another 'data extension'. We wanted to work with the biggest phylogenetic tree 
-  that exists at this moment, which goes over all observed species. For most \todo{most?} species there is no 
+  that exists at this moment, which goes over all observed species. For most \todo{most?} species 
+  there is no 
   phylogeny, but only a taxonomic classification. So the biggest 'phylogenetic tree' is a synthesis 
@@
 \chapter{Methods}
+
+  This work consist of two aspects. One is the application of the algorithm to our question
+
+  Diese Arbeit besteht aus zwei Fragestellungen
+  gute Algorithmen zu finden und sie auf unser Anwendungsbeispiel anzuwenden.
+
+  Zur Bewertung der gefundenen / entwickelten algorithmen haben wir eine Simulation ausgeführt.
+
+  Auf der Anderen Seite haben wir unser reales Problem aufgestellt, für die Algorithmen vorbereitet und 
+  diese angewendet.
+
+  Metadata -> Simulation ->  real Data
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Metadata analysis}
+    Properties of real Data - Metadata analysis
+
+    There are some Parameters to find out or notice:
+    \begin{itemize}
+      \item transition probabilities of tags
+      \item multifurcation
+      \item nr of parasites to free-living
+      \item nr of unknown nodes 
+    \end{itemize}
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
   \section{Simulation}
     \begin{itemize}
-      \item build random binary trees, tag these (parameters: parasites vs free-living, beta-distribution)
+      \item build random binary trees, tag these (parameters: parasites vs free-living, 
+        beta-distribution)
       \item run fitch-parsimony, wagner-parsimony, our parsimony like algorithm
@@
     \end{itemize}
+
+    \begin{enumerate}
+      \item build random binary trees
+      \item tag tree
+      \item multifurcate tree
+      \item run maximum parsimony algorithms
+      \begin{itemize}
+        \item Fitch
+        \item Sankoff (Castor package)
+        \item my algorithm
+      \end{itemize}
+      \item Evaluation
+    \end{enumerate}
+
+    %---------------------------------------------------------------------------------------------------
+    \subsection{random binary tree}
+      To get a random binary tree, I used the Phylo package from biopython. They offer a randomized
+        function which returns a BaseTree \footnote{
+          https://github.com/biopython/biopython/blob/master/Bio/Phylo/BaseTree.py
+        }:
+      \begin{lstlisting}
+        from Bio import Phylo
+        Phylo.BaseTree.Tree.randomized(number_leafnodes)
+      \end{lstlisting}
+      From the BaseTree class:
+      \begin{lstlisting}
+        def randomized(cls, taxa, branch_length=1.0, 
+              branch_stdev=None):
+        """Create a randomized bifurcating tree given a list
+              of taxa.
+          :param taxa: Either an integer specifying the number
+              of taxa to create (automatically named taxon#), 
+              or an iterable of taxon names, as strings.
+          :returns: a tree of the same type as this class.
+        """
+      \end{lstlisting}
+      \todo{Zitat von BaseTree und buildTree.py}
+
+    %---------------------------------------------------------------------------------------------------
+    \subsection{tag tree}
+      At this point we want one fully tagged tree, and one less tagged tree which looks like our real 
+        data.\\
+      Let's say the first specie (the root node) was free-living (start with a parasite without a host 
+        makes no sence). For every transition from a node to his child, we take a random number from
+        the father distribution. We decided that from the biological perspective a beta distribution
+        reflects our transition probabilities best (see Figure 2.1 \todo{ref einfügen}). \\
+        For example when our father node was free-living, then we take from the free-living beta
+        distribution. Is the number under the threshold for beeing parasite, we get a change and tag
+        the current node as parasite. Otherwise we tag it as free-living. \\
+        With this procedure we traverse through the tree from the root to every leave node. A part of
+        this code you see here:
+      \begin{lstlisting}
+        from numpy import random
+        if father_tag == 0:
+          # freeliving_distribution:
+          new_random = random.beta(a=A_FL, b=B_FL)
+        else:
+          # parasite_distribution:
+          new_random = random.beta(a=A_P, b=B_P)
+        tag = 0         # -> FL
+        if new_random < percentage_parasites:
+          tag = 1       # -> P
+      \end{lstlisting}
+      \begin{figure}
+        \caption{60\% Free-living - 40\% Parasites}
+        \centering
+          \includegraphics[width=0.5\textwidth]{Figures/40-60.png}
+      \end{figure}
+      \todo{Bessere Beschriftung, Plot neu erstellen! U.a. mit threshold}
+
+      unknowns.. forget information.. nodelist
+
+    %---------------------------------------------------------------------------------------------------
+    \subsection{multifurcate tree}
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{real data analysis}
+    \begin{itemize}
+      \item Import tree
+      \item Import interactions
+      \item run castor algorithm / and others?
+      \item interprete results (leave one out)
+    \end{itemize}
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
   \section{Implementation}
+
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
 \chapter{Results}
+
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
 \chapter{Discussion}
-
+  Wie gut ist der randomisiert erstellte Baum? \\
   Wie gut kommt unsere Simulation an die echte Datenlage heran. \\
   Fehlerqoute der Daten an sich? \\
-  Wie gut ist unsere Datenlage? 3 mio knoten, 1.8 named species (leaf nodes), 200.000 leaf nodes mit Information. \\
+  Wie gut ist unsere Datenlage? 3 mio knoten, 1.8 named species (leaf nodes), 200.000 leaf nodes mit 
+  Information. \\
   Simulation von subtrees \\
@@
 
-%-------------------------------------------------------------------------------------------------------------------------------------------------------------
-%-------------------------------------------------------------------------------------------------------------------------------------------------------------
-%-------------------------------------------------------------------------------------------------------------------------------------------------------------
+  Selecting of the 'right'  / best Distribution
+
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
 \bibliography{bibliographie}

### 2018-01-19 Paper - Latex/Paper - Skizze - v1.tex
Paper - Methods - multifurcate tree

@@
       \todo{Bessere Beschriftung, Plot neu erstellen! U.a. mit threshold}
-
-      unknowns.. forget information.. nodelist
+      We save each tag with the associated node ID in a nodelist, where we can save all information
+        about our nodes, we want. \\
+      The real tree has much less information, we have only information from some current species 
+        (leave nodes) and \todo{and probably negligible internal nodes}. \\
+      To simulate our real tree we save for every node an empty placeholde except for some leave nodes.
+      There we save the tags again. The amount of these unknown information is one parameter, which we
+      got from our real tree. Or which we can change to \todo{...}
+      \TODO{Was hiervon gehört ind Methoden, was schon in Implementierung oder ganz woanders hin?}
 
@@
     \subsection{multifurcate tree}
+      Another parameter is the nature and strength of the multifunction of the tree, since we do not 
+        have a binary tree in the real case. After several measurements and analyzes, which we explain 
+        in \todo{section/chapter x}, we decided to use a $1 over x$ distribution, where x is the depth 
+        of a node. This means, how deaper we are, how less information we have. \\
+      We traverse through the tree and pick a random number between 0 and 1. If random number is smaller 
+        as our limit ($1 over x$), than we forget the node and hang every child to the father node of 
+        the current node.
+      \todo{then / than}
+      \begin{lstlisting}
+        from numpy import random
+        from utilities import Helpers
+
+        def get_non_binary_tree(subtree, nodelist):
+          i = 0
+          while i != len(subtree.clades):
+            if subtree.clades[i].is_terminal():             # is leave node?
+              i += 1
+            else:
+              element = Helpers.find_element_in_nodelist(subtree.clades[i].name, nodelist)
+              limit = get_limit(element[1])
+              new_random = random.uniform()                 # choose if we want to delete ourselve
+              if new_random < limit:                        # or new_random < 0.9:
+                subtree.clades += subtree.clades[i].clades  # add children
+                del subtree.clades[i]                       # delete internal node
+              else:                                         # if we don't deleted ourselve go on with children
+                get_non_binary_tree(subtree.clades[i], nodelist)  # otherwise the children are in the current clade array
+                i += 1
+          return
+
+          def get_limit(depth):
+            limit = 1 - 1 / ((depth + 3) / 4)
+            if limit < 0.1:
+              limit = 0.1
+            return limit
+      \end{lstlisting}
+      % # current clades: clade_1 clade_2 ... clade_i-1 clade_i ... clade:_n
+      % # add children of clade_i, delete clade_i
+      % # new clades:clade_1 clade_2 ... clade_i-1 child_clade_1 ... child_clade_m ... clade:_n
+      % # child_clade_1 is new clade i
+      Wir lassen das Limit nicht beliebig klein werden, sondern beschränken es auf 0.1.
+
   %---------------------------------------------------------------------------------------------------

### 2018-01-24 Paper - Latex/Paper - Skizze - v1.tex
Paper - Methods - Fitch Figure 1
some new figures
Fitch Version evaluations

@@
     %---------------------------------------------------------------------------------------------------
+    \subsection{maximum parsimony algorithms}
+      \subsubsection{Fitch maximum parsimony}
+        Described from [COO98] + others ... - implemented for multifurcating trees
+
+        Fitch algorithm for binary trees:
+        \begin{figure}
+          \caption{bla}
+          \centering
+            \includegraphics[width=0.5\textwidth]{Figures/Fitch1.png}
+        \end{figure}
+
+        Der Baum hat die folgende Struktur: Alle inneren Knoten sind leer. In den Blattknoten befindet 
+        sich entweder das Tag FL oder P, oder deren Vereinigung, wenn es sich um einen unknown node handelt.
+
+        Der Fitch Algorithmus ist aufgeteilt in drei Schritte, in welchen man jeweils durch den Baum traversiert.
+        Schritt 1 beginnt von de Blättern aus, da sich dort zu Beginn die einzige Information befindet. 
+        Für jeden Knoten gilt, wenn seine Kinder schon Information enthalten, dann bilde die Schnittmenge 
+        der Tags und schreibe diese als Information in den aktuellen Knoten. Ist die Schnittmenge leer, 
+        dann schreibe die Vereinigung aller möglichen Tags in den Knoten. Für alle Kinder, die noch keine 
+        Information haben, führe diesen Schritt erst für diese aus.
+        Schritt zwei geht von den Kindern der Wurzel bis zu den Vätern der Blätter. Jeder Knoten bekommt 
+        einen zweiten Tag, der sich aus der Vereinigung des Tags des Vaterknoten und der Geschwisterknoten
+        zusammensetzt. Ist diese leer, bekommt der Knoten wieder die Vereinigung aller Tags, also ${FL,P}$ als Tag.
+
+        Hier gibt es einige Möglichkeiten, wie dieser Schritt genau aussieht.
+        1. Version: Es wird nur der erste Tag vom Vaterknoten genutzt. Außerdem wird von den 
+        Geschwisterknoten zuerst der Schnitt gebildet, und danach vom Ergebnis nochmal mit dem Vaterknoten zusammen.
+        (Immer wenn der Schnitt leer ist, ist das Ergebnis die Vereinigung aller Tags, also ${FL,P}$. Auch im folgenden...)
+        2. Version: Es wird nur der erste Tag vom Vaterknoten genutzt. Er wird zusammen mit den 
+        Geschwistertags genommen und direkt ein Schnitt aller Mengen gebildet.
+        3. Version: Es werden alle vorherigen Tags vom Vater genutzt und von diesen ein Schnitt gebildet.
+        Das selbe gilt für die Geschwistertags. Und dann wird ein dritter Schnitt zwischend en Ergebnissen gebildet.
+        4. Version: Es werden alle Tags genutzt und direkt in einem Schnitt zusammengenommen.
+
+        Der Finale Schritt traversiert nochmal über den Baum und Bildet aus den zwei Tags pro Knoten einen finalen
+        Tag, indem wieder der Schnitt der beiden Tags das Ergebnis ist.
+
+        Ich habe diese Versionen mit 100 Bäumen mit 10000 Blattknoten und der Verteilung 60\% FL zu 40\% P simuliert.
+        Bei 90 \% unbekannten Knoten lag Version 1 zu 89.67 \%, Version 2 zu 89.67 \%, Version 3 zu 
+          90.72 \% und Version 4 zu 90.74 \% richtig.
+
+        \begin{figure}
+          \caption{bla}
+          \centering
+            \includegraphics[width=0.6\textwidth]{Figures/simulation_fitch_evaluation.png}
+        \end{figure}
+
+        How to extend Fitch for multifunction?:
+        \begin{figure}
+          \caption{bla}
+          \centering
+            \includegraphics[width=1\textwidth]{Figures/Fitch2.png}
+        \end{figure}
+
+      \subsubsection{Sankoff}
+
+      \subsubsection{my Algorithm}
+
+  %---------------------------------------------------------------------------------------------------
   %---------------------------------------------------------------------------------------------------

### 2018-01-24 simulation/get_plots.py

@@ -32,6 +32,28 @@ def main():
     plot_hist('40-old')
     plot_data('40-old')
 
+    filepath = 'evaluation/40-fitch-unknown_plot.csv'
+    data = np.genfromtxt(filepath, delimiter=',', skip_header=1, skip_footer=0, names=['unknown', 'y_fitch1', 'y_fitch2', 'y_fitch3', 'y_fitch4'])
+
+    plt.tight_layout()
+    plt.show()
+
+    # plt.title(str(percentage_parasites), fontweight='bold')
+    
+    plt.plot(data['unknown'], data['y_fitch1'], color='g', linestyle='dashed', 
+        label='Fitch 1', linewidth=0.5, marker='.', markerfacecolor='black')#, markersize=5)
+    plt.plot(data['unknown'], data['y_fitch2'], color='c', linestyle='dashed', 
+        label='Fitch 2', linewidth=0.5, marker='.', markerfacecolor='black')
+    plt.plot(data['unknown'], data['y_fitch3'], color='m', linestyle='dashed', 
+        label='Fitch 3', linewidth=0.5, marker='.', markerfacecolor='black')
+    plt.plot(data['unknown'], data['y_fitch4'], color='y', linestyle='dashed', 
+        label='Fitch 4', linewidth=0.5, marker='.', markerfacecolor='black')
+    plt.xlabel('percentage unknown', fontsize=9)
+    plt.ylabel('correct predicted', fontsize=9)
+    plt.legend(loc="lower left", fontsize=9) #, scatterpoints=1, numpoints=2)
+    plt.axis([0, 1, 85, 100])
+    plt.grid()
+
     plt.tight_layout()
     plt.show()
 

### 2018-01-24 simulation/main_fitch.py

@@ -1,0 +1,222 @@
+"""main method"""
+import csv
+import datetime
+import sys
+from copy import deepcopy
+from pprint import pprint
+from time import gmtime, strftime
+
+from Bio import Phylo
+from termcolor import colored
+
+from non_binary_simulation import buildTree
+from non_binary_simulation.parsimony.Fitch_MP import fitch_parsimony
+from non_binary_simulation.parsimony.My_MP import my_parsimony
+from non_binary_simulation.parsimony.Sankoff_MP import sankoff_parsimony
+from utilities import Drawings, Helpers
+
+# input arguments
+args = sys.argv
+
+# global variables:
+START_TIME = datetime.datetime.now().replace(microsecond=0)
+CURRENT_TIME = datetime.datetime.now().replace(microsecond=0)
+
+# values for simulation:
+number_leafnodes = int(sys.argv[1])
+number_trees = int(sys.argv[2])         # number of simulated trees
+percentage_parasites = float(sys.argv[3]) # between 0 and 1
+percentage_unknown = float(sys.argv[4])   # between 0 and 1
+
+                            # [A_FL, B_FL, A_P, B_P]
+beta_distribution_parameters = [7, 3.5, 3.5, 7]   # 40 P - 60 FL
+
+# decide for distribution:
+if percentage_parasites == 0.1:
+    beta_distribution_parameters = [7, 24, 0.5, 7]     # 10 P - 90 FL
+elif percentage_parasites == 0.2:
+        beta_distribution_parameters = [7, 13.25, 1.25, 7] # 20 P - 80 FL
+elif percentage_parasites == 0.3:
+    beta_distribution_parameters = [7, 8.5, 2, 7]      # 30 P - 70 FL
+elif percentage_parasites == 0.4:
+    beta_distribution_parameters = [7, 5.5, 2.75, 7]   # 40 P - 60 FL
+elif percentage_parasites == 0.5:
+    beta_distribution_parameters = [7, 3.5, 3.5, 7]    # 50 P - 50 FL
+
+print(beta_distribution_parameters)
+
+def main():
+    """Main method"""
+    global START_TIME
+    global CURRENT_TIME
+    print(colored("------------------------ start simulation ------------------------", "green"))
+    print(strftime("%Y-%m-%d %H:%M:%S", gmtime()))
+    CURRENT_TIME = Helpers.print_time(START_TIME)
+    print(colored("---------------- metadata ----------------", "green"))
+    metadata()
[…]

### 2018-01-24 simulation/non_binary_simulation/parsimony/Fitch_MP.py

@@ -1,11 +1,8 @@
 from copy import deepcopy
 
-from utilities import Helpers
+from utilities import Fitch_Versions, Helpers
 
-# TAGS = ["FL", "P"]
-TAGS = [0, 1]
-
-def fitch_parsimony(tree_clade, nodelist):
+def fitch_parsimony(tree_clade, nodelist, version):
     """parsimony implemented from [COO98] - changed for multifurcating trees"""
     # down:
     parsimony_down(tree_clade, nodelist)
@@ -20,7 +17,8 @@ def fitch_parsimony(tree_clade, nodelist):
         child = Helpers.find_element_in_nodelist(clade.name, nodelist)
         sublist = deepcopy(children)
         del sublist[i]
-        parsimony_up(clade, nodelist, parent, sublist)
+        # ToDo: decide which one, next ToDo: a second parsimony down?
+        Fitch_Versions.parsimony_up(clade, nodelist, parent, sublist, version)
     # final:
     parsimony_final(tree_clade, nodelist)
     return
@@ -40,7 +38,7 @@ def parsimony_down(subtree, nodelist):
         child_tags.append(child[4][0])
     element = Helpers.find_element_in_nodelist(subtree.name, nodelist)
     # get intersection or union
-    tag_list = get_intersect_or_union(child_tags)
+    tag_list = Helpers.get_intersect_or_union(child_tags)
     # add new tag
     element[4].append(tag_list)
     return
@@ -62,7 +60,7 @@ def parsimony_up(subtree, nodelist, parent, siblings):
         siblings_tags += sibling[4]
     
     # get intersection or union
-    tag_list = get_intersect_or_union(siblings_tags)
+    tag_list = Helpers.get_intersect_or_union(siblings_tags)
     # add new tag
     element[4].append(tag_list)
 
@@ -91,7 +89,7 @@ def parsimony_final(subtree, nodelist):
         element[3] = element[4][0][0]
     else:
         # get intersection or union
-        tag_list = get_intersect_or_union(element[4])
+        tag_list = Helpers.get_intersect_or_union(element[4])
         # add final tag
         tag_string = ""
         for tag in tag_list:
@@ -103,26 +101,3 @@ def parsimony_final(subtree, nodelist):
         for clade in subtree.clades:
             parsimony_final(clade, nodelist)
     return
-
-def get_intersect_or_union(tags_list):
-    """returns the intersection of all list elements, if not empty"""
-    # Arguments:
-    #   tags_list - a list of tag_lists
[…]

### 2018-01-24 simulation/utilities/Fitch_Versions.py

@@ -1,0 +1,189 @@
+from copy import deepcopy
+
+from utilities import Helpers
+
+# Version 1:
+# use only first tag of parent, and every sibling
+# get_intersect_or_union(siblings_tags)
+# get_intersect_or_union(both)
+
+# Version 2:
+# use only first tag of parent, and every sibling
+# get_intersect_or_union(both)
+
+# Version 3:
+# use every tag
+# get_intersect_or_union(siblings_tags)
+# get_intersect_or_union(parent_tags)
+# get_intersect_or_union(both)
+
+# Version 4:
+# use every tag
+# get_intersect_or_union(both)
+
+# ----------------------------------------------------------------------------------------
+# 100  trees simulated with 10000 leafnodes 40.0 % parasites and 90.0 % unknown leafnodes.
+# correctly predicted (including already known leaf nodes):
+# differences Fitch1 / Fitch2 / Fitch3 / Fitch4
+# | 89.67 % | 89.67 % | 90.72 % |90.74 % |
+
+def parsimony_up(subtree, nodelist, parent, siblings, version):
+    if version == 1:
+        parsimony_up1(subtree, nodelist, parent, siblings)
+    elif version == 2:
+        parsimony_up2(subtree, nodelist, parent, siblings)
+    elif version == 3:
+        parsimony_up3(subtree, nodelist, parent, siblings)
+    elif version == 4:
+        parsimony_up4(subtree, nodelist, parent, siblings)
+    else:
+        print("This version number (", version, ") do not exist!")
+    return
+
+# -------------------- Version 1 --------------------
+def parsimony_up1(subtree, nodelist, parent, siblings):
+    """parsimony part: up direction -> from root to leafs"""
+    # Arguments:
+    #   subtree
+    #                   0   1       2           3           4
+    #   nodelist    - [id, depth, originaltag, finaltag, calc[taglist]]
+    #   parent      - nodelist element
+    #   siblings     - [nodelist element]
+    element = Helpers.find_element_in_nodelist(subtree.name, nodelist)
+
+    parent_tag = parent[4][0]  # parent[4] could look like [['0', '1'], ['1']] or [['1']]
+    siblings_tags = []
+    for sibling in siblings:
+        siblings_tags.append(sibling[4][0])
+
+    # get intersection or union
+    both_tags = Helpers.get_intersect_or_union(siblings_tags)
+    both_tags = [both_tags]
+    both_tags.append(parent_tag)
[…]

### 2018-01-24 simulation/utilities/Helpers.py

@@ -4,6 +4,8 @@ import datetime
 
 from termcolor import colored
 
+# TAGS = ["FL", "P"]
+TAGS = [0, 1]
 
 def find_element_in_nodelist(id_name, nodelist):
     """finds id in nodelist and returns the element"""
@@ -14,3 +16,28 @@ def print_time(time_old):
     # Text colors: grey, red, green, yellow, blue, magenta, cyan, white
     print(colored("time needed:", "magenta"), time_new - time_old)
     return time_new
+
+def get_intersect_or_union(tags_list):
+    """returns the intersection of all list elements, if not empty"""
+    # Arguments:
+    #   tags_list - a list of tag_lists
+    #       tags_list[tag_list]
+    if len(tags_list) == 1:
+        return tags_list[0]
+    # pairwise intersection
+    tag_set = []
+    while len(tags_list) > 1:
+        tag_list_i = tags_list[0]
+        tag_list_j = tags_list[1]
+        # RULE 1: share any states in common -> assign shared states
+        # intersection:
+        tag_set = (set(tag_list_i) & set(tag_list_j))
+        # RULE 2: no shared states -> assign union of states
+        if tag_set == set():
+            # union:
+            return TAGS
+        else:
+            tags_list.remove(tag_list_i) # same as 
+            tags_list.remove(tag_list_j)
+            tags_list.append(list(tag_set))
+    return list(tag_set)

### 2018-01-26 Paper - Latex/Paper - Skizze - v1.tex
Paper - Methods - Multifurcation

@@
 \title{master thesis}
-\date{August 2017}
+\date{Januar 2018}
+
+% \hfuzz=\maxdimen \tolerance=10000 \hbadness=10000
 
@@
   With more and more data, there is now the possibility to use more information to calculate the 
-  probabilities of the ancestral states. In addition to the states of the leaves, algorithms could 
+  probabilities of the ancestral states. In addition to the states of the leafs, algorithms could 
   also use branch lengths. The likelihood based algorithms came more in interest. \\
@@
 
-  This work consist of two aspects. One is the application of the algorithm to our question
+  This work consist of two aspects. One is the application of the algorithm to our question the
+    other a simulation of this to proof the credibility of our methods. \\
+  The resulting procedure is as follows:
+  \begin{enumerate}
+    \item Get the real tree and real data for the leaf nodes.
+    \item Get metadata of these for a realisitc the simulation.
+    \item Build and run the simulation.
+    \item Evaluation of parameters for the simulation and the real problem.
+    \item Run the resulted algorithm on the original data.
+    \item Evalute and interprete results. -> Origins etc...
+  \end{enumerate}
 
-  Diese Arbeit besteht aus zwei Fragestellungen
-  gute Algorithmen zu finden und sie auf unser Anwendungsbeispiel anzuwenden.
+  % Zur Bewertung der gefundenen / entwickelten algorithmen haben wir eine Simulation ausgeführt.
 
-  Zur Bewertung der gefundenen / entwickelten algorithmen haben wir eine Simulation ausgeführt.
-
-  Auf der Anderen Seite haben wir unser reales Problem aufgestellt, für die Algorithmen vorbereitet und 
-  diese angewendet.
-
-  Metadata -> Simulation ->  real Data
+  % Auf der Anderen Seite haben wir unser reales Problem aufgestellt, für die Algorithmen vorbereitet und 
+  % diese angewendet.
 
@@
     \end{itemize}
+
+    %---------------------------------------------------------------------------------------------------
+    \subsection{countings}
+      Some simple countings...\\
+      nr of parasites, free-living and unknown nodes ... from whole tree, subtrees...
+
+    %---------------------------------------------------------------------------------------------------
+    \subsection{Multifurcation}
+      One property of the tree is its ridge of multifurcation. For this we collected for every node its
+        number of children (degree $-1$), and plottet this in an histogram, how much nodes we have for 
+        every degree. Then we tried to find a function which best discribes this behavior. In figure 
+        \ref{fig:HistogramsOfMultifurcations} is this plot shown with three functions, which came 
+        \todo{close(st)} to this goal: $\frac{1000000000000000}{x^4}$ (magenta), 
+        $\frac{300000000000}{x^3}$ (red) and $\frac{80000000}{x^2}$ (black). \\
+      \begin{figure}[h]
+        \caption{Histogram of multifurcations and fitting functions}
+        \centering
+        \label{fig:HistogramsOfMultifurcations}
+        \includegraphics[width=0.7\textwidth]{Figures/HistogramsOfMultifurcations.png}
+      \end{figure}
+      From the biology we know, that this multifurcation is very clouded. Some parts of the tree are 
+        well known and others have not been very interesting for the research so far. So we also wanted 
+        to know how the multifurcations behave in some interesting subtrees. \\
+      \todo{subtrees... there is some old stuff...} \\
+      \todo{other subsections here...} \\
 
@@
         from Bio import Phylo
-        Phylo.BaseTree.Tree.randomized(number_leafnodes)
+        Phylo.BaseTree.Tree.randomized(number_leaf nodes)
       \end{lstlisting}
@@
         the current node as parasite. Otherwise we tag it as free-living. \\
-        With this procedure we traverse through the tree from the root to every leave node. A part of
+        With this procedure we traverse through the tree from the root to every leaf node. A part of
         this code you see here:
@@
       The real tree has much less information, we have only information from some current species 
-        (leave nodes) and \todo{and probably negligible internal nodes}. \\
-      To simulate our real tree we save for every node an empty placeholde except for some leave nodes.
+        (leaf nodes) and \todo{and probably negligible internal nodes}. \\
+      To simulate our real tree we save for every node an empty placeholde except for some leaf nodes.
       There we save the tags again. The amount of these unknown information is one parameter, which we
@@
           while i != len(subtree.clades):
-            if subtree.clades[i].is_terminal():             # is leave node?
+            if subtree.clades[i].is_terminal():             # is leaf node?
               i += 1
@@
         einen zweiten Tag, der sich aus der Vereinigung des Tags des Vaterknoten und der Geschwisterknoten
-        zusammensetzt. Ist diese leer, bekommt der Knoten wieder die Vereinigung aller Tags, also ${FL,P}$ als Tag.
+        zusammensetzt. Ist diese leer, bekommt der Knoten wieder die Vereinigung aller Tags, also $\{FL,P\}$ als Tag.
 
@@
         Geschwisterknoten zuerst der Schnitt gebildet, und danach vom Ergebnis nochmal mit dem Vaterknoten zusammen.
-        (Immer wenn der Schnitt leer ist, ist das Ergebnis die Vereinigung aller Tags, also ${FL,P}$. Auch im folgenden...)
+        (Immer wenn der Schnitt leer ist, ist das Ergebnis die Vereinigung aller Tags, also $\{FL,P\}$. Auch im folgenden...)
         2. Version: Es wird nur der erste Tag vom Vaterknoten genutzt. Er wird zusammen mit den 
@@
       \subsubsection{Sankoff}
+        Maximum parsimony algorithm from Sankoff implemented in the R package castor.
 
@@
 \chapter{Results}
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Influence of different parameters}
+
+  \begin{figure}
+    \caption{Influence of unknown data to prediction}
+    \centering
+    \includegraphics[width=1\textwidth]{Figures/simulation_evaluation_1.png}
+  \end{figure}
 

### 2018-01-31 metadata/extract_globi_data.py
extract data from GloBI data dump (this replaces get_interactions.R)

@@ -1,0 +1,114 @@
+# This code runs for about 10 minutes.
+
+import csv
+import itertools
+from time import gmtime, strftime
+
+
+def main():
+    print(strftime("%Y-%m-%d %H:%M:%S", gmtime()))
+    print('-------------------')
+
+    filepath = "../data/GloBI_Dump/interactions.tsv"
+    freeliving_source = ["parasiteOf", "pathogenOf"]
+    freeliving_target = ["hasParasite", "hasPathogen"]
+    parasite_source = ["preysOn", "eats", "flowersVisitedBy", "hasPathogen", "pollinatedBy", "hasParasite", "hostOf"]
+    parasite_target = ["preyedUponBy", "parasiteOf", "visitsFlowersOf", "pathogenOf", "hasHost"]
+    #           [["ott_id","taxon_name"]]
+    freelivings = []
+    parasites = []
+    SAME_AS = []
+    freelivings_path = '../data/interaction_data/freelivings.csv' 
+    parasites_path = '../data/interaction_data/parasites.csv' 
+
+    index = 0
+    no_ott_source = 0
+    no_ott_target = 0
+
+    with open(filepath, "r", encoding="utf8") as tsv_file:
+        reader = csv.reader(tsv_file, delimiter='\t')
+        for row in reader:
+            # print(row)
+            # break
+            index += 1
+            interaction = row[10]
+            if row[0] != '':
+                if len(row[0].split(':')) < 2:
+                    joined = ''.join(row[:6])
+                    if joined.find('SAME_AS') != -1:
+                        ott_index = row.index('SAME_AS') + 1
+                        SAME_AS.append([row[10], row[ott_index], row[ott_index + 1]])
+                    else:
+                        no_ott_source += 1
+                else:
+                    ott = row[0].split(':')[1]
+                    name = row[1]
+                    if interaction in freeliving_source:
+                        freelivings.append([ott, name])
+                    elif interaction in parasite_source:
+                        parasites.append([ott, name])
+            if row[11] != '':
+                if len(row[11].split(':')) < 2:
+                    if ((''.join(row[10:15])).find('SAME_AS')) != -1:
+                        print('target:', row[10:15])
+                    no_ott_target += 1
+                else:
+                    ott = row[11].split(':')[1]
+                    name = row[12]
+                    if interaction in freeliving_target:
+                        freelivings.append([ott, name])
[…]

### 2018-01-31 Paper - Latex/Paper - Skizze - v1.tex
Paper - Methods - GloBI + Countings

@@
   %---------------------------------------------------------------------------------------------------
+  \section{Get data}
+    %---------------------------------------------------------------------------------------------------
+    \subsection{GloBI}
+      For tagging our leave nodes, we use the GloBI (Global Biotic Interactions) database. This database 
+        consists of entries of the form: species A interacts with B. \\
+      We appointed some interactions, where we know from the biological perspective that the species 
+      source or target has to be a parasite or a free-living species. These are the following:
+      \begin{lstlisting}
+        freeliving_source = ["parasiteOf", "pathogenOf"]
+        freeliving_target = ["hasParasite", "hasPathogen"]
+        parasite_source = ["preysOn", "eats", "flowersVisitedBy", "hasPathogen", "pollinatedBy", "hasParasite", "hostOf"]
+        parasite_target = ["preyedUponBy", "parasiteOf", "visitsFlowersOf", "pathogenOf", "hasHost"]
+      \end{lstlisting}
+      We build two lists: parasites and free-livings, and add the source or targets of an interaction
+        to these. \\
+      \todo{klar? Oder Beispiel bringen? (Katze isst Maus -> Katze ist Freilebend)} \\
+      % For every interaction from these lists, we get one or two species for our parasite or 
+      %   free-living lists.
+      \todo{ott id hier erwähnen?} \\
+      \todo{einige spezies nicht mit einbezogen, da sie keine OTT id haben, hier könnte man noch verbessern (future work)}
+      \todo{You can find all interaction types here: https://github.com/jhpoelen/eol-globi-data/blob/master/eol-globi-lib/src/main/java/org/eol/globi/domain/InteractType.java .}
+
+    %---------------------------------------------------------------------------------------------------
+    \subsection{OTL}
+      \todo{Open Tree of Life}
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
   \section{Metadata analysis}
@@
     %---------------------------------------------------------------------------------------------------
-    \subsection{countings}
+    \subsection{Countings}
       Some simple countings...\\
       nr of parasites, free-living and unknown nodes ... from whole tree, subtrees...
+      \begin{center}
+        \begin{tabular}{ | l | p{3cm} | }
+          \hline
+          Name & Number of \\
+          \hline \hline
+          interactions & 5346414 \\ \hline
+          freeliving species & 48875 (distinct) \\ \hline
+          parasite species &  64125 (distinct) \\ \hline
+          unused possible species & 2126 (source), 2144439 (target) \\
+          % number of freelivings: 509595
+          % number of freelivings: 45881 (distinct)
+          % number of parasites: 3438001
+          % number of parasites: 63532 (distinct)
+          % number of SAME_AS: 16012
+          % number of SAME_AS: 5667 (distinct)
+          \hline  
+        \end{tabular}
+      \end{center}
 

### 2018-01-31 metadata/build_metadata.sh
cleanup, add shell script

@@ -1,0 +1,17 @@
+
+# -------- -------- cleanup and build filesystem -------- -------- #
+rm -rf data                                 #delete preexisting data dir
+mkdir data                                  #make data dir
+cd data
+
+# -------- -------- get data and unzip -------- -------- #
+mkdir GLoBI_Dump
+cd GLoBI_Dump
+
+if wget -q https://depot.globalbioticinteractions.org/datasets/org/globalbioticinteractions/interactions/0.1/interactions-0.1-ott.zip -nv; then echo "GLoBI DL succesful"; else echo "GLoBI DL-link broken" 1>&3; exit 1;  fi
+unzip interactions-0.1-ott.zip
+gunzip interactions.tsv.gz
+
+# -------- -------- build metadata files -------- -------- #
+cd ../../metadata
+extract_globi_data.py

### 2018-01-31 scripts/unused/prepareInteractions.py

@@ -1,56 +1,0 @@
-import csv
-
-# First define a dialect describing your tsv format. See the documentation on dialects for more information.
-class TsvDialect(csv.Dialect):
-    delimiter = '\t'
-    lineterminator = '\n'
-    # Controls when quotes should be generated by the writer and recognised by the reader.
-    # It can take on any of the QUOTE_* constants (see section Module Contents) and defaults to QUOTE_MINIMAL.
-    quoting = csv.QUOTE_NONE
-    escapechar = None
-    skipinitialspace = True
-    strict = True
-
-# you can just pass this class around, or you can register it under a name
-csv.register_dialect('tsv', TsvDialect)
-# Then you can walk through each line and copy to a new tsv:
-
-# with open('../data/interactions/interactions.tsv', 'r', encoding="latin1") as src, open('../data/interactions/interactions - decreased.tsv', 'w', encoding="latin1") as res:
-#     csrc = csv.reader(src, dialect='tsv')
-#     cres = csv.writer(res, dialect='tsv')
-#     for row in csrc:
-#         newrow = row[:34].copy()
-#         newrow = newrow[1:].copy()
-#         cres.writerow(newrow)
-#         # print(*newrow, file=res, sep='\t')
-
-
-with open('../data/interactions/interactions - decreased.tsv', 'r', encoding="latin1") as fin, open('../data/interactions/interactions - decreased2.tsv', 'w', encoding="latin1") as fout:
-    freader = csv.reader(fin, dialect='tsv')
-    fwriter = csv.writer(fout, dialect='tsv')
-    idx = 1
-    for line in freader:
-        line[4], line[0] = line[0], line[4] #switches position between first and last column
-        del line[3] #delete fourth column
-        line.insert(0, idx)
-        fwriter.writerow(line)
-        idx += 1
-
-# 0   1   2   3   4  
-# sourceTaxonId   sourceTaxonIds  sourceTaxonName sourceTaxonRank sourceTaxonPathNames
-# 5   6   7   8   9
-# sourceTaxonPathIds      sourceTaxonPathRankNames        sourceLifeStageId   sourceLifeStageName     sourceBodyPartId
-# 10  11  12  13  14
-# sourceBodyPartName      sourcePhysiologicalStateId      sourcePhysiologicalStateName    interactionTypeName interactionTypeId
-# 15  16  17  18  19 
[…]

### 2018-01-31 metadata/build_metadata.sh
cleanup

@@ -14,4 +14,4 @@ gunzip interactions.tsv.gz
 
 # -------- -------- build metadata files -------- -------- #
 cd ../../metadata
-extract_globi_data.py
+extract_globi_data.py > log-extract_globi_data.txt

### 2018-01-31 metadata/build_nodelists.py

@@ -8,8 +8,8 @@ from termcolor import colored, cprint
 
 from Helpers import print_time
 
-path_parasites = "../data/interaction_data/parasite.csv"
-path_freelivings = "../data/interaction_data/freeliving.csv"
+path_parasites = "../data/interaction_data/parasites.csv"
+path_freelivings = "../data/interaction_data/freelivings.csv"
 
 # global variables:
 START_TIME = datetime.datetime.now().replace(microsecond=0)

### 2018-01-31 scripts/unused/get_interactions_by_type.R

@@ -1,55 +1,0 @@
-library(rglobi)
-
-main <- function() {
-    print("-------- get all Parasites: --------")
-    # we have to split our request, first we ask for the parasites as a source of interactions, then as a target
-    print("parasites source:")
-    # use source of these interactions:
-    parasite_source <- c("parasiteOf", "pathogenOf")
-    ps_data = get_data(parasite_source, c(1:2))
-
-    print("parasites target:")
-    # use target of these interactions:
-    parasite_target <- c("hasParasite", "hasPathogen")
-    pt_data = get_data(parasite_target, c(6:7))
-
-    print(paste("# parasites source =",nrow(ps_data)))
-    print(paste("# parasites target =",nrow(pt_data)))
-    p_data <- rbind(ps_data, pt_data)
-    p_data <- p_data[!duplicated(p_data),]
-    print(paste("# total without duplicates=",nrow(p_data)))
-
-    write.csv(p_data, file = "output.csv")
-    return()
-}
-
-get_data <- function(interactions, rows) {
-    limit <- 5000
-    i <- 0
-    # use otherkeys to get more than a limited result from the query
-    otherkeys = list("limit"=limit, "skip"=i)
-    raw_data <- get_interactions_by_type(interactiontype = interactions, otherkeys = otherkeys)
-    reduced_data <- raw_data[rows]
-    data <- reduced_data[!duplicated(reduced_data),]
-    print(paste(i+1,"th request"))
-    print(nrow(data))
-
-    while(nrow(raw_data) >= limit) {
-        i <- i + 1
-        skip <- i * limit
-        otherkeys = list("limit"=limit, "skip"=skip, "taxonIdPrefix"="OTT")
-        raw_data <- get_interactions_by_type(interactiontype = interactions, otherkeys = otherkeys)
-        reduced_data <- raw_data[rows]
-        reduced_data <- reduced_data[!duplicated(reduced_data),]
-        data <- rbind(data, reduced_data)
-        if(nrow(data) > 10000) {
-            data <- data[!duplicated(data),]
-            print(paste(i+1,"th request"))
-            print(nrow(data))
-        }
-    }
-    colnames(data) <- c("taxon_external_id", "taxon_name")
-    return(data)
-}
-
-main()

### 2018-02-04 Paper - Latex/Paper - Skizze - v2.tex
Paper - add comments

--- 2018-01-31 Paper - Latex/Paper - Skizze - v1.tex
@@
 \chapter{Introduction}
+  \anmerkungstext{Alle Figures richtig beschriften. Generell: Alle Figure captions sollten selbsterklärend sein. Sprich, ich sollte 
+    nur die Caption (normalerweise auch unter dem Bild) lesen und nicht den Rest das Papers und dann 
+    trotzdem verstehen können, was eigentlich passiert ist und - hilfreich - auch warum das relevant 
+    ist. (Bernhard)} \\ \\
+
+  \anmerkung{allgemein zu diesem Kapitel:} \\
+  \anmerkung{Eine Einleitung hat etwa 2 Seiten. General problem -> more specific problem (Emanuel)}
+  \anmerkungstext{Die Intro ist noch arg knapp =) und ich erkenne die Struktur noch nicht ganz.
+    Mein Vorschlag einer Gliederung (jeweils ca. ein Absatz)1) Motivation: \\
+      * Was ist das große Ziel? Was soll erreicht werden \\
+      * Warum ist das relevant? Was könnte man dann tun? \\
+    2) Hintergrund \\
+      * Was gab es in dieser Richtung bereits als ganze Ansätze oder wenn nicht, warum nicht? Woran 
+        ist es bisher gescheitert  \\
+      * welche Grundlagen sind notwendig: \\
+      ** open tree of life: Was ist das, warum relevant und überlegen als reine Ansätze? \\
+      ** Algorithmen: Was gibt es? Ruhig ausführlicher als hier bereits und vor allem auch nach einer 
+        Darstellung am Ende ableiten, was für uns relevant ist. Also beschreiben, wie Methode a, b, c 
+        funktionieren und dann abwägen, was daher für Dich am relevantesten ist. \\
+    3) Outlook/Structure of this work (Bernhard)} \\
+
   This paper is about the further development of parsimony algorithms for non-binary trees, applied 
@@
   the ancestral state reconstruction of parasitism. \\
+  \anmerkung{Der erste Satz muss nochmal überarbeitet werden. Das Ziel / Ergebnis der Arbeit hat sich 
+    inzwischen geändert} \\
+  \anmerkungstext{Wir haben mehr einen Algorithmus getestet und an unserem spezifischen Problem angewendet, 
+    als viel selbst zu entwickeln. Allerdings haben wir den Fitch Algorithmus von binär auf multinär 
+    umgeschrieben.} \\
+
   Researchers of the phylogenies have been dealt with the ancenstral state reconstruction in the 
@@
   This tree is not binary and therefore the developed algorithms are not directly applicable. \\
+  \anmerkung{GloBI und OTL in der Einleitung vorstellen. (Emanuel)}
   In this work, we have looked at the algorithms that are generally suited to our data, to develop 
@@
 \chapter{Methods}
+  \anmerkung{Graphischen Workflow hinzufügen, mehr Motivation und genauer. (Bernhard)}
 
@@
 
-    There are some Parameters to find out or notice:
+    There are some Parameters to find out or notice: \\
+    \anmerkungstext{hier unterscheiden zwischen einfachen Zahlen (countings / one dimensional) und 
+      komplexen variablen (Emanuel)} \\
+    \anmerkungstext{arg}{außerdem zu unterscheiden: Biologische Parameter (transition probabilities), 
+      fixe Daten und zu berechnende (multifurcation,...) (Emanuel)}
     \begin{itemize}
@@
     \end{itemize}
+    \anmerkung{multifurcations und unknown leave nodes sind ähnlich beeinflusst (Emanuel)} \\
+    \todo{Hier darauf hinweisen, dass wir für multifurcations und unknown data den einfluss auf die 
+      Algorithmen testen.}
 
@@
           interactions & 5346414 \\ \hline
-          freeliving species & 48875 (distinct) \\ \hline
-          parasite species &  64125 (distinct) \\ \hline
-          unused possible species & 2126 (source), 2144439 (target) \\
-          % number of freelivings: 509595
-          % number of freelivings: 45881 (distinct)
-          % number of parasites: 3438001
-          % number of parasites: 63532 (distinct)
-          % number of SAME_AS: 16012
-          % number of SAME_AS: 5667 (distinct)
+          freeliving species & 51337 (distinct) \\ \hline
+          parasite species &  47332 (distinct) \\ \hline
+          unused possible species & 57352 (source), 809993 (target) \\
+          % number of freelivings: 489179
+          % number of freelivings: 42657 (distinct)
+          % number of parasites: 3353580
+          % number of parasites: 44260 (distinct)
+          % number of SAME_AS: 86198
+          % number of SAME_AS: 16710 (distinct)
           \hline  
@@
     \subsection{Multifurcation}
+      \anmerkung{Description/Definition of Multifurcation -> to the Intro (Bernhard)} \\
+      \anmerkung{Regressionsanalyse (Bernhard)} \\
+      \anmerkung{poisson glm: \#children \~ ~ I phylum -> R fitdist p (Emanuel)} \\
+      \anmerkung{different parameters for different taxa? (Emanuel)} \\
       One property of the tree is its ridge of multifurcation. For this we collected for every node its
@@
         to know how the multifurcations behave in some interesting subtrees. \\
+      \anmerkung{do we? Is that really universal knowledge or could it be supported by data or a citation? (Bernhard)} \\
       \todo{subtrees... there is some old stuff...} \\
@@
   \section{Simulation}
+    \anmerkung{Motivate the goal of the simulation (Bernhard)}
     \begin{itemize}
@@
     \subsection{random binary tree}
+      \anmerkung{Again, motivate first, why this is required and why you choose this solution (Bernhard)} \\
       To get a random binary tree, I used the Phylo package from biopython. They offer a randomized
@@
       From the BaseTree class:
+      \anmerkung{trivial, does not give real info (Emanuel)}
       \begin{lstlisting}
@@
     \subsection{tag tree}
+      \anmerkung{instead of 'tag tee' simulating stages and transitions between them (Emanuel)} \\
       At this point we want one fully tagged tree, and one less tagged tree which looks like our real 
@@
         reflects our transition probabilities best (see Figure 2.1 \todo{ref einfügen}). \\
+      \anmerkung{why is that the case and why is that from a biological perspective? (Bernhard)} \\
+      \anmerkungstext{I'd rather say that to ensure that the parameter of the binomial distribution is 
+        restricted to the [0,1] interval, we model it... (Bernhard)} \\
       For example when our father node was free-living, then we take from the free-living beta
@@
       \end{figure}
-      \todo{Bessere Beschriftung, Plot neu erstellen! U.a. mit threshold}
-      We save each tag with the associated node ID in a nodelist, where we can save all information
-        about our nodes, we want. \\
+      \todo{Bessere Beschriftung, Plot neu erstellen! U.a. mit threshold} \\
+      We save each tag with the associated node ID in a nodelist. \\
+      \anmerkung{simulationg loss of information (1) states (2) topology/multifurcation (Emanuel)} \\
       The real tree has much less information, we have only information from some current species 
@@
       got from our real tree. Or which we can change to \todo{...}
-      \TODO{Was hiervon gehört ind Methoden, was schon in Implementierung oder ganz woanders hin?}
+      \todo{Was hiervon gehört ind Methoden, was schon in Implementierung oder ganz woanders hin?}
 
@@
     \subsection{multifurcate tree}
+      \anmerkung{simulating loss of information (Emanuel)} \\
       Another parameter is the nature and strength of the multifunction of the tree, since we do not 
         have a binary tree in the real case. After several measurements and analyzes, which we explain 
-        in \todo{section/chapter x}, we decided to use a $1 over x$ distribution, where x is the depth 
+        in \todo{section/chapter x}, \anmerkung{fit, justification (Emanuel)} we decided to use a $\frac{1}{x}$ distribution, where x is the depth 
         of a node. This means, how deaper we are, how less information we have. \\
       We traverse through the tree and pick a random number between 0 and 1. If random number is smaller 
-        as our limit ($1 over x$), than we forget the node and hang every child to the father node of 
-        the current node.
-      \todo{then / than}
+        as our limit ($\frac{1}{x}$), than we forget the node and hang every child to the father node of 
+        the current node. \\
+      \anmerkung{poisson process -> fit that distribution, include depth as a predictor, see if significant (Emanuel)}
       \begin{lstlisting}

### 2018-02-04 metadata/build_nodelists.py
add indizes of nodelist to trees

@@ -68,7 +68,7 @@ def main():
         print(colored(nr_used_freelivings, 'blue'), "freeliving tags were used,", colored(nr_used_parasites, 'blue'), "parasite tags were used =>", colored(unknown, 'blue'), "unknown leave nodes")
         print(colored(internal_freeliving, 'blue'), "internal freeliving tags found and", colored(internal_parasite, 'blue'), "internal parasite tags found")
         print("Rootnode, Depths: [Min, Max, Mean], Originaltag, Finaltag, Nr_children")
-        print(nodelist[-1])
+        print(nodelist[0])
         # ---- reset countings ----
         nr_leave_nodes = 0
         nr_used_freelivings = 0

### 2018-02-04 metadata/build_subtrees.py

@@ -1,3 +1,5 @@
+from copy import deepcopy
+
 from Bio import Phylo
 from termcolor import colored
 
@@ -6,6 +8,9 @@ subtree_otts = [['ott304358', 'Eukaryota'], ['ott352914', 'Fungi'], ['ott691846'
         ['ott395057', 'Nematoda'], ['ott801601', 'Vertebrata'], ['ott229562', 'Tetrapoda'], 
         ['ott244265', 'Mammalia'], ['ott913935', 'Primates'], ['ott770311', 'Hominidae'], 
         ['ott361838', 'Chloroplastida']]
+index = 0
+nr_internal_nodes = 0
+nr_leaf_nodes = 0
 
 def main():
     path_tree = "../data/opentree9.1_tree/labelled_supertree/labelled_supertree.tre"
@@ -19,18 +24,41 @@ def main():
 
 def find_subtree(subtree):
     global subtree_otts
+    global index
+    global nr_internal_nodes
+    global nr_leaf_nodes
     if len(subtree_otts) == 0:
         return
     if not subtree.is_terminal():
         for item in subtree_otts:
             if subtree.name == item[0]:
+                new_subtree = deepcopy(subtree)
+                new_subtree = prepare_subtree(new_subtree)
+                index = 0
                 subtree_path = '../data/subtree/' + item[1] + '.tre'
                 print("save tree at", subtree_path)
-                Phylo.write(subtree, subtree_path, 'newick')
+                Phylo.write(new_subtree, subtree_path, 'newick')
+                print(item[1], 'has', nr_internal_nodes, 'internal nodes and', nr_leaf_nodes, 'leaf_nodes')
+                nr_internal_nodes = 0
+                nr_leaf_nodes = 0
                 subtree_otts.remove(item)
-                print(subtree_otts)
         for clade in subtree.clades:
             find_subtree(clade)
     return
+
+def prepare_subtree(subtree):
+    global index
+    global nr_internal_nodes
+    global nr_leaf_nodes
+    # For the quicker finding of the element in the nodelist of the accociated node.
+    subtree.name = subtree.name + "$" + str(index)
+    index += 1
+    if subtree.is_terminal():
+        nr_leaf_nodes += 1
+    else:
+        nr_internal_nodes += 1
+        for clade in subtree.clades:
+            clade = prepare_subtree(clade)
+    return subtree
     
 main()

### 2018-02-04 metadata/run_castor.py
add maximum parsimony sankoff (castor)

@@ -1,0 +1,118 @@
+"""Maximum parsimony algorithm from Sankoff implemented in the R package castor"""
+
+import ast
+import csv
+import datetime
+from time import gmtime, strftime
+
+import rpy2.robjects
+from Bio import Phylo
+from termcolor import colored
+
+from Helpers import find_element_in_nodelist, print_time
+
+# global variables:
+START_TIME = datetime.datetime.now().replace(microsecond=0)
+CURRENT_TIME = datetime.datetime.now().replace(microsecond=0)
+r_path = "../simulation/utilities/castor_parsimony_simulation.R"
+
+subtree_names = ['Eukaryota', 'Metazoa', 'Chloroplastida', 'Fungi']
+
+print(colored("------------------------ Sankoff Maximum Parsimony ------------------------", "green"))
+
+def main():
+    global START_TIME
+    global CURRENT_TIME
+
+    for subtree_name in reversed(subtree_names):
+        print('Run castor - Sankoff parsimony - for', subtree_name)
+        print(colored("---------------- read tree ----------------", "green"))
+        subtree_path = '../data/subtree/' + subtree_name + '.tre'
+        tree = Phylo.read(subtree_path, 'newick')
+        CURRENT_TIME = print_time(CURRENT_TIME)
+        print(colored("---------------- read nodelist ----------------", "green"))
+        nodelist_path = '../data/nodelist/' + subtree_name + '.csv' 
+        nodelist = []
+        #              0    1       2           3           4
+        # nodelist - [id, depths, nr_children, originaltag, finaltag]
+        with open(nodelist_path, 'r') as csv_file:
+            reader = csv.reader(csv_file, delimiter=',')
+            for row in reader:
+                if row != []:
+                    ott = row[0]
+                    depths = ast.literal_eval(row[1])
+                    nr_children = int(row[2])
+                    originaltag = row[3]
+                    finaltag = row[4]
+                    nodelist.append([ott, depths, nr_children, originaltag, finaltag])
+        CURRENT_TIME = print_time(CURRENT_TIME)
+        print(colored("---------------- Sankoff parsimony ----------------", "green"))
+        sankoff_parsimony(tree, nodelist)
+        CURRENT_TIME = print_time(CURRENT_TIME)
+        print(colored("--------------------------------", "green"))
+    print(colored("--------------------------------", "green"))
+    return
+
[…]

### 2018-02-04 metadata/build_metadata.sh
add a shell script for the workflow

@@ -1,17 +1,42 @@
 
+# -------- -------- Prepare logfile and runtime computation -------- -------- #
+echo "Logifle written to: build_data.log"
+exec 3>&1 1>>build_data.log 2>&1            #write stdout 1,2 to logfile 3 to console
+echo $(date)
+start=$(date +%s)                           #get starting date
+# -------- -------- install node packages -------- -------- #
+# ToDo!
+echo "$(tput setaf 1)$(tput setab 7)------- packages installed (1/7) --------$(tput sgr 0)" 1>&3
 # -------- -------- cleanup and build filesystem -------- -------- #
 rm -rf data                                 #delete preexisting data dir
 mkdir data                                  #make data dir
 cd data
-
 # -------- -------- get data and unzip -------- -------- #
+if wget -q http://files.opentreeoflife.org/synthesis/opentree9.1/opentree9.1_tree.tgz -nv; then echo "OTT DL succesful"; else echo "OTT DL-link broken" 1>&3; exit 1;  fi    # download OTT and post error msg if link is unreachable
+tar -xf opentree9.1_tree.tgz                #untar OTT
+rm opentree9.1_tree.tgz                     #remove .tar
+wait
 mkdir GLoBI_Dump
 cd GLoBI_Dump
-
 if wget -q https://depot.globalbioticinteractions.org/datasets/org/globalbioticinteractions/interactions/0.1/interactions-0.1-ott.zip -nv; then echo "GLoBI DL succesful"; else echo "GLoBI DL-link broken" 1>&3; exit 1;  fi
 unzip interactions-0.1-ott.zip
 gunzip interactions.tsv.gz
-
+echo "$(tput setaf 1)$(tput setab 7)------- Tree and Interaction-data downloaded (2/7) --------$(tput sgr 0)" 1>&3
 # -------- -------- build metadata files -------- -------- #
 cd ../../metadata
 extract_globi_data.py > log-extract_globi_data.txt
+echo "$(tput setaf 1)$(tput setab 7)------- Free-livings and Parasites extracted (3/7) --------$(tput sgr 0)" 1>&3
+python3 build_subtrees.py > log-build_subtrees.txt
+echo "$(tput setaf 1)$(tput setab 7)------- Subtrees builded(4/7) --------$(tput sgr 0)" 1>&3
+python3 build_nodelist.py > log-build_nodelist.txt
[…]

### 2018-02-04 metadata/run_castor.py

@@ -24,7 +24,7 @@ def main():
     global START_TIME
     global CURRENT_TIME
 
-    for subtree_name in reversed(subtree_names):
+    for subtree_name in subtree_names:
         print('Run castor - Sankoff parsimony - for', subtree_name)
         print(colored("---------------- read tree ----------------", "green"))
         subtree_path = '../data/subtree/' + subtree_name + '.tre'

### 2018-02-05 Paper - Latex/Paper - Skizze - v2.tex
Methods - add Workflow, Countings

@@
   \anmerkung{Graphischen Workflow hinzufügen, mehr Motivation und genauer. (Bernhard)}
+  \begin{figure}[h!]
+    \caption{Workflow}
+    \centering
+    \label{fig:Workflow}
+    \includegraphics[width=1\textwidth]{Figures/Workflow.png}
+  \end{figure}
 
@@
           parasite species &  47332 (distinct) \\ \hline
-          unused possible species & 57352 (source), 809993 (target) \\
+          unused possible species & 57352 (source), 809993 (target) \\ \hline
           % number of freelivings: 489179
@@
           % number of SAME_AS: 16710 (distinct)
+          Eukaryota & 241974 internal nodes, 2293463 leaf nodes \\
+          Chloroplastida has 43486 internal nodes and 412434 leaf_nodes
+          % Metazoa has 179944 internal nodes and 1491012 leaf_nodes
+          % Nematoda has 3437 internal nodes and 30127 leaf_nodes
+          % Vertebrata has 30466 internal nodes and 88415 leaf_nodes
+          % Tetrapoda has 21870 internal nodes and 47540 leaf_nodes
+          % Mammalia has 4727 internal nodes and 8615 leaf_nodes
+          % Primates has 492 internal nodes and 686 leaf_nodes
+          % Hominidae has 12 internal nodes and 14 leaf_nodes
+          % Fungi has 9534 internal nodes and 314571 leaf_nodes
           \hline  
@@
       \end{center}
+      $\frac{100}{2293463 * (51337 + 47332)} \approx 4.3$ -> only 4.3\% of leaf nodes are filled with information
 

### 2018-02-05 Paper - Latex/Paper - Skizze - v2.tex
Paper - Introduction

@@
 \chapter*{Abstract}
+  \anmerkungstext{Alle Figures richtig beschriften. Generell: Alle Figure captions sollten 
+    selbsterklärend sein. Sprich, ich sollte nur die Caption (normalerweise auch unter dem Bild) 
+    lesen und nicht den Rest das Papers und dann trotzdem verstehen können, was eigentlich passiert 
+    ist und - hilfreich - auch warum das relevant ist. (Bernhard)} \\
 
@@
 \chapter{Introduction}
-  \anmerkungstext{Alle Figures richtig beschriften. Generell: Alle Figure captions sollten selbsterklärend sein. Sprich, ich sollte 
-    nur die Caption (normalerweise auch unter dem Bild) lesen und nicht den Rest das Papers und dann 
-    trotzdem verstehen können, was eigentlich passiert ist und - hilfreich - auch warum das relevant 
-    ist. (Bernhard)} \\ \\
-
-  \anmerkung{allgemein zu diesem Kapitel:} \\
-  \anmerkung{Eine Einleitung hat etwa 2 Seiten. General problem -> more specific problem (Emanuel)}
-  \anmerkungstext{Die Intro ist noch arg knapp =) und ich erkenne die Struktur noch nicht ganz.
-    Mein Vorschlag einer Gliederung (jeweils ca. ein Absatz)1) Motivation: \\
-      * Was ist das große Ziel? Was soll erreicht werden \\
-      * Warum ist das relevant? Was könnte man dann tun? \\
-    2) Hintergrund \\
-      * Was gab es in dieser Richtung bereits als ganze Ansätze oder wenn nicht, warum nicht? Woran 
-        ist es bisher gescheitert  \\
-      * welche Grundlagen sind notwendig: \\
-      ** open tree of life: Was ist das, warum relevant und überlegen als reine Ansätze? \\
-      ** Algorithmen: Was gibt es? Ruhig ausführlicher als hier bereits und vor allem auch nach einer 
-        Darstellung am Ende ableiten, was für uns relevant ist. Also beschreiben, wie Methode a, b, c 
-        funktionieren und dann abwägen, was daher für Dich am relevantesten ist. \\
-    3) Outlook/Structure of this work (Bernhard)} \\
-
   This paper is about the further development of parsimony algorithms for non-binary trees, applied 
@@
 
+  \anmerkung{Mein Vorschlag einer Gliederung (jeweils ca. ein Absatz) (Bernhard)}
+  \begin{enumerate}
+    \item Motivation:
+      \begin{itemize}
+        \item Was ist das große Ziel? \\
+          Das Ziel dieser Arbeit ist die Anwendung von maximum parsiomony algorithmen auf nicht 
+          binäre Bäume und auf sehr große Datensätze. Insbesondere auf das Beispiel 'Entstehung des 
+          Parasitismus' im ganzen Eukaryotischen Tree of Life.
+        \item Was soll erreicht werden? \\
+          Wir wollen vorhandene Algorithm (Sankoff/castor) auf diese Aufgabenstellung hin testen 
+          und ihre Vorhersagekraft abschätzen. Außerdem wollen wir den Fitch algorithmus für binäre 
+          Bäume auf unser Problem erweitern und mit dem Sankoff Algorithmus vergleichen.
+        \item Warum ist das relevant? Was könnte man dann tun?\\
+          \todo{!!!}
+      \end{itemize}
+    \item Hintergrund:
+      \begin{itemize}
+        \item Was gab es in dieser Richtung bereits als ganze Ansätze oder wenn nicht, warum nicht?
+          Woran ist es bisher gescheitert? \\
+          Bisher wurden vorallem Algorithmen für das binäre Problem entwickelt, da man wesentlich 
+            kleinere Teilbäume betrachtet hat, von welchen man auch alle Aufspaltungen kennt. Durch 
+            die Entwicklung von OTL, eines gesamten Baum des Lebens, ergibt sich das Problem, dass 
+            dieser bei weitem nicht binär ist. \\ \\
   Researchers of the phylogenies have been dealt with the ancenstral state reconstruction in the 
@@
     that exists at this moment, which goes over all observed species. For most \todo{most?} species 
-  there is no 
-  phylogeny, but only a taxonomic classification. So the biggest 'phylogenetic tree' is a synthesis 
+    there is no phylogeny, but only a taxonomic classification.
+
+        \item Welche Grundlagen sind notwendig:
+          \begin{itemize}
+            \item open tree of life: Was ist das, warum relevant und überlegen als reine Ansätze? \\
+              \todo{!!!} \\ \\
+  So the biggest 'phylogenetic tree' is a synthesis 
     of phylogenetic trees filled with a taxonomic tree given by Open Tree of Life \cite{Hinchliff2015}.
     This tree is not binary and therefore the developed algorithms are not directly applicable. \\
+            \item Algorithmen: Was gibt es? Ruhig ausführlicher als hier bereits und vor allem auch 
+              nach einer Darstellung am Ende ableiten, was für uns relevant ist. Also beschreiben, 
+              wie Methode a, b, c funktionieren und dann abwägen, was daher für Dich am 
+              relevantesten ist. \\
+              \todo{!!!} \\
               \anmerkung{GloBI und OTL in der Einleitung vorstellen. (Emanuel)}
+          \end{itemize}
+      \end{itemize}
+    \item Outlook/Structure of this work
+  \end{enumerate}
+
   In this work, we have looked at the algorithms that are generally suited to our data, to develop 
@@
       \begin{center}
-        \begin{tabular}{ | l | p{3cm} | }
+        \begin{tabular}{ | l | p{3.9cm} | }
           \hline
@@
           Eukaryota & 241974 internal nodes, 2293463 leaf nodes \\
-          Chloroplastida has 43486 internal nodes and 412434 leaf_nodes
+          % Chloroplastida has 43486 internal nodes and 412434 leaf_nodes
           % Metazoa has 179944 internal nodes and 1491012 leaf_nodes

### 2018-02-06 metadata/edit_species_lists.py
update castor

@@ -133,7 +133,6 @@ def get_tag(name, species_list):
     for item in species_list:
         # mrcaott_item = 'mrca' + item + 'ott'
         if item == name or name.endswith(item): # or name.startswith(mrcaott_item):
-            print(item, '==', name)
             species_list.remove(item)
             return [True, species_list]
         if not (name.startswith('mrca') or name.startswith('ott')):

### 2018-02-06 metadata/run_castor.py

@@ -15,14 +15,17 @@ from Helpers import find_element_in_nodelist, print_time
 START_TIME = datetime.datetime.now().replace(microsecond=0)
 CURRENT_TIME = datetime.datetime.now().replace(microsecond=0)
 r_path = "../simulation/utilities/castor_parsimony_simulation.R"
+nodelist = []
 
-subtree_names = ['Eukaryota', 'Metazoa', 'Chloroplastida', 'Fungi']
+subtree_names = ['Eukaryota', 'Metazoa', 'Chloroplastida', 'Fungi', 'Vertebrata', 'Tetrapoda', 
+        'Nematoda', 'Mammalia', 'Primates', 'Hominidae']
 
 print(colored("------------------------ Sankoff Maximum Parsimony ------------------------", "green"))
 
 def main():
     global START_TIME
     global CURRENT_TIME
+    global nodelist
 
     for subtree_name in subtree_names:
         print('Run castor - Sankoff parsimony - for', subtree_name)
@@ -32,7 +35,6 @@ def main():
         CURRENT_TIME = print_time(CURRENT_TIME)
         print(colored("---------------- read nodelist ----------------", "green"))
         nodelist_path = '../data/nodelist/' + subtree_name + '.csv' 
-        nodelist = []
         #              0    1       2           3           4
         # nodelist - [id, depths, nr_children, originaltag, finaltag]
         with open(nodelist_path, 'r') as csv_file:
@@ -47,24 +49,31 @@ def main():
                     nodelist.append([ott, depths, nr_children, originaltag, finaltag])
         CURRENT_TIME = print_time(CURRENT_TIME)
         print(colored("---------------- Sankoff parsimony ----------------", "green"))
-        sankoff_parsimony(tree, nodelist)
+        sankoff_parsimony(tree)
+        CURRENT_TIME = print_time(CURRENT_TIME)
+        print(colored("---------------- Save nodelist ----------------", "green"))
+        nodelist_path = '../data/nodelist/' + subtree_name + '-castor.csv' 
+        with open(nodelist_path, 'w') as nodelist_file:
+            writer = csv.writer(nodelist_file, quoting=csv.QUOTE_ALL)
+            writer.writerow(nodelist)
         CURRENT_TIME = print_time(CURRENT_TIME)
         print(colored("--------------------------------", "green"))
     print(colored("--------------------------------", "green"))
     return
 
[…]

### 2018-02-06 Paper - Latex/Paper - Skizze - v2.tex
Paper - Introduction

@@
     \item Run the resulted algorithm on the original data.
-    \item Evalute and interprete results. -> Origins etc...
+    \item Evalute and interprete results. $\rightarrow$ Origins etc...
   \end{enumerate}
@@
         to these. \\
-      \todo{klar? Oder Beispiel bringen? (Katze isst Maus -> Katze ist Freilebend)} \\
+      \todo{klar? Oder Beispiel bringen? (Katze isst Maus $\rightarrow$ Katze ist Freilebend)} \\
       % For every interaction from these lists, we get one or two species for our parasite or 
@@
   \section{Metadata analysis}
-    Properties of real Data - Metadata analysis
+    Properties of real Data - Metadata analysis \\
 
-    There are some Parameters to find out or notice: \\
-    \anmerkungstext{hier unterscheiden zwischen einfachen Zahlen (countings / one dimensional) und 
-      komplexen variablen (Emanuel)} \\
-    \anmerkungstext{arg}{außerdem zu unterscheiden: Biologische Parameter (transition probabilities), 
-      fixe Daten und zu berechnende (multifurcation,...) (Emanuel)}
+    Um eine möglichst realistische Simulation zu erzeugen haben wir auf der einen Seite einige Daten 
+      gesammelt (Kaptiel Countings), und außerdem beeinflussende Parameter untersucht.
+
+    Wir haben zwei große Arten von Parametern:
+    \begin{enumerate}
+      \item Biological parameters (A result of the evolutionary process.):
         \begin{itemize}
-      \item transition probabilities of tags
-      \item multifurcation
-      \item nr of parasites to free-living
-      \item nr of unknown nodes 
+          \item transition probabilities
         \end{itemize}
-    \anmerkung{multifurcations und unknown leave nodes sind ähnlich beeinflusst (Emanuel)} \\
+      \item Distribution of the loss of information:
+        \begin{itemize}
+          \item Loss of topology ($\rightarrow$ mutlifurcations).
+          \item Unknown information about the states of some leaf nodes.
+        \end{itemize}
+    \end{enumerate}
+
     \todo{Hier darauf hinweisen, dass wir für multifurcations und unknown data den einfluss auf die 
@@
     \subsection{Countings}
-      Some simple countings...\\
-      nr of parasites, free-living and unknown nodes ... from whole tree, subtrees...
       \begin{center}
@@
           \hline \hline
-          interactions & 5346414 \\ \hline
-          freeliving species & 51337 (distinct) \\ \hline
-          parasite species &  47332 (distinct) \\ \hline
-          unused possible species & 57352 (source), 809993 (target) \\ \hline
-          % number of freelivings: 489179
-          % number of freelivings: 42657 (distinct)
-          % number of parasites: 3353580
-          % number of parasites: 44260 (distinct)
-          % number of SAME_AS: 86198
-          % number of SAME_AS: 16710 (distinct)
           Eukaryota & 241974 internal nodes, 2293463 leaf nodes \\
@@
           % Fungi has 9534 internal nodes and 314571 leaf_nodes
+          interactions & 5346414 \\ \hline
+          freeliving species & 51337 (distinct) \\ \hline
+          parasite species &  47332 (distinct) \\ \hline
+          $\rightarrow$ unknown nodes & ??? \\ \hline
+          unused possible species & 57352 (source), 809993 (target) \\ \hline
+          % number of freelivings: 489179
+          % number of freelivings: 42657 (distinct)
+          % number of parasites: 3353580
+          % number of parasites: 44260 (distinct)
+          % number of SAME_AS: 86198
+          % number of SAME_AS: 16710 (distinct)
           \hline  
@@
       \end{center}
-      $\frac{100}{2293463 * (51337 + 47332)} \approx 4.3$ -> only 4.3\% of leaf nodes are filled with information
+      \todo{tree, subtrees? figure dazu?}
+      $\frac{100}{2293463 * (51337 + 47332)} \approx 4.3$ $\rightarrow$ only 4.3\% of leaf nodes are filled with information
+
+      #interactions zu #Parasiten und #Freilebend -> Wieviel gibt GloBI her? (dazu noch #unused possible species, wieviele Parasiten ohne ott haben wir gefunden?)
+      #Parasiten und #Freilebend und #Blattknoten -> Wieviele unbekannte Knoten haben wir?
+      #Interne Knoten und #Blattknoten -> Wie stark ist die Multifurkation?
+
+    %---------------------------------------------------------------------------------------------------
+    \subsection{Transition probabilities}
+      \anmerkungtext{Wir hätten aber maximal 2 beta-Verteilungen mit jeweils 2 Parametern und je einem 
+        eigenen Schwellenwert bei dem in die andere Verteilung gewechselt wird. Also 6 Parameter. Ich 
+        finde den Parameterraum den du bisher betrachtest zum einen nicht systematisch erfasst, zum 
+        anderen wahrscheinlich auch zu klein. Du kannst "Parameter sparen" indem zu z.B die beiden 
+        Verteilungen und cut-offs symmetrisch (gespiegelt an 0.5) machst. Solltest aber meines Erachtens 
+        die Schwellenwerte freier variieren. Das können wir bis zu unserem nächsten Treffen zurückstellen 
+        und dann gemeinsam diskutieren. (Emanuel)} \\
+      Das mit dem symmetrisch spiegeln geht halt nur bei maximal 40-60 Verteilungen richtig gut, danach 
+        haben brauchen eventuell eine lange Austestphase, bis ein Baum dieser Verteilung entspricht.
+      Wenn wir allerdings dafür zwei verschiedene Schwellenwerte einführen könnte das dieses Problem 
+        eventuell ausgleichen. Das müsste ich austesten.
+
+      \todo{Kapitel tag tree hier einbinden}
 
@@
     \subsection{Multifurcation}
-      \anmerkung{Description/Definition of Multifurcation -> to the Intro (Bernhard)} \\
+      \anmerkung{Description/Definition of Multifurcation $\rightarrow$ to the Intro (Bernhard)} \\
       \anmerkung{Regressionsanalyse (Bernhard)} \\
-      \anmerkung{poisson glm: \#children \~ ~ I phylum -> R fitdist p (Emanuel)} \\
+      \anmerkung{poisson glm: \#children \~ ~ I phylum $\rightarrow$ R fitdist p (Emanuel)} \\
       \anmerkung{different parameters for different taxa? (Emanuel)} \\
@@
           new_random = random.beta(a=A_P, b=B_P)
-        tag = 0         # -> FL
+        tag = 0         # $\rightarrow$ FL
         if new_random < percentage_parasites:
-          tag = 1       # -> P
+          tag = 1       # $\rightarrow$ P
       \end{lstlisting}
@@
         the current node. \\
-      \anmerkung{poisson process -> fit that distribution, include depth as a predictor, see if significant (Emanuel)}
+      \anmerkung{poisson process $\rightarrow$ fit that distribution, include depth as a predictor, see if significant (Emanuel)}
       \begin{lstlisting}
@@
     \item Wie ist die Verteilung der vergessenen internen Knoten? Zum Wurzelknoten hin mehr vergessen?
-    \item Wie sehen die übergangswahrscheinlichkeiten aus von P->FL und andersherum?
+    \item Wie sehen die übergangswahrscheinlichkeiten aus von P$\rightarrow$FL und andersherum?
     \item Verteilung Parasiten zu Freilebend zu keine Information

### 2018-02-09 Paper - Latex/Paper - Skizze - v2.tex
Paper - Methods - Workflow

@@
 \chapter{Methods}
-  \anmerkung{Graphischen Workflow hinzufügen, mehr Motivation und genauer. (Bernhard)}
+  We would like to apply a maximum parsimony algorithm to the entire tree of life to obtain an 
+    ancestral state reconstruction of free-living vs. parasite. On one side we need a simulation to
+    find out, which is the best algorithm with which parameters. And on the other side we run the 
+    selected Algorithm and evaluate the results.\\
   \begin{figure}[h!]
@@
     \label{fig:Workflow}
-    \includegraphics[width=1\textwidth]{Figures/Workflow.png}
+    \includegraphics[width=0.4\textwidth]{Figures/Workflow-overview.png}
   \end{figure}
-
-  This work consist of two aspects. One is the application of the algorithm to our question the
-    other a simulation of this to proof the credibility of our methods. \\
-  The resulting procedure is as follows:
+  For this we have to look at the following different aspects:
   \begin{enumerate}
-    \item Get the real tree and real data for the leaf nodes.
+    \item Get the real tree and real data for the leaf nodes. $\rightarrow$ OTL, GloBI
     \item Get metadata of these for a realisitc the simulation.
@@
 
+  This work consist of two aspects. One is the application of the algorithm to our question the
+    other a simulation of this to proof the credibility of our methods. \\
+  The resulting procedure is as follows:
+
   % Zur Bewertung der gefundenen / entwickelten algorithmen haben wir eine Simulation ausgeführt.
@@
   % diese angewendet.
+
+  \begin{figure}[h!]
+    \caption{Workflow}
+    \centering
+    \label{fig:Workflow}
+    \includegraphics[width=1\textwidth]{Figures/Workflow.png}
+  \end{figure}
 

### 2018-02-11 Paper - Latex/Paper - Skizze - v2.tex
Paper - Methods - Introduction / Motivation

--- 2018-02-06 Paper - Latex/Paper - Skizze - v2.tex
@@
 \chapter{Methods}
-  \anmerkung{Graphischen Workflow hinzufügen, mehr Motivation und genauer. (Bernhard)}
+  As initiated, we would like to apply a maximum parsimony algorithm to the entire tree of life to 
+    obtain an ancestral state reconstruction of free-living versus parasite states. \\
+  So far, these reconstructions have been made mainly on binary trees with better data availability. 
+    Therefore, we decided to use a simulation to decide how to evaluate the existing algorithms and 
+    possibly adapt them to our given problem. \\
+  Accordingly, in addition to the necessary data sets (GloBI, OTL), the chosen algorithm and the 
+    evaluation of its results, this chapter also deals with the previously performed simulation and 
+    the evaluation of the various algorithms and their parameters. \\
+  Figure \ref{fig:workflow} briefly outlines these relationships.
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.4\textwidth]{Figures/Workflow-overview.png}
+    \caption{Workflow \\
+      The coming sections are thus subdivided into the following topics: \\
+      \todo{or:} The resulting procedure is as follows: \\
+      (1) Get the real tree and real data for the leaf nodes $\rightarrow$ OTL, GloBI databases.
+      (2) Get metadata of these for a realisitc the simulation.
+      (3) Build and run the simulation.
+      (4) Evaluation of parameters for the simulation and the real problem.
+      (5) Run the resulted algorithm on the original data.
+      (6) Evalute and interprete results. $\rightarrow$ Origins etc...
+    }
+    \label{fig:workflow}
+  \end{figure} \\
+  \todo{Metadata analysis nötig für run maximum parsimony?} \\
+
+  % \begin{enumerate}
+  %   \item Get the real tree and real data for the leaf nodes. $\rightarrow$ OTL, GloBI databases
+  %   \item Get metadata of these for a realisitc the simulation.
+  %   \item Build and run the simulation.
+  %   \item Evaluation of parameters for the simulation and the real problem.
+  %   \item Run the resulted algorithm on the original data.
+  %   \item Evalute and interprete results. $\rightarrow$ Origins etc...
+  % \end{enumerate}
+
   \begin{figure}[h!]
@@
 
-  This work consist of two aspects. One is the application of the algorithm to our question the
-    other a simulation of this to proof the credibility of our methods. \\
-  The resulting procedure is as follows:
-  \begin{enumerate}
-    \item Get the real tree and real data for the leaf nodes.
-    \item Get metadata of these for a realisitc the simulation.
-    \item Build and run the simulation.
-    \item Evaluation of parameters for the simulation and the real problem.
-    \item Run the resulted algorithm on the original data.
-    \item Evalute and interprete results. $\rightarrow$ Origins etc...
-  \end{enumerate}
-
-  % Zur Bewertung der gefundenen / entwickelten algorithmen haben wir eine Simulation ausgeführt.
-
-  % Auf der Anderen Seite haben wir unser reales Problem aufgestellt, für die Algorithmen vorbereitet und 
-  % diese angewendet.
-
   %---------------------------------------------------------------------------------------------------
@@
   \section{Get data}
+  For our research we need two types of data: a tree and information about the states. \\
+  For the tree we decided to use Open Tree of Life (OTL), because it's the biggest available synthesis 
+    tree. \\
+  \todo{hier referenzen zu nem paper das das bestätigt o.ä.} \\
+  For the state information, we decided to use the Global biotic interaction database (GloBI). Also in 
+    this case, this is one of the largest databases and both OTL and GloBI support the OTT 
+    identification. OTT (open tree taxonomy) is a taxonomy that assigns to each species a unique id, 
+    both ancestor and now living species (internal and leaf nodes).
+
+    %---------------------------------------------------------------------------------------------------
+    \subsection{OTL}
+      \todo{Open Tree of Life}
+
     %---------------------------------------------------------------------------------------------------
@@
       For tagging our leave nodes, we use the GloBI (Global Biotic Interactions) database. This database 
-        consists of entries of the form: species A interacts with B. \\
+        consists of entries of the form: species A (source) interacts with B (target). \\
       We appointed some interactions, where we know from the biological perspective that the species 
       source or target has to be a parasite or a free-living species. These are the following:
-      \begin{lstlisting}
-        freeliving_source = ["parasiteOf", "pathogenOf"]
-        freeliving_target = ["hasParasite", "hasPathogen"]
-        parasite_source = ["preysOn", "eats", "flowersVisitedBy", "hasPathogen", "pollinatedBy", "hasParasite", "hostOf"]
-        parasite_target = ["preyedUponBy", "parasiteOf", "visitsFlowersOf", "pathogenOf", "hasHost"]
-      \end{lstlisting}
+      \begin{itemize}
+        \item free-living source: preysOn, eats, flowersVisitedBy, hasPathogen, pollinatedBy, 
+          hasParasite, hostOf
+        \item free-living target: preyedUponBy, parasiteOf, visitsFlowersOf, pathogenOf, hasHost
+        \item parasite source: parasiteOf, pathogenOf
+        \item parasite target: hasParasite, hasPathogen
+      \end{itemize}
+      \todo{Interactions nochmal prüfen! Darauf basieren unsere Ergebnisse!} \\
       We build two lists: parasites and free-livings, and add the source or targets of an interaction
@@
       %   free-living lists.
-      \todo{ott id hier erwähnen?} \\
       \todo{einige spezies nicht mit einbezogen, da sie keine OTT id haben, hier könnte man noch verbessern (future work)}
-      \todo{You can find all interaction types here: https://github.com/jhpoelen/eol-globi-data/blob/master/eol-globi-lib/src/main/java/org/eol/globi/domain/InteractType.java .}
-
-    %---------------------------------------------------------------------------------------------------
-    \subsection{OTL}
-      \todo{Open Tree of Life}
+      \todo{You can find all interaction types here:
+        https://github.com/jhpoelen/eol-globi-data/blob/master/eol-globi-lib/src/main/java/org/eol/globi/domain/InteractType.java .}
 

### 2018-02-16 Paper - Latex/Paper - Skizze - v2.tex
Paper - Methods - Taxa things...; - Apendices - two tables added

@@
       \begin{center}
-        \begin{tabular}{ | l | p{3.9cm} | }
+        \begin{tabular}{ | l | l | }
           \hline
@@
           \hline \hline
-          Eukaryota & 241974 internal nodes, 2293463 leaf nodes \\
+          Eukaryota & 241 974 internal nodes, \\
+          & 2 293 463 leaf nodes \\ \hline
           % Chloroplastida has 43486 internal nodes and 412434 leaf_nodes
@@
           % Fungi has 9534 internal nodes and 314571 leaf_nodes
-          interactions & 5346414 \\ \hline
-          freeliving species & 51337 (distinct) \\ \hline
-          parasite species &  47332 (distinct) \\ \hline
+          interactions & 5 346 414 \\ \hline
+          freeliving species & 51 337 (distinct) \\ \hline
+          parasite species &  47 332 (distinct) \\ \hline
           $\rightarrow$ unknown nodes & ??? \\ \hline
-          unused possible species & 57352 (source), 809993 (target) \\ \hline
+          unused possible species & 57 352 (source), \\
+          & 809 993 (target) \\
           % number of freelivings: 489179
@@
           \hline
+          Nr of Children $== 1$ & 55 700 \\
+          & 51 744 (height $=2$) \\
+          & 3 956 (height $>2$) \\ \hline
         \end{tabular}
@@
       \todo{tree, subtrees? figure dazu?}
-      $\frac{100}{2293463 * (51337 + 47332)} \approx 4.3$ $\rightarrow$ only 4.3\% of leaf nodes are filled with information
+      $\frac{100}{2293463 * (51337 + 47332)} \approx 4.3$ $\rightarrow$ only 4.3\% of leaf nodes are 
+        filled with information
 
-      #interactions zu #Parasiten und #Freilebend -> Wieviel gibt GloBI her? (dazu noch #unused possible species, wieviele Parasiten ohne ott haben wir gefunden?)
-      #Parasiten und #Freilebend und #Blattknoten -> Wieviele unbekannte Knoten haben wir?
-      #Interne Knoten und #Blattknoten -> Wie stark ist die Multifurkation?
+      \#interactions zu \#Parasiten und \#Freilebend $\rightarrow$ Wieviel gibt GloBI her? (dazu noch 
+        \#unused possible species, wieviele Parasiten ohne ott haben wir gefunden?)
+      \#Parasiten und \#Freilebend und \#Blattknoten $\rightarrow$ Wieviele unbekannte Knoten haben wir?
+      \#Interne Knoten und \#Blattknoten $\rightarrow$ Wie stark ist die Multifurkation?
+      %---------------------------------------------------------------------------------------------------
+      \subsubsection{Data artifacts}
+        Zu der Frage, warum gibt es $nrChildren==1$. Es gibt tatsächlich 55700 Knoten mit nur einem Kind. 
+          Davon ist der großteil direkt vor einem Blatt (51744), aber 3956 ($height >2$) sind irgendwo im 
+          Baum. Ein paar Beispiele: \\
+        Nephroselmidophyceae: (class) \\
+        https://tree.opentreeoflife.org/opentree/argus/ottol@1038762 \\
+        Phrynocrinidae: (family) \\
+        https://tree.opentreeoflife.org/opentree/argus/ottol@3647979 \\
+        Elaeocarpus sylvestris: \\
+        https://tree.opentreeoflife.org/opentree/argus/opentree9.1@ott166969 \\
+        Was bedeutet das für unsere Analyse? Ignorieren wir die \~~4000 internen und Zählen sie zu den 
+          Blättern, oder zählen wir alle zu den Internen oder puzzlen wir sie einzeln raus. D.h. nur die 
+          mit der Zusatzeigenschaft ($height == 2$) sind auch Blätter. \\
+        Es könnte aber auch Fälle geben wie: ...-O-O-O-O-O, dann könnte man auch einen Knoten mit höherer 
+          Höhe als Blatt zählen. Das müsste dann gelten $min height = max height$. \\ 
+        \begin{lstlisting}
+          leaf.taxa <-  all.taxa[all.taxa$nr_children==0, ]
+          extendedLeaf.taxa <- all.taxa[all.taxa$nr_children<2 & min.height==max.height, ]
+          inner.taxa <- all.taxa[all.taxa$nr_children>1 | (all.taxa$nr_children==1 & min.height!=max.height), ]
+        \end{lstlisting}
+        \todo{macht extendedLeaf wirklich einen Sinn?}
+
+      %---------------------------------------------------------------------------------------------------
+      \subsubsection{Distribution of data in the taxa}
+        Mithilfe des taxonomischen Baums von OTL haben wir die Knoten ihren Kingdoms, Phyla und Classes 
+          zugeteilt. \\
+        Please see the appendix on page \pageref{sec:taxaTable1} for a complete table \ref{sec:taxaTable1} 
+          of these data. \\
+        \todo{gibt es einen Zusammenhang zwischen Anzahl} \\
+        \todo{max max height zu anzahl nodes in phylum plotten? oder mean max height oder ... 
+          (mean, min height...)} \\
+        \todo{depth...}
+
+      %---------------------------------------------------------------------------------------------------
+      \subsubsection{Distribution of Taxa}
+        - In our tree we can distinguish 28 different Taxa with the OTL taxonomic tree. \\
+        - The most of them are hardly represented. The major taxonomic groups are: ... \\
+        - Here you can see some characteristics of the Multifurcation of the tree. \\
+        In a phylogeny, the taxonomic division of the tree is far too coarse, meaning that there should 
+          be more subtaxa or 'unranked' nodes. But the closer we get to the root, the more the pure
+          taxonomic tree is reflected. If the tree were binary, the taxa would have to double. But the 
+          multipliers for some are much bigger and for others much smaller. \\
+        Please see the appendix on page \pageref{sec:taxaTable2} for a complete table \ref{sec:taxaTable2} 
+          of these data. \\
+        \todo{Was hierzu ist richtig und wichtig?}
 
@@
     \subsection{Transition probabilities}
-      \anmerkungtext{Wir hätten aber maximal 2 beta-Verteilungen mit jeweils 2 Parametern und je einem 
+      \anmerkungstext{Wir hätten aber maximal 2 beta-Verteilungen mit jeweils 2 Parametern und je einem 
         eigenen Schwellenwert bei dem in die andere Verteilung gewechselt wird. Also 6 Parameter. Ich 
         finde den Parameterraum den du bisher betrachtest zum einen nicht systematisch erfasst, zum 
-        anderen wahrscheinlich auch zu klein. Du kannst "Parameter sparen" indem zu z.B die beiden 
+        anderen wahrscheinlich auch zu klein. Du kannst -Parameter sparen- indem zu z.B die beiden 
         Verteilungen und cut-offs symmetrisch (gespiegelt an 0.5) machst. Solltest aber meines Erachtens 
@@
     \subsection{Multifurcation}
+
+      \begin{figure}
+        \begin{subfigure}{.5\textwidth}
+          \centering
+          \includegraphics[width=.8\linewidth]{Figures/multifurc.pdf}
+          \caption{all nodes}
+        \end{subfigure}%
+        \begin{subfigure}{.5\textwidth}
+          \centering
+          \includegraphics[width=.8\linewidth]{Figures/nr_children.pdf}
+          \caption{inner nodes (shiftet to 0)}
+        \end{subfigure}
+        \caption{plots of children of nodes}
+        \label{fig:childrenOfNodes}
+        \end{figure}
+
+      Hier Beschreibung von \ref{fig:childrenOfNodes}... \\
+
       \anmerkung{Description/Definition of Multifurcation $\rightarrow$ to the Intro (Bernhard)} \\
@@
     \centering
-    \includegraphics[width=1\textwidth]{Figures/simulation_evaluation_1.png}
+    \includegraphics[width=0.9\textwidth]{Figures/simulation_evaluation_1.png}
   \end{figure}
@@
 
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+\chapter{Appendices}
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Distribution of data in the taxa}\label{sec:taxaTable1}
+    \begin{center}
+      \begin{tabular}{ |l|r|l|r|r| }
+        \hline
+        Kingdom (3) & Number of Nodes & Phylum (25) & Number of Nodes & max max height \\
+        \hline \hline
+        Metazoa & 1 465 207 & Arthropoda & 1 170 539 & 54 \\
+        & & Chordata & 106 650 & 74 \\
+        & & Mollusca & 80 022 & 22 \\
+        & & Platyhelminthes & 27 141 & 9 \\
+        & & Nematoda & 24 564 & 23 \\
+        & & Cnidaria & 14 878 & 36 \\
+        & & Porifera & 11 737 & 26 \\
+        & & Echinodermata & 10 654 & 14 \\
+        & & Bryozoa & 8 631 & 11 \\
+        & & Rotifera & 3 093 & 7 \\
+        & & Nemertea & 1 793 & 7 \\
+        & & Tardigrada & 1 654 & 7 \\
+        & & Acanthocephala & 1 596 & 6 \\
+        & & Brachiopoda & 1 055 & 9 \\
+        & & Nematomorpha & 633 & 7 \\
+        & & Chaetognatha & 360 & 7 \\
+        & & Hemichordata & 196 & 5 \\ 
+        & & Cycliophora & 11 & 5 \\ 
+        % 1465207-(1170539+106650+80022+27141+24564+14878+11737+10654+8631+3093+1793+1654+1596+1055+633+360+196+11) = 0          \hline
+        Fungi & 254 871 & Ascomycota & 157 045 & 19 \\ 
+        & & Basidiomycota & 92 931 & 18 \\
+        & & Microsporidia & 1 949 & 6 \\ 
+        & & Glomeromycota & 1 490 & 6 \\
+        & & Chytridiomycota & 1 456 & 6 \\
+        % 254871-157045-92931-1949-1490-1456 = 0
+        \hline
+        Chloroplastida & 121 239 & Streptophyta & 120 731 & 49 \\
+        & & Chlorophyta & 508 & 6 \\
+        % 121239-120731-508 = 0
+        \hline  
+      \end{tabular}
+    \end{center}
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Taxa table}\label{sec:taxaTable2}
+    \begin{center}
+      % \begin{tabular}{ |>{\rowmac}l|>{\rowmac}r|<{\clearrow} }
+      \begin{tabular}{ |l|r||r|r| }
+        \hline
+        Taxa & Number of Nodes & Internal Nodes & Leaf Nodes \\
+        \hline \hline
+        \setrow{\bfseries}kingdom & ? & - & - \\ \hline
+        \setrow{\bfseries}phylum & ? & - & - \\
+        superclass & 1 & 1 & 0 \\ \hline
+        \setrow{\bfseries}class & 139 & 111 & 28 \\
+        subclass & 82 & 72 & 10 \\
+        infraclass & 8 & 7 & 1 \\
+        superorder & 33 & 31 & 2 \\ \hline
+        \setrow{\bfseries}order & 614 & 483 & 131 \\
+        suborder & 231 & 178 & 53 \\
+        infraorder & 89 & 73 & 16 \\
+        parvorder & 14 & 12 & 2 \\
+        superfamily & 628 & 489 & 139 \\ \hline
+        \setrow{\bfseries}family & 5740 & 4202 & 1538 \\
+        subfamily & 2617 & 1915 & 702 \\
+        supertribe & 1 & 0 & 1 \\
+        tribe & 1262 & 868 & 394 \\
+        subtribe & 267 & 221 & 46 \\ \hline
+        \setrow{\bfseries}genus & 127006 & 81494 & 45512 \\
+        subgenus & 1176 & 801 & 375 \\ \hline
+        section & 3 & 2 & 1 \\
+        subsection & 1 & 1 & 0 \\
+        species group + species subgroup & 181 + 93 & 129 + 74 & 52 + 19 \\
+        \setrow{\bfseries}species & 1649679 & 4424 & 1645255 (1639247) \\
+        subspecies & 16486 & 16 & 16470 (16449) \\
+        variety + varietas & 226 + 1529 & 0 + 4 & 226 (224) + 1525 (1515) \\
+        forma & 182 & 0 & 182 (182) \\
+        \hline \hline
+        no rank & 519 & 403 & 116 (7) \\
+        no rank - terminal & 32510 & 0 & 32510 (32510) \\
+        \hline  
+      \end{tabular}
+    \end{center}
+    extended leaf nodes (real leaf nodes)
+
 \end{document}

### 2018-02-16 metadata/run_castor.py
update castor script

@@ -31,18 +31,19 @@ def main():
     CURRENT_TIME = print_time(CURRENT_TIME)
     print(colored("---------------- read nodelist ----------------", "green"))
     nodelist_path = '../data/nodelist/Eukaryota.csv' 
-    #              0    1       2           3           4
-    # nodelist - [id, depths, nr_children, originaltag, finaltag]
+    #              0    1       2           3           4           5
+    # nodelist - [id, depth, heights, nr_children, originaltag, finaltag]
     with open(nodelist_path, 'r') as csv_file:
         reader = csv.reader(csv_file, delimiter=',')
         for row in reader:
             if row != []:
                 ott = row[0]
-                depths = ast.literal_eval(row[1])
-                nr_children = int(row[2])
-                originaltag = row[3]
-                finaltag = row[4]
-                nodelist.append([ott, depths, nr_children, originaltag, finaltag])
+                depth = int(row[1])
+                heights = ast.literal_eval(row[2])
+                nr_children = int(row[3])
+                originaltag = row[4]
+                finaltag = row[5]
+                nodelist.append([ott, depth, heights, nr_children, originaltag, finaltag])
     CURRENT_TIME = print_time(CURRENT_TIME)
     print(colored("---------------- Sankoff parsimony ----------------", "green"))
     sankoff_parsimony(tree)
@@ -63,8 +64,8 @@ def sankoff_parsimony(tree):
     """Using rpy2 for forwarding to R code"""
     # Arguments:
     #   subtree
-    #              0    1       2           3           4
-    #   nodelist - [id, depths, nr_children, originaltag, finaltag]
+    #              0    1       2           3           4           5
+    #   nodelist - [id, depth, heights, nr_children, originaltag, finaltag]
     global nodelist
 
     # ---- cache tree for R script ---
@@ -95,14 +96,14 @@ def sankoff_parsimony(tree):
     for i in range(2*l, 3*l):
         if j < number_of_tips[0]:
             element = find_element_in_nodelist(leaf_nodes[j], nodelist)
-            if element[4] == '':    # if unknown
+            if element[5] == '':    # if unknown
                 # set finaltag:
-                element[4] = likelihoods[i]
+                element[5] = likelihoods[i]
             j += 1
         else:
             element = find_element_in_nodelist(internal_nodes[k], nodelist)
             # set finaltag:
-            element[4] = likelihoods[i]
+            element[5] = likelihoods[i]
             k += 1
     return
 
[…]

### 2018-02-17 metadata/extend_nodelist.py
small fixes

@@ -7,7 +7,7 @@ nodelist = pd.read_csv('../data/nodelist/Eukaryota-castor.csv', encoding='utf-8'
 merged = pd.merge(nodelist, ott_taxa, how='left', on='ott_id')
 
 print(len(nodelist),'merge', len(ott_taxa), '->', len(merged))
-print('castor results added')
+print('ranks to castor results added')
 
 kingdom_mapping = pd.read_csv('../data/nodelist/Eukaryota-kingdom_mapping.csv', encoding='utf-8')
 merged = pd.merge(merged, kingdom_mapping, how='left', on='ott_id')
@@ -29,7 +29,7 @@ print('class taxa added')
 
 order_mapping = pd.read_csv('../data/nodelist/Eukaryota-order_mapping.csv', encoding='utf-8')
 merged = pd.merge(merged, order_mapping, how='left', on='ott_id')
-merged.to_csv('../results/Eukaryota-taxa-new-new.csv', index=False, encoding='utf-8')
+merged.to_csv('../results/Eukaryota-taxa.csv', index=False, encoding='utf-8')
 
 print('merge', len(order_mapping))
 print('order taxa added')

### 2018-02-17 metadata/run_castor.py

@@ -50,7 +50,7 @@ def main():
     CURRENT_TIME = print_time(CURRENT_TIME)
     print(colored("---------------- Save nodelist ----------------", "green"))
     nodelist_path = '../data/nodelist/Eukaryota-castor.csv' 
-    header = ['ott_id', 'depths', 'nr_children', 'originaltag', 'finaltag']
+    header = ['ott_id', 'depth', 'heights', 'nr_children', 'originaltag', 'finaltag']
     with open(nodelist_path, 'w') as nodelist_file:
         writer = csv.writer(nodelist_file, delimiter=',')
         writer.writerow(header)

### 2018-02-17 Paper - Latex/Paper - Skizze - v2.tex
Paper - Methods - Multifurcation - Regressionsanalyse

@@
         https://tree.opentreeoflife.org/opentree/argus/opentree9.1@ott166969 \\
-        Was bedeutet das für unsere Analyse? Ignorieren wir die \~~4000 internen und Zählen sie zu den 
+        Was bedeutet das für unsere Analyse? Ignorieren wir die $\sim$ 4000 internen und Zählen sie zu den 
           Blättern, oder zählen wir alle zu den Internen oder puzzlen wir sie einzeln raus. D.h. nur die 
@@
           Höhe als Blatt zählen. Das müsste dann gelten $min height = max height$. \\ 
-        \begin{lstlisting}
+        \begin{lstlisting}[gobble=8]
           leaf.taxa <-  all.taxa[all.taxa$nr_children==0, ]
@@
           taxonomic tree is reflected. If the tree were binary, the taxa would have to double. But the 
-          multipliers for some are much bigger and for others much smaller. \\
+          multipliers for some are much bigger and for others much smaller, which you can see in in figure 
+          \ref{fig:taxaTable2}. \\
         Please see the appendix on page \pageref{sec:taxaTable2} for a complete table \ref{sec:taxaTable2} 
@@
         \todo{Was hierzu ist richtig und wichtig?}
+        \begin{figure}
+          \centering
+          \includegraphics[width=0.9\textwidth]{Figures/TaxaTable2.JPG}
+          \caption{Distribution of Nodes in Rank-Cathegories}
+          \label{fig:taxaTable2}
+        \end{figure}
 
@@
     \subsection{Multifurcation}
+      Ein von den Daten beeinflusster Parameter ist die Multifurkation des Baumes, d.h. wie weit sind 
+        wir von einem binären Baum entfehrnt, was hängt mit der stärke der Multifurkation zusammen und 
+        welche Auswirkung hat sie auf unsere Fragestellung. \\
+      In Figure \ref{fig:childrenOfNodes} haben wir die Multifurkation über den gesamten Baum abgebildet,
+        dazu haben wir für jeden Knoten die Anzahl seiner Kinder gezählt und dies als Histogram 
+        geplottet. \\
+      Subfigure \ref{fig:childrenOfNodes_innerNodes} beschränkt sich hierbei nur auf die inner nodes 
+        während Subfigure \ref{fig:childrenOfNodes_allNodes} alle Knoten abbildet. \\
+      \todo{Welchen der beiden Plots wollen wir nehmen, einer genügt eigentlich.}
 
@@
           \caption{all nodes}
+          \label{fig:childrenOfNodes_allNodes}
         \end{subfigure}%
@@
           \caption{inner nodes (shiftet to 0)}
+          \label{fig:childrenOfNodes_innerNodes}
         \end{subfigure}
@@
 
-      Hier Beschreibung von \ref{fig:childrenOfNodes}... \\
+      Wir haben verschiedene Eigenschaften der Multifurkation untersucht:
+      \begin{itemize}
+        \item stärke der Multifurcation in verschiedenen Subbäumen
+        \item zusammenhang zur tiefe im Baum
+        \item zusammenhang zu höhe im baum
+        \item einfluss auf die vorhersage des Castor und Fitch Algorithmus (Simulation) \todo{...}
+      \end{itemize}
 
-      \anmerkung{Description/Definition of Multifurcation $\rightarrow$ to the Intro (Bernhard)} \\
-      \anmerkung{Regressionsanalyse (Bernhard)} \\
-      \anmerkung{poisson glm: \#children \~ ~ I phylum $\rightarrow$ R fitdist p (Emanuel)} \\
+      %---------------------------------------------------------------------------------------------------
+      \subsubsection{Poisson regression}
+
+        \begin{lstlisting}[gobble=8]
+          glm(formula = multifurc ~ 1, family = "poisson", data = inner.taxa)
+        \end{lstlisting}
+        The intercept is $2.821 > 0$ $\Rightarrow$ there is a multifunction.
+        (Intercept: Stärke der Multifurcation) \\
+        Comparing the different kingdoms, we find that multifunctionality is greater in Fungi than in 
+        Chloroplastida than in Metazoa:
+        $$4.0999 (Fungi Intercept) > -0.9132 (Chloroplastida Intercept) > -1.4320 (Metazoa Intercept)$$
+        % Degrees of Freedom: 96010 Total (i.e. Null);  96010 Residual
+        Wir haben außerdem drei komplexitätsstärken von Modellen verglichen bezüglich der höhe und tiefe 
+          des Baums mit dem folgenden Deviance Table:
+
+        \begin{center}
+          \begin{tabular}{ |l|r|l| }
+            \hline
+            Model & Residuals Dev & Deviance Pr(>Chi) \\
+            \hline \hline
+            multifurc $\sim$ kingdom & 7774454 & \\
+            multifurc $\sim$ phylum & 7435700 & 338754 \\
+            multifurc $\sim$ class & 7337241 & 98459 \\
+            \rowcolor{green} multifurc $\sim$ order & 7076068 & 261172 \\
+
+            % [1] "------------------------kingdom - phylum - class - order--------------------------"
+            % Analysis of Deviance Table
+
+            % Model 1: multifurc ~ kingdom
+            % Model 2: multifurc ~ phylum
+            % Model 3: multifurc ~ class
+            % Model 4: multifurc ~ order
+            %   Resid. Df Resid. Dev  Df Deviance  Pr(>Chi)
+            % 1    167222    7774454
+            % 2    167173    7435700  49   338754 < 2.2e-16 ***
+            % 3    167039    7337241 134    98459 < 2.2e-16 ***
+            % 4    166352    7076068 687   261172 < 2.2e-16 ***
+            % ---
+            % Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+
+            % 1] "-------------------phylum - depth / min/max/mean.height-----------------------"
+            % Analysis of Deviance Table
+
+            % Model 1: multifurc ~ phylum
+            % Model 2: multifurc ~ phylum + depth
+            % Model 3: multifurc ~ phylum + min.height
+            % Model 4: multifurc ~ phylum + max.height
+            % Model 5: multifurc ~ phylum + mean.height
+            %   Resid. Df Resid. Dev Df Deviance  Pr(>Chi)
+            % 1    167173    7435700
+            % 2    167172    7431609  1     4090 < 2.2e-16 ***
+            % 3    167172    7233486  0   198124
+            % 4    167172    7375889  0  -142403
+            % 5    167172    7128318  0   247570
+            % ---
+            % Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+            % [1] "--------------------------------------------------"
+
+            \hline \hline
+            multifurc $\sim$ order & 4762407 & \\
+            multifurc $\sim$ order + max.height & 4721600 & $40807 < 2.2e-16$ \\
+            \rowcolor{green} multifurc $\sim$ order * max.height & 4674368 & $47233 < 2.2e-16$ \\
+            \hline
+            multifurc $\sim$ order & 4762407 & \\
+            multifurc $\sim$ order + min.height & 4712672 & $49735 < 2.2e-16$ \\
+            multifurc $\sim$ order * min.height & 4694783 & $17889 < 2.2e-16$ \\
+            \hline
+            multifurc $\sim$ order & 4762407 & \\
+            multifurc $\sim$ order + mean.height & 4717014 & $45393 < 2.2e-16$ \\
+            multifurc $\sim$ order * mean.height & 4694424 & $22590 < 2.2e-16$ \\
+            \hline \hline
+            multifurc $\sim$ phylum & 4664706 & \\
+            multifurc $\sim$ phylum + max.height & 4601257 & 63449 < 2.2e-16 \\
+            \rowcolor{green} multifurc $\sim$ phylum * max.height & 4546220 & 55036 < 2.2e-16 \\
+            \hline \hline
+            multifurc $\sim$ class & 4581569 & \\
+            multifurc $\sim$ class + max.height & 4510567 & 71003 \\
+            \rowcolor{green} multifurc $\sim$ class * max.height & 4434635 & 75932 \\
+
+          \end{tabular}
+        \end{center}
+        * Residuals: Fehler - wieviele Werte sind nicht gut modelliert. (umso kleiner umso besser - grün)\\
+        * Deviance - Abweichung
+
       \anmerkung{different parameters for different taxa? (Emanuel)} \\
@@
         \ref{fig:HistogramsOfMultifurcations} is this plot shown with three functions, which came 
-        \todo{close(st)} to this goal: $\frac{1000000000000000}{x^4}$ (magenta), 
+        closest to this goal: $\frac{1000000000000000}{x^4}$ (magenta), 
         $\frac{300000000000}{x^3}$ (red) and $\frac{80000000}{x^2}$ (black). \\
@@
         }:
-      \begin{lstlisting}
+      \begin{lstlisting}[gobble=6]
         from Bio import Phylo
@@
       \anmerkung{trivial, does not give real info (Emanuel)}
-      \begin{lstlisting}
+      \begin{lstlisting}[gobble=6]
         def randomized(cls, taxa, branch_length=1.0, 
@@
         this code you see here:
-      \begin{lstlisting}
+      \begin{lstlisting}[gobble=6]
         from numpy import random
@@
       \anmerkung{poisson process $\rightarrow$ fit that distribution, include depth as a predictor, see if significant (Emanuel)}
-      \begin{lstlisting}
+      \begin{lstlisting}[gobble=6]
         from numpy import random
@@
       % \begin{tabular}{ |>{\rowmac}l|>{\rowmac}r|<{\clearrow} }
-      \begin{tabular}{ |l|r||r|r| }
+      \begin{tabular}{ |l|r||r|r|r| }
         \hline
-        Taxa & Number of Nodes & Internal Nodes & Leaf Nodes \\
+        Taxa & Number of Nodes & Internal Nodes & Leaf Nodes & Terminal Leaf Nodes \\
         \hline \hline
-        \setrow{\bfseries}kingdom & ? & - & - \\ \hline
-        \setrow{\bfseries}phylum & ? & - & - \\
-        superclass & 1 & 1 & 0 \\ \hline
-        \setrow{\bfseries}class & 139 & 111 & 28 \\
-        subclass & 82 & 72 & 10 \\
-        infraclass & 8 & 7 & 1 \\
-        superorder & 33 & 31 & 2 \\ \hline
-        \setrow{\bfseries}order & 614 & 483 & 131 \\
-        suborder & 231 & 178 & 53 \\
-        infraorder & 89 & 73 & 16 \\
-        parvorder & 14 & 12 & 2 \\
-        superfamily & 628 & 489 & 139 \\ \hline
-        \setrow{\bfseries}family & 5740 & 4202 & 1538 \\
-        subfamily & 2617 & 1915 & 702 \\
-        supertribe & 1 & 0 & 1 \\
-        tribe & 1262 & 868 & 394 \\
-        subtribe & 267 & 221 & 46 \\ \hline
-        \setrow{\bfseries}genus & 127006 & 81494 & 45512 \\
-        subgenus & 1176 & 801 & 375 \\ \hline
-        section & 3 & 2 & 1 \\
-        subsection & 1 & 1 & 0 \\
-        species group + species subgroup & 181 + 93 & 129 + 74 & 52 + 19 \\
-        \setrow{\bfseries}species & 1649679 & 4424 & 1645255 (1639247) \\
-        subspecies & 16486 & 16 & 16470 (16449) \\
-        variety + varietas & 226 + 1529 & 0 + 4 & 226 (224) + 1525 (1515) \\
-        forma & 182 & 0 & 182 (182) \\
+        \setrow{\bfseries}domain & 1 & 1 & &  \\ \hline
+        \setrow{\bfseries}kingdom & 3 & 3 & &  \\
+        subkingdom & 2 & 2 & & \\
+        infrakingdom & 5 & 5 & & \\
+        superphylum & 2 & 2 & & \\ \hline
+        \setrow{\bfseries}phylum & 57 & 54 & 3 & \\
+        subphylum & 22 & 20 & 2 & \\
+        infraphylum & 2 & 2 & & \\
+        superclass & 8 & 8 & & \\ \hline
+        \setrow{\bfseries}class & 209 & 175 & 34 & \\
+        subclass & 120 & 106 & 14 & \\
+        infraclass & 14 & 11 & 3 & \\
+        superorder & 40 & 37 & 3 & \\ \hline
+        \setrow{\bfseries}order & 1014 & 772 & 242 & \\
+        suborder & 285 & 222 & 63 & \\
+        infraorder & 95 & 78 & 17 & \\
+        parvorder & 14 & 12 & 2 & \\
+        superfamily & 829 & 626 & 203 & \\ \hline
+        \setrow{\bfseries}family & 8449 & 6143 & 2306 & \\
+        subfamily & 3090 & 2250 & 840 & \\
+        supertribe & 1 & 0 & 1 & \\
+        tribe & 1764 & 1285 & 479 & \\
+        subtribe & 435 & 359 & 77 & \\ \hline
+        \setrow{\bfseries}genus & 164656 & 105452 & 59204 & \\
+        subgenus & 1266 & 869 & 397 & \\
+        section & 3 & 2 & 1 & \\
+        subsection & 1 & 1 & 0 & \\
+        species group & 365 & 288 & 77 & \\
+        species subgroup & 123 & 100 & 23 & \\ \hline
+        \setrow{\bfseries}species & 2247251 & 7423 & 2239828 & 2228993 \\
+        subspecies & 22437 & 75 & 22362 & 22239 \\
+        variety & 1755 & 7 & 1748 & 1726 \\
+        varietas & 5970 & 19 & 5951 & 5909 \\
+        forma & 1181 & & 1181 & 1181 \\
         \hline \hline
-        no rank & 519 & 403 & 116 (7) \\
-        no rank - terminal & 32510 & 0 & 32510 (32510) \\
+        no rank & 954 & 719 & 235 & 7 \\
+        no rank - terminal & 37452 & & 37452 & 37452 \\
+        (no entry) & 40099 & 40099 & & \\
         \hline  

### 2018-02-17 scripts/R/analyse_input.R
analyse metadata + results

@@ -2,15 +2,18 @@ library(data.table)
 library(ggplot2)
 library(effects)
 
-all.taxa <- fread("~/Lydia_data/Eukaryota-taxa.csv")
+format(Sys.time(), "%a %b %d %X %Y")
+
+all.taxa <- fread("../../results/Eukaryota-taxa.csv")
 
 ### right mode for all
+all.taxa$kingdom <- as.factor(all.taxa$kingdom)
 all.taxa$phylum <- as.factor(all.taxa$phylum)
 all.taxa$class <- as.factor(all.taxa$class)
-all.taxa$kingdom <- as.factor(all.taxa$kingdom)
+all.taxa$order <- as.factor(all.taxa$order)
 
 
-heights <- do.call("rbind", strsplit(gsub("\\[|\\]", "", all.taxa$depths), ", "))
+heights <- do.call("rbind", strsplit(gsub("\\[|\\]", "", all.taxa$heights), ", "))
 
 heights <- as.data.frame(apply(heights, 2, as.numeric))
 
@@ -18,118 +21,209 @@ names(heights) <- c("min.height", "max.height", "mean.height")
 
 all.taxa <- cbind(all.taxa, heights)
 
-table(all.taxa$kingdom)
+## list all Kingdoms, Phyla:
+# table(all.taxa$kingdom)
+# table(all.taxa$phylum)
 
-table(all.taxa$kingdom, all.taxa$phylum)
+## which Phylum in which Kingdom:
+# table(all.taxa$kingdom, all.taxa$phylum)
 
 summary(all.taxa$nr_children)
+## [Min. 1st Qu.  Median    Mean 3rd Qu.    Max. ] over all phyla - max height
+# tapply(all.taxa$max.height, all.taxa$phylum, summary)
 
-tapply(all.taxa$max.height, all.taxa$phylum, summary)
-
-### phyla and kingdom nodes are not in the table
+### all nodes sorted by rank
 table(all.taxa$rank)[order(table(all.taxa$rank))]
 
 ### find out what is going on here...
-table(all.taxa[all.taxa$nr_children==1, "rank"])
+# print('------------------------ all.taxa$nr_children==1 --------------------------')
+# table(all.taxa[all.taxa$nr_children==1, "finaltag"])
+# print('---------------- nr_children==1 ---------------------')
+# table(all.taxa[all.taxa$nr_children==1, "rank"])
[…]

### 2018-02-17 Paper - Latex/Paper - Skizze - v2.tex
Paper - Methods - Multifurcations - Regressionsanalyse -> phylum * mean height

@@
 
-            % 1] "-------------------phylum - depth / min/max/mean.height-----------------------"
-            % Analysis of Deviance Table
-
-            % Model 1: multifurc ~ phylum
-            % Model 2: multifurc ~ phylum + depth
-            % Model 3: multifurc ~ phylum + min.height
-            % Model 4: multifurc ~ phylum + max.height
-            % Model 5: multifurc ~ phylum + mean.height
-            %   Resid. Df Resid. Dev Df Deviance  Pr(>Chi)
-            % 1    167173    7435700
-            % 2    167172    7431609  1     4090 < 2.2e-16 ***
-            % 3    167172    7233486  0   198124
-            % 4    167172    7375889  0  -142403
-            % 5    167172    7128318  0   247570
-            % ---
-            % Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-            % [1] "--------------------------------------------------"
-
             \hline \hline
-            multifurc $\sim$ order & 4762407 & \\
-            multifurc $\sim$ order + max.height & 4721600 & $40807 < 2.2e-16$ \\
-            \rowcolor{green} multifurc $\sim$ order * max.height & 4674368 & $47233 < 2.2e-16$ \\
+            multifurc $\sim$ phylum + depth & 7431609 & \\
+            multifurc $\sim$ phylum + max.height & 7375889 & 55721 \\
+            multifurc $\sim$ phylum + min.height & 7233486 & 142403 \\
+            \rowcolor{green} multifurc $\sim$ phylum + mean.height & 7128318 & 105167 \\
+            \hline \hline
+            multifurc ~ phylum * depth & 7335396 & -24155 \\
+            multifurc ~ phylum * max.height & 7311241 & \\
+            multifurc ~ phylum * min.height & 7177002 & 158394 \\
+            \rowcolor{green} multifurc ~ phylum * mean.height & 7020258 & 156745 \\
+            \hline \hline
+            multifurc ~ phylum & 7435700 & \\
+            multifurc ~ phylum + mean.height & 7128318 & 307381 \\
+            \rowcolor{green} multifurc ~ phylum * mean.height & 7020258 & 108061 \\
             \hline
-            multifurc $\sim$ order & 4762407 & \\
-            multifurc $\sim$ order + min.height & 4712672 & $49735 < 2.2e-16$ \\
-            multifurc $\sim$ order * min.height & 4694783 & $17889 < 2.2e-16$ \\
-            \hline
-            multifurc $\sim$ order & 4762407 & \\
-            multifurc $\sim$ order + mean.height & 4717014 & $45393 < 2.2e-16$ \\
-            multifurc $\sim$ order * mean.height & 4694424 & $22590 < 2.2e-16$ \\
-            \hline \hline
-            multifurc $\sim$ phylum & 4664706 & \\
-            multifurc $\sim$ phylum + max.height & 4601257 & 63449 < 2.2e-16 \\
-            \rowcolor{green} multifurc $\sim$ phylum * max.height & 4546220 & 55036 < 2.2e-16 \\
-            \hline \hline
-            multifurc $\sim$ class & 4581569 & \\
-            multifurc $\sim$ class + max.height & 4510567 & 71003 \\
-            \rowcolor{green} multifurc $\sim$ class * max.height & 4434635 & 75932 \\
-
           \end{tabular}

### 2018-02-18 Paper - Latex/Paper - Skizze - v2.tex
Paper - rearrange some stuff

@@
 
-% \hfuzz=\maxdimen \tolerance=10000 \hbadness=10000
+\hfuzz=\maxdimen \tolerance=10000 \hbadness=10000
 
@@
 %---------------------------------------------------------------------------------------------------
+%--------------------------------------------------------------------------------------------------- 
 \chapter*{Abstract}
@@
 
+%---------------------------------------------------------------------------------------------------
 %---------------------------------------------------------------------------------------------------
@@
 %---------------------------------------------------------------------------------------------------
+%--------------------------------------------------------------------------------------------------- 
 \chapter{Methods}
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Get data}
+  %---------------------------------------------------------------------------------------------------
+  \section{Get data - Properties of real Data}
     For our research we need two types of data: a tree and information about the states. \\
@@
     %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
     \subsection{OTL}
@@
 
+      %---------------------------------------------------------------------------------------------------
+      \subsubsection{Distribution of Taxa}
+        - In our tree we can distinguish 28 different Taxa with the OTL taxonomic tree. \\
+        - The most of them are hardly represented. The major taxonomic groups are: ... \\
+        - Here you can see some characteristics of the Multifurcation of the tree. \\
+        \begin{figure}[h!]
+          \centering
+          \includegraphics[width=0.9\textwidth]{Figures/TaxaTable2.JPG}
+          \caption{Distribution of Nodes in Rank-Cathegories}
+          \label{fig:taxaTable2}
+        \end{figure}
+        In a phylogeny, the taxonomic division of the tree is far too coarse, meaning that there should 
+          be more subtaxa or 'unranked' nodes. But the closer we get to the root, the more the pure
+          taxonomic tree is reflected. If the tree were binary, the taxa would have to double. But the 
+          multipliers for some are much bigger and for others much smaller, which you can see in in figure 
+          \ref{fig:taxaTable2}. \\
+        Please see the appendix on page \pageref{sec:taxaTable2} for a complete table \ref{sec:taxaTable2} 
+          of these data. \\
+        \todo{Was hierzu ist richtig und wichtig?}
+
+      %---------------------------------------------------------------------------------------------------
+      \subsubsection{Distribution of data in the taxa}
+        Mithilfe des taxonomischen Baums von OTL haben wir die Knoten ihren Kingdoms, Phyla und Classes 
+          zugeteilt. \\
+        Please see the appendix on page \pageref{sec:taxaTable1} for a complete table \ref{sec:taxaTable1} 
+          of these data. \\
+        \todo{gibt es einen Zusammenhang zwischen Anzahl} \\
+        \todo{max max height zu anzahl nodes in phylum plotten? oder mean max height oder ... 
+          (mean, min height...)} \\
+        \todo{depth...}
+
+    %---------------------------------------------------------------------------------------------------
     %---------------------------------------------------------------------------------------------------
@@
       %   free-living lists.
-      \todo{einige spezies nicht mit einbezogen, da sie keine OTT id haben, hier könnte man noch verbessern (future work)}
+      \todo{einige spezies nicht mit einbezogen, da sie keine OTT id haben, hier könnte man noch 
+        verbessern (future work)}
       \todo{You can find all interaction types here:
-        https://github.com/jhpoelen/eol-globi-data/blob/master/eol-globi-lib/src/main/java/org/eol/globi/domain/InteractType.java .}
+        https://github.com/jhpoelen/eol-globi-data/blob/master/eol-globi-lib/src/main/java/org/eol/globi/domain/InteractType.java .} \\ \\
+
+      With this we got $\sim 51000$ (distinct) freeliving species and $\sim 47000$ (distinct) parasite 
+        species (see section countings) \todo{ref einfügen}. But we found also  $\sim 57000$ (not 
+        distinct) source species and $\sim 810000$ (not distinct) target species without OTT ids. 
+        Since we currently use only OTT ids, we could not use this information. \\
+      \todo{mehr dazu in section: unknown nodes...}
 
     %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  \section{Metadata analysis}
-    Properties of real Data - Metadata analysis \\
-
-    Um eine möglichst realistische Simulation zu erzeugen haben wir auf der einen Seite einige Daten 
-      gesammelt (Kaptiel Countings), und außerdem beeinflussende Parameter untersucht.
-
-    Wir haben zwei große Arten von Parametern:
-    \begin{enumerate}
-      \item Biological parameters (A result of the evolutionary process.):
-        \begin{itemize}
-          \item transition probabilities
-        \end{itemize}
-      \item Distribution of the loss of information:
-        \begin{itemize}
-          \item Loss of topology ($\rightarrow$ mutlifurcations).
-          \item Unknown information about the states of some leaf nodes.
-        \end{itemize}
-    \end{enumerate}
-
-    \todo{Hier darauf hinweisen, dass wir für multifurcations und unknown data den einfluss auf die 
-      Algorithmen testen.}
-
     %---------------------------------------------------------------------------------------------------
@@
       \end{center}
-      \todo{tree, subtrees? figure dazu?}
+      \todo{tree, subtrees? figure dazu?} \\
       $\frac{100}{2293463 * (51337 + 47332)} \approx 4.3$ $\rightarrow$ only 4.3\% of leaf nodes are 
@@
       \#Interne Knoten und \#Blattknoten $\rightarrow$ Wie stark ist die Multifurkation?
+
       %---------------------------------------------------------------------------------------------------
@@
   %---------------------------------------------------------------------------------------------------
-      \subsubsection{Distribution of data in the taxa}
-        Mithilfe des taxonomischen Baums von OTL haben wir die Knoten ihren Kingdoms, Phyla und Classes 
-          zugeteilt. \\
-        Please see the appendix on page \pageref{sec:taxaTable1} for a complete table \ref{sec:taxaTable1} 
-          of these data. \\
-        \todo{gibt es einen Zusammenhang zwischen Anzahl} \\
-        \todo{max max height zu anzahl nodes in phylum plotten? oder mean max height oder ... 
-          (mean, min height...)} \\
-        \todo{depth...}
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Metadata analysis}
+    Um eine möglichst realistische Simulation zu erzeugen haben wir auf der einen Seite einige Daten 
+      gesammelt (vorheriges Kaptiel), und außerdem beeinflussende Parameter untersucht. \\
+    Wir haben zwei große Arten von Parametern:
+    \begin{enumerate}
+      \item Biological parameters (A result of the evolutionary process.):
+        \begin{itemize}
+          \item transition probabilities
+        \end{itemize}
+      \item Distribution of the loss of information:
+        \begin{itemize}
+          \item Loss of topology ($\rightarrow$ mutlifurcations).
+          \item Unknown information about the states of some leaf nodes.
+        \end{itemize}
+    \end{enumerate}
+    We tested the influence of these parameters on our result using our simulation. \\
+    \todo{ref zu section simulation}
 
     %---------------------------------------------------------------------------------------------------
-      \subsubsection{Distribution of Taxa}
-        - In our tree we can distinguish 28 different Taxa with the OTL taxonomic tree. \\
-        - The most of them are hardly represented. The major taxonomic groups are: ... \\
-        - Here you can see some characteristics of the Multifurcation of the tree. \\
-        In a phylogeny, the taxonomic division of the tree is far too coarse, meaning that there should 
-          be more subtaxa or 'unranked' nodes. But the closer we get to the root, the more the pure
-          taxonomic tree is reflected. If the tree were binary, the taxa would have to double. But the 
-          multipliers for some are much bigger and for others much smaller, which you can see in in figure 
-          \ref{fig:taxaTable2}. \\
-        Please see the appendix on page \pageref{sec:taxaTable2} for a complete table \ref{sec:taxaTable2} 
-          of these data. \\
-        \todo{Was hierzu ist richtig und wichtig?}
-        \begin{figure}
-          \centering
-          \includegraphics[width=0.9\textwidth]{Figures/TaxaTable2.JPG}
-          \caption{Distribution of Nodes in Rank-Cathegories}
-          \label{fig:taxaTable2}
-        \end{figure}
-
     %---------------------------------------------------------------------------------------------------
@@
     %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
     \subsection{Multifurcation}
@@
         während Subfigure \ref{fig:childrenOfNodes_allNodes} alle Knoten abbildet. \\
-      \todo{Welchen der beiden Plots wollen wir nehmen, einer genügt eigentlich.}
+      \todo{Welchen der beiden Plots wollen wir nehmen, einer genügt eigentlich:}
 
-      \begin{figure}
+      \begin{figure}[h!]
         \begin{subfigure}{.5\textwidth}
@@
         \item zusammenhang zur tiefe im Baum
-        \item zusammenhang zu höhe im baum
+        \item zusammenhang zu höhe im baum (max, min, mean)
         \item einfluss auf die vorhersage des Castor und Fitch Algorithmus (Simulation) \todo{...}
@@
         \begin{center}
-          \begin{tabular}{ |l|r|l| }
+          \begin{longtable}{ |l|r|r| }
             \hline
-            Model & Residuals Dev & Deviance Pr(>Chi) \\
+            Model & Residuals Dev & Deviance Pr \\
             \hline \hline
@@
             \rowcolor{green} multifurc $\sim$ order & 7076068 & 261172 \\
-
-            % [1] "------------------------kingdom - phylum - class - order--------------------------"
-            % Analysis of Deviance Table
-
-            % Model 1: multifurc ~ kingdom
-            % Model 2: multifurc ~ phylum
-            % Model 3: multifurc ~ class
-            % Model 4: multifurc ~ order
-            %   Resid. Df Resid. Dev  Df Deviance  Pr(>Chi)
-            % 1    167222    7774454
-            % 2    167173    7435700  49   338754 < 2.2e-16 ***
-            % 3    167039    7337241 134    98459 < 2.2e-16 ***
-            % 4    166352    7076068 687   261172 < 2.2e-16 ***
-            % ---
-            % Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-
-            \hline \hline
+            \hline \hline \hline
             multifurc $\sim$ phylum + depth & 7431609 & \\
@@
             \hline \hline
-            multifurc ~ phylum * depth & 7335396 & -24155 \\
-            multifurc ~ phylum * max.height & 7311241 & \\
-            multifurc ~ phylum * min.height & 7177002 & 158394 \\
+            multifurc ~ phylum * depth & 7335396 & \\
+            multifurc ~ phylum * max.height & 7311241 & 24155 \\
+            multifurc ~ phylum * min.height & 7177002 & 134238 \\
             \rowcolor{green} multifurc ~ phylum * mean.height & 7020258 & 156745 \\
@@
             \rowcolor{green} multifurc ~ phylum * mean.height & 7020258 & 108061 \\
+            \hline \hline \hline
+            multifurc $\sim$ class + depth & 7334754 & \\
+            multifurc $\sim$ class + max.height & 7275856 & 58898 \\
+            multifurc $\sim$ class + min.height & 7144686 & 131170 \\
+            \rowcolor{green} multifurc $\sim$ class + mean.height & 7055313 & 89374 \\
+            \hline \hline
+            multifurc ~ class * depth & 7250759 & \\
+            multifurc ~ class * max.height & 7187504 & 63256 \\
+            multifurc ~ class * min.height & 7094933 & 92570 \\
+            \rowcolor{green} multifurc ~ class * mean.height & 6965794 & 129139 \\
+            \hline \hline
+            multifurc ~ class & 7337241 & \\
+            multifurc ~ class + mean.height & 7055313 & 281928 \\
+            \rowcolor{green} multifurc ~ class * mean.height & 6965794 & 89518 \\
+            \hline \hline \hline
+            multifurc $\sim$ order + depth & 7027578 & \\
+            multifurc $\sim$ order + max.height & 7005424 & 22154 \\
+            multifurc $\sim$ order + min.height & 6890703 & 114721 \\
+            \rowcolor{green} multifurc $\sim$ order + mean.height & 6815271 & 75432 \\
             \hline
-          \end{tabular}
+          \end{longtable}
         \end{center}
-        * Residuals: Fehler - wieviele Werte sind nicht gut modelliert. (umso kleiner umso besser - grün)\\
-        * Deviance - Abweichung
+        * Residuals: Fehler - wieviele Werte sind nicht gut modelliert. (umso kleiner umso besser - grün) \\
+        * Deviance - Abweichung \\
 
-      \anmerkung{different parameters for different taxa? (Emanuel)} \\
+        \begin{lstlisting}[gobble=8]
+          class * depth / min/max/mean.height: Warning message: glm.fit: fitted rates numerically 0 occurred
+          order * depth / min/max/mean.height: Error: cannot allocate vector of size 2.2 Gb
+        \end{lstlisting}
+
+        \todotext{Nur ein Ausschnitt hier und dann... You can find the whole Deviance Table in the 
+          Appendix...} \\
+        Interpretation: Die Multifurkation ist sehr ungleich verteilt. Daher ist die vorhersage umso 
+          genauer umso kleinere Subtrees wir betrachten. ...
+        \begin{lstlisting}[gobble=8]
+          Model 1: multifurc ~ kingdom
+          Model 2: multifurc ~ phylum
+          Model 3: multifurc ~ class
+          Model 4: multifurc ~ order
+            Resid. Df Resid. Dev  Df Deviance  Pr(>Chi)
+          1    167222    7774454
+          2    167173    7435700  49   338754 < 2.2e-16 ***
+          3    167039    7337241 134    98459 < 2.2e-16 ***
+          4    166352    7076068 687   261172 < 2.2e-16 ***
+        \end{lstlisting}
+        \anmerkung{different parameters for different taxa? (Emanuel)} \\ \\
+
+        \todo{old Stuff:} \\
         One property of the tree is its ridge of multifurcation. For this we collected for every node its
@@
         \anmerkung{do we? Is that really universal knowledge or could it be supported by data or a citation? (Bernhard)} \\
-      \todo{subtrees... there is some old stuff...} \\
-      \todo{other subsections here...} \\
 
+  %---------------------------------------------------------------------------------------------------
   %---------------------------------------------------------------------------------------------------
@@
     %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
     \subsection{random binary tree}
@@
 
+    %---------------------------------------------------------------------------------------------------
     %---------------------------------------------------------------------------------------------------
@@
     %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
     \subsection{multifurcate tree}
@@
 
+      %---------------------------------------------------------------------------------------------------
       \subsubsection{Sankoff}
@@
 
+      %---------------------------------------------------------------------------------------------------  
       \subsubsection{my Algorithm}
 
+  %---------------------------------------------------------------------------------------------------
   %---------------------------------------------------------------------------------------------------
@@
   %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
   \section{Implementation}
@@
 %---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
 \chapter{Results}
 
+  %---------------------------------------------------------------------------------------------------
   %---------------------------------------------------------------------------------------------------

### 2018-02-21 Paper - Latex/Paper - Skizze - v2.tex
Paper - Results -  Taxa, Multifurcations

@@
   lengths and no other additional information like different transition probabilities of our states.
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %--------------------------------------------------------------------------------------------------- 
+  \section{Definitions}
+    \begin{itemize}
+      \item Parasit - Freilebend
+      \item Multifurkation - binär
+      \item height (min, max, mean), depth of a tree/node (Distanz zur Wurzel vs distanz zum Blatt)
+      \item maximum parsimony
+      \item OTL, OTT, GloBI
+    \end{itemize}
 
@@
     \subsection{Multifurcation}
-      Ein von den Daten beeinflusster Parameter ist die Multifurkation des Baumes, d.h. wie weit sind 
-        wir von einem binären Baum entfehrnt, was hängt mit der stärke der Multifurkation zusammen und 
-        welche Auswirkung hat sie auf unsere Fragestellung. \\
-      In Figure \ref{fig:childrenOfNodes} haben wir die Multifurkation über den gesamten Baum abgebildet,
-        dazu haben wir für jeden Knoten die Anzahl seiner Kinder gezählt und dies als Histogram 
-        geplottet. \\
-      Subfigure \ref{fig:childrenOfNodes_innerNodes} beschränkt sich hierbei nur auf die inner nodes 
-        während Subfigure \ref{fig:childrenOfNodes_allNodes} alle Knoten abbildet. \\
+      One property of the tree is its ridge of multifurcation. A complete kinship tree would be binary, 
+        but since we only work with a synthesis tree of individual trees, this tree is multifurcated. 
+        For a first overview we collected for every node its number of children (degree $-1$), and 
+        plottet this in an histogram. In Figure \ref{fig:childrenOfNodes} you can see how much nodes we 
+        have for every degree. \\
+      \todotext{Subfigure \ref{fig:childrenOfNodes_innerNodes} beschränkt sich hierbei nur auf die inner 
+        nodes während Subfigure \ref{fig:childrenOfNodes_allNodes} alle Knoten abbildet.} \\
       \todo{Welchen der beiden Plots wollen wir nehmen, einer genügt eigentlich:}
-
       \begin{figure}[h!]
@@
       \end{figure}
-
-      Wir haben verschiedene Eigenschaften der Multifurkation untersucht:
+      As you can see, we are very far from a binary tree. Therefore, the impact of multifurcations on 
+        our research question has been investigated:
       \begin{itemize}
@@
 
-      %---------------------------------------------------------------------------------------------------
-      \subsubsection{Poisson regression}
+      "Nested models were compared using likelihood ratio tests, models using different predictors were 
+      compared according to their deviance and AIC."
 
-        \begin{lstlisting}[gobble=8]
-          glm(formula = multifurc ~ 1, family = "poisson", data = inner.taxa)
-        \end{lstlisting}
-        The intercept is $2.821 > 0$ $\Rightarrow$ there is a multifunction.
-        (Intercept: Stärke der Multifurcation) \\
-        Comparing the different kingdoms, we find that multifunctionality is greater in Fungi than in 
-        Chloroplastida than in Metazoa:
-        $$4.0999 (Fungi Intercept) > -0.9132 (Chloroplastida Intercept) > -1.4320 (Metazoa Intercept)$$
-        % Degrees of Freedom: 96010 Total (i.e. Null);  96010 Residual
-        Wir haben außerdem drei komplexitätsstärken von Modellen verglichen bezüglich der höhe und tiefe 
-          des Baums mit dem folgenden Deviance Table:
-
-        \begin{center}
-          \begin{longtable}{ |l|r|r| }
-            \hline
-            Model & Residuals Dev & Deviance Pr \\
-            \hline \hline
-            multifurc $\sim$ kingdom & 7774454 & \\
-            multifurc $\sim$ phylum & 7435700 & 338754 \\
-            multifurc $\sim$ class & 7337241 & 98459 \\
-            \rowcolor{green} multifurc $\sim$ order & 7076068 & 261172 \\
-            \hline \hline \hline
-            multifurc $\sim$ phylum + depth & 7431609 & \\
-            multifurc $\sim$ phylum + max.height & 7375889 & 55721 \\
-            multifurc $\sim$ phylum + min.height & 7233486 & 142403 \\
-            \rowcolor{green} multifurc $\sim$ phylum + mean.height & 7128318 & 105167 \\
-            \hline \hline
-            multifurc ~ phylum * depth & 7335396 & \\
-            multifurc ~ phylum * max.height & 7311241 & 24155 \\
-            multifurc ~ phylum * min.height & 7177002 & 134238 \\
-            \rowcolor{green} multifurc ~ phylum * mean.height & 7020258 & 156745 \\
-            \hline \hline
-            multifurc ~ phylum & 7435700 & \\
-            multifurc ~ phylum + mean.height & 7128318 & 307381 \\
-            \rowcolor{green} multifurc ~ phylum * mean.height & 7020258 & 108061 \\
-            \hline \hline \hline
-            multifurc $\sim$ class + depth & 7334754 & \\
-            multifurc $\sim$ class + max.height & 7275856 & 58898 \\
-            multifurc $\sim$ class + min.height & 7144686 & 131170 \\
-            \rowcolor{green} multifurc $\sim$ class + mean.height & 7055313 & 89374 \\
-            \hline \hline
-            multifurc ~ class * depth & 7250759 & \\
-            multifurc ~ class * max.height & 7187504 & 63256 \\
-            multifurc ~ class * min.height & 7094933 & 92570 \\
-            \rowcolor{green} multifurc ~ class * mean.height & 6965794 & 129139 \\
-            \hline \hline
-            multifurc ~ class & 7337241 & \\
-            multifurc ~ class + mean.height & 7055313 & 281928 \\
-            \rowcolor{green} multifurc ~ class * mean.height & 6965794 & 89518 \\
-            \hline \hline \hline
-            multifurc $\sim$ order + depth & 7027578 & \\
-            multifurc $\sim$ order + max.height & 7005424 & 22154 \\
-            multifurc $\sim$ order + min.height & 6890703 & 114721 \\
-            \rowcolor{green} multifurc $\sim$ order + mean.height & 6815271 & 75432 \\
-            \hline
-          \end{longtable}
-        \end{center}
-        * Residuals: Fehler - wieviele Werte sind nicht gut modelliert. (umso kleiner umso besser - grün) \\
-        * Deviance - Abweichung \\
-
-        \begin{lstlisting}[gobble=8]
-          class * depth / min/max/mean.height: Warning message: glm.fit: fitted rates numerically 0 occurred
-          order * depth / min/max/mean.height: Error: cannot allocate vector of size 2.2 Gb
-        \end{lstlisting}
-
-        \todotext{Nur ein Ausschnitt hier und dann... You can find the whole Deviance Table in the 
-          Appendix...} \\
-        Interpretation: Die Multifurkation ist sehr ungleich verteilt. Daher ist die vorhersage umso 
-          genauer umso kleinere Subtrees wir betrachten. ...
-        \begin{lstlisting}[gobble=8]
-          Model 1: multifurc ~ kingdom
-          Model 2: multifurc ~ phylum
-          Model 3: multifurc ~ class
-          Model 4: multifurc ~ order
-            Resid. Df Resid. Dev  Df Deviance  Pr(>Chi)
-          1    167222    7774454
-          2    167173    7435700  49   338754 < 2.2e-16 ***
-          3    167039    7337241 134    98459 < 2.2e-16 ***
-          4    166352    7076068 687   261172 < 2.2e-16 ***
-        \end{lstlisting}
-        \anmerkung{different parameters for different taxa? (Emanuel)} \\ \\
-
-        \todo{old Stuff:} \\
-        One property of the tree is its ridge of multifurcation. For this we collected for every node its
-          number of children (degree $-1$), and plottet this in an histogram, how much nodes we have for 
-          every degree. Then we tried to find a function which best discribes this behavior. In figure 
-          \ref{fig:HistogramsOfMultifurcations} is this plot shown with three functions, which came 
-          closest to this goal: $\frac{1000000000000000}{x^4}$ (magenta), 
-          $\frac{300000000000}{x^3}$ (red) and $\frac{80000000}{x^2}$ (black). \\
-        \begin{figure}[h]
-          \caption{Histogram of multifurcations and fitting functions}
-          \centering
-          \label{fig:HistogramsOfMultifurcations}
-          \includegraphics[width=0.7\textwidth]{Figures/HistogramsOfMultifurcations.png}
-        \end{figure}
-        From the biology we know, that this multifurcation is very clouded. Some parts of the tree are 
-          well known and others have not been very interesting for the research so far. So we also wanted 
-          to know how the multifurcations behave in some interesting subtrees. \\
-        \anmerkung{do we? Is that really universal knowledge or could it be supported by data or a citation? (Bernhard)} \\
+        % \todo{old Stuff:} \\
+        %   Then we tried to find a function which best discribes this behavior. In figure 
+        %   \ref{fig:HistogramsOfMultifurcations} is this plot shown with three functions, which came 
+        %   closest to this goal: $\frac{1000000000000000}{x^4}$ (magenta), 
+        %   $\frac{300000000000}{x^3}$ (red) and $\frac{80000000}{x^2}$ (black). \\
+        % \begin{figure}[h]
+        %   \caption{Histogram of multifurcations and fitting functions}
+        %   \centering
+        %   \label{fig:HistogramsOfMultifurcations}
+        %   \includegraphics[width=0.7\textwidth]{Figures/HistogramsOfMultifurcations.png}
+        % \end{figure}
+        % From the biology we know, that this multifurcation is very clouded. Some parts of the tree are 
+        %   well known and others have not been very interesting for the research so far. So we also wanted 
+        %   to know how the multifurcations behave in some interesting subtrees. \\
+        % \anmerkung{do we? Is that really universal knowledge or could it be supported by data or a citation? (Bernhard)} \\
 
@@
     \subsection{tag tree}
-      \anmerkung{instead of 'tag tee' simulating stages and transitions between them (Emanuel)} \\
+      \anmerkung{instead of 'tag tee' simulating states and transitions between them (Emanuel)} \\
       At this point we want one fully tagged tree, and one less tagged tree which looks like our real 
@@
 \chapter{Results}
+  Ein großer Punkt in diesem Kapitel ist das Ergebnis der Untersuchung der Datenlage. Wie ist der 
+    Stand? Welchen Einfluss hat das auf unser eigentliches Ergebnis? Was kann man dagegen tun? \\
+  Ansonsten geht es in diesem Kapitel hauptsächlich um die tatsächliche Rekonstruktion der states.
+    Dass heißt zum einen der der inneren Knoten und dadurch der Untersuchung von Origins und Losses
+    und zum anderen der Vorhersage von unbekannten states von Leaf nodes.
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Tree}
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \subsection{Taxa}
+      Die Untersuchung der Taxa der Eukaryoten hat das folgende ergeben:
+      Es gibt 3 Kingdoms: Chloroplastida, Metazoa, Fungi. \\
+      \todo{Hier fehlt nichts. Ref einfügen.} \\
+      Phyla (53): \\
+      Acanthocephala, Amoebozoa, Apicomplexa, Arthropoda, Ascomycota, Bacillariophyta, Basidiomycota, 
+        Brachiopoda, Bryozoa, Chaetognatha, Chlorophyta, Chordata, Chromerida, Chytridiomycota, 
+        Ciliophora, Cnidaria, Colponemidia, Ctenophora, Cycliophora, Echinodermata, Entoprocta, 
+        Entorrhizomycota, Euglenida, Foraminifera, Gastrotricha, Glomeromycota, Gnathostomulida, 
+        Haplosporida, Haptophyta, Hemichordata, Kinorhyncha, Loricifera, Microsporidia, Mollusca, 
+        Myzostomida, Nematoda, Nematomorpha, Nemertea, Onychophora, Orthonectida, Phaeophyceae, 
+        Picozoa, Placozoa, Platyhelminthes, Porifera, Priapulida, Rhodophyta, Rhombozoa, Rotifera, 
+        Streptophyta, Tardigrada, Xanthophyceae \\
+      Wobei von Streptophyta -> Anthocerotophyta, Marchantiophyta, Bryophyta, Tracheophyta als
+        Phylum im Phylum gefunden und nicht einbezogen wurden und Magnoliophyta als Phylum in 
+        Tracheophyta ebenfalls nicht. \\
+      Es fällt auf, dass einige wichtige Phyla fehlen: \todo{Emanuel fragen}. \\
+      Außerdem haben wir 195 Klassen und 924 Ordnungen feststellen können.
+
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \section{Multifurcation}
+
+       %---------------------------------------------------------------------------------------------------
+       %---------------------------------------------------------------------------------------------------
+       \subsection{Poisson regression}
+
+        \begin{lstlisting}[gobble=8]
+          glm(formula = multifurc ~ 1, family = "poisson", data = inner.taxa)
+        \end{lstlisting}
+        The intercept is $2.821 > 0$ $\Rightarrow$ there is a multifunction.
+        (Intercept: Stärke der Multifurcation) \\
+        Comparing the different kingdoms, we find that multifunctionality is greater in Fungi than in 
+        Chloroplastida than in Metazoa:
+        $$4.0999 (Fungi Intercept) > -0.9132 (Chloroplastida Intercept) > -1.4320 (Metazoa Intercept)$$
+        % Degrees of Freedom: 96010 Total (i.e. Null);  96010 Residual
+        Wir haben außerdem drei komplexitätsstärken von Modellen verglichen bezüglich der höhe und tiefe 
+          des Baums mit dem folgenden Deviance Table:
+
+        \begin{center}
+          \begin{longtable}{ |l|r|r| }
+            \hline
+            Model & Residuals Dev & Deviance Pr \\
+            \hline \hline
+            multifurc $\sim$ kingdom & 7774454 & \\
+            multifurc $\sim$ phylum & 7435700 & 338754 \\
+            multifurc $\sim$ class & 7337241 & 98459 \\
+            \rowcolor{green} multifurc $\sim$ order & 7076068 & 261172 \\
+            \hline \hline \hline
+            multifurc $\sim$ phylum + depth & 7431609 & \\
+            multifurc $\sim$ phylum + max.height & 7375889 & 55721 \\
+            multifurc $\sim$ phylum + min.height & 7233486 & 142403 \\
+            \rowcolor{green} multifurc $\sim$ phylum + mean.height & 7128318 & 105167 \\
+            \hline \hline
+            multifurc ~ phylum * depth & 7335396 & \\
+            multifurc ~ phylum * max.height & 7311241 & 24155 \\
+            multifurc ~ phylum * min.height & 7177002 & 134238 \\
+            \rowcolor{green} multifurc ~ phylum * mean.height & 7020258 & 156745 \\
+            \hline \hline
+            multifurc ~ phylum & 7435700 & \\
+            multifurc ~ phylum + mean.height & 7128318 & 307381 \\
+            \rowcolor{green} multifurc ~ phylum * mean.height & 7020258 & 108061 \\
+            \hline \hline \hline
+            multifurc $\sim$ class + depth & 7334754 & \\
+            multifurc $\sim$ class + max.height & 7275856 & 58898 \\
+            multifurc $\sim$ class + min.height & 7144686 & 131170 \\
+            \rowcolor{green} multifurc $\sim$ class + mean.height & 7055313 & 89374 \\
+            \hline \hline
+            multifurc ~ class * depth & 7250759 & \\
+            multifurc ~ class * max.height & 7187504 & 63256 \\
+            multifurc ~ class * min.height & 7094933 & 92570 \\
+            \rowcolor{green} multifurc ~ class * mean.height & 6965794 & 129139 \\
+            \hline \hline
+            multifurc ~ class & 7337241 & \\
+            multifurc ~ class + mean.height & 7055313 & 281928 \\
+            \rowcolor{green} multifurc ~ class * mean.height & 6965794 & 89518 \\
+            \hline \hline \hline
+            multifurc $\sim$ order + depth & 7027578 & \\
+            multifurc $\sim$ order + max.height & 7005424 & 22154 \\
+            multifurc $\sim$ order + min.height & 6890703 & 114721 \\
+            \rowcolor{green} multifurc $\sim$ order + mean.height & 6815271 & 75432 \\
+            \hline
+          \end{longtable}
+        \end{center}
+        * Residuals: Fehler - wieviele Werte sind nicht gut modelliert. (umso kleiner umso besser - grün) \\
+        * Deviance - Abweichung \\
+
+        \begin{lstlisting}[gobble=8]
+          class * depth / min/max/mean.height: Warning message: glm.fit: fitted rates numerically 0 occurred
+          order * depth / min/max/mean.height: Error: cannot allocate vector of size 2.2 Gb
+        \end{lstlisting}
+
+        \todotext{Nur ein Ausschnitt hier und dann... You can find the whole Deviance Table in the 
+          Appendix...} \\
+        Interpretation: Die Multifurkation ist sehr ungleich verteilt. Daher ist die vorhersage umso 
+          genauer umso kleinere Subtrees wir betrachten. ...
+        \begin{lstlisting}[gobble=8]
+          Model 1: multifurc ~ kingdom
+          Model 2: multifurc ~ phylum
+          Model 3: multifurc ~ class
+          Model 4: multifurc ~ order
+            Resid. Df Resid. Dev  Df Deviance  Pr(>Chi)
+          1    167222    7774454
+          2    167173    7435700  49   338754 < 2.2e-16 ***
+          3    167039    7337241 134    98459 < 2.2e-16 ***
+          4    166352    7076068 687   261172 < 2.2e-16 ***
+        \end{lstlisting}
+        \anmerkung{different parameters for different taxa? (Emanuel)} \\ \\
 

### 2018-02-21 code/castor/prepare_resulted_tree.py
put results of castor into the tree

@@ -1,12 +1,11 @@
 import ast
 import csv
 import datetime
+from code.utilities.Helpers import find_element_in_nodelist, print_time
 from time import gmtime, strftime
 
 from Bio import Phylo
 from termcolor import colored
-
-from Helpers import find_element_in_nodelist, print_time
 
 # global variables:
 START_TIME = datetime.datetime.now().replace(microsecond=0)
@@ -19,35 +18,33 @@ def main():
     global nodelist
     
     print(colored("---------------- read tree ----------------", "green"))
-    subtree_path = '../data/subtree/Eukaryota.tre'
+    subtree_path = './data/subtree/Eukaryota.tre'
     tree = Phylo.read(subtree_path, 'newick')
     CURRENT_TIME = print_time(CURRENT_TIME)
 
     print(colored("---------------- read nodelist ----------------", "green"))
-    nodelist_path = '../results/Eukaryota-taxa.csv' 
-    #               0       1   2       3           4       5           6           7
-    # nodelist - [ott_id, name, rank, uniqname, depths, nr_children, originaltag, finaltag]
+    nodelist_path = './data/nodelist/Eukaryota-castor.csv' 
+    #                0    1              2       3       4           5
+    # nodelist    - [id, originaltag, finaltag, depth, heights, nr_children]
     with open(nodelist_path, 'r') as csv_file:
         reader = csv.reader(csv_file, delimiter=',')
+        next(reader, None)      # skip the header
         for row in reader:
             if row != []:
                 ott_id = row[0]
-                originaltag = row[6]
-                finaltag = row[7]
-                print(ott_id, originaltag, finaltag)
+                originaltag = row[1]
+                finaltag = row[2]
                 nodelist.append([ott_id, originaltag, finaltag])
     CURRENT_TIME = print_time(CURRENT_TIME)
 
     print(colored("---------------- prepare tree ----------------", "green"))
     prepare_tree(tree.clade)
     print(colored("---------------- Save tree ----------------", "green"))
-    Phylo.write(tree, 'results/Eukaryota_tree.tre', 'newick')
+    Phylo.write(tree, './results/Eukaryota_tree-castor.tre', 'newick')
     CURRENT_TIME = print_time(CURRENT_TIME)
     print(colored("--------------------------------", "green"))
-    
     return
     
-
 def prepare_tree(subtree):
     """tag all leafs"""
     # Arguments:
@@ -55,9 +52,6 @@ def prepare_tree(subtree):
[…]

### 2018-02-21 code/castor/run_castor.py

@@ -22,11 +22,11 @@ def main():
 
     print('Run castor - Sankoff parsimony - for Eukaryota')
     print(colored("---------------- read tree ----------------", "green"))
-    subtree_path = '../data/subtree/Eukaryota.tre'
+    subtree_path = './data/subtree/Eukaryota.tre'
     tree = Phylo.read(subtree_path, 'newick')
     CURRENT_TIME = print_time(CURRENT_TIME)
     print(colored("---------------- read nodelist ----------------", "green"))
-    nodelist_path = '../data/nodelist/Eukaryota.csv' 
+    nodelist_path = './data/nodelist/Eukaryota.csv' 
     #                0    1              2       3       4           5
     # nodelist    - [id, originaltag, finaltag, depth, heights, nr_children]
     nodelist = []
@@ -46,7 +46,7 @@ def main():
     sankoff_parsimony(tree, nodelist)
     CURRENT_TIME = print_time(CURRENT_TIME)
     print(colored("---------------- Save nodelist ----------------", "green"))
-    nodelist_path = '../data/nodelist/Eukaryota-castor.csv' 
+    nodelist_path = './data/nodelist/Eukaryota-castor.csv' 
     header = ['ott_id', 'originaltag', 'finaltag', 'depth', 'heights', 'nr_children']
     with open(nodelist_path, 'w') as nodelist_file:
         writer = csv.writer(nodelist_file, delimiter=',')

### 2018-02-21 code/metadata/build_nodelist.py

@@ -7,10 +7,10 @@ from time import gmtime, strftime
 from Bio import Phylo
 from termcolor import colored, cprint
 
-# path_freelivings = "../data/interaction_data/reduced_freelivings.csv"
-# path_parasites = "../data/interaction_data/reduced_parasites.csv"
-path_freelivings = "../data/interaction_data/freelivings.csv"
-path_parasites = "../data/interaction_data/parasites.csv"
+# path_freelivings = "./data/interaction_data/reduced_freelivings.csv"
+# path_parasites = "./data/interaction_data/reduced_parasites.csv"
+path_freelivings = "./data/interaction_data/freelivings.csv"
+path_parasites = "./data/interaction_data/parasites.csv"
 
 # global variables:
 START_TIME = datetime.datetime.now().replace(microsecond=0)
@@ -47,7 +47,7 @@ def main():
     parasites = read_tags(path_parasites)
     CURRENT_TIME = print_time(CURRENT_TIME)
     print(colored("---------------- read tree ----------------", "green"))
-    subtree_path = '../data/subtree/Eukaryota.tre'
+    subtree_path = './data/subtree/Eukaryota.tre'
     print("Build nodelist for: Eukaryota")
     tree = Phylo.read(subtree_path, 'newick')
     print(colored("---------------- tag tree ----------------", "green"))
@@ -102,7 +102,7 @@ def fill_tree_with_tags(subtree, depth):
         heights = [min_heigth + 1, max_heigth + 1, mean_heigth]
         nodelist[current_list_index][4] = heights
     # -------------------------------------------------
-    csv_title = '../data/nodelist/Eukaryota.csv' 
+    csv_title = './data/nodelist/Eukaryota.csv' 
     nodelist_file = open(csv_title, 'a')
     writer = csv.writer(nodelist_file)
     writer.writerow((nodelist[current_list_index])) 

### 2018-02-21 code/utilities/Helpers.py

@@ -9,7 +9,10 @@ TAGS = [0, 1]
 
 def find_element_in_nodelist(id_name, nodelist):
     """finds id in nodelist and returns the element"""
-    return nodelist[int(id_name.split("$")[1])]
+    element = nodelist[int(id_name.split("$")[1])]
+    if element[0] != id_name.split("$")[1]:
+        print(id_name, "!=", element)
+    return element
 
 def print_time(time_old):
     time_new = datetime.datetime.now().replace(microsecond=0)

### 2018-02-24 Paper - Latex/Paper - Skizze - v2.tex
Paper - Results - Results of castor - biological view

@@
       To simulate our real tree we save for every node an empty placeholde except for some leaf nodes.
-      There we save the tags again. The amount of these unknown information is one parameter, which we
+      There we save the states again. The amount of these unknown information is one parameter, which we
       got from our real tree. Or which we can change to \todo{...}
@@
         Für jeden Knoten gilt, wenn seine Kinder schon Information enthalten, dann bilde die Schnittmenge 
-        der Tags und schreibe diese als Information in den aktuellen Knoten. Ist die Schnittmenge leer, 
-        dann schreibe die Vereinigung aller möglichen Tags in den Knoten. Für alle Kinder, die noch keine 
+        der states und schreibe diese als Information in den aktuellen Knoten. Ist die Schnittmenge leer, 
+        dann schreibe die Vereinigung aller möglichen states in den Knoten. Für alle Kinder, die noch keine 
         Information haben, führe diesen Schritt erst für diese aus.
         Schritt zwei geht von den Kindern der Wurzel bis zu den Vätern der Blätter. Jeder Knoten bekommt 
-        einen zweiten Tag, der sich aus der Vereinigung des Tags des Vaterknoten und der Geschwisterknoten
-        zusammensetzt. Ist diese leer, bekommt der Knoten wieder die Vereinigung aller Tags, also $\{FL,P\}$ als Tag.
+        einen zweiten Tag, der sich aus der Vereinigung des states des Vaterknoten und der Geschwisterknoten
+        zusammensetzt. Ist diese leer, bekommt der Knoten wieder die Vereinigung aller states, also $\{FL,P\}$ als Tag.
 
@@
         Geschwisterknoten zuerst der Schnitt gebildet, und danach vom Ergebnis nochmal mit dem Vaterknoten zusammen.
-        (Immer wenn der Schnitt leer ist, ist das Ergebnis die Vereinigung aller Tags, also $\{FL,P\}$. Auch im folgenden...)
+        (Immer wenn der Schnitt leer ist, ist das Ergebnis die Vereinigung aller states, also $\{FL,P\}$. Auch im folgenden...)
         2. Version: Es wird nur der erste Tag vom Vaterknoten genutzt. Er wird zusammen mit den 
-        Geschwistertags genommen und direkt ein Schnitt aller Mengen gebildet.
-        3. Version: Es werden alle vorherigen Tags vom Vater genutzt und von diesen ein Schnitt gebildet.
-        Das selbe gilt für die Geschwistertags. Und dann wird ein dritter Schnitt zwischend en Ergebnissen gebildet.
-        4. Version: Es werden alle Tags genutzt und direkt in einem Schnitt zusammengenommen.
+        Geschwisterstates genommen und direkt ein Schnitt aller Mengen gebildet.
+        3. Version: Es werden alle vorherigen states vom Vater genutzt und von diesen ein Schnitt gebildet.
+        Das selbe gilt für die Geschwisterstates. Und dann wird ein dritter Schnitt zwischend en Ergebnissen gebildet.
+        4. Version: Es werden alle states genutzt und direkt in einem Schnitt zusammengenommen.
 
-        Der Finale Schritt traversiert nochmal über den Baum und Bildet aus den zwei Tags pro Knoten einen finalen
-        Tag, indem wieder der Schnitt der beiden Tags das Ergebnis ist.
+        Der Finale Schritt traversiert nochmal über den Baum und Bildet aus den zwei states pro Knoten einen finalen
+        Tag, indem wieder der Schnitt der beiden states das Ergebnis ist.
 
@@
     Dass heißt zum einen der der inneren Knoten und dadurch der Untersuchung von Origins und Losses
-    und zum anderen der Vorhersage von unbekannten states von Leaf nodes.
+    und zum anderen der Vorhersage von unbekannten states von Leaf nodes. \\
+  Und natürlich dem Ergebnis der Simulation.
 
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Tree}
+  \section{Metadata analysis}
+
     %---------------------------------------------------------------------------------------------------
@@
         Tracheophyta ebenfalls nicht. \\
-      Es fällt auf, dass einige wichtige Phyla fehlen: \todo{Emanuel fragen}. \\
       Außerdem haben wir 195 Klassen und 924 Ordnungen feststellen können.
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Influence of different parameters}
+  \section{Results of castor}
+
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \subsection{Biological view}
+
+      \todo{Castor replaces originaltags with finaltags. There are 82 originaltags != finaltag.} \\ \\
+
+      We picked a few phyla to evaluate the results from the biological point of view. \\
+      Table \ref{table:phylum leaf nodes states} shows some known phyla: Chordata, Nematoda, 
+        Platyhelminthes and Apicomplexa \\
+      As we know \todo{ref einfügen} the Chordata are full of free-living species and there are only a 
+        few parasites. The algorithm reflects this. We started with 99.83\% free-living species and 
+        predicted 99.94\% species as parasites \todo{(inklusive all known nodes)}. Only 0.06\% were 
+        predicted as parasites. These few parasites are mostly breeding parasites (brood parasitism) and 
+        some individual errors from the GloBI database. \\
+      Same observation but with less free-livings is the Apicomplexa Phylum. Here we have only a few 
+        free-livings \todo{ref einfügen}. And as we see, we had good start data and predicted 00.95\% as 
+        parasites. \\
+      For the Platyhelminthes the literature says that there are mostly all Platyhelminthes parasites
+        \todo{ref einfügen}. But at the end we predicted 4.18\% as free-living. The class Seriata is the 
+        reason for the most of free-livings in this phylum. These are partly free-living flatworms, so 
+        the prediction looks right. \\
+        \todotext{ Wiki: \\
+        *The Seriata are an order of turbellarian flatworms.[1][2] \\
+        They are found in both freshwater and marine environments, and also include a number of species 
+        found in damp terrestrial conditions. Most are free-living, but the group includes the genus 
+        Bdelloura, which lives comensally on the gills of horseshoe crabs. Seriatans are distinguished 
+        from other related groups by the presence of a folded pharynx and of a number of diverticula 
+        arising from the intestine. The intestine itself may be either simple or branched.[3]}
+
+      With the Nematoda it looks very different.  In the Nematoda its much worse. Here speaks the 
+        literature of \todo{x percent} free-living, but we found only 2.63\% of them. The problem at 
+        this point, however, is obvious: The parasites have been much more studied and thus we start 
+        with only 0.63\% free-living species. Against such a shifted data situation, the algorithm is 
+        powerless.
+
+      \begin{table}
+        \begin{center}
+          \begin{tabular}{ |l|r||r|r||r|r|r|r|r|r| }
+            \hline
+            & & \multicolumn{2}{c}{original states} & \multicolumn{6}{c}{final states} \\
+            Phylum & \# nodes & (FL) & (P) 
+              & 0 (FL) & 0.4 & 0.5 & 0.667 & 0.75 & 1 (P) \\
+            \hline \hline
+            Chordata & 91785 & 10451 & 18 
+              & 91734 & 0 & 0 & 0 & 0 & 51 \\
+            & & 99.83\% & 0.49\%
+              & 99.94\% & & & & & 0.06\% \\ \hline
+            Nematoda & 30127 & 21 & 3289 
+              & 791 & 0 & 1017 & 0 & 0 & 28319 \\
+            & & 0.63\% & 99.37\%
+              & 2.63\% & & 3.38\% & & & 94\% \\ \hline
+            Platyhelminthes & 22683 & 7 & 7086 
+              & 949 & 0 & 151 & 0 & 0 & 21583 \\
+            & & 0.1\% & 99.9\%
+              & 4.18\% & & 0.67\% & & & 95.15\% \\ \hline
+            Apicomplexa & 1863 & 1 & 255 
+              & 1 & 0 & 0 & 0 & 0 & 1862 \\
+            & & 0.39\% & 99.61\%
+              & 0.05\% & & & & & 99.95\% \\
+            \hline \hline
+            Anthropoda & 1198981 & 18912 & 11141 
+              & 1099509 & 1313 & 22478 & 4176 & 1665 & 70223 \\
+            & & 62.93\% & 37.07\%
+              & 91.7\% & 0.11\% & 1.87\% & 0.35\% & 0.14\% & 5.86\% \\
+            \hline
+          \end{tabular} 
+        \end{center}
+        \caption{Phylum (leaf nodes)}
+        \label{table:phylum leaf nodes states} 
+      \end{table}
+
+      \anmerkungstext{Das sind schonmal vier große Kontraste, wenn dann noch Zeit bleibt, die 
+        schwirigen... Arthropoden, Fungi, Pflanzen... (Emanuel)} \\
+
+      \begin{table}
+        \begin{center}
+          \begin{tabular}{ |l|r||r|r||r|r|r|r|r|r|r|r| }
+            \hline
+            & & \multicolumn{2}{c}{original states} & \multicolumn{8}{c}{final states} \\
+            Kingdom & \# nodes & (FL) & (P) 
+              & 0 (FL) & 0.25 & 0.333 & 0.4 & 0.667 & 0.75 & 1 (P) \\
+            \hline \hline
+            none & 84456 & 45 & 529 
+              & 15035 & 243 & 25910 & 0 & 8764 & 6183 & 0 & 28140 \\
+            Fungi & 324105 & 577 & 2983
+              & 39088 & 0 & 0 & 0 & 5858 & 0 & 0 & 274803 \\
+            Chloroplastida & 460457 & 3519 & 77
+              & 454211 & 0 & 0 & 0 & 4688 & 0 & 0 & 1558 \\
+            Metazoa & 1670956 & 30758 & 22373
+              & 1485749 & 0 & 0 & 1313 & 29002 & 5102 & 1957 & 147833 \\
+            \hline  
+          \end{tabular}
+        \end{center}
+        \caption{Kingdom (inkl internal nodes)}
+      \end{table}
+
+      \begin{table}
+        \begin{center}
+          \begin{tabular}{ |l|r||r|r||r|r|r|r|r|r| }
+            \hline
+            & & \multicolumn{2}{c}{original states} & \multicolumn{6}{c}{final states} \\
+            Phylum & \# nodes & (FL) & (P) 
+              & 0 (FL) & 0.4 & 0.5 & 0.667 & 0.75 & 1 (P) \\
+            \hline \hline
+            Chordata & 122546 & 10451 & 18 
+              & 122473 & 0 & 0 & 0 & 0 & 73 \\
+            Nematoda & 33564 & 21 & 3289 
+              & 846 & 0 & 1133 & 0 & 0 & 31585 \\
+            Platyhelminthes & 27142 & 7 & 7086 
+              & 1010 & 0 & 175 & 0 & 0 & 25957 \\
+            Apicomplexa & 2102 & 1 & 255 
+              & 1 & 0 & 0 & 0 & 0 & 2101 \\
+            \hline
+            Anthropoda & 1319460 & 18912 & 11141 
+              & 1207204 & 1313 & 25499 & 4852 & 1957 & 78635 \\
+            \hline
+          \end{tabular}
+        \end{center}
+        \caption{Phylum (inkl internal nodes)}
+      \end{table}
+
+      \begin{table}
+        \begin{center}
+          \begin{tabular}{ |l|r||r|r||r|r|r|r|r|r|r|r| }
+            \hline
+            & & \multicolumn{2}{c}{original states} & \multicolumn{8}{c}{final states} \\
+            Kingdom & \# nodes & (FL) & (P) 
+              & 0 (FL) & 0.25 & 0.333 & 0.4 & 0.5 & 0.667 & 0.75 & 1 (P) \\
+            \hline \hline
+            none & 75446 & 45 & 529 
+              & 13426 & 220 & 24082 & 0 & 7792 & 5302 & 0 & 24493 \\
+            Fungi & 31457 & 577 & 2983
+              & 38520 & 0 & 0 & 0 & 5723 & 0 & 0 & 266463 \\
+            Chloroplastida & 416478 & 3519 & 77
+              & 410795 & 0 & 0 & 0 & 4182 & 0 & 0 & 1501 \\
+            Metazoa & 1491012 & 30758 & 22373
+              & 1328135 & 0 & 0 & 930 & 25535 & 4423 & 1665 & 130324 \\
+            \hline  
+          \end{tabular}
+        \end{center}
+        \caption{Kingdom (leaf nodes)}
+      \end{table}
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Results of simulation}
+
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \subsection{Influence of different parameters}
 

### 2018-02-24 code/evaluation/analyse_output.R

@@ -1,0 +1,87 @@
+library(data.table)
+# library(ggplot2)
+
+format(Sys.time(), "%a %b %d %X %Y")
+
+all.taxa <- fread("../../results/Eukaryota-taxa.csv")
+
+### right mode for all
+all.taxa$kingdom <- as.factor(all.taxa$kingdom)
+all.taxa$phylum <- as.factor(all.taxa$phylum)
+all.taxa$class <- as.factor(all.taxa$class)
+all.taxa$order <- as.factor(all.taxa$order)
+
+
+heights <- do.call("rbind", strsplit(gsub("\\[|\\]", "", all.taxa$heights), ", "))
+
+heights <- as.data.frame(apply(heights, 2, as.numeric))
+
+names(heights) <- c("min.height", "max.height", "mean.height")
+
+all.taxa <- cbind(all.taxa, heights)
+
+## list all Kingdoms, Phyla:
+# table(all.taxa$kingdom)
+# table(all.taxa$phylum)
+
+## which Phylum in which Kingdom:
+# table(all.taxa$kingdom, all.taxa$phylum)
+
+### all nodes sorted by rank
+# table(all.taxa$rank)[order(table(all.taxa$rank))]
+
+print('------------all.taxa$originaltag------------------')
+table(all.taxa$originaltag)
+print('------------all.taxa$finaltag------------------')
+table(all.taxa$finaltag)
+
+table(all.taxa[all.taxa$finaltag+1 != all.taxa$originaltag, ]$kingdom)
+print('--------------------------------------------------')
+
+leaf.taxa <-  all.taxa[all.taxa$nr_children==0, ]
+extendedLeaf.taxa <- all.taxa[all.taxa$nr_children<2 & min.height==max.height, ]
+inner.taxa <- all.taxa[all.taxa$nr_children>1 | (all.taxa$nr_children==1 & min.height!=max.height), ]
+
+print('----------------------- leaf.taxa$rank ---------------------------')
+leaf.taxa <- as.data.frame(leaf.taxa)
+# table(leaf.taxa$rank)[order(table(leaf.taxa$rank))]
+print('----------------------- extendedLeaf.taxa$rank ---------------------------')
+extendedLeaf.taxa <- as.data.frame(extendedLeaf.taxa)
+# table(extendedLeaf.taxa$rank)[order(table(extendedLeaf.taxa$rank))]
+print('----------------------- inner.taxa$rank ---------------------------')
[…]

### 2018-02-24 code/metadata/analyse_input.R

@@ -48,7 +48,6 @@ table(all.taxa$rank)[order(table(all.taxa$rank))]
 # table(all.taxa[all.taxa$nr_children==1 & all.taxa$max.height==2, "finaltag"])
 print('--------------------------------------------------')
 
-
 ## pdf(path, width=8, height=6)
 # ggplot(all.taxa, aes(nr_children)) +
 #     geom_histogram() +
@@ -101,10 +100,10 @@ phylum.furc.mod <- glm(multifurc~phylum, data=inner.taxa,
 class.furc.mod <- glm(multifurc~class, data=inner.taxa,
                         family="poisson")
 
-order.furc.mod <- glm(multifurc~order, data=inner.taxa,
-                        family="poisson")
+# order.furc.mod <- glm(multifurc~order, data=inner.taxa,
+#                         family="poisson")
 
-anova(kingdom.furc.mod, phylum.furc.mod, class.furc.mod, order.furc.mod, test="LRT")
+# anova(kingdom.furc.mod, phylum.furc.mod, class.furc.mod, order.furc.mod, test="LRT")
 # anova(kingdom.furc.mod, phylum.furc.mod, test="LRT")
 
 
@@ -138,56 +137,67 @@ anova(kingdom.furc.mod, phylum.furc.mod, class.furc.mod, order.furc.mod, test="L
 # phylumTmeanHeight.furc.mod <- glm(multifurc~phylum*mean.height, data=inner.taxa,
 #                    family="poisson")
 
-# anova(phylumTmaxHeightt.furc.mod, phylumTdepth.furc.mod, phylumTminHeight.furc.mod, phylumTmeanHeight.furc.mod, test="LRT")
+# anova(phylumTdepth.furc.mod, phylumTmaxHeightt.furc.mod, phylumTminHeight.furc.mod, phylumTmeanHeight.furc.mod, test="LRT")
 
 # print('-------------------phylum mean.height-----------------------')
 
 # anova(phylum.furc.mod, phylumPmeanHeight.furc.mod, phylumTmeanHeight.furc.mod, test="LRT")
 
-print('-------------------order + depth / min/max/mean.height-----------------------')
+print('-------------------class + depth / min/max/mean.height-----------------------')
 
-orderPdepth.furc.mod <- glm(multifurc~order+depth, data=inner.taxa,
+classPdepth.furc.mod <- glm(multifurc~class+depth, data=inner.taxa,
                    family="poisson")
 
[…]

### 2018-02-25 code/evaluation/count_origins_and_losses.py
count origins and losses

@@ -1,0 +1,81 @@
+import sys
+
+from Bio import Phylo
+from termcolor import colored
+
+# input arguments
+args = sys.argv
+
+# values for simulation:
+subtree_ott = sys.argv[1]
+
+# subtree_otts = [['ott304358', 'Eukaryota'], ['ott361838', 'Chloroplastida'],
+#         ['ott691846', 'Metazoa'], ['ott395057', 'Nematoda'], ['ott801601', 'Vertebrata'],
+#         ['ott229562', 'Tetrapoda'], ['ott244265', 'Mammalia'], ['ott913935', 'Primates'],
+#         ['ott770311', 'Hominidae'], ['ott352914', 'Fungi'], ['ott844192', 'Bacteria'],
+#         ['ott996421', 'Archaea']]
+
+# global variables
+nr_internal_nodes = 0
+nr_leaf_nodes = 0
+origins = 0
+losses = 0
+
+def main():
+    print(colored("---------------- read tree ----------------", "green"))
+    tree = Phylo.read('./results/Eukaryota_tree-castor.tre', 'newick')
+    
+    print(colored("---------------- find subtrees ----------------", "green"))
+    find_subtree(tree.clade)
+    return
+
+def find_subtree(subtree):
+    # global subtree_ott
+    global nr_internal_nodes
+    global nr_leaf_nodes
+    global origins
+    global losses
+
+    if not subtree.is_terminal():
+        # subtree.name = ott $ index $ originaltag or $(finaltag)
+        node = subtree.name.split('$')
+        if node[0] == subtree_ott:
+            print('Rootnode of this subtree has state: ', node[2])
+            count_origins_and_losses(subtree, get_state(node[2]))
+            print(subtree_ott, 'has', nr_internal_nodes, 'internal nodes and', nr_leaf_nodes, 'leaf_nodes')
+            print(subtree_ott, 'has', origins, 'origins (FL -> P) and', losses, 'losses (P -> FL)')
+        for clade in subtree.clades:
+            find_subtree(clade)
+    return
+
+def count_origins_and_losses(subtree, father_state):
+    global nr_internal_nodes
+    global nr_leaf_nodes
+    global origins
+    global losses
+
+    node = subtree.name.split('$')
+    node_state = get_state(node[2])
+    if node_state != father_state:
+        if father_state == 0:
+            origins += 1        # FL -> P
+        else:
+            losses += 1         # P -> FL
+
+    if subtree.is_terminal():
+        nr_leaf_nodes += 1
[…]

### 2018-02-25 code/castor/prepare_resulted_tree.py
some bugfixes

@@ -53,10 +53,10 @@ def prepare_tree(subtree):
     #   nodelist - [ott_id, originaltag, finaltag]
     element = find_element_in_nodelist(subtree.name, nodelist)
     if subtree.is_terminal():
-        if element[1] != '':
-            subtree.name = subtree.name + '$' + element[1]
-        else:
+        if element[1] == '' or element[1] == 'NA':
             subtree.name = subtree.name + '$(' + element[2] + ')'
+        else:
+            subtree.name = subtree.name + '$' + element[1]
     else:
         subtree.name = subtree.name + '$(' + element[2] + ')'
         for clade in subtree.clades:

### 2018-02-25 code/evaluation/count_origins_and_losses.py

@@ -40,42 +40,51 @@ def find_subtree(subtree):
         # subtree.name = ott $ index $ originaltag or $(finaltag)
         node = subtree.name.split('$')
         if node[0] == subtree_ott:
+            # Phylo.draw(subtree)
             print('Rootnode of this subtree has state: ', node[2])
-            count_origins_and_losses(subtree, get_state(node[2]))
+            print(colored("---------------- count origins and losses ----------------", "green"))
+            count_origins_and_losses(subtree, get_state(node[2]), False)
             print(subtree_ott, 'has', nr_internal_nodes, 'internal nodes and', nr_leaf_nodes, 'leaf_nodes')
             print(subtree_ott, 'has', origins, 'origins (FL -> P) and', losses, 'losses (P -> FL)')
         for clade in subtree.clades:
             find_subtree(clade)
     return
 
-def count_origins_and_losses(subtree, father_state):
+def count_origins_and_losses(subtree, father_state, found):
     global nr_internal_nodes
     global nr_leaf_nodes
     global origins
     global losses
 
+    new_found = False
+
     node = subtree.name.split('$')
     node_state = get_state(node[2])
-    if node_state != father_state:
-        if father_state == 0:
-            origins += 1        # FL -> P
-        else:
-            losses += 1         # P -> FL
+    if not  found:
+        if node_state != father_state:
+            print(node_state, father_state)
+            if father_state == 0:
+                origins += 1        # FL -> P
+                new_found = True
+            else:
+                losses += 1         # P -> FL
+                new_found = True
 
     if subtree.is_terminal():
         nr_leaf_nodes += 1
     else:
         nr_internal_nodes += 1
+        found = False
         for clade in subtree.clades:
-            clade = count_origins_and_losses(clade, node_state)
-    return subtree
+            found = count_origins_and_losses(clade, node_state, found)
+    return new_found
 
 def get_state(state):
     if state.startswith('('):
-        # finaltag
-        return int(state[1:-1])
+        # finaltag:     0 = FL, 1 = P
+        return float(state[1:-1])
     else:
-        # originaltag
-        return int(state) -1
+        # originaltag:  1 = FL, 2 = P
+        return float(state) -1
 
 main()

### 2018-02-25 Paper - Latex/Paper - Skizze - v2.tex
Paper - Results - Lesbarkeit der Tabellen...

@@
 \hfuzz=\maxdimen \tolerance=10000 \hbadness=10000
+% \usepackage[showframe=true]{geometry}
 
@@
         \begin{center}
-          \begin{tabular}{ |l|r||r|r||r|r|r|r|r|r| }
-            \hline
-            & & \multicolumn{2}{c}{original states} & \multicolumn{6}{c}{final states} \\
-            Phylum & \# nodes & (FL) & (P) 
-              & 0 (FL) & 0.4 & 0.5 & 0.667 & 0.75 & 1 (P) \\
+          \hspace*{-1cm}\begin{tabular}{ |l|r||r|r||r|r|r|r|r|r| }
+            \hline
+            & & \multicolumn{2}{c||}{original states} & \multicolumn{6}{c|}{final states} \\
+            Phylum & \# nodes & FL & P
+              & 0 (FL) & 0.4 & 0.5 & 0.67 & 0.75 & 1 (P) \\
             \hline \hline
@@
         \begin{center}
-          \begin{tabular}{ |l|r||r|r||r|r|r|r|r|r|r|r| }
-            \hline
-            & & \multicolumn{2}{c}{original states} & \multicolumn{8}{c}{final states} \\
-            Kingdom & \# nodes & (FL) & (P) 
-              & 0 (FL) & 0.25 & 0.333 & 0.4 & 0.667 & 0.75 & 1 (P) \\
+          \hspace*{-2cm}\begin{tabular}{ |l|r||r|r||r|r|r|r|r|r|r|r| }
+            \hline
+            & & \multicolumn{2}{c||}{original states} & \multicolumn{8}{c|}{final states} \\
+            Kingdom & \# nodes & FL & P
+              & 0 (FL) & 0.25 & 0.33 & 0.4 & 0.5 & 0.67 & 0.75 & 1 (P) \\
             \hline \hline
@@
             \hline
-            & & \multicolumn{2}{c}{original states} & \multicolumn{6}{c}{final states} \\
-            Phylum & \# nodes & (FL) & (P) 
-              & 0 (FL) & 0.4 & 0.5 & 0.667 & 0.75 & 1 (P) \\
+            & & \multicolumn{2}{c||}{original states} & \multicolumn{6}{c|}{final states} \\
+            Phylum & \# nodes & FL & P
+              & 0 (FL) & 0.4 & 0.5 & 0.67 & 0.75 & 1 (P) \\
             \hline \hline
@@
         \begin{center}
-          \begin{tabular}{ |l|r||r|r||r|r|r|r|r|r|r|r| }
-            \hline
-            & & \multicolumn{2}{c}{original states} & \multicolumn{8}{c}{final states} \\
-            Kingdom & \# nodes & (FL) & (P) 
-              & 0 (FL) & 0.25 & 0.333 & 0.4 & 0.5 & 0.667 & 0.75 & 1 (P) \\
+          \hspace*{-2cm}\begin{tabular}{ |l|r||r|r||r|r|r|r|r|r|r|r| }
+            \hline
+            & & \multicolumn{2}{c||}{original states} & \multicolumn{8}{c|}{final states} \\
+            Kingdom & \# nodes & FL & P
+              & 0 (FL) & 0.25 & 0.33 & 0.4 & 0.5 & 0.67 & 0.75 & 1 (P) \\
             \hline \hline

### 2018-02-25 code/evaluation/count_origins_and_losses.py
add round to origins -> less origins

@@ -82,9 +82,11 @@ def count_origins_and_losses(subtree, father_state, found):
 def get_state(state):
     if state.startswith('('):
         # finaltag:     0 = FL, 1 = P
-        return float(state[1:-1])
+        # possible tags: 0, 0.333, 0.4, 0.5, 0.667, 0.75, 1
+        # rounded to:    0  0      0    0    1      1     1
+        return round(float(state[1:-1]))
     else:
         # originaltag:  1 = FL, 2 = P
-        return float(state) -1
+        return round(float(state) -1)
 
 main()

### 2018-02-25 Paper - Latex/Paper - Skizze - v2.tex
Paper - Results - Origins and Losses

@@
       Table \ref{table:phylum leaf nodes states} shows some known phyla: Chordata, Nematoda, 
-        Platyhelminthes and Apicomplexa \\
+        Platyhelminthes and Apicomplexa. \\
       As we know \todo{ref einfügen} the Chordata are full of free-living species and there are only a 
@@
         with only 0.63\% free-living species. Against such a shifted data situation, the algorithm is 
-        powerless.
+        powerless. And yet the percentage has increased.
 
@@
             \hline \hline
-            Anthropoda & 1198981 & 18912 & 11141 
+            Arthropoda & 1198981 & 18912 & 11141 
               & 1099509 & 1313 & 22478 & 4176 & 1665 & 70223 \\
@@
             \hline
-            Anthropoda & 1319460 & 18912 & 11141 
+            Arthropoda & 1319460 & 18912 & 11141 
               & 1207204 & 1313 & 25499 & 4852 & 1957 & 78635 \\
@@
       \end{table}
+
+\newpage
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \subsection{Origins and Losses}
+
+      Sara B. Weinstein and Armand M. Kuris have been searching for origins of parasitism in Animalia 
+        \cite{Weinstein2016}. They identified 223 parasitic origins: 223 in Metazoa $\supset$ 143 in 
+        Arthropoda $\supset$ 87 in Insecta. \\
+      This has led us to count the origins and losses of parasitism in our investigation as well. \\
+      We count only one origin / loss in a parent node with different children's nodes. \\
+      Here we have encountered a problem: The Castor algorithm gives us probabilities for states. That 
+        means there are also nodes with state like 0.3 or 0.5. So how do you count? Our solution was, 
+        to round these values. We have to say that we round 0.5 to 0.
+
+      \begin{table} [h]
+        \begin{center}
+          \begin{tabular}{ |l|r|r||r|r|r| }
+            \hline
+            Domain / Kingdom & \# internal & \# leaf & Rootnode & \multicolumn{2}{c|}{without and with rounding} \\ 
+            / Phylum / Class & \multicolumn{2}{c||}{nodes} & state & \# origins & \# losses \\
+            & & & state & (FL -> P) & (P -> FL) \\
+            \hline \hline
+            Eukaryota & 241974 & 2293463 & 1.0 & 415 & 495 \\
+            & & & P & 462 & 369 \\
+            \hline \hline
+            Metazoa & 179944 & 1491012 & 0.5 & 294 & 206 \\
+            & & & & 321 & 129 \\ \hline
+            Fungi & 9534 & 314571 & 0.5 & 80 & 263 \\
+            & & & & 97 & 222 \\ \hline
+            Chloroplastida & 43486 & 412434 & 0.0 & 40 & 7 \\
+            & & & FL & 42 & 2 \\
+            \hline \hline            
+            Arthropoda & 120479 & 1198981 & 0.0 & 260 & 170 \\
+            & & & FL & 281 & 108 \\ \hline
+            Apicomplexa & 239 & 1863 & 1.0 & 0 & 1 \\
+            & & & P & 0 & 1 \\ \hline
+            Nematoda & 3437 & 30127 & 1.0 & 0 & 17 \\
+            & & & P & 2 & 11 \\ \hline
+            Chordata & 30761 & 91785 & 0.0 & 12 & 1 \\
+            & & & FL & 12 & 1 \\ \hline
+            Platyhelminthes & 4459 & 22683 & 1.0 & 0 & 5 \\
+            & & & P & 0 & 5 \\ \hline
+            \hline \hline            
+            Insecta & 91256 & 989572 & 0.0 & 234 & 107 \\
+            & & & FL & 245 & 77 \\ 
+            \hline  
+          \end{tabular}
+        \end{center}
+        \caption{Origins and losses}
+        \label{table:origins and losses} 
+      \end{table}
+
+      In Table \ref{table:origins and losses} we can see, that we found some more origins than Weinstein 
+        and on top of that some losses. \\ \\
+
+      Lets have a look at the same phyla as in the section before: Chordata, Nematoda, 
+        Platyhelminthes and Apicomplexa. \\
+      Chordata are full of free-living species and so we see only a few origins of parasitism. The root
+      and mostly all species are predicted as free-living. \\
+      In Apicomplexa and the Platyhelminthes are looking fine too. Our algorithm gives us only one loss 
+        of parasitism in Apicomplexa and five in the Platyhelminthes. They are both from the root over 
+        mostly all species predicted as parasites. \\
+      Nematoda is again full of problems. The rootnode is predicted as a parasite and so we have more 
+        losses of parasitism for the less information of free-living species in this phylum. The rest 
+        is parasitic \\
+
+      \begin{lstlisting}[gobble=6]
+        # possible tags: 0, 0.333, 0.4, 0.5, 0.667, 0.75, 1
+        # rounded to:    0  0      0    0    1      1     1
+        if node_state != father_state:
+          if father_state == 0:
+              origins += 1        # FL -> P
+              new_found = True
+          else:
+              losses += 1         # P -> FL
+              new_found = True
+      \end{lstlisting}
+
+      \todo{without rounding change else: to elif $father_state == 1$}
 

### 2018-02-25 Paper - Latex/Paper - Skizze - v2.tex
count updates

@@
             \hline \hline
-            Eukaryota & 241974 & 2293463 & 1.0 & 415 & 495 \\
+            Eukaryota & 241974 & 2293463 & 1.0 & 415 & 363 \\
             & & & P & 462 & 369 \\
             \hline \hline
-            Metazoa & 179944 & 1491012 & 0.5 & 294 & 206 \\
+            Metazoa & 179944 & 1491012 & 0.5 & 294 & 123 \\
             & & & & 321 & 129 \\ \hline
-            Fungi & 9534 & 314571 & 0.5 & 80 & 263 \\
+            Fungi & 9534 & 314571 & 0.5 & 80 & 222 \\
             & & & & 97 & 222 \\ \hline
-            Chloroplastida & 43486 & 412434 & 0.0 & 40 & 7 \\
+            Chloroplastida & 43486 & 412434 & 0.0 & 40 & 2 \\
             & & & FL & 42 & 2 \\
             \hline \hline            
-            Arthropoda & 120479 & 1198981 & 0.0 & 260 & 170 \\
+            Arthropoda & 120479 & 1198981 & 0.0 & 260 & 102 \\
             & & & FL & 281 & 108 \\ \hline
@@
             & & & P & 0 & 1 \\ \hline
-            Nematoda & 3437 & 30127 & 1.0 & 0 & 17 \\
+            Nematoda & 3437 & 30127 & 1.0 & 0 & 11 \\
             & & & P & 2 & 11 \\ \hline
@@
             \hline \hline            
-            Insecta & 91256 & 989572 & 0.0 & 234 & 107 \\
+            Insecta & 91256 & 989572 & 0.0 & 234 & 77 \\
             & & & FL & 245 & 77 \\ 

### 2018-02-25 code/evaluation/count_origins_and_losses.py

@@ -62,10 +62,12 @@ def count_origins_and_losses(subtree, father_state, found):
     node_state = get_state(node[2])
     if not  found:
         if node_state != father_state:
-            print(node_state, father_state)
             if father_state == 0:
                 origins += 1        # FL -> P
                 new_found = True
+            # elif father_state == 1:
+            #     losses += 1         # P -> FL
+            #     new_found = True
             else:
                 losses += 1         # P -> FL
                 new_found = True
@@ -85,8 +87,10 @@ def get_state(state):
         # possible tags: 0, 0.333, 0.4, 0.5, 0.667, 0.75, 1
         # rounded to:    0  0      0    0    1      1     1
         return round(float(state[1:-1]))
+        # return float(state[1:-1])
     else:
         # originaltag:  1 = FL, 2 = P
         return round(float(state) -1)
+        # return float(state) -1
 
 main()

### 2018-02-26 Paper - Latex/Paper - Skizze - v2.tex
Paper - new Title, OTL, GloBI

@@
     \pagestyle{empty}
+
+    	\vspace{20mm}
+    	\begin{Large}
+    	    \textbf{An analysis of the Castor package to predict parasitism in Eukaryota}\\
+      \end{Large}
+
+      \vspace{20mm}
+      or
 
@@
   the ancestral state reconstruction of parasitism. \\
-  \anmerkung{Der erste Satz muss nochmal überarbeitet werden. Das Ziel / Ergebnis der Arbeit hat sich 
+  \anmerkungstext{Der erste Satz muss nochmal überarbeitet werden. Das Ziel / Ergebnis der Arbeit hat sich 
     inzwischen geändert} \\
@@
         \item Warum ist das relevant? Was könnte man dann tun?\\
+          predict states of species... \\
           \todo{!!!}
@@
     \subsection{OTL}
-      \todo{Open Tree of Life}
+      For our project we looked for a large database for phylogenetic trees and also for a taxonomic 
+        tree. Since we run our algorithm on the phylogenetic tree, and for the evaluation and other 
+        properties the taxonomy provides us with much more information. \\
+      OTL gives us both. A synthesis of phylogenetic trees (currently 819 trees) and a taxonomic tree. 
+        OTL also includes the large phylogenetic database TreeBASE \cite{Hinchliff2015}. \\
+      \todo{Das steht auf der Website nicht in dem Paper...} \\
+      For phylogenetic data, there are at least five big data collections, namely: ITIS (Integrated 
+      Taxonomic Information System), NCBI (National Center for Biotechnology Information [18]), WORMS 
+      (World Register of Marine Species [14]), GBIF (Global Biodiversity Information Facility [17]), 
+      OTT (OpenTreeOfLife-Taxonomy [4]).
+      \todotext{Marius:} "Every dataset has it's own characteristics and downsides. ITIS is only a small 
+        set of 100\% confirmed and named species. GBIF is not composed with the help of phylogeny, the 
+        same is valid for the NCBI taxonomy. The WORMS taxonomy is a way too small dataset of mostly 
+        marine species. \\
+      We choosed the taxonomy from OpenTreeOfLife because it's including most of the known taxonomies 
+        and got synthesised by preffering taxonomies that match with available phylogenetic data. At the 
+        same time the team from OTL preferred a maximum number of species [4]. This is resulting in 
+        somekind of hybrid between taxonomy and phylogeny." \\
 
@@
     \subsection{GloBI}
+    \todotext{Marius:} "There aren't many big active interaction databases out there, most of them are 
+      offline or outdated. For example: Interaction Web Database [35], Webs on the Web [36], Animal 
+      Diversity Web [37] and ecoweb [38]. GloBI is including most of the known ones and is still growing 
+      actively [3]. So the question which interaction database could be used was answered rather quickly." \\ \\
+
       For tagging our leave nodes, we use the GloBI (Global Biotic Interactions) database. This database 
@@
     \end{enumerate}
-    We tested the influence of these parameters on our result using our simulation. \\
-    \todo{ref zu section simulation}
+    We tested the influence of these parameters on our result using our simulation (Section 
+      \ref{sec:simulation}).
 
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Simulation}
+  \section{Simulation}\label{sec:simulation}
     \anmerkung{Motivate the goal of the simulation (Bernhard)}
@@
             \hline
-            Domain / Kingdom & \# internal & \# leaf & Rootnode & \multicolumn{2}{c|}{without and with rounding} \\ 
-            / Phylum / Class & \multicolumn{2}{c||}{nodes} & state & \# origins & \# losses \\
-            & & & state & (FL -> P) & (P -> FL) \\
+            Domain  & \# internal & \# leaf & Rootnode & \multicolumn{2}{c|}{without and with rounding} \\ 
+            / Kingdom  & \multicolumn{2}{c||}{nodes} & state & \# origins & \# losses \\
+            / Phylum / Class & & & & (FL -> P) & (P -> FL) \\
             \hline \hline
@@
             Platyhelminthes & 4459 & 22683 & 1.0 & 0 & 5 \\
-            & & & P & 0 & 5 \\ \hline
+            & & & P & 0 & 5 \\
             \hline \hline            
@@
       In Table \ref{table:origins and losses} we can see, that we found some more origins than Weinstein 
-        and on top of that some losses. \\ \\
+        and on top of that some losses. \\
 

### 2018-03-02 Paper - Latex/Paper - Skizze - v2.tex
Paper - new title; add some references; Cross Evaluation

@@
     	\begin{Large}
-    	    \textbf{An analysis of the Castor package to predict parasitism in Eukaryota}\\
-      \end{Large}
-
-      \vspace{20mm}
-      or
-
-      \vspace{20mm}
-    	\begin{Large}
-    	    \textbf{Origins and losses of parasitism}\\
-          an analysis of the phylogenetic tree of life with a parsimony-like algorithm\\
+          \textbf{An analysis of maximum parsimony algorithms to predict parasitism in Eukaryota}\\
+          using a large multiurcated phylogenetic synthesis tree
       \end{Large}
@@
       For phylogenetic data, there are at least five big data collections, namely: ITIS (Integrated 
-      Taxonomic Information System), NCBI (National Center for Biotechnology Information [18]), WORMS 
-      (World Register of Marine Species [14]), GBIF (Global Biodiversity Information Facility [17]), 
-      OTT (OpenTreeOfLife-Taxonomy [4]).
+        Taxonomic Information System) \cite{ITIS}, NCBI (National Center for Biotechnology Information) 
+        \cite{NCBI1988}, WORMS (World Register of Marine Species) \cite{WoRMS2018}, GBIF (Global 
+        Biodiversity Information Facility) \cite{GBIF}, OTT (OpenTreeOfLife-Taxonomy) 
+        \cite{Hinchliff2015}. \\
       \todotext{Marius:} "Every dataset has it's own characteristics and downsides. ITIS is only a small 
@@
         and got synthesised by preffering taxonomies that match with available phylogenetic data. At the 
-        same time the team from OTL preferred a maximum number of species [4]. This is resulting in 
-        somekind of hybrid between taxonomy and phylogeny." \\
+        same time the team from OTL preferred a maximum number of species \cite{Hinchliff2015}. This is 
+        resulting in somekind of hybrid between taxonomy and phylogeny." \\
 
@@
       \todotext{Marius:} "There aren't many big active interaction databases out there, most of them are 
-      offline or outdated. For example: Interaction Web Database [35], Webs on the Web [36], Animal 
-      Diversity Web [37] and ecoweb [38]. GloBI is including most of the known ones and is still growing 
-      actively [3]. So the question which interaction database could be used was answered rather quickly." \\ \\
-
-      For tagging our leave nodes, we use the GloBI (Global Biotic Interactions) database. This database 
-        consists of entries of the form: species A (source) interacts with B (target). \\
+        offline or outdated. For example: IWDB (Interaction Web Database) \cite{IWDB2003}, Webs on the 
+        Web \cite{WOW2004}, Animal Diversity Web \cite{Myers2003} and ecoweb \cite{Cohen2010}. GloBI is 
+        including most of the known ones and is still growing actively \cite{Poelen2014}. So the 
+        question which interaction database could be used was answered rather quickly." \\
+
+      This database consists of entries of the form: species A (source) interacts with B (target). \\
       We appointed some interactions, where we know from the biological perspective that the species 
@@
             multifurc $\sim$ class & 7337241 & 98459 \\
-            \rowcolor{green} multifurc $\sim$ order & 7076068 & 261172 \\
+            \rowcolor{green!50} multifurc $\sim$ order & 7076068 & 261172 \\
             \hline \hline \hline
@@
             multifurc $\sim$ phylum + min.height & 7233486 & 142403 \\
-            \rowcolor{green} multifurc $\sim$ phylum + mean.height & 7128318 & 105167 \\
+            \rowcolor{green!50} multifurc $\sim$ phylum + mean.height & 7128318 & 105167 \\
             \hline \hline
@@
             multifurc ~ phylum * min.height & 7177002 & 134238 \\
-            \rowcolor{green} multifurc ~ phylum * mean.height & 7020258 & 156745 \\
+            \rowcolor{green!50} multifurc ~ phylum * mean.height & 7020258 & 156745 \\
             \hline \hline
@@
             multifurc ~ phylum + mean.height & 7128318 & 307381 \\
-            \rowcolor{green} multifurc ~ phylum * mean.height & 7020258 & 108061 \\
+            \rowcolor{green!50} multifurc ~ phylum * mean.height & 7020258 & 108061 \\
             \hline \hline \hline
@@
             multifurc $\sim$ class + min.height & 7144686 & 131170 \\
-            \rowcolor{green} multifurc $\sim$ class + mean.height & 7055313 & 89374 \\
+            \rowcolor{green!50} multifurc $\sim$ class + mean.height & 7055313 & 89374 \\
             \hline \hline
@@
             multifurc ~ class * min.height & 7094933 & 92570 \\
-            \rowcolor{green} multifurc ~ class * mean.height & 6965794 & 129139 \\
+            \rowcolor{green!50} multifurc ~ class * mean.height & 6965794 & 129139 \\
             \hline \hline
@@
             multifurc ~ class + mean.height & 7055313 & 281928 \\
-            \rowcolor{green} multifurc ~ class * mean.height & 6965794 & 89518 \\
+            \rowcolor{green!50} multifurc ~ class * mean.height & 6965794 & 89518 \\
             \hline \hline \hline
@@
             multifurc $\sim$ order + min.height & 6890703 & 114721 \\
-            \rowcolor{green} multifurc $\sim$ order + mean.height & 6815271 & 75432 \\
+            \rowcolor{green!50} multifurc $\sim$ order + mean.height & 6815271 & 75432 \\
             \hline
@@
     %---------------------------------------------------------------------------------------------------
+    \subsection{Cross evaluation - leave 100 out}
+      We ran the castor algorithm (\todo{10000}) 10 times with leaving 100 randomized free-living or 
+        parasitic species out of the input data to see how stable our result is. \\
+      What could happen by removing a parasite or free-living of the list?
+      \begin{itemize}
+        \item It could be a specie, which don't exist in the tree leaf nodes. -> no effect
+        \item It could be a specie, which exists in both lists. -> If it was a parasite, it is now 
+          free-living, because we prefer parasites. Otherwise we have no effect again. (1053 are possible)
+        \item Normal case: We loose information, because its a specie in our tree and we change it to a 
+          leave node with no information.
+      \end{itemize}
+      \begin{table}
+        \begin{center}
+          \begin{tabular}{ |c||r|r|r||c|r| }
+            \hline
+            run & \multicolumn{3}{c||}{distance} & changed & lost \\
+            & all nodes & leaf nodes & internal nodes & tag & tag \\
+            \hline \hline
+            0 & 4.0 & 4.0 & 0.0 & 4 & 48 \\
+            1 & 4.0 & 4.0 & 0.0 & 2 & \cellcolor{green!50}45 \\
+            2 & 85.3 & 79.3 & 6.0 & 3 & 51 \\
+            3 & 1.0 & 1.0 & 0.0 & 1 & 47 \\
+            \rowcolor{red!50}4 & 1248.0 & 1230.5 & 17.5 & \cellcolor{green!50}0 & 54 \\
+            5 & 169.0 & 168.0 & 1.0 & 3 & 52 \\
+            6 & 1.0 & 1.0 & 0.0 & 1 & 48 \\
+            7 & 1.0 & 1.0 & 0.0 & 1 & 53 \\
+            8 & 1.0 & 1.0 & 0.0 & 1 & \cellcolor{red!50}54 \\
+            9 & 1.0 & 1.0 & 0.0 & 1 & 52 \\
+            \hline
+          \end{tabular}
+        \end{center}
+        \caption{Example runs. \\ green: min value, red: max value}
+      \end{table}
+
+      \begin{table}
+        \begin{center}
+          \begin{tabular}{ |cl||r|r|r|r| }
+            \hline
+            & & min & max & mean & variance \\
+            \hline \hline
+            \multirow{3}{*}{distance} & all & 1.0 & 1248.0 & 151.53 & 151528.92 \\
+            & leaf nodes                    & 1.0 & 1230.5 & 149.08 & 147380.74 \\
+            & internal nodes                & 0.0 & 17.5 & 2.45 & 31.47 \\ \hline
+            \multicolumn{2}{|c||}{changed tag} & 0.0 & 4.0 & 1.7 & 1.57 \\ \hline
+            lost tag & all tags             & 45.0 & 54.0 & \cellcolor{green!50}50.40 & 10.04 \\
+            & FL tags                       & 16.0 & 32.0 & 23.10 & 18.77 \\
+            & P tags                        & 16.0 & 36.0 & 27.30 & 41.34 \\
+            \hline
+          \end{tabular}
+        \end{center}
+        \caption{Statistics to Cross validation}
+      \end{table}
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
   %---------------------------------------------------------------------------------------------------
@@
 \bibliography{bibliographie}
-\bibliographystyle{alphadin}
 

### 2018-03-04 code/utilities/castor_parsimony_simulation.R
evaluation castor run corrected

@@ -24,10 +24,10 @@ internal_nodes <- tree$node.label
 # map_to_state_space(raw_states, fill_gaps=FALSE, sort_order="natural", include_state_values=FALSE)
 mapping <- map_to_state_space(states, include_state_values = TRUE)
 tip_states <- mapping$mapped_states
-# print("State names:")
-# print(mapping$state_names)
+print("State names:")
+print(mapping$state_names)
 x <- replace(tip_states, tip_states==3, NA)
-# print("run parsimony algorithm...")
+print("run parsimony algorithm...")
 
 # ---- run parsimony algorithm ----
 # Reconstruct ancestral discrete states of nodes and predict unknown (hidden) states of tips on a tree using maximum parsimony. Transition costs can vary between transitions, and can optionally be weighted by edge length.

### 2018-03-04 code/utilities/castor_util.py

@@ -35,11 +35,11 @@ def sankoff_parsimony(run_id):
     f = open(r_path, "r")
     code = ''.join(f.readlines())
     if run_id >= 0:
-        print(colored("---------------- run castor ----------------", "green"))
+        print(colored("---------------- prepare R script ----------------", "green"))
         code_Array = code.split("code/bufferfiles/simulated_tagged_tree.tre")
         code = tagged_tree_path.join(code_Array)
 
-    print(colored("---------------- prepare R script ----------------", "green"))
+    print(colored("---------------- run castor ----------------", "green"))
 
     rpy2.robjects.r(code)
     # assume that...
@@ -51,8 +51,8 @@ def sankoff_parsimony(run_id):
     number_of_tips = rpy2.robjects.globalenv['number_of_tips']
     internal_nodes = rpy2.robjects.globalenv['internal_nodes']
 
+    print(colored("---------------- save likelihoods ----------------", "green"))
     l = int(len(likelihoods)/3)
-        
     j = 0
     k = 0
     for i in range(2*l, 3*l):
@@ -100,10 +100,10 @@ def randomly_change_nodelist():
     while changed < border:
         index = random.randrange(len(nodelist))
         element = nodelist[index]
-        if element[1] != 'NA':
-            element[1] = 'NA'
-            nodelist[index] = element
-            changed +=1
+        if element[5] == 0:
+            if element[1] != 'NA':
+                element[1] = 'NA'
+                changed +=1
     return
 
 def cache_tree(tagged_tree_path):

### 2018-03-04 Paper - Latex/Paper - Skizze - v2.tex
Results - Multifurcation; BICs added

@@
   %---------------------------------------------------------------------------------------------------
-      \subsubsection{Data artifacts}
-        Zu der Frage, warum gibt es $nrChildren==1$. Es gibt tatsächlich 55700 Knoten mit nur einem Kind. 
-          Davon ist der großteil direkt vor einem Blatt (51744), aber 3956 ($height >2$) sind irgendwo im 
-          Baum. Ein paar Beispiele: \\
-        Nephroselmidophyceae: (class) \\
-        https://tree.opentreeoflife.org/opentree/argus/ottol@1038762 \\
-        Phrynocrinidae: (family) \\
-        https://tree.opentreeoflife.org/opentree/argus/ottol@3647979 \\
-        Elaeocarpus sylvestris: \\
-        https://tree.opentreeoflife.org/opentree/argus/opentree9.1@ott166969 \\
-        Was bedeutet das für unsere Analyse? Ignorieren wir die $\sim$ 4000 internen und Zählen sie zu den 
-          Blättern, oder zählen wir alle zu den Internen oder puzzlen wir sie einzeln raus. D.h. nur die 
-          mit der Zusatzeigenschaft ($height == 2$) sind auch Blätter. \\
-        Es könnte aber auch Fälle geben wie: ...-O-O-O-O-O, dann könnte man auch einen Knoten mit höherer 
-          Höhe als Blatt zählen. Das müsste dann gelten $min height = max height$. \\ 
-        \begin{lstlisting}[gobble=8]
-          leaf.taxa <-  all.taxa[all.taxa$nr_children==0, ]
-          extendedLeaf.taxa <- all.taxa[all.taxa$nr_children<2 & min.height==max.height, ]
-          inner.taxa <- all.taxa[all.taxa$nr_children>1 | (all.taxa$nr_children==1 & min.height!=max.height), ]
-        \end{lstlisting}
-        \todo{macht extendedLeaf wirklich einen Sinn?}
-
-  %---------------------------------------------------------------------------------------------------
   %---------------------------------------------------------------------------------------------------
@@
     \subsection{Multifurcation}
-      One property of the tree is its ridge of multifurcation. A complete kinship tree would be binary, 
-        but since we only work with a synthesis tree of individual trees, this tree is multifurcated. 
-        For a first overview we collected for every node its number of children (degree $-1$), and 
-        plottet this in an histogram. In Figure \ref{fig:childrenOfNodes} you can see how much nodes we 
-        have for every degree. \\
-      \todotext{Subfigure \ref{fig:childrenOfNodes_innerNodes} beschränkt sich hierbei nur auf die inner 
-        nodes während Subfigure \ref{fig:childrenOfNodes_allNodes} alle Knoten abbildet.} \\
-      \todo{Welchen der beiden Plots wollen wir nehmen, einer genügt eigentlich:}
-      \begin{figure}[h!]
-        \begin{subfigure}{.5\textwidth}
-          \centering
-          \includegraphics[width=.8\linewidth]{Figures/multifurc.pdf}
-          \caption{all nodes}
-          \label{fig:childrenOfNodes_allNodes}
-        \end{subfigure}%
-        \begin{subfigure}{.5\textwidth}
-          \centering
-          \includegraphics[width=.8\linewidth]{Figures/nr_children.pdf}
-          \caption{inner nodes (shiftet to 0)}
-          \label{fig:childrenOfNodes_innerNodes}
-        \end{subfigure}
-        \caption{plots of children of nodes}
-        \label{fig:childrenOfNodes}
-      \end{figure}
-      As you can see, we are very far from a binary tree. Therefore, the impact of multifurcations on 
-        our research question has been investigated:
+      We have a very high multifurcation rate \pageref{sec:ResultsMultifurcation}.
+
+      Therefore, the impact of multifurcations on our research question has been investigated:
       \begin{itemize}
@@
       compared according to their deviance and AIC."
+      \begin{lstlisting}[gobble=8]
+        glm(formula = multifurc ~ 1, family = "poisson", data = inner.taxa)
+      \end{lstlisting}
 
@@
 \chapter{Results}
-  Ein großer Punkt in diesem Kapitel ist das Ergebnis der Untersuchung der Datenlage. Wie ist der 
-    Stand? Welchen Einfluss hat das auf unser eigentliches Ergebnis? Was kann man dagegen tun? \\
-  Ansonsten geht es in diesem Kapitel hauptsächlich um die tatsächliche Rekonstruktion der states.
-    Dass heißt zum einen der der inneren Knoten und dadurch der Untersuchung von Origins und Losses
-    und zum anderen der Vorhersage von unbekannten states von Leaf nodes. \\
-  Und natürlich dem Ergebnis der Simulation.
+  A big point in this chapter is the result of examining the input data. How is the situation? What 
+    influence does that have on our actual result? What can we do about it? Our simulation gave us 
+    some results to this. \\
+  Otherwise, this chapter is mainly about the actual reconstruction of the states. This means, on 
+    one hand investigation of origins and losses of the inner nodes and on the other, the prediction 
+    of unknown states of leaf nodes. \\
    
@@
     \subsection{Taxa}
-      Die Untersuchung der Taxa der Eukaryoten hat das folgende ergeben:
-      Es gibt 3 Kingdoms: Chloroplastida, Metazoa, Fungi. \\
-      \todo{Hier fehlt nichts. Ref einfügen.} \\
-      Phyla (53): \\
-      Acanthocephala, Amoebozoa, Apicomplexa, Arthropoda, Ascomycota, Bacillariophyta, Basidiomycota, 
-        Brachiopoda, Bryozoa, Chaetognatha, Chlorophyta, Chordata, Chromerida, Chytridiomycota, 
-        Ciliophora, Cnidaria, Colponemidia, Ctenophora, Cycliophora, Echinodermata, Entoprocta, 
-        Entorrhizomycota, Euglenida, Foraminifera, Gastrotricha, Glomeromycota, Gnathostomulida, 
-        Haplosporida, Haptophyta, Hemichordata, Kinorhyncha, Loricifera, Microsporidia, Mollusca, 
-        Myzostomida, Nematoda, Nematomorpha, Nemertea, Onychophora, Orthonectida, Phaeophyceae, 
-        Picozoa, Placozoa, Platyhelminthes, Porifera, Priapulida, Rhodophyta, Rhombozoa, Rotifera, 
-        Streptophyta, Tardigrada, Xanthophyceae \\
-      Wobei von Streptophyta -> Anthocerotophyta, Marchantiophyta, Bryophyta, Tracheophyta als
-        Phylum im Phylum gefunden und nicht einbezogen wurden und Magnoliophyta als Phylum in 
-        Tracheophyta ebenfalls nicht. \\
-      Außerdem haben wir 195 Klassen und 924 Ordnungen feststellen können.
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \section{Multifurcation}
+      The investigation of the taxonomy revealed that our tree has three kingdoms: Chloroplastida, 
+        Metazoa, Fungi, 53 phyla, 195 classes and 924 orders. \\
+      Since the analysis of the tree is not part of this work, it should be mentioned here that, 
+        according to recent findings, this is not complete and we lack some taxa in every rank. For 
+        example, Hans says that one distinguishes between seven and nine kingdoms 
+        \cite{CavalierSmith1981}. \\
+      In section \pageref{sec:listPhyla} of the appendix you can find a list of all phyla.
+
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \section{Multifurcation}\label{sec:ResultsMultifurcation}
+      One property of the tree is its ridge of multifurcation. A complete phylogenetic tree would be 
+        binary, but since we only work with a synthesis tree, this tree is multifurcated. \\
+      For a first overview we collected for every node its number of children (degree $-1$), and plotted
+        this in an histogram, see figure \ref{fig:childrenOfNodes}. The multifurcation affects only the
+        internal nodes. We collected the number of children $-2$ of every node (a node with two children 
+        is binary). 
+      \begin{wrapfigure}{r}{0.6\textwidth}
+        \begin{center}
+          \includegraphics[trim = 0mm 0mm 30mm 0mm, clip, width=0.58\textwidth]{Figures/multifurc.pdf}
+        \end{center}
+        \caption{Histogram about the multifurcation of the internal nodes of the synthesis tree. \\ 
+          light blue: binary; dark blue: multifunction}
+        \label{fig:childrenOfNodes}
+      \end{wrapfigure}
+      That means it discribes the number of nodes which we have lost from the real (binary) 
+      phylogenetic tree. \\
+      As you can see, we are very far from a binary tree.
+
+      %---------------------------------------------------------------------------------------------------
+      \subsubsection{Data artifacts}
+      At this point we also found out that there are some nodes with only one child node (55700 nodes). \\
+      These are both, the most nodes are right in front of a leaf, as well as some nodes are deep in the 
+        tree (3956 with height $>2$). They are probably a result from the fact that taxonomic information 
+        has been incorporated into a phylogeny. \\
+
+      Some examples:
+      \begin{itemize}
+        \item Nephroselmidophyceae: (class) \\
+          https://tree.opentreeoflife.org/opentree/argus/ottol@1038762
+        \item Phrynocrinidae: (family) \\
+          https://tree.opentreeoflife.org/opentree/argus/ottol@3647979
+        \item Elaeocarpus sylvestris: \\
+          https://tree.opentreeoflife.org/opentree/argus/opentree9.1@ott166969
+      \end{itemize}
 
@@
       \subsection{Poisson regression}
-
-        \begin{lstlisting}[gobble=8]
-          glm(formula = multifurc ~ 1, family = "poisson", data = inner.taxa)
-        \end{lstlisting}
+        glm (generalized linear model) analysis: \\
+
         The intercept is $2.821 > 0$ $\Rightarrow$ there is a multifunction.
@@
           genauer umso kleinere Subtrees wir betrachten. ...
-        \begin{lstlisting}[gobble=8]
-          Model 1: multifurc ~ kingdom
-          Model 2: multifurc ~ phylum
-          Model 3: multifurc ~ class
-          Model 4: multifurc ~ order
-            Resid. Df Resid. Dev  Df Deviance  Pr(>Chi)
-          1    167222    7774454
-          2    167173    7435700  49   338754 < 2.2e-16 ***
-          3    167039    7337241 134    98459 < 2.2e-16 ***
-          4    166352    7076068 687   261172 < 2.2e-16 ***
-        \end{lstlisting}
+
         \anmerkung{different parameters for different taxa? (Emanuel)} \\ \\
+
+        Because of the difference in the complexity of the models, we compared their BICs:
+        \begin{table}
+          \begin{center}
+            \begin{tabular}{ |l|r| }
+              \hline
+              Model & BIC \\
+              \hline \hline
+              multifurc $\sim$ 1 & 8623935 \\
+              multifurc $\sim$ kingdom & 8273333 \\
+              multifurc $\sim$ phylum & 7937828 \\
+              multifurc $\sim$ class & 7842157 \\
+              \rowcolor{green!50}multifurc $\sim$ order & 7644249\\
+              \hline \hline
+              multifurc $\sim$ phylum + depth & 7934322 \\
+              multifurc $\sim$ phylum + max.height & 7749121 \\
+              multifurc $\sim$ phylum + min.height & 7875521 \\
+              \rowcolor{green!50} multifurc $\sim$ phylum + mean.height & 7644249 \\
+              \hline
+              multifurc ~ phylum * depth & 7836755 \\
+              multifurc ~ phylum * max.height & 7693555 \\
+              multifurc ~ phylum * min.height & 7808940 \\
+              \rowcolor{green!50} multifurc ~ phylum * mean.height & 7536296 \\
+              \hline \hline
+              multifurc $\sim$ class + depth & \\
+              multifurc $\sim$ class + max.height & \\
+              multifurc $\sim$ class + min.height & \\
+              multifurc $\sim$ class + mean.height & \\
+              \hline
+              multifurc ~ class * depth & \\
+              multifurc ~ class * max.height & \\
+              multifurc ~ class * min.height & \\
+              multifurc ~ class * mean.height &\\
+              \hline
+            \end{tabular} 
+          \end{center}
+          \caption{BIC...}
+          \label{table:...} 
+        \end{table}
 
@@
 \chapter{Appendices}
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{List of all phyla}\label{sec:listPhyla}
+
+  Phyla (53): \\
+  Acanthocephala, Amoebozoa, Apicomplexa, Arthropoda, Ascomycota, Bacillariophyta, Basidiomycota, 
+    Brachiopoda, Bryozoa, Chaetognatha, Chlorophyta, Chordata, Chromerida, Chytridiomycota, 
+    Ciliophora, Cnidaria, Colponemidia, Ctenophora, Cycliophora, Echinodermata, Entoprocta, 
+    Entorrhizomycota, Euglenida, Foraminifera, Gastrotricha, Glomeromycota, Gnathostomulida, 
+    Haplosporida, Haptophyta, Hemichordata, Kinorhyncha, Loricifera, Microsporidia, Mollusca, 
+    Myzostomida, Nematoda, Nematomorpha, Nemertea, Onychophora, Orthonectida, Phaeophyceae, 
+    Picozoa, Placozoa, Platyhelminthes, Porifera, Priapulida, Rhodophyta, Rhombozoa, Rotifera, 
+    Streptophyta, Tardigrada, Xanthophyceae \\
+  Wobei von Streptophyta -> Anthocerotophyta, Marchantiophyta, Bryophyta, Tracheophyta als
+    Phylum im Phylum gefunden und nicht einbezogen wurden und Magnoliophyta als Phylum in 
+    Tracheophyta ebenfalls nicht. \\
+
   %---------------------------------------------------------------------------------------------------

### 2018-03-04 code/metadata/analyse_input.R

@@ -46,30 +46,22 @@ table(all.taxa$rank)[order(table(all.taxa$rank))]
 # table(all.taxa[all.taxa$nr_children==1 & all.taxa$max.height>2, "finaltag"])
 # print('--------------------------------------------------')
 # table(all.taxa[all.taxa$nr_children==1 & all.taxa$max.height==2, "finaltag"])
-print('--------------------------------------------------')
-
-## pdf(path, width=8, height=6)
-# ggplot(all.taxa, aes(nr_children)) +
-#     geom_histogram() +
-#     scale_y_log10()
-# ggsave("nr_children.pdf")
-## dev.off()
 
 print('--------------------------------------------------')
 
 leaf.taxa <-  all.taxa[all.taxa$nr_children==0, ]
-extendedLeaf.taxa <- all.taxa[all.taxa$nr_children<2 & min.height==max.height, ]
-inner.taxa <- all.taxa[all.taxa$nr_children>1 | (all.taxa$nr_children==1 & min.height!=max.height), ]
+inner.taxa <- all.taxa[all.taxa$nr_children>1, ]
+extendedInner.taxa <- all.taxa[all.taxa$nr_children>0, ]
 
 print('----------------------- leaf.taxa$rank ---------------------------')
 leaf.taxa <- as.data.frame(leaf.taxa)
 # table(leaf.taxa$rank)[order(table(leaf.taxa$rank))]
-print('----------------------- extendedLeaf.taxa$rank ---------------------------')
-extendedLeaf.taxa <- as.data.frame(extendedLeaf.taxa)
-# table(extendedLeaf.taxa$rank)[order(table(extendedLeaf.taxa$rank))]
 print('----------------------- inner.taxa$rank ---------------------------')
 inner.taxa <- as.data.frame(inner.taxa)
 # table(inner.taxa$rank)[order(table(inner.taxa$rank))]
+print('----------------------- extendedInner.taxa$rank ---------------------------')
+extendedInner.taxa <- as.data.frame(extendedInner.taxa)
+# table(extendedLeaf.taxa$rank)[order(table(extendedLeaf.taxa$rank))]
 print('--------------------------------------------------')
 
 # tapply(inner.taxa$max.height, inner.taxa$rank, summary)
@@ -77,31 +69,36 @@ print('--------------------------------------------------')
 inner.taxa$multifurc <- inner.taxa$nr_children-1
 
 # ggplot(inner.taxa, aes(multifurc)) +
[…]

### 2018-03-04 Paper - Latex/Paper - Skizze - v2.tex
update table

@@
 
-        \begin{center}
-          \begin{longtable}{ |l|r|r| }
-            \hline
-            Model & Residuals Dev & Deviance Pr \\
-            \hline \hline
-            multifurc $\sim$ kingdom & 7774454 & \\
-            multifurc $\sim$ phylum & 7435700 & 338754 \\
-            multifurc $\sim$ class & 7337241 & 98459 \\
-            \rowcolor{green!50} multifurc $\sim$ order & 7076068 & 261172 \\
-            \hline \hline \hline
-            multifurc $\sim$ phylum + depth & 7431609 & \\
-            multifurc $\sim$ phylum + max.height & 7375889 & 55721 \\
-            multifurc $\sim$ phylum + min.height & 7233486 & 142403 \\
-            \rowcolor{green!50} multifurc $\sim$ phylum + mean.height & 7128318 & 105167 \\
-            \hline \hline
-            multifurc ~ phylum * depth & 7335396 & \\
-            multifurc ~ phylum * max.height & 7311241 & 24155 \\
-            multifurc ~ phylum * min.height & 7177002 & 134238 \\
-            \rowcolor{green!50} multifurc ~ phylum * mean.height & 7020258 & 156745 \\
-            \hline \hline
-            multifurc ~ phylum & 7435700 & \\
-            multifurc ~ phylum + mean.height & 7128318 & 307381 \\
-            \rowcolor{green!50} multifurc ~ phylum * mean.height & 7020258 & 108061 \\
-            \hline \hline \hline
-            multifurc $\sim$ class + depth & 7334754 & \\
-            multifurc $\sim$ class + max.height & 7275856 & 58898 \\
-            multifurc $\sim$ class + min.height & 7144686 & 131170 \\
-            \rowcolor{green!50} multifurc $\sim$ class + mean.height & 7055313 & 89374 \\
-            \hline \hline
-            multifurc ~ class * depth & 7250759 & \\
-            multifurc ~ class * max.height & 7187504 & 63256 \\
-            multifurc ~ class * min.height & 7094933 & 92570 \\
-            \rowcolor{green!50} multifurc ~ class * mean.height & 6965794 & 129139 \\
-            \hline \hline
-            multifurc ~ class & 7337241 & \\
-            multifurc ~ class + mean.height & 7055313 & 281928 \\
-            \rowcolor{green!50} multifurc ~ class * mean.height & 6965794 & 89518 \\
-            \hline \hline \hline
-            multifurc $\sim$ order + depth & 7027578 & \\
-            multifurc $\sim$ order + max.height & 7005424 & 22154 \\
-            multifurc $\sim$ order + min.height & 6890703 & 114721 \\
-            \rowcolor{green!50} multifurc $\sim$ order + mean.height & 6815271 & 75432 \\
-            \hline
-          \end{longtable}
-        \end{center}
+        \begin{table}
+          \begin{center}
+            \begin{tabular}{ |l|r|r|r|r| }
+              \hline
+              Model / Taxa & Kingdom & Phylum & Class & Order \\
+              \hline \hline
+              multifurc $\sim$ taxa & 7774454 & 7435700 & 7337241 & 7076068 \\
+              \hline
+              multifurc $\sim$ taxa + depth & 7752303 & 7431609 & 7334754 & 7027578 \\
+              multifurc $\sim$ taxa + max.height & 7730196 & 7375889 & 7275856 & 7005424 \\
+              multifurc $\sim$ taxa + min.height & 7472500 & 7233486 & 7144686 & \cellcolor{green!50}6890703 \\
+              multifurc $\sim$ taxa + mean.height & 7304402 & 7128318 & 7055313 & \cellcolor{green!50}6815271 \\
+              \hline
+              multifurc $\sim$ taxa * depth & 7714881 & 7335396 & 7250759 & \\
+              multifurc $\sim$ taxa * max.height & 7692980 & 7311241 & 7187504 & \\
+              multifurc $\sim$ taxa * min.height & 7442387 & 7177002 & 7094933 & \\
+              multifurc $\sim$ taxa * mean.height & 7247309 & 7020258 & \cellcolor{green!50}6965794 & \\
+              \hline
+            \end{tabular} 
+          \end{center}
+          \caption{Residuals...}
+          \label{table:...} 
+        \end{table}
         * Residuals: Fehler - wieviele Werte sind nicht gut modelliert. (umso kleiner umso besser - grün) \\
-        * Deviance - Abweichung \\
 
@@
 
-        \todotext{Nur ein Ausschnitt hier und dann... You can find the whole Deviance Table in the 
-          Appendix...} \\
         Interpretation: Die Multifurkation ist sehr ungleich verteilt. Daher ist die vorhersage umso 
@@
           \begin{center}
-            \begin{tabular}{ |l|r| }
-              \hline
-              Model & BIC \\
-              \hline \hline
-              multifurc $\sim$ 1 & 8623935 \\
-              multifurc $\sim$ kingdom & 8273333 \\
-              multifurc $\sim$ phylum & 7937828 \\
-              multifurc $\sim$ class & 7842157 \\
-              \rowcolor{green!50}multifurc $\sim$ order & 7644249\\
-              \hline \hline
-              multifurc $\sim$ phylum + depth & 7934322 \\
-              multifurc $\sim$ phylum + max.height & 7749121 \\
-              multifurc $\sim$ phylum + min.height & 7875521 \\
-              \rowcolor{green!50} multifurc $\sim$ phylum + mean.height & 7644249 \\
-              \hline
-              multifurc ~ phylum * depth & 7836755 \\
-              multifurc ~ phylum * max.height & 7693555 \\
-              multifurc ~ phylum * min.height & 7808940 \\
-              \rowcolor{green!50} multifurc ~ phylum * mean.height & 7536296 \\
-              \hline \hline
-              multifurc $\sim$ class + depth & \\
-              multifurc $\sim$ class + max.height & \\
-              multifurc $\sim$ class + min.height & \\
-              multifurc $\sim$ class + mean.height & \\
-              \hline
-              multifurc ~ class * depth & \\
-              multifurc ~ class * max.height & \\
-              multifurc ~ class * min.height & \\
-              multifurc ~ class * mean.height &\\
+            \begin{tabular}{ |l|r|r|r|r| }
+              \hline
+              Model / Taxa & Kingdom & Phylum & Class & Order \\
+              \hline \hline
+              multifurc $\sim$ taxa & 8273333 & 7937828 & 7842157 & 7644249\\
+              \hline
+              multifurc $\sim$ taxa + depth & 8273318 & 7934322 & 7839364 & \\
+              multifurc $\sim$ taxa + max.height & 7993515 & 7749121 & 7661817 & \\
+              multifurc $\sim$ taxa + min.height & 8251211 & 7875521  & 7778327 & \\
+              multifurc $\sim$ taxa + mean.height & 7825417 & 7644249 &  \cellcolor{green!50}7572474 & \\
+              \hline
+              multifurc $\sim$ taxa * depth & 8235932 & 7836755 & 7757688 & \\
+              multifurc $\sim$ taxa * max.height & 7963438 & 7693555 & 7614820 & \\
+              multifurc $\sim$ taxa * min.height & 8214030 & 7808940 & 7690618 & \\
+              multifurc $\sim$ taxa * mean.height & 7768360 & \cellcolor{green!50}7536296 & \cellcolor{green!50}7484953 & \\
               \hline

### 2018-03-04 code/metadata/analyse_input.R

@@ -80,67 +80,106 @@ print('--------------------------------------------------')
 
 null.furc.mod <- glm(multifurc~1, data=inner.taxa,
                    family="poisson")
-print('BIC=' + BIC(null.furc.mod))
 
-# print('------------------------kingdom - phylum - class - order--------------------------')
+print('------------------------kingdom - phylum - class - order--------------------------')
 
-# kingdom.furc.mod <- glm(multifurc~kingdom, data=inner.taxa,
-#                         family="poisson")
-# print('BIC=' + BIC(kingdom.furc.mod))
+kingdom.furc.mod <- glm(multifurc~kingdom, data=inner.taxa,
+                        family="poisson")
+print(c('BIC=',  BIC(kingdom.furc.mod)))
 
 # phylum.furc.mod <- glm(multifurc~phylum, data=inner.taxa,
 #                         family="poisson")
-# print('BIC=' + BIC(phylum.furc.mod))
+# print(c('BIC=',  BIC(phylum.furc.mod)))
 
 # class.furc.mod <- glm(multifurc~class, data=inner.taxa,
 #                         family="poisson")
-# print('BIC=' + BIC(class.furc.mod))
+# print(c('BIC=',  BIC(class.furc.mod)))
 
-# order.furc.mod <- glm(multifurc~order, data=inner.taxa,
-#                         family="poisson")
-# print('BIC=' + BIC(order.furc.mod))
+order.furc.mod <- glm(multifurc~order, data=inner.taxa,
+                        family="poisson")
+print(c('BIC=',  BIC(order.furc.mod)))
 
 # anova(kingdom.furc.mod, phylum.furc.mod, class.furc.mod, order.furc.mod, test="LRT")
 # anova(kingdom.furc.mod, phylum.furc.mod, test="LRT")
 
+print('-------------------kingdom + depth / min/max/mean.height-----------------------')
 
-# print('-------------------phylum + depth / min/max/mean.height-----------------------')
+# kingdomPdepth.furc.mod <- glm(multifurc~kingdom+depth, data=inner.taxa,
+#                    family="poisson")
+# print(c('BIC=',  BIC(kingdomPdepth.furc.mod)))
+
[…]

### 2018-03-05 Paper - Latex/Paper - Skizze - v2.tex
Paper - Methods:remove countings; - Results - Unknown leaf nodes

@@
       \todo{mehr dazu in section: unknown nodes...}
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{Countings}
-      \begin{center}
-        \begin{tabular}{ | l | l | }
-          \hline
-          Name & Number of \\
-          \hline \hline
-          Eukaryota & 241 974 internal nodes, \\
-          & 2 293 463 leaf nodes \\ \hline
-          % Chloroplastida has 43486 internal nodes and 412434 leaf_nodes
-          % Metazoa has 179944 internal nodes and 1491012 leaf_nodes
-          % Nematoda has 3437 internal nodes and 30127 leaf_nodes
-          % Vertebrata has 30466 internal nodes and 88415 leaf_nodes
-          % Tetrapoda has 21870 internal nodes and 47540 leaf_nodes
-          % Mammalia has 4727 internal nodes and 8615 leaf_nodes
-          % Primates has 492 internal nodes and 686 leaf_nodes
-          % Hominidae has 12 internal nodes and 14 leaf_nodes
-          % Fungi has 9534 internal nodes and 314571 leaf_nodes
-          interactions & 5 346 414 \\ \hline
-          freeliving species & 51 337 (distinct) \\ \hline
-          parasite species &  47 332 (distinct) \\ \hline
-          $\rightarrow$ unknown nodes & ??? \\ \hline
-          unused possible species & 57 352 (source), \\
-          & 809 993 (target) \\
-          % number of freelivings: 489179
-          % number of freelivings: 42657 (distinct)
-          % number of parasites: 3353580
-          % number of parasites: 44260 (distinct)
-          % number of SAME_AS: 86198
-          % number of SAME_AS: 16710 (distinct)
-          \hline
-          Nr of Children $== 1$ & 55 700 \\
-          & 51 744 (height $=2$) \\
-          & 3 956 (height $>2$) \\ \hline
-        \end{tabular}
-      \end{center}
-      \todo{tree, subtrees? figure dazu?} \\
-      $\frac{100}{2293463 * (51337 + 47332)} \approx 4.3$ $\rightarrow$ only 4.3\% of leaf nodes are 
-        filled with information
-
-      \#interactions zu \#Parasiten und \#Freilebend $\rightarrow$ Wieviel gibt GloBI her? (dazu noch 
-        \#unused possible species, wieviele Parasiten ohne ott haben wir gefunden?)
-      \#Parasiten und \#Freilebend und \#Blattknoten $\rightarrow$ Wieviele unbekannte Knoten haben wir?
-      \#Interne Knoten und \#Blattknoten $\rightarrow$ Wie stark ist die Multifurkation?
 
@@
       One property of the tree is its ridge of multifurcation. A complete phylogenetic tree would be 
-        binary, but since we only work with a synthesis tree, this tree is multifurcated. \\
+        binary, which means the number of leaf nodes is closely to the number of internal nodes. But 
+        since we only work with a synthesis tree, this tree is multifurcated: we have 241 974 internal 
+        nodes and 2 293 463 leaf nodes. \\
       For a first overview we collected for every node its number of children (degree $-1$), and plotted
@@
         has been incorporated into a phylogeny. \\
-
       Some examples:
@@
 
-        \begin{table}
+        \begin{table}[h]
           \begin{center}
@@
         Because of the difference in the complexity of the models, we compared their BICs:
-        \begin{table}
+        \begin{table}[h]
           \begin{center}
@@
               \hline
-              multifurc $\sim$ taxa + depth & 8273318 & 7934322 & 7839364 & \\
-              multifurc $\sim$ taxa + max.height & 7993515 & 7749121 & 7661817 & \\
-              multifurc $\sim$ taxa + min.height & 8251211 & 7875521  & 7778327 & \\
-              multifurc $\sim$ taxa + mean.height & 7825417 & 7644249 &  \cellcolor{green!50}7572474 & \\
-              \hline
-              multifurc $\sim$ taxa * depth & 8235932 & 7836755 & 7757688 & \\
+              multifurc $\sim$ taxa + depth & 8273318 & 7934322 & 7839364 & \cellcolor{green!50}7539999 \\
+              multifurc $\sim$ taxa + max.height & 7993515 & 7749121 & 7661817 & \cellcolor{green!50}7416211 \\
+              multifurc $\sim$ taxa + min.height & 8251211 & 7875521  & 7778327 & \cellcolor{green!50}7516883 \\
+              multifurc $\sim$ taxa + mean.height & 7825417 & 7644249 & \cellcolor{green!50}7572474 & \cellcolor{green!50}7340741 \\
+              \hline
+              multifurc $\sim$ taxa * depth & 8235932 & 7836755 & 7757688 & \cellcolor{green!50}7383808 \\
               multifurc $\sim$ taxa * max.height & 7963438 & 7693555 & 7614820 & \\
@@
         \end{table}
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Unknown leaf nodes}
+    Next to the problem of the multifurcation of the tree is the less of data we have for the species.
+      For the ancestral state reconstruction, we need information in the leaf nodes. \\
+    The eukaryotic synthesis tree has 293 463 leaf nodes. The GloBI database has 5 346 414 interactions 
+      (at this timepoint). Out of this data we got 51 337 distinct free-living species and 47 332 
+      distinct parasite species $\rightarrow$ unknown nodes 2194794 ($\approx 95.7\%$). \\
+    With this only $\approx 4.3\%$ information in our leaf nodes are
+
+    \todo{einbauen?:} \\
+    unused possible species  57 352 (source), \\
+    809 993 (target) \\
+
+    \#interactions zu \#Parasiten und \#Freilebend $\rightarrow$ Wieviel gibt GloBI her? (dazu noch 
+      \#unused possible species, wieviele Parasiten ohne ott haben wir gefunden?)
+
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \subsection{Results of simulation / Influence of different parameters}
+
+    \begin{figure}
+      \caption{Influence of unknown data to prediction}
+      \centering
+      \includegraphics[trim = 0mm 0mm 0mm 50mm, clip,width=0.9\textwidth]{Figures/simulation_evaluation_1.png}
+    \end{figure}
 
@@
       \end{table}
-
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  \section{Results of simulation}
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{Influence of different parameters}
-
-    \begin{figure}
-      \caption{Influence of unknown data to prediction}
-      \centering
-      \includegraphics[width=0.9\textwidth]{Figures/simulation_evaluation_1.png}
-    \end{figure}
 

### 2018-03-05 Paper - Latex/Paper - Skizze - v2.tex
cleanup
Paper - Results - data update

@@
               \hline
-              multifurc $\sim$ taxa * depth & 7714881 & 7335396 & 7250759 & \\
-              multifurc $\sim$ taxa * max.height & 7692980 & 7311241 & 7187504 & \\
-              multifurc $\sim$ taxa * min.height & 7442387 & 7177002 & 7094933 & \\
-              multifurc $\sim$ taxa * mean.height & 7247309 & 7020258 & \cellcolor{green!50}6965794 & \\
+              multifurc $\sim$ taxa * depth & 7714881 & 7335396 & 7250759 & \cellcolor{green!50}6843004 \\
+              multifurc $\sim$ taxa * max.height & 7692980 & 7311241 & 7187504 & \cellcolor{green!50}6795823 \\
+              multifurc $\sim$ taxa * min.height & 7442387 & 7177002 & 7094933 & \cellcolor{green!50}6795099 \\
+              multifurc $\sim$ taxa * mean.height & 7247309 & 7020258 & \cellcolor{green!50}6965794 & \cellcolor{green!50}6665565 \\
               \hline
@@
               multifurc $\sim$ taxa * depth & 8235932 & 7836755 & 7757688 & \cellcolor{green!50}7383808 \\
-              multifurc $\sim$ taxa * max.height & 7963438 & 7693555 & 7614820 & \\
-              multifurc $\sim$ taxa * min.height & 8214030 & 7808940 & 7690618 & \\
-              multifurc $\sim$ taxa * mean.height & 7768360 & \cellcolor{green!50}7536296 & \cellcolor{green!50}7484953 & \\
+              multifurc $\sim$ taxa * max.height & 7963438 & 7693555 & 7614820 & \cellcolor{green!50}7335338 \\
+              multifurc $\sim$ taxa * min.height & 8214030 & 7808940 & 7690618 & \cellcolor{green!50}7336627\\
+              multifurc $\sim$ taxa * mean.height & 7768360 & \cellcolor{green!50}7536296 & \cellcolor{green!50}7484953 & \cellcolor{green!50}7206369 \\
               \hline
@@
     809 993 (target) \\
-
     \#interactions zu \#Parasiten und \#Freilebend $\rightarrow$ Wieviel gibt GloBI her? (dazu noch 

### 2018-03-05 Paper - Latex/Paper - Skizze - v2.tex
Paper - Abstract

@@
 \chapter*{Abstract}
-  \anmerkungstext{Alle Figures richtig beschriften. Generell: Alle Figure captions sollten 
-    selbsterklärend sein. Sprich, ich sollte nur die Caption (normalerweise auch unter dem Bild) 
-    lesen und nicht den Rest das Papers und dann trotzdem verstehen können, was eigentlich passiert 
-    ist und - hilfreich - auch warum das relevant ist. (Bernhard)} \\
-
+  With increasing amounts of data, new investigations are also possible in phylogeny. This work 
+    deals with the ancestral state reconstruction of parasitism in the tree of life of eukaryotes. 
+    To predict states of the unknown species and estimate origins and losses of parasitism. \\
+  We performed an analysis of existing algorithms and applied a Sankoff maximum parsimony algorithm 
+    using the R package Castor \cite{Louca2017}. \\
+  The challenge here is the size of the tree and the little information about it. On the one hand, 
+    such a large phylogenetic tree is not completely existent, and we therefore work with a synthesis 
+    tree of OTL \cite{Hinchliff2015}, which is highly multifurcated. On the other hand, for the 
+    approximately 300 000 leaf nodes we found only for $\approx 4,3\%$ information whether they are 
+    parasitic or free-living species (obtained from the GloBI database \cite{Poelen2014}).
 \tableofcontents
@@
   the ancestral state reconstruction of parasitism. \\
-  \anmerkungstext{Der erste Satz muss nochmal überarbeitet werden. Das Ziel / Ergebnis der Arbeit hat sich 
-    inzwischen geändert} \\
+  \anmerkungstext{Der erste Satz muss nochmal überarbeitet werden. Das Ziel / Ergebnis der Arbeit 
+    hat sich inzwischen geändert} \\
   \anmerkungstext{Wir haben mehr einen Algorithmus getestet und an unserem spezifischen Problem angewendet, 
@@
         \item Was soll erreicht werden? \\
-          Wir wollen vorhandene Algorithm (Sankoff/castor) auf diese Aufgabenstellung hin testen 
+          Wir wollen vorhandene Algorithm (Sankoff/castor \cite{Louca2017}) auf diese Aufgabenstellung hin testen 
           und ihre Vorhersagekraft abschätzen. Außerdem wollen wir den Fitch algorithmus für binäre 
@@
         \item Fitch
-        \item Sankoff (Castor package)
+        \item Sankoff (Castor package \cite{Louca2017}) 
         \item my algorithm
@@
       \subsubsection{Sankoff}
-        Maximum parsimony algorithm from Sankoff implemented in the R package castor.
+        Maximum parsimony algorithm from Sankoff implemented in the R package castor \cite{Louca2017}.
 

### 2018-03-05 Paper - Latex/Paper - Skizze - v2.tex
Paper - Abstract - update

@@
 \chapter*{Abstract}
-  With increasing amounts of data, new investigations are also possible in phylogeny. This work 
+  With increasing amounts of data, new investigations are also possible in phylogeny. This study 
     deals with the ancestral state reconstruction of parasitism in the tree of life of eukaryotes. 
-    To predict states of the unknown species and estimate origins and losses of parasitism. \\
-  We performed an analysis of existing algorithms and applied a Sankoff maximum parsimony algorithm 
-    using the R package Castor \cite{Louca2017}. \\
-  The challenge here is the size of the tree and the little information about it. On the one hand, 
-    such a large phylogenetic tree is not completely existent, and we therefore work with a synthesis 
-    tree of OTL \cite{Hinchliff2015}, which is highly multifurcated. On the other hand, for the 
-    approximately 300 000 leaf nodes we found only for $\approx 4,3\%$ information whether they are 
-    parasitic or free-living species (obtained from the GloBI database \cite{Poelen2014}).
+    We predict unknown states of species and estimate origins and losses of parasitism. \\
+  We performed an analysis of existing algorithms and selected a Sankoff maximum parsimony algorithm 
+    using the R package \textit{Castor} \cite{Louca2017}. \\
+  The challenge here is the size of the tree and the little information about it. \\
+  Such a large phylogenetic tree does not completely exist and therefore we work with a synthesis 
+    tree of OTL \cite{Hinchliff2015} which is highly multifurcated. \\
+  For the 2,535,437 leaf nodes we could not gather much data. From the GloBI database 
+    \cite{Poelen2014} whith we used for this, we could only collect 25,992 parasitic and 34,879 
+    free-living species. It follows that we have only $\approx 2.4\%$ state information. \\
+
+  Nevertheless, the analysis of our results revealed that our forecast is largely credible. \\
+  We have compared the results of some subtrees with known knowledge (Chordata, Nematoda, 
+    Platyhelminthes and Apicomplexa) and except for the Nematoda the results looked very good. In 
+    the case of nematodes, the data situation is strongly shifted to the few parasites. \\
+  Our number of origins we could partly compare with the results of Sara B. Weinstein and Armand M. 
+  Kuris from their article \textit{Independent origins of parasitism in Animalia} \cite{Weinstein2016} 
+    and have come to a similar magnitude. They identified 223 parasitic origins in Metazoa and we 
+    were able to estimate about 300 origins. \\
+
 \tableofcontents

### 2018-03-05 Paper - Latex/Paper - Skizze - v2.tex
pdf
Paper - Abstract - fix

@@
   For the 2,535,437 leaf nodes we could not gather much data. From the GloBI database 
-    \cite{Poelen2014} whith we used for this, we could only collect 25,992 parasitic and 34,879 
+    \cite{Poelen2014} which we used, we could only collect 25,992 parasitic and 34,879 
     free-living species. It follows that we have only $\approx 2.4\%$ state information. \\
@@
   We have compared the results of some subtrees with known knowledge (Chordata, Nematoda, 
-    Platyhelminthes and Apicomplexa) and except for the Nematoda the results looked very good. In 
+    Platyhelminthes and Apicomplexa) and, except for the Nematoda, the results looked very good. In 
     the case of nematodes, the data situation is strongly shifted to the few parasites. \\
-  Our number of origins we could partly compare with the results of Sara B. Weinstein and Armand M. 
+  We could partly compare our number of origins with the results of Sara B. Weinstein and Armand M. 
   Kuris from their article \textit{Independent origins of parasitism in Animalia} \cite{Weinstein2016} 

### 2018-03-06 Paper - Latex/Paper - Skizze - v3.tex
Paper - Abstract - Renards Anmerkungen eingearbeitet; Results - Crosstable hinzugefügt

--- 2018-03-05 Paper - Latex/Paper - Skizze - v2.tex
@@
 \chapter*{Abstract}
-  With increasing amounts of data, new investigations are also possible in phylogeny. This study 
-    deals with the ancestral state reconstruction of parasitism in the tree of life of eukaryotes. 
-    We predict unknown states of species and estimate origins and losses of parasitism. \\
-  We performed an analysis of existing algorithms and selected a Sankoff maximum parsimony algorithm 
-    using the R package \textit{Castor} \cite{Louca2017}. \\
+  This study focuses on the ancestral state reconstruction of parasitism in the tree of life of
+    Eukaryota. We predict unknown states of species and estimate origins and losses of parasitism. \\
   The challenge here is the size of the tree and the little information about it. \\
@@
     free-living species. It follows that we have only $\approx 2.4\%$ state information. \\
-
-  Nevertheless, the analysis of our results revealed that our forecast is largely credible. \\
+  So far, especially small scale studies have been carried out or highly manual. In this scale, it 
+    requires different data sources to be interconnected. \\
+  We performed an analysis of existing algorithms and selected a Sankoff maximum parsimony algorithm 
+    using the R package \textit{Castor} \cite{Louca2017}. \\
+  Nevertheless, the results are convincing and even though purely computational approach which did 
+    not include human experts input, results coincide with prior knowledge. Also regarding the number 
+    of events, our estimates coincide with previous results by human experts, e.g. the study by 
+    Weinstein and Kuris \cite{Weinstein2016}. \\
+
+  ------------ \\
+
+  \anmerkungstext{Klassisch packt man keine Referenzen in Abstracts (bzw. wenn das meist als 
+    Kurzreferenz also (Author et al., 2017). (Bernhard)} \\
   We have compared the results of some subtrees with known knowledge (Chordata, Nematoda, 
     Platyhelminthes and Apicomplexa) and, except for the Nematoda, the results looked very good. In 
-    the case of nematodes, the data situation is strongly shifted to the few parasites. \\
+    the case of Nematoda, the data situation is strongly shifted to the few parasites. \\
   We could partly compare our number of origins with the results of Sara B. Weinstein and Armand M. 
-  Kuris from their article \textit{Independent origins of parasitism in Animalia} \cite{Weinstein2016} 
+  Kuris from their article \textit{Independent origins of parasitism in Animalia}  
     and have come to a similar magnitude. They identified 223 parasitic origins in Metazoa and we 
@@
                 \hline \hline
-              multifurc $\sim$ taxa & 7774454 & 7435700 & 7337241 & 7076068 \\
-              \hline
-              multifurc $\sim$ taxa + depth & 7752303 & 7431609 & 7334754 & 7027578 \\
-              multifurc $\sim$ taxa + max.height & 7730196 & 7375889 & 7275856 & 7005424 \\
-              multifurc $\sim$ taxa + min.height & 7472500 & 7233486 & 7144686 & \cellcolor{green!50}6890703 \\
-              multifurc $\sim$ taxa + mean.height & 7304402 & 7128318 & 7055313 & \cellcolor{green!50}6815271 \\
-              \hline
-              multifurc $\sim$ taxa * depth & 7714881 & 7335396 & 7250759 & \cellcolor{green!50}6843004 \\
-              multifurc $\sim$ taxa * max.height & 7692980 & 7311241 & 7187504 & \cellcolor{green!50}6795823 \\
-              multifurc $\sim$ taxa * min.height & 7442387 & 7177002 & 7094933 & \cellcolor{green!50}6795099 \\
-              multifurc $\sim$ taxa * mean.height & 7247309 & 7020258 & \cellcolor{green!50}6965794 & \cellcolor{green!50}6665565 \\
+                multifurc $\sim$ taxa & 7774454 & \cellcolor{green!10}7435700 & \cellcolor{green!15}7337241 & \cellcolor{green!30}7076068 \\
+                \hline
+                multifurc $\sim$ taxa + depth & 7752303 & \cellcolor{green!10}7431609 & \cellcolor{green!15}7334754 & \cellcolor{green!30}7027578 \\
+                multifurc $\sim$ taxa + max.height & 7730196 & \cellcolor{green!15}7375889 & \cellcolor{green!20}7275856 & \cellcolor{green!30}7005424 \\
+                multifurc $\sim$ taxa + min.height & \cellcolor{green!10}7472500 & \cellcolor{green!20}7233486 & \cellcolor{green!25}7144686 & \cellcolor{green!40}6890703 \\
+                multifurc $\sim$ taxa + mean.height & \cellcolor{green!15}7304402 & \cellcolor{green!25}7128318 & \cellcolor{green!30}7055313 & \cellcolor{green!40}6815271 \\
+                \hline
+                multifurc $\sim$ taxa * depth & 7714881 & \cellcolor{green!15}7335396 & \cellcolor{green!20}7250759 & \cellcolor{green!40}6843004 \\
+                multifurc $\sim$ taxa * max.height & \cellcolor{green!5}7692980 & \cellcolor{green!15}7311241 & \cellcolor{green!25}7187504 & \cellcolor{green!45}6795823 \\
+                multifurc $\sim$ taxa * min.height & \cellcolor{green!10}7442387 & \cellcolor{green!25}7177002 & \cellcolor{green!30}7094933 & \cellcolor{green!45}6795099 \\
+                multifurc $\sim$ taxa * mean.height & \cellcolor{green!20}7247309 & \cellcolor{green!30}7020258 & \cellcolor{green!35}6965794 & \cellcolor{green!50}6665565 \\
                 \hline
@@
 
-        \begin{lstlisting}[gobble=8]
-          class * depth / min/max/mean.height: Warning message: glm.fit: fitted rates numerically 0 occurred
-          order * depth / min/max/mean.height: Error: cannot allocate vector of size 2.2 Gb
-        \end{lstlisting}
+        \begin{figure}
+          \centering
+          \includegraphics[trim = 0mm 0mm 0mm 0mm, clip,width=0.95\textwidth]{Figures/Kreuztabelle_Residuals.JPG}
+          \caption{Crosstable of Residual values}
+        \end{figure}
 
@@
               \hline \hline
-              multifurc $\sim$ taxa & 8273333 & 7937828 & 7842157 & 7644249\\
-              \hline
-              multifurc $\sim$ taxa + depth & 8273318 & 7934322 & 7839364 & \cellcolor{green!50}7539999 \\
-              multifurc $\sim$ taxa + max.height & 7993515 & 7749121 & 7661817 & \cellcolor{green!50}7416211 \\
-              multifurc $\sim$ taxa + min.height & 8251211 & 7875521  & 7778327 & \cellcolor{green!50}7516883 \\
-              multifurc $\sim$ taxa + mean.height & 7825417 & 7644249 & \cellcolor{green!50}7572474 & \cellcolor{green!50}7340741 \\
-              \hline
-              multifurc $\sim$ taxa * depth & 8235932 & 7836755 & 7757688 & \cellcolor{green!50}7383808 \\
-              multifurc $\sim$ taxa * max.height & 7963438 & 7693555 & 7614820 & \cellcolor{green!50}7335338 \\
-              multifurc $\sim$ taxa * min.height & 8214030 & 7808940 & 7690618 & \cellcolor{green!50}7336627\\
-              multifurc $\sim$ taxa * mean.height & 7768360 & \cellcolor{green!50}7536296 & \cellcolor{green!50}7484953 & \cellcolor{green!50}7206369 \\
+              multifurc $\sim$ taxa & 8273333 & \cellcolor{green!15}7937828 & \cellcolor{green!20}7842157 & \cellcolor{green!30}7644249\\
+              \hline
+              multifurc $\sim$ taxa + depth & 8273318 & \cellcolor{green!15}7934322 & \cellcolor{green!20}7839364 & \cellcolor{green!35}7539999 \\
+              multifurc $\sim$ taxa + max.height & \cellcolor{green!15}7993515 & \cellcolor{green!25}7749121 & \cellcolor{green!30}7661817 & \cellcolor{green!40}7416211 \\
+              multifurc $\sim$ taxa + min.height & 8251211 & \cellcolor{green!20}7875521  & \cellcolor{green!25}7778327 & \cellcolor{green!35}7516883 \\
+              multifurc $\sim$ taxa + mean.height & \cellcolor{green!20}7825417 & \cellcolor{green!30}7644249 & \cellcolor{green!35}7572474 & \cellcolor{green!45}7340741 \\
+              \hline
+              multifurc $\sim$ taxa * depth & 8235932 & \cellcolor{green!20}7836755 & \cellcolor{green!25}7757688 & \cellcolor{green!45}7383808 \\
+              multifurc $\sim$ taxa * max.height & \cellcolor{green!15}7963438 & \cellcolor{green!30}7693555 & \cellcolor{green!30}7614820 & \cellcolor{green!45}7335338 \\
+              multifurc $\sim$ taxa * min.height & 8214030 & \cellcolor{green!20}7808940 & \cellcolor{green!30}7690618 & \cellcolor{green!45}7336627\\
+              multifurc $\sim$ taxa * mean.height & \cellcolor{green!25}7768360 & \cellcolor{green!35}7536296 & \cellcolor{green!50}7484953 & \cellcolor{green!50}7206369 \\
               \hline
@@
         \end{table}
+
+        \begin{figure}
+          \centering
+          \includegraphics[trim = 0mm 0mm 0mm 0mm, clip,width=0.95\textwidth]{Figures/Kreuztabelle_BIC.JPG}
+          \caption{Crosstable of BIC values}
+        \end{figure}
 
@@
     \begin{figure}
-      \caption{Influence of unknown data to prediction}
       \centering
       \includegraphics[trim = 0mm 0mm 0mm 50mm, clip,width=0.9\textwidth]{Figures/simulation_evaluation_1.png}
+      \caption{Influence of unknown data to prediction}
     \end{figure}

### 2018-03-06 Paper - Latex/Paper - Skizze - v3.tex
Paper - Methods - Workflows updated

@@
     \centering
-    \includegraphics[width=0.4\textwidth]{Figures/Workflow-overview.png}
+    \includegraphics[width=0.55\textwidth]{Figures/Workflow-overview.png}
     \caption{Workflow \\
@@
     \label{fig:workflow}
-  \end{figure} \\
-  \todo{Metadata analysis nötig für run maximum parsimony?} \\
+  \end{figure}
 
@@
   \begin{figure}[h!]
-    \caption{Workflow}
     \centering
+    \includegraphics[width=1\textwidth]{Figures/Workflow.png}
+    \caption{Big overview of the whole Workflow}
     \label{fig:Workflow}
-    \includegraphics[width=1\textwidth]{Figures/Workflow.png}
   \end{figure}
@@
     For our research we need two types of data: a tree and information about the states. \\
-    For the tree we decided to use Open Tree of Life (OTL), because it's the biggest available synthesis 
-      tree. \\
-    \todo{hier referenzen zu nem paper das das bestätigt o.ä.} \\
-    For the state information, we decided to use the Global biotic interaction database (GloBI). Also in 
-      this case, this is one of the largest databases and both OTL and GloBI support the OTT 
-      identification. OTT (open tree taxonomy) is a taxonomy that assigns to each species a unique id, 
-      both ancestor and now living species (internal and leaf nodes).
+    For the tree we decided to use Open Tree of Life (OTL). \\
+    For the state information, we decided to use the Global biotic interaction database (GloBI).
 

### 2018-03-06 Paper - Latex/Paper - Skizze - v3.tex
Paper - move properties of OTL tree to the appendix

@@
 
-      %---------------------------------------------------------------------------------------------------
-      \subsubsection{Distribution of Taxa}
-        - In our tree we can distinguish 28 different Taxa with the OTL taxonomic tree. \\
-        - The most of them are hardly represented. The major taxonomic groups are: ... \\
-        - Here you can see some characteristics of the Multifurcation of the tree. \\
-        \begin{figure}[h!]
-          \centering
-          \includegraphics[width=0.9\textwidth]{Figures/TaxaTable2.JPG}
-          \caption{Distribution of Nodes in Rank-Cathegories}
-          \label{fig:taxaTable2}
-        \end{figure}
-        In a phylogeny, the taxonomic division of the tree is far too coarse, meaning that there should 
-          be more subtaxa or 'unranked' nodes. But the closer we get to the root, the more the pure
-          taxonomic tree is reflected. If the tree were binary, the taxa would have to double. But the 
-          multipliers for some are much bigger and for others much smaller, which you can see in in figure 
-          \ref{fig:taxaTable2}. \\
-        Please see the appendix on page \pageref{sec:taxaTable2} for a complete table \ref{sec:taxaTable2} 
-          of these data. \\
-        \todo{Was hierzu ist richtig und wichtig?}
-
-      %---------------------------------------------------------------------------------------------------
-      \subsubsection{Distribution of data in the taxa}
-        Mithilfe des taxonomischen Baums von OTL haben wir die Knoten ihren Kingdoms, Phyla und Classes 
-          zugeteilt. \\
-        Please see the appendix on page \pageref{sec:taxaTable1} for a complete table \ref{sec:taxaTable1} 
-          of these data. \\
-        \todo{gibt es einen Zusammenhang zwischen Anzahl} \\
-        \todo{max max height zu anzahl nodes in phylum plotten? oder mean max height oder ... 
-          (mean, min height...)} \\
-        \todo{depth...}
+      We took a closer look at some of the features of the Synthesis tree. On the one hand the 
+        distribution of the taxa and on the other the distribution of the nodes on the taxa. Since this
+        is not directly relevant to our study, there is a section in the appendix \ref{sec:otl analysis}.
 
@@
         \cite{CavalierSmith1981}. \\
-      In section \pageref{sec:listPhyla} of the appendix you can find a list of all phyla.
+      In section \pageref{subsec:listPhyla} of the appendix you can find a list of all phyla.
 
@@
   %---------------------------------------------------------------------------------------------------
-  \section{List of all phyla}\label{sec:listPhyla}
+  \section{OTL analysis}\label{sec:otl analysis}
+
+    %---------------------------------------------------------------------------------------------------
+    \subsection{List of all phyla}\label{subsec:listPhyla}
 
@@
     %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  \section{Distribution of data in the taxa}\label{sec:taxaTable1}
-    \begin{center}
-      \begin{tabular}{ |l|r|l|r|r| }
-        \hline
-        Kingdom (3) & Number of Nodes & Phylum (25) & Number of Nodes & max max height \\
-        \hline \hline
-        Metazoa & 1 465 207 & Arthropoda & 1 170 539 & 54 \\
-        & & Chordata & 106 650 & 74 \\
-        & & Mollusca & 80 022 & 22 \\
-        & & Platyhelminthes & 27 141 & 9 \\
-        & & Nematoda & 24 564 & 23 \\
-        & & Cnidaria & 14 878 & 36 \\
-        & & Porifera & 11 737 & 26 \\
-        & & Echinodermata & 10 654 & 14 \\
-        & & Bryozoa & 8 631 & 11 \\
-        & & Rotifera & 3 093 & 7 \\
-        & & Nemertea & 1 793 & 7 \\
-        & & Tardigrada & 1 654 & 7 \\
-        & & Acanthocephala & 1 596 & 6 \\
-        & & Brachiopoda & 1 055 & 9 \\
-        & & Nematomorpha & 633 & 7 \\
-        & & Chaetognatha & 360 & 7 \\
-        & & Hemichordata & 196 & 5 \\ 
-        & & Cycliophora & 11 & 5 \\ 
-        % 1465207-(1170539+106650+80022+27141+24564+14878+11737+10654+8631+3093+1793+1654+1596+1055+633+360+196+11) = 0          \hline
-        Fungi & 254 871 & Ascomycota & 157 045 & 19 \\ 
-        & & Basidiomycota & 92 931 & 18 \\
-        & & Microsporidia & 1 949 & 6 \\ 
-        & & Glomeromycota & 1 490 & 6 \\
-        & & Chytridiomycota & 1 456 & 6 \\
-        % 254871-157045-92931-1949-1490-1456 = 0
-        \hline
-        Chloroplastida & 121 239 & Streptophyta & 120 731 & 49 \\
-        & & Chlorophyta & 508 & 6 \\
-        % 121239-120731-508 = 0
-        \hline  
-      \end{tabular}
-    \end{center}
-
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  \section{Taxa table}\label{sec:taxaTable2}
+    \subsubsection{Distribution of Taxa}
+    - In the tree we can distinguish 28 different Taxa with the OTL taxonomic tree. \\
+    - The most of them are hardly represented. The major taxonomic groups are: ... \\
+    - Here you can see some characteristics of the Multifurcation of the tree. \\
+    \begin{figure}[h!]
+      \centering
+      \includegraphics[width=0.9\textwidth]{Figures/TaxaTable2.JPG}
+      \caption{Distribution of Nodes in Rank-Cathegories}
+      \label{fig:taxaTable2}
+    \end{figure}
+    In a phylogeny, the taxonomic division of the tree is far too coarse, meaning that there should 
+      be more subtaxa or 'unranked' nodes. But the closer we get to the root, the more the pure
+      taxonomic tree is reflected. If the tree were binary, the taxa would have to double. But the 
+      multipliers for some are much bigger and for others much smaller, which you can see in in figure 
+      \ref{fig:taxaTable2}. \\
+      ... (see Table \ref{table:...})
+
+    \begin{table}[h!]
       \begin{center}
@@
         \end{tabular}
+        \caption{\todo{...}}
+        \label{table:...} 
       \end{center}  
+    \end{table}
     extended leaf nodes (real leaf nodes)
 
+  %---------------------------------------------------------------------------------------------------
+  \subsubsection{Distribution of data in the taxa}
+    Mithilfe des taxonomischen Baums von OTL haben wir die Knoten ihren Kingdoms, Phyla und Classes 
+      zugeteilt (see Table \ref{table:...}). \\
+
+    \begin{table}[h]
+      \begin{center}
+        \begin{tabular}{ |l|r|l|r|r| }
+          \hline
+          Kingdom (3) & Number of Nodes & Phylum (25) & Number of Nodes & max max height \\
+          \hline \hline
+          Metazoa & 1 465 207 & Arthropoda & 1 170 539 & 54 \\
+          & & Chordata & 106 650 & 74 \\
+          & & Mollusca & 80 022 & 22 \\
+          & & Platyhelminthes & 27 141 & 9 \\
+          & & Nematoda & 24 564 & 23 \\
+          & & Cnidaria & 14 878 & 36 \\
+          & & Porifera & 11 737 & 26 \\
+          & & Echinodermata & 10 654 & 14 \\
+          & & Bryozoa & 8 631 & 11 \\
+          & & Rotifera & 3 093 & 7 \\
+          & & Nemertea & 1 793 & 7 \\
+          & & Tardigrada & 1 654 & 7 \\
+          & & Acanthocephala & 1 596 & 6 \\
+          & & Brachiopoda & 1 055 & 9 \\
+          & & Nematomorpha & 633 & 7 \\
+          & & Chaetognatha & 360 & 7 \\
+          & & Hemichordata & 196 & 5 \\ 
+          & & Cycliophora & 11 & 5 \\ 
+          % 1465207-(1170539+106650+80022+27141+24564+14878+11737+10654+8631+3093+1793+1654+1596+1055+633+360+196+11) = 0          \hline
+          Fungi & 254 871 & Ascomycota & 157 045 & 19 \\ 
+          & & Basidiomycota & 92 931 & 18 \\
+          & & Microsporidia & 1 949 & 6 \\ 
+          & & Glomeromycota & 1 490 & 6 \\
+          & & Chytridiomycota & 1 456 & 6 \\
+          % 254871-157045-92931-1949-1490-1456 = 0
+          \hline
+          Chloroplastida & 121 239 & Streptophyta & 120 731 & 49 \\
+          & & Chlorophyta & 508 & 6 \\
+          % 121239-120731-508 = 0
+          \hline  
+        \end{tabular}
+        \caption{\todo{...}}
+        \label{table:...} 
+      \end{center}  
+    \end{table}
+
 \end{document}

### 2018-03-07 code/build_metadata-run_castor.sh
generalize scripts

@@ -11,11 +11,11 @@ python3 -m code.metadata.extract_globi_data > logs/log-extract_globi_data.txt
 echo "$(tput setaf 1)$(tput setab 7)------- Free-livings and Parasites extracted (3/7) --------$(tput sgr 0)" 1>&3
 python3 -m code.metadata.build_subtree ott304358 Eukaryota > logs/log-build_subtrees.txt
 echo "$(tput setaf 1)$(tput setab 7)------- Subtrees builded(4/7) --------$(tput sgr 0)" 1>&3
-python3 -m code.metadata.build_nodelist > logs/log-build_nodelist.txt
+python3 -m code.metadata.build_nodelist Eukaryota > logs/log-build_nodelist.txt
 echo "$(tput setaf 1)$(tput setab 7)------- Nodelists builded(5/7) --------$(tput sgr 0)" 1>&3
 
 # -------- -------- run castor files -------- -------- #
-python3 -m code.castor.run_castor > logs/log-run_castor.txt
+python3 -m code.castor.run_castor Eukaryota > logs/log-run_castor.txt
 echo "$(tput setaf 1)$(tput setab 7)------- Maximum Parsimony: Sankoff (Castor) ready(6/7) --------$(tput sgr 0)" 1>&3
 
 # -------- -------- build more metadata files -------- -------- #

### 2018-03-07 code/castor/run_castor.py

@@ -1,13 +1,20 @@
 """Maximum parsimony algorithm from Sankoff implemented in the R package castor"""
-
 import csv
 import datetime
+import sys
 from code.utilities.castor_util import sankoff_parsimony
-from code.utilities.Helpers import find_element_in_nodelist, print_time
+from code.utilities.Helpers import print_time
 from time import gmtime, strftime
 
-from Bio import Phylo
 from termcolor import colored
+
+# input arguments
+args = sys.argv
+
+# values from  input:
+subtree_name = sys.argv[1]
+
+# examples: 'Eukaryota'
 
 # global variables:
 START_TIME = datetime.datetime.now().replace(microsecond=0)
@@ -19,13 +26,13 @@ def main():
     global START_TIME
     global CURRENT_TIME
 
-    print('Run castor - Sankoff parsimony - for Eukaryota')
+    print('Run castor - Sankoff parsimony - for ', subtree_name)
 
     print(colored("---------------- Sankoff parsimony ----------------", "green"))
     nodelist = sankoff_parsimony(-1)
     CURRENT_TIME = print_time(CURRENT_TIME)
     print(colored("---------------- Save nodelist ----------------", "green"))
-    nodelist_path = './data/nodelist/Eukaryota-castor.csv' 
+    nodelist_path = './data/nodelist/' + subtree_name + '-castor.csv' 
     header = ['ott_id', 'originaltag', 'finaltag', 'depth', 'heights', 'nr_children']
     with open(nodelist_path, 'w') as nodelist_file:
         writer = csv.writer(nodelist_file, delimiter=',')

### 2018-03-07 Paper - Latex/Paper - Skizze - v3.tex
Paper - Results - change Cross evaluation data

@@
     \subsection{Cross evaluation - leave 100 out}
-      We ran the castor algorithm (\todo{10000}) 10 times with leaving 100 randomized free-living or 
+      We ran the castor algorithm (\todo{10000}) 70 times with leaving 100 randomized free-living or 
         parasitic species out of the input data to see how stable our result is. \\
@@
       \end{itemize}
-      \begin{table}
-        \begin{center}
-          \begin{tabular}{ |c||r|r|r||c|r| }
-            \hline
-            run & \multicolumn{3}{c||}{distance} & changed & lost \\
-            & all nodes & leaf nodes & internal nodes & tag & tag \\
-            \hline \hline
-            0 & 4.0 & 4.0 & 0.0 & 4 & 48 \\
-            1 & 4.0 & 4.0 & 0.0 & 2 & \cellcolor{green!50}45 \\
-            2 & 85.3 & 79.3 & 6.0 & 3 & 51 \\
-            3 & 1.0 & 1.0 & 0.0 & 1 & 47 \\
-            \rowcolor{red!50}4 & 1248.0 & 1230.5 & 17.5 & \cellcolor{green!50}0 & 54 \\
-            5 & 169.0 & 168.0 & 1.0 & 3 & 52 \\
-            6 & 1.0 & 1.0 & 0.0 & 1 & 48 \\
-            7 & 1.0 & 1.0 & 0.0 & 1 & 53 \\
-            8 & 1.0 & 1.0 & 0.0 & 1 & \cellcolor{red!50}54 \\
-            9 & 1.0 & 1.0 & 0.0 & 1 & 52 \\
-            \hline
-          \end{tabular}
-        \end{center}
-        \caption{Example runs. \\ green: min value, red: max value}
-      \end{table}
 
@@
             \hline \hline
-            \multirow{3}{*}{distance} & all & 1.0 & 1248.0 & 151.53 & 151528.92 \\
-            & leaf nodes                    & 1.0 & 1230.5 & 149.08 & 147380.74 \\
-            & internal nodes                & 0.0 & 17.5 & 2.45 & 31.47 \\ \hline
-            \multicolumn{2}{|c||}{changed tag} & 0.0 & 4.0 & 1.7 & 1.57 \\ \hline
-            lost tag & all tags             & 45.0 & 54.0 & \cellcolor{green!50}50.40 & 10.04 \\
-            & FL tags                       & 16.0 & 32.0 & 23.10 & 18.77 \\
-            & P tags                        & 16.0 & 36.0 & 27.30 & 41.34 \\
+            \multirow{3}{*}{distance} & all   & 0 & 3587.70 & 199.68 & 253570.50 \\
+            & leaf nodes                      & 0 & 3021.12 & 185.59 & 194202.16 \\
+            & internal nodes                  & 0 & 566.58 & 14.08 & 5207.58 \\ \hline
+            \multicolumn{2}{|c||}{changed tag} & 0 & 0 & 0 & 0 \\ \hline
+            \multirow{3}{*}{lost} & all tags  & 100 & 100 & 100 & 0 \\
+            & FL tags                         & 44 & 66 & 57.24 & 20.08 \\
+            & P tags                          & 34 & 56 & 42.76 & 20.08 \\
             \hline
@@
         \caption{Statistics to Cross validation}
+      \end{table}
+
+      \begin{table}
+        \begin{center}
+          \begin{tabular}{ |cl||r|r|r|r| }
+            \hline
+            & & min & max & mean & variance \\
+            \hline \hline
+            \rowcolor{green!50}distance & all   & 1 & 2 & 1.33 & 0.33 \\
+            \rowcolor{orange!50}&               & 0 & 3587.70 & 217.94 & 273760.68 \\
+            \rowcolor{green!50}& leaf nodes     & 1 & 2 & 1.33 & 0.33 \\
+            \rowcolor{orange!50}&               & 0 & 3021.12 & 202.57 & 209274.86 \\
+            \rowcolor{green!50}& internal nodes& 0 & 0 & 0.00 & 0.00 \\
+            \rowcolor{orange!50}&               & 0 & 566.58 & 15.37 & 5684.00 \\ \hline
+            \rowcolor{green!50}lost & FL tags   & 44 & 49 & 46.67 & 6.33 \\
+            \rowcolor{orange!50}&               & 51 & 66 & 57.95 & 13.47 \\
+            \rowcolor{green!50}& P tags         & 51 & 56 & 53.33 & 6.33 \\
+            \rowcolor{orange!50}&               & 34 & 49 & 42.05 & 13.47 \\
+            \hline
+          \end{tabular}
+        \end{center}
+        \caption{Statistics to Cross validation \\
+          - \colorbox{green!50}{Less free-livings - 3 examples} \\
+          - \colorbox{orange!50}{Less parasites - 64 examples}}
       \end{table}

### 2018-03-07 code/evaluation/cross_validation.py

@@ -30,7 +30,7 @@ def main():
     print(len(nodelist))
 
     print(colored("---------------- read leave 100 out nodelists ----------------", "green"))
-    for i in range(0, 10):
+    for i in range(0, 70):
         print("run:", i)
         index = 0
         changed_tag = 0
@@ -41,7 +41,7 @@ def main():
         distance_leaf = 0
         distance_inner = 0
 
-        nodelist_path = './data/evaluation/Eukaryota' + str(i) + '-100-castor.csv' 
+        nodelist_path = './data/evaluation/Eukaryota' + str(i) + '-castor.csv' 
         #                0    1              2       3       4           5
         # nodelist    - [id, originaltag, finaltag, depth, heights, nr_children]
         with open(nodelist_path, 'r') as csv_file:
@@ -72,13 +72,18 @@ def main():
                         else:
                             print('Error: the nodelist entry-otts are unequal:')
                             print(nodelist[index][0], '!=', ott_id)
-                    # else:
-                    #     print(row)
                     index += 1
-        print('current list had', index, 'lines')
-        print(index - len(nodelist), 'lines where skipped')
         cross_evaluation_results.append([i, distance, distance_leaf, distance_inner, changed_tag, loose_tag, loose_FL, loose_P])
-    pprint(cross_evaluation_results)
+    # pprint(cross_evaluation_results)
+    
+    less_FL_results = []
+    less_P_results = []
+    for element in cross_evaluation_results:
+        if element[6] < 45:
+            less_FL_results.append(element)
+        if element[7] < 45:
+            less_P_results.append(element)
+
     cross_evaluation_results = array(cross_evaluation_results)
     print("distance:")
     print(stats.describe(cross_evaluation_results[:, 1]))
@@ -94,6 +99,37 @@ def main():
     print(stats.describe(cross_evaluation_results[:, 6]))
     print("loose_P:")
     print(stats.describe(cross_evaluation_results[:, 7]))
+
+    print('---- less FL and less P ----')
+
+    
+    print(len(less_FL_results))
+    print(len(less_P_results))
+    less_FL_results = array(less_FL_results)
+    less_P_results = array(less_P_results)
+
+    print("distance:")
+    print(stats.describe(less_FL_results[:, 1]))
+    print(stats.describe(less_P_results[:, 1]))
+    print("distance_leaf:")
[…]

### 2018-03-10 Paper - Latex/Paper - Skizze - v3.tex
cross validation with full data

@@
             \hline
-            & & min & max & mean & variance \\
-            \hline \hline
-            \multirow{3}{*}{distance} & all   & 0 & 3587.70 & 199.68 & 253570.50 \\
-            & leaf nodes                      & 0 & 3021.12 & 185.59 & 194202.16 \\
-            & internal nodes                  & 0 & 566.58 & 14.08 & 5207.58 \\ \hline
-            \multicolumn{2}{|c||}{changed tag} & 0 & 0 & 0 & 0 \\ \hline
-            \multirow{3}{*}{lost} & all tags  & 100 & 100 & 100 & 0 \\
-            & FL tags                         & 44 & 66 & 57.24 & 20.08 \\
-            & P tags                          & 34 & 56 & 42.76 & 20.08 \\
+            & & min & max & mean & variance ($\sigma^2$) & $\sigma$ \\
+            \hline \hline
+            \multirow{3}{*}{distance} & all   & 0 & 3587.70 & 224.96 & 313650.61 & 560.05 \\
+            & leaf nodes                      & 0 & 3021.12 & 208.69 & 248103.38 & 498.10 \\
+            & internal nodes                  & 0 & 566.58 & 16.28 & 4927.95 & 70.20 \\ \hline
+            \multicolumn{2}{|c||}{changed tag} & 0 & 0 & 0 & 0 & 0 \\ \hline
+            \multirow{3}{*}{lost} & all tags  & 100 & 100 & 100 & 0 & 0 \\
+            & FL tags                         & 44 & 66 & 57.25 & 19.50 & 4.42 \\
+            & P tags                          & 34 & 56 & 42.75 & 19.50 & 4.42 \\
             \hline

### 2018-03-10 code/castor/run_castor.py

@@ -4,7 +4,6 @@ import datetime
 import sys
 from code.utilities.castor_util import sankoff_parsimony
 from code.utilities.Helpers import print_time
-from time import gmtime, strftime
 
 from termcolor import colored
 

### 2018-03-10 code/evaluation/cross_validation.py

@@ -25,13 +25,17 @@ def main():
                 ott_id = row[0]
                 originaltag = row[1]
                 finaltag = float(row[2])
+                depth = row[3]
                 nr_children = row[5]
-                nodelist.append([ott_id, originaltag, finaltag, nr_children])
+                run = []
+                new_finaltag = []
+                correct_predicted = ""
+                nodelist.append([ott_id, originaltag, finaltag, depth, nr_children, run, new_finaltag, correct_predicted])
     print(len(nodelist))
 
     print(colored("---------------- read leave 100 out nodelists ----------------", "green"))
-    for i in range(0, 70):
-        print("run:", i)
+    for run in range(0, 100):
+        print("run:", run)
         index = 0
         changed_tag = 0
         loose_tag = 0
@@ -41,7 +45,7 @@ def main():
         distance_leaf = 0
         distance_inner = 0
 
-        nodelist_path = './data/evaluation/Eukaryota' + str(i) + '-castor.csv' 
+        nodelist_path = './data/evaluation/Eukaryota' + str(run) + '-castor.csv' 
         #                0    1              2       3       4           5
         # nodelist    - [id, originaltag, finaltag, depth, heights, nr_children]
         with open(nodelist_path, 'r') as csv_file:
@@ -55,6 +59,22 @@ def main():
                     if index < len(nodelist):
                         if nodelist[index][0] == ott_id:
                             if originaltag != nodelist[index][1]:
+                                # ----------------------------------
+                                nodelist[index][5].append(run)
+                                nodelist[index][6].append(finaltag)
+                                if float(nodelist[index][1])-1 == finaltag:
+                                    if nodelist[index][7] == 'False':
+                                        print('different prediction!')
+                                        nodelist[index][7] = 'True$False'
+                                    else:
+                                        nodelist[index][7] = 'True'
+                                else: 
+                                    if nodelist[index][7] == 'True':
+                                        print('different prediction!')
+                                        nodelist[index][7] = 'True$False'
+                                    else:
+                                        nodelist[index][7] = 'False'
+                                # ----------------------------------
                                 if originaltag != 'NA':
                                     changed_tag += 1
                                 else:
@@ -64,7 +84,7 @@ def main():
                                     else:
                                         loose_P += 1
[…]

### 2018-03-10 code/metadata/extend_nodelist.py

@@ -3,7 +3,8 @@ import pandas as pd
 # We do an SQL LEFT OUTER JOIN.
 
 ott_taxa = pd.read_csv('./data/interaction_data/ott_taxa.csv', encoding='utf-8')
-nodelist = pd.read_csv('./data/nodelist/Eukaryota-castor.csv', encoding='utf-8')
+# nodelist = pd.read_csv('./data/nodelist/Eukaryota-castor.csv', encoding='utf-8')
+nodelist = pd.read_csv('./data/evaluation/Eukaryota-cross_evaluation.csv', encoding='utf-8')
 merged = pd.merge(nodelist, ott_taxa, how='left', on='ott_id')
 
 print(len(nodelist),'merge', len(ott_taxa), '->', len(merged))
@@ -29,7 +30,8 @@ print('class taxa added')
 
 order_mapping = pd.read_csv('./data/nodelist/Eukaryota-order_mapping.csv', encoding='utf-8')
 merged = pd.merge(merged, order_mapping, how='left', on='ott_id')
-merged.to_csv('./results/Eukaryota-taxa.csv', index=False, encoding='utf-8')
+# merged.to_csv('./results/Eukaryota-taxa.csv', index=False, encoding='utf-8')
+merged.to_csv('./results/Eukaryota-cross_evaluation-taxa.csv', index=False, encoding='utf-8')
 
 print('merge', len(order_mapping))
 print('order taxa added')

### 2018-03-10 code/metadata/analyse_input.R
analyse globi input

@@ -28,24 +28,12 @@ all.taxa <- cbind(all.taxa, heights)
 ## which Phylum in which Kingdom:
 # table(all.taxa$kingdom, all.taxa$phylum)
 
-summary(all.taxa$nr_children)
+# summary(all.taxa$nr_children)
 ## [Min. 1st Qu.  Median    Mean 3rd Qu.    Max. ] over all phyla - max height
 # tapply(all.taxa$max.height, all.taxa$phylum, summary)
 
 ### all nodes sorted by rank
-table(all.taxa$rank)[order(table(all.taxa$rank))]
-
-### find out what is going on here...
-# print('------------------------ all.taxa$nr_children==1 --------------------------')
-# table(all.taxa[all.taxa$nr_children==1, "finaltag"])
-# print('---------------- nr_children==1 ---------------------')
-# table(all.taxa[all.taxa$nr_children==1, "rank"])
-# print('---------------- nr_children==1 & max.height>2 ---------------------')
-# table(all.taxa[all.taxa$nr_children==1 & all.taxa$max.height>2, "rank"])
-# print('--------------------------------------------------')
-# table(all.taxa[all.taxa$nr_children==1 & all.taxa$max.height>2, "finaltag"])
-# print('--------------------------------------------------')
-# table(all.taxa[all.taxa$nr_children==1 & all.taxa$max.height==2, "finaltag"])
+# table(all.taxa$rank)[order(table(all.taxa$rank))]
 
 print('--------------------------------------------------')
 
@@ -76,16 +64,18 @@ inner.taxa$multifurc <- inner.taxa$nr_children-1
 #     labs(x="number of children", y="number of nodes")
 # ggsave("multifurc.pdf")
 
-print('--------------------------------------------------')
 
-null.furc.mod <- glm(multifurc~1, data=inner.taxa,
-                   family="poisson")
+print('--------------------------------------------------')
+print('-------------------------multifurc data-------------------------')
+print('--------------------------------------------------')
+# null.furc.mod <- glm(multifurc~1, data=inner.taxa,
+#                    family="poisson")
 
 print('------------------------kingdom - phylum - class - order--------------------------')
 
[…]

### 2018-03-11 code/metadata/analyse_input.R
analyse input -> unknown data

@@ -302,12 +302,6 @@ print('--------------------------------------------------')
 leaf.taxa$globi.data <- !is.na(leaf.taxa$originaltag)
 null.globi.mod <- glm(globi.data~1, data=leaf.taxa, family="binomial")
 
-# summary(phylum.globi.mod)
-
-# effect("phylum", phylum.globi.mod)
-
-# anova(null.globi.mod, phylum.globi.mod)
-
 # phylum.globi.mod$aic
 
 # kingdom.globi.mod$aic
@@ -317,30 +311,33 @@ print('------------------------kingdom - phylum - class - order-----------------
 
 kingdom.globi.mod <- glm(globi.data~kingdom, data=leaf.taxa, family="binomial")
 print(c('BIC=',  BIC(kingdom.globi.mod)))
+effect("kingdom", kingdom.globi.mod)
 
 phylum.globi.mod <- glm(globi.data~phylum, data=leaf.taxa, family="binomial")
 print(c('BIC=',  BIC(phylum.globi.mod)))
+effect("phylum", phylum.globi.mod)
 
 class.globi.mod <- glm(globi.data~class, data=leaf.taxa, family="binomial")
 print(c('BIC=',  BIC(class.globi.mod)))
+effect("class", class.globi.mod)
 
-order.globi.mod <- glm(globi.data~order, data=leaf.taxa, family="binomial")
-print(c('BIC=',  BIC(order.globi.mod)))
+# order.globi.mod <- glm(globi.data~order, data=leaf.taxa, family="binomial")
+# print(c('BIC=',  BIC(order.globi.mod)))
+# effect("order", order.globi.mod)
 
-
-anova(null.globi.mod, kingdom.globi.mod)
-summary(kingdom.globi.mod)
 # anova(kingdom.globi.mod, phylum.globi.mod, class.globi.mod, order.globi.mod, test="LRT")
-anova(kingdom.globi.mod, phylum.globi.mod, test="LRT")
-effect("kingdom", kingdom.globi.mod)
+anova(kingdom.globi.mod, phylum.globi.mod, class.gloni.mod, test="LRT")
+
 
 print('-------------------kingdom + depth / * depth-----------------------')
 
 kingdomPdepth.globi.mod <- glm(globi.data~kingdom+depth, data=leaf.taxa, family="binomial")
 print(c('BIC=',  BIC(kingdomPdepth.globi.mod)))
[…]

### 2018-03-11 Paper - Latex/Paper - Skizze - v3.tex
Paper - cleanup... add more data.. add effect  section in results...

@@
       \end{itemize}
-      \todo{Interactions nochmal prüfen! Darauf basieren unsere Ergebnisse!} \\
       We build two lists: parasites and free-livings, and add the source or targets of an interaction
         to these. \\
-      \todo{klar? Oder Beispiel bringen? (Katze isst Maus $\rightarrow$ Katze ist Freilebend)} \\
       % For every interaction from these lists, we get one or two species for our parasite or 
       %   free-living lists.
-      \todo{einige spezies nicht mit einbezogen, da sie keine OTT id haben, hier könnte man noch 
-        verbessern (future work)}
+
       \todo{You can find all interaction types here:
-        https://github.com/jhpoelen/eol-globi-data/blob/master/eol-globi-lib/src/main/java/org/eol/globi/domain/InteractType.java .} \\ \\
-
-      With this we got $\sim 51000$ (distinct) freeliving species and $\sim 47000$ (distinct) parasite 
-        species (see section countings) \todo{ref einfügen}. But we found also  $\sim 57000$ (not 
-        distinct) source species and $\sim 810000$ (not distinct) target species without OTT ids. 
-        Since we currently use only OTT ids, we could not use this information. \\
-      \todo{mehr dazu in section: unknown nodes...}
+        https://github.com/jhpoelen/eol-globi-data/blob/master/eol-globi-lib/src/main/java/org/eol/globi/domain/InteractType.java .}
 
@@
 
-        \begin{figure}
-          \centering
-          \includegraphics[trim = 0mm 0mm 0mm 0mm, clip,width=0.95\textwidth]{Figures/Kreuztabelle_Residuals.JPG}
-          \caption{Crosstable of Residual values}
-        \end{figure}
-
         Interpretation: Die Multifurkation ist sehr ungleich verteilt. Daher ist die vorhersage umso 
           genauer umso kleinere Subtrees wir betrachten. ...
-
-        \anmerkung{different parameters for different taxa? (Emanuel)} \\ \\
 
@@
         \end{table}
-
-        \begin{figure}
-          \centering
-          \includegraphics[trim = 0mm 0mm 0mm 0mm, clip,width=0.95\textwidth]{Figures/Kreuztabelle_BIC.JPG}
-          \caption{Crosstable of BIC values}
-        \end{figure}
 
@@
       distinct parasite species $\rightarrow$ unknown nodes 2194794 ($\approx 95.7\%$). \\
-    With this only $\approx 4.3\%$ information in our leaf nodes are
-
-    \todo{einbauen?:} \\
-    unused possible species  57 352 (source), \\
-    809 993 (target) \\
-    \#interactions zu \#Parasiten und \#Freilebend $\rightarrow$ Wieviel gibt GloBI her? (dazu noch 
-      \#unused possible species, wieviele Parasiten ohne ott haben wir gefunden?)
+    We found also $57,352$ (not distinct) source species and $809,993$ (not distinct) target
+      species without OTT ids. Since we currently use only OTT ids, we could not use this information. \\
+    \todo{With this only $\approx 4.3\%$ information in our leaf nodes are ...} \\
+    We also compared different models in terms of their BICs (Table: \ref{table:BIC unknown information}). 
+      The Residuals are not very meaningful here, since all models have different dimensions.
+
+      % Model 1: globi.data ~ kingdom + depth
+      % Model 2: globi.data ~ kingdom * depth
+      %   Resid. Df Resid. Dev Df Deviance  Pr(>Chi)
+      % 1   2297502     544789
+      % 2   2297499     544062  3   727.05 < 2.2e-16 ***
+
+      % Model 1: globi.data ~ phylum + depth
+      % Model 2: globi.data ~ phylum * depth
+      % Resid. Df Resid. Dev Df Deviance  Pr(>Chi)
+      % 1   2297453     493017
+      % 2   2297406     488366 47   4650.8 < 2.2e-16 ***
+
+      \begin{table}[h!]
+        \begin{center}
+          \begin{tabular}{ |l|r|r|r|r| }
+            \hline
+            Model / Taxa & Kingdom & Phylum & Class & Order \\
+            \hline \hline
+            multifurc $\sim$ taxa & 545799 & 500004 & 485121 & XXXXX\\
+            \hline
+            multifurc $\sim$ taxa + depth & 544862 & 493808 & XXXXX & XXXXX \\
+            \hline
+            multifurc $\sim$ taxa * depth & 544179 & 489845 & XXXXX & \cellcolor{green!60}XXXXX \\
+            \hline
+          \end{tabular} 
+        \end{center}
+        \caption{BIC of unknown information}
+        \label{table:BIC unknown information} 
+      \end{table}
 
@@
         Platyhelminthes and Apicomplexa. \\
-      As we know \todo{ref einfügen} the Chordata are full of free-living species and there are only a 
-        few parasites. The algorithm reflects this. We started with 99.83\% free-living species and 
-        predicted 99.94\% species as parasites \todo{(inklusive all known nodes)}. Only 0.06\% were 
-        predicted as parasites. These few parasites are mostly breeding parasites (brood parasitism) and 
-        some individual errors from the GloBI database. \\
+      Since GloBI is not perfect, all examples contain a few bugs.
+      As known the Chordata are full of free-living species and there are only a few parasites. Among 
+        the birds are some breeding parasites (brood parasitism) like the cuckoo and clepto-parasites as 
+        the skuas \cite{Rothschild1957}. The algorithm reflects this. We started with 99.83\% 
+        free-living species and predicted 99.94\% species as parasites \todo{(inklusive all known nodes)}. 
+        Only 0.06\% were predicted as parasites. \\
+      \todo{We found the cuckoo and some skuas...?} \\
       Same observation but with less free-livings is the Apicomplexa Phylum. Here we have only a few 
@@
 
-      With the Nematoda it looks very different. In the Nematoda its much worse. Here speaks the 
-        literature of \todo{x percent} free-living, but we found only 2.63\% of them. The problem at 
-        this point, however, is obvious: The parasites have been much more studied and thus we start 
-        with only 0.63\% free-living species. Against such a shifted data situation, the algorithm is 
-        powerless. And yet the percentage has increased.
+      With the Nematoda it looks very different. In the Nematoda its much worse. Most Nematoda are 
+        free-living, but we found only 2.63\% of them. Blaxter et al. speaks of at least seven 
+        independently arosed parasitism \cite{Blaxter1998}. \\
+        The problem at this point, however, is obvious: The parasites have been much more studied and 
+        thus we start with only 0.63\% free-living species. Against such a shifted data situation, the 
+        algorithm is almost powerless. And yet the percentage has increased.
 
@@
         is parasitic \\
+        As we have already mentioned Blaxter et al. found at least seven origins of parasitism 
+          \cite{Blaxter1998}. If we assume that the root node of Nematoda is free-living, then some 
+          losses would have to turn around and become Origins. So it could be that we end up in a similar 
+          size as Blaxter.
 
@@
     \subsection{Cross evaluation - leave 100 out}
-      We ran the castor algorithm (\todo{10000}) 70 times with leaving 100 randomized free-living or 
-        parasitic species out of the input data to see how stable our result is. \\
+      We ran the castor algorithm 100 times with leaving 100 randomized free-living or parasitic species 
+        out of the input data to see how stable our result is. Of these 10,000 nodes, 9,238 were unique. 
+        Of that, we predicted 9060 ($\approx 98.17\%$) correctly and 169 ($\approx 1.82\%$) wrongly, with 
+        duplicate draws always having the same prediction. \\
+      What is the best way to model this data? We again tested the influence of the taxa and the depth of 
+        leaf nodes and calculated the BICs (Table: \ref{table:BIC cross validation}).
+
+      \begin{table}[h]
+        \begin{center}
+          \begin{tabular}{ |l|r|r|r|r| }
+            \hline
+            Model / Taxa & Kingdom & Phylum & Class & Order \\
+            \hline \hline
+            correct predicted $\sim$ taxa & 117936 & 112242 & XXXXX & XXXXX \\
+            \hline
+            correct predicted $\sim$ taxa + depth & 117776 & XXXXX & XXXXX & XXXXX \\
+            \hline
+            correct predicted $\sim$ taxa * depth & XXXXX & XXXXX & XXXXX & \cellcolor{green!60}XXXXX \\
+            \hline
+          \end{tabular} 
+        \end{center}
+        \caption{BICs of cross validation prediction}
+        \label{table:BIC cross validation} 
+      \end{table}
+
+      Resiudals:
+      \begin{itemize}
+        \item correct predicted $\sim$ 1: 120325
+        \item correct predicted $\sim$ kingdom: 117877
+        \item correct predicted $\sim$ phylum: 111466
+      \end{itemize}
+
       What could happen by removing a parasite or free-living of the list?
@@
 
+      Influence on the rest of the data:
       \begin{table}
         \begin{center}
-          \begin{tabular}{ |cl||r|r|r|r| }
+          \begin{tabular}{ |cl||r|r|r|r|r| }
             \hline
@@
       \end{table}
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Effects of Taxa in the different models}
+
+    \anmerkung{different parameters for different taxa? (Emanuel) -> Effects...} \\ \\
+
+    The comparisons of the effects of the taxa can be found in Table \ref{table:Effects unknown data} 
+    and showed ...
+
+    \begin{table}[h!]
+      \begin{center}
+        \begin{longtable}{ |l|l|r|r|r| }
+          \hline
+          \multicolumn{2}{|c|}{Taxa / Model} & globi $\sim$ taxa & globi $\sim$ taxa + depth & globi $\sim$ taxa * depth\\
+          \hline \hline
+          Kingdom & no kingdom  & 0.007608091 & 0.009900630 & 0.0004645054 \\
+          & Fungi               & 0.011317000 & 0.013723310 & 0.0064413062 \\
+          & Chloroplastida      & 0.008634310 & 0.008018847 & 0.0058472786 \\
+          & Metazoa             & 0.035634187 & 0.034139782 & 0.0343237575 \\
+          \hline
+          Phylum & no phylum    & 1.569769e-02 & 3.001749e-02 & 5.757839e-03 \\
+          & Rhombozoa           & 1.538462e-02 & 4.128162e-02 & 1.000000e+00 \\
+          & Hemichordata        & 1.736770e-07 & 3.791496e-07 & 1.736742e-07 \\
+          & Chromerida          & 1.736770e-07 & 4.605436e-07 & 2.220446e-16 \\
+          & Amoebozoa           & 5.343198e-03 & 1.312565e-02 & 2.401619e-03 \\
+          & Onychophora         & 1.736770e-07 & 3.663718e-07 & 1.736753e-07 \\
+          & ... & ... & ... & ... \\
+          % & Priapulida          & 4.347826e-02 & 8.773029e-02 \\
+          % & Tardigrada          & 1.736770e-07 & 3.393298e-07 \\
+          % & Chordata            & 1.140600e-01 & 8.242171e-02 \\
+          % & Xanthophyceae       & 1.736770e-07 & 3.483928e-07 \\
+          % & Haptophyta          & 3.484321e-03 \\
+          % & Microsporidia       & 8.703271e-02 \\
+          % & Chytridiomycota     & 3.062361e-02 \\
+          % & Nematomorpha        & 1.495017e-02 \\
+          % & Loricifera          & 1.736770e-07 \\
+          % & Gnathostomulida     & 1.736770e-07 \\
+          % & Myzostomida         & 4.464286e-03 \\
+          % & Gastrotricha & 1.736770e-07 \\
+          % & Ciliophora & 8.372371e-03 \\
+          % & Entoprocta & 1.736770e-07 \\
+          % & Glomeromycota & 6.609385e-04 \\
+          % & Nematoda & 1.098682e-01 \\
+          % & Cycliophora & 1.736770e-07 \\
+          % & Apicomplexa & 1.374128e-01 \\
+          % & Ascomycota & 1.232671e-02 \\
+          % & Bryozoa & 4.194290e-03 \\
+          % & Nemertea & 9.465855e-03 \\
+          % & Echinodermata & 1.971448e-02 \\
+          % & Rotifera & 8.638563e-03 \\
+          % & Picozoa & 1.736770e-07 \\
+          % & Phaeophyceae & 1.219884e-03 \\
+          % & Acanthocephala & 3.935018e-01 \\
+          % & Bacillariophyta & 4.757374e-05 \\
+          % & Colponemidia & 1.736770e-07 \\
+          % & Platyhelminthes & 3.127011e-01 \\
+          % & Entorrhizomycota & 1.736770e-07 \\
+          % & Chaetognatha & 2.941176e-02 \\
+          % & Placozoa & 1.736770e-07 \\
+          % & Euglenida & 1.729107e-03 \\
+          % & Arthropoda & 2.506545e-02 \\
+          % & Basidiomycota & 6.149777e-03 \\
+          % & Cnidaria & 1.928587e-02 \\
+          % & Ctenophora & 4.205607e-02 \\
+          % & Kinorhyncha & 1.736770e-07 \\
+          % & Porifera & 7.720212e-03 \\
+          % & Orthonectida & 1.153846e-01 \\
+          % & Mollusca & 9.876095e-03 \\
+          % & Brachiopoda & 6.920415e-03 \\
+          % & Haplosporida & 8.108108e-02 \\
+          % & Rhodophyta & 1.971220e-04 \\
+          % & Streptophyta & 8.901842e-03 \\
+          % & Foraminifera & 3.395201e-04 \\
+          % & Chlorophyta & 3.084992e-04 \\
+          \hline \hline
+          \multicolumn{2}{|c|}{Taxa / Model} & correct predicted & correct predicted & correct predicted \\
+          \multicolumn{2}{|c|}{} & $\sim$ taxa & $\sim$ taxa + depth & $\sim$ taxa * depth\\
+          \hline \hline
+          Kingdom & no kingdom  & 0.001139888 & ... & ... \\
+          & Fungi               & 0.001789739 & ... & ... \\
+          & Chloroplastida      & 0.001251109 & ... & ... \\
+          & Metazoa             & 0.005414443 & ... & ... \\
+          % \hline
+          % Phylum & no phylum    & XXXXX & 3.001749e-02 & 5.757839e-03 \\
+          % & Rhombozoa           & XXXXX & 4.128162e-02 & 1.000000e+00 \\
+          % & Hemichordata        & XXXXX & 3.791496e-07 & 1.736742e-07 \\
+          % & Chromerida          & XXXXX & 4.605436e-07 & 2.220446e-16 \\
+          % & Amoebozoa           & XXXXX & 1.312565e-02 & 2.401619e-03 \\
+          % & Onychophora         & XXXXX & 3.663718e-07 & 1.736753e-07 \\
+          % & ... & ... & ... & ... \\
+          \hline
+        \end{longtable} 
+      \end{center}
+      \caption{Effects of Taxa in models for unknown data}
+      \label{table:Effects unknown data} 
+    \end{table}
+
+    globi $\sim$ taxa * depth: NOTE: kingdom is not a high-order term in the model
+
+%        ['ott151014', 'Haptophyta']      ['ott16113', 'Microsporidia']
+%                       1.023682e-02                       2.297956e-01
+%   ['ott177160', 'Chytridiomycota']      ['ott189836', 'Nematomorpha']
+%                       8.586035e-02                       3.000311e-02
+%        ['ott199402', 'Loricifera']   ['ott242963', 'Gnathostomulida']
+%                       3.538708e-07                       3.160858e-07
+%       ['ott260040', 'Myzostomida']       ['ott29723', 'Gastrotricha']
+%                       9.396517e-03                       3.335103e-07
+%        ['ott302424', 'Ciliophora']        ['ott362916', 'Entoprocta']
+%                       2.114329e-02                       3.281554e-07
+%     ['ott385878', 'Glomeromycota']          ['ott395057', 'Nematoda']
+%                       1.687966e-03                       1.582959e-01
+%        ['ott41147', 'Cycliophora']       ['ott422673', 'Apicomplexa']
+%                       3.160858e-07                       2.849943e-01
+%        ['ott439373', 'Ascomycota']           ['ott442934', 'Bryozoa']
+%                       2.217673e-02                       7.020371e-03
+%          ['ott445195', 'Nemertea']     ['ott451020', 'Echinodermata']
+%                       1.640797e-02                       3.399753e-02
+%          ['ott471706', 'Rotifera']          ['ott4738955', 'Picozoa']
+%                       1.516272e-02                       6.032169e-07
+%       ['ott48614', 'Phaeophyceae']     ['ott49622', 'Acanthocephala']
+%                       2.014280e-03                       5.672835e-01
+%  ['ott5342311', 'Bacillariophyta']     ['ott5355158', 'Colponemidia']
+%                       1.048765e-04                       5.155971e-07
+%   ['ott555379', 'Platyhelminthes'] ['ott5653719', 'Entorrhizomycota']
+%                       4.271198e-01                       4.449469e-07
+%      ['ott570366', 'Chaetognatha']          ['ott570376', 'Placozoa']
+%                       5.936368e-02                       4.965510e-07
+%        ['ott6137051', 'Euglenida']        ['ott632179', 'Arthropoda']
+%                       4.727403e-03                       1.935197e-02
+%     ['ott634628', 'Basidiomycota']          ['ott641033', 'Cnidaria']
+%                       1.149917e-02                       3.192464e-02
+%        ['ott641212', 'Ctenophora']       ['ott677389', 'Kinorhyncha']
+%                       1.077673e-01                       3.540771e-07
+%           ['ott67819', 'Porifera']      ['ott691845', 'Orthonectida']
+%                       1.613863e-02                       2.716252e-01
+%          ['ott802117', 'Mollusca']       ['ott826261', 'Brachiopoda']
+%                       1.372700e-02                       1.079344e-02
+%      ['ott858063', 'Haplosporida']        ['ott878953', 'Rhodophyta']
+%                       1.925711e-01                       5.358571e-04
+%      ['ott916750', 'Streptophyta']      ['ott936399', 'Foraminifera']
+%                       6.529378e-03                       7.447417e-04
+%       ['ott979501', 'Chlorophyta']
+%                       7.296356e-04
+
+% ['ott1085175', 'Priapulida']        ['ott111438', 'Tardigrada']
+%                       1.000000e+00                       1.736778e-07
+%          ['ott125642', 'Chordata']     ['ott151001', 'Xanthophyceae']
+%                       1.138205e-01                       1.736786e-07
+%        ['ott151014', 'Haptophyta']      ['ott16113', 'Microsporidia']
+%                       1.000000e+00                       9.998257e-01
+%   ['ott177160', 'Chytridiomycota']      ['ott189836', 'Nematomorpha']
+%                       1.000000e+00                       2.220446e-16
+%        ['ott199402', 'Loricifera']   ['ott242963', 'Gnathostomulida']
+%                       2.220446e-16                       2.220446e-16
+%       ['ott260040', 'Myzostomida']       ['ott29723', 'Gastrotricha']
+%                       4.381889e-06                       1.736782e-07
+%        ['ott302424', 'Ciliophora']        ['ott362916', 'Entoprocta']
+%                       5.518629e-05                       1.736802e-07
+%     ['ott385878', 'Glomeromycota']          ['ott395057', 'Nematoda']
+%                       9.966669e-01                       4.725574e-01
+%        ['ott41147', 'Cycliophora']       ['ott422673', 'Apicomplexa']
+%                       2.220446e-16                       8.049756e-01
+%        ['ott439373', 'Ascomycota']           ['ott442934', 'Bryozoa']
+%                       1.541511e-02                       1.230174e-03
+%          ['ott445195', 'Nemertea']     ['ott451020', 'Echinodermata']
+%                       1.777755e-01                       2.505179e-03
+%          ['ott471706', 'Rotifera']          ['ott4738955', 'Picozoa']
+%                       3.125183e-01                       1.736782e-07
+%       ['ott48614', 'Phaeophyceae']     ['ott49622', 'Acanthocephala']
+%                       9.252076e-04                       3.992551e-04
+%  ['ott5342311', 'Bacillariophyta']     ['ott5355158', 'Colponemidia']
+%                       1.114784e-10                       2.220446e-16
+%   ['ott555379', 'Platyhelminthes'] ['ott5653719', 'Entorrhizomycota']
+%                       2.478056e-02                       1.736781e-07
+%      ['ott570366', 'Chaetognatha']          ['ott570376', 'Placozoa']
+%                       1.000000e+00                       4.021433e-08
+%        ['ott6137051', 'Euglenida']        ['ott632179', 'Arthropoda']
+%                       9.257999e-01                       1.658528e-02
+%     ['ott634628', 'Basidiomycota']          ['ott641033', 'Cnidaria']
+%                       1.473459e-03                       1.218008e-02
+%        ['ott641212', 'Ctenophora']       ['ott677389', 'Kinorhyncha']
+%                       2.878555e-03                       1.736844e-07
+%           ['ott67819', 'Porifera']      ['ott691845', 'Orthonectida']
+%                       1.329787e-02                       2.931611e-02
+%          ['ott802117', 'Mollusca']       ['ott826261', 'Brachiopoda']
+%                       5.167513e-03                       9.974617e-01
+%      ['ott858063', 'Haplosporida']        ['ott878953', 'Rhodophyta']
+%                       9.999999e-01                       9.658119e-11
+%      ['ott916750', 'Streptophyta']      ['ott936399', 'Foraminifera']
+%                       6.037565e-03                       6.367782e-03
+%       ['ott979501', 'Chlorophyta']
+%                       2.027010e-05
 
@@
 
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+\chapter{Komplett aussortierte Tabellen etc}
+
+  \begin{figure}
+    \centering
+    \includegraphics[trim = 0mm 0mm 0mm 0mm, clip,width=0.95\textwidth]{Figures/Kreuztabelle_Residuals.JPG}
+    \caption{Crosstable of Residual values}
+  \end{figure}
+
+  \begin{figure}
+    \centering
+    \includegraphics[trim = 0mm 0mm 0mm 0mm, clip,width=0.95\textwidth]{Figures/Kreuztabelle_BIC.JPG}
+    \caption{Crosstable of BIC values}
+  \end{figure}
+
 \end{document}

### 2018-03-11 Paper - Latex/Paper - Skizze - v3.tex
Paper - Methods - Metadata analysis, Transition probabilities, Multifurcation, Simulation,...

@@
       This database consists of entries of the form: species A (source) interacts with B (target). \\
-      We appointed some interactions, where we know from the biological perspective that the species 
-      source or target has to be a parasite or a free-living species. These are the following:
+      We appointed some interactions\footnote{\hyperlink{
+        https://github.com/jhpoelen/eol-globi-data/blob/master/eol-globi-lib/src/main/java/org/eol/globi/domain/InteractType.java
+        }{https://github.com/jhpoelen/eol-globi-data/.../InteractType.java}}
+        , where we know from the biological perspective that the species source or target has to be a 
+        parasite or a free-living species. These are the following:
       \begin{itemize}
@@
       We build two lists: parasites and free-livings, and add the source or targets of an interaction
-        to these. \\
-      % For every interaction from these lists, we get one or two species for our parasite or 
-      %   free-living lists.
-
-      \todo{You can find all interaction types here:
-        https://github.com/jhpoelen/eol-globi-data/blob/master/eol-globi-lib/src/main/java/org/eol/globi/domain/InteractType.java .}
+        to these.
 
@@
   \section{Metadata analysis}
-    Um eine möglichst realistische Simulation zu erzeugen haben wir auf der einen Seite einige Daten 
-      gesammelt (vorheriges Kaptiel), und außerdem beeinflussende Parameter untersucht. \\
-    Wir haben zwei große Arten von Parametern:
+    In order to generate the most realistic simulation, influencing parameters were investigated. \\
+    There are two major types of parameters:
     \begin{enumerate}
@@
         \begin{itemize}
-          \item Loss of topology ($\rightarrow$ mutlifurcations).
-          \item Unknown information about the states of some leaf nodes.
+          \item Loss of topology ($\rightarrow$ mutlifurcations)
+          \item Unknown information about states of some leaf nodes
         \end{itemize}
@@
     \subsection{Transition probabilities}
-      \anmerkungstext{Wir hätten aber maximal 2 beta-Verteilungen mit jeweils 2 Parametern und je einem 
-      eigenen Schwellenwert bei dem in die andere Verteilung gewechselt wird. Also 6 Parameter. Ich 
-      finde den Parameterraum den du bisher betrachtest zum einen nicht systematisch erfasst, zum 
-      anderen wahrscheinlich auch zu klein. Du kannst -Parameter sparen- indem zu z.B die beiden 
-      Verteilungen und cut-offs symmetrisch (gespiegelt an 0.5) machst. Solltest aber meines Erachtens 
-      die Schwellenwerte freier variieren. Das können wir bis zu unserem nächsten Treffen zurückstellen 
-      und dann gemeinsam diskutieren. (Emanuel)} \\
-      Das mit dem symmetrisch spiegeln geht halt nur bei maximal 40-60 Verteilungen richtig gut, danach 
-      haben brauchen eventuell eine lange Austestphase, bis ein Baum dieser Verteilung entspricht.
-      Wenn wir allerdings dafür zwei verschiedene Schwellenwerte einführen könnte das dieses Problem 
-      eventuell ausgleichen. Das müsste ich austesten.
-
-      \todo{Kapitel tag tree hier einbinden}
+      This subsection deals with the transition probabilities from free-living (hereinafter / as a 
+        formula FL) to parasitic (hereinafter P) and vice versa: $\mathcal{P}(FL \rightarrow P)$, 
+        $\mathcal{P}(P \rightarrow FL)$. \\
+      Different parasite types have different transition probabilities. It is very difficult to make a 
+        statement about these probabilities.
+      In general, we assume that there are 40\% parasites and 60\% free-livings \todo{ref} and 
+        $\mathcal{P}(FL \rightarrow P) > \mathcal{P}(P \rightarrow FL)$, because a reverse mutation is 
+        usually less likely. \todo{This is discussed in section x of the discussion.} \\
+
+      For the maximum parsimony analysis of the real data, all transition probabilities were equated.
+        However, the used castor package \cite{Louca2017} offers the possibility to enter different 
+        transition probabilities. \\
+
+      In the simulation, we chose two beta distributions and a threshold that indicates the change 
+        between states. \\
+      Different thresholds with different beta distributions were simulated, with different distributions 
+        of parasites and free-livings: 50\% P to 50\% FL, 40\% P to 60\% FL, 30\% P to 70\% FL and 
+        20\% P to 80 \% FL (\todo{see results simulation, ref...}).
 
@@
     \subsection{Multifurcation}
-      We have a very high multifurcation rate \pageref{sec:ResultsMultifurcation}.
-
-      Therefore, the impact of multifurcations on our research question has been investigated:
-      \begin{itemize}
-        \item stärke der Multifurcation in verschiedenen Subbäumen
-        \item zusammenhang zur tiefe im Baum
-        \item zusammenhang zu höhe im baum (max, min, mean)
-        \item einfluss auf die vorhersage des Castor und Fitch Algorithmus (Simulation) \todo{...}
-      \end{itemize}
-
-      "Nested models were compared using likelihood ratio tests, models using different predictors were 
-      compared according to their deviance and AIC."
-      \begin{lstlisting}[gobble=8]
-        glm(formula = multifurc ~ 1, family = "poisson", data = inner.taxa)
-      \end{lstlisting}
-
-        % \todo{old Stuff:} \\
-        %   Then we tried to find a function which best discribes this behavior. In figure 
-        %   \ref{fig:HistogramsOfMultifurcations} is this plot shown with three functions, which came 
-        %   closest to this goal: $\frac{1000000000000000}{x^4}$ (magenta), 
-        %   $\frac{300000000000}{x^3}$ (red) and $\frac{80000000}{x^2}$ (black). \\
-        % \begin{figure}[h]
-        %   \caption{Histogram of multifurcations and fitting functions}
-        %   \centering
-        %   \label{fig:HistogramsOfMultifurcations}
-        %   \includegraphics[width=0.7\textwidth]{Figures/HistogramsOfMultifurcations.png}
-        % \end{figure}
-        % From the biology we know, that this multifurcation is very clouded. Some parts of the tree are 
-        %   well known and others have not been very interesting for the research so far. So we also wanted 
-        %   to know how the multifurcations behave in some interesting subtrees. \\
-        % \anmerkung{do we? Is that really universal knowledge or could it be supported by data or a citation? (Bernhard)} \\
+      We have a very high multifurcation rate (see results section \pageref{sec:ResultsMultifurcation}).
+      Therefore, the impact of multifurcations on our research question has been investigated. \\
+      Generalized Linear Models with poisson regression were compared according to their residuals and 
+      BIC. \\
+      \anmerkungstext{Nested models were compared using likelihood ratio tests, models using different 
+        predictors were compared according to their deviance and AIC. (Emanuel)} \\
+      \todo{Einfluss auf die Vorhersage des Castor und Fitch Algorithmus (Simulation)}
 
@@
   \section{Simulation}\label{sec:simulation}
-    \anmerkung{Motivate the goal of the simulation (Bernhard)}
-    \begin{itemize}
-      \item build random binary trees, tag these (parameters: parasites vs free-living, 
-        beta-distribution)
-      \item run fitch-parsimony, wagner-parsimony, our parsimony like algorithm
-      \item build not binary tree (poisson distribution?)
-      \item run new algorithms
-      \item compare trees (distances)
-    \end{itemize}
-
-    \begin{enumerate}
-      \item build random binary trees
-      \item tag tree
-      \item multifurcate tree
-      \item run maximum parsimony algorithms
-      \begin{itemize}
-        \item Fitch
-        \item Sankoff (Castor package \cite{Louca2017}) 
-        \item my algorithm
-      \end{itemize}
-      \item Evaluation
-    \end{enumerate}
+    There are various possibilities of ancestral state reconstruction. The simulation compared 
+      different algorithms. \\
+    On the one hand different implementations of the Fitch maximum parsimony were compared and on the 
+      other hand the best of them with the implementation of the sankoff algorithm of the castor 
+      package \cite{Louca2017}. \\
+
+    \begin{figure}[h!]
+      \centering
+      \includegraphics[width=1\textwidth]{Figures/Workflow-Simulation.png}
+      \caption{Course of the simulation with influence of the metadata analysis from the real data.}
+      \label{fig:Simulation Workflow}
+    \end{figure}
+
+    % \begin{wrapfigure}{r}{0.6\textwidth}
+    %   \begin{center}
+    %     \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.58\textwidth]{Figures/Workflow-Simulation.png}
+    %   \end{center}
+    %   \caption{Overview of the Simulation}
+    %   \label{fig:Simulation Workflow}
+    % \end{wrapfigure}
+
+    Figure \ref{fig:Simulation Workflow} shows the course of the simulation. The individual steps are 
+      explained in the following subsections.
+
+    \todo{Evaluation - compare trees (distances)}
 
@@
     \subsection{random binary tree}
-      \anmerkung{Again, motivate first, why this is required and why you choose this solution (Bernhard)} \\
-      To get a random binary tree, I used the Phylo package from biopython. They offer a randomized
-        function which returns a BaseTree \footnote{
-          https://github.com/biopython/biopython/blob/master/Bio/Phylo/BaseTree.py
-        }:
-      \begin{lstlisting}[gobble=6]
-        from Bio import Phylo
-        Phylo.BaseTree.Tree.randomized(number_leaf nodes)
-      \end{lstlisting}
-      From the BaseTree class:
-      \anmerkung{trivial, does not give real info (Emanuel)}
-      \begin{lstlisting}[gobble=6]
-        def randomized(cls, taxa, branch_length=1.0, 
-              branch_stdev=None):
-        """Create a randomized bifurcating tree given a list
-              of taxa.
-          :param taxa: Either an integer specifying the number
-              of taxa to create (automatically named taxon#), 
-              or an iterable of taxon names, as strings.
-          :returns: a tree of the same type as this class.
-        """
-      \end{lstlisting}
-      \todo{Zitat von BaseTree und buildTree.py}
+      You need a tree to do a simulation of ancestral state reconstruction. It had to be decided whether 
+        to take the real tree or simulate a tree. In this simulation, trees were created randomly, as 
+        one can replicate a complete binary phylogentic tree. Thus, there is also the possibility to 
+        simulate the multifurcation. \\
+
+      To get a random binary tree, the Phylo package from biopython were used \cite{Cock2009}. They offer 
+        a randomized function which returns a BaseTree\footnote{
+          \hyperlink{https://github.com/biopython/biopython/blob/master/Bio/Phylo/BaseTree.py}
+          {https://github.com/biopython/biopython/blob/master/Bio/Phylo/BaseTree.py}
+        }. \\
+      \todo{ref in die discussion über die randomized function? Diskutieren wir das?}
 
@@
   %---------------------------------------------------------------------------------------------------
-      \subsubsection{my Algorithm}
-
-  %---------------------------------------------------------------------------------------------------
   %---------------------------------------------------------------------------------------------------
@@
       \item run castor algorithm / and others?
-      \item interprete results (leave one out)
+      \item interprete results (cross validation - leave 100 out)
     \end{itemize}
@@
   \section{Implementation}
+    You can find the full code on GitHub: 
+      \hyperlink{github.com/Irallia/IZW-HU-Parasites}{github.com/Irallia/IZW-HU-Parasites}. \\
+    Most of the code was written in Python. The analyzes and the use of the Castor package in R. There 
+      are some shell scripts to execute whole workflows.
 
@@
           \multicolumn{2}{|c|}{Taxa / Model} & correct predicted & correct predicted & correct predicted \\
-          \multicolumn{2}{|c|}{} & $\sim$ taxa & $\sim$ taxa + depth & $\sim$ taxa * depth\\
+          \multicolumn{2}{|c|}{} & $\sim$ taxa & $\sim$ taxa + depth & $\sim$ taxa * depth \\
           \hline \hline

### 2018-03-11 Paper - Latex/Paper - Skizze - v3.tex
Paper - Methods - simulate loss of information

@@
         However, the used castor package \cite{Louca2017} offers the possibility to enter different 
-        transition probabilities. \\
+        transition probabilities.
+      \begin{wrapfigure}{r}{0.5\textwidth}
+        \begin{center}
+          \includegraphics[trim = 0mm 0mm 0mm 15mm, clip, width=0.48\textwidth]{Figures/40-60.png}
+        \end{center}
+        \caption{60\% Free-living - 40\% Parasites \\ red: parasites, blue: free-living, \\ the threshold is at 0.4}
+        \label{fig:Beta distribution}
+      \end{wrapfigure}
 
@@
         of parasites and free-livings: 50\% P to 50\% FL, 40\% P to 60\% FL, 30\% P to 70\% FL and 
-        20\% P to 80 \% FL (\todo{see results simulation, ref...}).
+        20\% P to 80 \% FL (\todo{see results simulation, ref...}). Figure \ref{fig:Beta distribution} 
+        shows one example of these. \\
+      \todo{Plot neu erstellen: Achsenbeschriftung, threshold}
 
@@
 
-    % \begin{wrapfigure}{r}{0.6\textwidth}
-    %   \begin{center}
-    %     \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.58\textwidth]{Figures/Workflow-Simulation.png}
-    %   \end{center}
-    %   \caption{Overview of the Simulation}
-    %   \label{fig:Simulation Workflow}
-    % \end{wrapfigure}
-
     Figure \ref{fig:Simulation Workflow} shows the course of the simulation. The individual steps are 
@@
     %---------------------------------------------------------------------------------------------------
-    \subsection{tag tree}
-      \anmerkung{instead of 'tag tee' simulating states and transitions between them (Emanuel)} \\
-      At this point we want one fully tagged tree, and one less tagged tree which looks like our real 
-        data.\\
-      Let's say the first specie (the root node) was free-living (start with a parasite without a host 
-        makes no sence). For every transition from a node to his child, we take a random number from
-        the father distribution. We decided that from the biological perspective a beta distribution
-        reflects our transition probabilities best (see Figure 2.1 \todo{ref einfügen}). \\
-      \anmerkung{why is that the case and why is that from a biological perspective? (Bernhard)} \\
-      \anmerkungstext{I'd rather say that to ensure that the parameter of the binomial distribution is 
-        restricted to the [0,1] interval, we model it... (Bernhard)} \\
-      For example when our father node was free-living, then we take from the free-living beta
-        distribution. Is the number under the threshold for beeing parasite, we get a change and tag
-        the current node as parasite. Otherwise we tag it as free-living. \\
-      With this procedure we traverse through the tree from the root to every leaf node. A part of
-        this code you see here:
-      \begin{lstlisting}[gobble=6]
-        from numpy import random
-        if father_tag == 0:
-          # freeliving_distribution:
-          new_random = random.beta(a=A_FL, b=B_FL)
-        else:
-          # parasite_distribution:
-          new_random = random.beta(a=A_P, b=B_P)
-        tag = 0         # $\rightarrow$ FL
-        if new_random < percentage_parasites:
-          tag = 1       # $\rightarrow$ P
-      \end{lstlisting}
-      \begin{figure}
-        \caption{60\% Free-living - 40\% Parasites}
-        \centering
-          \includegraphics[width=0.5\textwidth]{Figures/40-60.png}
-      \end{figure}
-      \todo{Bessere Beschriftung, Plot neu erstellen! U.a. mit threshold} \\
-      We save each tag with the associated node ID in a nodelist. \\
-      \anmerkung{simulationg loss of information (1) states (2) topology/multifurcation (Emanuel)} \\
-      The real tree has much less information, we have only information from some current species 
-        (leaf nodes) and \todo{and probably negligible internal nodes}. \\
-      To simulate our real tree we save for every node an empty placeholde except for some leaf nodes.
-      There we save the states again. The amount of these unknown information is one parameter, which we
-      got from our real tree. Or which we can change to \todo{...}
-      \todo{Was hiervon gehört ind Methoden, was schon in Implementierung oder ganz woanders hin?}
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{multifurcate tree}
-      \anmerkung{simulating loss of information (Emanuel)} \\
-      Another parameter is the nature and strength of the multifunction of the tree, since we do not 
-        have a binary tree in the real case. After several measurements and analyzes, which we explain 
-        in \todo{section/chapter x}, \anmerkung{fit, justification (Emanuel)} we decided to use a $\frac{1}{x}$ distribution, where x is the depth 
-        of a node. This means, how deaper we are, how less information we have. \\
+    \subsection{simulating states and transitions between them}
+      The next step is to simulate the states of the nodes using the transitions. Again, we simulate 
+        fully known states and then 'forget' everything but a few in the leaf nodes so that you can 
+        later compare the reconstruction with the origin. \\
+      The root node (ancestor of all subsequent species) is (of course) free-living. That means it will 
+        start in the free-living beta distribution. Now traverse from the root to the leaf nodes, always 
+        pulling out of the current distribution until you get above the threshold and the new node 
+        changes state. \\
+      To ensure that the parameter of the binomial distribution is restricted to the [0,1] interval, we 
+        model it with a beta distribution as in Figure \ref{fig:Beta distribution}. \\
+
+      After traversing through the tree, each state is saved in a nodelist associated with the node ID 
+        which is the OTT from OTL. \\
+
+      Here begins the simulation of the lost information. This is on the one hand the states and on the 
+        other the topology of the tree. Some splits of nodes are unknown with which the tree is 
+        multifurcated (explained in the following section \todo{pageref}). \\
+
+      In the real tree, there is usually only information about species living today $\rightarrow$ leaf 
+        nodes. And beyond only a small percentage of these. All information about the states of the 
+        internal node and one leaf node is 'forgotten' and stored in another column to the node. \\
+      Different percentages of forgetting the information were simulated, as you can read in the 
+      \todo{section ... from the results}.
+
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \subsection{simulating loss of information of the tree topology}
+      As previously explained, some divisions in the tree are not known, so the real tree is not binary.
+        We simulate this multifurcation of the tree by \todo{...}.
+
+      On the one hand, the strength of multifunctionation plays a role, as does the distribution. 
+        Modeling was done as explained in \todo{sec x}.
+
+      \todo{bisher ohne Begründung:!!!}
+      we decided to use a $\frac{1}{x}$ distribution, where x is the depth of a node. This means, how 
+      deaper we are, how less information we have. \\
       We traverse through the tree and pick a random number between 0 and 1. If random number is smaller 
@@
       \begin{lstlisting}[gobble=6]
-        from numpy import random
-        from utilities import Helpers
-
         def get_non_binary_tree(subtree, nodelist):
@@
       \end{lstlisting}
-      % # current clades: clade_1 clade_2 ... clade_i-1 clade_i ... clade:_n
-      % # add children of clade_i, delete clade_i
-      % # new clades:clade_1 clade_2 ... clade_i-1 child_clade_1 ... child_clade_m ... clade:_n
-      % # child_clade_1 is new clade i
-      Wir lassen das Limit nicht beliebig klein werden, sondern beschränken es auf 0.1.
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{maximum parsimony algorithms}
-      \subsubsection{Fitch maximum parsimony}
+      Wir lassen das Limit nicht beliebig klein werden, sondern beschränken es auf 0.1. \\
+
+      With this loss of information the reconstruction can start.
+
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \section{maximum parsimony algorithms}
+
+      %---------------------------------------------------------------------------------------------------
+      %---------------------------------------------------------------------------------------------------
+      \subsection{Fitch maximum parsimony}
         Described from [COO98] + others ... - implemented for multifurcating trees

### 2018-03-12 Paper - Latex/Paper - Skizze - v3.tex
Paper - Introduction - Definition of parasite; - Methods - ancestral state reconstruction methods

@@
 \chapter{Introduction}
-  This paper is about the further development of parsimony algorithms for non-binary trees, applied 
-  to the currently largest phylogeny synthesis tree of Open Tree Of Life, with the application to 
-  the ancestral state reconstruction of parasitism. \\
-  \anmerkungstext{Der erste Satz muss nochmal überarbeitet werden. Das Ziel / Ergebnis der Arbeit 
-    hat sich inzwischen geändert} \\
-  \anmerkungstext{Wir haben mehr einen Algorithmus getestet und an unserem spezifischen Problem angewendet, 
-    als viel selbst zu entwickeln. Allerdings haben wir den Fitch Algorithmus von binär auf multinär 
-    umgeschrieben.} \\
+  This paper is about the analysis of ancestral state reconstruction algorithms for non-binary trees, 
+    applied to the currently largest phylogeny synthesis tree of Open Tree Of Life, with the 
+    application of prediciton of parasitism. \\
 
@@
 
+    Parasite \\
+    Since we use Globi to classify species as parasitic or free-living, we use their definition of 
+      parasitism. In GloBi, ontobee definitions are used.
+    The interaction has parasite is defined as: "An interaction relationship between two organisms 
+      living together in more or less intimate association in a relationship in which association is 
+      disadvantageous or destructive to one of the organisms." \cite{...}. This definition includes: ecto,-
+    and endoparasites, parasitoids, kleptoparasites and pathogenes.
+
+    \todotext{Mungall, C., (2017). Definition for the interaction-term: "parasitised by; has parasite" ob
+    ontobee.org. Last checked: 24.07.2017 at 
+    \hyperlink{ontobee.org/ontology/RO?iri=http://purl.obolibrary.org/obo/RO_0002445}
+    {ontobee.org/ontology/...}}
+
 %---------------------------------------------------------------------------------------------------
@@
         statement about these probabilities.
-      In general, we assume that there are 40\% parasites and 60\% free-livings \todo{ref} and 
+      In general, we assume that there are 40\% parasites and 60\% free-livings which is based on the 
+        estimates by Windsor \cite{Windsor1998} and 
         $\mathcal{P}(FL \rightarrow P) > \mathcal{P}(P \rightarrow FL)$, because a reverse mutation is 
@@
 
+% simulate loss of information
       Here begins the simulation of the lost information. This is on the one hand the states and on the 
@@
     %---------------------------------------------------------------------------------------------------
-    \section{maximum parsimony algorithms}
+    \section{ancestral state reconstruction methods}
+      Royer-Carenzi et al. distinguishes two major classes of ancestral state reconstruction methods: \\
+      The first is to explain the current state with the least number of state changes between an 
+        ancestor and his child, this is called parsimonious.
+      The other class she presents involves modeling the character evolution as a stochastic process and 
+        using the likelihoods to compute the possible ancestral character states. This is generally done 
+        with a continuous time Markov model \cite{RoyerCarenzi2013}. \\
+
+      \todo{Pasqualin et al. unterscheiden noch eine weitere Methode: stochastic mapping...} \\
+
+      One of the major disadvantages of parsimony methods is that, unlike likelihood approaches, they 
+        can not take divergece times (branch length) into account. Since we have no development times in 
+        our case, you can ignore this. \\
+      Another problem pointed out by Royer-Carenzi is that parsimony approaches are either based on 
+        predefined parameters (generalized parsimony) or on strong and often controversial assumptions, 
+        like irreversibility for dollo parsimony. Again, this problem is irrelevant for us, because you 
+        can only work with generalized models in the analysis of the entire Eukaryota tree. \\
+
+      Since the simpler parsimony methods are sufficient for our case, we have decided for them. \\
+      \todotext{In the following we introduce ... there are these methods .. which are important for us ...}
 
@@
 
-      % Model 1: globi.data ~ kingdom + depth
-      % Model 2: globi.data ~ kingdom * depth
-      %   Resid. Df Resid. Dev Df Deviance  Pr(>Chi)
-      % 1   2297502     544789
-      % 2   2297499     544062  3   727.05 < 2.2e-16 ***
-
-      % Model 1: globi.data ~ phylum + depth
-      % Model 2: globi.data ~ phylum * depth
-      % Resid. Df Resid. Dev Df Deviance  Pr(>Chi)
-      % 1   2297453     493017
-      % 2   2297406     488366 47   4650.8 < 2.2e-16 ***
+      \begin{table}[h!]
+        \begin{center}
+          \begin{tabular}{ |l|r|r|r|r| }
+            \hline
+            Model / Taxa & Kingdom & Phylum & Class & Order \\
+            \hline \hline
+            multifurc $\sim$ taxa & 545740 & 499227 & 482265 & XXXXX\\
+            \hline
+            multifurc $\sim$ taxa + depth & 544789 & 493017 & XXXXX & XXXXX \\
+            \hline
+            multifurc $\sim$ taxa * depth & 544062 & 488366 & XXXXX & \cellcolor{green!60}XXXXX \\
+            \hline
+          \end{tabular} 
+        \end{center}
+        \caption{Residuals of unknown information}
+        \label{table:...} 
+      \end{table}
 
@@
 
-\newpage
     %---------------------------------------------------------------------------------------------------
@@
 
-      Sara B. Weinstein and Armand M. Kuris have been searching for origins of parasitism in Animalia 
-        \cite{Weinstein2016}. They identified 223 parasitic origins: 223 in Metazoa $\supset$ 143 in 
-        Arthropoda $\supset$ 87 in Insecta. \\
+      Weinstein and Kuris have been searching for origins of parasitism in Animalia \cite{Weinstein2016}. 
+        They identified 223 parasitic origins: 223 in Metazoa $\supset$ 143 in Arthropoda $\supset$ 87 
+        in Insecta. \\
       This has led us to count the origins and losses of parasitism in our investigation as well. \\

### 2018-03-12 code/metadata/analyse_input.R
analyse family taxa

@@ -11,6 +11,7 @@ all.taxa$kingdom <- as.factor(all.taxa$kingdom)
 all.taxa$phylum <- as.factor(all.taxa$phylum)
 all.taxa$class <- as.factor(all.taxa$class)
 all.taxa$order <- as.factor(all.taxa$order)
+all.taxa$family <- as.factor(all.taxa$family)
 
 
 heights <- do.call("rbind", strsplit(gsub("\\[|\\]", "", all.taxa$heights), ", "))
@@ -71,26 +72,29 @@ print('--------------------------------------------------')
 # null.furc.mod <- glm(multifurc~1, data=inner.taxa,
 #                    family="poisson")
 
-print('------------------------kingdom - phylum - class - order--------------------------')
+print('------------------------kingdom - phylum - class - order - family--------------------------')
 
-# kingdom.furc.mod <- glm(multifurc~kingdom, data=inner.taxa,
-#                         family="poisson")
-# print(c('BIC=',  BIC(kingdom.furc.mod)))
+kingdom.furc.mod <- glm(multifurc~kingdom, data=inner.taxa,
+                        family="poisson")
+print(c('BIC=',  BIC(kingdom.furc.mod)))
 
-# phylum.furc.mod <- glm(multifurc~phylum, data=inner.taxa,
-#                         family="poisson")
-# print(c('BIC=',  BIC(phylum.furc.mod)))
+phylum.furc.mod <- glm(multifurc~phylum, data=inner.taxa,
+                        family="poisson")
+print(c('BIC=',  BIC(phylum.furc.mod)))
 
-# class.furc.mod <- glm(multifurc~class, data=inner.taxa,
-#                         family="poisson")
-# print(c('BIC=',  BIC(class.furc.mod)))
+class.furc.mod <- glm(multifurc~class, data=inner.taxa,
+                        family="poisson")
+print(c('BIC=',  BIC(class.furc.mod)))
 
-# order.furc.mod <- glm(multifurc~order, data=inner.taxa,
-#                         family="poisson")
-# print(c('BIC=',  BIC(order.furc.mod)))
+order.furc.mod <- glm(multifurc~order, data=inner.taxa,
+                        family="poisson")
+print(c('BIC=',  BIC(order.furc.mod)))
 
[…]

### 2018-03-12 code/metadata/extend_nodelist.py

@@ -3,8 +3,8 @@ import pandas as pd
 # We do an SQL LEFT OUTER JOIN.
 
 ott_taxa = pd.read_csv('./data/interaction_data/ott_taxa.csv', encoding='utf-8')
-# nodelist = pd.read_csv('./data/nodelist/Eukaryota-castor.csv', encoding='utf-8')
-nodelist = pd.read_csv('./data/evaluation/Eukaryota-cross_evaluation.csv', encoding='utf-8')
+nodelist = pd.read_csv('./data/nodelist/Eukaryota-castor.csv', encoding='utf-8')
+# nodelist = pd.read_csv('./data/evaluation/Eukaryota-cross_evaluation.csv', encoding='utf-8')
 merged = pd.merge(nodelist, ott_taxa, how='left', on='ott_id')
 
 print(len(nodelist),'merge', len(ott_taxa), '->', len(merged))
@@ -30,8 +30,14 @@ print('class taxa added')
 
 order_mapping = pd.read_csv('./data/nodelist/Eukaryota-order_mapping.csv', encoding='utf-8')
 merged = pd.merge(merged, order_mapping, how='left', on='ott_id')
-# merged.to_csv('./results/Eukaryota-taxa.csv', index=False, encoding='utf-8')
-merged.to_csv('./results/Eukaryota-cross_evaluation-taxa.csv', index=False, encoding='utf-8')
 
 print('merge', len(order_mapping))
+print('order taxa added')
+
+family_mapping = pd.read_csv('./data/nodelist/Eukaryota-family_mapping.csv', encoding='utf-8')
+merged = pd.merge(merged, family_mapping, how='left', on='ott_id')
+merged.to_csv('./results/Eukaryota-taxa.csv', index=False, encoding='utf-8')
+# merged.to_csv('./results/Eukaryota-cross_evaluation-taxa.csv', index=False, encoding='utf-8')
+
+print('merge', len(family_mapping))
 print('order taxa added')

### 2018-03-12 Paper - Latex/Paper - Skizze - v3.tex
analyse Effects of unknown data models

@@
 
+  In den Bacteria und Archaea wurde das mal allgemein für binary traits gemacht:
+  "A total 90\% of all binary traits described molecular functions, specifically the presence or absence of a gene or a set of gene involved in biochemical pathways."
+  \cite{Goberna2015} \\
+  Unterschied bei uns ist parasitismus komplexer.. da sind meist nicht einzelne Gene zuständig..
+
   %---------------------------------------------------------------------------------------------------
@@
         nodes and 2 293 463 leaf nodes. \\
+      \begin{figure}[h]
+        \centering
+        \begin{subfigure}[b]{0.5\textwidth}
+          \includegraphics[width=\textwidth]{Figures/multifurc.pdf}
+          \caption{Histogram with automatic binwidth. \\ ~ \\ ~}
+        \end{subfigure}
+        ~~~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[b]{0.42\textwidth}
+          \includegraphics[trim = 0mm 0mm 30mm 0mm, clip, width=\textwidth]{Figures/multifurc_small.pdf}
+          \caption{Histogram with $binwidth = 1$. \\ light blue: binary; dark blue: multifunction}
+        \end{subfigure}
+        \caption{Histograms about the multifurcation of the internal nodes of the synthesis tree.}
+        \label{fig:childrenOfNodes}
+      \end{figure}
+
       For a first overview we collected for every node its number of children (degree $-1$), and plotted
-        this in an histogram, see figure \ref{fig:childrenOfNodes}. The multifurcation affects only the
-        internal nodes. We collected the number of children $-2$ of every node (a node with two children 
-        is binary). 
-      \begin{wrapfigure}{r}{0.6\textwidth}
-        \begin{center}
-          \includegraphics[trim = 0mm 0mm 30mm 0mm, clip, width=0.58\textwidth]{Figures/multifurc.pdf}
-        \end{center}
-        \caption{Histogram about the multifurcation of the internal nodes of the synthesis tree. \\ 
-          light blue: binary; dark blue: multifunction}
-        \label{fig:childrenOfNodes}
-      \end{wrapfigure}
-      That means it discribes the number of nodes which we have lost from the real (binary) 
+        this in two histograms, see figure \ref{fig:childrenOfNodes}. \\
+      The multifurcation affects only the internal nodes. We collected the number of children $-2$ of 
+        every node (a node with two children is binary). That means it discribes the number of nodes which we have lost from the real (binary) 
       phylogenetic tree. \\
@@
         \begin{center}
-          \begin{tabular}{ |l|r|r|r|r| }
-            \hline
-            Model / Taxa & Kingdom & Phylum & Class & Order \\
-            \hline \hline
-            multifurc $\sim$ taxa & 545740 & 499227 & 482265 & XXXXX\\
-            \hline
-            multifurc $\sim$ taxa + depth & 544789 & 493017 & XXXXX & XXXXX \\
-            \hline
-            multifurc $\sim$ taxa * depth & 544062 & 488366 & XXXXX & \cellcolor{green!60}XXXXX \\
+          \begin{tabular}{ |l|r|r|r| }
+            \hline
+            Model / Taxa & Kingdom & Phylum & Class \\
+            \hline \hline
+            multifurc $\sim$ taxa & 545740 & 499227 & 482265 \\
+            \hline
+            multifurc $\sim$ taxa + depth & 544789 & 493017 & XXXXX \\
+            \hline
+            multifurc $\sim$ taxa * depth & 544062 & 488366 & \cellcolor{green!60}XXXXX \\
             \hline
@@
         \begin{center}
-          \begin{tabular}{ |l|r|r|r|r| }
-            \hline
-            Model / Taxa & Kingdom & Phylum & Class & Order \\
-            \hline \hline
-            multifurc $\sim$ taxa & 545799 & 500004 & 485121 & XXXXX\\
-            \hline
-            multifurc $\sim$ taxa + depth & 544862 & 493808 & XXXXX & XXXXX \\
-            \hline
-            multifurc $\sim$ taxa * depth & 544179 & 489845 & XXXXX & \cellcolor{green!60}XXXXX \\
+          \begin{tabular}{ |l|r|r|r| }
+            \hline
+            Model / Taxa & Kingdom & Phylum & Class \\
+            \hline \hline
+            multifurc $\sim$ taxa & \cellcolor{green!15}545799 & \cellcolor{green!35}500004 & \cellcolor{green!45}485121 \\
+            \hline
+            multifurc $\sim$ taxa + depth & \cellcolor{green!15}544862 & \cellcolor{green!40}493808 & \cellcolor{green!45}481869 \\
+            \hline
+            multifurc $\sim$ taxa * depth & \cellcolor{green!15}544179 & \cellcolor{green!45}489845 & \cellcolor{green!50}XXXXX \\
             \hline
@@
       \end{table}
+
+      \todo{Taxa like order or family were too expensive to calculate...}
 
@@
         free-living, but we found only 2.63\% of them. Blaxter et al. speaks of at least seven 
-        independently arosed parasitism \cite{Blaxter1998}. \\
+        independently arosed parasitism \cite{Blaxter1998}. In a recent article Blaxter identifies 18 
+        origins \cite{Blaxter2015} in Nematoda. \\
         The problem at this point, however, is obvious: The parasites have been much more studied and 
@@
         algorithm is almost powerless. And yet the percentage has increased.
+
+        The evolution of parasitism in Nematoda: \\
+        "while only approximately 23 000 species have been described (J.
+Hallan, unpublished; https://insects.tamu.edu/research/collection/hallan/), the true species-level diversity may be 1 million or more (Lambshead, 1993)." \\
+        " Estimates of the number of species of parasitic nematode per host suggest that there may be of the order of 25 000 nematode parasites just of vertebrates, most of which remain undescribed (Dobson et al.
+2008)" \\
+        "a large proportion of nematode species may be parasites." \cite{Blaxter2015} \\
 
@@
 
-    \anmerkung{different parameters for different taxa? (Emanuel) -> Effects...} \\ \\
-
     The comparisons of the effects of the taxa can be found in Table \ref{table:Effects unknown data} 
@@
       \begin{center}
-        \begin{longtable}{ |l|l|r|r|r| }
-          \hline
-          \multicolumn{2}{|c|}{Taxa / Model} & globi $\sim$ taxa & globi $\sim$ taxa + depth & globi $\sim$ taxa * depth\\
-          \hline \hline
-          Kingdom & no kingdom  & 0.007608091 & 0.009900630 & 0.0004645054 \\
-          & Fungi               & 0.011317000 & 0.013723310 & 0.0064413062 \\
-          & Chloroplastida      & 0.008634310 & 0.008018847 & 0.0058472786 \\
-          & Metazoa             & 0.035634187 & 0.034139782 & 0.0343237575 \\
-          \hline
-          Phylum & no phylum    & 1.569769e-02 & 3.001749e-02 & 5.757839e-03 \\
-          & Rhombozoa           & 1.538462e-02 & 4.128162e-02 & 1.000000e+00 \\
-          & Hemichordata        & 1.736770e-07 & 3.791496e-07 & 1.736742e-07 \\
-          & Chromerida          & 1.736770e-07 & 4.605436e-07 & 2.220446e-16 \\
-          & Amoebozoa           & 5.343198e-03 & 1.312565e-02 & 2.401619e-03 \\
-          & Onychophora         & 1.736770e-07 & 3.663718e-07 & 1.736753e-07 \\
-          & ... & ... & ... & ... \\
-          % & Priapulida          & 4.347826e-02 & 8.773029e-02 \\
-          % & Tardigrada          & 1.736770e-07 & 3.393298e-07 \\
-          % & Chordata            & 1.140600e-01 & 8.242171e-02 \\
-          % & Xanthophyceae       & 1.736770e-07 & 3.483928e-07 \\
-          % & Haptophyta          & 3.484321e-03 \\
-          % & Microsporidia       & 8.703271e-02 \\
-          % & Chytridiomycota     & 3.062361e-02 \\
-          % & Nematomorpha        & 1.495017e-02 \\
-          % & Loricifera          & 1.736770e-07 \\
-          % & Gnathostomulida     & 1.736770e-07 \\
-          % & Myzostomida         & 4.464286e-03 \\
-          % & Gastrotricha & 1.736770e-07 \\
-          % & Ciliophora & 8.372371e-03 \\
-          % & Entoprocta & 1.736770e-07 \\
-          % & Glomeromycota & 6.609385e-04 \\
-          % & Nematoda & 1.098682e-01 \\
-          % & Cycliophora & 1.736770e-07 \\
-          % & Apicomplexa & 1.374128e-01 \\
-          % & Ascomycota & 1.232671e-02 \\
-          % & Bryozoa & 4.194290e-03 \\
-          % & Nemertea & 9.465855e-03 \\
-          % & Echinodermata & 1.971448e-02 \\
-          % & Rotifera & 8.638563e-03 \\
-          % & Picozoa & 1.736770e-07 \\
-          % & Phaeophyceae & 1.219884e-03 \\
-          % & Acanthocephala & 3.935018e-01 \\
-          % & Bacillariophyta & 4.757374e-05 \\
-          % & Colponemidia & 1.736770e-07 \\
-          % & Platyhelminthes & 3.127011e-01 \\
-          % & Entorrhizomycota & 1.736770e-07 \\
-          % & Chaetognatha & 2.941176e-02 \\
-          % & Placozoa & 1.736770e-07 \\
-          % & Euglenida & 1.729107e-03 \\
-          % & Arthropoda & 2.506545e-02 \\
-          % & Basidiomycota & 6.149777e-03 \\
-          % & Cnidaria & 1.928587e-02 \\
-          % & Ctenophora & 4.205607e-02 \\
-          % & Kinorhyncha & 1.736770e-07 \\
-          % & Porifera & 7.720212e-03 \\
-          % & Orthonectida & 1.153846e-01 \\
-          % & Mollusca & 9.876095e-03 \\
-          % & Brachiopoda & 6.920415e-03 \\
-          % & Haplosporida & 8.108108e-02 \\
-          % & Rhodophyta & 1.971220e-04 \\
-          % & Streptophyta & 8.901842e-03 \\
-          % & Foraminifera & 3.395201e-04 \\
-          % & Chlorophyta & 3.084992e-04 \\
-          \hline \hline
-          \multicolumn{2}{|c|}{Taxa / Model} & correct predicted & correct predicted & correct predicted \\
-          \multicolumn{2}{|c|}{} & $\sim$ taxa & $\sim$ taxa + depth & $\sim$ taxa * depth \\
-          \hline \hline
-          Kingdom & no kingdom  & 0.001139888 & ... & ... \\
-          & Fungi               & 0.001789739 & ... & ... \\
-          & Chloroplastida      & 0.001251109 & ... & ... \\
-          & Metazoa             & 0.005414443 & ... & ... \\
+        \begin{tabular}{ |l|l|r|r|r|r| }
+          \hline
+          Taxa & Model / Effects & min & max & mean & median \\
+          \hline \hline
+          Kingdom & globi $\sim$ taxa & 0,01 & 0,04 & 0,02 & 0,01 \\
+          & globi $\sim$ taxa + depth & 0,01 & 0,03 & 0,02 & 0,01 \\
+          & globi $\sim$ taxa * depth & 0,00 & 0,03 & 0,01 & 0,01 \\
+          \hline
+          Phylum & globi $\sim$ taxa & 0,17 & 393501,80 & 32208,79 & 6149,78 \\
+          & globi $\sim$ taxa + depth & 0,32 & 567010,90 & 55149,54 & 10783,18 \\
+          & globi $\sim$ taxa * depth & 0,00 & 1000000,00 & 225375,33 & 2511,58 \\
           % \hline
-          % Phylum & no phylum    & XXXXX & 3.001749e-02 & 5.757839e-03 \\
-          % & Rhombozoa           & XXXXX & 4.128162e-02 & 1.000000e+00 \\
-          % & Hemichordata        & XXXXX & 3.791496e-07 & 1.736742e-07 \\
-          % & Chromerida          & XXXXX & 4.605436e-07 & 2.220446e-16 \\
-          % & Amoebozoa           & XXXXX & 1.312565e-02 & 2.401619e-03 \\
-          % & Onychophora         & XXXXX & 3.663718e-07 & 1.736753e-07 \\
-          % & ... & ... & ... & ... \\
-          \hline
-        \end{longtable} 
+          % Class & globi $\sim$ taxa & 0,10 & 628190,10 & 44684,53 & 1491,77 \\
+          % & globi $\sim$ taxa + depth &  &  &  &  \\
+          % & globi $\sim$ taxa * depth &  &  &  &  \\
+          \hline
+        \end{tabular} 
       \end{center}
@@
     globi $\sim$ taxa * depth: NOTE: kingdom is not a high-order term in the model
-
-%        ['ott151014', 'Haptophyta']      ['ott16113', 'Microsporidia']
-%                       1.023682e-02                       2.297956e-01
-%   ['ott177160', 'Chytridiomycota']      ['ott189836', 'Nematomorpha']
-%                       8.586035e-02                       3.000311e-02
-%        ['ott199402', 'Loricifera']   ['ott242963', 'Gnathostomulida']
-%                       3.538708e-07                       3.160858e-07
-%       ['ott260040', 'Myzostomida']       ['ott29723', 'Gastrotricha']
-%                       9.396517e-03                       3.335103e-07
-%        ['ott302424', 'Ciliophora']        ['ott362916', 'Entoprocta']
-%                       2.114329e-02                       3.281554e-07
-%     ['ott385878', 'Glomeromycota']          ['ott395057', 'Nematoda']
-%                       1.687966e-03                       1.582959e-01
-%        ['ott41147', 'Cycliophora']       ['ott422673', 'Apicomplexa']
-%                       3.160858e-07                       2.849943e-01
-%        ['ott439373', 'Ascomycota']           ['ott442934', 'Bryozoa']
-%                       2.217673e-02                       7.020371e-03
-%          ['ott445195', 'Nemertea']     ['ott451020', 'Echinodermata']
-%                       1.640797e-02                       3.399753e-02
-%          ['ott471706', 'Rotifera']          ['ott4738955', 'Picozoa']
-%                       1.516272e-02                       6.032169e-07
-%       ['ott48614', 'Phaeophyceae']     ['ott49622', 'Acanthocephala']
-%                       2.014280e-03                       5.672835e-01
-%  ['ott5342311', 'Bacillariophyta']     ['ott5355158', 'Colponemidia']
-%                       1.048765e-04                       5.155971e-07
-%   ['ott555379', 'Platyhelminthes'] ['ott5653719', 'Entorrhizomycota']
-%                       4.271198e-01                       4.449469e-07
-%      ['ott570366', 'Chaetognatha']          ['ott570376', 'Placozoa']
-%                       5.936368e-02                       4.965510e-07
-%        ['ott6137051', 'Euglenida']        ['ott632179', 'Arthropoda']
-%                       4.727403e-03                       1.935197e-02
-%     ['ott634628', 'Basidiomycota']          ['ott641033', 'Cnidaria']
-%                       1.149917e-02                       3.192464e-02
-%        ['ott641212', 'Ctenophora']       ['ott677389', 'Kinorhyncha']
-%                       1.077673e-01                       3.540771e-07
-%           ['ott67819', 'Porifera']      ['ott691845', 'Orthonectida']
-%                       1.613863e-02                       2.716252e-01
-%          ['ott802117', 'Mollusca']       ['ott826261', 'Brachiopoda']
-%                       1.372700e-02                       1.079344e-02
-%      ['ott858063', 'Haplosporida']        ['ott878953', 'Rhodophyta']
-%                       1.925711e-01                       5.358571e-04
-%      ['ott916750', 'Streptophyta']      ['ott936399', 'Foraminifera']
-%                       6.529378e-03                       7.447417e-04
-%       ['ott979501', 'Chlorophyta']
-%                       7.296356e-04
-
-% ['ott1085175', 'Priapulida']        ['ott111438', 'Tardigrada']
-%                       1.000000e+00                       1.736778e-07
-%          ['ott125642', 'Chordata']     ['ott151001', 'Xanthophyceae']
-%                       1.138205e-01                       1.736786e-07
-%        ['ott151014', 'Haptophyta']      ['ott16113', 'Microsporidia']
-%                       1.000000e+00                       9.998257e-01
-%   ['ott177160', 'Chytridiomycota']      ['ott189836', 'Nematomorpha']
-%                       1.000000e+00                       2.220446e-16
-%        ['ott199402', 'Loricifera']   ['ott242963', 'Gnathostomulida']
-%                       2.220446e-16                       2.220446e-16
-%       ['ott260040', 'Myzostomida']       ['ott29723', 'Gastrotricha']
-%                       4.381889e-06                       1.736782e-07
-%        ['ott302424', 'Ciliophora']        ['ott362916', 'Entoprocta']
-%                       5.518629e-05                       1.736802e-07
-%     ['ott385878', 'Glomeromycota']          ['ott395057', 'Nematoda']
-%                       9.966669e-01                       4.725574e-01
-%        ['ott41147', 'Cycliophora']       ['ott422673', 'Apicomplexa']
-%                       2.220446e-16                       8.049756e-01
-%        ['ott439373', 'Ascomycota']           ['ott442934', 'Bryozoa']
-%                       1.541511e-02                       1.230174e-03
-%          ['ott445195', 'Nemertea']     ['ott451020', 'Echinodermata']
-%                       1.777755e-01                       2.505179e-03
-%          ['ott471706', 'Rotifera']          ['ott4738955', 'Picozoa']
-%                       3.125183e-01                       1.736782e-07
-%       ['ott48614', 'Phaeophyceae']     ['ott49622', 'Acanthocephala']
-%                       9.252076e-04                       3.992551e-04
-%  ['ott5342311', 'Bacillariophyta']     ['ott5355158', 'Colponemidia']
-%                       1.114784e-10                       2.220446e-16
-%   ['ott555379', 'Platyhelminthes'] ['ott5653719', 'Entorrhizomycota']
-%                       2.478056e-02                       1.736781e-07
-%      ['ott570366', 'Chaetognatha']          ['ott570376', 'Placozoa']
-%                       1.000000e+00                       4.021433e-08
-%        ['ott6137051', 'Euglenida']        ['ott632179', 'Arthropoda']
-%                       9.257999e-01                       1.658528e-02
-%     ['ott634628', 'Basidiomycota']          ['ott641033', 'Cnidaria']
-%                       1.473459e-03                       1.218008e-02
-%        ['ott641212', 'Ctenophora']       ['ott677389', 'Kinorhyncha']
-%                       2.878555e-03                       1.736844e-07
-%           ['ott67819', 'Porifera']      ['ott691845', 'Orthonectida']
-%                       1.329787e-02                       2.931611e-02
-%          ['ott802117', 'Mollusca']       ['ott826261', 'Brachiopoda']
-%                       5.167513e-03                       9.974617e-01
-%      ['ott858063', 'Haplosporida']        ['ott878953', 'Rhodophyta']
-%                       9.999999e-01                       9.658119e-11
-%      ['ott916750', 'Streptophyta']      ['ott936399', 'Foraminifera']
-%                       6.037565e-03                       6.367782e-03
-%       ['ott979501', 'Chlorophyta']
-%                       2.027010e-05
 

### 2018-03-12 code/evaluation/analyse_output.R

@@ -35,51 +35,106 @@ table(all.taxa$originaltag)
 print('------------all.taxa$finaltag------------------')
 table(all.taxa$finaltag)
 
-table(all.taxa[all.taxa$finaltag+1 != all.taxa$originaltag, ]$kingdom)
+# table(all.taxa[all.taxa$finaltag+1 != all.taxa$originaltag, ]$kingdom)
+
+print('---------------------------')
+
+table(droplevels(all.taxa[all.taxa$finaltag+1 != all.taxa$originaltag, ]$phylum))
+
+print('-----------Ascomycota-------------')
+ascomycota <- all.taxa[all.taxa$phylum=="['ott439373', 'Ascomycota']", ]
+bug_data.ascomycota <- ascomycota[ascomycota$finaltag+1 != ascomycota$originaltag, ]
+table(droplevels(bug_data.ascomycota$class))
+dim(ascomycota)
+
+print('---------------------------')
+
+print('-----------Chordata-------------')
+chordata <- all.taxa[all.taxa$phylum=="['ott125642', 'Chordata']", ]
+bug_data.chordata <- chordata[chordata$finaltag+1 != chordata$originaltag, ]
+table(droplevels(bug_data.chordata$class))
+dim(chordata)
+
+print('-----------Sarcopterygii-------------')
+sarcopterygii <- chordata[chordata$class=="['ott458402', 'Sarcopterygii']", ]
+bug_data.sarcopterygii <- sarcopterygii[sarcopterygii$finaltag+1 != sarcopterygii$originaltag, ]
+table(droplevels(bug_data.sarcopterygii$order))
+dim(sarcopterygii)
+
+print('---------------------------')
+
+print('-----------Arthropoda-------------')
+arthropoda <- all.taxa[all.taxa$phylum=="['ott632179', 'Arthropoda']", ]
+bug_data.arthropoda <- arthropoda[arthropoda$finaltag+1 != arthropoda$originaltag, ]
+table(droplevels(bug_data.arthropoda$class))
+
+print('-----------Insecta-------------')
+insecta <- arthropoda[arthropoda$class=="['ott1062253', 'Insecta']", ]
+bug_data.insecta <- insecta[insecta$finaltag+1 != insecta$originaltag, ]
+table(droplevels(bug_data.insecta$order))
+
+diptera <- insecta[insecta$order=="['ott661378', 'Diptera']", ]
+dim(diptera)
+
[…]

### 2018-03-12 code/metadata/analyse_input.R

@@ -57,14 +57,21 @@ print('--------------------------------------------------')
 
 inner.taxa$multifurc <- inner.taxa$nr_children-1
 
-# ggplot(inner.taxa, aes(multifurc)) +
-#     geom_histogram( 
-#         col="black", 
-#         aes(fill=..count..)) +
-#     scale_y_log10() +
-#     labs(x="number of children", y="number of nodes")
-# ggsave("multifurc.pdf")
+ggplot(inner.taxa, aes(multifurc)) +
+    geom_histogram(col="black") +
+    scale_y_log10() +
+    labs(x="number of children", y="number of nodes")
+ggsave("multifurc.pdf")
 
+ggplot(inner.taxa, aes(multifurc)) +
+    geom_histogram( 
+        col="black", 
+        binwidth = 1,
+        aes(fill=..count..)) +
+    xlim(0, 30) +
+    scale_y_log10() +
+    labs(x="number of children", y="number of nodes")
+ggsave("multifurc_small.pdf")
 
 print('--------------------------------------------------')
 print('-------------------------multifurc data-------------------------')
@@ -98,173 +105,166 @@ anova(kingdom.furc.mod, phylum.furc.mod, class.furc.mod, order.furc.mod, family.
 
 print('-------------------kingdom + depth / min/max/mean.height-----------------------')
 
-# kingdomPdepth.furc.mod <- glm(multifurc~kingdom+depth, data=inner.taxa,
-#                    family="poisson")
-# print(c('BIC=',  BIC(kingdomPdepth.furc.mod)))
+kingdomPdepth.furc.mod <- glm(multifurc~kingdom+depth, data=inner.taxa,
+                   family="poisson")
+print(c('BIC=',  BIC(kingdomPdepth.furc.mod)))
 
-# kingdomPminHeight.furc.mod <- glm(multifurc~kingdom+min.height, data=inner.taxa,
-#                    family="poisson")
-# print(c('BIC=',  BIC(kingdomPminHeight.furc.mod)))
+kingdomPminHeight.furc.mod <- glm(multifurc~kingdom+min.height, data=inner.taxa,
+                   family="poisson")
+print(c('BIC=',  BIC(kingdomPminHeight.furc.mod)))
 
[…]

### 2018-03-13 Paper - Latex/Paper - Skizze - v3.tex
Paper - Results - correlation between Effects of Phyla

@@
             \hline \hline
-            multifurc $\sim$ taxa & 545740 & 499227 & 482265 \\
-            \hline
-            multifurc $\sim$ taxa + depth & 544789 & 493017 & XXXXX \\
-            \hline
-            multifurc $\sim$ taxa * depth & 544062 & 488366 & \cellcolor{green!60}XXXXX \\
+            multifurc $\sim$ taxa & 545740 & \cellcolor{green!10}499227 & \cellcolor{green!30}482265 \\
+            \hline
+            multifurc $\sim$ taxa + depth & 544789 & \cellcolor{green!10}493017 & \cellcolor{green!50}478998 \\
+            \hline
+            multifurc $\sim$ taxa * depth & 544062 & \cellcolor{green!30}488366 & \cellcolor{green!50}476382 \\
             \hline
@@
             \hline \hline
-            multifurc $\sim$ taxa & \cellcolor{green!15}545799 & \cellcolor{green!35}500004 & \cellcolor{green!45}485121 \\
-            \hline
-            multifurc $\sim$ taxa + depth & \cellcolor{green!15}544862 & \cellcolor{green!40}493808 & \cellcolor{green!45}481869 \\
-            \hline
-            multifurc $\sim$ taxa * depth & \cellcolor{green!15}544179 & \cellcolor{green!45}489845 & \cellcolor{green!50}XXXXX \\
-            \hline
-          \end{tabular} 
-        \end{center}
-        \caption{BIC of unknown information}
+            multifurc $\sim$ taxa & 545799 & \cellcolor{green!10}500004 & \cellcolor{green!50}485121 \\
+            \hline
+            multifurc $\sim$ taxa + depth & 544862 & \cellcolor{green!30}493808 & \cellcolor{green!50}481869 \\
+            \hline
+            multifurc $\sim$ taxa * depth & 544179 & \cellcolor{green!50}489845 & \cellcolor{green!50}481494 \\
+            \hline
+          \end{tabular} 
+        \end{center}
+        \caption{BICs of unknown information}
         \label{table:BIC unknown information} 
@@
             \hline \hline
+            correct predicted $\sim$ taxa & XXXXX & XXXXX & XXXXX & XXXXX \\
+            \hline
+            correct predicted $\sim$ taxa + depth & 117703 & XXXXX & XXXXX & XXXXX \\
+            \hline
+            correct predicted $\sim$ taxa * depth & 117592 & XXXXX & XXXXX & \cellcolor{green!60}XXXXX \\
+            \hline
+          \end{tabular} 
+        \end{center}
+        \caption{Residuals of cross validation prediction}
+        \label{table:Residuals cross validation} 
+      \end{table}
+
+      \begin{table}[h]
+        \begin{center}
+          \begin{tabular}{ |l|r|r|r|r| }
+            \hline
+            Model / Taxa & Kingdom & Phylum & Class & Order \\
+            \hline \hline
             correct predicted $\sim$ taxa & 117936 & 112242 & XXXXX & XXXXX \\
@@
                   & globi $\sim$ taxa * depth & 0,00 & 1000000,00 & 225375,33 & 2511,58 \\
-          % \hline
-          % Class & globi $\sim$ taxa & 0,10 & 628190,10 & 44684,53 & 1491,77 \\
-          % & globi $\sim$ taxa + depth &  &  &  &  \\
-          % & globi $\sim$ taxa * depth &  &  &  &  \\
           \hline
@@
     globi $\sim$ taxa * depth: NOTE: kingdom is not a high-order term in the model
+
+    \begin{figure}[h!]
+      \centering
+      \includegraphics[trim = 0mm 0mm 0mm 15mm, clip, width=\textwidth]{Figures/EffectsOfModel-Data-Phylum.JPG}
+      \caption{Effects of Model: Data $\sim$ Phylum}
+      \label{fig:...}
+    \end{figure}
+    \begin{figure}[h!]
+      \centering
+      \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{Figures/EffectsOf3Models-Data-Phylum.JPG}
+      \caption{Effects of 3 Models: Data $\sim$ Phylum (+/* depth)}
+      \label{fig:...}
+    \end{figure}
+    \begin{figure}[h!]
+      \centering
+      \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{Figures/EffectsOf3Models-Data-Phylum_loglog.JPG}
+      \caption{Effects of 3 Models: Data $\sim$ Phylum (+/* depth) \\ both axis in log scale}
+      \label{fig:...}
+    \end{figure}
 

### 2018-03-13 code/evaluation/analyse_cross-validation.R

@@ -1,0 +1,100 @@
+library(data.table)
+# library(ggplot2)
+# library(effects)
+library(lme4)
+
+format(Sys.time(), "%a %b %d %X %Y")
+
+all.taxa <- fread("../../results/Eukaryota-cross_evaluation-taxa.csv")
+# ott_id,originaltag,finaltag,depth,nr_children,run,new_finaltag,correct_predicted,name,rank,uniqname,kingdom,phylum,class,order
+
+### right mode for all
+all.taxa$kingdom <- as.factor(all.taxa$kingdom)
+all.taxa$phylum <- as.factor(all.taxa$phylum)
+all.taxa$class <- as.factor(all.taxa$class)
+all.taxa$order <- as.factor(all.taxa$order)
+
+print('----------------------- leaf.taxa$T/F ---------------------------')
+leaf.taxa <-  all.taxa[all.taxa$nr_children==0, ]
+leaf.taxa <- as.data.frame(leaf.taxa)
+table(leaf.taxa$correct_predicted)[order(table(leaf.taxa$correct_predicted))]
+
+leaf.taxa$correct_predicted <- !is.na(leaf.taxa$correct_predicted)
+
+null.correct_predicted.mod <- glm(correct_predicted~1, data=leaf.taxa, family="binomial")
+
+print('------------------------kingdom - phylum - class - order--------------------------')
+
+kingdom.correct_predicted.mod <- glm(correct_predicted~kingdom, data=leaf.taxa, family="binomial")
+print(c('BIC=',  BIC(kingdom.correct_predicted.mod)))
+# effect("kingdom", kingdom.correct_predicted.mod)
+# anova(null.correct_predicted.mod, kingdom.correct_predicted.mod)
+
+# summary(kingdom.correct_predicted.mod)
+
+phylum.correct_predicted.mod <- glm(correct_predicted~phylum, data=leaf.taxa, family="binomial")
+print(c('BIC=',  BIC(phylum.correct_predicted.mod)))
+# effect("phylum", phylum.correct_predicted.mod)
+
+class.correct_predicted.mod <- glm(correct_predicted~class, data=leaf.taxa, family="binomial")
+print(c('BIC=',  BIC(class.correct_predicted.mod)))
+
+order.correct_predicted.mod <- glm(correct_predicted~order, data=leaf.taxa, family="binomial")
+print(c('BIC=',  BIC(order.correct_predicted.mod)))
+
[…]

### 2018-03-14 Paper - Latex/Paper - Skizze - v3.tex
Paper - Methods - Ancestral state reconstruction methodes - Fitch Maximum Parsimony

@@
 
+    Multifurcation \\
+    binary or bifurcating... \cite{Felsenstein2003}
+
 %---------------------------------------------------------------------------------------------------
@@
     %---------------------------------------------------------------------------------------------------
-    \section{ancestral state reconstruction methods}
+    \section{Ancestral state reconstruction methods}
+      For about 50 years, people have been working on ancestral state reconstruction. The first paper 
+        mentioned above is by Camin and Sokal, who in 1965 were working on algorithms for discrete-state 
+        data \cite{Camin1965}. Different methods have been developed and the question is which method is 
+        the most suitable for our problem. \\
+      For this purpose, various studied methods and their advantages and disadvantages were compared. \\
+
       Royer-Carenzi et al. distinguishes two major classes of ancestral state reconstruction methods: \\
       The first is to explain the current state with the least number of state changes between an 
-        ancestor and his child, this is called parsimonious.
+        ancestor and his child, this is called parsimonious. \\
       The other class she presents involves modeling the character evolution as a stochastic process and 
@@
 
-      Since the simpler parsimony methods are sufficient for our case, we have decided for them. \\
-      \todotext{In the following we introduce ... there are these methods .. which are important for us ...}
+      Following the principle of the simpler model first, the decision has \todo{fallen?} on parsimonious 
+        methods since these are sufficient for the case present here. \\
+      Felsenstein \cite{Felsenstein2003} discusses in his book two algorithms that generalize all 
+        previous methods (from Camin and Sokal \cite{Camin1965}, \todo{Kluge and Farris} and Farris 
+        \cite{Farris1970}): Fitch parsiomony \cite{Fitch1971} and Sankoff parsimony \cite{Sankoff1975}. \\
+      \anmerkungstext{Unter Farris war auch noch der Begriff Wagner trees in gebrauch, als 
+        Verallgemeinerung der parsimonious trees von Camin und Sokal. (Lydia)} \\
+      \todo{Wagner-parsimony \cite{Swofford1987}} \\
+
+      Thus, the methods used in this work are those of Fitch and Sankoff. For Fitch, the algorithm has 
+        been extended from binary to multifurcated trees. For the Sankoff algorithm, Louca and Doebeli 
+        have presented an implementation for non-binary trees published in an R package named 
+        \textit{castor} \cite{Louca2017}.
 
@@
       \subsection{Fitch maximum parsimony}
-        Described from [COO98] + others ... - implemented for multifurcating trees
-
-        Fitch algorithm for binary trees:
-        \begin{figure}
-          \caption{bla}
+        Fitch maximum parsimony is an algorithm for rooted, binary trees and describes an ancestral state 
+          reconstruction for discrete states \cite{Fitch1971} by minimizing transitions between states. \\
+        Note, the original Fitch algorithm has the sole purpose of minimizing the number of transitions 
+          and not reconstructing the ancestral nodes. Felsenstein \cite{Felsenstein2003} describes a 
+          simple extension for the reconstruction. Cunningham et al. \cite{Cunningham1998} have refined 
+          these. \todotext{Wir haben mit ein paar kleinen änderungen optimiert... und schließlich auf multifurcated angepasst...} \\
+        To understand the differences to the multifurcated case, the algorithm for the binary case is 
+          explained briefly. \\
+
+        Input: A rooted, binary tree, with state informations in the leaf nodes. Each node is depicted as 
+          a set of states. Internal nodes have three sets, which are empty at the beginning, excluding the
+          root node, it has only one. Leaf nodes have their state as a set (eg \{FL\}, unknown leaf 
+          nodes) the union of all possible states (\{FL, P\}). \\
+        The algorithm traverses three times trough the tree and fills these sets. \\
+        In each step, two sets are considered and their intersect formed. There are two cases:
+        \begin{wrapfigure}{r}{0.4\textwidth}
           \centering
-            \includegraphics[width=0.5\textwidth]{Figures/Fitch1.png}
-        \end{figure}
-
-        Der Baum hat die folgende Struktur: Alle inneren Knoten sind leer. In den Blattknoten befindet 
-        sich entweder das Tag FL oder P, oder deren Vereinigung, wenn es sich um einen unknown node handelt.
-
-        Der Fitch Algorithmus ist aufgeteilt in drei Schritte, in welchen man jeweils durch den Baum traversiert.
-        Schritt 1 beginnt von de Blättern aus, da sich dort zu Beginn die einzige Information befindet. 
-        Für jeden Knoten gilt, wenn seine Kinder schon Information enthalten, dann bilde die Schnittmenge 
-        der states und schreibe diese als Information in den aktuellen Knoten. Ist die Schnittmenge leer, 
-        dann schreibe die Vereinigung aller möglichen states in den Knoten. Für alle Kinder, die noch keine 
-        Information haben, führe diesen Schritt erst für diese aus.
-        Schritt zwei geht von den Kindern der Wurzel bis zu den Vätern der Blätter. Jeder Knoten bekommt 
-        einen zweiten Tag, der sich aus der Vereinigung des states des Vaterknoten und der Geschwisterknoten
-        zusammensetzt. Ist diese leer, bekommt der Knoten wieder die Vereinigung aller states, also $\{FL,P\}$ als Tag.
-
-        Hier gibt es einige Möglichkeiten, wie dieser Schritt genau aussieht.
-        1. Version: Es wird nur der erste Tag vom Vaterknoten genutzt. Außerdem wird von den 
-        Geschwisterknoten zuerst der Schnitt gebildet, und danach vom Ergebnis nochmal mit dem Vaterknoten zusammen.
-        (Immer wenn der Schnitt leer ist, ist das Ergebnis die Vereinigung aller states, also $\{FL,P\}$. Auch im folgenden...)
-        2. Version: Es wird nur der erste Tag vom Vaterknoten genutzt. Er wird zusammen mit den 
-        Geschwisterstates genommen und direkt ein Schnitt aller Mengen gebildet.
-        3. Version: Es werden alle vorherigen states vom Vater genutzt und von diesen ein Schnitt gebildet.
-        Das selbe gilt für die Geschwisterstates. Und dann wird ein dritter Schnitt zwischend en Ergebnissen gebildet.
-        4. Version: Es werden alle states genutzt und direkt in einem Schnitt zusammengenommen.
-
-        Der Finale Schritt traversiert nochmal über den Baum und Bildet aus den zwei states pro Knoten einen finalen
-        Tag, indem wieder der Schnitt der beiden states das Ergebnis ist.
+          \includegraphics[width=0.39\textwidth]{Figures/Fitch1.png}
+          \caption{Fitch algorithm for binary trees}
+          \label{fig: binary Fitch}
+        \end{wrapfigure}
+        \begin{enumerate}
+          \item The intersection is not empty and corresponds to the new set.
+          \item The intersection is empty. $\rightarrow$ Build the union of these sets as new set.
+        \end{enumerate}
+        First traverse from the leaf nodes to the root / move down the tree / postorder tree traversal. Each internal node is formed from its child nodes. \\
+        Second traverse from the root node to the leafs. Each internal node is formed from its father node 
+          and its sibling node. \\
+        Last traversion (direction does not matter \todotext{does it? Welche Mengen/Menge wird genommen 
+          von jedem Knoten?}): Build the final state for every node. It is formed 
+          from the sets of previous traversals. \\
+
+        Figure \ref{fig: binary Fitch} shows the firch algorithm for binary trees with 5 leaf nodes, \todo{one unknown}.
+
+        The finale step is not part of the original Fitch algorithm, as it only aims to minimize the 
+          transitions without predicting actual states of internal nodes. This step is described by \todo{...}. \\
+
+        % Der Fitch Algorithmus ist aufgeteilt in drei Schritte, in welchen man jeweils durch den Baum traversiert.
+        % Schritt 1 beginnt von de Blättern aus, da sich dort zu Beginn die einzige Information befindet. 
+        % Für jeden Knoten gilt, wenn seine Kinder schon Information enthalten, dann bilde die Schnittmenge 
+        % der states und schreibe diese als Information in den aktuellen Knoten. Ist die Schnittmenge leer, 
+        % dann schreibe die Vereinigung aller möglichen states in den Knoten. Für alle Kinder, die noch keine 
+        % Information haben, führe diesen Schritt erst für diese aus.
+        % Schritt zwei geht von den Kindern der Wurzel bis zu den Vätern der Blätter. Jeder Knoten bekommt 
+        % einen zweiten Tag, der sich aus der Vereinigung des states des Vaterknoten und der Geschwisterknoten
+        % zusammensetzt. Ist diese leer, bekommt der Knoten wieder die Vereinigung aller states, also $\{FL,P\}$ als Tag.
+
+        % Hier gibt es einige Möglichkeiten, wie dieser Schritt genau aussieht.
+        % 1. Version: Es wird nur der erste Tag vom Vaterknoten genutzt. Außerdem wird von den 
+        % Geschwisterknoten zuerst der Schnitt gebildet, und danach vom Ergebnis nochmal mit dem Vaterknoten zusammen.
+        % (Immer wenn der Schnitt leer ist, ist das Ergebnis die Vereinigung aller states, also $\{FL,P\}$. Auch im folgenden...)
+        % 2. Version: Es wird nur der erste Tag vom Vaterknoten genutzt. Er wird zusammen mit den 
+        % Geschwisterstates genommen und direkt ein Schnitt aller Mengen gebildet.
+        % 3. Version: Es werden alle vorherigen states vom Vater genutzt und von diesen ein Schnitt gebildet.
+        % Das selbe gilt für die Geschwisterstates. Und dann wird ein dritter Schnitt zwischend en Ergebnissen gebildet.
+        % 4. Version: Es werden alle states genutzt und direkt in einem Schnitt zusammengenommen.
+
+        % Der Finale Schritt traversiert nochmal über den Baum und Bildet aus den zwei states pro Knoten einen finalen
+        % Tag, indem wieder der Schnitt der beiden states das Ergebnis ist.
 
@@
       \subsubsection{Sankoff}
-        Maximum parsimony algorithm from Sankoff implemented in the R package castor \cite{Louca2017}.
+        Maximum parsimony algorithm from Sankoff implemented in the R package castor \cite{Louca2017}. \\
+        \todo{transition probabilities: all equal}
 
@@
           \begin{center}
-              \begin{tabular}{ |l|r|r|r|r| }
-                \hline
-                Model / Taxa & Kingdom & Phylum & Class & Order \\
+              \begin{tabular}{ |l|r|r|r|r|r| }
+                \hline
+                Model / Taxa & Kingdom & Phylum & Class & Order & Family \\
                 \hline \hline
@@
           \begin{center}
-            \begin{tabular}{ |l|r|r|r|r| }
-              \hline
-              Model / Taxa & Kingdom & Phylum & Class & Order \\
-              \hline \hline
-              multifurc $\sim$ taxa & 8273333 & \cellcolor{green!15}7937828 & \cellcolor{green!20}7842157 & \cellcolor{green!30}7644249\\
+            \begin{tabular}{ |l|r|r|r|r|r| }
+              \hline
+              Model / Taxa & Kingdom & Phylum & Class & Order & Family \\
+              \hline \hline
+              multifurc $\sim$ taxa & 8273333 & \cellcolor{green!15}7937828 & \cellcolor{green!20}7842157 & \cellcolor{green!30}7644249 \\
+              multifurc $\sim$ taxa & 8257680 & \cellcolor{green!15}7922207 & \cellcolor{green!20}7826490 & \cellcolor{green!35}7574154 \\
               \hline
@@
         \begin{center}
-          \begin{tabular}{ |l|r|r|r| }
-            \hline
-            Model / Taxa & Kingdom & Phylum & Class \\
+          \begin{tabular}{ |l|r|r|r|r| }
+            \hline
+            Model / Taxa & Kingdom & Phylum & Class & Order \\
             \hline \hline
@@
             \hline
-            multifurc $\sim$ taxa + depth & 544862 & \cellcolor{green!30}493808 & \cellcolor{green!50}481869 \\
+            multifurc $\sim$ taxa + depth & 544862 & \cellcolor{green!30}493808 & \cellcolor{green!50}481869 & 478851 \\
             \hline

### 2018-03-15 Paper - Latex/Paper - Skizze - v3.tex
Paper - Methods - Fitch... ; update simulation code, multifurcation input added

@@
     \cite{Poelen2014} which we used, we could only collect 25,992 parasitic and 34,879 
-    free-living species. It follows that we have only $\approx 2.4\%$ state information. \\
+    free-living species. It follows that we have only $\approx 2.4~\%$ state information. \\
   So far, especially small scale studies have been carried out or highly manual. In this scale, it 
@@
   In den Bacteria und Archaea wurde das mal allgemein für binary traits gemacht:
-  "A total 90\% of all binary traits described molecular functions, specifically the presence or absence of a gene or a set of gene involved in biochemical pathways."
+  "A total 90~\% of all binary traits described molecular functions, specifically the presence or absence of a gene or a set of gene involved in biochemical pathways."
   \cite{Goberna2015} \\
@@
       \todotext{Marius:} "Every dataset has it's own characteristics and downsides. ITIS is only a small 
-        set of 100\% confirmed and named species. GBIF is not composed with the help of phylogeny, the 
+        set of 100~\% confirmed and named species. GBIF is not composed with the help of phylogeny, the 
         same is valid for the NCBI taxonomy. The WORMS taxonomy is a way too small dataset of mostly 
@@
         statement about these probabilities.
-      In general, we assume that there are 40\% parasites and 60\% free-livings which is based on the 
+      In general, we assume that there are 40~\% parasites and 60~\% free-livings which is based on the 
         estimates by Windsor \cite{Windsor1998} and 
@@
         \end{center}
-        \caption{60\% Free-living - 40\% Parasites \\ red: parasites, blue: free-living, \\ the threshold is at 0.4}
+        \caption{60~\% Free-living - 40~\% Parasites \\ red: parasites, blue: free-living, \\ the threshold is at 0.4}
         \label{fig:Beta distribution}
@@
       Different thresholds with different beta distributions were simulated, with different distributions 
-        of parasites and free-livings: 50\% P to 50\% FL, 40\% P to 60\% FL, 30\% P to 70\% FL and 
-        20\% P to 80 \% FL (\todo{see results simulation, ref...}). Figure \ref{fig:Beta distribution} 
+        of parasites and free-livings: 50~\% P to 50~\% FL, 40~\% P to 60~\% FL, 30~\% P to 70~\% FL and 
+        20~\% P to 80~\% FL (\todo{see results simulation, ref...}). Figure \ref{fig:Beta distribution} 
         shows one example of these. \\
@@
           simple extension for the reconstruction. Cunningham et al. \cite{Cunningham1998} have refined 
-          these. \todotext{Wir haben mit ein paar kleinen änderungen optimiert... und schließlich auf multifurcated angepasst...} \\
+          these. \todotext{Wir haben mit ein paar kleinen änderungen optimiert... und schließlich auf 
+          multifurcated angepasst...} \todotext{eigentlich ist Cunningham 'nur' eine kritische 
+          Neubewertung. Sie beziehen ihren Algortihmus auf Swofford und Maddison...} \\
         To understand the differences to the multifurcated case, the algorithm for the binary case is 
-          explained briefly. \\
-
+          briefly explained and referred to the extension. \\
+          \begin{wrapfigure}[19]{r}{0.5\textwidth}
+            \centering
+            \includegraphics[width=0.4\textwidth]{Figures/Fitch1.png}
+            \caption{Fitch algorithm for binary trees. \\
+              The unknown leaf node is discribed with both states. Computed internal nodes (exclusive the 
+              root node) consists of three sets, where the last set is the final one (bold). \\
+              From the second internal node (seen from the root node) there are several possibilities to 
+              create the second and third set.}
+            \label{fig: binary Fitch}
+          \end{wrapfigure}
         Input: A rooted, binary tree, with state informations in the leaf nodes. Each node is depicted as 
-          a set of states. Internal nodes have three sets, which are empty at the beginning, excluding the
-          root node, it has only one. Leaf nodes have their state as a set (eg \{FL\}, unknown leaf 
-          nodes) the union of all possible states (\{FL, P\}). \\
+          a set of states. There are only two states in this paper, free-living (FL) and parasitic (P). 
+          Internal nodes have three sets, which are empty at the beginning, excluding the root node, it 
+          has only one. Leaf nodes have their state as a set (eg \{FL\} or \{P\}, unknown leaf nodes the 
+          union of all possible states (\{FL, P\}). \\
         The algorithm traverses three times trough the tree and fills these sets. \\
         In each step, two sets are considered and their intersect formed. There are two cases:
-        \begin{wrapfigure}{r}{0.4\textwidth}
-          \centering
-          \includegraphics[width=0.39\textwidth]{Figures/Fitch1.png}
-          \caption{Fitch algorithm for binary trees}
-          \label{fig: binary Fitch}
-        \end{wrapfigure}
         \begin{enumerate}
@@
         \end{enumerate}
-        First traverse from the leaf nodes to the root / move down the tree / postorder tree traversal. Each internal node is formed from its child nodes. \\
+        First traverse from the leaf nodes to the root / move down the tree / postorder tree traversal. 
+          Each internal node is formed from its child nodes, where at the beginning the only information
+          lies. \\
         Second traverse from the root node to the leafs. Each internal node is formed from its father node 
           and its sibling node. \\
-        Last traversion (direction does not matter \todotext{does it? Welche Mengen/Menge wird genommen 
-          von jedem Knoten?}): Build the final state for every node. It is formed 
+        Last traversion (direction does not matter): Build the final state for every node. It is formed 
           from the sets of previous traversals. \\
-
-        Figure \ref{fig: binary Fitch} shows the firch algorithm for binary trees with 5 leaf nodes, \todo{one unknown}.
-
-        The finale step is not part of the original Fitch algorithm, as it only aims to minimize the 
-          transitions without predicting actual states of internal nodes. This step is described by \todo{...}. \\
-
-        % Der Fitch Algorithmus ist aufgeteilt in drei Schritte, in welchen man jeweils durch den Baum traversiert.
-        % Schritt 1 beginnt von de Blättern aus, da sich dort zu Beginn die einzige Information befindet. 
-        % Für jeden Knoten gilt, wenn seine Kinder schon Information enthalten, dann bilde die Schnittmenge 
-        % der states und schreibe diese als Information in den aktuellen Knoten. Ist die Schnittmenge leer, 
-        % dann schreibe die Vereinigung aller möglichen states in den Knoten. Für alle Kinder, die noch keine 
-        % Information haben, führe diesen Schritt erst für diese aus.
-        % Schritt zwei geht von den Kindern der Wurzel bis zu den Vätern der Blätter. Jeder Knoten bekommt 
-        % einen zweiten Tag, der sich aus der Vereinigung des states des Vaterknoten und der Geschwisterknoten
-        % zusammensetzt. Ist diese leer, bekommt der Knoten wieder die Vereinigung aller states, also $\{FL,P\}$ als Tag.
-
-        % Hier gibt es einige Möglichkeiten, wie dieser Schritt genau aussieht.
-        % 1. Version: Es wird nur der erste Tag vom Vaterknoten genutzt. Außerdem wird von den 
-        % Geschwisterknoten zuerst der Schnitt gebildet, und danach vom Ergebnis nochmal mit dem Vaterknoten zusammen.
-        % (Immer wenn der Schnitt leer ist, ist das Ergebnis die Vereinigung aller states, also $\{FL,P\}$. Auch im folgenden...)
-        % 2. Version: Es wird nur der erste Tag vom Vaterknoten genutzt. Er wird zusammen mit den 
-        % Geschwisterstates genommen und direkt ein Schnitt aller Mengen gebildet.
-        % 3. Version: Es werden alle vorherigen states vom Vater genutzt und von diesen ein Schnitt gebildet.
-        % Das selbe gilt für die Geschwisterstates. Und dann wird ein dritter Schnitt zwischend en Ergebnissen gebildet.
-        % 4. Version: Es werden alle states genutzt und direkt in einem Schnitt zusammengenommen.
-
-        % Der Finale Schritt traversiert nochmal über den Baum und Bildet aus den zwei states pro Knoten einen finalen
-        % Tag, indem wieder der Schnitt der beiden states das Ergebnis ist.
-
-        Ich habe diese Versionen mit 100 Bäumen mit 10000 Blattknoten und der Verteilung 60\% FL zu 40\% P simuliert.
-        Bei 90 \% unbekannten Knoten lag Version 1 zu 89.67 \%, Version 2 zu 89.67 \%, Version 3 zu 
-          90.72 \% und Version 4 zu 90.74 \% richtig.
-
+        (The original Fitch algorithm was designed to minimize transitions without predicting actual states 
+          of internal nodes, so it was just the first traversal.) \\
+        The extension to the non-binary case is quite obvious, but holds some opportunities. In this case, 
+          more than two children may be present for the first traversal, but the incision or union may 
+          also be formed over more than two sets. Also in the second traversing, there may be several 
+          sibling nodes. However, there are several possibilities here that were all tested and compared 
+          in the simulation. Some of these options are already available in the binary case:
+        \begin{itemize}
+          \item The father node has (except for the root node) two state sets, because he came through 
+            the up-traversing previously. Are both sets used or only the first traversing?
+          \item Since there are several siblings, do you first of all make the cut or union, or directly 
+            in the whole with the father node?
+        \end{itemize}
+        The first point already has an effect on the binary case. Figure \ref{fig: binary Fitch} shows 
+          both possibilities of the three sets. \\
+        Cunningham uses only the first state set of the father node \cite{Cunningham1998}. \\
+        From these two points four different versions of Fitch were formed:
+        \begin{enumerate}
+          \item Fitch 1: First state set of father node; intersection/union of siblings first.
+          \item Fitch 2: First state set of father node; intersection/union of siblings together with father node.
+          \item Fitch 3: Both state sets of father node; intersection/union of siblings first.
+          \item Fitch 4: Both state sets of father node; intersection/union of siblings together with father node sets.
+        \end{enumerate}
         \begin{figure}
-          \caption{bla}
           \centering
-            \includegraphics[width=0.6\textwidth]{Figures/simulation_fitch_evaluation.png}
+          \includegraphics[width=0.8\textwidth]{Figures/simulation_fitch_evaluation.png}
+          \caption{Test of Fitch Versions.}
+          \label{fig:Fitch versions}
         \end{figure}
-
-        How to extend Fitch for multifunction?:
-        \begin{figure}
-          \caption{bla}
-          \centering
-            \includegraphics[width=1\textwidth]{Figures/Fitch2.png}
-        \end{figure}
+        These four versions were tested in the simulation with 100 trees and 10000 leaf nodes and a
+          distribution of 60~\% FL to 40~\% P. Figure \ref{fig:Fitch versions} shows this over all unknown 
+          node percentage. \\
+        At 90~\% unknown nodes, version 1 was 89.67~\%, version 2 was 89.67~\%, version 3 was 90.72~\%, 
+          and version 4 was 90.74~\% correct. Therefore, only version 4 was used for all further 
+          simulations.
 
@@
 
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  \section{real data analysis}
-    \begin{itemize}
-      \item Import tree
-      \item Import interactions
-      \item run castor algorithm / and others?
-      \item interprete results (cross validation - leave 100 out)
-    \end{itemize}
+  % %---------------------------------------------------------------------------------------------------
+  % %---------------------------------------------------------------------------------------------------
+  % %---------------------------------------------------------------------------------------------------
+  % \section{real data analysis}
+  %   \begin{itemize}
+  %     \item Import tree
+  %     \item Import interactions
+  %     \item run castor algorithm / and others?
+  %     \item interprete results (cross validation - leave 100 out)
+  %   \end{itemize}
 
@@
       (at this timepoint). Out of this data we got 51 337 distinct free-living species and 47 332 
-      distinct parasite species $\rightarrow$ unknown nodes 2194794 ($\approx 95.7\%$). \\
+      distinct parasite species $\rightarrow$ unknown nodes 2194794 ($\approx 95.7~\%$). \\
     We found also $57,352$ (not distinct) source species and $809,993$ (not distinct) target
       species without OTT ids. Since we currently use only OTT ids, we could not use this information. \\
-    \todo{With this only $\approx 4.3\%$ information in our leaf nodes are ...} \\
+    \todo{With this only $\approx 4.3~\%$ information in our leaf nodes are ...} \\
     We also compared different models in terms of their BICs (Table: \ref{table:BIC unknown information}). 
@@
         the birds are some breeding parasites (brood parasitism) like the cuckoo and clepto-parasites as 
-        the skuas \cite{Rothschild1957}. The algorithm reflects this. We started with 99.83\% 
-        free-living species and predicted 99.94\% species as parasites \todo{(inklusive all known nodes)}. 
-        Only 0.06\% were predicted as parasites. \\
+        the skuas \cite{Rothschild1957}. The algorithm reflects this. We started with 99.83~\% 
+        free-living species and predicted 99.94~\% species as parasites \todo{(inklusive all known nodes)}. 
+        Only 0.06~\% were predicted as parasites. \\
       \todo{We found the cuckoo and some skuas...?} \\
       Same observation but with less free-livings is the Apicomplexa Phylum. Here we have only a few 
-        free-livings \todo{ref einfügen}. And as we see, we had good start data and predicted 00.95\% as 
+        free-livings \todo{ref einfügen}. And as we see, we had good start data and predicted 00.95~\% as 
         parasites. \\
       For the Platyhelminthes the literature says that there are mostly all Platyhelminthes parasites
-        \todo{ref einfügen}. But at the end we predicted 4.18\% as free-living. The class Seriata is the 
+        \todo{ref einfügen}. But at the end we predicted 4.18~\% as free-living. The class Seriata is the 
         reason for the most of free-livings in this phylum. These are partly free-living flatworms, so 
@@
       With the Nematoda it looks very different. In the Nematoda its much worse. Most Nematoda are 
-        free-living, but we found only 2.63\% of them. Blaxter et al. speaks of at least seven 
+        free-living, but we found only 2.63~\% of them. Blaxter et al. speaks of at least seven 
         independently arosed parasitism \cite{Blaxter1998}. In a recent article Blaxter identifies 18 
@@
         The problem at this point, however, is obvious: The parasites have been much more studied and 
-        thus we start with only 0.63\% free-living species. Against such a shifted data situation, the 
+        thus we start with only 0.63~\% free-living species. Against such a shifted data situation, the 
         algorithm is almost powerless. And yet the percentage has increased.
@@
               & 91734 & 0 & 0 & 0 & 0 & 51 \\
-            & & 99.83\% & 0.49\%
-              & 99.94\% & & & & & 0.06\% \\ \hline
+            & & 99.83~\% & 0.49~\%
+              & 99.94~\% & & & & & 0.06~\% \\ \hline
             Nematoda & 30127 & 21 & 3289 
               & 791 & 0 & 1017 & 0 & 0 & 28319 \\
-            & & 0.63\% & 99.37\%
-              & 2.63\% & & 3.38\% & & & 94\% \\ \hline
+            & & 0.63~\% & 99.37~\%
+              & 2.63~\% & & 3.38~\% & & & 94~\% \\ \hline
             Platyhelminthes & 22683 & 7 & 7086 
               & 949 & 0 & 151 & 0 & 0 & 21583 \\
-            & & 0.1\% & 99.9\%
-              & 4.18\% & & 0.67\% & & & 95.15\% \\ \hline
+            & & 0.1~\% & 99.9~\%
+              & 4.18~\% & & 0.67~\% & & & 95.15~\% \\ \hline
             Apicomplexa & 1863 & 1 & 255 
               & 1 & 0 & 0 & 0 & 0 & 1862 \\
-            & & 0.39\% & 99.61\%
-              & 0.05\% & & & & & 99.95\% \\
+            & & 0.39~\% & 99.61~\%
+              & 0.05~\% & & & & & 99.95~\% \\
             \hline \hline
@@
               & 1099509 & 1313 & 22478 & 4176 & 1665 & 70223 \\
-            & & 62.93\% & 37.07\%
-              & 91.7\% & 0.11\% & 1.87\% & 0.35\% & 0.14\% & 5.86\% \\
+            & & 62.93~\% & 37.07~\%
+              & 91.7~\% & 0.11~\% & 1.87~\% & 0.35~\% & 0.14~\% & 5.86~\% \\
             \hline
@@
         out of the input data to see how stable our result is. Of these 10,000 nodes, 9,238 were unique. 
-        Of that, we predicted 9060 ($\approx 98.17\%$) correctly and 169 ($\approx 1.82\%$) wrongly, with 
+        Of that, we predicted 9060 ($\approx 98.17~\%$) correctly and 169 ($\approx 1.82~\%$) wrongly, with 
         duplicate draws always having the same prediction. \\
@@
 
+  How to extend Fitch for multifunction?:
+  \begin{figure}
+    \centering
+      \includegraphics[width=1\textwidth]{Figures/Fitch2.png}
+  \end{figure}
+
 \end{document}

### 2018-03-15 code/simulation/main.py

@@ -26,9 +26,10 @@ CURRENT_TIME = datetime.datetime.now().replace(microsecond=0)
 
 # values for simulation:
 number_leafnodes = int(sys.argv[1])
-number_trees = int(sys.argv[2])         # number of simulated trees
-percentage_parasites = float(sys.argv[3]) # between 0 and 1
-percentage_unknown = float(sys.argv[4])   # between 0 and 1
+number_trees = int(sys.argv[2])                 # number of simulated trees
+percentage_parasites = float(sys.argv[3])       # between 0 and 1
+percentage_unknown = float(sys.argv[4])         # between 0 and 1
+percentage_multifurcation = float(sys.argv[5])  # between 0 and 1
 
 def main():
     """Main method"""
@@ -43,14 +44,15 @@ def main():
     print("Simulate", colored(number_trees, 'blue'), "random trees with", 
         colored(number_leafnodes, 'blue'), "leafnodes", 
         colored(percentage_parasites*100, 'blue'), "% parasites and",
-        colored(percentage_unknown*100, 'blue'), "% unknown leafnodes.")
+        colored(percentage_unknown*100, 'blue'), "% unknown leafnodes and",
+        colored(percentage_multifurcation*100, 'blue'), "% multifurcation of internal nodes.")
     beta_distribution_parameters = decide_for_beta_distribution_parameters(percentage_parasites)
     print(beta_distribution_parameters)
     diffs = [["Fitch", "My", "Sankoff"]]
     for i in range(1, number_trees + 1):
         print("Tree", colored(i, 'red'))
         print(colored("---------------- get random tree ----------------", "green"))
-        result = buildTree.get_random_tagged_tree(number_leafnodes, percentage_parasites, percentage_unknown, beta_distribution_parameters)
+        result = buildTree.get_random_tagged_tree(number_leafnodes, percentage_parasites, percentage_unknown, percentage_multifurcation, beta_distribution_parameters)
         current_tree = result[0]
         nodelist = result[1]
         # CURRENT_TIME = print_time(CURRENT_TIME)
@@ -85,7 +87,7 @@ def main():
     s_dif = round(s_dif / number_trees, 2)
 
     row = [percentage_unknown, f_dif, m_dif, s_dif]
-    csv_title = "evaluation/" + str(int(percentage_parasites*100)) + "-unknown_plot.csv" 
[…]

### 2018-03-15 code/simulation/non_binary_simulation/buildTree.py

@@ -9,14 +9,19 @@ from Bio import Phylo
 
 # global variable:
 permitted_deviation = 0.02 # 2%
+percentage_multifurcation = 0.5
 
-def get_random_tagged_tree(number_leafnodes, percentage_parasites, percentage_unknown, beta_distribution_parameters):
+def get_random_tagged_tree(number_leafnodes, percentage_parasites, percentage_unknown, p_multifurcation, beta_distribution_parameters):
     """build a random binary tree fully tagged with FL and P"""
     # Arguments:
     #   number_leafnodes                - needed for randomized function
-    #   percentage_unknown              - proportion of unknown leafnodes
     #   percentage_parasites
+    #   percentage_unknown              - proportion of unknown leafnodes
+    #   percentage_multifurcation
     #   beta_distribution_parameters    - [A_FL, B_FL, A_P, B_P]
+
+    global percentage_multifurcation
+    percentage_multifurcation = p_multifurcation
 
     START_TIME = datetime.datetime.now().replace(microsecond=0)
     CURRENT_TIME = datetime.datetime.now().replace(microsecond=0)
@@ -119,17 +124,18 @@ def tag_tree(subtree, nodelist, father_tag, leaf_distr, percentage_parasites, pe
     return [subtree, nodelist, leaf_distr, depths]
 
 def get_non_binary_tree(subtree, nodelist):
+    global percentage_multifurcation
     i = 0
     while i != len(subtree.clades):
         if subtree.clades[i].is_terminal():                 # is leave node?
             i += 1
         else:
             element = find_element_in_nodelist(subtree.clades[i].name, nodelist)
-            limit = get_limit(element[1][2])
+            # limit = get_limit(element[1][2])
             # print('i=', i, 'len=', len(subtree.clades))
             new_random = uniform(0, 1)                      # choose if we want to delete ourselve
             # print(new_random, ' < ', limit)
-            if new_random < limit:                          # or new_random < 0.9:
+            if new_random < percentage_multifurcation:                          # or new_random < 0.9:
                 # print('delete me!')
                 subtree.clades += subtree.clades[i].clades  # add children
                 del subtree.clades[i]                       # delete internal node
@@ -143,9 +149,9 @@ def get_non_binary_tree(subtree, nodelist):
             
     return
 
-def get_limit(depth):
-    limit = 1 - 1/((depth+3)/4)
-    if limit < 0.1:
[…]

### 2018-03-15 code/simulation/non_binary_simulation/parsimony/My_MP.py

@@ -1,20 +1,20 @@
 from copy import deepcopy
 
-from utilities import Helpers
+from code.utilities.Helpers import find_element_in_nodelist
 
 def my_parsimony(tree_clade, nodelist):
     """mean based parsimony"""
     # down:
     parsimony_down(tree_clade, nodelist)
     # up:
-    parent = Helpers.find_element_in_nodelist(tree_clade.name, nodelist)
+    parent = find_element_in_nodelist(tree_clade.name, nodelist)
     children = []
     for clade in tree_clade.clades:
-        child = Helpers.find_element_in_nodelist(clade.name, nodelist)
+        child = find_element_in_nodelist(clade.name, nodelist)
         children.append(child)
     for i in range(0, len(tree_clade.clades)):
         clade = tree_clade.clades[i]
-        child = Helpers.find_element_in_nodelist(clade.name, nodelist)
+        child = find_element_in_nodelist(clade.name, nodelist)
         sublist = deepcopy(children)
         del sublist[i]
         parsimony_up(clade, nodelist, parent, sublist)
@@ -30,7 +30,7 @@ def parsimony_down(subtree, nodelist):
     #   nodelist    - [id, depth, originaltag, finaltag, calc[taglist]]
     mean = 0
     for clade in subtree.clades:
-        child = Helpers.find_element_in_nodelist(clade.name, nodelist)
+        child = find_element_in_nodelist(clade.name, nodelist)
         # if child is not tagged, first tag it:
         if child[4] == []:
             parsimony_down(clade, nodelist)
@@ -41,7 +41,7 @@ def parsimony_down(subtree, nodelist):
             else:
                 child[4][0] = child[4][0][0]
         mean = mean + child[4][0]     # else: +0 for 'P'
-    element = Helpers.find_element_in_nodelist(subtree.name, nodelist)
+    element = find_element_in_nodelist(subtree.name, nodelist)
     # calculate and add mean
     mean = mean / len(subtree.clades)
     element[4].append(mean)
@@ -61,7 +61,7 @@ def parsimony_up(subtree, nodelist, parent, siblings):
     for sibling in siblings:
         siblings_tags += sibling[4]
 
-    element = Helpers.find_element_in_nodelist(subtree.name, nodelist)
+    element = find_element_in_nodelist(subtree.name, nodelist)
     # calculate and add mean
     mean = sum(siblings_tags) / len(siblings_tags)
     element[4].append(mean)
[…]

### 2018-03-15 code/simulation/non_binary_simulation/parsimony/Sankoff_MP.py

@@ -3,7 +3,7 @@
 import rpy2.robjects
 from Bio import Phylo
 
-from utilities import Helpers
+from code.utilities.Helpers import find_element_in_nodelist
 
 
 def sankoff_parsimony(tree, nodelist):
@@ -37,13 +37,13 @@ def sankoff_parsimony(tree, nodelist):
     k = 0
     for i in range(2*l, 3*l):
         if j < number_of_tips[0]:
-            element = Helpers.find_element_in_nodelist(leaf_nodes[j], nodelist)
+            element = find_element_in_nodelist(leaf_nodes[j], nodelist)
             if element[3] == '':    # if unknown
                 # set finaltag:
                 element[3] = likelihoods[i]
             j += 1
         else:
-            element = Helpers.find_element_in_nodelist(internal_nodes[k], nodelist)
+            element = find_element_in_nodelist(internal_nodes[k], nodelist)
             # set finaltag:
             element[3] = likelihoods[i]
             k += 1
@@ -56,7 +56,7 @@ def prepare_tree(subtree, nodelist):
     #                   0   1       2           3           4
     #   nodelist    - [id, depth, originaltag, finaltag, calc[taglist]]
     if subtree.is_terminal():
-        element = Helpers.find_element_in_nodelist(subtree.name, nodelist)
+        element = find_element_in_nodelist(subtree.name, nodelist)
         if len(element[4][0]) > 1:
             subtree.name = ''
         else:

### 2018-03-15 code/utilities/Drawings.py

@@ -1,12 +1,13 @@
 """functions just for nice figures"""
-from utilities import Helpers
+from code.utilities.Helpers import find_element_in_nodelist
+
 
 def tag_names(subtree, nodelist, tag_id):
     """tag all nodes"""
     # Arguments:
     #   subtree
     #   nodelist      - [id, originaltag, finaltag, calc[taglist]]
-    element = Helpers.find_element_in_nodelist(subtree.name, nodelist)
+    element = find_element_in_nodelist(subtree.name, nodelist)
     subtree.name = element[tag_id]
     for clade in subtree.clades:
         tag_names(clade, nodelist, tag_id)
@@ -18,7 +19,7 @@ def tag_leaf_names(subtree, nodelist):
     #   subtree
     #   nodelist      - [id, originaltag, finaltag, calc[taglist]]
     if subtree.is_terminal():
-        element = Helpers.find_element_in_nodelist(subtree.name, nodelist)
+        element = find_element_in_nodelist(subtree.name, nodelist)
         subtree.name = element[1]
     else:
         subtree.name = ''

### 2018-03-15 code/utilities/Fitch_Versions.py

@@ -1,6 +1,6 @@
 from copy import deepcopy
 
-from Helpers import find_element_in_nodelist, get_intersect_or_union
+from code.utilities.Helpers import find_element_in_nodelist, get_intersect_or_union
 
 # Version 1:
 # use only first tag of parent, and every sibling

### 2018-03-15 code/utilities/castor_parsimony_simulation.R

@@ -12,12 +12,13 @@ path_tagged_tree <- "code/bufferfiles/simulated_tagged_tree.tre"
 tagged_tree <- read.tree(path_tagged_tree)
 
 # ---- get the tagged tips of the tree ----
-state_ids <- tree$tip.label
+ state_ids <- tree$tip.label
 states <- tagged_tree$tip.label
 # print("tip states:")
 # print(states)
 # print(state_ids)
-number_of_tips <- length(state_ids)
+
+## number_of_tips <- length(state_ids)
 internal_nodes <- tree$node.label
 
 # ---- map them to numbers (NA for unknown states) ----

### 2018-03-15 code/simulation/main_fitch.py
update fitch version simulation

@@ -23,9 +23,10 @@ CURRENT_TIME = datetime.datetime.now().replace(microsecond=0)
 
 # values for simulation:
 number_leafnodes = int(sys.argv[1])
-number_trees = int(sys.argv[2])         # number of simulated trees
-percentage_parasites = float(sys.argv[3]) # between 0 and 1
-percentage_unknown = float(sys.argv[4])   # between 0 and 1
+number_trees = int(sys.argv[2])                 # number of simulated trees
+percentage_parasites = float(sys.argv[3])       # between 0 and 1
+percentage_unknown = float(sys.argv[4])         # between 0 and 1
+percentage_multifurcation = float(sys.argv[5])  # between 0 and 1
 
 def main():
     """Main method"""
@@ -47,7 +48,7 @@ def main():
     for i in range(1, number_trees + 1):
         print("Tree", colored(i, 'red'))
         print(colored("---------------- get random tree ----------------", "green"))
-        result = buildTree.get_random_tagged_tree(number_leafnodes, percentage_parasites, percentage_unknown, beta_distribution_parameters)
+        result = buildTree.get_random_tagged_tree(number_leafnodes, percentage_parasites, percentage_unknown, percentage_multifurcation, beta_distribution_parameters)
         current_tree = result[0]
         nodelist = result[1]
         # CURRENT_TIME = print_time(CURRENT_TIME)
@@ -77,7 +78,7 @@ def main():
     f_dif4 = round(f_dif4 / number_trees, 2)
 
     row = [percentage_unknown, f_dif1, f_dif2, f_dif3, f_dif4]
-    csv_title = "evaluation/" + str(int(percentage_parasites*100)) + "-fitch-unknown_plot.csv" 
+    csv_title = "data/simulation/" + str(int(percentage_parasites*100)) + "-fitch-unknown_plot.csv" 
     fp = open(csv_title, 'a')
     writer = csv.writer(fp)
     writer.writerow((row)) 

### 2018-03-16 code/simulation/get_plots.py
save buffered trees in different files

@@ -1,49 +1,51 @@
 import matplotlib.lines as mlines
 import matplotlib.patches as mpatches
 import matplotlib.pyplot as plt
-import numpy as np
-from numpy import random
+from numpy import genfromtxt
+from random import betavariate
+
 
 # global variables:
 PLOT_NUMBER = 1
 ROWS = 5
-COLS = 2
+COLS = 3
 
 def main():
     global PLOT_NUMBER
-    f, axs = plt.subplots(ROWS, COLS, figsize=(7,10))
+    f, axs = plt.subplots(ROWS, COLS, figsize=(9,10))
     plt.suptitle('Influence of unknown data to prediction', fontsize=12, y=1, fontweight='bold')
     plt.NullFormatter()
 
     for pp in [10, 20, 30, 40, 50]: 
         plot_hist(pp)
-        plot_data(pp)
+        plot_data_unknown(pp)
+        plot_data_multifurc(pp)
 
     plt.tight_layout()
     plt.show()
 
-    PLOT_NUMBER = 1
-    f, axs = plt.subplots(ROWS, COLS, figsize=(7, 10))
-    plt.suptitle('Influence of unknown data to prediction', fontsize=12, y=1)
+    # PLOT_NUMBER = 1
+    # f, axs = plt.subplots(ROWS, COLS, figsize=(7, 10))
+    # plt.suptitle('Influence of unknown data to prediction', fontsize=12, y=1)
 
-    plot_hist(40)
-    plot_data(40)
+    # plot_hist(40)
+    # plot_data(40)
     
-    plot_hist('40-old')
-    plot_data('40-old')
+    # plot_hist('40-old')
+    # plot_data('40-old')
 
-    plt.tight_layout()
-    plt.show()
+    # plt.tight_layout()
+    # plt.show()
 
     PLOT_NUMBER = 1
-    f, axs = plt.subplots(ROWS, COLS, figsize=(7, 10))
+    f, axs = plt.subplots(ROWS, 1, figsize=(4, 10))
     plt.suptitle('Fitch Versions and Unknown Data', fontsize=12, y=1)
 
-    filepath = 'evaluation/30-fitch-unknown_plot.csv'
+    filepath = 'data/simulation/30-fitch-unknown_plot.csv'
     plot_fitch_versions(filepath)
-    filepath = 'evaluation/40-fitch-unknown_plot.csv'
+    filepath = 'data/simulation/40-fitch-unknown_plot.csv'
     plot_fitch_versions(filepath)
[…]

### 2018-03-16 code/simulation/main.py

@@ -11,7 +11,7 @@ from code.simulation.non_binary_simulation.parsimony.Sankoff_MP import \
 from code.utilities.Drawings import tag_leaf_names, tag_names
 from code.utilities.Helpers import print_time
 from copy import deepcopy
-from pprint import pprint
+# from pprint import pprint
 from time import gmtime, strftime
 
 from Bio import Phylo
@@ -46,7 +46,7 @@ def main():
         colored(percentage_parasites*100, 'blue'), "% parasites and",
         colored(percentage_unknown*100, 'blue'), "% unknown leafnodes and",
         colored(percentage_multifurcation*100, 'blue'), "% multifurcation of internal nodes.")
-    beta_distribution_parameters = decide_for_beta_distribution_parameters(percentage_parasites)
+    beta_distribution_parameters = decide_for_beta_distribution_parameters()
     print(beta_distribution_parameters)
     diffs = [["Fitch", "My", "Sankoff"]]
     for i in range(1, number_trees + 1):
@@ -87,7 +87,7 @@ def main():
     s_dif = round(s_dif / number_trees, 2)
 
     row = [percentage_unknown, percentage_multifurcation, f_dif, m_dif, s_dif]
-    csv_title = "data/simulation/" + str(int(percentage_parasites*100)) + "-unknown_" + str(int(percentage_multifurcation*100)) + "-multifurcation.csv" 
+    csv_title = "data/simulation/" + str(int(percentage_parasites*100)) + "-unknown-multifurcation.csv"
     fp = open(csv_title, 'a')
     writer = csv.writer(fp)
     writer.writerow((row)) 
@@ -134,7 +134,8 @@ def run_parsimony_algorithms(current_tree, nodelist):
     print(colored("--------------------------------", "green"))
     return differences
 
-def decide_for_beta_distribution_parameters(percentage_parasites):
+def decide_for_beta_distribution_parameters():
+    global percentage_parasites
                                 # [A_FL, B_FL, A_P, B_P]
     beta_distribution_parameters = [7, 3.5, 3.5, 7]   # 40 P - 60 FL
 

### 2018-03-16 code/simulation/main_fitch.py

@@ -79,7 +79,7 @@ def main():
     f_dif4 = round(f_dif4 / number_trees, 2)
 
     row = [percentage_unknown, percentage_multifurcation, f_dif1, f_dif2, f_dif3, f_dif4]
-    csv_title = "data/simulation/fitch_" + str(int(percentage_parasites*100)) + "-unknown_" + str(int(percentage_multifurcation*100)) + "-multifurcation.csv"
+    csv_title = "data/simulation/fitch_" + str(int(percentage_parasites*100)) + "-unknown-multifurcation.csv"
     fp = open(csv_title, 'a')
     writer = csv.writer(fp)
     writer.writerow((row)) 

### 2018-03-16 code/simulation/non_binary_simulation/parsimony/Sankoff_MP.py

@@ -4,17 +4,19 @@ import rpy2.robjects
 from Bio import Phylo
 
 from code.utilities.Helpers import find_element_in_nodelist
-
+from random import randint
 
 def sankoff_parsimony(tree, nodelist):
     """Using rpy2 for forwarding to R code"""
 
     # ---- cache tree for R script ---
+    random_name = str(randint(0, 1000))
+    path_simulated_tree = 'code/bufferfiles/simulated_tree' + random_name + '.tre'
+    path_tagged_tree = 'code/bufferfiles/tagged_tree' + random_name + '.tre'
 
-    Phylo.write(tree, 'code/bufferfiles/simulated_tree.tre', 'newick')
-
+    Phylo.write(tree, path_simulated_tree , 'newick')
     prepare_tree(tree.clade, nodelist)
-    Phylo.write(tree, 'code/bufferfiles/tagged_tree.tre', 'newick')
+    Phylo.write(tree, path_tagged_tree, 'newick')
     
     # -------- R code --------
     
@@ -23,7 +25,9 @@ def sankoff_parsimony(tree, nodelist):
     code = ''.join(f.readlines())
     print("---------------- prepare R script ----------------")
     code_Array = code.split("data/subtree/Eukaryota.tre")
-    code = "code/bufferfiles/simulated_tree.tre".join(code_Array)
+    code = path_simulated_tree.join(code_Array)
+    code_Array = code.split("code/bufferfiles/tagged_tree.tre")
+    code = path_tagged_tree.join(code_Array)
 
     result = rpy2.robjects.r(code)
     # assume that...

### 2018-03-16 Paper - Latex/Paper - Skizze - v3.tex
Paper - rearrange subsections; add some new data for the simulation

@@
     %---------------------------------------------------------------------------------------------------
-    \subsection{Multifurcation}
-      We have a very high multifurcation rate (see results section \pageref{sec:ResultsMultifurcation}).
-      Therefore, the impact of multifurcations on our research question has been investigated. \\
-      Generalized Linear Models with poisson regression were compared according to their residuals and 
-      BIC. \\
-      \anmerkungstext{Nested models were compared using likelihood ratio tests, models using different 
-        predictors were compared according to their deviance and AIC. (Emanuel)} \\
-      \todo{Einfluss auf die Vorhersage des Castor und Fitch Algorithmus (Simulation)}
+    \subsection{Missing information}
+
+      A binary tree with $n$ leaf nodes has $n-1$ internal nodes. The present Eukaryota tree of OTL has 
+        2,293,463 leaf nodes and only 41,974 internal nodes, that is:
+      $$100-\frac{100}{(2293463-1) \times 41974} \approx 98.16 \%$$
+        missing internal nodes. \\
+
+      % \anmerkungstext{Nested models were compared using likelihood ratio tests, models using different 
+      %   predictors were compared according to their deviance and AIC. (Emanuel)} \\
+
+      For the present Eukaryota tree with 2,293,463 leaf nodes, 34,869 free-livings and 25,962 parasites 
+        are found, which are
+        $$100-\frac{100}{2293463 \times (34860+25962)} \approx 97.34 \%$$
+        unknown states of leaf nodes. \\
+
+      In the simulation, the influence of the multifurcations and missing data in leaf nodes on the 
+        predictive accuracy of the ancestral state reconstruction algorithms is tested. \\
+      For the real data, generalized linear models are compared with poisson respectively binomial 
+        regression according to their residuals and BICs.
 
@@
       As previously explained, some divisions in the tree are not known, so the real tree is not binary.
-        We simulate this multifurcation of the tree by \todo{...}.
-
-      On the one hand, the strength of multifunctionation plays a role, as does the distribution. 
-        Modeling was done as explained in \todo{sec x}.
-
-      \todo{bisher ohne Begründung:!!!}
-      we decided to use a $\frac{1}{x}$ distribution, where x is the depth of a node. This means, how 
-      deaper we are, how less information we have. \\
-      We traverse through the tree and pick a random number between 0 and 1. If random number is smaller 
-        as our limit ($\frac{1}{x}$), than we forget the node and hang every child to the father node of 
-        the current node. \\
-      \anmerkung{poisson process $\rightarrow$ fit that distribution, include depth as a predictor, see if significant (Emanuel)}
-      \begin{lstlisting}[gobble=6]
-        def get_non_binary_tree(subtree, nodelist):
-          i = 0
-          while i != len(subtree.clades):
-            if subtree.clades[i].is_terminal():             # is leaf node?
-              i += 1
-            else:
-              element = Helpers.find_element_in_nodelist(subtree.clades[i].name, nodelist)
-              limit = get_limit(element[1])
-              new_random = random.uniform()                 # choose if we want to delete ourselve
-              if new_random < limit:                        # or new_random < 0.9:
-                subtree.clades += subtree.clades[i].clades  # add children
-                del subtree.clades[i]                       # delete internal node
-              else:                                         # if we don't deleted ourselve go on with children
-                get_non_binary_tree(subtree.clades[i], nodelist)  # otherwise the children are in the current clade array
-                i += 1
-          return
-
-          def get_limit(depth):
-            limit = 1 - 1 / ((depth + 3) / 4)
-            if limit < 0.1:
-              limit = 0.1
-            return limit
-      \end{lstlisting}
-      Wir lassen das Limit nicht beliebig klein werden, sondern beschränken es auf 0.1. \\
-
-      With this loss of information the reconstruction can start.
+      This multifurcation was simulated by an equally distributed percentage of forgotten internal nodes.
 
@@
           node percentage. \\
-        At 90~\% unknown nodes, version 1 was 89.67~\%, version 2 was 89.67~\%, version 3 was 90.72~\%, 
-          and version 4 was 90.74~\% correct. Therefore, only version 4 was used for all further 
-          simulations.
+        At 90~\% unknown nodes and 90~\% of multifurcation of the internal nodes, version 1 was 89.26~\%, 
+          version 2 was 89.26~\%, version 3 was 89.35~\%, and version 4 was 89.31~\% correct. Therefore, 
+          only version 3 was used for all further simulations.
 
@@
   \section{Metadata analysis}
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{Taxa}
-      The investigation of the taxonomy revealed that our tree has three kingdoms: Chloroplastida, 
-        Metazoa, Fungi, 53 phyla, 195 classes and 924 orders. \\
-      Since the analysis of the tree is not part of this work, it should be mentioned here that, 
-        according to recent findings, this is not complete and we lack some taxa in every rank. For 
-        example, Hans says that one distinguishes between seven and nine kingdoms 
-        \cite{CavalierSmith1981}. \\
-      In section \pageref{subsec:listPhyla} of the appendix you can find a list of all phyla.
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \section{Multifurcation}\label{sec:ResultsMultifurcation}
-      One property of the tree is its ridge of multifurcation. A complete phylogenetic tree would be 
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \subsection{Missing information}
+      As previously presented, we have two types of missing information: unknown states of leaf nodes 
+        and multifurcation. \\
+
+      We examined the ridge of multifurcation of the tree. A complete phylogenetic tree would be 
         binary, which means the number of leaf nodes is closely to the number of internal nodes. But 
@@
       phylogenetic tree. \\
-      As you can see, we are very far from a binary tree.
+      As you can see, we are very far from a binary tree. \\
+
+      Some subtrees have been examined, these have the following percentages of missing information: See 
+        table \ref{table:percentage loss information subtrees}.
+
+      \begin{table} [h]
+        \begin{center}
+          \begin{tabular}{ |l|r|r||r|r|r| }
+            \hline
+            Domain  & \% unknown states & \% multifurcation \\ 
+            / Kingdom  & (missing state information & (missing \\
+            / Phylum / Class & of leaf nodes) & internal nodes) \\
+            \hline \hline
+            Eukaryota       & 97.34~\%  & 98.16~\% \\
+            \hline \hline
+            Metazoa         & 96.44~\%  & 87.93~\% \\ \hline
+            Fungi           & 98.87~\%  & 96.97~\% \\ \hline
+            Chloroplastida  & 99.14~\%  & 89.46~\% \\
+            \hline \hline            
+            Arthropoda      & 97.49~\%  & 89.95~\% \\ \hline
+            Apicomplexa     & 86.26~\%  & 87.16~\% \\ \hline
+            Nematoda        & 89.01~\%  & 88.59~\% \\ \hline
+            Chordata        & 88.59~\%  & \cellcolor{green!50}66.49~\% \\ \hline
+            Platyhelminthes & \cellcolor{green!50}68.73~\%  & 80.34~\% \\
+            \hline \hline            
+            Insecta         & 97.11~\%  & 90.78~\% \\
+            \hline  
+          \end{tabular}
+        \end{center}
+        \caption{Examination of subtrees regarding missing information}
+        \label{table:percentage loss information subtrees} 
+      \end{table}
 
@@
       %---------------------------------------------------------------------------------------------------
-      %---------------------------------------------------------------------------------------------------
-      \subsection{Poisson regression}
-        glm (generalized linear model) analysis: \\
-
+      \subsubsection{Taxa}
+        The investigation of the taxonomy revealed that our tree has three kingdoms: Chloroplastida, 
+          Metazoa, Fungi, 53 phyla, 195 classes and 924 orders. \\
+        Since the analysis of the tree is not part of this work, it should be mentioned here that, 
+          according to recent findings, this is not complete and we lack some taxa in every rank. For 
+          example, Cavalier-Smith says that one distinguishes between seven and nine kingdoms 
+          \cite{CavalierSmith1981}. \\
+        In section \pageref{subsec:listPhyla} of the appendix you can find a list of all phyla.
+
+      %---------------------------------------------------------------------------------------------------
+      \subsubsection{Poisson regression of the multifurcation}
+        % glm (generalized linear model) analysis: \\
         The intercept is $2.821 > 0$ $\Rightarrow$ there is a multifunction.
@@
       %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  \section{Unknown leaf nodes}
+      \subsubsection{Binomial regression of the unknown state information}
+
         Next to the problem of the multifurcation of the tree is the less of data we have for the species.
@@
               \hline \hline
-            multifurc $\sim$ taxa & 545799 & \cellcolor{green!10}500004 & \cellcolor{green!50}485121 \\
-            \hline
-            multifurc $\sim$ taxa + depth & 544862 & \cellcolor{green!30}493808 & \cellcolor{green!50}481869 & 478851 \\
-            \hline
-            multifurc $\sim$ taxa * depth & 544179 & \cellcolor{green!50}489845 & \cellcolor{green!50}481494 \\
+              multifurc $\sim$ taxa & \cellcolor{green!15}545799 & \cellcolor{green!35}500004 & \cellcolor{green!45}485121 & XXXXX \\
+              \hline
+              multifurc $\sim$ taxa + depth & \cellcolor{green!15}544862 & \cellcolor{green!40}493808 & \cellcolor{green!45}481869 & \cellcolor{green!50}478851 \\
+              \hline
+              multifurc $\sim$ taxa * depth & \cellcolor{green!15}544179 & \cellcolor{green!45}489845 & \cellcolor{green!45}481494 & \cellcolor{green!50}478188 \\
               \hline
@@
 
-    \begin{figure}
+    \begin{figure}[h!]
       \centering
-      \includegraphics[trim = 0mm 0mm 0mm 50mm, clip,width=0.9\textwidth]{Figures/simulation_evaluation_1.png}
+      \includegraphics[trim = 0mm 0mm 0mm 0mm, clip,width=0.8\textwidth]{Figures/simulation_evaluation_1.png}
       \caption{Influence of unknown data to prediction}
@@
 
-      \todo{Castor replaces originaltags with finaltags. There are 82 originaltags != finaltag.} \\ \\
+      \todo{Castor replaces originaltags with finaltags. There are 82 originaltags != finaltag.} \\
 
@@
       Since GloBI is not perfect, all examples contain a few bugs.
+
+      \todo{\ref{table:table:percentage loss information subtrees}} \\
+
       As known the Chordata are full of free-living species and there are only a few parasites. Among 
@@
 \chapter{Discussion}
-  Wie gut ist der randomisiert erstellte Baum? \\
-  Wie gut kommt unsere Simulation an die echte Datenlage heran. \\
+
   Fehlerqoute der Daten an sich? \\
@@
   Information. \\
-  Simulation von subtrees \\
   Welche Teile des Baumes sind gut, an welchen muss noch viel geforscht werden. \\
   Wieviele Origins haben wir gefunden, was bedeutet diese Zahl? \\
-
-  Parameter der Simulation:
+  Es gibt noch ungenutze information in GloBI.
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Simulation}
+    For fixed calculations we assume a distribution of 60\% free-living to 40\% parasites, 95\% 
+      missing data and a multifuration rate of 95\%.
+    How well does our simulation approach the real data situation? \\
+    There are some points to discuss:
     \begin{itemize}
-    \item Wie ist die Verteilung der vergessenen internen Knoten? Zum Wurzelknoten hin mehr vergessen?
-    \item Wie sehen die übergangswahrscheinlichkeiten aus von P$\rightarrow$FL und andersherum?
-    \item Verteilung Parasiten zu Freilebend zu keine Information
+      \item How close is the randomized binary tree to a true phylogeny?
+      \item The distribution of parasites to free-ranging species is a pure assumption. From different 
+        sources about 40\% parasites are estimated, are these also beta-distributed?
+      \item How well do the transition probabilities match parasitism? Depending on the type of 
+        parasitism, this will certainly look different. In addition, it can be assumed that the 
+        probability for losses is lower than for origins.
+      \item The equal distribution of the multifurcation is a blank assumption. It is very likely to 
+        be higher towards the root node because there is less information back in time. On the other 
+        hand, there are many studies that have studied various species without considering phylogeny. 
+        Which also creates a high number of children of a node directly at the leaf nodes.
     \end{itemize}
-
-  Selecting of the 'right'  / best Distribution
+    In order to be able to observe these problems, we have programmed our simulation according to the 
+      parameters. This allowed us to estimate the influence of some of these parameters.
 
@@
 
-%---------------------------------------------------------------------------------------------------
-%---------------------------------------------------------------------------------------------------
-%---------------------------------------------------------------------------------------------------
-\chapter{Komplett aussortierte Tabellen etc}
-
-  \begin{figure}
-    \centering
-    \includegraphics[trim = 0mm 0mm 0mm 0mm, clip,width=0.95\textwidth]{Figures/Kreuztabelle_Residuals.JPG}
-    \caption{Crosstable of Residual values}
-  \end{figure}
-
-  \begin{figure}
-    \centering
-    \includegraphics[trim = 0mm 0mm 0mm 0mm, clip,width=0.95\textwidth]{Figures/Kreuztabelle_BIC.JPG}
-    \caption{Crosstable of BIC values}
-  \end{figure}
-
-  How to extend Fitch for multifunction?:
-  \begin{figure}
-    \centering
-      \includegraphics[width=1\textwidth]{Figures/Fitch2.png}
-  \end{figure}
-
 \end{document}

### 2018-03-16 code/metadata/analyse_input.R

@@ -52,26 +52,177 @@ print('----------------------- extendedInner.taxa$rank -------------------------
 extendedInner.taxa <- as.data.frame(extendedInner.taxa)
 # table(extendedLeaf.taxa$rank)[order(table(extendedLeaf.taxa$rank))]
 print('--------------------------------------------------')
+print('--------------------------------------------------')
+print('----------------------- data of subtrees ---------------------------')
+# table(inner.taxa$kingdom)
+# table(inner.taxa$phylum)
+
+print('Fungi')
+fungi <- all.taxa[all.taxa$kingdom=="['ott352914', 'Fungi']", ]
+percentage_multifurcation = 100-(100/(sum(fungi$nr_children==0)-1) * sum(fungi$nr_children>0))
+print(
+    c('Subtree fungi has', 
+        sum(fungi$nr_children>0), 'internal nodes and', 
+        sum(fungi$nr_children==0), 'leaf nodes ->', 
+        percentage_multifurcation, '% multifurcation'))
+percentage_unknown = 100-(100/sum(fungi$nr_children==0) * (sum(fungi$originaltag==1, na.rm=T) + sum(fungi$originaltag==2, na.rm=T)))
+print(
+    c('Subtree fungi has', 
+        sum(fungi$originaltag==1, na.rm=T), 'free-livings and ', 
+        sum(fungi$originaltag==2, na.rm=T), 'parasites ->', 
+        percentage_unknown, '% unknown states'))
+print('--------------------------')
+
+print('Chloroplastida')
+chloroplastida <- all.taxa[all.taxa$kingdom=="['ott361838', 'Chloroplastida']", ]
+percentage_multifurcation = 100-(100/(sum(chloroplastida$nr_children==0)-1) * sum(chloroplastida$nr_children>0))
+print(
+    c('Subtree chloroplastida has', 
+        sum(chloroplastida$nr_children>0), 'internal nodes and', 
+        sum(chloroplastida$nr_children==0), 'leaf nodes ->', 
+        percentage_multifurcation, '% multifurcation'))
+percentage_unknown = 100-(100/sum(chloroplastida$nr_children==0) * (sum(chloroplastida$originaltag==1, na.rm=T) + sum(chloroplastida$originaltag==2, na.rm=T)))
+print(
+    c('Subtree chloroplastida has', 
+        sum(chloroplastida$originaltag==1, na.rm=T), 'free-livings and ', 
[…]

### 2018-03-16 code/simulation/get_plots.py

@@ -13,7 +13,7 @@ COLS = 3
 def main():
     global PLOT_NUMBER
     f, axs = plt.subplots(ROWS, COLS, figsize=(9,10))
-    plt.suptitle('Influence of unknown data to prediction', fontsize=12, y=1, fontweight='bold')
+    # plt.suptitle('Influence of unknown data to prediction', fontsize=12, y=1, fontweight='bold')
     plt.NullFormatter()
 
     for pp in [10, 20, 30, 40, 50]: 
@@ -135,7 +135,7 @@ def plot_data_unknown(percentage_parasites):
         label='Sankoff', linewidth=0.5, marker='.', markerfacecolor='black')
     plt.legend(loc="lower left", fontsize=9) #, scatterpoints=1, numpoints=2)
     plt.axis([0, 1, 50, 100])
-    if PLOT_NUMBER != 11:
+    if PLOT_NUMBER != 15:
         plt.xticks([])
     else:
         plt.xlabel('percentage unknown', fontsize=9)
@@ -163,7 +163,7 @@ def plot_data_multifurc(percentage_parasites):
         label='Sankoff', linewidth=0.5, marker='.', markerfacecolor='black')
     plt.legend(loc="lower left", fontsize=9) #, scatterpoints=1, numpoints=2)
     plt.axis([0, 1, 50, 100])
-    if PLOT_NUMBER != 11:
+    if PLOT_NUMBER != 16:
         plt.xticks([])
     else:
         plt.xlabel('percentage multifurcation', fontsize=9)

### 2018-03-18 Paper - Latex/Paper - Skizze - v4.tex
Paper - Results - Results of simulation

--- 2018-03-16 Paper - Latex/Paper - Skizze - v3.tex
@@
 
-    \begin{figure}[h!]
+      As presented, we compare two methods in our simulation to their prediction accuracy: Fitch and 
+        Sankoff. \\
+      We examine different parameters. In figure \ref{fig:influence of unknown data} is an overview of 
+        the results. \\
+      The first column describes the distributions of free-livings and parasites with a given threshold 
+        for the respective simulations to the right. \\
+      The middle column investigates the influence of the unknown states, the right the influence of the 
+        strength of the multifurcation. \\
+      The y-axes indicate the percentage of correctly predicted states (including known states). On the 
+        x-axis the percentage of forgotten states or missing internal nodes. \\
+      Each point corresponds to the average of one hundred simulations, each with 10,000 leaf nodes. \\
+      For the middle column we set the strength of the multifurcations to 0.95\% similar to the real 
+        data and in the right column the amount of the unknowns to 0.95\% also similar to the real data. \\
+
+      As you can see both algortithms are always over 50\% and therefore better than guessing. Moreover, 
+        they are usually close to each other, with Sankoff always makes better predictions except for 
+        equally distributed states as Fitch. \\
+      You can see that the distribution of states has a strong influence on the prediction. The more 
+        evenly distributed, the harder it is to predict. \\
+      If more than 60\% of internal nodes are missing, Fitch breaks significantly in his prediction 
+        compared to Sankoff.
+
+      \begin{figure}
         \centering
-      \includegraphics[trim = 0mm 0mm 0mm 0mm, clip,width=0.8\textwidth]{Figures/simulation_evaluation_1.png}
+        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip,width=\textwidth]{Figures/simulation_evaluation_1.png}
         \caption{Influence of unknown data to prediction}
+        \label{fig:influence of unknown data}
       \end{figure}
+
+      In the end, Sankoff is in most cases the more accurate algortihmus and was therefore used for our 
+        prediction of the real data.
 

### 2018-03-18 code/simulation/get_plots.py

@@ -109,8 +109,8 @@ def plot_hist(percentage_parasites):
     ax.get_legend().get_title().set_fontweight("bold")
     plt.axis([0, 1, 0, 8])
     # plt.ylabel('???', fontsize=9)
-    if PLOT_NUMBER != 11:
-        plt.xticks([])
+    # if PLOT_NUMBER != 11:
+    #     plt.xticks([])
     # else:
         # plt.xlabel('???', fontsize=9)
     plt.grid(True)
@@ -135,13 +135,10 @@ def plot_data_unknown(percentage_parasites):
         label='Sankoff', linewidth=0.5, marker='.', markerfacecolor='black')
     plt.legend(loc="lower left", fontsize=9) #, scatterpoints=1, numpoints=2)
     plt.axis([0, 1, 50, 100])
-    if PLOT_NUMBER != 15:
-        plt.xticks([])
-    else:
+    if PLOT_NUMBER == 15:
         plt.xlabel('percentage unknown', fontsize=9)
-    # plt.yscale('log')
-    # plt.yscale('symlog')
-    # plt.yscale('logit')
+    # else:
+    #     plt.xticks([])
     plt.grid()
     return
 
@@ -154,22 +151,22 @@ def plot_data_multifurc(percentage_parasites):
     PLOT_NUMBER += 1
 
     # plt.title(str(percentage_parasites), fontweight='bold')
-    # plt.ylabel('correct predicted', fontsize=9)
+    plt.ylabel('correct predicted', fontsize=9)
     plt.plot(data['multifurcation'], data['y_fitch'], color='g', linestyle='dashed', 
         label='Fitch', linewidth=0.5, marker='.', markerfacecolor='black')#, markersize=5)
     # plt.plot(data['unknown'], data['y_my'], color='c', linestyle='dashed', 
     #     label='My', linewidth=0.5, marker='.', markerfacecolor='black')
     plt.plot(data['multifurcation'], data['y_sankoff'], color='m', linestyle='dashed', 
         label='Sankoff', linewidth=0.5, marker='.', markerfacecolor='black')
-    plt.legend(loc="lower left", fontsize=9) #, scatterpoints=1, numpoints=2)
+    if PLOT_NUMBER < 10:
+        plt.legend(loc="lower left", fontsize=9) #, scatterpoints=1, numpoints=2)
+    else: 
[…]

### 2018-03-20 Paper - Latex/Paper - Skizze - v4.tex
Paper - Version 4
Paper - Results - Biological View

@@
             \hline \hline            
-            Arthropoda      & 97.49~\%  & 89.95~\% \\ \hline
+            % Arthropoda      & 97.49~\%  & 89.95~\% \\ \hline
             Apicomplexa     & 86.26~\%  & 87.16~\% \\ \hline
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Results of castor}
+  \section{Results of the real data analysis created with Sankoff}
 
@@
     \subsection{Biological view}
-
-      \todo{Castor replaces originaltags with finaltags. There are 82 originaltags != finaltag.} \\
-
-      We picked a few phyla to evaluate the results from the biological point of view. \\
-      Table \ref{table:phylum leaf nodes states} shows some known phyla: Chordata, Nematoda, 
-        Platyhelminthes and Apicomplexa. \\
-      Since GloBI is not perfect, all examples contain a few bugs.
-
-      \todo{\ref{table:table:percentage loss information subtrees}} \\
-
-      As known the Chordata are full of free-living species and there are only a few parasites. Among 
-        the birds are some breeding parasites (brood parasitism) like the cuckoo and clepto-parasites as 
-        the skuas \cite{Rothschild1957}. The algorithm reflects this. We started with 99.83~\% 
-        free-living species and predicted 99.94~\% species as parasites \todo{(inklusive all known nodes)}. 
-        Only 0.06~\% were predicted as parasites. \\
-      \todo{We found the cuckoo and some skuas...?} \\
-      Same observation but with less free-livings is the Apicomplexa Phylum. Here we have only a few 
-        free-livings \todo{ref einfügen}. And as we see, we had good start data and predicted 00.95~\% as 
-        parasites. \\
+      To analyze the results, we have selected some phyla (sub-trees) to evaluate our results 
+        selectively from the biological point of view: Chordata, Nematoda, Platyhelminthes and 
+        Apicomplexa. \\
+      In Table \ref{table:phylum leaf nodes states} we compare the given states with the predicted ones. \\
+      There are several factors that play a role here, and in part, crystallize in these examples. \\
+      An important factor here is that the credibility of the results with the accuracy of the input 
+        data, i. the data of GloBI, stands and falls. Errors of incorrect input data can be amplified by 
+        incorrect prediction of unknown species and can be reversed in order to improve the data 
+        situation of GloBI. \\
+      Since we look at such large trees we can not expect to know all the parasites, so we look at 
+        individual positives. Positive in the sense that the majority have the opposite state.
+
+      \begin{table}[h]
+        \begin{center}
+          \begin{tabular}{ |l|r||r|r||r|r|r|r| }
+            \hline
+            & & \multicolumn{2}{c||}{original states} & \multicolumn{4}{c|}{final states} \\
+            Phylum & \# nodes       & FL & P              & 0 (FL) & 0.3 & 0.5 & 1 (P) \\
+            \hline \hline
+            Chordata & 91785        & 10451 & 18          & 91759 & 0 & 0 & 26 \\
+            &                       & 99.83~\% & 0.49~\%  & 99.97~\% & & & 0.03~\% \\ \hline
+            Nematoda & 30127        & 21 & 3289           & 1604 & 142 & 1196 & 27185 \\
+            &                       & 0.63~\% & 99.37~\%  & 5.32~\% & 0.47~\% & 3.97~\% & 90.23~\% \\ \hline
+            Platyhelminthes & 22683 & 7 & 7086            & 175 & & & 22508 \\
+            &                       & 0.1~\% & 99.9~\%    & 0.77~\% & 0 & 0 & 99.23~\% \\ \hline
+            Apicomplexa & 1863      & 1 & 255             & 1 & 0 & 0 & 1862 \\
+            &                       & 0.39~\% & 99.61~\%  & 0.05~\% & & & 99.95~\% \\
+            % \hline \hline
+            % Phylum & \# nodes & FL & P
+            %   & 0 (FL) & 0.4 & 0.5 & 0.67 & 0.75 & 1 (P) \\
+            % Arthropoda & 1198981 & 18912 & 11141 
+            %   & 1099509 & 1313 & 22478 & 4176 & 1665 & 70223 \\
+            % & & 62.93~\% & 37.07~\%
+            %   & 91.7~\% & 0.11~\% & 1.87~\% & 0.35~\% & 0.14~\% & 5.86~\% \\
+            \hline
+          \end{tabular} 
+        \end{center}
+        \caption{Phylum (leaf nodes)}
+        \label{table:phylum leaf nodes states} 
+      \end{table}
+
+      In contrast to the other phyla examined, the phylogeny is more pronounced (less multifurcation) (see 
+        Table \ref{table:table:percentage loss information subtrees}). This results in a weaker spread of 
+        errors. This is reflected in the results from the table \ref{table:phylum leaf nodes states}. 
+        There are 18 parasites as input data and only 8 more are predicted. The chordata mostly consist of 
+        free-living species, so this seems believable. We started with 99.83~\%  species and 
+        predict 99.97~\% species as free-living (including already known nodes). 
+        \todo{A few punctual tests give us the following:}
+
+      \begin{figure}[h!]
+        \centering
+        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip,width=0.85\textwidth]{Figures/ChordataParasites.png}
+        \caption{Parasites of Phylum: Chordata}
+        \label{fig:ChordataParasites}
+      \end{figure}
+
+      We mapped the few parasitic spezies in a rough taxonomy (see Figure \ref{fig:ChordataParasites}): \\
+      Known parasitic birds belong to the order Sauria. Here we know from Rothschild  here there are 
+        breeding parasites, like the cuckoo and clepto-parasites as the skuas \cite{Rothschild1957}. We
+        got 6 input parasites from GloBI and there are no predictions: A woodpecker - Sphyrapicus varius
+        and a duck - Aix sponsa, a cow bird - Molothrus ater known as broodparasite and some others. \\
+        % Other birds: Columba livia, Nestor meridionalis, Sphyrapicus varius \\
+        % Snake: Storeria dekayi (probably caused by wrong input data.)
+      % \begin{itemize}
+      %   \item Order Cypriniformes (7): carp-type without family.
+      %   \item Order Acanthomorphata(3):, one slime fish (family Blenniidae) and two others without family
+      %   \item Order Anura (1): a toad (Family Bufonidae) - there exists some parasitic species in here, 
+      %     they eat fin or pieces of larger fish.
+      %   \item Order Siluriformes (1): a catfish (Family Loricariidae) - there exists some parasitic 
+      %     species in here.
+      % \end{itemize}
+      % For the Chordata as parasitic species were predicted in the following orders and families:
+      % \begin{itemize}
+      %   \item Order Cypriniformes (16), nine predicted parasites.
+      %   \item Order Sauria (6), only given input parasites.
+      %   \item Order Acanthomorphata(3), only given input parasites.
+      %   \item Order Anura (1), only given input parasite.
+      %   \item Order Siluriformes (1), only given input parasites.
+      % \end{itemize}
+
+      The Apicomplexa are a parasitic phylum. We found only one input organism: Stemonitis fusca as a 
+        free-living specie. In GloBI it is listed as being parasitized by Nectria candicans and Nectriopsis 
+        sporangiicola\footnote{
+          \hyperlink{https://www.globalbioticinteractions.org/?interactionType=parasiteOf&targetTaxon=Stemonitis\%20fusca}
+          {https://www.globalbioticinteractions.org/?interactionType=parasiteOf\&targetTaxon=Stemonitis\%20fusca}
+        }. The algorithm has not predicted new free-livings. \\
+
       For the Platyhelminthes the literature says that there are mostly all Platyhelminthes parasites
-        \todo{ref einfügen}. But at the end we predicted 4.18~\% as free-living. The class Seriata is the 
+        \todo{ref einfügen}. But at the end we predicted 0.1~\% as free-living. The class Seriata is the 
         reason for the most of free-livings in this phylum. These are partly free-living flatworms, so 
@@
         from other related groups by the presence of a folded pharynx and of a number of diverticula 
-        arising from the intestine. The intestine itself may be either simple or branched.[3]}
-
-      With the Nematoda it looks very different. In the Nematoda its much worse. Most Nematoda are 
-        free-living, but we found only 2.63~\% of them. Blaxter et al. speaks of at least seven 
+        arising from the intestine. The intestine itself may be either simple or branched.[3]} \\
+      Note:Plythylmintes had less missing information than starting point, see Table \ref{table:percentage loss information subtrees}.
+
+      With the Nematoda it looks very different. In the Nematoda its much worse. Large parts of Nematoda 
+        are free-living, but we found only 5.32~\% of them. Blaxter et al. speaks of at least seven 
         independently arosed parasitism \cite{Blaxter1998}. In a recent article Blaxter identifies 18 
@@
 
-        The evolution of parasitism in Nematoda: \\
+      \todo{The evolution of parasitism in Nematoda:} \\
       "while only approximately 23 000 species have been described (J.
@@
 
-      \begin{table}
-        \begin{center}
-          \hspace*{-1cm}\begin{tabular}{ |l|r||r|r||r|r|r|r|r|r| }
+      % \anmerkungstext{Das sind schonmal vier große Kontraste, wenn dann noch Zeit bleibt, die 
+      %   schwirigen... Arthropoden, Fungi, Pflanzen... (Emanuel)} \\
+
+      \todotext{Im Folgenden folgen 3 weitere ähnliche tabellen. Einmal eine ähnliche Tabelle inklusive 
+        interner Knoten \ref{table:Phylum internal nodes}, zweimal die Übersicht über die Kingdoms 
+        Blattknoten \ref{table:Kingdom leaf nodes} bzw interne Knoten \ref{table:Kingdom internal nodes}. Welche 
+        nehmen wir? Rest Appendix oder ganz raus?}
+
+      \begin{table}[h!]
+        \begin{center}
+          \begin{tabular}{ |l|r||r|r||r|r|r|r|r|r| }
             \hline
@@
             \hline \hline
-            Chordata & 91785 & 10451 & 18 
-              & 91734 & 0 & 0 & 0 & 0 & 51 \\
-            & & 99.83~\% & 0.49~\%
-              & 99.94~\% & & & & & 0.06~\% \\ \hline
-            Nematoda & 30127 & 21 & 3289 
-              & 791 & 0 & 1017 & 0 & 0 & 28319 \\
-            & & 0.63~\% & 99.37~\%
-              & 2.63~\% & & 3.38~\% & & & 94~\% \\ \hline
-            Platyhelminthes & 22683 & 7 & 7086 
-              & 949 & 0 & 151 & 0 & 0 & 21583 \\
-            & & 0.1~\% & 99.9~\%
-              & 4.18~\% & & 0.67~\% & & & 95.15~\% \\ \hline
-            Apicomplexa & 1863 & 1 & 255 
-              & 1 & 0 & 0 & 0 & 0 & 1862 \\
-            & & 0.39~\% & 99.61~\%
-              & 0.05~\% & & & & & 99.95~\% \\
-            \hline \hline
-            Arthropoda & 1198981 & 18912 & 11141 
-              & 1099509 & 1313 & 22478 & 4176 & 1665 & 70223 \\
-            & & 62.93~\% & 37.07~\%
-              & 91.7~\% & 0.11~\% & 1.87~\% & 0.35~\% & 0.14~\% & 5.86~\% \\
-            \hline
-          \end{tabular} 
-        \end{center}
-        \caption{Phylum (leaf nodes)}
-        \label{table:phylum leaf nodes states} 
-      \end{table}
-
-      \anmerkungstext{Das sind schonmal vier große Kontraste, wenn dann noch Zeit bleibt, die 
-        schwirigen... Arthropoden, Fungi, Pflanzen... (Emanuel)} \\
+            Chordata & 122546 & 10451 & 18 
+              & 122473 & 0 & 0 & 0 & 0 & 73 \\
+            Nematoda & 33564 & 21 & 3289 
+              & 846 & 0 & 1133 & 0 & 0 & 31585 \\
+            Platyhelminthes & 27142 & 7 & 7086 
+              & 1010 & 0 & 175 & 0 & 0 & 25957 \\
+            Apicomplexa & 2102 & 1 & 255 
+              & 1 & 0 & 0 & 0 & 0 & 2101 \\
+            % \hline
+            % Arthropoda & 1319460 & 18912 & 11141 
+            %   & 1207204 & 1313 & 25499 & 4852 & 1957 & 78635 \\
+            \hline
+          \end{tabular}
+        \end{center}
+        \caption{Phylum (inkl internal nodes)}
+        \label{table:Phylum internal nodes}
+      \end{table}
+
+      \begin{table}
+        \begin{center}
+          \hspace*{-2cm}\begin{tabular}{ |l|r||r|r||r|r|r|r|r|r|r|r| }
+            \hline
+            & & \multicolumn{2}{c||}{original states} & \multicolumn{8}{c|}{final states} \\
+            Kingdom & \# nodes & FL & P
+              & 0 (FL) & 0.25 & 0.33 & 0.4 & 0.5 & 0.67 & 0.75 & 1 (P) \\
+            \hline \hline
+            none & 75446 & 45 & 529 
+              & 13426 & 220 & 24082 & 0 & 7792 & 5302 & 0 & 24493 \\
+            Fungi & 31457 & 577 & 2983
+              & 38520 & 0 & 0 & 0 & 5723 & 0 & 0 & 266463 \\
+            Chloroplastida & 416478 & 3519 & 77
+              & 410795 & 0 & 0 & 0 & 4182 & 0 & 0 & 1501 \\
+            Metazoa & 1491012 & 30758 & 22373
+              & 1328135 & 0 & 0 & 930 & 25535 & 4423 & 1665 & 130324 \\
+            \hline  
+          \end{tabular}
+        \end{center}
+        \caption{Kingdom (leaf nodes)}
+        \label{table:Kingdom leaf nodes}
+      \end{table}
 
@@
         \caption{Kingdom (inkl internal nodes)}
-      \end{table}
-
-      \begin{table}
-        \begin{center}
-          \begin{tabular}{ |l|r||r|r||r|r|r|r|r|r| }
-            \hline
-            & & \multicolumn{2}{c||}{original states} & \multicolumn{6}{c|}{final states} \\
-            Phylum & \# nodes & FL & P
-              & 0 (FL) & 0.4 & 0.5 & 0.67 & 0.75 & 1 (P) \\
-            \hline \hline
-            Chordata & 122546 & 10451 & 18 
-              & 122473 & 0 & 0 & 0 & 0 & 73 \\
-            Nematoda & 33564 & 21 & 3289 
-              & 846 & 0 & 1133 & 0 & 0 & 31585 \\
-            Platyhelminthes & 27142 & 7 & 7086 
-              & 1010 & 0 & 175 & 0 & 0 & 25957 \\
-            Apicomplexa & 2102 & 1 & 255 
-              & 1 & 0 & 0 & 0 & 0 & 2101 \\
-            \hline
-            Arthropoda & 1319460 & 18912 & 11141 
-              & 1207204 & 1313 & 25499 & 4852 & 1957 & 78635 \\
-            \hline
-          \end{tabular}
-        \end{center}
-        \caption{Phylum (inkl internal nodes)}
-      \end{table}
-
-      \begin{table}
-        \begin{center}
-          \hspace*{-2cm}\begin{tabular}{ |l|r||r|r||r|r|r|r|r|r|r|r| }
-            \hline
-            & & \multicolumn{2}{c||}{original states} & \multicolumn{8}{c|}{final states} \\
-            Kingdom & \# nodes & FL & P
-              & 0 (FL) & 0.25 & 0.33 & 0.4 & 0.5 & 0.67 & 0.75 & 1 (P) \\
-            \hline \hline
-            none & 75446 & 45 & 529 
-              & 13426 & 220 & 24082 & 0 & 7792 & 5302 & 0 & 24493 \\
-            Fungi & 31457 & 577 & 2983
-              & 38520 & 0 & 0 & 0 & 5723 & 0 & 0 & 266463 \\
-            Chloroplastida & 416478 & 3519 & 77
-              & 410795 & 0 & 0 & 0 & 4182 & 0 & 0 & 1501 \\
-            Metazoa & 1491012 & 30758 & 22373
-              & 1328135 & 0 & 0 & 930 & 25535 & 4423 & 1665 & 130324 \\
-            \hline  
-          \end{tabular}
-        \end{center}
-        \caption{Kingdom (leaf nodes)}
+        \label{table:Kingdom internal nodes}
       \end{table}
@@
   Wieviele Origins haben wir gefunden, was bedeutet diese Zahl? \\
-  Es gibt noch ungenutze information in GloBI.
+  Es gibt noch ungenutze information in GloBI. \\
+  Wir können GloBI verbessern ... Wir haben GloBI auf die gefundenen Abweichungen aufmerksam gemacht... 
+    Fehler werden durch die prediction eventuell verstärkt...\\
 

### 2018-03-20 code/evaluation/analyse_output.R

@@ -4,6 +4,7 @@ library(data.table)
 format(Sys.time(), "%a %b %d %X %Y")
 
 all.taxa <- fread("../../results/Eukaryota-taxa.csv")
+# ott_id,originaltag,finaltag,depth,heights,nr_children,name,rank,uniqname,kingdom,phylum,class,order,family
 
 ### right mode for all
 all.taxa$kingdom <- as.factor(all.taxa$kingdom)
@@ -20,121 +21,98 @@ names(heights) <- c("min.height", "max.height", "mean.height")
 
 all.taxa <- cbind(all.taxa, heights)
 
-## list all Kingdoms, Phyla:
-# table(all.taxa$kingdom)
-# table(all.taxa$phylum)
-
-## which Phylum in which Kingdom:
-# table(all.taxa$kingdom, all.taxa$phylum)
-
-### all nodes sorted by rank
-# table(all.taxa$rank)[order(table(all.taxa$rank))]
-
-print('------------all.taxa$originaltag------------------')
-table(all.taxa$originaltag)
-print('------------all.taxa$finaltag------------------')
-table(all.taxa$finaltag)
-
-# table(all.taxa[all.taxa$finaltag+1 != all.taxa$originaltag, ]$kingdom)
-
-print('---------------------------')
-
-table(droplevels(all.taxa[all.taxa$finaltag+1 != all.taxa$originaltag, ]$phylum))
-
-print('-----------Ascomycota-------------')
-ascomycota <- all.taxa[all.taxa$phylum=="['ott439373', 'Ascomycota']", ]
-bug_data.ascomycota <- ascomycota[ascomycota$finaltag+1 != ascomycota$originaltag, ]
-table(droplevels(bug_data.ascomycota$class))
-dim(ascomycota)
-
-print('---------------------------')
-
-print('-----------Chordata-------------')
-chordata <- all.taxa[all.taxa$phylum=="['ott125642', 'Chordata']", ]
-bug_data.chordata <- chordata[chordata$finaltag+1 != chordata$originaltag, ]
-table(droplevels(bug_data.chordata$class))
-dim(chordata)
-
-print('-----------Sarcopterygii-------------')
-sarcopterygii <- chordata[chordata$class=="['ott458402', 'Sarcopterygii']", ]
-bug_data.sarcopterygii <- sarcopterygii[sarcopterygii$finaltag+1 != sarcopterygii$originaltag, ]
-table(droplevels(bug_data.sarcopterygii$order))
-dim(sarcopterygii)
-
[…]

### 2018-03-20 Paper - Latex/Paper - Skizze - v4.tex
Paper - Methods - rewrite Intro

@@
   \section{Definitions}
+
     \begin{itemize}
-      \item Parasit - Freilebend
-      \item Multifurkation - binär
+      \item Multifurkation - binär (binary or bifurcating... \cite{Felsenstein2003})
       \item height (min, max, mean), depth of a tree/node (Distanz zur Wurzel vs distanz zum Blatt)
-      \item maximum parsimony
       \item OTL, OTT, GloBI
@@
 
-    Parasite \\
+    %---------------------------------------------------------------------------------------------------
+    %--------------------------------------------------------------------------------------------------- 
+    \subsection{Parasite}
       Since we use Globi to classify species as parasitic or free-living, we use their definition of 
@@
 
-    Multifurcation \\
-    binary or bifurcating... \cite{Felsenstein2003}
+    %---------------------------------------------------------------------------------------------------
+    %--------------------------------------------------------------------------------------------------- 
+    \subsection{Maximum parsimony}
+      Maximum parsimony methods Maximum parsimony in phylogeny refers to favoring the tree that needs 
+        the least evolutionary change to explain the observed data. \\
+      In our case, it is about the change of states 'is free-living' or 'is parasitic'.
 
@@
 \chapter{Methods}
-  As initiated, we would like to apply a maximum parsimony algorithm to the entire tree of life to 
+  As initiated, in this paper, a maximum parsimony algorithm is applied to the whole tree of life to 
     obtain an ancestral state reconstruction of free-living versus parasite states. \\
   So far, these reconstructions have been made mainly on binary trees with better data availability. 
-    Therefore, we decided to use a simulation to decide how to evaluate the existing algorithms and 
-    possibly adapt them to our given problem. \\
+    Therefore, a simulation is first performed to evaluate existing algorithms and decide how they 
+    may be adapted to our given problem. This is to perform the ancestral state reconstruction for a 
+    multifurcated (non-binary) tree using binary states. \\
   Accordingly, in addition to the necessary data sets (GloBI, OTL), the chosen algorithm and the 
@@
     \centering
-    \includegraphics[width=0.55\textwidth]{Figures/Workflow-overview.png}
+    \includegraphics[width=0.5\textwidth]{Figures/Workflow-overview.png}
     \caption{Workflow \\
-      The coming sections are thus subdivided into the following topics: \\
-      \todo{or:} The resulting procedure is as follows: \\
-      (1) Get the real tree and real data for the leaf nodes $\rightarrow$ OTL, GloBI databases.
-      (2) Get metadata of these for a realisitc the simulation.
+      The resulting procedure is as follows: \\
+      (1) Retrieve phylogenentic tree data as input for the tree (OTL) and the state information (GloBI).
+      (2) Get metadata of these for a realisitc the simulation of the maximum parsimony algorithms (Fitch \& Sankoff).
       (3) Build and run the simulation.
-      (4) Evaluation of parameters for the simulation and the real problem.
-      (5) Run the resulted algorithm on the original data.
-      (6) Evalute and interprete results. $\rightarrow$ Origins etc...
+      (4) Evaluation of parameters for the simulation and the ancestral state reconstruction of the real tree.
+      (5) Evaluate the accuracy of developed algorithms and choose the best.
+      (6) Run the resulted algorithm on the original data.
+      (7) Evalute and interprete results. %$\rightarrow$ Origins etc...
     }
     \label{fig:workflow}
-  \end{figure}
-
-  % \begin{enumerate}
-  %   \item Get the real tree and real data for the leaf nodes. $\rightarrow$ OTL, GloBI databases
-  %   \item Get metadata of these for a realisitc the simulation.
-  %   \item Build and run the simulation.
-  %   \item Evaluation of parameters for the simulation and the real problem.
-  %   \item Run the resulted algorithm on the original data.
-  %   \item Evalute and interprete results. $\rightarrow$ Origins etc...
-  % \end{enumerate}
-
-  \begin{figure}[h!]
-    \centering
-    \includegraphics[width=1\textwidth]{Figures/Workflow.png}
-    \caption{Big overview of the whole Workflow}
-    \label{fig:Workflow}
   \end{figure}
@@
         \centering
-        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip,width=\textwidth]{Figures/simulation_evaluation_1.png}
+        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{Figures/simulation_evaluation_1.png}
         \caption{Influence of unknown data to prediction}
@@
         \centering
-        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip,width=0.85\textwidth]{Figures/ChordataParasites.png}
+        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.85\textwidth]{Figures/ChordataParasites.png}
         \caption{Parasites of Phylum: Chordata}
@@
 \chapter{Appendices}
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Methods overview}
+    % \begin{figure}[h!]
+    %   \centering
+    %   \includegraphics[angle=90, width=0.4\textwidth]{Figures/Workflow.png}
+    %   \caption{Big overview of the whole Workflow}
+    %   \label{fig:BigWorkflow}
+    % \end{figure}
+    \begin{figure}[h!]
+      \centering
+      \includegraphics[width=\textwidth]{Figures/Workflow.png}
+      \caption{Big overview of the whole Workflow}
+      \label{fig:BigWorkflow}
+    \end{figure}
+
   %---------------------------------------------------------------------------------------------------

### 2018-03-20 Paper - Latex/Paper - Skizze - v4.tex
Paper - Methods - rewrite OTL & GloBI

@@
 
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  \section{Get data - Properties of real Data}
-    For our research we need two types of data: a tree and information about the states. \\
-    For the tree we decided to use Open Tree of Life (OTL). \\
-    For the state information, we decided to use the Global biotic interaction database (GloBI).
+  \todo{In den einzelnen Abschnitten Teile von dem großen Workflow verwenden?: \ref{fig:BigWorkflow}}
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Description of data sets}
+    For \colorbox{red}{our} research two types of data are required: a tree and information about the 
+      states. \\
+    For the tree \colorbox{red}{we} decided to use Open Tree of Life (OTL) \cite{Hinchliff2015}. \\
+    For the state information, \colorbox{red}{we} decided to use the Global biotic interaction 
+      database (GloBI) \cite{Poelen2014}.
 
@@
     \subsection{OTL}
-      For our project we looked for a large database for phylogenetic trees and also for a taxonomic 
-        tree. Since we run our algorithm on the phylogenetic tree, and for the evaluation and other 
-        properties the taxonomy provides us with much more information. \\
-      OTL gives us both. A synthesis of phylogenetic trees (currently 819 trees) and a taxonomic tree. 
-        OTL also includes the large phylogenetic database TreeBASE \cite{Hinchliff2015}. \\
+      For \colorbox{red}{our} project a large database for phylogenetic trees and also for a taxonomic 
+        tree is needed. Since an ancestral state reconstruction algorithm is applied to the phylogenetic 
+        tree, and for the assessment and other properties the taxonomy provides much more information. \\
+      OTL gives a synthesis of phylogenetic trees (currently 819 trees) and a taxonomic tree. OTL also 
+        includes the large phylogenetic database TreeBASE \cite{Hinchliff2015}. \\
       \todo{Das steht auf der Website nicht in dem Paper...} \\
-      For phylogenetic data, there are at least five big data collections, namely: ITIS (Integrated 
-        Taxonomic Information System) \cite{ITIS}, NCBI (National Center for Biotechnology Information) 
-        \cite{NCBI1988}, WORMS (World Register of Marine Species) \cite{WoRMS2018}, GBIF (Global 
-        Biodiversity Information Facility) \cite{GBIF}, OTT (OpenTreeOfLife-Taxonomy) 
-        \cite{Hinchliff2015}. \\
-      \todotext{Marius:} "Every dataset has it's own characteristics and downsides. ITIS is only a small 
-        set of 100~\% confirmed and named species. GBIF is not composed with the help of phylogeny, the 
-        same is valid for the NCBI taxonomy. The WORMS taxonomy is a way too small dataset of mostly 
-        marine species. \\
-      We choosed the taxonomy from OpenTreeOfLife because it's including most of the known taxonomies 
-        and got synthesised by preffering taxonomies that match with available phylogenetic data. At the 
-        same time the team from OTL preferred a maximum number of species \cite{Hinchliff2015}. This is 
-        resulting in somekind of hybrid between taxonomy and phylogeny." \\
-
-      We took a closer look at some of the features of the Synthesis tree. On the one hand the 
+      For phylogenetic data, there are at least five big data collections, namely:
+      \begin{itemize}
+        \item ITIS (Integrated Taxonomic Information System) \cite{ITIS}
+        \item NCBI (National Center for Biotechnology Information) \cite{NCBI1988}
+        \item WORMS (World Register of Marine Species) \cite{WoRMS2018}
+        \item GBIF (Global Biodiversity Information Facility) \cite{GBIF}
+        \item OTT (OpenTreeOfLife-Taxonomy) \cite{Hinchliff2015}
+      \end{itemize}
+      \todo{In die discussion?:} \\
+      ITIS is only a small set of 100~\% confirmed and named species. GBIF is not composed with the help 
+        of phylogeny, the same is valid for the NCBI taxonomy. The WORMS taxonomy is a way too small 
+        dataset of mostly marine species. \\
+      Here the taxonomy from OTL is used because it is including most of the known taxonomies and is 
+        synthesised by preffering taxonomies that match with available phylogenetic data. Furthermore 
+        the team from OTL preferre a maximum number of species \cite{Hinchliff2015}. This is resulting 
+        in somekind of hybrid between taxonomy and phylogeny. \anmerkungstext{Wie genau ist das ein 
+        Hybrid? Genauer beschreiben, was Du damit meinst... (Thilo)} \\
+
+      A closer look is being made to some of the features of the synthesis tree. On the one hand the 
         distribution of the taxa and on the other the distribution of the nodes on the taxa. Since this 
-        is not directly relevant to our study, there is a section in the appendix \ref{sec:otl analysis}.
+        is not directly relevant to \colorbox{red}{our} study, there is a section in the appendix 
+        \ref{sec:otl analysis}.
 
@@
       This database consists of entries of the form: species A (source) interacts with B (target). \\
-      We appointed some interactions\footnote{\hyperlink{
+      A number of interactions have been identified\footnote{\hyperlink{
         https://github.com/jhpoelen/eol-globi-data/blob/master/eol-globi-lib/src/main/java/org/eol/globi/domain/InteractType.java
         }{https://github.com/jhpoelen/eol-globi-data/.../InteractType.java}}
-        , where we know from the biological perspective that the species source or target has to be a 
-        parasite or a free-living species. These are the following:
+        ,including those that the species source or target has become a parasite or a free-living 
+        species from the biological perspective. These are the following:
       \begin{itemize}
@@
       \end{itemize}
-      We build two lists: parasites and free-livings, and add the source or targets of an interaction
-        to these.
+      Two lists are formed: parasites and free-livings, and the source or targets of an interaction
+        are added to these.
 

### 2018-03-20 Paper - Latex/Paper - Skizze - v4.tex
Paper - Methods - rewrite Metadata analysis

@@
   \section{Metadata analysis}
-    In order to generate the most realistic simulation, influencing parameters were investigated. \\
+    In order to generate a realistic simulation, influencing parameters are investigated. \\
     There are two major types of parameters:
@@
     \end{enumerate}
-    We tested the influence of these parameters on our result using our simulation (Section 
+    The influence of these parameters are tested on our result using our simulation (Section 
       \ref{sec:simulation}).
@@
         statement about these probabilities.
-      In general, we assume that there are 40~\% parasites and 60~\% free-livings which is based on the 
-        estimates by Windsor \cite{Windsor1998} and 
+      In general, \colorbox{red}{we} assume that there are 40~\% parasites and 60~\% free-livings which 
+        is based on the estimates by Windsor \cite{Windsor1998} and 
         $\mathcal{P}(FL \rightarrow P) > \mathcal{P}(P \rightarrow FL)$, because a reverse mutation is 
@@
 
-      For the maximum parsimony analysis of the real data, all transition probabilities were equated.
+      For the maximum parsimony analysis of the real data, all transition probabilities are equated.
         However, the used castor package \cite{Louca2017} offers the possibility to enter different 
@@
 
-      In the simulation, we chose two beta distributions and a threshold that indicates the change 
+      In the simulation two beta distributions have been chosen and a threshold that indicates the change 
         between states. \\
-      Different thresholds with different beta distributions were simulated, with different distributions 
-        of parasites and free-livings: 50~\% P to 50~\% FL, 40~\% P to 60~\% FL, 30~\% P to 70~\% FL and 
-        20~\% P to 80~\% FL (\todo{see results simulation, ref...}). Figure \ref{fig:Beta distribution} 
+      Different thresholds with different beta distributions are simulated, with different distributions 
+        of parasites and free-livings:
+        \begin{itemize}
+          \item 50~\% P to 50~\% FL,
+          \item 40~\% P to 60~\% FL,
+          \item 30~\% P to 70~\% FL and 
+          \item 20~\% P to 80~\% FL
+        \end{itemize}
+        (\todo{see results simulation, ref...}). Figure \ref{fig:Beta distribution} 
         shows one example of these. \\
@@
       $$100-\frac{100}{(2293463-1) \times 41974} \approx 98.16 \%$$
-        missing internal nodes. \\
+        missing internal nodes. This means that there is a lack of information about the underlying 
+        phylogeny. Instead of a binary tree this tree is highly multifurcated. \\
 
@@
 
-      In the simulation, the influence of the multifurcations and missing data in leaf nodes on the 
+      In the simulation, the influence of the multifurcation and missing data in leaf nodes on the 
         predictive accuracy of the ancestral state reconstruction algorithms is tested. \\
@@
         regression according to their residuals and BICs.
+      \anmerkungstext{Erklären, warum und wozu das gemacht wird. Warum BIC und nicht AIC? Erklären,
+        was beide bedeuten, wäre sinnvoll. (Thilo)}
 
@@
   \section{Simulation}\label{sec:simulation}
-    There are various possibilities of ancestral state reconstruction. The simulation compared 
-      different algorithms. \\
-    On the one hand different implementations of the Fitch maximum parsimony were compared and on the 
-      other hand the best of them with the implementation of the sankoff algorithm of the castor 
-      package \cite{Louca2017}. \\
+    There are various possibilities of ancestral state reconstruction. The simulation compares
+      different algorithms with each other. \\
+    First different implementations of the Fitch maximum parsimony are compared and then the best of 
+      them is compared with the implementation of the sankoff algorithm of the castor package 
+      \cite{Louca2017}. \\
 
@@
 
-    Figure \ref{fig:Simulation Workflow} shows the course of the simulation. The individual steps are 
-      explained in the following subsections.
+    \todotext{Figure \ref{fig:Simulation Workflow} shows the course of the simulation. The individual 
+      steps are explained in the following subsections: ...}
 
@@
     \subsection{random binary tree}
-      You need a tree to do a simulation of ancestral state reconstruction. It had to be decided whether 
-        to take the real tree or simulate a tree. In this simulation, trees were created randomly, as 
+      A tree is needed to do a simulation of ancestral state reconstruction. It had to be decided whether 
+        to take the real tree or simulate a tree. In this simulation, trees are created randomly, as 
         one can replicate a complete binary phylogentic tree. Thus, there is also the possibility to 
@@
 
-      To get a random binary tree, the Phylo package from biopython were used \cite{Cock2009}. They offer 
+      To get a random binary tree, the Phylo package from biopython is used \cite{Cock2009}. They offer 
         a randomized function which returns a BaseTree\footnote{

### 2018-03-20 Paper - Latex/Paper - Skizze - v4.tex
Paper - Methods - rewrite ancestral state reconstruction

@@
           Woran ist es bisher gescheitert? \\
+          For about 50 years, people have been working on ancestral state reconstruction. The first paper 
+            mentioned above is by Camin and Sokal, who in 1965 were working on algorithms for discrete-state 
+            data \cite{Camin1965}. Different methods have been developed and the question is which method is 
+            the most suitable for our problem. \\
+          For this purpose, various studied methods and their advantages and disadvantages were compared. \\
+
           Bisher wurden vorallem Algorithmen für das binäre Problem entwickelt, da man wesentlich 
@@
     \subsection{simulating states and transitions between them}
-      The next step is to simulate the states of the nodes using the transitions. Again, we simulate 
-        fully known states and then 'forget' everything but a few in the leaf nodes so that you can 
-        later compare the reconstruction with the origin. \\
-      The root node (ancestor of all subsequent species) is (of course) free-living. That means it will 
-        start in the free-living beta distribution. Now traverse from the root to the leaf nodes, always 
-        pulling out of the current distribution until you get above the threshold and the new node 
-        changes state. \\
-      To ensure that the parameter of the binomial distribution is restricted to the [0,1] interval, we 
-        model it with a beta distribution as in Figure \ref{fig:Beta distribution}. \\
+      The next step is to simulate the states of the nodes using the transitions. Again, fully known 
+        states are simulated and then everything is 'forgotten' but a few in the leaf nodes so that 
+        \colorbox{red}{you} can later compare the reconstruction with the origin. \\
+      The root node is defined as ancestor of all subsequent species and in this case, determined to be
+        free-living. Therefore, a beta distribution for free-living is used at the beginning. Now 
+        traverse from the root to the leaf nodes, always pulling out of the current distribution until 
+        \colorbox{red}{you} get above the threshold and the new node changes state. \anmerkungstext{Für 
+        den Tree/Graph Traversal würde sich eine erklärende Abbildung anbieten. Nur Text macht es sehr 
+        schwer verständlich an der Stelle. (Thilo)} \\
+      To ensure that the parameter of the binomial distribution is restricted to the [0,1] interval, it 
+        is modeled with a beta distribution as in Figure \ref{fig:Beta distribution}. \\
 
@@
         internal node and one leaf node is 'forgotten' and stored in another column to the node. \\
-      Different percentages of forgetting the information were simulated, as you can read in the 
-      \todo{section ... from the results}.
+      Different percentages of forgetting the information are simulated, as \colorbox{red}{you} can read 
+      in the \todo{section ... from the results}.
 
@@
     \section{Ancestral state reconstruction methods}
-      For about 50 years, people have been working on ancestral state reconstruction. The first paper 
-        mentioned above is by Camin and Sokal, who in 1965 were working on algorithms for discrete-state 
-        data \cite{Camin1965}. Different methods have been developed and the question is which method is 
-        the most suitable for our problem. \\
-      For this purpose, various studied methods and their advantages and disadvantages were compared. \\
+      As presented in the introduction, there are some methods for ancestral state reconstruction. For 
+        this purpose, various studied methods and their advantages and disadvantages are compared below. \\
 
@@
       One of the major disadvantages of parsimony methods is that, unlike likelihood approaches, they 
-        can not take divergece times (branch length) into account. Since we have no development times in 
-        our case, you can ignore this. \\
+        can not take divergece times (branch length) into account. Since there are no development times 
+        of species in our case, \colorbox{red}{you} can ignore this. \\
       Another problem pointed out by Royer-Carenzi is that parsimony approaches are either based on 
         predefined parameters (generalized parsimony) or on strong and often controversial assumptions, 
-        like irreversibility for dollo parsimony. Again, this problem is irrelevant for us, because you 
-        can only work with generalized models in the analysis of the entire Eukaryota tree. \\
-
-      Following the principle of the simpler model first, the decision has \todo{fallen?} on parsimonious 
-        methods since these are sufficient for the case present here. \\
+        like irreversibility of transitions for dollo parsimony. Again, this problem is irrelevant to 
+        the problem at hand, because \colorbox{red}{you} can only work with generalized models in the 
+        analysis of the entire Eukaryota tree. \\
+
+      Parsimony-based methods are used in this work, since they are fully sufficient for the presented 
+        use case here. Following the principle of the simpler model first. \\
       Felsenstein \cite{Felsenstein2003} discusses in his book two algorithms that generalize all 
@@
             the up-traversing previously. Are both sets used or only the first traversing?
-          \item Since there are several siblings, do you first of all make the cut or union, or directly 
-            in the whole with the father node?
+          \item Since there are several siblings, do \colorbox{red}{you} first of all make the cut or union, 
+            or directly in the whole with the father node?
         \end{itemize}
@@
   \section{Implementation}
-    You can find the full code on GitHub: 
+    \colorbox{red}{You} can find the full code on GitHub: 
       \hyperlink{github.com/Irallia/IZW-HU-Parasites}{github.com/Irallia/IZW-HU-Parasites}. \\
@@
       phylogenetic tree. \\
-      As you can see, we are very far from a binary tree. \\
+      As \colorbox{red}{you} can see, we are very far from a binary tree. \\
 
@@
           \cite{CavalierSmith1981}. \\
-        In section \pageref{subsec:listPhyla} of the appendix you can find a list of all phyla.
+        In section \pageref{subsec:listPhyla} of the appendix \colorbox{red}{you} can find a list of all phyla.
 
@@
 
-      As you can see both algortithms are always over 50\% and therefore better than guessing. Moreover, 
+      As \colorbox{red}{you} can see both algortithms are always over 50\% and therefore better than guessing. Moreover, 
         they are usually close to each other, with Sankoff always makes better predictions except for 
         equally distributed states as Fitch. \\
-      You can see that the distribution of states has a strong influence on the prediction. The more 
+      \colorbox{red}{You} can see that the distribution of states has a strong influence on the prediction. The more 
         evenly distributed, the harder it is to predict. \\
@@
       Here we have encountered a problem: The Castor algorithm gives us probabilities for states. That 
-        means there are also nodes with state like 0.3 or 0.5. So how do you count? Our solution was, 
+        means there are also nodes with state like 0.3 or 0.5. So how do \colorbox{red}{you} count? Our solution was, 
         to round these values. We have to say that we round 0.5 to 0.
@@
     - The most of them are hardly represented. The major taxonomic groups are: ... \\
-    - Here you can see some characteristics of the Multifurcation of the tree. \\
+    - Here \colorbox{red}{you} can see some characteristics of the Multifurcation of the tree. \\
     \begin{figure}[h!]
@@
       taxonomic tree is reflected. If the tree were binary, the taxa would have to double. But the 
-      multipliers for some are much bigger and for others much smaller, which you can see in in figure 
+      multipliers for some are much bigger and for others much smaller, which \colorbox{red}{you} can see in in figure 
       \ref{fig:taxaTable2}. \\

### 2018-03-20 Paper - Latex/Paper - Skizze - v4.tex
Paper - Introduction

@@
     application of prediciton of parasitism. \\
-
-  \anmerkung{Mein Vorschlag einer Gliederung (jeweils ca. ein Absatz) (Bernhard)}
-  \begin{enumerate}
-    \item Motivation:
-      \begin{itemize}
-        \item Was ist das große Ziel? \\
-          Das Ziel dieser Arbeit ist die Anwendung von maximum parsiomony algorithmen auf nicht 
-          binäre Bäume und auf sehr große Datensätze. Insbesondere auf das Beispiel 'Entstehung des 
-          Parasitismus' im ganzen Eukaryotischen Tree of Life.
-        \item Was soll erreicht werden? \\
-          Wir wollen vorhandene Algorithm (Sankoff/castor \cite{Louca2017}) auf diese Aufgabenstellung hin testen 
-          und ihre Vorhersagekraft abschätzen. Außerdem wollen wir den Fitch algorithmus für binäre 
-          Bäume auf unser Problem erweitern und mit dem Sankoff Algorithmus vergleichen.
-        \item Warum ist das relevant? Was könnte man dann tun?\\
-          predict states of species... \\
-          \todo{!!!}
-      \end{itemize}
-    \item Hintergrund:
-      \begin{itemize}
-        \item Was gab es in dieser Richtung bereits als ganze Ansätze oder wenn nicht, warum nicht?
-          Woran ist es bisher gescheitert? \\
+  \todo{Or:} The aim of this thesis is the application of maximum parsiomony algorithms to non-binary 
+    trees and very large datasets. In particular, the example 'Origins of Parasitism' throughout the 
+    Eukaryota Tree of Life. \\
+  We will test the existing algorithms Sankoff (R package \textit{Castor}\cite{Louca2017}) and Fitch 
+    for this task and estimate their predictive power. In addition, we will extend the Fitch 
+    algorithm from binary trees to multifurcating trees to make it usable and comparable for our 
+    current problem. \\
+  This achieves that we can predict ancestral states and unknown states of living species for large 
+    non-binary relatives trees. \\
+
   For about 50 years, people have been working on ancestral state reconstruction. The first paper 
@@
     the most suitable for our problem. \\
-          For this purpose, various studied methods and their advantages and disadvantages were compared. \\
-
-          Bisher wurden vorallem Algorithmen für das binäre Problem entwickelt, da man wesentlich 
-            kleinere Teilbäume betrachtet hat, von welchen man auch alle Aufspaltungen kennt. Durch 
-            die Entwicklung von OTL, eines gesamten Baum des Lebens, ergibt sich das Problem, dass 
-            dieser bei weitem nicht binär ist. \\ \\
-  Researchers of the phylogenies have been dealt with the ancenstral state reconstruction in the 
-    60s. The first methods were only brute force \todo{Quelle, siehe Fitch: Camin and Sokal 1965}. 
-    Next came a set of parsimony algorithms such as: Fitch-parsimony \cite{Fitch1971}, 
-    Wagner-parsimony \cite{Swofford1987} ... \todo{weitere?}. \\
-    With more and more data, there is now the possibility to use more information to calculate the 
-    probabilities of the ancestral states. In addition to the states of the leafs, algorithms could 
-    also use branch lengths. The likelihood based algorithms came more in interest. \\
-    Our focus came with another 'data extension'. We wanted to work with the biggest phylogenetic tree 
-    that exists at this moment, which goes over all observed species. For most \todo{most?} species 
-    there is no phylogeny, but only a taxonomic classification.
-
-        \item Welche Grundlagen sind notwendig:
-          \begin{itemize}
-            \item open tree of life: Was ist das, warum relevant und überlegen als reine Ansätze? \\
-              \todo{!!!} \\ \\
-  So the biggest 'phylogenetic tree' is a synthesis 
-    of phylogenetic trees filled with a taxonomic tree given by Open Tree of Life \cite{Hinchliff2015}.
-    This tree is not binary and therefore the developed algorithms are not directly applicable. \\
-            \item Algorithmen: Was gibt es? Ruhig ausführlicher als hier bereits und vor allem auch 
-              nach einer Darstellung am Ende ableiten, was für uns relevant ist. Also beschreiben, 
-              wie Methode a, b, c funktionieren und dann abwägen, was daher für Dich am 
-              relevantesten ist. \\
-              \todo{!!!} \\
-              \anmerkung{GloBI und OTL in der Einleitung vorstellen. (Emanuel)}
-          \end{itemize}
-      \end{itemize}
-    \item Outlook/Structure of this work
-  \end{enumerate}
-
-  In this work, we have looked at the algorithms that are generally suited to our data, to develop 
-  them further for the not binary case, and finally to compare their usability with our sythesis 
-  tree. \\
-  We have decided to consider only parsimony algorithms since we have no information on branch 
-  lengths and no other additional information like different transition probabilities of our states.
-
-  In den Bacteria und Archaea wurde das mal allgemein für binary traits gemacht:
+
+  \todotext{In den Bacteria und Archaea wurde das mal allgemein für binary traits gemacht: \\
   "A total 90~\% of all binary traits described molecular functions, specifically the presence or absence of a gene or a set of gene involved in biochemical pathways."
   \cite{Goberna2015} \\
-  Unterschied bei uns ist parasitismus komplexer.. da sind meist nicht einzelne Gene zuständig..
+  Unterschied bei uns ist parasitismus komplexer.. da sind meist nicht einzelne Gene zuständig..} \\
+
+  For this purpose, various studied methods and their advantages and disadvantages will be compared. \\
+  These algorithms were developed especially for the binary problem, since one has considered much 
+    smaller subtrees, of which one knows all the splits. \\
+  By developing a whole of an entire tree of life, the problem arises that it is by no means binary.
+
+  % Researchers of the phylogenies have been dealt with the ancenstral state reconstruction in the 
+  %   60s. The first methods were only brute force \todo{Quelle, siehe Fitch: Camin and Sokal 1965}. 
+  %   Next came a set of parsimony algorithms such as: Fitch-parsimony \cite{Fitch1971}, 
+  %   Wagner-parsimony \cite{Swofford1987} ... \todo{weitere?}. \\
+  %   With more and more data, there is now the possibility to use more information to calculate the 
+  %   probabilities of the ancestral states. In addition to the states of the leafs, algorithms could 
+  %   also use branch lengths. The likelihood based algorithms came more in interest. \\
+  %   Our focus came with another 'data extension'. We wanted to work with the biggest phylogenetic tree 
+  %   that exists at this moment, which goes over all observed species. For most \todo{most?} species 
+  %   there is no phylogeny, but only a taxonomic classification.
+  To accomplish this task, a large phylogenetic tree and information about the current species states 
+    is needed. %In this work we use the synthesis tree of Open Tree of Life (OTL) \cite{Hinchliff2015} 
+  The biggest 'phylogenetic tree' is a synthesis of phylogenetic trees filled with a taxonomic tree 
+    given by Open Tree of Life \cite{Hinchliff2015}. This tree is not binary and therefore the 
+    developed algorithms are not directly applicable.Therefore, an algorithm must be found that can 
+    work with non-binary trees. \\
+  For the information about the current states of the species we use the interaction database Global 
+    Biotic Interactions (GloBI) \cite{Poelen2014}.
+
+  % In this work, we have looked at the algorithms that are generally suited to our data, to develop 
+  % them further for the not binary case, and finally to compare their usability with our sythesis 
+  % tree. \\
+  % We have decided to consider only parsimony algorithms since we have no information on branch 
+  % lengths and no other additional information like different transition probabilities of our states.
 

### 2018-03-20 Paper - Latex/Paper - Skizze - v4.tex
Paper - Results - Biological viwe - update Figure and text for it

@@
       \subsubsection{Data artifacts}
-        At this point we also found out that there are some nodes with only one child node (55700 nodes). \\
+        At this point we also found out that there are some nodes with only one child node (55,700 nodes). \\
         These are both, the most nodes are right in front of a leaf, as well as some nodes are deep in the 
-          tree (3956 with height $>2$). They are probably a result from the fact that taxonomic information 
+          tree (3,956 with height $>2$). They are probably a result from the fact that taxonomic information 
           has been incorporated into a phylogeny. \\
@@
         \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.85\textwidth]{Figures/ChordataParasites.png}
-        \caption{Parasites of Phylum: Chordata}
+        \caption{Parasites of Phylum: Chordata \\ 
+          Input parasites (green) $\rightarrow$ predicted parasites (white $\rightarrow$ green)}
         \label{fig:ChordataParasites}
       \end{figure}
+    %---------------------------------------------------------------------------------------------------
 
@@
         breeding parasites, like the cuckoo and clepto-parasites as the skuas \cite{Rothschild1957}. We
-        got 6 input parasites from GloBI and there are no predictions: A woodpecker - Sphyrapicus varius
-        and a duck - Aix sponsa, a cow bird - Molothrus ater known as broodparasite and some others. \\
+        got 6 input parasites from GloBI and there are no predictions: A woodpecker - 
+        \textit{Sphyrapicus varius} and a duck - \textit{Aix sponsa}, a cow bird - \textit{Molothrus ate} 
+        known as broodparasite and some others. \\
+      An example of the amplification of mistakes here are the carp. There seems to be a paper from the 
+        GloBI concluding: Grass carp (\textit{Ctenopharyngodon idella)} has Pathogen common carp 
+        (\textit{Cyprinus carpio})\footnote{
+          \hyperlink{https://www.globalbioticinteractions.org/?interactionType=hasParasite&targetTaxon=Cyprinus\%20carpio}
+          {https://www.globalbioticinteractions.org/?interactionType=hasParasite\&targetTaxon=Cyprinus\%20carpio}
+        }. Since there is hardly any information about free-living, it follows that all siblings are 
+        also predicted to be parasitic. \\
         % Other birds: Columba livia, Nestor meridionalis, Sphyrapicus varius \\
@@
       % \begin{itemize}
-      %   \item Order Cypriniformes (7): carp-type without family.
       %   \item Order Acanthomorphata(3):, one slime fish (family Blenniidae) and two others without family
@@
       %     species in here.
-      % \end{itemize}
-      % For the Chordata as parasitic species were predicted in the following orders and families:
-      % \begin{itemize}
-      %   \item Order Cypriniformes (16), nine predicted parasites.
-      %   \item Order Sauria (6), only given input parasites.
-      %   \item Order Acanthomorphata(3), only given input parasites.
-      %   \item Order Anura (1), only given input parasite.
-      %   \item Order Siluriformes (1), only given input parasites.
       % \end{itemize}

### 2018-03-20 code/evaluation/analyse_output.R

@@ -81,38 +81,39 @@ table(apicomplexa[apicomplexa$finaltag==0, ]$name)
 
 print('-------------More about Chordata:-----------')
 print('--------Classes with parasites:-------')
-table(droplevels(chordata[chordata$finaltag==1, ]$class))
-Actinopteri <- chordata[chordata$class=="['ott285821', 'Actinopteri']", ]
-Sarcopterygii <- chordata[chordata$class=="['ott458402', 'Sarcopterygii']", ]
-print('--------Orders with parasites:-------')
-table(droplevels(Actinopteri[Actinopteri$originaltag==2, ]$order))
-table(droplevels(Actinopteri[Actinopteri$finaltag==1, ]$order))
-print('------------')
-table(droplevels(Sarcopterygii[Sarcopterygii$originaltag==2, ]$order))
-table(droplevels(Sarcopterygii[Sarcopterygii$finaltag==1, ]$order))
+# table(droplevels(chordata[chordata$finaltag==1, ]$class))
+table(chordata[chordata$originaltag==2, ]$name)
+# Actinopteri <- chordata[chordata$class=="['ott285821', 'Actinopteri']", ]
+# Sarcopterygii <- chordata[chordata$class=="['ott458402', 'Sarcopterygii']", ]
+# print('--------Orders with parasites:-------')
+# table(droplevels(Actinopteri[Actinopteri$originaltag==2, ]$order))
+# table(droplevels(Actinopteri[Actinopteri$finaltag==1, ]$order))
+# print('------------')
+# table(droplevels(Sarcopterygii[Sarcopterygii$originaltag==2, ]$order))
+# table(droplevels(Sarcopterygii[Sarcopterygii$finaltag==1, ]$order))
 
-Cypriniformes <- chordata[chordata$order=="['ott1005931', 'Cypriniformes']", ]
-Sauria <- chordata[chordata$order=="['ott329823', 'Sauria']", ]
-Anura <- chordata[chordata$order=="['ott991547', 'Anura']", ]
-Acanthomorphata <- chordata[chordata$order=="['ott108720', 'Acanthomorphata']", ]
-Siluriformes <- chordata[chordata$order=="['ott701516', 'Siluriformes']", ]
-print('--------Families with parasites:-------')
+# Cypriniformes <- chordata[chordata$order=="['ott1005931', 'Cypriniformes']", ]
+# Sauria <- chordata[chordata$order=="['ott329823', 'Sauria']", ]
[…]

### 2018-03-20 Paper - Latex/Paper - Skizze - v4.tex
Paper - Results - Biological View: Platyhelminthes

@@
       In contrast to the other phyla examined, the phylogeny is more pronounced (less multifurcation) (see 
-        Table \ref{table:table:percentage loss information subtrees}). This results in a weaker spread of 
-        errors. This is reflected in the results from the table \ref{table:phylum leaf nodes states}. 
-        There are 18 parasites as input data and only 8 more are predicted. The chordata mostly consist of 
-        free-living species, so this seems believable. We started with 99.83~\%  species and 
-        predict 99.97~\% species as free-living (including already known nodes). 
-        \todo{A few punctual tests give us the following:}
+        Table \ref{table:percentage loss information subtrees}). This results in a weaker spread of errors. 
+        This is reflected in the results from the table \ref{table:phylum leaf nodes states}. There are 18 
+        parasites as input data and only 8 more are predicted. The chordata mostly consist of free-living 
+        species, so this seems believable. We started with 99.83~\%  species and predict 99.97~\% species 
+        as free-living (including already known nodes). \todo{A few punctual tests give us the following:}
 
@@
       \end{figure}
-    %---------------------------------------------------------------------------------------------------
 
@@
 
-      For the Platyhelminthes the literature says that there are mostly all Platyhelminthes parasites
-        \todo{ref einfügen}. But at the end we predicted 0.1~\% as free-living. The class Seriata is the 
-        reason for the most of free-livings in this phylum. These are partly free-living flatworms, so 
-        the prediction looks right. \\
-        \todotext{ Wiki: \\
-        *The Seriata are an order of turbellarian flatworms.[1][2] \\
-        They are found in both freshwater and marine environments, and also include a number of species 
-        found in damp terrestrial conditions. Most are free-living, but the group includes the genus 
-        Bdelloura, which lives comensally on the gills of horseshoe crabs. Seriatans are distinguished 
-        from other related groups by the presence of a folded pharynx and of a number of diverticula 
-        arising from the intestine. The intestine itself may be either simple or branched.[3]} \\
-      Note:Plythylmintes had less missing information than starting point, see Table \ref{table:percentage loss information subtrees}.
+      Most species of Platyhelminthes (flatworms) are parasites, although there are also free-living, 
+        predatory feeding species. These are summarized in the Turbellaria, while the parasites are 
+        divided into three other classes \cite{Ax1961}. This also corresponds to our observations. There 
+        is one class (Rhabditophora) that contains all but one single exception of free-living species 
+        of this phylum, which includes the Turbellaria. \\
+      It should be noted, however, that this classification is outdated, as it has been proven that 
+        the Turbellaria are not monophyletic. But we will not go into that here. \\
+      For the Platyhelminthes we had more state information for the leaf nodes compared to the other 
+        considered subtrees, see Table \ref{table:percentage loss information subtrees}. We start with 
+        0.1~\% free-livings and predicted 0.77~\% as free-living spezies. \\
 

### 2018-03-20 code/evaluation/analyse_output.R

@@ -79,10 +79,10 @@ table(apicomplexa[apicomplexa$finaltag==0, ]$name)
 
 
 
-print('-------------More about Chordata:-----------')
-print('--------Classes with parasites:-------')
+# print('-------------More about Chordata:-----------')
+# print('--------Classes with parasites:-------')
 # table(droplevels(chordata[chordata$finaltag==1, ]$class))
-table(chordata[chordata$originaltag==2, ]$name)
+# table(chordata[chordata$originaltag==2, ]$name)
 # Actinopteri <- chordata[chordata$class=="['ott285821', 'Actinopteri']", ]
 # Sarcopterygii <- chordata[chordata$class=="['ott458402', 'Sarcopterygii']", ]
 # print('--------Orders with parasites:-------')
@@ -115,7 +115,14 @@ table(chordata[chordata$originaltag==2, ]$name)
 # table(Sauria[Sauria$finaltag==1, ]$family)
 # table(Sauria[Sauria$finaltag==1, ]$name)
 
-
-
+print('-------------More about platyhelminthes:-----------')
+print('--------Classes with parasites:-------')
+table(droplevels(platyhelminthes[platyhelminthes$originaltag==1, ]$class))
+table(droplevels(platyhelminthes[platyhelminthes$finaltag==0, ]$class))
+Rhabditophora <- platyhelminthes[platyhelminthes$class=="['ott3669734', 'Rhabditophora']", ]
+# and ['ott407243', 'Trematoda']
+print('--------Orders with parasites:-------')
+table(droplevels(Rhabditophora[Rhabditophora$originaltag==1, ]$order))
+table(droplevels(Rhabditophora[Rhabditophora$finaltag==1, ]$order))
 
 format(Sys.time(), "%a %b %d %X %Y")

### 2018-03-20 Paper - Latex/Paper - Skizze - v4.tex
Paper - Results - Biological View: Nematoda

@@
         0.1~\% free-livings and predicted 0.77~\% as free-living spezies. \\
-
-      With the Nematoda it looks very different. In the Nematoda its much worse. Large parts of Nematoda 
-        are free-living, but we found only 5.32~\% of them. Blaxter et al. speaks of at least seven 
-        independently arosed parasitism \cite{Blaxter1998}. In a recent article Blaxter identifies 18 
-        origins \cite{Blaxter2015} in Nematoda. \\
-        The problem at this point, however, is obvious: The parasites have been much more studied and 
-        thus we start with only 0.63~\% free-living species. Against such a shifted data situation, the 
-        algorithm is almost powerless. And yet the percentage has increased.
-
-      \todo{The evolution of parasitism in Nematoda:} \\
-      "while only approximately 23 000 species have been described (J.
-Hallan, unpublished; https://insects.tamu.edu/research/collection/hallan/), the true species-level diversity may be 1 million or more (Lambshead, 1993)." \\
-      " Estimates of the number of species of parasitic nematode per host suggest that there may be of the order of 25 000 nematode parasites just of vertebrates, most of which remain undescribed (Dobson et al.
-2008)" \\
-      "a large proportion of nematode species may be parasites." \cite{Blaxter2015} \\
+    %---------------------------------------------------------------------------------------------------
+
+      With the Nematoda it looks more complicated. Large parts of Nematoda are free-living, but we 
+        found only 5.32~\% of them. Blaxter et al. estimates the order of 25,000 parasites in the 
+        Nematoda \cite{Blaxter2015} and speaks of at least seven independently arosed parasitism 
+        \cite{Blaxter1998}. In a recent article Blaxter identifies 18 origins \cite{Blaxter2015} in 
+        Nematoda. \\
+      The problem at this point, however, is obvious: Hallan speaks of the fact that only 23,00 species 
+        were described by the Nematoda but one assumes 1 million or more\footnote{J. Hallan, unpublished; 
+          \hyperlink{https://insects.tamu.edu/research/collection/hallan/}
+          {https://insects.tamu.edu/research/collection/hallan/}
+        }. \todo{Link ist nicht erreichbar!} The parasites have been much more studied and thus we start 
+        with only 0.63~\% free-living species. Against such a shifted data situation, the algorithm is 
+        almost powerless. And yet the percentage has increased. \\
 

### 2018-03-21 Paper - Latex/Paper - Skizze - v4.tex
Paper - Introduction

@@
   This paper is about the analysis of ancestral state reconstruction algorithms for non-binary trees, 
-    applied to the currently largest phylogeny synthesis tree of Open Tree Of Life, with the 
-    application of prediciton of parasitism. \\
-  \todo{Or:} The aim of this thesis is the application of maximum parsiomony algorithms to non-binary 
-    trees and very large datasets. In particular, the example 'Origins of Parasitism' throughout the 
-    Eukaryota Tree of Life. \\
-  We will test the existing algorithms Sankoff (R package \textit{Castor}\cite{Louca2017}) and Fitch 
-    for this task and estimate their predictive power. In addition, we will extend the Fitch 
-    algorithm from binary trees to multifurcating trees to make it usable and comparable for our 
-    current problem. \\
+    applied to the currently largest phylogenetic synthesis tree of Open Tree Of Life (OTL)
+    \cite{Hinchliff2015}, with the application of prediciton of parasitism. \\
+  % \todo{Or:} The aim of this paper is the application of maximum parsiomony algorithms to non-binary 
+  %   trees and very large datasets. In particular, the example 'Origins of Parasitism' throughout the 
+  %   Eukaryota Tree of Life. \\
+
+  We will test the existing maximum parsimony algorithms Fitch \cite{Fitch1971} and Sankoff 
+    \cite{Sankoff1975} for this task and estimate their predictive power. The present tree of OTL is 
+    not binary. A tree is binary (or bifurcated), when every node has at most two children otherwise 
+    it is multifurcated \cite{Felsenstein2003}. \\
+  Maximum parsimony methods are developed for phylogenies, which are usually depicted as binary trees.
+    Parsimonious in phylogeny refers to favoring the tree that needs the least evolutionary change 
+    to explain the observed data. In our case, it is about the change of states 'is free-living' or 
+    'is parasitic'. \\
+    % Parsimonious in this context means to minimize the number of transitions between species states 
+    % (free-living or parasitic). 
+  The Sankoff method is implemented by Louca et al. for the non-binary case and is available as an R 
+    package called \textit{Castor} \cite{Louca2017}. In addition, we have implemented the Fitch 
+    method and adapted it for multifurcated trees. \\% to make it usable and comparable for our current problem.
   This achieves that we can predict ancestral states and unknown states of living species for large 
@@
   For about 50 years, people have been working on ancestral state reconstruction. The first paper 
-    mentioned above is by Camin and Sokal, who in 1965 were working on algorithms for discrete-state 
-    data \cite{Camin1965}. Different methods have been developed and the question is which method is 
-    the most suitable for our problem. \\
-
-  \todotext{In den Bacteria und Archaea wurde das mal allgemein für binary traits gemacht: \\
-  "A total 90~\% of all binary traits described molecular functions, specifically the presence or absence of a gene or a set of gene involved in biochemical pathways."
-  \cite{Goberna2015} \\
-  Unterschied bei uns ist parasitismus komplexer.. da sind meist nicht einzelne Gene zuständig..} \\
-
-  For this purpose, various studied methods and their advantages and disadvantages will be compared. \\
-  These algorithms were developed especially for the binary problem, since one has considered much 
-    smaller subtrees, of which one knows all the splits. \\
-  By developing a whole of an entire tree of life, the problem arises that it is by no means binary.
-
-  % Researchers of the phylogenies have been dealt with the ancenstral state reconstruction in the 
-  %   60s. The first methods were only brute force \todo{Quelle, siehe Fitch: Camin and Sokal 1965}. 
+    is by Camin and Sokal, who in 1965 were working on algorithms for discrete-state data 
+    \cite{Camin1965}. Different methods have been developed and the question is which method is the 
+    most suitable for our problem. \\
+  % The first methods were only brute force \todo{Quelle, siehe Fitch: Camin and Sokal 1965}. 
   %   Next came a set of parsimony algorithms such as: Fitch-parsimony \cite{Fitch1971}, 
@@
   %   also use branch lengths. The likelihood based algorithms came more in interest. \\
-  %   Our focus came with another 'data extension'. We wanted to work with the biggest phylogenetic tree 
-  %   that exists at this moment, which goes over all observed species. For most \todo{most?} species 
-  %   there is no phylogeny, but only a taxonomic classification.
-  To accomplish this task, a large phylogenetic tree and information about the current species states 
-    is needed. %In this work we use the synthesis tree of Open Tree of Life (OTL) \cite{Hinchliff2015} 
-  The biggest 'phylogenetic tree' is a synthesis of phylogenetic trees filled with a taxonomic tree 
-    given by Open Tree of Life \cite{Hinchliff2015}. This tree is not binary and therefore the 
-    developed algorithms are not directly applicable.Therefore, an algorithm must be found that can 
-    work with non-binary trees. \\
-  For the information about the current states of the species we use the interaction database Global 
-    Biotic Interactions (GloBI) \cite{Poelen2014}.
-
-  % In this work, we have looked at the algorithms that are generally suited to our data, to develop 
-  % them further for the not binary case, and finally to compare their usability with our sythesis 
-  % tree. \\
+
   % We have decided to consider only parsimony algorithms since we have no information on branch 
@@
 
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  %--------------------------------------------------------------------------------------------------- 
-  \section{Definitions}
-
-    \begin{itemize}
-      \item Multifurkation - binär (binary or bifurcating... \cite{Felsenstein2003})
-      \item height (min, max, mean), depth of a tree/node (Distanz zur Wurzel vs distanz zum Blatt)
-      \item OTL, OTT, GloBI
-    \end{itemize}
-
-    %---------------------------------------------------------------------------------------------------
-    %--------------------------------------------------------------------------------------------------- 
-    \subsection{Parasite}
-      Since we use Globi to classify species as parasitic or free-living, we use their definition of 
-        parasitism. In GloBi, ontobee definitions are used.
+  For this purpose, various studied methods and their advantages and disadvantages will be compared. \\
+  These algorithms were developed especially for the binary problem, since one has considered much 
+    smaller subtrees, of which one knows all the splits. \\
+  By developing a whole of an entire tree of life, the problem arises that it is by no means binary. \\
+
+  For these large phylogenetic synthesis trees, however, ancestral state reconstruction has so far 
+    only been done for Bacteria and Archaea for binary traits by Goberna and Verdú \cite{Goberna2015}.
+    However, this differs from eukaryotes in the sense that complex traits such as parasitism depend
+    on more than one gene. \\
+
+  To accomplish this task, a large phylogenetic tree and information about the current species states 
+    is needed. \\
+  The biggest 'phylogenetic tree' is a synthesis of phylogenetic trees filled with a taxonomic trees 
+    given by Open Tree of Life (OTL) \cite{Hinchliff2015}. %This tree is not binary and therefore the 
+    % developed algorithms are not directly applicable. Therefore, an algorithm must be found that can 
+    % work with non-binary trees. \\
+  For the information about the current states of the species we use the interaction database Global 
+    Biotic Interactions (GloBI) \cite{Poelen2014}. The data in GloBI are stored as interactions. 
+    Useful for us e.g. Species A parasitize species B. From this we conclude that species A is 
+    parasitic and species B free-living. In the case parasite parasitizes parasite, we get conflicting 
+    states for the second species. We solve this by preferring parasitic. \\
+
+  At this point a few words to the term parasitic. There are different definitions. Since we use Globi 
+    to classify species, we use their definition of parasitism. Again, in GloBi, ontobee definitions 
+    are used.
   The interaction has parasite is defined as: "An interaction relationship between two organisms 
     living together in more or less intimate association in a relationship in which association is 
-        disadvantageous or destructive to one of the organisms." \cite{...}. This definition includes: ecto,-
-      and endoparasites, parasitoids, kleptoparasites and pathogenes.
-
+    disadvantageous or destructive to one of the organisms." \cite{...}. This definition includes: 
+    ecto- and endoparasites, parasitoids, kleptoparasites and pathogenes.
   \todotext{Mungall, C., (2017). Definition for the interaction-term: "parasitised by; has parasite" ob
@@
   \hyperlink{ontobee.org/ontology/RO?iri=http://purl.obolibrary.org/obo/RO_0002445}
-      {ontobee.org/ontology/...}}
-
-    %---------------------------------------------------------------------------------------------------
-    %--------------------------------------------------------------------------------------------------- 
-    \subsection{Maximum parsimony}
-      Maximum parsimony methods Maximum parsimony in phylogeny refers to favoring the tree that needs 
-        the least evolutionary change to explain the observed data. \\
-      In our case, it is about the change of states 'is free-living' or 'is parasitic'.
+  {ontobee.org/ontology/...}} \\
+
+  This paper thus consists of the following points: (1) Find a suitable ancestral state 
+    reconstruction method. (2) Perform reconstructing on the Eucaryotic synthesis tree of OTL. \\
+  Point 1 consists of a simulation of our data situation and the application of various possible 
+    algorithms to these. To evaluate them based on the results. \\
+  The one by Louca et al. implemented Sankoff algorithm is the best in our comparisons. Therefore, 
+    point 2 consists of reconstructing the ancestral states and predicting the unknown leaf states. 
+    And then an evaluation of the results. \\
+
+  \todotext{Definitions of height (min, max, mean), depth of a tree/node (Distanz zur Wurzel vs 
+    distanz zum Blatt)}
 
@@
 
-      \begin{table}
+      \begin{table}[h!]
         \begin{center}
@@
       \begin{lstlisting}[gobble=6]
-        # possible tags: 0, 0.333, 0.4, 0.5, 0.667, 0.75, 1
-        # rounded to:    0  0      0    0    1      1     1
-        if node_state != father_state:
-          if father_state == 0:
-              origins += 1        # FL -> P
-              new_found = True
-          else:
-              losses += 1         # P -> FL
-              new_found = True
+        possible tags: 0, 0.333, 0.4, 0.5, 0.667, 0.75, 1
+        rounded to:    0  0      0    0    1      1     1
       \end{lstlisting}
 
-      \todo{without rounding change else: to elif $father_state == 1$}
+      % \begin{lstlisting}[gobble=6]
+      %   # possible tags: 0, 0.333, 0.4, 0.5, 0.667, 0.75, 1
+      %   # rounded to:    0  0      0    0    1      1     1
+      %   if node_state != father_state:
+      %     if father_state == 0:
+      %         origins += 1        # FL -> P
+      %         new_found = True
+      %     else:
+      %         losses += 1         # P -> FL
+      %         new_found = True
+      % \end{lstlisting}
+
+      % \todo{without rounding change else: to elif $father_state == 1$}
 

### 2018-03-21 Paper - Latex/Paper - Skizze - v4.tex
Paper - Anmerkung...
Paper - Methods - Definition of depht and height

@@
     most suitable for our problem. \\
+  \anmerkungstext{hier mehr dazu? Likelihood vs parsiomony... das befindet sich momentan im Methoden 
+    Teil: Ancestral state reconstruction methods} \\
   % The first methods were only brute force \todo{Quelle, siehe Fitch: Camin and Sokal 1965}. 
@@
     ecto- and endoparasites, parasitoids, kleptoparasites and pathogenes.
-  \todotext{Mungall, C., (2017). Definition for the interaction-term: "parasitised by; has parasite" ob
-  ontobee.org. Last checked: 24.07.2017 at 
+  \todotext{Mungall, C., (2017). Definition for the interaction-term: "parasitised by; has parasite" 
+  ob ontobee.org. Last checked: 24.07.2017 at 
   \hyperlink{ontobee.org/ontology/RO?iri=http://purl.obolibrary.org/obo/RO_0002445}
@@
     point 2 consists of reconstructing the ancestral states and predicting the unknown leaf states. 
-    And then an evaluation of the results. \\
-
-  \todotext{Definitions of height (min, max, mean), depth of a tree/node (Distanz zur Wurzel vs 
-    distanz zum Blatt)}
+    And then an evaluation of the results.
 
@@
         \begin{center}
-          \includegraphics[trim = 0mm 0mm 0mm 15mm, clip, width=0.48\textwidth]{Figures/40-60.png}
+          \includegraphics[trim = 0mm 0mm 0mm 13mm, clip, width=0.48\textwidth]{Figures/40-60.png}
         \end{center}
@@
       For the real data, generalized linear models are compared with poisson respectively binomial 
-        regression according to their residuals and BICs.
+        regression according to their residuals and BICs. \\
       \anmerkungstext{Erklären, warum und wozu das gemacht wird. Warum BIC und nicht AIC? Erklären,
-        was beide bedeuten, wäre sinnvoll. (Thilo)}
+        was beide bedeuten, wäre sinnvoll. (Thilo)} \\
+
+      For each node, depth, min, max and mean height were noted. Where the depth of a node is the 
+        distance (number of edges) to the root node and the height of a knot is described as the 
+        largest distance to a leaf node. In this work, a distinction is made between minimum, maximum 
+        and average distance ($\rightarrow$ min, max and mean height). \\
+      The influence in the modeling of these parameters was tested, additive as well as multiplicative.
 
@@
         with a continuous time Markov model \cite{RoyerCarenzi2013}. \\
-
       \todo{Pasqualin et al. unterscheiden noch eine weitere Methode: stochastic mapping...} \\
@@
           briefly explained and referred to the extension. \\
-          \begin{wrapfigure}[19]{r}{0.5\textwidth}
-            \centering
-            \includegraphics[width=0.4\textwidth]{Figures/Fitch1.png}
-            \caption{Fitch algorithm for binary trees. \\
-              The unknown leaf node is discribed with both states. Computed internal nodes (exclusive the 
-              root node) consists of three sets, where the last set is the final one (bold). \\
-              From the second internal node (seen from the root node) there are several possibilities to 
-              create the second and third set.}
-            \label{fig: binary Fitch}
-          \end{wrapfigure}
+
         Input: A rooted, binary tree, with state informations in the leaf nodes. Each node is depicted as 
@@
         \end{enumerate}
+
         First traverse from the leaf nodes to the root / move down the tree / postorder tree traversal.
+          \begin{wrapfigure}{r}{0.5\textwidth}
+            \centering
+            \includegraphics[width=0.4\textwidth]{Figures/Fitch1.png}
+            \caption{Fitch algorithm for binary trees. \\
+              The unknown leaf node is discribed with both states. Computed internal nodes (exclusive the 
+              root node) consists of three sets, where the last set is the final one (bold). \\
+              From the second internal node (seen from the root node) there are several possibilities to 
+              create the second and third set.}
+            \label{fig: binary Fitch}
+          \end{wrapfigure} 
           Each internal node is formed from its child nodes, where at the beginning the only information

### 2018-03-21 Paper - Latex/Paper - Skizze - v4.tex
Paper - Results - Poisson Regression

@@
   %---------------------------------------------------------------------------------------------------
-  \section{Metadata analysis}
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{Missing information}
+  \section{Metadata analysis - Missing information}
     As previously presented, we have two types of missing information: unknown states of leaf nodes 
@@
       nodes and 2 293 463 leaf nodes. \\
-      \begin{figure}[h]
+    For a first overview we collected for every node its number of children (degree $-1$), and plotted
+      this in two histograms, see figure \ref{fig:childrenOfNodes}. \\
+    The multifurcation affects only the internal nodes. We collected the number of children $-2$ of 
+      every node (a node with two children is binary). That means it discribes the number of nodes which we have lost from the real (binary) 
+    phylogenetic tree. \\
+    \begin{figure}[h!]
       \centering
       \begin{subfigure}[b]{0.5\textwidth}
-          \includegraphics[width=\textwidth]{Figures/multifurc.pdf}
+        \includegraphics[width=0.9\textwidth]{Figures/multifurc.pdf}
         \caption{Histogram with automatic binwidth. \\ ~ \\ ~}
@@
       \begin{subfigure}[b]{0.42\textwidth}
-          \includegraphics[trim = 0mm 0mm 30mm 0mm, clip, width=\textwidth]{Figures/multifurc_small.pdf}
-          \caption{Histogram with $binwidth = 1$. \\ light blue: binary; dark blue: multifunction}
+        \includegraphics[trim = 0mm 0mm 30mm 0mm, clip, width=0.9\textwidth]{Figures/multifurc_small.pdf}
+        \caption{Histogram with $binwidth = 1$. \\ light blue: binary; \\ dark blue: multifunction}
       \end{subfigure}
@@
     \end{figure}
-
-      For a first overview we collected for every node its number of children (degree $-1$), and plotted
-        this in two histograms, see figure \ref{fig:childrenOfNodes}. \\
-      The multifurcation affects only the internal nodes. We collected the number of children $-2$ of 
-        every node (a node with two children is binary). That means it discribes the number of nodes which we have lost from the real (binary) 
-      phylogenetic tree. \\
     As \colorbox{red}{you} can see, we are very far from a binary tree. \\
-
     Some subtrees have been examined, these have the following percentages of missing information: See 
       table \ref{table:percentage loss information subtrees}.
-
-      \begin{table} [h]
+    \begin{table}[h!]
       \begin{center}
@@
           \hline
-            Domain  & \% unknown states & \% multifurcation \\ 
-            / Kingdom  & (missing state information & (missing \\
-            / Phylum / Class & of leaf nodes) & internal nodes) \\
+          Subtree of & unknown states & multifurcation \\ 
           \hline \hline
@@
       \end{center}
-        \caption{Examination of subtrees regarding missing information}
+      \caption{Examination of subtrees regarding missing information. \\ 
+        % Taxa of subtrees: Domain, Kingdom, Phylum, Class \\ 
+        Unknown states: missing state information of leaf nodes \\ 
+        Multifurcation: missing internal nodes}
       \label{table:percentage loss information subtrees} 
@@
     %---------------------------------------------------------------------------------------------------
-      \subsubsection{Data artifacts}
+    %---------------------------------------------------------------------------------------------------
+    \subsection{Data artifacts}
       At this point we also found out that there are some nodes with only one child node (55,700 nodes). \\
@@
     %---------------------------------------------------------------------------------------------------
-      \subsubsection{Taxa}
+    %---------------------------------------------------------------------------------------------------
+    \subsection{Taxa}
       The investigation of the taxonomy revealed that our tree has three kingdoms: Chloroplastida, 
@@
     %---------------------------------------------------------------------------------------------------
-      \subsubsection{Poisson regression of the multifurcation}
-        % glm (generalized linear model) analysis: \\
-        The intercept is $2.821 > 0$ $\Rightarrow$ there is a multifunction.
-        (Intercept: Stärke der Multifurcation) \\
+    %---------------------------------------------------------------------------------------------------
+    \subsection{Poisson regression of the multifurcation}
+      First of all we measured the strength of the multifurcation with the help of the intercept: 
+        $2.821 > 0$ $\Rightarrow$ there is a multifunction. \\
       Comparing the different kingdoms, we find that multifunctionality is greater in Fungi than in 
@@
       % Degrees of Freedom: 96010 Total (i.e. Null);  96010 Residual
-        Wir haben außerdem drei komplexitätsstärken von Modellen verglichen bezüglich der höhe und tiefe 
-          des Baums mit dem folgenden Deviance Table:
-
-        \begin{table}[h]
-          \begin{center}
-              \begin{tabular}{ |l|r|r|r|r|r| }
-                \hline
-                Model / Taxa & Kingdom & Phylum & Class & Order & Family \\
+      Then we have 9 times 4 models of different complexity levels.
+      \begin{table}[h!]
+        \begin{center}
+            \begin{tabular}{ |l|r|r|r|r| }
+              \hline
+              Model / Taxa & Kingdom & Phylum & Class & Order \\
               \hline \hline
@@
         \end{center}
-          \caption{Residuals...}
-          \label{table:...} 
-        \end{table}
-        * Residuals: Fehler - wieviele Werte sind nicht gut modelliert. (umso kleiner umso besser - grün) \\
-
-        Interpretation: Die Multifurkation ist sehr ungleich verteilt. Daher ist die vorhersage umso 
-          genauer umso kleinere Subtrees wir betrachten. ...
-
-        Because of the difference in the complexity of the models, we compared their BICs:
+        \caption{Residuals of multifurcation models}
+        \label{table:Residuals multifurcation} 
+      \end{table}
+      In Table \ref{table:Residuals multifurcation} is a deviance table, where the different residuals 
+        are listed. Since only residuals are comparable in complexity, we have also calculated the BIC 
+        values of the models in table \ref{table:BIC multifurcation}. \\
       \begin{table}[h]
         \begin{center}
-            \begin{tabular}{ |l|r|r|r|r|r| }
-              \hline
-              Model / Taxa & Kingdom & Phylum & Class & Order & Family \\
+          \begin{tabular}{ |l|r|r|r|r| }
+            \hline
+            Model / Taxa & Kingdom & Phylum & Class & Order \\
             \hline \hline
@@
         \end{center}
-          \caption{BIC...}
-          \label{table:...} 
-        \end{table}
-
-      %---------------------------------------------------------------------------------------------------
-      \subsubsection{Binomial regression of the unknown state information}
+        \caption{BIC of multifurcation models}
+        \label{table:BIC multifurcation} 
+      \end{table}
+
+      % * Residuals: Fehler - wieviele Werte sind nicht gut modelliert. (umso kleiner umso besser - grün) \\
+      The Residuals give us the error of the model. If the value is small, our data will be well modeled. \\
+      Within the complexity classes it can be seen that the mean height gives the best additional factor. \\
+
+      Despite higher complexity, the BIC values are getting smaller from model to model, meaning that 
+        the finest model available here is also the best one of these. Smaller taxa than orders (eg 
+        family) were computationally too expensive to calculate.
+
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \subsection{Binomial regression of the unknown state information}
 
@@
   %---------------------------------------------------------------------------------------------------
-    \subsection{Results of simulation / Influence of different parameters}
+  %---------------------------------------------------------------------------------------------------
+  \section{Results of simulation / Influence of different parameters}
 

### 2018-03-21 Paper - Latex/Paper - Skizze - v4.tex
Paper - Results - BIC of unknown states

@@
           node percentage. \\
-        At 90~\% unknown nodes and 90~\% of multifurcation of the internal nodes, version 1 was 89.26~\%, 
-          version 2 was 89.26~\%, version 3 was 89.35~\%, and version 4 was 89.31~\% correct. Therefore, 
+        % At 90~\% unknown nodes and 90~\% of multifurcation of the internal nodes, version 1 was 89.26~\%, 
+        %   version 2 was 89.26~\%, version 3 was 89.35~\%, and version 4 was 89.31~\% correct. Therefore, 
+        %   only version 3 was used for all further simulations.
+        At 95~\% unknown nodes and 95~\% of multifurcation of the internal nodes, version 1 was 88.37~\%, 
+          version 2 was 88.37~\%, version 3 was 88.4~\%, and version 4 was 88.39~\% correct. Therefore, 
           only version 3 was used for all further simulations.
+
+      % Fitch versions:
+      % | 88.37 % | 88.37 % | 88.4 % |88.39 % |
 
@@
       \begin{center}
-        \begin{tabular}{ |l|r|r||r|r|r| }
+        \begin{tabular}{ |l||r|r| }
           \hline
@@
       \end{table}
-
       % * Residuals: Fehler - wieviele Werte sind nicht gut modelliert. (umso kleiner umso besser - grün) \\
@@
         For the ancestral state reconstruction, we need information in the leaf nodes. \\
-      The eukaryotic synthesis tree has 293 463 leaf nodes. The GloBI database has 5 346 414 interactions 
-        (at this timepoint). Out of this data we got 51 337 distinct free-living species and 47 332 
-        distinct parasite species $\rightarrow$ unknown nodes 2194794 ($\approx 95.7~\%$). \\
-      We found also $57,352$ (not distinct) source species and $809,993$ (not distinct) target
+      The eukaryotic synthesis tree has 293,463 leaf nodes. The GloBI database has 5 346 414 interactions 
+        (at this timepoint). Out of this data we got 51,337 distinct free-living species and 47 332 
+        distinct parasite species $\rightarrow$ unknown nodes 2,194,794 ($\approx 95.7~\%$). \\
+      We found also 57,352 (not distinct!) source species and 809,993 (not distinct!) target
         species without OTT ids. Since we currently use only OTT ids, we could not use this information. \\
-      \todo{With this only $\approx 4.3~\%$ information in our leaf nodes are ...} \\
+      % \todo{With this only $\approx 4.3~\%$ information in our leaf nodes are ...} \\
+
       We also compared different models in terms of their BICs (Table: \ref{table:BIC unknown information}). 
-        The Residuals are not very meaningful here, since all models have different dimensions.
-
-      \begin{table}[h!]
-        \begin{center}
-          \begin{tabular}{ |l|r|r|r| }
-            \hline
-            Model / Taxa & Kingdom & Phylum & Class \\
-            \hline \hline
-            multifurc $\sim$ taxa & 545740 & \cellcolor{green!10}499227 & \cellcolor{green!30}482265 \\
-            \hline
-            multifurc $\sim$ taxa + depth & 544789 & \cellcolor{green!10}493017 & \cellcolor{green!50}478998 \\
-            \hline
-            multifurc $\sim$ taxa * depth & 544062 & \cellcolor{green!30}488366 & \cellcolor{green!50}476382 \\
-            \hline
-          \end{tabular}
-        \end{center}
-        \caption{Residuals of unknown information}
-        \label{table:...}
-      \end{table}
+        The Residuals are not very meaningful here, since all models have different complexities. % /dimensions
+        For the sake of completeness, the associated deviance tables are located with the residuals in 
+        the appendix \ref{sec:Residuals unknown information}.
 
@@
       \end{table}
-
-      \todo{Taxa like order or family were too expensive to calculate...}
+      It also follows from this table that the most complex model is the best. In general, the BIC 
+        values are smaller than those of the multifurcation models. The modeling here is thus better. \\
+      Again, the calculation of finer models (eg family) was too expensive. \\
+
+      These missing data modeling results can be used to better simulate the data.
 
@@
 
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Missing leaf state modelling - Resiudal tables}\label{sec:Residuals unknown information}
+
+    \begin{table}[h!]
+      \begin{center}
+        \begin{tabular}{ |l|r|r|r| }
+          \hline
+          Model / Taxa & Kingdom & Phylum & Class \\
+          \hline \hline
+          multifurc $\sim$ taxa & 545740 & \cellcolor{green!10}499227 & \cellcolor{green!30}482265 \\
+          \hline
+          multifurc $\sim$ taxa + depth & 544789 & \cellcolor{green!10}493017 & \cellcolor{green!50}478998 \\
+          \hline
+          multifurc $\sim$ taxa * depth & 544062 & \cellcolor{green!30}488366 & \cellcolor{green!50}476382 \\
+          \hline
+        \end{tabular}
+      \end{center}
+      \caption{Residuals of unknown information}
+    \end{table}
+
 \end{document}

### 2018-03-22 Paper - Latex/Paper - Skizze - v4.tex
Paper - Introduction - Anmerkungen von Thilo eingearbeitet

@@
   We will test the existing maximum parsimony algorithms Fitch \cite{Fitch1971} and Sankoff 
-    \cite{Sankoff1975} for this task and estimate their predictive power. The present tree of OTL is 
-    not binary. A tree is binary (or bifurcated), when every node has at most two children otherwise 
-    it is multifurcated \cite{Felsenstein2003}. \\
+    \cite{Sankoff1975} for this task and estimate their predictive power. The present tree structure 
+    of OTL is not binary. A tree is binary (or bifurcated), when each node has at most two children 
+    otherwise it is multifurcated \cite{Felsenstein2003}. \\
+  % \anmerkungstext{auch hier kannst du multiifurcated direkt erklären: that is it each not has 
+    % multiple (n >= 3) children (Thilo)}
   Maximum parsimony methods are developed for phylogenies, which are usually depicted as binary trees.
@@
     \cite{Camin1965}. Different methods have been developed and the question is which method is the 
-    most suitable for our problem. \\
+    most suitable for the problem at hand: The ancestral state reconstruction for a huge 
+    multifurcated tree with \colorbox{red}{binary/two discrete} states. \\
   \anmerkungstext{hier mehr dazu? Likelihood vs parsiomony... das befindet sich momentan im Methoden 
     Teil: Ancestral state reconstruction methods} \\
+  % Royer-Carenzi et al. distinguishes two major classes of ancestral state reconstruction methods: \\
+  %   The first is to explain the current state with the least number of state changes between an 
+  %     ancestor and his child, this is called parsimonious. \\
+  %   The other class she presents involves modeling the character evolution as a stochastic process and 
+  %     using the likelihoods to compute the possible ancestral character states. This is generally done 
+  %     with a continuous time Markov model \cite{RoyerCarenzi2013}. \\
+
   % The first methods were only brute force \todo{Quelle, siehe Fitch: Camin and Sokal 1965}. 
@@
   For the information about the current states of the species we use the interaction database Global 
-    Biotic Interactions (GloBI) \cite{Poelen2014}. The data in GloBI are stored as interactions. 
-    Useful for us e.g. Species A parasitize species B. From this we conclude that species A is 
-    parasitic and species B free-living. In the case parasite parasitizes parasite, we get conflicting 
-    states for the second species. We solve this by preferring parasitic. \\
-
-  At this point a few words to the term parasitic. There are different definitions. Since we use Globi 
-    to classify species, we use their definition of parasitism. Again, in GloBi, ontobee definitions 
-    are used.
-  The interaction has parasite is defined as: "An interaction relationship between two organisms 
-    living together in more or less intimate association in a relationship in which association is 
-    disadvantageous or destructive to one of the organisms." \cite{...}. This definition includes: 
-    ecto- and endoparasites, parasitoids, kleptoparasites and pathogenes.
+    Biotic Interactions (GloBI) \cite{Poelen2014}. The data in GloBI are stored as interactions e.g. 
+    species A parasitize species B. From this we conclude that species A is parasitic and species B 
+    free-living. \\
+
+  At this point a few words to the term parasitic. There are different definitions. Since we use 
+    GloBI to classify species, we use their definition of parasitism. Again, in GloBi, Ontobee 
+    definitions are used \cite{Xiang2011}.
+  The interaction \textit{has parasite} is defined as: "An interaction relationship between two 
+    organisms living together in more or less intimate association in a relationship in which 
+    association is disadvantageous or destructive to one of the organisms." \cite{...}. This 
+    definition includes: ecto- and endoparasites, parasitoids, kleptoparasites and pathogenes.
   \todotext{Mungall, C., (2017). Definition for the interaction-term: "parasitised by; has parasite" 
@@
 
-  This paper thus consists of the following points: (1) Find a suitable ancestral state 
+  The objectives of this work are the following points: (1) Find a suitable ancestral state 
     reconstruction method. (2) Perform reconstructing on the Eucaryotic synthesis tree of OTL. \\
-  Point 1 consists of a simulation of our data situation and the application of various possible 
-    algorithms to these. To evaluate them based on the results. \\
+  The goal of Point 1 is to evaluate the possible methods based on a simulation of our data 
+    situation. \\
   The one by Louca et al. implemented Sankoff algorithm is the best in our comparisons. Therefore, 
     point 2 consists of reconstructing the ancestral states and predicting the unknown leaf states. 
-    And then an evaluation of the results.
+    And then perform an evaluation of the results.
 
@@
       \end{itemize}
+      Of these interactions, e.g. species A parasitize species B, the state of the species is 
+        determined, here is species A parasitic and species B free-living. The case a parasite 
+        conquers (parasitizes) another parasite yields conflicting states for the second species. 
+        This is solved by preferring parasitic. \\
       Two lists are formed: parasites and free-livings, and the source or targets of an interaction
@@
             \hline \hline
-            multifurc $\sim$ taxa & \cellcolor{green!15}545799 & \cellcolor{green!35}500004 & \cellcolor{green!45}485121 & XXXXX \\
+            multifurc $\sim$ taxa & \cellcolor{green!15}545799 & \cellcolor{green!35}500004 & \cellcolor{green!45}485121 & \cellcolor{green!45}484681 \\
             \hline
@@
         values are smaller than those of the multifurcation models. The modeling here is thus better. \\
-      Again, the calculation of finer models (eg family) was too expensive. \\
+      Again, the calculation of finer models (eg order or family) was too expensive. \\
 
@@
     Each point corresponds to the average of one hundred simulations, each with 10,000 leaf nodes. \\
-    For the middle column we set the strength of the multifurcations to 0.95\% similar to the real 
-      data and in the right column the amount of the unknowns to 0.95\% also similar to the real data. \\
-
-    As \colorbox{red}{you} can see both algortithms are always over 50\% and therefore better than guessing. Moreover, 
+    For the middle column we set the strength of the multifurcations to 0.95~\% similar to the real 
+      data and in the right column the amount of the unknowns to 0.95~\% also similar to the real data. \\
+
+    As \colorbox{red}{you} can see both algortithms are always over 50~\% and therefore better than guessing. Moreover, 
       they are usually close to each other, with Sankoff always makes better predictions except for 
@@
       evenly distributed, the harder it is to predict. \\
-    If more than 60\% of internal nodes are missing, Fitch breaks significantly in his prediction 
+    If more than 60~\% of internal nodes are missing, Fitch breaks significantly in his prediction 
       compared to Sankoff.
@@
         out of the input data to see how stable our result is. Of these 10,000 nodes, 9,238 were unique. 
-        Of that, we predicted 9060 ($\approx 98.17~\%$) correctly and 169 ($\approx 1.82~\%$) wrongly, with 
-        duplicate draws always having the same prediction. \\
-      What is the best way to model this data? We again tested the influence of the taxa and the depth of 
-        leaf nodes and calculated the BICs (Table: \ref{table:BIC cross validation}).
+        Of that, we predicted 9060 ($\approx 98.17~\%$) correctly and 169 ($\approx 1.82~\%$) wrongly, 
+        with duplicate draws always having the same prediction. \\
+      What is the best way to model this data? We again tested the influence of the taxa and the depth 
+        of leaf nodes and calculated the BICs (Table: \ref{table:BIC cross validation}).
 
@@
             \hline \hline
-            correct predicted $\sim$ taxa & XXXXX & XXXXX & XXXXX & XXXXX \\
+            correct predicted $\sim$ taxa & 117877 & 111466 & XXXXX & XXXXX \\
             \hline
@@
             \hline \hline
-            correct predicted $\sim$ taxa & 117936 & 112242 & XXXXX & XXXXX \\
+            correct predicted $\sim$ taxa & 117936 & 112242 & 111733 & XXXXX \\
             \hline
@@
       \end{table}
-
-      Resiudals:
-      \begin{itemize}
-        \item correct predicted $\sim$ 1: 120325
-        \item correct predicted $\sim$ kingdom: 117877
-        \item correct predicted $\sim$ phylum: 111466
-      \end{itemize}
 

### 2018-03-22 Paper - Latex/Paper - Skizze - v4.tex
Paper - Titlepage + Congress Abstract

@@
     \pagestyle{empty}
-
-    	\vspace{20mm}
+  	\begin{center}
+      {\Large Freie Universität Berlin} \\
+    	\begin{Huge}
+      	Fachbereich Mathematik und Informatik \\
+      	\vspace{3mm}
+    	\end{Huge}
+    	\vspace{2cm}
     	\begin{Large}
-          \textbf{An analysis of maximum parsimony algorithms to predict parasitism in Eukaryota}\\
-          using a large multiurcated phylogenetic synthesis tree
+        \textbf{An analysis of maximum parsimony algorithms to predict parasitism in Eukaryota} \\
+        \vspace{3mm}
+        using a large multifurcated phylogenetic synthesis tree \\
     	\end{Large}
-
+      \vspace{3cm}
+      \textbf{Eingereicht am:} \\
+      3.4.2018 \\
+    	\vspace{2cm}
+    	Lydia Buntrock \\
+      E-Mail: info@irallia.de \\
+     	\vspace{3cm}
+      \textbf{Betreuer:} \\
+      Dr. Bernhard Y. Renard \\
+      \& \\
+      Prof. Dr. rer. nat. Emanuel Heitlinger \\      
+  	\end{center}
   	\clearpage
@@
 \chapter*{Abstract}
+
+% Parasitism in Eukaryota - Reconstruction of ancestral and unavailable extant states
+
+% Lydia Buntrock^1; Jorrit Poelen^?; Berhard Renard^2; Emanuel Heitlinger^1,3;
+
+% 1 - Institute for Biology, Molecular Parasitology, Humboldt University, Berlin, Germany
+% 2 - Bioinformatics Unit (MF1), Department for Methods Development and Research Infrastructure, Robert Koch Institute, Berlin, Germany
+% 3 - Research Group Ecology and Evolution of Molecular Parasite Host Interactions, Leibniz Institute for Zoo and Wildlife Research, Berlin, Germany
+
+% ## Wenn du willst kannst du auch das IZW (3) an deinen Namen heften!
+% ## Yorrit bitte das Abstract schicken und fragen ob er Co-Author sein will.
+
+  Parasitism can be defined as an interaction between species in which one of the interaction 
+    partners, the parasite, lives in or on the other, the host. The parasite draws food from its 
+    host and harms it in the process. According to some estimates, above 50\% of all eukaryotes are 
+    parasites. Nevertheless, it is difficult to obtain information whether a particular taxon is a 
+    parasite computationally making it difficult to query large sets of taxa. \\
+
+  Here we test in how far it is possible to use the open tree of life (OTL), a synthesis of 
+    phylogenetic trees on a backbone taxonomy (resulting in unresolved nodes), to expand available 
+    information via phylogenetic trait prediction. We use the Global Biotic Interactions (GloBI) 
+    database to categorise 25,992 and 34,879 species as parasites and free-living, respectively and 
+    predict states for over ~2.7 million (97.6\%) leaf nodes without state information. \\
+
+  We estimate the accuracy of our maximum parsimony based predictions using cross-evaluation and 
+    simulation at roughly 80\% overall, but strongly varying between clades. We describe this 
+    variation across taxa as associated with available state and topology information. We compare 
+    our results with several smaller scale studies, which used manual expert curation and conclude 
+    that computationally inferred state changes largely agree in number and placement with those. In 
+    clades in which available state information is biased (mostly towards parasites, e.g. in 
+    Nematodes) phylogenetic prediction is bound to provide results contradicting conventional 
+    wisdom. \\
+
+  This represents, to our knowledge, the first comprehensive computational reconstruction of the 
+    emergence of parasitism in eukaryotes. We argue that such an approach is necessary to allow 
+    further incorporation of parasitism as an important trait in species interaction databases and 
+    in individual studies on eukaryotes e.g. in the microbiome. \\
+
+  ------------ \\
+
   This study focuses on the ancestral state reconstruction of parasitism in the tree of life of

### 2018-03-22 Paper - Latex/Paper - Skizze - v4.tex
Paper - Pagenumbering, serifenlose Schrift
Paper - rearrange Introduction; refine OTL & GloBI

@@
     \clearpage
+    \pagenumbering{Roman}
   \end{titlepage}
@@
 \clearpage
+\pagenumbering{arabic}
 
@@
 \chapter{Introduction}
-  This paper is about the analysis of ancestral state reconstruction algorithms for non-binary trees, 
-    applied to the currently largest phylogenetic synthesis tree of Open Tree Of Life (OTL)
+  This thesis is about the analysis of ancestral state reconstruction algorithms for non-binary 
+    trees, applied to the currently largest phylogenetic synthesis tree of Open Tree of Life (OTL)
     \cite{Hinchliff2015}, with the application of prediciton of parasitism. \\
-  % \todo{Or:} The aim of this paper is the application of maximum parsiomony algorithms to non-binary 
-  %   trees and very large datasets. In particular, the example 'Origins of Parasitism' throughout the 
-  %   Eukaryota Tree of Life. \\
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %--------------------------------------------------------------------------------------------------- 
+  \section{Motivation}
+    The aim of this thesis is the application of maximum parsiomony algorithms to non-binary 
+      trees and very large datasets. In particular, the example find the 'Origins of Parasitism' 
+      throughout the Eukaryota Tree of Life. \\
+    For these large phylogenetic synthesis trees, however, ancestral state reconstruction has so far 
+      only been done for Bacteria and Archaea for binary traits by Goberna and Verdú \cite{Goberna2015}.
+      However, this differs from eukaryotes in the sense that complex traits such as parasitism depend
+      on more than one gene. \\
+    \todo{Warum ist das relevant? Was könnte man dann tun?}
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %--------------------------------------------------------------------------------------------------- 
+  \section{Background}
+    For about 50 years, people have been working on ancestral state reconstruction. The first paper 
+      is by Camin and Sokal, who in 1965 were working on algorithms for discrete-state data 
+      \cite{Camin1965}. Different methods have been developed and the question is which method is the 
+      most suitable for the problem at hand: The ancestral state reconstruction for a huge 
+      multifurcated tree with \colorbox{red}{binary/two discrete} states. \\
+    Royer-Carenzi et al. distinguishes two major classes of ancestral state reconstruction methods: \\
+    The first is maximum parsimony: explain the current state with the least number of state changes 
+      between the child and his ancestor. \\
+    The other class she presents describes modeling the character evolution as a stochastic process and 
+      using the likelihoods to compute the possible ancestral character states. This is generally done 
+      with a continuous time Markov model \cite{RoyerCarenzi2013}. \\
+
+    Parsimony methods are simple methods in which you can not include information such as branch 
+      length (development time of the species). This is also their main point of criticism compared to 
+      the more complex likelihood based models. Since there are no branch lengths or other information 
+      available for the present relationship tree, and thus can not take advantage of the 
+      other models, we decided in favor for parsimonious. \\
 
@@
       \cite{Sankoff1975} for this task and estimate their predictive power. The present tree structure 
-    of OTL is not binary. A tree is binary (or bifurcated), when each node has at most two children 
-    otherwise it is multifurcated \cite{Felsenstein2003}. \\
-  % \anmerkungstext{auch hier kannst du multiifurcated direkt erklären: that is it each not has 
-    % multiple (n >= 3) children (Thilo)}
+      of OTL is not binary. A tree is multifurcated if each node has multiple ($n >= 3$) children 
+      \cite{Felsenstein2003}. \\
     Maximum parsimony methods are developed for phylogenies, which are usually depicted as binary trees.
@@
 
-  For about 50 years, people have been working on ancestral state reconstruction. The first paper 
-    is by Camin and Sokal, who in 1965 were working on algorithms for discrete-state data 
-    \cite{Camin1965}. Different methods have been developed and the question is which method is the 
-    most suitable for the problem at hand: The ancestral state reconstruction for a huge 
-    multifurcated tree with \colorbox{red}{binary/two discrete} states. \\
-  \anmerkungstext{hier mehr dazu? Likelihood vs parsiomony... das befindet sich momentan im Methoden 
-    Teil: Ancestral state reconstruction methods} \\
-  % Royer-Carenzi et al. distinguishes two major classes of ancestral state reconstruction methods: \\
-  %   The first is to explain the current state with the least number of state changes between an 
-  %     ancestor and his child, this is called parsimonious. \\
-  %   The other class she presents involves modeling the character evolution as a stochastic process and 
-  %     using the likelihoods to compute the possible ancestral character states. This is generally done 
-  %     with a continuous time Markov model \cite{RoyerCarenzi2013}. \\
-
-  % The first methods were only brute force \todo{Quelle, siehe Fitch: Camin and Sokal 1965}. 
-  %   Next came a set of parsimony algorithms such as: Fitch-parsimony \cite{Fitch1971}, 
-  %   Wagner-parsimony \cite{Swofford1987} ... \todo{weitere?}. \\
-  %   With more and more data, there is now the possibility to use more information to calculate the 
-  %   probabilities of the ancestral states. In addition to the states of the leafs, algorithms could 
-  %   also use branch lengths. The likelihood based algorithms came more in interest. \\
-
-  % We have decided to consider only parsimony algorithms since we have no information on branch 
-  % lengths and no other additional information like different transition probabilities of our states.
-
-  For this purpose, various studied methods and their advantages and disadvantages will be compared. \\
-  These algorithms were developed especially for the binary problem, since one has considered much 
-    smaller subtrees, of which one knows all the splits. \\
-  By developing a whole of an entire tree of life, the problem arises that it is by no means binary. \\
-
-  For these large phylogenetic synthesis trees, however, ancestral state reconstruction has so far 
-    only been done for Bacteria and Archaea for binary traits by Goberna and Verdú \cite{Goberna2015}.
-    However, this differs from eukaryotes in the sense that complex traits such as parasitism depend
-    on more than one gene. \\
+    % For this purpose, various studied methods and their advantages and disadvantages will be compared. \\
+    % These algorithms were developed especially for the binary problem, since one has considered much 
+    %   smaller subtrees, of which one knows all the splits. \\
+    % By developing a whole of an entire tree of life, the problem arises that it is by no means binary. \\
 
@@
       organisms living together in more or less intimate association in a relationship in which 
-    association is disadvantageous or destructive to one of the organisms." \cite{...}. This 
-    definition includes: ecto- and endoparasites, parasitoids, kleptoparasites and pathogenes.
-  \todotext{Mungall, C., (2017). Definition for the interaction-term: "parasitised by; has parasite" 
-  ob ontobee.org. Last checked: 24.07.2017 at 
-  \hyperlink{ontobee.org/ontology/RO?iri=http://purl.obolibrary.org/obo/RO_0002445}
-  {ontobee.org/ontology/...}} \\
-
+      association is disadvantageous or destructive to one of the organisms."\footnote{
+        \hyperlink{http://www.ontobee.org/ontology/RO?iri=http://purl.obolibrary.org/obo/RO_0002445}
+        {ontobee.org/ontology/RO?iri=http://purl.obolibrary.org/obo/RO\_000244}; Last checked: 22.03.2018.
+      }. This definition includes: ecto- and endoparasites, parasitoids, kleptoparasites and pathogenes.
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %--------------------------------------------------------------------------------------------------- 
+  \section{Structure of this work}
     The objectives of this work are the following points: (1) Find a suitable ancestral state 
@@
 \chapter{Methods}
-  As initiated, in this paper, a maximum parsimony algorithm is applied to the whole tree of life to 
-    obtain an ancestral state reconstruction of free-living versus parasite states. \\
+  As stated in the introduction, in this thesis, a maximum parsimony algorithm is applied to the 
+    whole tree of life to obtain an ancestral state reconstruction of free-living versus parasite 
+    states. \\
   So far, these reconstructions have been made mainly on binary trees with better data availability. 
@@
     the evaluation of the various algorithms and their parameters. \\
-  Figure \ref{fig:workflow} briefly outlines these relationships.
+  Figure \ref{fig:workflow} briefly outlines these relationships. A more detailed view of the 
+    workflow can be found in the appendix \ref{fig:BigWorkflow}.
   \begin{figure}[h!]
     \centering
-    \includegraphics[width=0.5\textwidth]{Figures/Workflow-overview.png}
-    \caption{Workflow \\
-      The resulting procedure is as follows: \\
+    \includegraphics[width=0.45\textwidth]{Figures/Workflow-overview.png}
+    \caption{The Workflow of the resulting procedure with the following steps: \\
       (1) Retrieve phylogenentic tree data as input for the tree (OTL) and the state information (GloBI).
@@
 
-  \todo{In den einzelnen Abschnitten Teile von dem großen Workflow verwenden?: \ref{fig:BigWorkflow}}
-
   %---------------------------------------------------------------------------------------------------
@@
   \section{Description of data sets}
-    For \colorbox{red}{our} research two types of data are required: a tree and information about the 
-      states. \\
-    For the tree \colorbox{red}{we} decided to use Open Tree of Life (OTL) \cite{Hinchliff2015}. \\
-    For the state information, \colorbox{red}{we} decided to use the Global biotic interaction 
-      database (GloBI) \cite{Poelen2014}.
+    Two types of data are needed for an ancestral state reconstruction: a tree and information about 
+      the states. \\
+    For the Tree Open Tree of Life (OTL) is used \cite{Hinchliff2015} and for the state information 
+      the Global Biotic Interaction database (GloBI) is taken \cite{Poelen2014}. \\
+    % These are presented below.
 
@@
     \subsection{OTL}
-      For \colorbox{red}{our} project a large database for phylogenetic trees and also for a taxonomic 
-        tree is needed. Since an ancestral state reconstruction algorithm is applied to the phylogenetic 
-        tree, and for the assessment and other properties the taxonomy provides much more information. \\
-      OTL gives a synthesis of phylogenetic trees (currently 819 trees) and a taxonomic tree. OTL also 
+      For this project a large database for phylogenetic trees and also for a taxonomic tree is needed. 
+        Since an ancestral state reconstruction algorithm is applied to the phylogenetic tree, and for 
+        the assessment and other properties the taxonomy provides much more information. \\
+      OTL gives a synthesis of phylogenetic trees (currently 819 trees) and a taxonomic tree\footnote{
+          \hyperlink{https://tree.opentreeoflife.org/about/synthesis-release/v9.1}
+          {https://tree.opentreeoflife.org/about/synthesis-release/v9.1}; Last checked: 22.03.2018.
+        }. OTL also 
         includes the large phylogenetic database TreeBASE \cite{Hinchliff2015}. \\
@@
     \subsection{GloBI}
-      \todotext{Marius:} "There aren't many big active interaction databases out there, most of them are 
-        offline or outdated. For example: IWDB (Interaction Web Database) \cite{IWDB2003}, Webs on the 
-        Web \cite{WOW2004}, Animal Diversity Web \cite{Myers2003} and ecoweb \cite{Cohen2010}. GloBI is 
-        including most of the known ones and is still growing actively \cite{Poelen2014}. So the 
-        question which interaction database could be used was answered rather quickly." \\
+      The most big interaction databases are offline or outdated. For example: IWDB (Interaction Web 
+        Database) \cite{IWDB2003}, Webs on the Web \cite{WOW2004}, Animal Diversity Web \cite{Myers2003} 
+        and ecoweb \cite{Cohen2010}. GloBI is including most of the known ones and is still growing 
+        actively \cite{Poelen2014}. So the question was answered rather quickly which interaction 
+        database could be used. \\
 
@@
         This is solved by preferring parasitic. \\
-      Two lists are formed: parasites and free-livings, and the source or targets of an interaction
-        are added to these.
+      For each species known IDs are stored in GloBI. This includes OTT (the taxonomy of OTL). All 
+        species that have stored an OTT id and have a matching interaction are formed into two lists: 
+        parasites and free-livings.
 
@@
 
+    % The first methods were only brute force \cite{Camin1965} 
+    %   Next came a set of parsimony algorithms such as: Fitch-parsimony \cite{Fitch1971}, 
+    %   Wagner-parsimony \cite{Swofford1987} ... \todo{weitere?}. \\
+    %   With more and more data, there is now the possibility to use more information to calculate the 
+    %   probabilities of the ancestral states. In addition to the states of the leafs, algorithms could 
+    %   also use branch lengths. The likelihood based algorithms came more in interest. \\
+
       Royer-Carenzi et al. distinguishes two major classes of ancestral state reconstruction methods: \\
@@
         Input: A rooted, binary tree, with state informations in the leaf nodes. Each node is depicted as 
-          a set of states. There are only two states in this paper, free-living (FL) and parasitic (P). 
+          a set of states. There are only two states in this thesis, free-living (FL) and parasitic (P). 
           Internal nodes have three sets, which are empty at the beginning, excluding the root node, it 

### 2018-03-22 Paper - Latex/Paper - Skizze - v4.tex
Paper - Update Workflows; rearrange some Sections

@@
       \end{itemize}
-      \todo{In die discussion?:} \\
       ITIS is only a small set of 100~\% confirmed and named species. GBIF is not composed with the help 
@@
         distribution of the taxa and on the other the distribution of the nodes on the taxa. Since this 
-        is not directly relevant to \colorbox{red}{our} study, there is a section in the appendix 
+        is not directly relevant for this study, there is a section in the appendix 
         \ref{sec:otl analysis}.
@@
         https://github.com/jhpoelen/eol-globi-data/blob/master/eol-globi-lib/src/main/java/org/eol/globi/domain/InteractType.java
-        }{https://github.com/jhpoelen/eol-globi-data/.../InteractType.java}}
-        ,including those that the species source or target has become a parasite or a free-living 
+        }{https://github.com/jhpoelen/eol-globi-data/.../InteractType.java}; Last checked: 22.03.2018.}
+        , including those that the species source or target has become a parasite or a free-living 
         species from the biological perspective. These are the following:
@@
     In order to generate a realistic simulation, influencing parameters are investigated. \\
-    There are two major types of parameters:
+    Since the transitions are minimized in an ancestral state reconstruction, this is an important 
+      parameter to consider. On the other hand, the completeness of our input data are influencing 
+      values. Therefore, two major types are distinguished:
     \begin{enumerate}
@@
     \subsection{Transition probabilities}
-      This subsection deals with the transition probabilities from free-living (hereinafter / as a 
+      As mentioned above, in an ancestral state reconstruction, transitions are minimized, with 
+        transition probabilities playing a role. \\
+      This subsection deals with these transition probabilities from free-living (hereinafter / as a 
         formula FL) to parasitic (hereinafter P) and vice versa: $\mathcal{P}(FL \rightarrow P)$, 
@@
       Different parasite types have different transition probabilities. It is very difficult to make a 
-        statement about these probabilities.
-      In general, \colorbox{red}{we} assume that there are 40~\% parasites and 60~\% free-livings which 
-        is based on the estimates by Windsor \cite{Windsor1998} and 
-        $\mathcal{P}(FL \rightarrow P) > \mathcal{P}(P \rightarrow FL)$, because a reverse mutation is 
-        usually less likely. \todo{This is discussed in section x of the discussion.} \\
+        statement about these probabilities. It is generally assumed in this work that there are 40~\% 
+        parasites and 60~\% free-livings which is based on the estimates by Windsor \cite{Windsor1998} 
+        and $\mathcal{P}(FL \rightarrow P) > \mathcal{P}(P \rightarrow FL)$, because a reverse mutation 
+        is usually less likely. \todo{This is discussed in section x of the discussion.} \\
 
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Simulation}\label{sec:simulation}
-    There are various possibilities of ancestral state reconstruction. The simulation compares
-      different algorithms with each other. \\
-    First different implementations of the Fitch maximum parsimony are compared and then the best of 
-      them is compared with the implementation of the sankoff algorithm of the castor package 
-      \cite{Louca2017}. \\
-
-    \begin{figure}[h!]
-      \centering
-      \includegraphics[width=1\textwidth]{Figures/Workflow-Simulation.png}
-      \caption{Course of the simulation with influence of the metadata analysis from the real data.}
-      \label{fig:Simulation Workflow}
-    \end{figure}
-
-    \todotext{Figure \ref{fig:Simulation Workflow} shows the course of the simulation. The individual 
-      steps are explained in the following subsections: ...}
-
-    \todo{Evaluation - compare trees (distances)}
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{random binary tree}
-      A tree is needed to do a simulation of ancestral state reconstruction. It had to be decided whether 
-        to take the real tree or simulate a tree. In this simulation, trees are created randomly, as 
-        one can replicate a complete binary phylogentic tree. Thus, there is also the possibility to 
-        simulate the multifurcation. \\
-
-      To get a random binary tree, the Phylo package from biopython is used \cite{Cock2009}. They offer 
-        a randomized function which returns a BaseTree\footnote{
-          \hyperlink{https://github.com/biopython/biopython/blob/master/Bio/Phylo/BaseTree.py}
-          {https://github.com/biopython/biopython/blob/master/Bio/Phylo/BaseTree.py}
-        }. \\
-      \todo{ref in die discussion über die randomized function? Diskutieren wir das?}
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{simulating states and transitions between them}
-      The next step is to simulate the states of the nodes using the transitions. Again, fully known 
-        states are simulated and then everything is 'forgotten' but a few in the leaf nodes so that 
-        \colorbox{red}{you} can later compare the reconstruction with the origin. \\
-      The root node is defined as ancestor of all subsequent species and in this case, determined to be
-        free-living. Therefore, a beta distribution for free-living is used at the beginning. Now 
-        traverse from the root to the leaf nodes, always pulling out of the current distribution until 
-        \colorbox{red}{you} get above the threshold and the new node changes state. \anmerkungstext{Für 
-        den Tree/Graph Traversal würde sich eine erklärende Abbildung anbieten. Nur Text macht es sehr 
-        schwer verständlich an der Stelle. (Thilo)} \\
-      To ensure that the parameter of the binomial distribution is restricted to the [0,1] interval, it 
-        is modeled with a beta distribution as in Figure \ref{fig:Beta distribution}. \\
-
-      After traversing through the tree, each state is saved in a nodelist associated with the node ID 
-        which is the OTT from OTL. \\
-
-% simulate loss of information
-      Here begins the simulation of the lost information. This is on the one hand the states and on the 
-        other the topology of the tree. Some splits of nodes are unknown with which the tree is 
-        multifurcated (explained in the following section \todo{pageref}). \\
-
-      In the real tree, there is usually only information about species living today $\rightarrow$ leaf 
-        nodes. And beyond only a small percentage of these. All information about the states of the 
-        internal node and one leaf node is 'forgotten' and stored in another column to the node. \\
-      Different percentages of forgetting the information are simulated, as \colorbox{red}{you} can read 
-      in the \todo{section ... from the results}.
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{simulating loss of information of the tree topology}
-      As previously explained, some divisions in the tree are not known, so the real tree is not binary.
-      This multifurcation was simulated by an equally distributed percentage of forgotten internal nodes.
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
   \section{Ancestral state reconstruction methods}
@@
         briefly explained and referred to the extension. \\
-
-        Input: A rooted, binary tree, with state informations in the leaf nodes. Each node is depicted as 
-          a set of states. There are only two states in this thesis, free-living (FL) and parasitic (P). 
-          Internal nodes have three sets, which are empty at the beginning, excluding the root node, it 
-          has only one. Leaf nodes have their state as a set (eg \{FL\} or \{P\}, unknown leaf nodes the 
-          union of all possible states (\{FL, P\}). \\
-        The algorithm traverses three times trough the tree and fills these sets. \\
-        In each step, two sets are considered and their intersect formed. There are two cases:
-        \begin{enumerate}
-          \item The intersection is not empty and corresponds to the new set.
-          \item The intersection is empty. $\rightarrow$ Build the union of these sets as new set.
-        \end{enumerate}
-
-        First traverse from the leaf nodes to the root / move down the tree / postorder tree traversal.
-          \begin{wrapfigure}{r}{0.5\textwidth}
+        \begin{wrapfigure}[19]{r}{0.5\textwidth}
           \centering
@@
         \end{wrapfigure} 
+      Input: A rooted, binary tree, with state informations in the leaf nodes. Each node is depicted as 
+        a set of states. There are only two states in this thesis, free-living (FL) and parasitic (P). 
+        Internal nodes have three sets, which are empty at the beginning, excluding the root node, it 
+        has only one. Leaf nodes have their state as a set (eg \{FL\} or \{P\}, unknown leaf nodes the 
+        union of all possible states (\{FL, P\}). \\
+
+      The algorithm traverses three times trough the tree and fills these sets. \\
+      In each step, two sets are considered and their intersect formed. There are two cases:
+      \begin{enumerate}
+        \item The intersection is not empty and corresponds to the new set.
+        \item The intersection is empty. $\rightarrow$ Build the union of these sets as new set.
+      \end{enumerate}
+      First traverse from the leaf nodes to the root / move down the tree / postorder tree traversal.
         Each internal node is formed from its child nodes, where at the beginning the only information
@@
 
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Simulation}\label{sec:simulation}
+    The simulation compares these different of ancestral state reconstruction algorithms with each 
+      other. \\
+    First different implementations of the Fitch maximum parsimony are compared and then the best of 
+      them is compared with the implementation of the Sankoff algorithm of the \textit{Castor} package 
+      \cite{Louca2017}. \\
+
+    \begin{figure}[h!]
+      \centering
+      \includegraphics[width=1\textwidth]{Figures/Workflow-Simulation.png}
+      \caption{Course of the simulation with influence of the metadata analysis from the real data.}
+      \label{fig:Simulation Workflow}
+    \end{figure}
+
+    \todotext{Figure \ref{fig:Simulation Workflow} shows the course of the simulation. The individual 
+      steps are explained in the following subsections: ...}
+
+    \todo{Evaluation - compare trees (distances)}
+
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \subsection{random binary tree}
+      A tree is needed to do a simulation of ancestral state reconstruction. It had to be decided whether 
+        to take the real tree or simulate a tree. In this simulation, trees are created randomly, as 
+        one can replicate a complete binary phylogentic tree. Thus, there is also the possibility to 
+        simulate the multifurcation. \\
+
+      To get a random binary tree, the Phylo package from biopython is used \cite{Cock2009}. They offer 
+        a randomized function which returns a BaseTree\footnote{
+          \hyperlink{https://github.com/biopython/biopython/blob/master/Bio/Phylo/BaseTree.py}
+          {https://github.com/biopython/biopython/blob/master/Bio/Phylo/BaseTree.py}
+        }. \\
+      \todo{ref in die discussion über die randomized function? Diskutieren wir das?}
+
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \subsection{simulating states and transitions between them}
+      The next step is to simulate the states of the nodes using the transitions. Again, fully known 
+        states are simulated and then everything is 'forgotten' but a few in the leaf nodes so that 
+        \colorbox{red}{you} can later compare the reconstruction with the origin. \\
+      The root node is defined as ancestor of all subsequent species and in this case, determined to be
+        free-living. Therefore, a beta distribution for free-living is used at the beginning. Now 
+        traverse from the root to the leaf nodes, always pulling out of the current distribution until 
+        \colorbox{red}{you} get above the threshold and the new node changes state. \anmerkungstext{Für 
+        den Tree/Graph Traversal würde sich eine erklärende Abbildung anbieten. Nur Text macht es sehr 
+        schwer verständlich an der Stelle. (Thilo)} \\
+      To ensure that the parameter of the binomial distribution is restricted to the [0,1] interval, it 
+        is modeled with a beta distribution as in Figure \ref{fig:Beta distribution}. \\
+
+      After traversing through the tree, each state is saved in a nodelist associated with the node ID 
+        which is the OTT from OTL. \\
+
+% simulate loss of information
+      Here begins the simulation of the lost information. This is on the one hand the states and on the 
+        other the topology of the tree. Some splits of nodes are unknown with which the tree is 
+        multifurcated (explained in the following section \todo{pageref}). \\
+
+      In the real tree, there is usually only information about species living today $\rightarrow$ leaf 
+        nodes. And beyond only a small percentage of these. All information about the states of the 
+        internal node and one leaf node is 'forgotten' and stored in another column to the node. \\
+      Different percentages of forgetting the information are simulated, as \colorbox{red}{you} can read 
+      in the \todo{section ... from the results}.
+
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \subsection{simulating loss of information of the tree topology}
+      As previously explained, some divisions in the tree are not known, so the real tree is not binary.
+      This multifurcation was simulated by an equally distributed percentage of forgotten internal nodes.
+
   % %---------------------------------------------------------------------------------------------------

### 2018-03-22 Paper - Latex/Paper - Skizze - v4.tex
Paper - Methods - update Plots; remove some subsections

@@
       \textbf{Betreuer:} \\
-      Dr. Bernhard Y. Renard \\
+      Prof. Dr. Bernhard Y. Renard \\
       \& \\
@@
     \centering
-    \includegraphics[width=0.45\textwidth]{Figures/Workflow-overview.png}
+    \includegraphics[width=0.6\textwidth]{Figures/Workflow-overview.png}
     \caption{The Workflow of the resulting procedure with the following steps: \\
@@
         \begin{center}
-          \includegraphics[trim = 0mm 0mm 0mm 13mm, clip, width=0.48\textwidth]{Figures/40-60.png}
+          \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.45\textwidth]{Figures/40-60.JPG}
         \end{center}
@@
         shows one example of these. \\
-      \todo{Plot neu erstellen: Achsenbeschriftung, threshold}
 
@@
         briefly explained and referred to the extension. \\
-        \begin{wrapfigure}[19]{r}{0.5\textwidth}
+
+      Input: A rooted, binary tree, with state informations in the leaf nodes. Each node is depicted as 
+        a set of states. There are only two states in this thesis, free-living (FL) and parasitic (P). 
+        Internal nodes have three sets, which are empty at the beginning, excluding the root node, it 
+        has only one. Leaf nodes have their state as a set (eg \{FL\} or \{P\}, unknown leaf nodes the 
+        union of all possible states (\{FL, P\}). \\
+
+      The algorithm traverses three times trough the tree and fills these sets. \\
+      In each step, two sets are considered and their intersect formed. There are two cases:
+      \begin{enumerate}
+        \item The intersection is not empty and corresponds to the new set.
+        \item The intersection is empty. $\rightarrow$ Build the union of these sets as new set.
+      \end{enumerate}
+      \begin{wrapfigure}{r}{0.5\textwidth}
         \centering
@@
       \end{wrapfigure}
-      Input: A rooted, binary tree, with state informations in the leaf nodes. Each node is depicted as 
-        a set of states. There are only two states in this thesis, free-living (FL) and parasitic (P). 
-        Internal nodes have three sets, which are empty at the beginning, excluding the root node, it 
-        has only one. Leaf nodes have their state as a set (eg \{FL\} or \{P\}, unknown leaf nodes the 
-        union of all possible states (\{FL, P\}). \\
-
-      The algorithm traverses three times trough the tree and fills these sets. \\
-      In each step, two sets are considered and their intersect formed. There are two cases:
-      \begin{enumerate}
-        \item The intersection is not empty and corresponds to the new set.
-        \item The intersection is empty. $\rightarrow$ Build the union of these sets as new set.
-      \end{enumerate}
       First traverse from the leaf nodes to the root / move down the tree / postorder tree traversal.
+
         Each internal node is formed from its child nodes, where at the beginning the only information
@@
       \includegraphics[width=1\textwidth]{Figures/Workflow-Simulation.png}
-      \caption{Course of the simulation with influence of the metadata analysis from the real data.}
+      \caption{A simulation was performed to compare different maximum parsimony algorithms. \\
+        The course of the simulation with influence of the metadata analysis from the real data can
+          be seen: \\
+        (1) A phylogenetic tree is created randomly. (2) Simulate node states for all nodes. (3) 
+          'Forget' internal states and some leaf node states. (4) 'Lose' phylogeny information. (5) 
+          Make a nodelist for the algorithm. (6) Run algorithms. (7) Evaluate results. \\
+        Points 3 and 4 are influenced by metadata of the real-data analysis.}
       \label{fig:Simulation Workflow}
     \end{figure}
-
-    \todotext{Figure \ref{fig:Simulation Workflow} shows the course of the simulation. The individual 
-      steps are explained in the following subsections: ...}
-
-    \todo{Evaluation - compare trees (distances)}
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{random binary tree}
+    The course of a simulation is shown in Figure \ref{fig:Simulation Workflow}. The individual steps 
+      are explained in the following. \\
+
     A tree is needed to do a simulation of ancestral state reconstruction. It had to be decided whether 
@@
       simulate the multifurcation. \\
-
     To get a random binary tree, the Phylo package from biopython is used \cite{Cock2009}. They offer 
@@
 
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{simulating states and transitions between them}
     The next step is to simulate the states of the nodes using the transitions. Again, fully known 
@@
       traverse from the root to the leaf nodes, always pulling out of the current distribution until 
-        \colorbox{red}{you} get above the threshold and the new node changes state. \anmerkungstext{Für 
-        den Tree/Graph Traversal würde sich eine erklärende Abbildung anbieten. Nur Text macht es sehr 
-        schwer verständlich an der Stelle. (Thilo)} \\
+      the randomly drawn number is above the threshold and the new node changes state. 
+      \anmerkungstext{Für den Tree/Graph Traversal würde sich eine erklärende Abbildung anbieten. Nur 
+      Text macht es sehr schwer verständlich an der Stelle. (Thilo)} \\
     To ensure that the parameter of the binomial distribution is restricted to the [0,1] interval, it 
@@
     Here begins the simulation of the lost information. This is on the one hand the states and on the 
-        other the topology of the tree. Some splits of nodes are unknown with which the tree is 
-        multifurcated (explained in the following section \todo{pageref}). \\
+      other the topology of the tree. \\
 
@@
       internal node and one leaf node is 'forgotten' and stored in another column to the node. \\
-      Different percentages of forgetting the information are simulated, as \colorbox{red}{you} can read 
-      in the \todo{section ... from the results}.
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{simulating loss of information of the tree topology}
-      As previously explained, some divisions in the tree are not known, so the real tree is not binary.
-      This multifurcation was simulated by an equally distributed percentage of forgotten internal nodes.
+
+    Last step for the preparation is the multifurcation of the tree. As previously explained, some 
+      divisions in the tree are not known, so the real tree is not binary. This multifurcation is 
+      simulated by an equally distributed percentage of forgotten internal nodes. \\
+
+    Different percentages of forgetting information are simulated, see figure 
+      \ref{fig:influence of unknown data} in the results. \\
+
+    The last step is the evaluation of the results. This is done with a simple difference calculation 
+      of the node states. \\
+    In the nodelist, the originally simulated states and the newly calculated states are stored for 
+      each node ($FL = 0$, $P = 1$). The sum of the differences of the node states gives the distance 
+      of the prediction to the original tree.
 

### 2018-03-22 code/simulation/get_plots.py

@@ -94,6 +94,9 @@ def plot_hist(percentage_parasites):
     n, bins, patches = plt.hist(parasite_distribution, 100, normed=1, facecolor='r', alpha=0.75)
     n, bins, patches = plt.hist(freeliving_distribution, 100, normed=1, facecolor='b', alpha=0.75)
 
+
+    plt.ylabel('number of draws', fontsize=9)
+
     if PLOT_NUMBER == 1:
         plt.title('Histogram of distributions', fontweight='bold')
     if percentage_parasites != '40-old':
@@ -108,19 +111,16 @@ def plot_hist(percentage_parasites):
     plt.legend(handles=[blue_patch, red_patch, black_line], title=title, loc="upper right", fontsize=9) # shadow=True, fancybox=True)
     ax.get_legend().get_title().set_fontweight("bold")
     plt.axis([0, 1, 0, 8])
-    # plt.ylabel('???', fontsize=9)
-    # if PLOT_NUMBER != 11:
-    #     plt.xticks([])
-    # else:
-        # plt.xlabel('???', fontsize=9)
+    if PLOT_NUMBER == 14:
+        plt.xlabel('drawn random number', fontsize=9)
     plt.grid(True)
 
     return
 
 def plot_data_unknown(percentage_parasites):
     global PLOT_NUMBER
-    filepath = 'data/simulation/' + str(percentage_parasites) + '-unknown_plot.csv'
-    data = genfromtxt(filepath, delimiter=',', skip_header=1, skip_footer=0, names=['unknown', 'y_fitch', 'y_my', 'y_sankoff'])
+    filepath = 'data/simulation/' + str(percentage_parasites) + '-unknown.csv'
+    data = genfromtxt(filepath, delimiter=',', skip_header=1, skip_footer=0, names=['unknown', 'multifurcation', 'y_fitch', 'y_my', 'y_sankoff'])
 
     plt.subplot(ROWS, COLS, PLOT_NUMBER)
     PLOT_NUMBER += 1
@@ -144,7 +144,7 @@ def plot_data_unknown(percentage_parasites):
 
 def plot_data_multifurc(percentage_parasites):
     global PLOT_NUMBER
-    filepath = 'data/simulation/' + str(percentage_parasites) + '-unknown-multifurcation.csv'
+    filepath = 'data/simulation/' + str(percentage_parasites) + '-multifurcation.csv'
[…]

### 2018-03-22 Paper - Latex/Paper - Skizze - v4.tex
Paper - Methods - Simulation: figure added

@@
         \begin{center}
-          \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.45\textwidth]{Figures/40-60.JPG}
+          \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.45\textwidth]{Figures/40-60.png}
         \end{center}
@@
       traverse from the root to the leaf nodes, always pulling out of the current distribution until 
-      the randomly drawn number is above the threshold and the new node changes state. 
-      \anmerkungstext{Für den Tree/Graph Traversal würde sich eine erklärende Abbildung anbieten. Nur 
-      Text macht es sehr schwer verständlich an der Stelle. (Thilo)} \\
+      the randomly drawn number is above the threshold and the new node changes state. Figure 
+      \ref{fig:set node states} shows a part of this simulating states. \\
     To ensure that the parameter of the binomial distribution is restricted to the [0,1] interval, it 
-      is modeled with a beta distribution as in Figure \ref{fig:Beta distribution}. \\
+      is modeled with a beta distribution as in Figure \ref{fig:set node states}. \\
 
@@
       which is the OTT from OTL. \\
-
+    \begin{wrapfigure}{r}{0.65\textwidth}
+      \centering
+      \includegraphics[width=0.65\textwidth]{Figures/40-60_all.jpg}
+      \caption{Set node states: Start with a free-living (FL) root node (red); \\
+        (1) + (2) draw random numbers for its children, the numbers are under the threshold 
+        $\rightarrow$ the nodes are again free-living; go on with the children; \\
+        (3) draw a random number, this nubmer is over the threshold the node state changes to parasitic (P) (blue); \\
+        (4) now the node states stay parasitic until the random numer lies unter the threshold.}
+      \label{fig:set node states}
+    \end{wrapfigure}
 % simulate loss of information

### 2018-03-22 code/simulation/get_plots.py

@@ -23,19 +23,58 @@ def main():
 
     plt.tight_layout()
     plt.show()
+    # ------------------------------------------------------------------------
+    # ------------------------------------------------------------------------
 
-    # PLOT_NUMBER = 1
-    # f, axs = plt.subplots(ROWS, COLS, figsize=(7, 10))
-    # plt.suptitle('Influence of unknown data to prediction', fontsize=12, y=1)
+    f, axs = plt.subplots(1, 1, figsize=(4,3))
 
-    # plot_hist(40)
-    # plot_data(40)
+    # -------------------------------------plot distribution------------------------------------
+    beta_distribution_parameters = [7, 5.5, 2.75, 7]   # 40 P - 60 FL
+    #   for freeliving_distribution
+    A_FL = beta_distribution_parameters[0]
+    B_FL = beta_distribution_parameters[1]
+    #   for parasite_distribution
+    A_P = beta_distribution_parameters[2]
+    B_P = beta_distribution_parameters[3]
+
+    freeliving_distribution = []
+    parasite_distribution = []
+    for item in range(0, 1000000):
+        freeliving_distribution.append(betavariate(A_FL, B_FL))
+        parasite_distribution.append(betavariate(A_P, B_P))
+
+    ax = plt.subplot(1, 1, 1)
+
+    # the histogram of the data
+    n, bins, patches = plt.hist(parasite_distribution, 100, normed=1, facecolor='r', alpha=0.75)
+    n, bins, patches = plt.hist(freeliving_distribution, 100, normed=1, facecolor='b', alpha=0.75)
+
+    plt.xlabel('drawn random number', fontsize=9)
+    plt.ylabel('number of draws', fontsize=9)
+
+    title = str(40) + '% P - ' + str(100-40) + '% FL'
+    plt.axvline(x=40/100, color='black')#, xmin=0.25, xmax=0.402, linewidth=2)
     
-    # plot_hist('40-old')
-    # plot_data('40-old')
+    blue_patch = mpatches.Patch(color='blue', label='free-livings')
+    red_patch = mpatches.Patch(color='red', label='parasites')
+    black_line = mlines.Line2D([], [], color='black', label='threshold')#, marker='*', markersize=15)
+    plt.legend(handles=[blue_patch, red_patch, black_line], title=title, loc="upper right", fontsize=9) # shadow=True, fancybox=True)
+    ax.get_legend().get_title().set_fontweight("bold")
[…]

### 2018-03-22 Paper - Latex/Paper - Skizze - v4.tex
Paper - Methods - Simulation: fine tune

@@
 
-    The next step is to simulate the states of the nodes using the transitions. Again, fully known 
-      states are simulated and then everything is 'forgotten' but a few in the leaf nodes so that 
-      \colorbox{red}{you} can later compare the reconstruction with the origin. \\
+    The next step is to simulate states for all nodes. \\
     The root node is defined as ancestor of all subsequent species and in this case, determined to be
@@
 
-    After traversing through the tree, each state is saved in a nodelist associated with the node ID 
-      which is the OTT from OTL. \\
-    \begin{wrapfigure}{r}{0.65\textwidth}
+    After traversing through the tree, each state is saved in a nodelist associated with the  
+    \begin{wrapfigure}[21]{r}{0.65\textwidth}
       \centering
       \includegraphics[width=0.65\textwidth]{Figures/40-60_all.jpg}
-      \caption{Set node states: Start with a free-living (FL) root node (red); \\
-        (1) + (2) draw random numbers for its children, the numbers are under the threshold 
-        $\rightarrow$ the nodes are again free-living; go on with the children; \\
-        (3) draw a random number, this nubmer is over the threshold the node state changes to parasitic (P) (blue); \\
-        (4) now the node states stay parasitic until the random numer lies unter the threshold.}
+      \caption{Set node states: Distribution of states (left); traversion through the tree (right). \\
+        Start with a free-living root node (FL: red). \\
+        (1) + (2) Draw random numbers for its children from the free-living distribution (red), the numbers are under the threshold 
+        $\rightarrow$ the nodes are again free-living; go on with the children. \\
+        (3) The number drawn is above the threshold. $\rightarrow$ The node state changes to parasitic (P: blue). \\
+        (4) Now draw random numbers from the parasite distribution (red) until one number lies unter the threshold. Then change back.}
       \label{fig:set node states}
     \end{wrapfigure}
+    node ID which is the OTT from OTL. \\
+
 % simulate loss of information
@@
   \section{Implementation}
-    \colorbox{red}{You} can find the full code on GitHub: 
+    The complete code is located on GitHub: 
       \hyperlink{github.com/Irallia/IZW-HU-Parasites}{github.com/Irallia/IZW-HU-Parasites}. \\

### 2018-03-22 Paper - Latex/Paper - Skizze - v4.tex
Paper - more data, less 'you's

@@
     One of the major disadvantages of parsimony methods is that, unlike likelihood approaches, they 
-      can not take divergece times (branch length) into account. Since there are no development times 
-      of species in our case, \colorbox{red}{you} can ignore this. \\
+      can not take divergece times (branch length) into account. Since the OTL does not include 
+      development times of species, this is irrelevant. \\
     Another problem pointed out by Royer-Carenzi is that parsimony approaches are either based on 
       predefined parameters (generalized parsimony) or on strong and often controversial assumptions, 
-      like irreversibility of transitions for dollo parsimony. Again, this problem is irrelevant to 
-      the problem at hand, because \colorbox{red}{you} can only work with generalized models in the 
-      analysis of the entire Eukaryota tree. \\
+      like irreversibility of transitions for dollo parsimony. Again, this problem is unimportant to 
+      the problem at hand, because in the analysis of the entire Eukaryota tree only generalized 
+      models make sense. \\
 
@@
             \hline \hline
-            correct predicted $\sim$ taxa & 117877 & 111466 & XXXXX & XXXXX \\
-            \hline
-            correct predicted $\sim$ taxa + depth & 117703 & XXXXX & XXXXX & XXXXX \\
-            \hline
-            correct predicted $\sim$ taxa * depth & 117592 & XXXXX & XXXXX & \cellcolor{green!60}XXXXX \\
+            correct predicted $\sim$ taxa & 117877 & 111466 & 108878 & XXXXX \\
+            \hline
+            correct predicted $\sim$ taxa + depth & 117703 & 110513 & XXXXX & XXXXX \\
+            \hline
+            correct predicted $\sim$ taxa * depth & 117592 & 109827 & XXXXX & \cellcolor{green!60}XXXXX \\
             \hline
@@
             \hline
-            correct predicted $\sim$ taxa + depth & 117776 & XXXXX & XXXXX & XXXXX \\
-            \hline
-            correct predicted $\sim$ taxa * depth & XXXXX & XXXXX & XXXXX & \cellcolor{green!60}XXXXX \\
+            correct predicted $\sim$ taxa + depth & 117776 & 111304 & 111273 & XXXXX \\
+            \hline
+            correct predicted $\sim$ taxa * depth & 117709 & 111262 & XXXXX & \cellcolor{green!60}XXXXX \\
             \hline

### 2018-03-23 Paper - Latex/Paper - Skizze - v4.tex
Paper - Results: rewrite Results motivation and the first parts of Metadata analysis

@@
     \end{enumerate}
-    The influence of these parameters are tested on our result using our simulation (Section 
+    The influence of these parameters are tested on our result using our simulation (section 
       \ref{sec:simulation}).
@@
     %---------------------------------------------------------------------------------------------------
-    \subsection{Missing information}
+    \subsection{Missing information} \label{sec:methods - missing information}
 
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Ancestral state reconstruction methods}
+  \section{Ancestral state reconstruction methods} \label{sec:ancestral state reconstruction}
     As presented in the introduction, there are some methods for ancestral state reconstruction. For 
@@
       use case here. Following the principle of the simpler model first. \\
+    \anmerkungstext{Nochmal darstellen warum und selbst wenn sie fully sufficient wäre, heißt es ja 
+      nicht, dass man sie nehmen muss. Also: motiviere! (Renard)} \\
     Felsenstein \cite{Felsenstein2003} discusses in his book two algorithms that generalize all 
@@
 
-  % %---------------------------------------------------------------------------------------------------
-  % %---------------------------------------------------------------------------------------------------
-  % %---------------------------------------------------------------------------------------------------
-  % \section{real data analysis}
-  %   \begin{itemize}
-  %     \item Import tree
-  %     \item Import interactions
-  %     \item run castor algorithm / and others?
-  %     \item interprete results (cross validation - leave 100 out)
-  %   \end{itemize}
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{real data analysis}
+    \todo{Evaluation section in methods?}
+    \begin{itemize}
+      \item Import tree
+      \item Import interactions
+      \item run castor algorithm / and others?
+      \item interprete results (cross validation - leave 100 out)
+    \end{itemize}
+    We then evaluated the results in two ways. On the one hand, we have examined the results of some 
+      sub-trees for their credibility with the help of biological background knowledge. On the other 
+      hand, we performed a leaf 100 out cross validation.
 
@@
 \chapter{Results}
-  A big point in this chapter is the result of examining the input data. How is the situation? What 
-    influence does that have on our actual result? What can we do about it? Our simulation gave us 
-    some results to this. \\
-  Otherwise, this chapter is mainly about the actual reconstruction of the states. This means, on 
-    one hand investigation of origins and losses of the inner nodes and on the other, the prediction 
-    of unknown states of leaf nodes. \\
-   
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  \section{Metadata analysis - Missing information}
-    As previously presented, we have two types of missing information: unknown states of leaf nodes 
-      and multifurcation. \\
-
-    We examined the ridge of multifurcation of the tree. A complete phylogenetic tree would be 
-      binary, which means the number of leaf nodes is closely to the number of internal nodes. But 
-      since we only work with a synthesis tree, this tree is multifurcated: we have 241 974 internal 
-      nodes and 2 293 463 leaf nodes. \\
-    For a first overview we collected for every node its number of children (degree $-1$), and plotted
-      this in two histograms, see figure \ref{fig:childrenOfNodes}. \\
-    The multifurcation affects only the internal nodes. We collected the number of children $-2$ of 
-      every node (a node with two children is binary). That means it discribes the number of nodes which we have lost from the real (binary) 
-    phylogenetic tree. \\
-    \begin{figure}[h!]
-      \centering
-      \begin{subfigure}[b]{0.5\textwidth}
-        \includegraphics[width=0.9\textwidth]{Figures/multifurc.pdf}
-        \caption{Histogram with automatic binwidth. \\ ~ \\ ~}
-      \end{subfigure}
-      ~~~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-        %(or a blank line to force the subfigure onto a new line)
-      \begin{subfigure}[b]{0.42\textwidth}
-        \includegraphics[trim = 0mm 0mm 30mm 0mm, clip, width=0.9\textwidth]{Figures/multifurc_small.pdf}
-        \caption{Histogram with $binwidth = 1$. \\ light blue: binary; \\ dark blue: multifunction}
-      \end{subfigure}
-      \caption{Histograms about the multifurcation of the internal nodes of the synthesis tree.}
-      \label{fig:childrenOfNodes}
-    \end{figure}
-    As \colorbox{red}{you} can see, we are very far from a binary tree. \\
-    Some subtrees have been examined, these have the following percentages of missing information: See 
-      table \ref{table:percentage loss information subtrees}.
+  This work deals with the ancestral state reconstruction of the entire Eukaryota relatives tree. \\
+
+  For this reconstruction, we first analyzed our data. This is the tree of OTL \cite{Hinchliff2015}
+    and the data for the leaf nodes (free-living or parasite states) from GloBI \cite{Poelen2014} 
+    (section \ref{sec:results - missing information}). \\
+  Next we compared different possible methods. We decided to take a closer look at maximum parsimony 
+    algorithms because they are best suited to the problem at hand. The reason for this can be found 
+    in section \ref{sec:ancestral state reconstruction}. We tested these on different simulations of 
+    the data and compared their predictive power (section \ref{sec:results of simulation}). \\
+  We used the Sankoff algorithm \cite{Sankoff1975} implemented by Louca et al. \cite{Louca2017}, 
+    which performs best, for the actual reconstruction on the real data. \\
+
+  We then evaluated the results in two ways. On the one hand, we have examined the results of some 
+    sub-trees for their credibility with the help of biological background knowledge (Subsection 
+    \ref{sec:biological view}). On the other hand, we performed a leaf 100 out cross validation
+    (Subsection \ref{sec:results cross evaluation}).
+
+  % The next sections now guide you through the results of these different steps.
+
+%   Otherwise, this chapter is mainly about the actual reconstruction of the states. This means, on 
+%     one hand investigation of origins and losses of the inner nodes and on the other, the prediction 
+%     of unknown states of leaf nodes. \\
+%    
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Metadata analysis - Missing information} \label{sec:results - missing information}
+    As previously presented in the methods (section \ref{sec:methods - missing information}), we have 
+      two types of missing information: unknown states of leaf nodes and multifurcation. \\
+
+    A tree is multifurcated if there are nodes that have more than two children. In the case of a 
+      phylogenetic tree, the ridge of multifurcation describes the amount of lack of information about 
+      the topology of the tree. A complete phylogenetic tree would be binary, meaning that the number 
+      of leaf nodes equals the number of internal nodes minus one. Since we only work with a 
+      artificially constructed tree (synthesis of several phylogenetic trees), this tree is strongly 
+      multifurcated: It has 241,974 internal nodes for 2,293,463 leaf nodes $\rightarrow$ 98.16 \% 
+      missing nodes. \\
+    We calculated these percentages of missing nodes and also missing state information for some 
+      subtrees and plotted them in table \ref{table:percentage loss information subtrees}. \\
     \begin{table}[h!]
@@
       \caption{Examination of subtrees regarding missing information. \\ 
-        % Taxa of subtrees: Domain, Kingdom, Phylum, Class \\ 
-        Unknown states: missing state information of leaf nodes \\ 
-        Multifurcation: missing internal nodes}
+        The percentage values show the ratio of missing information of: unknown states (missing state 
+          information of leaf nodes) and multifurcation (missing internal nodes). \\
+        The subtrees are from different taxa: domain (Eukaryota), kingdom (Metazoa, Fungi, 
+          Chloroplastida), phylum (Apicomplexa, Nematoda, Chordata, Platyhelminthes) and class 
+          (Insecta). \\
+        The two by far smallest values were highlighted in green.} 
       \label{table:percentage loss information subtrees} 
@@
 
+    We also have for a first overview we collected for each node its number of children (degree $-1$), 
+      and plotted this in two histograms, see figure \ref{fig:childrenOfNodes}. \\
+    \begin{figure}
+      \centering
+      \begin{subfigure}[b]{0.59\textwidth}
+        \includegraphics[width=0.9\textwidth]{Figures/multifurc.pdf}
+        \caption{Histogram with automatic binwidth. \\ ~}
+      \end{subfigure}
+      \begin{subfigure}[b]{0.4\textwidth}
+        \includegraphics[trim = 0mm 0mm 30mm 0mm, clip, width=0.9\textwidth]{Figures/multifurc_small.pdf}
+        \caption{Histogram with $binwidth = 1$. Higher multifurcation than 30 has been cut off. \\ light blue: binary; \\ dark blue: multifurcation}
+      \end{subfigure}
+      \caption{Histograms about the multifurcation of the internal nodes of the synthesis tree. \\
+        For each node, the number of children (degree $-1$) was collected. A node is multifurcated 
+        if it has more than two children, so we deducted two from each number of children. We have 
+        plotted this in two histograms: number of children $-2$ on the x-axis with log scale and the 
+        number of nodes with this amount on the y-axis.}
+      \label{fig:childrenOfNodes}
+    \end{figure}
+    The multifurcation affects only the internal nodes. We collected the number of children $-2$ of 
+      every node (a node with two children is binary). That means it discribes the number of nodes 
+      which we have lost from the real (binary) phylogenetic tree. \\
+    It can be recognized that we are very far from a binary tree. \\
+
     %---------------------------------------------------------------------------------------------------
@@
     \subsection{Data artifacts}
-      At this point we also found out that there are some nodes with only one child node (55,700 nodes). \\
-      These are both, the most nodes are right in front of a leaf, as well as some nodes are deep in the 
-        tree (3,956 with height $>2$). They are probably a result from the fact that taxonomic information 
-        has been incorporated into a phylogeny. \\
-      Some examples:
+      At this point we also found out that there are nodes with only one child node (55,700 nodes). \\
+      The most of these nodes are next to a leaf node, others are deep in the tree (3,956 with height 
+        $>2$). They are probably a result from the fact that taxonomic information has been incorporated 
+        into a phylogeny. \\
+      \anmerkungstext{probably? Da ist eine Spekulation hier? Kann man das nicht herausfinden? 
+        Spekulieren solltest du am ehesten erst in der Diskussion. (Thilo)} \\
+      Some examples of these nodes are:
       \begin{itemize}
@@
       \end{itemize}
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{Taxa}
-      The investigation of the taxonomy revealed that our tree has three kingdoms: Chloroplastida, 
-        Metazoa, Fungi, 53 phyla, 195 classes and 924 orders. \\
-      Since the analysis of the tree is not part of this work, it should be mentioned here that, 
-        according to recent findings, this is not complete and we lack some taxa in every rank. For 
-        example, Cavalier-Smith says that one distinguishes between seven and nine kingdoms 
-        \cite{CavalierSmith1981}. \\
-      In section \pageref{subsec:listPhyla} of the appendix \colorbox{red}{you} can find a list of all phyla.
 
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Results of simulation / Influence of different parameters}
+  \section{Results of simulation / Influence of different parameters} \label{sec:results of simulation}
 
@@
     %---------------------------------------------------------------------------------------------------
-    \subsection{Biological view}
+    \subsection{Biological view} \label{sec:biological view}
       To analyze the results, we have selected some phyla (sub-trees) to evaluate our results 
@@
       %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{Origins and Losses}
+      \subsubsection{Origins and Losses}
 
@@
     %---------------------------------------------------------------------------------------------------
-    \subsection{Cross evaluation - leave 100 out}
+    \subsection{Cross evaluation - leave 100 out} \label{sec:results cross evaluation}
       We ran the castor algorithm 100 times with leaving 100 randomized free-living or parasitic species 
@@
     Fehler werden durch die prediction eventuell verstärkt...\\
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Data situation}
+
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \subsection{Taxa}
+      The investigation of the taxonomy revealed that the OTL tree has three kingdoms: Chloroplastida, 
+        Metazoa, Fungi, 53 phyla, 195 classes and 924 orders. \\
+      Since the analysis of the tree is not part of this work, it should be mentioned here that, 
+        according to recent findings, this is not complete and we lack some taxa in every rank. For 
+        example, Cavalier-Smith says that one distinguishes between seven and nine kingdoms 
+        \cite{CavalierSmith1981}. \\
+      In section \pageref{subsec:listPhyla} of the appendix is a list of all phyla.
 

### 2018-03-23 Paper - Latex/Paper - Skizze - v4.tex
Paper - Result - AIC vs BIC ...

@@
       For the real data, generalized linear models are compared with poisson respectively binomial 
-        regression according to their residuals and BICs. \\
-      \anmerkungstext{Erklären, warum und wozu das gemacht wird. Warum BIC und nicht AIC? Erklären,
-        was beide bedeuten, wäre sinnvoll. (Thilo)} \\
+        regression according to their residuals. In order to compare models of different complexity, the 
+        BIC (Bayesian Information Criterion) values were calculated in addition to the residuals.\\
+      There are two different information criteria: AIC (Akaike Information Criteria) and BIC. \\
+      The advantage of the BIC is that the penalty is dependent on the sample size and is therefore 
+        advantageous for large samples. \\
 
@@
         and average distance ($\rightarrow$ min, max and mean height). \\
-      The influence in the modeling of these parameters was tested, additive as well as multiplicative.
+      The influence in the modeling of these parameters was tested, additive as well as multiplicative. \\
+
+      For all these calculations, the following R functions were used: \textit{glm()}, \textit{anova()} 
+        and \textit{BIC()}.
+      % https://stat.ethz.ch/R-manual/R-devel/library/stats/html/glm.html
 
@@
     \subsection{Poisson regression of the multifurcation}
-      First of all we measured the strength of the multifurcation with the help of the intercept: 
-        $2.821 > 0$ $\Rightarrow$ there is a multifunction. \\
-      Comparing the different kingdoms, we find that multifunctionality is greater in Fungi than in 
-        Chloroplastida than in Metazoa:
-      $$4.0999 (Fungi Intercept) > -0.9132 (Chloroplastida Intercept) > -1.4320 (Metazoa Intercept)$$
-      % Degrees of Freedom: 96010 Total (i.e. Null);  96010 Residual
-      Then we have 9 times 4 models of different complexity levels.
-      \begin{table}[h!]
-        \begin{center}
-            \begin{tabular}{ |l|r|r|r|r| }
-              \hline
-              Model / Taxa & Kingdom & Phylum & Class & Order \\
-              \hline \hline
-              multifurc $\sim$ taxa & 7774454 & \cellcolor{green!10}7435700 & \cellcolor{green!15}7337241 & \cellcolor{green!30}7076068 \\
-              \hline
-              multifurc $\sim$ taxa + depth & 7752303 & \cellcolor{green!10}7431609 & \cellcolor{green!15}7334754 & \cellcolor{green!30}7027578 \\
-              multifurc $\sim$ taxa + max.height & 7730196 & \cellcolor{green!15}7375889 & \cellcolor{green!20}7275856 & \cellcolor{green!30}7005424 \\
-              multifurc $\sim$ taxa + min.height & \cellcolor{green!10}7472500 & \cellcolor{green!20}7233486 & \cellcolor{green!25}7144686 & \cellcolor{green!40}6890703 \\
-              multifurc $\sim$ taxa + mean.height & \cellcolor{green!15}7304402 & \cellcolor{green!25}7128318 & \cellcolor{green!30}7055313 & \cellcolor{green!40}6815271 \\
-              \hline
-              multifurc $\sim$ taxa * depth & 7714881 & \cellcolor{green!15}7335396 & \cellcolor{green!20}7250759 & \cellcolor{green!40}6843004 \\
-              multifurc $\sim$ taxa * max.height & \cellcolor{green!5}7692980 & \cellcolor{green!15}7311241 & \cellcolor{green!25}7187504 & \cellcolor{green!45}6795823 \\
-              multifurc $\sim$ taxa * min.height & \cellcolor{green!10}7442387 & \cellcolor{green!25}7177002 & \cellcolor{green!30}7094933 & \cellcolor{green!45}6795099 \\
-              multifurc $\sim$ taxa * mean.height & \cellcolor{green!20}7247309 & \cellcolor{green!30}7020258 & \cellcolor{green!35}6965794 & \cellcolor{green!50}6665565 \\
-              \hline
-            \end{tabular}
-        \end{center}
-        \caption{Residuals of multifurcation models}
-        \label{table:Residuals multifurcation} 
-      \end{table}
-      In Table \ref{table:Residuals multifurcation} is a deviance table, where the different residuals 
-        are listed. Since only residuals are comparable in complexity, we have also calculated the BIC 
-        values of the models in table \ref{table:BIC multifurcation}. \\
+      For a regression analysis of the multifurcation first set up a simple generalized linear model and 
+        then output the intercept of it:
+      \lstset{language=R}
+      \begin{lstlisting}[gobble=6]
+        kingdom.furc.mod <- glm(multifurc~kingdom, 
+                                    data=inner.taxa,
+                                        family="poisson")
+        # get the intercept:
+        summary(kingdom.furc.mod)
+      \end{lstlisting}
+      Since the multifurcation can also be 0, the intercept describes the expected mean value and thus, 
+        if it is greater than 0, it says that we have a multifurcation: $2.62 > 0$ $\Rightarrow$ there 
+        is a multifurcation. \\
+      We next compared the intercept of the different kingdoms and found that
+        $$1.22 \text{ (Fungi intercept)} > -0.11 \text{ (Metazoa intercept)} > -0.09 \text{ (Chloroplastida intercept)}$$
+        % Coefficients:
+        %                                         Estimate Std. Error z value Pr(>|z|)
+        % (Intercept)                             2.624897   0.003641  721.00   <2e-16
+        % kingdom['ott352914', 'Fungi']           1.224650   0.004054  302.10   <2e-16
+        % kingdom['ott361838', 'Chloroplastida'] -0.090993   0.003960  -22.98   <2e-16
+        % kingdom['ott691846', 'Metazoa']        -0.114873   0.003732  -30.78   <2e-16
+        that means the strength of the multifurcation \colorbox{red}{is the same/has the same size 
+        sorting}. \todo{kann das sein?} \\
+    %---------------------------------------------------------------------------------------------------
+
+      We investigated several models that could describe multifurcation: \\
+      In doing so, we allowed the different influence of the taxa and the heights and depths of a node 
+        to be included. From this we got 9 times 4 models of different complexity levels (see first row 
+        of table \ref{table:BIC multifurcation}). \\
+      We first compared the models based on their residuals. These give us the error of the model. If 
+        the value is small, our data will be well modeled. These values are meaningful only for the same 
+        complexity, therefore we then calculated the BIC (Bayesian information criterion) values of the 
+        models and used them to evaluate the models.
+      \lstset{language=R}
+      \begin{lstlisting}[gobble=6]
+        anova(kingdom.furc.mod, phylum.furc.mod, class.furc.mod, 
+                      order.furc.mod, family.furc.mod, test="LRT")
+        BIC(kingdom.furc.mod)
+        ...
+      \end{lstlisting}
+      The deviance table with the residuals can be found in the appendix (table 
+        \ref{table:Residuals multifurcation}). Table \ref{table:BIC multifurcation}. lists the BICs.
+
       \begin{table}[h]
@@
         \end{center}
-        \caption{BIC of multifurcation models}
+        \caption{BIC (Bayesian information criterion) values of the multifurcation models \\
+          These models were created with the R function \textit{glm()} and compared with the 
+            \textit{BIC()} function. This results in the listed BIC values.}
         \label{table:BIC multifurcation} 
@@
       % * Residuals: Fehler - wieviele Werte sind nicht gut modelliert. (umso kleiner umso besser - grün) \\
-      The Residuals give us the error of the model. If the value is small, our data will be well modeled. \\
-      Within the complexity classes it can be seen that the mean height gives the best additional factor. \\
-
+      Within the every complexity class it can be seen that the mean height gives the best additional factor. \\
       Despite higher complexity, the BIC values are getting smaller from model to model, meaning that 
@@
         \begin{center}
-          \begin{tabular}{ |l|r|r|r|r| }
-            \hline
-            Model / Taxa & Kingdom & Phylum & Class & Order \\
-            \hline \hline
-            correct predicted $\sim$ taxa & 117877 & 111466 & 108878 & XXXXX \\
-            \hline
-            correct predicted $\sim$ taxa + depth & 117703 & 110513 & XXXXX & XXXXX \\
-            \hline
-            correct predicted $\sim$ taxa * depth & 117592 & 109827 & XXXXX & \cellcolor{green!60}XXXXX \\
+          \begin{tabular}{ |l|r|r|r| }
+            \hline
+            Model / Taxa & Kingdom & Phylum & Class \\% & Order \\
+            \hline \hline
+            correct predicted $\sim$ taxa & 117877 & \cellcolor{green!30}111466 & \cellcolor{green!45}108878 \\% & XXXXX \\
+            \hline
+            correct predicted $\sim$ taxa + depth & 117703 & \cellcolor{green!35}110513 & \cellcolor{green!45}108403 \\% & XXXXX \\
+            \hline
+            correct predicted $\sim$ taxa * depth & 117592 & \cellcolor{green!40}109827 & \cellcolor{green!50}107994 \\% & XXXXX \\
             \hline
@@
         \begin{center}
-          \begin{tabular}{ |l|r|r|r|r| }
-            \hline
-            Model / Taxa & Kingdom & Phylum & Class & Order \\
-            \hline \hline
-            correct predicted $\sim$ taxa & 117936 & 112242 & 111733 & XXXXX \\
-            \hline
-            correct predicted $\sim$ taxa + depth & 117776 & 111304 & 111273 & XXXXX \\
-            \hline
-            correct predicted $\sim$ taxa * depth & 117709 & 111262 & XXXXX & \cellcolor{green!60}XXXXX \\
+          \begin{tabular}{ |l|r|r|r| }
+            \hline
+            Model / Taxa & Kingdom & Phylum & Class \\% & Order \\
+            \hline \hline
+            correct predicted $\sim$ taxa & 117936 & \cellcolor{green!40}112242 & \cellcolor{green!50}111733 \\% & XXXXX \\
+            \hline
+            correct predicted $\sim$ taxa + depth & 117776 & \cellcolor{green!50}111304 & \cellcolor{green!50}111273 \\% & XXXXX \\
+            \hline
+            correct predicted $\sim$ taxa * depth & 117709 & \cellcolor{green!50}111262 & \cellcolor{green!30}113135 \\% & XXXXX \\
             \hline
@@
   %---------------------------------------------------------------------------------------------------
+  \section{Missing internal node modelling - Resiudal table} %\label{sec:Residuals unknown information}
+    \begin{table}[h!]
+      \begin{center}
+          \begin{tabular}{ |l|r|r|r|r| }
+            \hline
+            Model / Taxa & Kingdom & Phylum & Class & Order \\
+            \hline \hline
+            multifurc $\sim$ taxa & 7774454 & \cellcolor{green!10}7435700 & \cellcolor{green!15}7337241 & \cellcolor{green!30}7076068 \\
+            \hline
+            multifurc $\sim$ taxa + depth & 7752303 & \cellcolor{green!10}7431609 & \cellcolor{green!15}7334754 & \cellcolor{green!30}7027578 \\
+            multifurc $\sim$ taxa + max.height & 7730196 & \cellcolor{green!15}7375889 & \cellcolor{green!20}7275856 & \cellcolor{green!30}7005424 \\
+            multifurc $\sim$ taxa + min.height & \cellcolor{green!10}7472500 & \cellcolor{green!20}7233486 & \cellcolor{green!25}7144686 & \cellcolor{green!40}6890703 \\
+            multifurc $\sim$ taxa + mean.height & \cellcolor{green!15}7304402 & \cellcolor{green!25}7128318 & \cellcolor{green!30}7055313 & \cellcolor{green!40}6815271 \\
+            \hline
+            multifurc $\sim$ taxa * depth & 7714881 & \cellcolor{green!15}7335396 & \cellcolor{green!20}7250759 & \cellcolor{green!40}6843004 \\
+            multifurc $\sim$ taxa * max.height & \cellcolor{green!5}7692980 & \cellcolor{green!15}7311241 & \cellcolor{green!25}7187504 & \cellcolor{green!45}6795823 \\
+            multifurc $\sim$ taxa * min.height & \cellcolor{green!10}7442387 & \cellcolor{green!25}7177002 & \cellcolor{green!30}7094933 & \cellcolor{green!45}6795099 \\
+            multifurc $\sim$ taxa * mean.height & \cellcolor{green!20}7247309 & \cellcolor{green!30}7020258 & \cellcolor{green!35}6965794 & \cellcolor{green!50}6665565 \\
+            \hline
+          \end{tabular}
+      \end{center}
+      \caption{Residuals of multifurcation models \\
+        These models were created with the R function \textit{glm()} and compared with the 
+          \textit{anova()} function. This results in the listed residuals.}
+      \label{table:Residuals multifurcation} 
+    \end{table}
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
   \section{Missing leaf state modelling - Resiudal tables}\label{sec:Residuals unknown information}
-
     \begin{table}[h!]

### 2018-03-23 code/metadata/analyse_input.R

@@ -227,13 +227,17 @@ inner.taxa$multifurc <- inner.taxa$nr_children-1
 print('--------------------------------------------------')
 print('-------------------------multifurc data-------------------------')
 print('--------------------------------------------------')
-# null.furc.mod <- glm(multifurc~1, data=inner.taxa,
-#                    family="poisson")
-
+null.furc.mod <- glm(multifurc~1, data=inner.taxa, family="poisson")
+summary(null.furc.mod)
 print('------------------------kingdom - phylum - class - order - family--------------------------')
 
-# kingdom.furc.mod <- glm(multifurc~kingdom, data=inner.taxa,
-#                         family="poisson")
+kingdom.furc.mod <- glm(multifurc~kingdom, data=inner.taxa, family="poisson")
+# get the intercept:
+summary(kingdom.furc.mod)
+summary(kingdom.furc.mod)$kingdom
+print("---")
+mean(inner.taxa$multifurc)
+
 # print(c('BIC=',  BIC(kingdom.furc.mod)))
 
 # phylum.furc.mod <- glm(multifurc~phylum, data=inner.taxa,

### 2018-03-23 Paper - Latex/Paper - Skizze - v4.tex
Paper - Tables with bold header; more data; Binomial regression; Simulation results

@@
     We then evaluated the results in two ways. On the one hand, we have examined the results of some 
-      sub-trees for their credibility with the help of biological background knowledge. On the other 
+      subtrees for their credibility with the help of biological background knowledge. On the other 
       hand, we performed a leaf 100 out cross validation.
@@
   We then evaluated the results in two ways. On the one hand, we have examined the results of some 
-    sub-trees for their credibility with the help of biological background knowledge (Subsection 
+    subtrees for their credibility with the help of biological background knowledge (subsection 
     \ref{sec:biological view}). On the other hand, we performed a leaf 100 out cross validation
@@
           \hline
-          Subtree of & unknown states & multifurcation \\ 
+          \bfseries Subtree of & \bfseries Unknown States & \bfseries Multifurcation \\ 
           \hline \hline
@@
         sorting}. \todo{kann das sein?} \\
-    %---------------------------------------------------------------------------------------------------
 
@@
         complexity, therefore we then calculated the BIC (Bayesian information criterion) values of the 
-        models and used them to evaluate the models.
-      \lstset{language=R}
-      \begin{lstlisting}[gobble=6]
-        anova(kingdom.furc.mod, phylum.furc.mod, class.furc.mod, 
-                      order.furc.mod, family.furc.mod, test="LRT")
-        BIC(kingdom.furc.mod)
-        ...
-      \end{lstlisting}
+        models and used them to evaluate the models. \\
+      % \lstset{language=R}
+      % \begin{lstlisting}[gobble=6]
+      %   anova(kingdom.furc.mod, phylum.furc.mod, class.furc.mod, 
+      %                 order.furc.mod, family.furc.mod, test="LRT")
+      %   BIC(kingdom.furc.mod)
+      %   ...
+      % \end{lstlisting}
       The deviance table with the residuals can be found in the appendix (table 
@@
             \hline
-            Model / Taxa & Kingdom & Phylum & Class & Order \\
+            \bfseries Model / Taxa & \bfseries Kingdom & \bfseries Phylum & \bfseries Class & \bfseries Order \\
             \hline \hline
@@
         \end{center}
-        \caption{BIC (Bayesian information criterion) values of the multifurcation models \\
+        \caption{BIC (Bayesian information criterion) values of the multifurcation models. \\
           These models were created with the R function \textit{glm()} and compared with the 
@@
       Despite higher complexity, the BIC values are getting smaller from model to model, meaning that 
-        the finest model available here is also the best one of these. Smaller taxa than orders (eg 
-        family) were computationally too expensive to calculate.
+        the finest model available here is also the best one of these. Lower taxa than orders (eg 
+        family) were computationally too expensive to calculate. \\
+      The model multifurc $\sim$ order * mean.height turns out to be the best of our models, whereby it 
+        is possible that eg multifurc $\sim$ family * mean.height is better.
 
@@
 
-      Next to the problem of the multifurcation of the tree is the less of data we have for the species.
-        For the ancestral state reconstruction, we need information in the leaf nodes. \\
-      The eukaryotic synthesis tree has 293,463 leaf nodes. The GloBI database has 5 346 414 interactions 
-        (at this timepoint). Out of this data we got 51,337 distinct free-living species and 47 332 
+      Next to the problem of the multifurcation of the tree is the less of interaction data we have for 
+        the species. For the ancestral state reconstruction, we need information about the states 
+        (free-living or parasite) in the leaf nodes. \\
+      The eukaryotic synthesis tree has 293,463 leaf nodes. The GloBI database has 5,346,414 interactions 
+        (at 29.01.2018). Out of this data we got 51,337 distinct free-living species and 47 332 
         distinct parasite species $\rightarrow$ unknown nodes 2,194,794 ($\approx 95.7~\%$). \\
@@
       % \todo{With this only $\approx 4.3~\%$ information in our leaf nodes are ...} \\
+      \todo{discussion!!!} \\
 
@@
       Sankoff. \\
-    We examine different parameters. In figure \ref{fig:influence of unknown data} is an overview of 
-      the results. \\
-    The first column describes the distributions of free-livings and parasites with a given threshold 
-      for the respective simulations to the right. \\
-    The middle column investigates the influence of the unknown states, the right the influence of the 
-      strength of the multifurcation. \\
-    The y-axes indicate the percentage of correctly predicted states (including known states). On the 
-      x-axis the percentage of forgotten states or missing internal nodes. \\
-    Each point corresponds to the average of one hundred simulations, each with 10,000 leaf nodes. \\
-    For the middle column we set the strength of the multifurcations to 0.95~\% similar to the real 
-      data and in the right column the amount of the unknowns to 0.95~\% also similar to the real data. \\
-
-    As \colorbox{red}{you} can see both algortithms are always over 50~\% and therefore better than guessing. Moreover, 
-      they are usually close to each other, with Sankoff always makes better predictions except for 
-      equally distributed states as Fitch. \\
-    \colorbox{red}{You} can see that the distribution of states has a strong influence on the prediction. The more 
-      evenly distributed, the harder it is to predict. \\
-    If more than 60~\% of internal nodes are missing, Fitch breaks significantly in his prediction 
-      compared to Sankoff.
-
+    Figure \ref{fig:influence of unknown data} shows the results of examining various parameters.
+    \begin{figure}[h!]
+      \centering
+      \includegraphics[trim = 0mm 100mm 0mm 0mm, clip, width=\textwidth]{Figures/simulation_evaluation_1.png}
+    \end{figure}
+    ~ \\ ~ \\ ~ \\
     \begin{figure}
       \centering
-      \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{Figures/simulation_evaluation_1.png}
-      \caption{Influence of unknown data to prediction}
+      \includegraphics[trim = 0mm 0mm 0mm 150mm, clip, width=\textwidth]{Figures/simulation_evaluation_1.png}
+      \caption{Influence of unknown data to prediction. \\
+        The first column describes the distributions of free-livings and parasites with a given 
+          threshold for the respective simulations to the right. \\
+        The middle column investigates the influence of the unknown states, the right the influence of
+          the strength of the multifurcation. \\
+        The y-axes indicate the percentage of correctly predicted states (including known states). On 
+          the x-axis the percentage of forgotten states or missing internal nodes. \\
+        Each point corresponds to the average of one hundred simulations, each with 10,000 leaf nodes. \\
+        For the middle column we set the strength of the multifurcations to 0.95~\% similar to the 
+          real data and in the right column the amount of the unknowns to 0.95~\% also similar to the 
+          real data.}
       \label{fig:influence of unknown data}
     \end{figure}
-
-    In the end, Sankoff is in most cases the more accurate algortihmus and was therefore used for our 
-      prediction of the real data.
+    First, we tested different trasition probability distributions including threshold (first column). 
+      It can be observed that the more balanced the percentages of free-livings and parasites, the 
+      worse the prediction of the algorithms (second and third column). \\
+    It can be seen that both algortithms are always over 50~\% prediction and therefore better than 
+      guessing. Moreover, they are usually close to each other, with Sankoff always makes better 
+      predictions except for equally distributed states as Fitch. \\
+    On the other hand, we examined the influence of missing internal nodes (ridge of multifurcation) 
+      and missing leaf node information (unknown leaf nodes). \\
+    Both factors have a relatively linear influence on the Sankoff method. Fitch, on the other hand, 
+      breaks significantly in his prediction from about 70\% unknown leaf nodes or mutifurcation. \\
+
+    Since we have a lot of missing data in most subtrees (both internal nodes and state informations), 
+      the Sankoff gives a better prediction and was thus used for real data analysis.
 
@@
   \section{Results of the real data analysis created with Sankoff}
+    This section is about evaluating the prediction of real data using the Sankoff method. \\
+    It is divided into two subsections. \ref{sec:biological view}: The analysis of some subtrees using 
+      biological background knowledge. \ref{sec:results cross evaluation}: Presentation of the results 
+      of the leaf 100 out cross validation.
 
@@
     \subsection{Biological view} \label{sec:biological view}
-      To analyze the results, we have selected some phyla (sub-trees) to evaluate our results 
+      To analyze the results, we have selected some phyla (subtrees) to evaluate our results 
         selectively from the biological point of view: Chordata, Nematoda, Platyhelminthes and 
@@
             \hline
-            & & \multicolumn{2}{c||}{original states} & \multicolumn{4}{c|}{final states} \\
-            Phylum & \# nodes       & FL & P              & 0 (FL) & 0.3 & 0.5 & 1 (P) \\
+            & & \multicolumn{2}{c||}{\bfseries original states} & \multicolumn{4}{c|}{\bfseries final states} \\
+            \bfseries Phylum & \bfseries \# nodes & \bfseries FL & \bfseries P & \bfseries 0 \bfseries (FL) & \bfseries 0.3 &\bfseries  0.5 & \bfseries 1 (P) \\
             \hline \hline
@@
         0.1~\% free-livings and predicted 0.77~\% as free-living spezies. \\
-    %---------------------------------------------------------------------------------------------------
 
@@
             \hline
-            & & \multicolumn{2}{c||}{original states} & \multicolumn{6}{c|}{final states} \\
-            Phylum & \# nodes & FL & P
-              & 0 (FL) & 0.4 & 0.5 & 0.67 & 0.75 & 1 (P) \\
+            & & \multicolumn{2}{c||}{\bfseries original states} & \multicolumn{6}{c|}{\bfseries final states} \\
+            \bfseries Phylum & \bfseries \# nodes & \bfseries FL & \bfseries P
+              & \bfseries 0 (FL) & \bfseries 0.4 & \bfseries 0.5 & \bfseries 0.67 & \bfseries 0.75 & \bfseries 1 (P) \\
             \hline \hline
@@
             \hline
-            & & \multicolumn{2}{c||}{original states} & \multicolumn{8}{c|}{final states} \\
-            Kingdom & \# nodes & FL & P
-              & 0 (FL) & 0.25 & 0.33 & 0.4 & 0.5 & 0.67 & 0.75 & 1 (P) \\
+            & & \multicolumn{2}{c||}{\bfseries original states} & \multicolumn{8}{c|}{\bfseries final states} \\
+            \bfseries Kingdom & \bfseries \# nodes & \bfseries FL & \bfseries P
+              & \bfseries 0 (FL) & \bfseries 0.25 & \bfseries 0.33 & \bfseries 0.4 & \bfseries 0.5 & \bfseries 0.67 & \bfseries 0.75 & \bfseries 1 (P) \\
             \hline \hline
@@
               \hline
-              Domain  & \# internal & \# leaf & Rootnode & \multicolumn{2}{c|}{without and with rounding} \\ 
-              / Kingdom  & \multicolumn{2}{c||}{nodes} & state & \# origins & \# losses \\
-              / Phylum / Class & & & & (FL -> P) & (P -> FL) \\
+              \bfseries Domain  & \bfseries \# internal & \bfseries \# leaf & \bfseries Rootnode & \multicolumn{2}{c|}{\bfseries without and with rounding} \\ 
+              \bfseries / Kingdom  & \multicolumn{2}{c||}{\bfseries nodes} & \bfseries state & \bfseries \# origins & \bfseries \# losses \\
+              \bfseries / Phylum / Class & & & & \bfseries (FL -> P) & \bfseries (P -> FL) \\
               \hline \hline
@@
             \hline
-            Model / Taxa & Kingdom & Phylum & Class \\% & Order \\
+            \bfseries Model / Taxa &\bfseries  Kingdom & \bfseries Phylum & \bfseries Class \\% & Order \\
             \hline \hline
@@
             \hline
-            Model / Taxa & Kingdom & Phylum & Class \\% & Order \\
+            \bfseries Model / Taxa & \bfseries Kingdom & \bfseries Phylum & \bfseries Class \\% & Order \\
             \hline \hline
@@
       \end{table}
+
+      Lower taxa than classes (eg order) were computationally too expensive to calculate. \\
 
@@
             \hline
-            & & min & max & mean & variance ($\sigma^2$) & $\sigma$ \\
+            & & \bfseries min & \bfseries max & \bfseries mean & \bfseries variance ($\sigma^2$) & $\sigma$ \\
             \hline \hline
@@
             \hline
-            & & min & max & mean & variance \\
+            & & \bfseries min & \bfseries max & \bfseries mean & \bfseries variance \\
             \hline \hline
@@
           \hline
-          Taxa & Model / Effects & min & max & mean & median \\
+          \bfseries Taxa & \bfseries Model / Effects & \bfseries min & \bfseries max & \bfseries mean & \bfseries median \\
           \hline \hline
@@
           \hline
-          Taxa & Number of Nodes & Internal Nodes & Leaf Nodes & Terminal Leaf Nodes \\
+          \bfseries Taxa & \bfseries Number of Nodes & \bfseries Internal Nodes & \bfseries Leaf Nodes & \bfseries Terminal Leaf Nodes \\
           \hline \hline
@@
           \hline
-          Kingdom (3) & Number of Nodes & Phylum (25) & Number of Nodes & max max height \\
+          \bfseries Kingdom (3) & \bfseries Number of Nodes & \bfseries Phylum (25) & \bfseries Number of Nodes & \bfseries max max height \\
           \hline \hline
@@
           \hline
-          Model / Taxa & Kingdom & Phylum & Class \\
+          \bfseries Model / Taxa & \bfseries Kingdom & \bfseries Phylum & \bfseries Class \\
           \hline \hline

### 2018-03-23 code/simulation/get_plots.py

@@ -150,7 +150,7 @@ def plot_hist(percentage_parasites):
     plt.legend(handles=[blue_patch, red_patch, black_line], title=title, loc="upper right", fontsize=9) # shadow=True, fancybox=True)
     ax.get_legend().get_title().set_fontweight("bold")
     plt.axis([0, 1, 0, 8])
-    if PLOT_NUMBER == 14:
+    if (PLOT_NUMBER == 14) or (PLOT_NUMBER == 8):
         plt.xlabel('drawn random number', fontsize=9)
     plt.grid(True)
 
@@ -174,7 +174,7 @@ def plot_data_unknown(percentage_parasites):
         label='Sankoff', linewidth=0.5, marker='.', markerfacecolor='black')
     plt.legend(loc="lower left", fontsize=9) #, scatterpoints=1, numpoints=2)
     plt.axis([0, 1, 50, 100])
-    if PLOT_NUMBER == 15:
+    if (PLOT_NUMBER == 15) or (PLOT_NUMBER == 9):
         plt.xlabel('percentage unknown', fontsize=9)
     # else:
     #     plt.xticks([])
@@ -202,7 +202,7 @@ def plot_data_multifurc(percentage_parasites):
     else: 
         plt.legend(loc="upper left", fontsize=9) #, scatterpoints=1, numpoints=2)
     plt.axis([0, 1, 50, 100])
-    if PLOT_NUMBER == 16:
+    if (PLOT_NUMBER == 16) or (PLOT_NUMBER == 10):
         plt.xlabel('percentage multifurcation', fontsize=9)
     # else:
     #     plt.xticks([])

### 2018-03-24 Paper - Latex/Paper - Skizze - v4.tex
Paper - Results - Biological view: refine text

@@
       In Table \ref{table:phylum leaf nodes states} we compare the given states with the predicted ones. \\
-      There are several factors that play a role here, and in part, crystallize in these examples. \\
-      An important factor here is that the credibility of the results with the accuracy of the input 
-        data, i. the data of GloBI, stands and falls. Errors of incorrect input data can be amplified by 
-        incorrect prediction of unknown species and can be reversed in order to improve the data 
-        situation of GloBI. \\
+      Several factors such as the distribution of existing input data via parasitics and free-livings, 
+        faulty input data from GloBI and reinforcement of errors by multifurcation play an important 
+        role, which crystallize out in these examples. \\
+      An important factor here is that the credibility of the results. The accuracy of the input data 
+        stands and falls with the presence and the correctness of the data of GloBI. Errors of incorrect 
+        input data can be amplified by incorrect prediction of unknown species and can be reversed in 
+        order to improve the data situation of GloBI. \\
       Since we look at such large trees we can not expect to know all the parasites, so we look at 
-        individual positives. Positive in the sense that the majority have the opposite state.
-
-      \begin{table}[h]
+        individual positives. This is positive in the sense that the majority have the opposite state.
+
+      \begin{table}
         \begin{center}
@@
         \end{center}
-        \caption{Phylum (leaf nodes)}
+        \caption{Some selected phyla (subtrees), only leaf nodes, were examined for the evolution 
+          of the amount and percentage of given data to predicted data.}
         \label{table:phylum leaf nodes states} 
@@
 
-      In contrast to the other phyla examined, the phylogeny is more pronounced (less multifurcation) (see 
-        Table \ref{table:percentage loss information subtrees}). This results in a weaker spread of errors. 
-        This is reflected in the results from the table \ref{table:phylum leaf nodes states}. There are 18 
-        parasites as input data and only 8 more are predicted. The chordata mostly consist of free-living 
-        species, so this seems believable. We started with 99.83~\%  species and predict 99.97~\% species 
-        as free-living (including already known nodes). \todo{A few punctual tests give us the following:}
+      In contrast to the other phyla examined, the phylogeny in the Chordata is more pronounced (less 
+        multifurcation) (see Table \ref{table:percentage loss information subtrees}). This results in 
+        less variance of errors. What is reflected in the results from the table 
+        \ref{table:phylum leaf nodes states}. There are 18 parasites as input data and only 8 more are 
+        predicted. The Chordata mostly consist of free-living species, so this seems believable. We 
+        started with 99.83~\%  species and predict 99.97~\% species as free-living (including already 
+        known nodes).
 
@@
         \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.85\textwidth]{Figures/ChordataParasites.png}
-        \caption{Parasites of Phylum: Chordata \\ 
-          Input parasites (green) $\rightarrow$ predicted parasites (white $\rightarrow$ green)}
+        \caption{Parasites of Phylum: Chordata. \\
+          All parasite data of the chordata were mapped into a rough taxonomy (phylum, class, order, 
+            family) in order to understand their distribution and affiliation. \\
+          The internal nodes are the wanted taxa from OTL (with the addition of \# input parasites to 
+            $\rightarrow$ \# predicted parasites). \\
+          The leaf nodes are the input parasites (green) and the predicted parasites (white $\rightarrow$ 
+            green).}
         \label{fig:ChordataParasites}
@@
 
-      We mapped the few parasitic spezies in a rough taxonomy (see Figure \ref{fig:ChordataParasites}): \\
+      We mapped the few parasitic species in a \colorbox{red}{rough/simple} taxonomy (see Figure \ref{fig:ChordataParasites}): \\
       Known parasitic birds belong to the order Sauria. Here we know from Rothschild  here there are 
@@
         known as broodparasite and some others. \\
-      An example of the amplification of mistakes here are the carp. There seems to be a paper from the 
-        GloBI concluding: Grass carp (\textit{Ctenopharyngodon idella)} has Pathogen common carp 
+      An example of the amplification of mistakes here are the carp. There is a paper from which GloBI 
+        concludes: Grass carp (\textit{Ctenopharyngodon idella)} has Pathogen common carp 
         (\textit{Cyprinus carpio})\footnote{
@@
         considered subtrees, see Table \ref{table:percentage loss information subtrees}. We start with 
-        0.1~\% free-livings and predicted 0.77~\% as free-living spezies. \\
+        0.1~\% free-livings and predicted 0.77~\% as free-living species. \\
 
@@
         Nematoda. \\
-      The problem at this point, however, is obvious: Hallan speaks of the fact that only 23,00 species 
-        were described by the Nematoda but one assumes 1 million or more\footnote{J. Hallan, unpublished; 
+      The problem at this point, however, is: Hallan speaks of the fact that only 23,000 species 
+        were described by the Nematoda but is it assumed that one million or more species are in this 
+        phylum.\footnote{J. Hallan, unpublished; 
           \hyperlink{https://insects.tamu.edu/research/collection/hallan/}
@@
         }. \todo{Link ist nicht erreichbar!} The parasites have been much more studied and thus we start 
-        with only 0.63~\% free-living species. Against such a shifted data situation, the algorithm is 
-        almost powerless. And yet the percentage has increased. \\
+        with only 0.63~\% (table \ref{table:phylum leaf nodes states}) free-living species. Against such 
+        a shifted data situation, the algorithm is almost powerless to make correct predictions. And yet 
+        the percentage has increased to 5.34~\%. \\
 
@@
         \end{center}
-        \caption{Phylum (inkl internal nodes)}
+        \caption{Some selected phyla (subtrees), including internal nodes, were examined for the evolution 
+        of the amount and percentage of given data to predicted data.}
         \label{table:Phylum internal nodes}
@@
         \end{center}
-        \caption{Kingdom (leaf nodes)}
+        \caption{All kingdoms (subtrees), only leaf nodes, were examined for the evolution of the 
+          amount and percentage of given data to predicted data.}
         \label{table:Kingdom leaf nodes}
@@
         \end{center}
-        \caption{Kingdom (inkl internal nodes)}
+        \caption{All kingdoms (subtrees), inkluding internal nodes, were examined for the evolution of the 
+        amount and percentage of given data to predicted data.}
         \label{table:Kingdom internal nodes}
@@
         Here we have encountered a problem: The Castor algorithm gives us probabilities for states. That 
-          means there are also nodes with state like 0.3 or 0.5. So how do \colorbox{red}{you} count? Our solution was, 
-          to round these values. We have to say that we round 0.5 to 0.
+          means there are also nodes with state like 0.3 or 0.5. The question is, how to count these state 
+          changes. We decided to round the values.
+        % \begin{lstlisting}[gobble=6]
+        %   possible tags: 0, 0.333, 0.4, 0.5, 0.667, 0.75, 1
+        %   rounded to:    0  0      0    0    1      1     1
+        % \end{lstlisting}
 
@@
 
-        Lets have a look at the same phyla as in the section before: Chordata, Nematoda, 
+        When more closely regarding the same phyla as in the section before: Chordata, Nematoda, 
           Platyhelminthes and Apicomplexa. \\
@@
         and mostly all species are predicted as free-living. \\
-        In Apicomplexa and the Platyhelminthes are looking fine too. Our algorithm gives us only one loss 
-          of parasitism in Apicomplexa and five in the Platyhelminthes. They are both from the root over 
+        In Apicomplexa and the Platyhelminthes also look credible. Our algorithm gives us only one loss of
+          parasitism in Apicomplexa and five in the Platyhelminthes. They are both from the root over
           mostly all species predicted as parasites. \\
@@
           size as Blaxter.
-
-        \begin{lstlisting}[gobble=6]
-          possible tags: 0, 0.333, 0.4, 0.5, 0.667, 0.75, 1
-          rounded to:    0  0      0    0    1      1     1
-        \end{lstlisting}
-
-        % \begin{lstlisting}[gobble=6]
-        %   # possible tags: 0, 0.333, 0.4, 0.5, 0.667, 0.75, 1
-        %   # rounded to:    0  0      0    0    1      1     1
-        %   if node_state != father_state:
-        %     if father_state == 0:
-        %         origins += 1        # FL -> P
-        %         new_found = True
-        %     else:
-        %         losses += 1         # P -> FL
-        %         new_found = True
-        % \end{lstlisting}
-
-        % \todo{without rounding change else: to elif $father_state == 1$}
 

### 2018-03-24 Paper - Latex/Paper - Skizze - v4.tex
Paper - Results - Cross validation: refine text

@@
   For the 2,535,437 leaf nodes we could not gather much data. From the GloBI database 
-    \cite{Poelen2014} which we used, we could only collect 25,992 parasitic and 34,879 
-    free-living species. It follows that we have only $\approx 2.4~\%$ state information. \\
+    \cite{Poelen2014} which we used, we could only collect 25,992 parasitic and 34,879 free-living 
+    species. It follows that we have $\approx 2.4~\%$ state information. \\
   So far, especially small scale studies have been carried out or highly manual. In this scale, it 
@@
       \item run castor algorithm / and others?
-      \item interprete results (cross validation - leave 100 out)
+      \item interprete results (leave-100-out cross validation)
     \end{itemize}
@@
       subtrees for their credibility with the help of biological background knowledge. On the other 
-      hand, we performed a leaf 100 out cross validation.
+      hand, we performed a leave-100-out cross validation.
 
@@
     subtrees for their credibility with the help of biological background knowledge (subsection 
-    \ref{sec:biological view}). On the other hand, we performed a leaf 100 out cross validation
-    (Subsection \ref{sec:results cross evaluation}).
-
-  % The next sections now guide you through the results of these different steps.
+    \ref{sec:biological view}). On the other hand, we performed a leave-100-out cross validation
+    (Subsection \ref{sec:results - cross validation}) and predicted approximately 98.17~\% states 
+    correct.
 
@@
         family) were computationally too expensive to calculate. \\
-      The model multifurc $\sim$ order * mean.height turns out to be the best of our models, whereby it 
-        is possible that eg multifurc $\sim$ family * mean.height is better.
+      The model \textit{multifurc $\sim$ order * mean.height} turns out to be the best of our models, 
+        whereby it is possible that eg \textit{multifurc $\sim$ family * mean.height} is better.
 
@@
         (at 29.01.2018). Out of this data we got 51,337 distinct free-living species and 47 332 
-        distinct parasite species $\rightarrow$ unknown nodes 2,194,794 ($\approx 95.7~\%$). \\
+        distinct parasite species for the whole tree of life. From the Eukaryota we could determine 
+        25,992 and 34,879 species as parasites and free-living. With 2,293,463 leaf nodes we still have 
+        about 97.34~\% unknown leaf nodes. \\
       We found also 57,352 (not distinct!) source species and 809,993 (not distinct!) target
         species without OTT ids. Since we currently use only OTT ids, we could not use this information. \\        
-      % \todo{With this only $\approx 4.3~\%$ information in our leaf nodes are ...} \\
       \todo{discussion!!!} \\
@@
         \end{center}
-        \caption{BICs of unknown information}
+        \caption{BIC (Bayesian information criterion) values unknown state information models. \\
+          These models were created with the R function \textit{glm()} and compared with the 
+            \textit{BIC()} function. This results in the listed BIC values.}
         \label{table:BIC unknown information} 
@@
     It is divided into two subsections. \ref{sec:biological view}: The analysis of some subtrees using 
-      biological background knowledge. \ref{sec:results cross evaluation}: Presentation of the results 
-      of the leaf 100 out cross validation.
+      biological background knowledge. \ref{sec:results - cross validation}: Presentation of the results 
+      of the leave-100-out cross validation.
 
@@
 
-      \begin{figure}[h!]
+      \begin{figure}
         \centering
@@
         % \begin{lstlisting}[gobble=6]
-        %   possible tags: 0, 0.333, 0.4, 0.5, 0.667, 0.75, 1
+        %   possible states: 0, 0.333, 0.4, 0.5, 0.667, 0.75, 1
         %   rounded to:    0  0      0    0    1      1     1
@@
     %---------------------------------------------------------------------------------------------------
-    \subsection{Cross evaluation - leave 100 out} \label{sec:results cross evaluation}
-      We ran the castor algorithm 100 times with leaving 100 randomized free-living or parasitic species 
-        out of the input data to see how stable our result is. Of these 10,000 nodes, 9,238 were unique. 
-        Of that, we predicted 9060 ($\approx 98.17~\%$) correctly and 169 ($\approx 1.82~\%$) wrongly, 
-        with duplicate draws always having the same prediction. \\
-      What is the best way to model this data? We again tested the influence of the taxa and the depth 
-        of leaf nodes and calculated the BICs (Table: \ref{table:BIC cross validation}).
+    \subsection{Leave-100-out cross validation} \label{sec:results - cross validation}
+      For a further validation of our results, we carried out a leave-100-out cross validation. \\
+      In order to achieve about 15\% of the 60,871 input node states with a validation, 
+        we randomly left out 100 states 100 times. To make smaller amounts up to leave-one-out had too 
+        much computational effort. \todo{warum 15\%?}\\
+
+      Of these 10,000 nodes, 9,238 were unique. From the unique nodes, we predicted approximately 
+        98.17~\% correct and thus 1.82~\% wrong, with duplicate draws always having the same prediction 
+        (data not shown). \\
+
+      We have again dealt with the question of how this data is best modeled. The influence of the taxa 
+        (kingdom, phylum, class) and the depth of the leaf nodes was re-modeled and the BICs compared 
+        (table \ref{table:BIC cross validation}). Lower taxa than classes (eg order) were 
+        computationally too expensive to calculate. \\
+      The Residuals are included in the appendix (table \ref{table:Residuals cross validation}) for the 
+        sake of completeness; here too, due to the different complexity, they do not have much meaning 
+        for the comparison of the models. \\
+
+      \todo{table for these numbers?}
+      % 100/(25992+34879)*10000 = 16.43
+      % 100/(25992+34879)*9238 = 15.18
+      % 10000 nodes 9238 unique
+      % 9060 nodes $\approx 98.17~\%$ correctly predicted
+      % 169 ($\approx 1.82~\%$) wrongly predicted
 
@@
             \hline
-            \bfseries Model / Taxa &\bfseries  Kingdom & \bfseries Phylum & \bfseries Class \\% & Order \\
-            \hline \hline
-            correct predicted $\sim$ taxa & 117877 & \cellcolor{green!30}111466 & \cellcolor{green!45}108878 \\% & XXXXX \\
-            \hline
-            correct predicted $\sim$ taxa + depth & 117703 & \cellcolor{green!35}110513 & \cellcolor{green!45}108403 \\% & XXXXX \\
-            \hline
-            correct predicted $\sim$ taxa * depth & 117592 & \cellcolor{green!40}109827 & \cellcolor{green!50}107994 \\% & XXXXX \\
+            \bfseries Model / Taxa & \bfseries Kingdom & \bfseries Phylum & \bfseries Class \\% & Order \\
+            \hline \hline
+            correct predicted $\sim$ taxa & 117936 & \cellcolor{green!40}112242 & \cellcolor{green!50}111733 \\% & XXXXX \\
+            \hline
+            correct predicted $\sim$ taxa + depth & 117776 & \cellcolor{green!50}111304 & \cellcolor{green!50}111273 \\% & XXXXX \\
+            \hline
+            correct predicted $\sim$ taxa * depth & 117709 & \cellcolor{green!50}111262 & \cellcolor{green!30}113135 \\% & XXXXX \\
             \hline
@@
         \end{center}
-        \caption{Residuals of cross validation prediction}
-        \label{table:Residuals cross validation} 
-      \end{table}
-
-      \begin{table}[h]
-        \begin{center}
-          \begin{tabular}{ |l|r|r|r| }
-            \hline
-            \bfseries Model / Taxa & \bfseries Kingdom & \bfseries Phylum & \bfseries Class \\% & Order \\
-            \hline \hline
-            correct predicted $\sim$ taxa & 117936 & \cellcolor{green!40}112242 & \cellcolor{green!50}111733 \\% & XXXXX \\
-            \hline
-            correct predicted $\sim$ taxa + depth & 117776 & \cellcolor{green!50}111304 & \cellcolor{green!50}111273 \\% & XXXXX \\
-            \hline
-            correct predicted $\sim$ taxa * depth & 117709 & \cellcolor{green!50}111262 & \cellcolor{green!30}113135 \\% & XXXXX \\
-            \hline
-          \end{tabular} 
-        \end{center}
-        \caption{BICs of cross validation prediction}
+        \caption{BIC (Bayesian information criterion) values of cross validation prediction models. \\
+          These models were created with the R function \textit{glm()} and compared with the 
+            \textit{BIC()} function. This results in the listed BIC values.}
         \label{table:BIC cross validation} 
@@
 
-      Lower taxa than classes (eg order) were computationally too expensive to calculate. \\
-
-      What could happen by removing a parasite or free-living of the list?
-      \begin{itemize}
-        \item It could be a specie, which don't exist in the tree leaf nodes. -> no effect
-        \item It could be a specie, which exists in both lists. -> If it was a parasite, it is now 
-          free-living, because we prefer parasites. Otherwise we have no effect again. (1053 are possible)
-        \item Normal case: We loose information, because its a specie in our tree and we change it to a 
-          leave node with no information.
-      \end{itemize}
-
-      Influence on the rest of the data:
-      \begin{table}
+      The BIC values this time did not prove that the finest model is the best. Of our calculated models, 
+       \textit{correct predicted $\sim$ phylum * depth} has the smallest value. \\
+
+      We examined the influence of the omitted data on the prediction. On average, about twice as many 
+        leaf nodes are predicted differently. \color{red}The variance is very high. This means that 
+        we have a high degree of dispersion and thus a stochastic situation exists. It also describes 
+        the width of the present probability function. The standard deviation is about five times as 
+        high as the number of omitted nodes, so the variability is quintupled. \normalfont Table 
+        \ref{table:statistics cross validation} shows these results. \\
+      \begin{table}[h!]
         \begin{center}
@@
             \hline \hline
-            \multirow{3}{*}{distance} & all   & 0 & 3587.70 & 224.96 & 313650.61 & 560.05 \\
-            & leaf nodes                      & 0 & 3021.12 & 208.69 & 248103.38 & 498.10 \\
-            & internal nodes                  & 0 & 566.58 & 16.28 & 4927.95 & 70.20 \\ \hline
-            \multicolumn{2}{|c||}{changed tag} & 0 & 0 & 0 & 0 & 0 \\ \hline
-            \multirow{3}{*}{lost} & all tags  & 100 & 100 & 100 & 0 & 0 \\
-            & FL tags                         & 44 & 66 & 57.25 & 19.50 & 4.42 \\
-            & P tags                          & 34 & 56 & 42.75 & 19.50 & 4.42 \\
+            \multirow{3}{*}{\bfseries distance} & \bfseries all     & 0 & 3587.70 & 224.96 & 313650.61 & 560.05 \\
+            & \bfseries leaf nodes                                  & 0 & 3021.12 & 208.69 & 248103.38 & 498.10 \\
+            & \bfseries internal nodes                              & 0 & 566.58 & 16.28 & 4927.95 & 70.20 \\ \hline
+            \multirow{3}{*}{\bfseries lost} & \bfseries all states  & 100 & 100 & 100 & 0 & 0 \\
+            & \bfseries FL states                                   & 44 & 66 & 57.25 & 19.50 & 4.42 \\
+            & \bfseries P states                                    & 34 & 56 & 42.75 & 19.50 & 4.42 \\
             \hline
@@
         \end{center}
-        \caption{Statistics to Cross validation}
+        \caption{Statistics about the leave-100-out cross validation \\
+          The distance between original and new states was calculated using the Euclidean metric. This 
+            was summed over all states / all leaf node states and all internal node states. \\
+          The lower half of the table describes the distribution of the 'lost' states between parasites 
+            (P) and free-livings (FL).}
+        \label{table:statistics cross validation}
       \end{table}
-
-      \begin{table}
-        \begin{center}
-          \begin{tabular}{ |cl||r|r|r|r| }
-            \hline
-            & & \bfseries min & \bfseries max & \bfseries mean & \bfseries variance \\
-            \hline \hline
-            \rowcolor{green!50}distance & all   & 1 & 2 & 1.33 & 0.33 \\
-            \rowcolor{orange!50}&               & 0 & 3587.70 & 217.94 & 273760.68 \\
-            \rowcolor{green!50}& leaf nodes     & 1 & 2 & 1.33 & 0.33 \\
-            \rowcolor{orange!50}&               & 0 & 3021.12 & 202.57 & 209274.86 \\
-            \rowcolor{green!50}& internal nodes& 0 & 0 & 0.00 & 0.00 \\
-            \rowcolor{orange!50}&               & 0 & 566.58 & 15.37 & 5684.00 \\ \hline
-            \rowcolor{green!50}lost & FL tags   & 44 & 49 & 46.67 & 6.33 \\
-            \rowcolor{orange!50}&               & 51 & 66 & 57.95 & 13.47 \\
-            \rowcolor{green!50}& P tags         & 51 & 56 & 53.33 & 6.33 \\
-            \rowcolor{orange!50}&               & 34 & 49 & 42.05 & 13.47 \\
-            \hline
-          \end{tabular}
-        \end{center}
-        \caption{Statistics to Cross validation \\
-          - \colorbox{green!50}{Less free-livings - 3 examples} \\
-          - \colorbox{orange!50}{Less parasites - 64 examples}}
-      \end{table}
+    %---------------------------------------------------------------------------------------------------
+
+      % \begin{table}
+      %   \begin{center}
+      %     \begin{tabular}{ |cl||r|r|r|r| }
+      %       \hline
+      %       & & \bfseries min & \bfseries max & \bfseries mean & \bfseries variance \\
+      %       \hline \hline
+      %       \rowcolor{green!50}distance & all   & 1 & 2 & 1.33 & 0.33 \\
+      %       \rowcolor{orange!50}&               & 0 & 3587.70 & 217.94 & 273760.68 \\
+      %       \rowcolor{green!50}& leaf nodes     & 1 & 2 & 1.33 & 0.33 \\
+      %       \rowcolor{orange!50}&               & 0 & 3021.12 & 202.57 & 209274.86 \\
+      %       \rowcolor{green!50}& internal nodes& 0 & 0 & 0.00 & 0.00 \\
+      %       \rowcolor{orange!50}&               & 0 & 566.58 & 15.37 & 5684.00 \\ \hline
+      %       \rowcolor{green!50}lost & FL states & 44 & 49 & 46.67 & 6.33 \\
+      %       \rowcolor{orange!50}&               & 51 & 66 & 57.95 & 13.47 \\
+      %       \rowcolor{green!50}& P states       & 51 & 56 & 53.33 & 6.33 \\
+      %       \rowcolor{orange!50}&               & 34 & 49 & 42.05 & 13.47 \\
+      %       \hline
+      %     \end{tabular}
+      %   \end{center}
+      %   \caption{Statistics to cross validation \\
+      %     - \colorbox{green!50}{Less free-livings - 3 examples} \\
+      %     - \colorbox{orange!50}{Less parasites - 64 examples}}
+      % \end{table}
 
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Missing leaf state modelling - Resiudal tables}\label{sec:Residuals unknown information}
+  \section{Missing leaf state modelling - Resiudal table}\label{sec:Residuals unknown information}
     \begin{table}[h!]
@@
       \end{center}
-      \caption{Residuals of unknown information}
+      \caption{Residuals of unknown information models \\
+        These models were created with the R function \textit{glm()} and compared with the 
+          \textit{anova()} function. This results in the listed residuals.}
     \end{table}
 
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Cross validation prediction - Resiudal table}
+    \begin{table}[h]
+      \begin{center}
+        \begin{tabular}{ |l|r|r|r| }
+          \hline
+          \bfseries Model / Taxa &\bfseries  Kingdom & \bfseries Phylum & \bfseries Class \\% & Order \\
+          \hline \hline
+          correct predicted $\sim$ taxa & 117877 & \cellcolor{green!30}111466 & \cellcolor{green!45}108878 \\% & XXXXX \\
+          \hline
+          correct predicted $\sim$ taxa + depth & 117703 & \cellcolor{green!35}110513 & \cellcolor{green!45}108403 \\% & XXXXX \\
+          \hline
+          correct predicted $\sim$ taxa * depth & 117592 & \cellcolor{green!40}109827 & \cellcolor{green!50}107994 \\% & XXXXX \\
+          \hline
+        \end{tabular} 
+      \end{center}
+      \caption{Residuals of cross validation prediction \\
+        These models were created with the R function \textit{glm()} and compared with the 
+          \textit{anova()} function. This results in the listed residuals.}
+      \label{table:Residuals cross validation} 
+    \end{table}
+
 \end{document}

### 2018-03-24 Paper - Latex/Paper - Skizze - v4.tex
Paper - Discussion - Simulation

@@
         parasites and 60~\% free-livings which is based on the estimates by Windsor \cite{Windsor1998} 
-        and $\mathcal{P}(FL \rightarrow P) > \mathcal{P}(P \rightarrow FL)$, because a reverse mutation 
-        is usually less likely. \todo{This is discussed in section x of the discussion.} \\
+        and $\mathcal{P}(FL \rightarrow P) = \mathcal{P}(P \rightarrow FL)$, as a result of the 
+        diversity of parasites and the lack of general determinations for this. These parameters are 
+        debated in subsection \ref{sec:discussion - transition probabilities} of the discussion. \\
 
@@
     To get a random binary tree, the Phylo package from biopython is used \cite{Cock2009}. They offer 
-      a randomized function which returns a BaseTree\footnote{
+      a \textit{randomized()} function which returns a BaseTree\footnote{
         \hyperlink{https://github.com/biopython/biopython/blob/master/Bio/Phylo/BaseTree.py}
         {https://github.com/biopython/biopython/blob/master/Bio/Phylo/BaseTree.py}
-      }. \\
-    \todo{ref in die discussion über die randomized function? Diskutieren wir das?}
+      }. The credibility of this choice is examined in subsection 
+        \ref{sec:discussion - simulate phylogeny} of the discussion.\\
 
@@
         the width of the present probability function. The standard deviation is about five times as 
-        high as the number of omitted nodes, so the variability is quintupled. \normalfont Table 
+        high as the number of omitted nodes, so the variability is quintupled. \color{black} Table 
         \ref{table:statistics cross validation} shows these results. \\
@@
       \end{table}
-    %---------------------------------------------------------------------------------------------------
-
-      % \begin{table}
-      %   \begin{center}
-      %     \begin{tabular}{ |cl||r|r|r|r| }
-      %       \hline
-      %       & & \bfseries min & \bfseries max & \bfseries mean & \bfseries variance \\
-      %       \hline \hline
-      %       \rowcolor{green!50}distance & all   & 1 & 2 & 1.33 & 0.33 \\
-      %       \rowcolor{orange!50}&               & 0 & 3587.70 & 217.94 & 273760.68 \\
-      %       \rowcolor{green!50}& leaf nodes     & 1 & 2 & 1.33 & 0.33 \\
-      %       \rowcolor{orange!50}&               & 0 & 3021.12 & 202.57 & 209274.86 \\
-      %       \rowcolor{green!50}& internal nodes& 0 & 0 & 0.00 & 0.00 \\
-      %       \rowcolor{orange!50}&               & 0 & 566.58 & 15.37 & 5684.00 \\ \hline
-      %       \rowcolor{green!50}lost & FL states & 44 & 49 & 46.67 & 6.33 \\
-      %       \rowcolor{orange!50}&               & 51 & 66 & 57.95 & 13.47 \\
-      %       \rowcolor{green!50}& P states       & 51 & 56 & 53.33 & 6.33 \\
-      %       \rowcolor{orange!50}&               & 34 & 49 & 42.05 & 13.47 \\
-      %       \hline
-      %     \end{tabular}
-      %   \end{center}
-      %   \caption{Statistics to cross validation \\
-      %     - \colorbox{green!50}{Less free-livings - 3 examples} \\
-      %     - \colorbox{orange!50}{Less parasites - 64 examples}}
-      % \end{table}
 
@@
 \chapter{Discussion}
+  As in the previous chapters, the discussion is divided into three sections: input data, simulation 
+    and reconstruction of the real data.
 
@@
   \section{Simulation}
-    For fixed calculations we assume a distribution of 60\% free-living to 40\% parasites, 95\% 
-      missing data and a multifuration rate of 95\%.
-    How well does our simulation approach the real data situation? \\
+    % For fixed calculations we assume a distribution of 60\% free-living to 40\% parasites, 95\% 
+    %   missing data and a multifuration rate of 95\%.
+
     There are some points to discuss:
@@
       parameters. This allowed us to estimate the influence of some of these parameters.
+
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \subsection{Transition probabilities} \label{sec:discussion - transition probabilities}
+      We assume that different parasite types have different transition probabilities. Establishing a 
+        common distribution across the eukaryotic tree is therefore difficult. \\
+      Based on the estimates of Windsor \cite{Windsor1998}, we have assumed a distribution of 40\% 
+        parasites to 60\% free livings in this work. As a result of the diversity of parasites and the 
+        lack of generalizations, we have generally stated that 
+        $\mathcal{P}(FL \rightarrow P) = \mathcal{P}(P \rightarrow FL)$. But it is also reasonable to 
+        assume that in general $\mathcal{P}(FL \rightarrow P) > \mathcal{P}(P \rightarrow FL)$, because 
+        a reverse mutation is usually less likely. However, one would have to determine how much this 
+        difference is and thus discuss another parameter. \\
+
+      In the simulation, we tested different beta distributions with different thresholds and found that 
+        this combination has a considerable influence on the predictive power of the algorithms. \\
+      At this point it would be possible to test other distributions with equal threshold values or 
+        different threshold values with equal distributions. \\
+      However, if you choose a strong free-living distribution and balance it with the threshold to 
+        achieve a 40:60 parasite free-living distribution, for example, this could be very 
+        computationally expensive. \\
+
+      With these further simulations you could find out if the issue of distributions plays a big role. 
+        Conversely, one could estimate possible distributions based on the data location in the tree. 
+        However, this is likely to be very difficult given the poor data. For this reason, we have 
+        decided in this work to accept very general values and not to speculate much. \\
+
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \subsection{Simulation of a phylogeny} \label{sec:discussion - simulate phylogeny}
+      In our simulation, we start with the simulation of a phylogeny and then depict our data situation. \\
+      For this first step we use the \textit{randomized()} function of the phylo package from biopython
+        \cite{Cock2009}. The question is how close is such a randomized tree to a phylogeny. \\
+
+      The problems that can arise are that different species develop at different rates. This means that 
+        there could be sections in the tree with many branches (for example, subtrees of unicellular 
+        species), ie with high depths and opposite sections (of very complex species, for example). It 
+        can thus be assumed that the tree is not balanced. \\
+      For more precise statements, one would have to take deeper undercurrents, which was not possible 
+        in the context of this work.
 

### 2018-03-25 Paper - Latex/Paper - Skizze - v4.tex
Paper - discussion - Intro & intermediate part

@@
       \vspace{3cm}
-      \textbf{Eingereicht am:} \\
-      3.4.2018 \\
+      \textbf{Submitted on:} \\
+      3 April 2018 \\
     	\vspace{2cm}
@@
      	\vspace{3cm}
-      \textbf{Betreuer:} \\
+      \textbf{Supervisor:} \\
       Prof. Dr. Bernhard Y. Renard \\
@@
         25,992 and 34,879 species as parasites and free-living. With 2,293,463 leaf nodes we still have 
-        about 97.34~\% unknown leaf nodes. \\
-      We found also 57,352 (not distinct!) source species and 809,993 (not distinct!) target
-        species without OTT ids. Since we currently use only OTT ids, we could not use this information. \\        
-      \todo{discussion!!!} \\
+        about 97.34~\% unknown leaf nodes. In the discussion, section 
+        \ref{sec:discussion - data situation}, we will talk about ways to extend this data. \\
 
@@
 \chapter{Discussion}
-  As in the previous chapters, the discussion is divided into three sections: input data, simulation 
-    and reconstruction of the real data.
-
-  Fehlerqoute der Daten an sich? \\
-  Wie gut ist unsere Datenlage? 3 mio knoten, 1.8 named species (leaf nodes), 200.000 leaf nodes mit 
-  Information. \\
-  Welche Teile des Baumes sind gut, an welchen muss noch viel geforscht werden. \\
-  Wieviele Origins haben wir gefunden, was bedeutet diese Zahl? \\
-  Es gibt noch ungenutze information in GloBI. \\
-  Wir können GloBI verbessern ... Wir haben GloBI auf die gefundenen Abweichungen aufmerksam gemacht... 
-    Fehler werden durch die prediction eventuell verstärkt...\\
-
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  \section{Data situation}
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{Taxa}
+  This chapter deals with the question of how trustworthy our result of the ancestral state 
+    reconstruction of the Eukaryota tree is. And further on how well our simulation can simulate the 
+    real problem and thus make statements about the predictive power of the applied Sankoff algorithm.
+
+  We have pursued this question in various investigations and yet, of course, further possibilities 
+    for improvement remain. Despite these possibilities for improvement, our reconstruction gives a 
+    first good assessment of the whole tree.
+
+  \todo{Why is the study important?} \\
+  \todo{How does this study relate to previous studies?}
+
+  We evaluated our ancestral state reconstruction and the relational state prediction using three 
+    methods: a simulation, a selective analysis from a biological perspective and a leave-100-out 
+    cross validation.
+
+  Each theme has its own limitations. \\
+  There are various expansion options and points of criticism for the simulation, which in 
+    particular revolve around the question of how well we can simulate our real data. We dedicate 
+    this question to the subsection \ref{sec:discussion - simulation}. \\
+  Above all, the 'biological view' gives a first impression of the credibility of the results. But 
+    he can not make any statistical statements. Here the interested researcher may have to analyze 
+    the subtrees of relevant to him for himself. \\
+   Of course, cross-validation can be expanded. With more computing power, a leave-1-out cross 
+    validation could also be performed. However, our result on this point yields a strong result 
+    with 98.17~\% correct prediction that this does not seem necessary. \\
+  One last limitation also exists in the data situation itself. We have pointed out in various 
+    sections that we have a strong multifurcation and only a few data about leaf node states. In 
+    figure \ref{fig:influence of unknown data} you can see how the predictive power can improve if 
+    we have more data available. We discuss this point in section 
+    \ref{sec:discussion - data situation}.
+
+  % Wieviele Origins haben wir gefunden, was bedeutet diese Zahl? \\
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Data situation} \label{sec:discussion - data situation}
+    The used eukaryotic synthesis tree from OTL \cite{Hinchliff2015} has 241,974 internal nodes and 
+      293,463 leaf nodes. In addition, we could specify 25,992 parasitic and 34,879 free-living 
+      species from GloBI \cite{Poelen2014}. \\
+    This gives us a high number of missing internal nodes (high multifurcation) and a low number of 
+      node states of the leaf nodes. In table \ref{table:percentage loss information subtrees} we have 
+      written down this percentage including some subtrees. \\
+
     The investigation of the taxonomy revealed that the OTL tree has three kingdoms: Chloroplastida, 
@@
       \cite{CavalierSmith1981}. \\
-      In section \pageref{subsec:listPhyla} of the appendix is a list of all phyla.
-
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  \section{Simulation}
-    % For fixed calculations we assume a distribution of 60\% free-living to 40\% parasites, 95\% 
-    %   missing data and a multifuration rate of 95\%.
-
-    There are some points to discuss:
-    \begin{itemize}
-      \item How close is the randomized binary tree to a true phylogeny?
-      \item The distribution of parasites to free-ranging species is a pure assumption. From different 
-        sources about 40\% parasites are estimated, are these also beta-distributed?
-      \item How well do the transition probabilities match parasitism? Depending on the type of 
-        parasitism, this will certainly look different. In addition, it can be assumed that the 
-        probability for losses is lower than for origins.
-      \item The equal distribution of the multifurcation is a blank assumption. It is very likely to 
-        be higher towards the root node because there is less information back in time. On the other 
-        hand, there are many studies that have studied various species without considering phylogeny. 
-        Which also creates a high number of children of a node directly at the leaf nodes.
-    \end{itemize}
-    In order to be able to observe these problems, we have programmed our simulation according to the 
-      parameters. This allowed us to estimate the influence of some of these parameters.
+    In section \pageref{subsec:listPhyla} of the appendix is a list of all phyla. \\
+
+    Also, the global database is not fallible. We found out (section x) that there is some 
+      misinformation. \\
+    We were able to report some of these directly to Globi.
+
+    We found also 57,352 (not distinct!) source species and 809,993 (not distinct!) target species 
+      without OTT ids. Since we currently use only OTT ids, we could not use this information. \\
+    At this point there is thus the possibility to use more of the existing data, if one performs a 
+      matching with the other Ids.
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Simulation} \label{sec:discussion - simulation}
+    The aim of the simulation was to test the influence of various unknown or unsafe parameters in 
+      order to test the credibility of the prediction. \\
+    Some of these influences could not be tested: Firstly, the distribution of parasites and 
+      free-livings in the tree produces various parameters that we could not test all (see subsection 
+      \ref{sec:discussion - transition probabilities}) and, secondly, we discuss the simulation of a 
+      phylogenetic tree on which the evaluation based on certain parts (see subsection 
+      \ref{sec:discussion - simulate phylogeny}).
 
@@
         in the context of this work.
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Conclusion}
+
+  Die simulation ergab: x \\
+  Der biological view ergab: y \\
+  Die leave-100-out cross validation ergab: z
 

### 2018-03-25 Paper - Latex/Paper - Skizze - v4.tex
Paper - Discussion - Conclusion

@@
     The influence of these parameters are tested on our result using our simulation (section 
-      \ref{sec:simulation}).
+      \ref{sec:methods - simulation}).
 
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Simulation}\label{sec:simulation}
+  \section{Simulation}\label{sec:methods - simulation}
     The simulation compares these different of ancestral state reconstruction algorithms with each 
@@
     in section \ref{sec:ancestral state reconstruction}. We tested these on different simulations of 
-    the data and compared their predictive power (section \ref{sec:results of simulation}). \\
+    the data and compared their predictive power (section \ref{sec:results - simulation}). \\
   We used the Sankoff algorithm \cite{Sankoff1975} implemented by Louca et al. \cite{Louca2017}, 
@@
     subtrees for their credibility with the help of biological background knowledge (subsection 
-    \ref{sec:biological view}). On the other hand, we performed a leave-100-out cross validation
+    \ref{sec:results - biological view}). On the other hand, we performed a leave-100-out cross validation
     (Subsection \ref{sec:results - cross validation}) and predicted approximately 98.17~\% states 
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Results of simulation / Influence of different parameters} \label{sec:results of simulation}
+  \section{Results of simulation / Influence of different parameters} \label{sec:results - simulation}
 
@@
     This section is about evaluating the prediction of real data using the Sankoff method. \\
-    It is divided into two subsections. \ref{sec:biological view}: The analysis of some subtrees using 
+    It is divided into two subsections. \ref{sec:results - biological view}: The analysis of some subtrees using 
       biological background knowledge. \ref{sec:results - cross validation}: Presentation of the results 
@@
     %---------------------------------------------------------------------------------------------------
-    \subsection{Biological view} \label{sec:biological view}
+    \subsection{Biological view} \label{sec:results - biological view}
       To analyze the results, we have selected some phyla (subtrees) to evaluate our results 
@@
       %---------------------------------------------------------------------------------------------------
-      \subsubsection{Origins and Losses}
+      \subsubsection{Origins and Losses} \label{sec:results - origins and losses}
 
@@
 
-  Die simulation ergab: x \\
-  Der biological view ergab: y \\
-  Die leave-100-out cross validation ergab: z
+    From the simulation, we can conclude that we predict correctly about 60\% of the nodes in the 
+      present data situation (see section \ref{sec:results - simulation}).
+    The leave-100-out cross validation even showed that we predict the omitted nodes to be 98.17~\%  
+      percent correct (see section \ref{sec:results - cross validation}). \\
+    This allows for the assumption that the data is grouped and not uniformly distributed and thus 
+      smaller subtrees are present in which data are to be found in the simulation with smaller 
+      multifurcation and smaller value for unknown nodes. This is also confirmed by our biological 
+      analysis of the Chordata subtree (see subsection \ref{sec:results - biological view}). \\
+    However, this means that the ancestral states' data in the direction of root node are probably 
+      particularly unbelievable. Which makes the localization of Origins direction root node 
+      difficult. The question remains, how much this affects the estimation of the number of origins. 
+      Our comparison with the paper from Weinstein and Kuris \cite{Weinstein2016} (see subsection 
+      \ref{sec:results - origins and losses}), however, leaves us with optimism.
 

### 2018-03-25 Paper - Latex/Paper - Skizze - v4.tex
Proofreading

@@
   \section{Motivation}
-    The aim of this thesis is the application of maximum parsiomony algorithms to non-binary 
-      trees and very large datasets. In particular, the example find the 'Origins of Parasitism' 
+    The aim of this thesis is the application of maximum parsimony algorithms to non-binary 
+      trees and very large data sets. In particular, the example find the 'Origins of Parasitism' 
       throughout the Eukaryota Tree of Life. \\
@@
     The first is maximum parsimony: explain the current state with the least number of state changes 
-      between the child and his ancestor. \\
+      between the child and its ancestor. \\
     The other class she presents describes modeling the character evolution as a stochastic process and 
@@
 
-    We will test the existing maximum parsimony algorithms Fitch \cite{Fitch1971} and Sankoff 
+    We will test the existing maximum parsimony algorithms of Fitch \cite{Fitch1971} and Sankoff 
       \cite{Sankoff1975} for this task and estimate their predictive power. The present tree structure 
@@
       (1) Retrieve phylogenentic tree data as input for the tree (OTL) and the state information (GloBI).
-      (2) Get metadata of these for a realisitc the simulation of the maximum parsimony algorithms (Fitch \& Sankoff).
+      (2) Get metadata of these for a realisitc simulation of the maximum parsimony algorithms (Fitch \& Sankoff).
       (3) Build and run the simulation.
@@
       (5) Evaluate the accuracy of developed algorithms and choose the best.
-      (6) Run the resulted algorithm on the original data.
-      (7) Evalute and interprete results. %$\rightarrow$ Origins etc...
+      (6) Run the resulting algorithm on the original data.
+      (7) Evalute and interprete the results. %$\rightarrow$ Origins etc...
     }
@@
       the states. \\
-    For the Tree Open Tree of Life (OTL) is used \cite{Hinchliff2015} and for the state information 
+    For the tree Open Tree of Life (OTL) is used \cite{Hinchliff2015} and for the state information 
       the Global Biotic Interaction database (GloBI) is taken \cite{Poelen2014}. \\
@@
         \end{center}
-        \caption{60~\% Free-living - 40~\% Parasites \\ red: parasites, blue: free-living, \\ the threshold is at 0.4}
+        \caption{Simulated distributions of the states: \\
+          60~\% Free-living - 40~\% Parasites \\
+          red: parasites, blue: free-living, \\
+          the threshold is at 0.4}
         \label{fig:Beta distribution}
@@
       previous methods (from Camin and Sokal \cite{Camin1965}, \todo{Kluge and Farris} and Farris 
-      \cite{Farris1970}): Fitch parsiomony \cite{Fitch1971} and Sankoff parsimony \cite{Sankoff1975}. \\
+      \cite{Farris1970}): Fitch parsimony \cite{Fitch1971} and Sankoff parsimony \cite{Sankoff1975}. \\
     \anmerkungstext{Unter Farris war auch noch der Begriff Wagner trees in gebrauch, als 
@@
         Internal nodes have three sets, which are empty at the beginning, excluding the root node, it 
-        has only one. Leaf nodes have their state as a set (eg \{FL\} or \{P\}, unknown leaf nodes the 
+        has only one. Leaf nodes have their state as a set (e.g. \{FL\} or \{P\}, unknown leaf nodes the 
         union of all possible states (\{FL, P\}). \\
 
-      The algorithm traverses three times trough the tree and fills these sets. \\
+      The algorithm traverses three times through the tree and fills these sets. \\
       In each step, two sets are considered and their intersect formed. There are two cases:
@@
   %---------------------------------------------------------------------------------------------------
-  \section{real data analysis}
+  \section{Real data analysis}
     \todo{Evaluation section in methods?}
@@
       \item run castor algorithm / and others?
-      \item interprete results (leave-100-out cross validation)
+      \item interprete results (leave-100-out cross-validation)
     \end{itemize}
@@
       subtrees for their credibility with the help of biological background knowledge. On the other 
-      hand, we performed a leave-100-out cross validation.
+      hand, we performed a leave-100-out cross-validation.
 
@@
     subtrees for their credibility with the help of biological background knowledge (subsection 
-    \ref{sec:results - biological view}). On the other hand, we performed a leave-100-out cross validation
-    (Subsection \ref{sec:results - cross validation}) and predicted approximately 98.17~\% states 
+    \ref{sec:results - biological view}). On the other hand, we performed a leave-100-out cross-validation
+    (Subsection \ref{sec:results - cross-validation}) and predicted approximately 98.17~\% states 
     correct.
@@
     The multifurcation affects only the internal nodes. We collected the number of children $-2$ of 
-      every node (a node with two children is binary). That means it discribes the number of nodes 
+      every node (a node with two children is binary). That means it describes the number of nodes 
       which we have lost from the real (binary) phylogenetic tree. \\
@@
       Despite higher complexity, the BIC values are getting smaller from model to model, meaning that 
-        the finest model available here is also the best one of these. Lower taxa than orders (eg 
+        the finest model available here is also the best one of these. Lower taxa than orders (e.g. 
         family) were computationally too expensive to calculate. \\
       The model \textit{multifurc $\sim$ order * mean.height} turns out to be the best of our models, 
-        whereby it is possible that eg \textit{multifurc $\sim$ family * mean.height} is better.
+        whereby it is possible that e.g. \textit{multifurc $\sim$ family * mean.height} is better.
 
@@
       The eukaryotic synthesis tree has 293,463 leaf nodes. The GloBI database has 5,346,414 interactions 
-        (at 29.01.2018). Out of this data we got 51,337 distinct free-living species and 47 332 
+        (at 29.01.2018). Out of this data we got 51,337 distinct free-living species and 47,332 
         distinct parasite species for the whole tree of life. From the Eukaryota we could determine 
@@
         values are smaller than those of the multifurcation models. The modeling here is thus better. \\
-      Again, the calculation of finer models (eg order or family) was too expensive. \\
+      Again, the calculation of finer models (e.g. order or family) was too expensive. \\
 
@@
     \end{figure}
-    First, we tested different trasition probability distributions including threshold (first column). 
+    First, we tested different transition probability distributions including threshold (first column). 
       It can be observed that the more balanced the percentages of free-livings and parasites, the 
@@
     It is divided into two subsections. \ref{sec:results - biological view}: The analysis of some subtrees using 
-      biological background knowledge. \ref{sec:results - cross validation}: Presentation of the results 
-      of the leave-100-out cross validation.
+      biological background knowledge. \ref{sec:results - cross-validation}: Presentation of the results 
+      of the leave-100-out cross-validation.
 
@@
       The Apicomplexa are a parasitic phylum. We found only one input organism: Stemonitis fusca as a 
-        free-living specie. In GloBI it is listed as being parasitized by Nectria candicans and Nectriopsis 
+        free-living species. In GloBI it is listed as being parasitized by Nectria candicans and Nectriopsis 
         sporangiicola\footnote{
@@
           mostly all species predicted as parasites. \\
-        Nematoda is again full of problems. The rootnode is predicted as a parasite and so we have more 
+        Nematoda is again full of problems. The root node is predicted as a parasite and so we have more 
           losses of parasitism for the less information of free-living species in this phylum. The rest 
@@
     %---------------------------------------------------------------------------------------------------
-    \subsection{Leave-100-out cross validation} \label{sec:results - cross validation}
-      For a further validation of our results, we carried out a leave-100-out cross validation. \\
+    \subsection{Leave-100-out cross-validation} \label{sec:results - cross-validation}
+      For a further validation of our results, we carried out a leave-100-out cross-validation. \\
       In order to achieve about 15\% of the 60,871 input node states with a validation, 
@@
         (kingdom, phylum, class) and the depth of the leaf nodes was re-modeled and the BICs compared 
-        (table \ref{table:BIC cross validation}). Lower taxa than classes (eg order) were 
+        (table \ref{table:BIC cross-validation}). Lower taxa than classes (e.g. order) were 
         computationally too expensive to calculate. \\
-      The Residuals are included in the appendix (table \ref{table:Residuals cross validation}) for the 
+      The Residuals are included in the appendix (table \ref{table:Residuals cross-validation}) for the 
         sake of completeness; here too, due to the different complexity, they do not have much meaning 
@@
             \hline \hline
-            correct predicted $\sim$ taxa & 117936 & \cellcolor{green!40}112242 & \cellcolor{green!50}111733 \\% & XXXXX \\
-            \hline
-            correct predicted $\sim$ taxa + depth & 117776 & \cellcolor{green!50}111304 & \cellcolor{green!50}111273 \\% & XXXXX \\
-            \hline
-            correct predicted $\sim$ taxa * depth & 117709 & \cellcolor{green!50}111262 & \cellcolor{green!30}113135 \\% & XXXXX \\
+            correctly predicted $\sim$ taxa & 117936 & \cellcolor{green!40}112242 & \cellcolor{green!50}111733 \\% & XXXXX \\
+            \hline
+            correctly predicted $\sim$ taxa + depth & 117776 & \cellcolor{green!50}111304 & \cellcolor{green!50}111273 \\% & XXXXX \\
+            \hline
+            correctly predicted $\sim$ taxa * depth & 117709 & \cellcolor{green!50}111262 & \cellcolor{green!30}113135 \\% & XXXXX \\
             \hline
@@
         \end{center}
-        \caption{BIC (Bayesian information criterion) values of cross validation prediction models. \\
+        \caption{BIC (Bayesian information criterion) values of cross-validation prediction models. \\
           These models were created with the R function \textit{glm()} and compared with the 
             \textit{BIC()} function. This results in the listed BIC values.}
-        \label{table:BIC cross validation} 
+        \label{table:BIC cross-validation} 
       \end{table}
@@
       The BIC values this time did not prove that the finest model is the best. Of our calculated models, 
-       \textit{correct predicted $\sim$ phylum * depth} has the smallest value. \\
+       \textit{correctly predicted $\sim$ phylum * depth} has the smallest value. \\
 
@@
         high as the number of omitted nodes, so the variability is quintupled. \color{black} Table 
-        \ref{table:statistics cross validation} shows these results. \\
+        \ref{table:statistics cross-validation} shows these results. \\
       \begin{table}[h!]
@@
         \end{center}
-        \caption{Statistics about the leave-100-out cross validation \\
+        \caption{Statistics about the leave-100-out cross-validation \\
           The distance between original and new states was calculated using the Euclidean metric. This 
@@
             (P) and free-livings (FL).}
-        \label{table:statistics cross validation}
+        \label{table:statistics cross-validation}
       \end{table}
@@
     methods: a simulation, a selective analysis from a biological perspective and a leave-100-out 
-    cross validation.
+    cross-validation.
 
@@
       present data situation (see section \ref{sec:results - simulation}).
-    The leave-100-out cross validation even showed that we predict the omitted nodes to be 98.17~\%  
-      percent correct (see section \ref{sec:results - cross validation}). \\
+    The leave-100-out cross-validation even showed that we predict the omitted nodes to be 98.17~\%  
+      percent correct (see section \ref{sec:results - cross-validation}). \\
     This allows for the assumption that the data is grouped and not uniformly distributed and thus 
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Missing internal node modelling - Resiudal table} %\label{sec:Residuals unknown information}
+  \section{Missing internal node modeling - Residual table} %\label{sec:Residuals unknown information}
     \begin{table}[h!]
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Missing leaf state modelling - Resiudal table}\label{sec:Residuals unknown information}
+  \section{Missing leaf state modeling - Residual table}\label{sec:Residuals unknown information}
     \begin{table}[h!]
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Cross validation prediction - Resiudal table}
+  \section{Cross-validation prediction - Residual table}
     \begin{table}[h]
@@
           \hline \hline
-          correct predicted $\sim$ taxa & 117877 & \cellcolor{green!30}111466 & \cellcolor{green!45}108878 \\% & XXXXX \\
-          \hline
-          correct predicted $\sim$ taxa + depth & 117703 & \cellcolor{green!35}110513 & \cellcolor{green!45}108403 \\% & XXXXX \\
-          \hline
-          correct predicted $\sim$ taxa * depth & 117592 & \cellcolor{green!40}109827 & \cellcolor{green!50}107994 \\% & XXXXX \\
+          correctly predicted $\sim$ taxa & 117877 & \cellcolor{green!30}111466 & \cellcolor{green!45}108878 \\% & XXXXX \\
+          \hline
+          correctly predicted $\sim$ taxa + depth & 117703 & \cellcolor{green!35}110513 & \cellcolor{green!45}108403 \\% & XXXXX \\
+          \hline
+          correctly predicted $\sim$ taxa * depth & 117592 & \cellcolor{green!40}109827 & \cellcolor{green!50}107994 \\% & XXXXX \\
           \hline
@@
       \end{center}
-      \caption{Residuals of cross validation prediction \\
+      \caption{Residuals of cross-validation prediction \\
         These models were created with the R function \textit{glm()} and compared with the 
           \textit{anova()} function. This results in the listed residuals.}
-      \label{table:Residuals cross validation} 
+      \label{table:Residuals cross-validation} 
     \end{table}

### 2018-03-25 Paper - Latex/Paper - Skizze - v4.tex
more data

@@
       the more complex likelihood based models. Since there are no branch lengths or other information 
-      available for the present relationship tree, and thus can not take advantage of the 
+      available for the present relationship tree, and we thus can not take advantage of the 
       other models, we decided in favor for parsimonious. \\
@@
       \cite{CavalierSmith1981}. \\
-    In section \pageref{subsec:listPhyla} of the appendix is a list of all phyla. \\
-
-    Also, the global database is not fallible. We found out (section x) that there is some 
+    In \colorbox{red}{section/page} \pageref{subsec:listPhyla} of the appendix is a list of all phyla. \\
+
+    Also, the global database is not infallible. We found out (section \colorbox{red}{x}) that there is some 
       misinformation. \\

### 2018-03-26 Paper - Latex/Paper - Skizze - v4.tex
Paper - restructure

@@
 
-% Parasitism in Eukaryota - Reconstruction of ancestral and unavailable extant states
-
-% Lydia Buntrock^1; Jorrit Poelen^?; Berhard Renard^2; Emanuel Heitlinger^1,3;
-
-% 1 - Institute for Biology, Molecular Parasitology, Humboldt University, Berlin, Germany
-% 2 - Bioinformatics Unit (MF1), Department for Methods Development and Research Infrastructure, Robert Koch Institute, Berlin, Germany
-% 3 - Research Group Ecology and Evolution of Molecular Parasite Host Interactions, Leibniz Institute for Zoo and Wildlife Research, Berlin, Germany
-
-% ## Wenn du willst kannst du auch das IZW (3) an deinen Namen heften!
-% ## Yorrit bitte das Abstract schicken und fragen ob er Co-Author sein will.
-
   Parasitism can be defined as an interaction between species in which one of the interaction 
     partners, the parasite, lives in or on the other, the host. The parasite draws food from its 
-    host and harms it in the process. According to some estimates, above 50\% of all eukaryotes are 
+    host and harms it in the process. According to some estimates, above 40\% of all eukaryotes are 
     parasites. Nevertheless, it is difficult to obtain information whether a particular taxon is a 
-    parasite computationally making it difficult to query large sets of taxa. \\
-
-  Here we test in how far it is possible to use the open tree of life (OTL), a synthesis of 
+    parasite computationally making it difficult to query large sets of taxa.
+
+  Here we test in how far it is possible to use the Open Tree of Life (OTL), a synthesis of 
     phylogenetic trees on a backbone taxonomy (resulting in unresolved nodes), to expand available 
@@
     database to categorise 25,992 and 34,879 species as parasites and free-living, respectively and 
-    predict states for over ~2.7 million (97.6\%) leaf nodes without state information. \\
-
-  We estimate the accuracy of our maximum parsimony based predictions using cross-evaluation and 
-    simulation at roughly 80\% overall, but strongly varying between clades. We describe this 
-    variation across taxa as associated with available state and topology information. We compare 
-    our results with several smaller scale studies, which used manual expert curation and conclude 
-    that computationally inferred state changes largely agree in number and placement with those. In 
-    clades in which available state information is biased (mostly towards parasites, e.g. in 
-    Nematodes) phylogenetic prediction is bound to provide results contradicting conventional 
-    wisdom. \\
+    predict states for over $\sim$2.3 million (97.34\%) leaf nodes without state information.
+
+  We estimate the accuracy of our maximum parsimony based predictions using cross-validation and 
+    simulation at roughly 60\% overall, but strongly varying between clades. The cross-validation 
+    resulted in an accuracy of 98.17\% which is explained by the fact that the data are not 
+    uniformly distributed. We describe this variation across taxa as associated with available state 
+    and topology information. We compare our results with several smaller scale studies, which used 
+    manual expert curation and conclude that computationally inferred state changes largely agree in 
+    number and placement with those. In clades in which available state information is biased 
+    (mostly towards parasites, e.g. in Nematodes) phylogenetic prediction is bound to provide 
+    results contradicting conventional wisdom.
 
@@
     further incorporation of parasitism as an important trait in species interaction databases and 
-    in individual studies on eukaryotes e.g. in the microbiome. \\
-
-  ------------ \\
-
-  This study focuses on the ancestral state reconstruction of parasitism in the tree of life of
-    Eukaryota. We predict unknown states of species and estimate origins and losses of parasitism. \\
-  The challenge here is the size of the tree and the little information about it. \\
-  Such a large phylogenetic tree does not completely exist and therefore we work with a synthesis 
-    tree of OTL \cite{Hinchliff2015} which is highly multifurcated. \\
-  For the 2,535,437 leaf nodes we could not gather much data. From the GloBI database 
-    \cite{Poelen2014} which we used, we could only collect 25,992 parasitic and 34,879 free-living 
-    species. It follows that we have $\approx 2.4~\%$ state information. \\
-  So far, especially small scale studies have been carried out or highly manual. In this scale, it 
-    requires different data sources to be interconnected. \\
-  We performed an analysis of existing algorithms and selected a Sankoff maximum parsimony algorithm 
-    using the R package \textit{Castor} \cite{Louca2017}. \\
-  Nevertheless, the results are convincing and even though purely computational approach which did 
-    not include human experts input, results coincide with prior knowledge. Also regarding the number 
-    of events, our estimates coincide with previous results by human experts, e.g. the study by 
-    Weinstein and Kuris \cite{Weinstein2016}. \\
-
-  ------------ \\
-
-  \anmerkungstext{Klassisch packt man keine Referenzen in Abstracts (bzw. wenn das meist als 
-    Kurzreferenz also (Author et al., 2017). (Bernhard)} \\
-  We have compared the results of some subtrees with known knowledge (Chordata, Nematoda, 
-    Platyhelminthes and Apicomplexa) and, except for the Nematoda, the results looked very good. In 
-    the case of Nematoda, the data situation is strongly shifted to the few parasites. \\
-  We could partly compare our number of origins with the results of Sara B. Weinstein and Armand M. 
-  Kuris from their article \textit{Independent origins of parasitism in Animalia}  
-    and have come to a similar magnitude. They identified 223 parasitic origins in Metazoa and we 
-    were able to estimate about 300 origins. \\
+    in individual studies on eukaryotes e.g. in the microbiome.
+
+  % This study focuses on the ancestral state reconstruction of parasitism in the tree of life of
+  %   Eukaryota. We predict unknown states of species and estimate origins and losses of parasitism. \\
+  % The challenge here is the size of the tree and the little information about it. \\
+  % Such a large phylogenetic tree does not completely exist and therefore we work with a synthesis 
+  %   tree of OTL \cite{Hinchliff2015} which is highly multifurcated. \\
+  % For the 2,535,437 leaf nodes we could not gather much data. From the GloBI database 
+  %   \cite{Poelen2014} which we used, we could only collect 25,992 parasitic and 34,879 free-living 
+  %   species. It follows that we have $\approx 2.4\%$ state information. \\
+  % So far, especially small scale studies have been carried out or highly manual. In this scale, it 
+  %   requires different data sources to be interconnected. \\
+  % We performed an analysis of existing algorithms and selected a Sankoff maximum parsimony algorithm 
+  %   using the R package \textit{Castor} \cite{Louca2017}. \\
+  % Nevertheless, the results are convincing and even though purely computational approach which did 
+  %   not include human experts input, results coincide with prior knowledge. Also regarding the number 
+  %   of events, our estimates coincide with previous results by human experts, e.g. the study by 
+  %   Weinstein and Kuris \cite{Weinstein2016}. \\
 
@@
 
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  %--------------------------------------------------------------------------------------------------- 
-  \section{Motivation}
-    The aim of this thesis is the application of maximum parsimony algorithms to non-binary 
-      trees and very large data sets. In particular, the example find the 'Origins of Parasitism' 
-      throughout the Eukaryota Tree of Life. \\
-    For these large phylogenetic synthesis trees, however, ancestral state reconstruction has so far 
-      only been done for Bacteria and Archaea for binary traits by Goberna and Verdú \cite{Goberna2015}.
-      However, this differs from eukaryotes in the sense that complex traits such as parasitism depend
-      on more than one gene. \\
-    \todo{Warum ist das relevant? Was könnte man dann tun?}
-
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  %--------------------------------------------------------------------------------------------------- 
-  \section{Background}
   For about 50 years, people have been working on ancestral state reconstruction. The first paper 
@@
     using the likelihoods to compute the possible ancestral character states. This is generally done 
-      with a continuous time Markov model \cite{RoyerCarenzi2013}. \\
+    with a continuous time Markov model \cite{RoyerCarenzi2013}.
 
@@
     available for the present relationship tree, and we thus can not take advantage of the 
-      other models, we decided in favor for parsimonious. \\
+    other models, we decided in favor for parsimonious.
 
@@
   This achieves that we can predict ancestral states and unknown states of living species for large 
-      non-binary relatives trees. \\
+    non-binary relatives trees.
 
@@
     species A parasitize species B. From this we conclude that species A is parasitic and species B 
-      free-living. \\
+    free-living.
 
@@
       {ontobee.org/ontology/RO?iri=http://purl.obolibrary.org/obo/RO\_000244}; Last checked: 22.03.2018.
-      }. This definition includes: ecto- and endoparasites, parasitoids, kleptoparasites and pathogenes.
-
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  %--------------------------------------------------------------------------------------------------- 
-  \section{Structure of this work}
+    }. This definition includes: ecto- and endoparasites, parasitoids, kleptoparasites and pathogenes. \\
+
   The objectives of this work are the following points: (1) Find a suitable ancestral state 
@@
     And then perform an evaluation of the results.
+
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%--------------------------------------------------------------------------------------------------- 
+\chapter{Aims}
+  The aim of this thesis is the application of maximum parsimony algorithms to non-binary 
+    trees and very large data sets. In particular, the example find the 'Origins of Parasitism' 
+    throughout the Eukaryota Tree of Life. \\
+  For these large phylogenetic synthesis trees, however, ancestral state reconstruction has so far 
+    only been done for Bacteria and Archaea for binary traits by Goberna and Verdú \cite{Goberna2015}.
+    However, this differs from eukaryotes in the sense that complex traits such as parasitism depend
+    on more than one gene. \\
+  \todo{Warum ist das relevant? Was könnte man dann tun?}
 
@@
     For the tree Open Tree of Life (OTL) is used \cite{Hinchliff2015} and for the state information 
-      the Global Biotic Interaction database (GloBI) is taken \cite{Poelen2014}. \\
+      the Global Biotic Interactions database (GloBI) is taken \cite{Poelen2014}. \\
     % These are presented below.
@@
       \end{itemize}
-      ITIS is only a small set of 100~\% confirmed and named species. GBIF is not composed with the help 
+      ITIS is only a small set of 100\% confirmed and named species. GBIF is not composed with the help 
         of phylogeny, the same is valid for the NCBI taxonomy. The WORMS taxonomy is a way too small 
@@
       Different parasite types have different transition probabilities. It is very difficult to make a 
-        statement about these probabilities. It is generally assumed in this work that there are 40~\% 
-        parasites and 60~\% free-livings which is based on the estimates by Windsor \cite{Windsor1998} 
+        statement about these probabilities. It is generally assumed in this work that there are 40\% 
+        parasites and 60\% free-livings which is based on the estimates by Windsor \cite{Windsor1998} 
         and $\mathcal{P}(FL \rightarrow P) = \mathcal{P}(P \rightarrow FL)$, as a result of the 
@@
         \caption{Simulated distributions of the states: \\
-          60~\% Free-living - 40~\% Parasites \\
+          60\% Free-living - 40\% Parasites \\
           red: parasites, blue: free-living, \\
@@
         \begin{itemize}
-          \item 50~\% P to 50~\% FL,
-          \item 40~\% P to 60~\% FL,
-          \item 30~\% P to 70~\% FL and 
-          \item 20~\% P to 80~\% FL
+          \item 50\% P to 50\% FL,
+          \item 40\% P to 60\% FL,
+          \item 30\% P to 70\% FL and 
+          \item 20\% P to 80\% FL
         \end{itemize}
@@
       These four versions were tested in the simulation with 100 trees and 10000 leaf nodes and a
-        distribution of 60~\% FL to 40~\% P. Figure \ref{fig:Fitch versions} shows this over all unknown 
+        distribution of 60\% FL to 40\% P. Figure \ref{fig:Fitch versions} shows this over all unknown 
         node percentage. \\
-      % At 90~\% unknown nodes and 90~\% of multifurcation of the internal nodes, version 1 was 89.26~\%, 
-      %   version 2 was 89.26~\%, version 3 was 89.35~\%, and version 4 was 89.31~\% correct. Therefore, 
+      % At 90\% unknown nodes and 90\% of multifurcation of the internal nodes, version 1 was 89.26\%, 
+      %   version 2 was 89.26\%, version 3 was 89.35\%, and version 4 was 89.31\% correct. Therefore, 
       %   only version 3 was used for all further simulations.
-      At 95~\% unknown nodes and 95~\% of multifurcation of the internal nodes, version 1 was 88.37~\%, 
-        version 2 was 88.37~\%, version 3 was 88.4~\%, and version 4 was 88.39~\% correct. Therefore, 
+      At 95\% unknown nodes and 95\% of multifurcation of the internal nodes, version 1 was 88.37\%, 
+        version 2 was 88.37\%, version 3 was 88.4\%, and version 4 was 88.39\% correct. Therefore, 
         only version 3 was used for all further simulations.
@@
     \ref{sec:results - biological view}). On the other hand, we performed a leave-100-out cross-validation
-    (Subsection \ref{sec:results - cross-validation}) and predicted approximately 98.17~\% states 
+    (Subsection \ref{sec:results - cross-validation}) and predicted approximately 98.17\% states 
     correct.
@@
           \hline \hline
-          Eukaryota       & 97.34~\%  & 98.16~\% \\
-          \hline \hline
-          Metazoa         & 96.44~\%  & 87.93~\% \\ \hline
-          Fungi           & 98.87~\%  & 96.97~\% \\ \hline
-          Chloroplastida  & 99.14~\%  & 89.46~\% \\
-          \hline \hline            
-          % Arthropoda      & 97.49~\%  & 89.95~\% \\ \hline
-          Apicomplexa     & 86.26~\%  & 87.16~\% \\ \hline
-          Nematoda        & 89.01~\%  & 88.59~\% \\ \hline
-          Chordata        & 88.59~\%  & \cellcolor{green!50}66.49~\% \\ \hline
-          Platyhelminthes & \cellcolor{green!50}68.73~\%  & 80.34~\% \\
-          \hline \hline            
-          Insecta         & 97.11~\%  & 90.78~\% \\
+          Eukaryota       & 97.34\%  & 98.16\% \\
+          \hline \hline
+          Metazoa         & 96.44\%  & 87.93\% \\ \hline
+          Fungi           & 98.87\%  & 96.97\% \\ \hline
+          Chloroplastida  & 99.14\%  & 89.46\% \\
+          \hline \hline            
+          % Arthropoda      & 97.49\%  & 89.95\% \\ \hline
+          Apicomplexa     & 86.26\%  & 87.16\% \\ \hline
+          Nematoda        & 89.01\%  & 88.59\% \\ \hline
+          Chordata        & 88.59\%  & \cellcolor{green!50}66.49\% \\ \hline
+          Platyhelminthes & \cellcolor{green!50}68.73\%  & 80.34\% \\
+          \hline \hline            
+          Insecta         & 97.11\%  & 90.78\% \\
           \hline  
@@
         25,992 and 34,879 species as parasites and free-living. With 2,293,463 leaf nodes we still have 
-        about 97.34~\% unknown leaf nodes. In the discussion, section 
+        about 97.34\% unknown leaf nodes. In the discussion, section 
         \ref{sec:discussion - data situation}, we will talk about ways to extend this data. \\
@@
         Each point corresponds to the average of one hundred simulations, each with 10,000 leaf nodes. \\
-        For the middle column we set the strength of the multifurcations to 0.95~\% similar to the 
-          real data and in the right column the amount of the unknowns to 0.95~\% also similar to the 
+        For the middle column we set the strength of the multifurcations to 0.95\% similar to the 
+          real data and in the right column the amount of the unknowns to 0.95\% also similar to the 
           real data.}
@@
       worse the prediction of the algorithms (second and third column). \\
-    It can be seen that both algortithms are always over 50~\% prediction and therefore better than 
+    It can be seen that both algortithms are always over 50\% prediction and therefore better than 
       guessing. Moreover, they are usually close to each other, with Sankoff always makes better 
@@
             Chordata & 91785        & 10451 & 18          & 91759 & 0 & 0 & 26 \\
-            &                       & 99.83~\% & 0.49~\%  & 99.97~\% & & & 0.03~\% \\ \hline
+            &                       & 99.83\% & 0.49\%  & 99.97\% & & & 0.03\% \\ \hline
             Nematoda & 30127        & 21 & 3289           & 1604 & 142 & 1196 & 27185 \\
-            &                       & 0.63~\% & 99.37~\%  & 5.32~\% & 0.47~\% & 3.97~\% & 90.23~\% \\ \hline
+            &                       & 0.63\% & 99.37\%  & 5.32\% & 0.47\% & 3.97\% & 90.23\% \\ \hline
             Platyhelminthes & 22683 & 7 & 7086            & 175 & & & 22508 \\
-            &                       & 0.1~\% & 99.9~\%    & 0.77~\% & 0 & 0 & 99.23~\% \\ \hline
+            &                       & 0.1\% & 99.9\%    & 0.77\% & 0 & 0 & 99.23\% \\ \hline
             Apicomplexa & 1863      & 1 & 255             & 1 & 0 & 0 & 1862 \\
-            &                       & 0.39~\% & 99.61~\%  & 0.05~\% & & & 99.95~\% \\
+            &                       & 0.39\% & 99.61\%  & 0.05\% & & & 99.95\% \\
             % \hline \hline
@@
             %   & 1099509 & 1313 & 22478 & 4176 & 1665 & 70223 \\
-            % & & 62.93~\% & 37.07~\%
-            %   & 91.7~\% & 0.11~\% & 1.87~\% & 0.35~\% & 0.14~\% & 5.86~\% \\
+            % & & 62.93\% & 37.07\%
+            %   & 91.7\% & 0.11\% & 1.87\% & 0.35\% & 0.14\% & 5.86\% \\
             \hline
@@
         predicted. The Chordata mostly consist of free-living species, so this seems believable. We 
-        started with 99.83~\%  species and predict 99.97~\% species as free-living (including already 
+        started with 99.83\%  species and predict 99.97\% species as free-living (including already 
         known nodes).
@@
         considered subtrees, see Table \ref{table:percentage loss information subtrees}. We start with 
-        0.1~\% free-livings and predicted 0.77~\% as free-living species. \\
+        0.1\% free-livings and predicted 0.77\% as free-living species. \\
 
       With the Nematoda it looks more complicated. Large parts of Nematoda are free-living, but we 
-        found only 5.32~\% of them. Blaxter et al. estimates the order of 25,000 parasites in the 
+        found only 5.32\% of them. Blaxter et al. estimates the order of 25,000 parasites in the 
         Nematoda \cite{Blaxter2015} and speaks of at least seven independently arosed parasitism 
@@
         }. \todo{Link ist nicht erreichbar!} The parasites have been much more studied and thus we start 
-        with only 0.63~\% (table \ref{table:phylum leaf nodes states}) free-living species. Against such 
+        with only 0.63\% (table \ref{table:phylum leaf nodes states}) free-living species. Against such 
         a shifted data situation, the algorithm is almost powerless to make correct predictions. And yet 
-        the percentage has increased to 5.34~\%. \\
+        the percentage has increased to 5.34\%. \\
 
@@
       Of these 10,000 nodes, 9,238 were unique. From the unique nodes, we predicted approximately 
-        98.17~\% correct and thus 1.82~\% wrong, with duplicate draws always having the same prediction 
+        98.17\% correct and thus 1.82\% wrong, with duplicate draws always having the same prediction 
         (data not shown). \\
@@
       % 10000 nodes 9238 unique
-      % 9060 nodes $\approx 98.17~\%$ correctly predicted
-      % 169 ($\approx 1.82~\%$) wrongly predicted
+      % 9060 nodes $\approx 98.17\%$ correctly predicted
+      % 169 ($\approx 1.82\%$) wrongly predicted
 
@@
 %---------------------------------------------------------------------------------------------------
-  \section{Effects of Taxa in the different models}
-
-    The comparisons of the effects of the taxa can be found in Table \ref{table:Effects unknown data} 
-    and showed ...
-
-    \begin{table}[h!]
-      \begin{center}
-        \begin{tabular}{ |l|l|r|r|r|r| }
-          \hline
-          \bfseries Taxa & \bfseries Model / Effects & \bfseries min & \bfseries max & \bfseries mean & \bfseries median \\
-          \hline \hline
-          Kingdom & globi $\sim$ taxa         & 0,01 & 0,04 & 0,02 & 0,01 \\
-                  & globi $\sim$ taxa + depth & 0,01 & 0,03 & 0,02 & 0,01 \\
-                  & globi $\sim$ taxa * depth & 0,00 & 0,03 & 0,01 & 0,01 \\
-          \hline
-          Phylum & globi $\sim$ taxa          & 0,17 & 393501,80 & 32208,79 & 6149,78 \\
-                  & globi $\sim$ taxa + depth & 0,32 & 567010,90 & 55149,54 & 10783,18 \\
-                  & globi $\sim$ taxa * depth & 0,00 & 1000000,00 & 225375,33 & 2511,58 \\
-          \hline
-        \end{tabular} 
-      \end{center}
-      \caption{Effects of Taxa in models for unknown data}
-      \label{table:Effects unknown data} 
-    \end{table}
-
-    globi $\sim$ taxa * depth: NOTE: kingdom is not a high-order term in the model
-
-    \begin{figure}[h!]
-      \centering
-      \includegraphics[trim = 0mm 0mm 0mm 15mm, clip, width=\textwidth]{Figures/EffectsOfModel-Data-Phylum.JPG}
-      \caption{Effects of Model: Data $\sim$ Phylum}
-      \label{fig:...}
-    \end{figure}
-    \begin{figure}[h!]
-      \centering
-      \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{Figures/EffectsOf3Models-Data-Phylum.JPG}
-      \caption{Effects of 3 Models: Data $\sim$ Phylum (+/* depth)}
-      \label{fig:...}
-    \end{figure}
-    \begin{figure}[h!]
-      \centering
-      \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{Figures/EffectsOf3Models-Data-Phylum_loglog.JPG}
-      \caption{Effects of 3 Models: Data $\sim$ Phylum (+/* depth) \\ both axis in log scale}
-      \label{fig:...}
-    \end{figure}
-
-%---------------------------------------------------------------------------------------------------
-%---------------------------------------------------------------------------------------------------
-%---------------------------------------------------------------------------------------------------
 %---------------------------------------------------------------------------------------------------
@@
     validation could also be performed. However, our result on this point yields a strong result 
-    with 98.17~\% correct prediction that this does not seem necessary. \\
+    with 98.17\% correct prediction that this does not seem necessary. \\
   One last limitation also exists in the data situation itself. We have pointed out in various 
@@
       present data situation (see section \ref{sec:results - simulation}).
-    The leave-100-out cross-validation even showed that we predict the omitted nodes to be 98.17~\%  
+    The leave-100-out cross-validation even showed that we predict the omitted nodes to be 98.17\%  
       percent correct (see section \ref{sec:results - cross-validation}). \\

### 2018-03-27 Paper - Latex/Paper - Skizze - v4.tex
Thesis - Abstract

@@
     partners, the parasite, lives in or on the other, the host. The parasite draws food from its 
-    host and harms it in the process. According to some estimates, above 40\% of all eukaryotes are 
-    parasites. Nevertheless, it is difficult to obtain information whether a particular taxon is a 
-    parasite computationally making it difficult to query large sets of taxa.
+    host and harms it in the process. According to estimates, above 40\% of all eukaryotes are 
+    parasites. Nevertheless, it is computationally difficult to obtain information whether a 
+    particular taxon is a parasite making it difficult to query large sets of taxa.
 
@@
   We estimate the accuracy of our maximum parsimony based predictions using cross-validation and 
-    simulation at roughly 60\% overall, but strongly varying between clades. The cross-validation 
-    resulted in an accuracy of 98.17\% which is explained by the fact that the data are not 
-    uniformly distributed. We describe this variation across taxa as associated with available state 
-    and topology information. We compare our results with several smaller scale studies, which used 
+    simulation at 60-80\% overall, while strongly varying between clades. The cross-validation 
+    results in an accuracy of 98.17\% which is explained by the fact that the data are not uniformly 
+    distributed. We describe this variation across taxa as associated with available state and 
+    topology information. We compare our results with several smaller scale studies, which used 
     manual expert curation and conclude that computationally inferred state changes largely agree in 
@@
     in individual studies on eukaryotes e.g. in the microbiome.
+
+%---------------------------------------------------------------------------------------------------
 
@@
   %   species. It follows that we have $\approx 2.4\%$ state information. \\
-  % So far, especially small scale studies have been carried out or highly manual. In this scale, it 
+  % So far, especially small scale or highly manual studies have been carried out. In this scale, it 
   %   requires different data sources to be interconnected. \\
@@
   %   using the R package \textit{Castor} \cite{Louca2017}. \\
-  % Nevertheless, the results are convincing and even though purely computational approach which did 
-  %   not include human experts input, results coincide with prior knowledge. Also regarding the number 
-  %   of events, our estimates coincide with previous results by human experts, e.g. the study by 
-  %   Weinstein and Kuris \cite{Weinstein2016}. \\
+  % Nevertheless, the results are convincing and even though this is a purely computational approach 
+  %   which did not include human experts input, results coincide with prior knowledge. Also regarding 
+  %   the number of events, our estimates coincide with previous results by human experts, e.g. the 
+  %   study by Weinstein and Kuris \cite{Weinstein2016}. \\
 

### 2018-03-27 Paper - Latex/Paper - Skizze - v4.tex
Thesis - Introduction & Aims

@@
     trees, applied to the currently largest phylogenetic synthesis tree of Open Tree of Life (OTL)
-    \cite{Hinchliff2015}, with the application of prediciton of parasitism. \\
-
-  For about 50 years, people have been working on ancestral state reconstruction. The first paper 
-    is by Camin and Sokal, who in 1965 were working on algorithms for discrete-state data 
-    \cite{Camin1965}. Different methods have been developed and the question is which method is the 
-    most suitable for the problem at hand: The ancestral state reconstruction for a huge 
-    multifurcated tree with \colorbox{red}{binary/two discrete} states. \\
-  Royer-Carenzi et al. distinguishes two major classes of ancestral state reconstruction methods: \\
+    \cite{Hinchliff2015} to predict parasitism in Eukaryota.
+
+  For about 50 years, people have been working on ancestral state reconstruction, the inference of 
+    evolution that leads to the given data. \\
+  One of the first papers was written by Camin and Sokal, who in 1965 were working on algorithms for 
+    discrete-state data \cite{Camin1965}. Different methods have been developed and the question is 
+    which method is the most suitable for the problem at hand: the ancestral state reconstruction 
+    for a huge non-binary tree with two discrete states.
+
+  Royer-Carenzi et al. distinguish two major classes of ancestral state reconstruction methods: \\
   The first is maximum parsimony: explain the current state with the least number of state changes 
     between the child and its ancestor. \\
-  The other class she presents describes modeling the character evolution as a stochastic process and 
-    using the likelihoods to compute the possible ancestral character states. This is generally done 
-    with a continuous time Markov model \cite{RoyerCarenzi2013}.
-
-  Parsimony methods are simple methods in which you can not include information such as branch 
-    length (development time of the species). This is also their main point of criticism compared to 
-    the more complex likelihood based models. Since there are no branch lengths or other information 
-    available for the present relationship tree, and we thus can not take advantage of the 
-    other models, we decided in favor for parsimonious.
-
-  We will test the existing maximum parsimony algorithms of Fitch \cite{Fitch1971} and Sankoff 
-    \cite{Sankoff1975} for this task and estimate their predictive power. The present tree structure 
-    of OTL is not binary. A tree is multifurcated if each node has multiple ($n >= 3$) children 
-    \cite{Felsenstein2003}. \\
-  Maximum parsimony methods are developed for phylogenies, which are usually depicted as binary trees.
-    Parsimonious in phylogeny refers to favoring the tree that needs the least evolutionary change 
-    to explain the observed data. In our case, it is about the change of states 'is free-living' or 
-    'is parasitic'. \\
-    % Parsimonious in this context means to minimize the number of transitions between species states 
-    % (free-living or parasitic). 
+  The other class they present describes modeling the character evolution as a stochastic process 
+    and using the likelihoods to compute the possible ancestral character states. This is generally 
+    done with a continuous time Markov model \cite{RoyerCarenzi2013}. \\
+  \todo{Pasqualin et al. unterscheiden noch eine weitere Methode: stochastic mapping...}
+
+  Comparing the methods, we find that parsimony are methods in which you can not include information 
+    such as branch length (development time of the species). This is also their main disadvantage 
+    compared to the more complex likelihood based models. Since there are no branch lengths or other 
+    information available for the present relationship tree, and we can thus not take advantage of 
+    the other models. \\
+  The comparison of methods gives us the maximum parsimony method as the simplest and fastest method 
+    that meets all our requirements.
+
+  For an ancestral reconstruction on the phylogeny of Eukaryota, we use Open Tree of Life (OTL) 
+    \cite{Hinchliff2015}. \\
+  Phylogeny describes the evolution of species, while the taxonomy is a classification according to 
+    certain criteria in so-called taxa. \\
+  OTL is a comprehensive, dynamic and digitally available tree of life constructed from published 
+    phylogenetic trees along with a backbone of taxonomic data. Besides this, Hinchliff et al. also 
+    offer an OpenTreeOfLife-Taxonomy (OTT) with the help of which we identify the individual nodes. \\
+  It follows that the biggest 'phylogenetic tree' is this synthesis of phylogenetic trees filled 
+    with a taxonomic trees given by OTL.
+
+  For these large phylogenetic synthesis trees, however, ancestral state reconstruction has so far 
+    only been done for Bacteria and Archaea for binary traits by Goberna and Verdú \cite{Goberna2015}.
+    However, this differs from eukaryotes in the sense that complex traits such as parasitism depend
+    on more than one gene.
+
+  The present tree structure of OTL is not binary but multifurcated, meaning that each node has
+    multiple ($n >= 3$) children \cite{Felsenstein2003}. \\
+  Parsimonious in phylogeny refers to favoring the tree that needs the least evolutionary change to 
+    explain the observed data. Maximum parsimony methods have been developed for phylogenies, which 
+    are usually depicted as binary trees. Therefore, the selected parsimony methods are not directly 
+    applicable, as they were specifically applied to much smaller subtrees, where all splits are 
+    known. \\
+  We will extend and test the existing maximum parsimony algorithms of Fitch \cite{Fitch1971} and 
+    Sankoff \cite{Sankoff1975} for this task and estimate their predictive power.
+
   The Sankoff method is implemented by Louca et al. for the non-binary case and is available as an R 
     package called \textit{Castor} \cite{Louca2017}. In addition, we have implemented the Fitch 
-    method and adapted it for multifurcated trees. \\% to make it usable and comparable for our current problem.
+    method \cite{Fitch1971} \todo{hier vll die andere quelle nutzen nach der wir uns gerichtet haben?}and adapted it for multifurcated trees.
+\\% to make it usable and comparable for our current problem.
   This achieves that we can predict ancestral states and unknown states of living species for large 
-    non-binary relatives trees.
-
-  % For this purpose, various studied methods and their advantages and disadvantages will be compared. \\
-  % These algorithms were developed especially for the binary problem, since one has considered much 
-  %   smaller subtrees, of which one knows all the splits. \\
-  % By developing a whole of an entire tree of life, the problem arises that it is by no means binary. \\
-
-  To accomplish this task, a large phylogenetic tree and information about the current species states 
-    is needed. \\
-  The biggest 'phylogenetic tree' is a synthesis of phylogenetic trees filled with a taxonomic trees 
-    given by Open Tree of Life (OTL) \cite{Hinchliff2015}. %This tree is not binary and therefore the 
-    % developed algorithms are not directly applicable. Therefore, an algorithm must be found that can 
-    % work with non-binary trees. \\
-  For the information about the current states of the species we use the interaction database Global 
-    Biotic Interactions (GloBI) \cite{Poelen2014}. The data in GloBI are stored as interactions e.g. 
-    species A parasitize species B. From this we conclude that species A is parasitic and species B 
-    free-living.
-
-  At this point a few words to the term parasitic. There are different definitions. Since we use 
-    GloBI to classify species, we use their definition of parasitism. Again, in GloBi, Ontobee 
-    definitions are used \cite{Xiang2011}.
+    non-binary trees.
+
+  To accomplish this task, next to the phylogenetic tree information about the current species' 
+    states is needed. \\
+  For this information we use the interaction database Global Biotic Interactions (GloBI) 
+    \cite{Poelen2014}. The data in GloBI are stored as interactions e.g.  species A parasitize 
+    species B. From this we conclude that species A is parasitic and species B free-living. \\
+  From this data, we could specify $\sim$2.3 million leaf nodes 34,879 as free-living and 25,992 
+    as parasitic.
+
+  There are many different ways to define parasitism. Since we use GloBI to classify species, we use 
+    their definition of parasitism. Again, in GloBi, Ontobee definitions are used \cite{Xiang2011}. \\
   The interaction \textit{has parasite} is defined as: "An interaction relationship between two 
@@
   The objectives of this work are the following points: (1) Find a suitable ancestral state 
-    reconstruction method. (2) Perform reconstructing on the Eucaryotic synthesis tree of OTL. \\
+    reconstruction method. (2) Accomplish reconstructing on the Eucaryotic synthesis tree of OTL. \\
   The goal of Point 1 is to evaluate the possible methods based on a simulation of our data 
     situation. \\
-  The one by Louca et al. implemented Sankoff algorithm is the best in our comparisons. Therefore, 
-    point 2 consists of reconstructing the ancestral states and predicting the unknown leaf states. 
-    And then perform an evaluation of the results.
+  The Sankoff algorithm implemented by Louca et al. is the best in our comparisons. Therefore, 
+    point 2 consists of reconstructing the ancestral states and predicting the unknown leaf states 
+    with the aid of this algorithm. And then perform an evaluation of the results.
 
@@
 \chapter{Aims}
-  The aim of this thesis is the application of maximum parsimony algorithms to non-binary 
-    trees and very large data sets. In particular, the example find the 'Origins of Parasitism' 
-    throughout the Eukaryota Tree of Life. \\
-  For these large phylogenetic synthesis trees, however, ancestral state reconstruction has so far 
-    only been done for Bacteria and Archaea for binary traits by Goberna and Verdú \cite{Goberna2015}.
-    However, this differs from eukaryotes in the sense that complex traits such as parasitism depend
-    on more than one gene. \\
-  \todo{Warum ist das relevant? Was könnte man dann tun?}
+  The aim of this thesis is the application of maximum parsimony algorithms to non-binary trees and 
+    very large data sets to predict unknown leaf node states. \\
+  We discuss different ancestral state reconstruction methods and test the most appropriate ones on 
+    our data. Hereby, we want to find out how far it is possible to use the Open Tree of Life (OTL) 
+    to expandavailable information via phylogenetic trait prediction. As a basis for known states, 
+    we use the Global Biotic Interactions (GloBI) database, which cathegorises 34,879 and 25,992 
+    species as free-living and parasites. This data is used to perform an ancestral state 
+    reconstruction and predict states for over $\sim$2.3 million (97.34\%) leaf nodes without state 
+    information.
 
@@
       \todo{Das steht auf der Website nicht in dem Paper...} \\
-      For phylogenetic data, there are at least five big data collections, namely:
-      \begin{itemize}
-        \item ITIS (Integrated Taxonomic Information System) \cite{ITIS}
-        \item NCBI (National Center for Biotechnology Information) \cite{NCBI1988}
-        \item WORMS (World Register of Marine Species) \cite{WoRMS2018}
-        \item GBIF (Global Biodiversity Information Facility) \cite{GBIF}
-        \item OTT (OpenTreeOfLife-Taxonomy) \cite{Hinchliff2015}
-      \end{itemize}
-      ITIS is only a small set of 100\% confirmed and named species. GBIF is not composed with the help 
-        of phylogeny, the same is valid for the NCBI taxonomy. The WORMS taxonomy is a way too small 
-        dataset of mostly marine species. \\
+      % For taxonomic data, there are at least five big data collections, namely:
+      % \begin{itemize}
+      %   \item ITIS (Integrated Taxonomic Information System) \cite{ITIS}
+      %   \item NCBI (National Center for Biotechnology Information) \cite{NCBI1988}
+      %   \item WORMS (World Register of Marine Species) \cite{WoRMS2018}
+      %   \item GBIF (Global Biodiversity Information Facility) \cite{GBIF}
+      %   \item OTT (OpenTreeOfLife-Taxonomy) \cite{Hinchliff2015}
+      % \end{itemize}
+      % ITIS is only a small set of 100\% confirmed and named species. GBIF is not composed with the help 
+      %   of phylogeny, the same is valid for the NCBI taxonomy. The WORMS taxonomy is a way too small 
+      %   dataset of mostly marine species. \\
       Here the taxonomy from OTL is used because it is including most of the known taxonomies and is 
@@
       with a continuous time Markov model \cite{RoyerCarenzi2013}. \\
-    \todo{Pasqualin et al. unterscheiden noch eine weitere Methode: stochastic mapping...} \\
 
@@
 %---------------------------------------------------------------------------------------------------
-\chapter{Appendices}
+\chapter{Appendix}
   %---------------------------------------------------------------------------------------------------

### 2018-03-28 Paper - Latex/Paper - Skizze - v4.tex
Thesis - Introduction; Methods bis real data analysis

@@
 
+% The first methods were only brute force \cite{Camin1965} 
+%   Next came a set of parsimony algorithms such as: Fitch-parsimony \cite{Fitch1971}, 
+%   Wagner-parsimony \cite{Swofford1987} ... \todo{weitere?}. \\
+%   With more and more data, there is now the possibility to use more information to calculate the 
+%   probabilities of the ancestral states. In addition to the states of the leafs, algorithms could 
+%   also use branch lengths. The likelihood based algorithms came more in interest. \\
+
   Royer-Carenzi et al. distinguish two major classes of ancestral state reconstruction methods: \\
@@
 
-  Comparing the methods, we find that parsimony are methods in which you can not include information 
-    such as branch length (development time of the species). This is also their main disadvantage 
-    compared to the more complex likelihood based models. Since there are no branch lengths or other 
-    information available for the present relationship tree, and we can thus not take advantage of 
-    the other models. \\
+  One of the major disadvantages of parsimony methods is that, unlike likelihood approaches, they 
+    can not take divergence times (branch length) into account. Since the OTL does not include 
+    development times of species, this can not be considered here. \\
+  Another problem pointed out by Royer-Carenzi is that parsimony approaches are either based on 
+    predefined parameters (generalized parsimony) or on strong and often controversial assumptions, 
+    like irreversibility of transitions for dollo parsimony. This problem is unimportant to the 
+    present task because in the analysis of the entire Eukaryota tree only generalized models are 
+    meaningful. \\
+  % Comparing the methods, we find that parsimony are methods in which you can not include information 
+  %   such as branch length (development time of the species). This is also their main disadvantage 
+  %   compared to the more complex likelihood based models. Since there are no branch lengths or other 
+  %   information available for the present relationship tree, and we can thus not take advantage of 
+  %   the other models. \\
   The comparison of methods gives us the maximum parsimony method as the simplest and fastest method 
     that meets all our requirements.
+  % Parsimony-based methods are used in this work, since they are fast and fully sufficient for the 
+  %   presented use case here, following the principle of the simpler model first. \\
+
+  Felsenstein \cite{Felsenstein2003} discusses in his book two parsimony algorithms that generalize 
+    previous methods (from Camin and Sokal \cite{Camin1965}, Farris \cite{Farris1970} and others): 
+    Fitch parsimony \cite{Fitch1971} and Sankoff parsimony \cite{Sankoff1975}. Therefore, these are 
+    the methods used in this work. \\
+  % \anmerkungstext{Unter Farris war auch noch der Begriff Wagner trees in gebrauch, als 
+  %   Verallgemeinerung der parsimonious trees von Camin und Sokal. (Lydia)} \\
+  % \todo{Wagner-parsimony \cite{Swofford1987}} \\
+   For Fitch, the algorithm has been extended from binary to multifurcated trees. For the Sankoff 
+    algorithm, Louca and Doebeli have presented an implementation for non-binary trees published in 
+    an R package named \textit{castor} \cite{Louca2017}.
 
@@
   The Sankoff method is implemented by Louca et al. for the non-binary case and is available as an R 
-    package called \textit{Castor} \cite{Louca2017}. In addition, we have implemented the Fitch 
-    method \cite{Fitch1971} \todo{hier vll die andere quelle nutzen nach der wir uns gerichtet haben?}and adapted it for multifurcated trees.
+    package called \textit{Castor} \cite{Louca2017}. \\
+  Note, the original Fitch algorithm has the sole purpose of minimizing the number of transitions 
+    and not reconstructing the ancestral nodes. Felsenstein \cite{Felsenstein2003} describes a 
+    simple extension for the reconstruction. In this work, the algorithm extended to reconstruction 
+    is adapted to multifurcated trees, based on the critical reevaluation of this extension by 
+    Cunningham et al. \cite{Cunningham1998}.  
+  % In addition, we have implemented the Fitch 
+  %   method \cite{Fitch1971} \todo{hier vll die andere quelle nutzen nach der wir uns gerichtet haben?}and adapted it for multifurcated trees.
 \\% to make it usable and comparable for our current problem.
-  This achieves that we can predict ancestral states and unknown states of living species for large 
-    non-binary trees.
+  % This achieves that we can predict ancestral states and unknown states of living species for large 
+  %   non-binary trees.
 
@@
     states is needed. \\
-  For this information we use the interaction database Global Biotic Interactions (GloBI) 
-    \cite{Poelen2014}. The data in GloBI are stored as interactions e.g.  species A parasitize 
-    species B. From this we conclude that species A is parasitic and species B free-living. \\
+  Most of the largest interaction databases are offline or outdated. For example: IWDB (Interaction 
+    Web Database) \cite{IWDB2003}, Webs on the Web \cite{WOW2004}, Animal Diversity Web 
+    \cite{Myers2003} and ecoweb \cite{Cohen2010}. \\
+  We use the interaction database Global Biotic Interactions (GloBI) \cite{Poelen2014} because it is 
+    including most of the known databases and is still growing actively \cite{Poelen2014}. \\
+  The data in GloBI are stored as interactions e.g.  species A parasitize species B. From this we 
+    conclude that species A is parasitic and species B free-living. \\
   From this data, we could specify $\sim$2.3 million leaf nodes 34,879 as free-living and 25,992 
@@
 
+  In order to generate a realistic simulation, influencing parameters are investigated. \\
+  Since the transitions are minimized in an ancestral state reconstruction, this is an important 
+    parameter to consider. On the other hand, the completeness of our input data is an influencing 
+    value. Therefore, two major types are distinguished:
+  \begin{enumerate}
+    \item Biological parameters (a result of the evolutionary process):
+      \begin{itemize}
+        \item State distributions and transition probabilities
+      \end{itemize}
+    \item Distribution of missing information:
+      \begin{itemize}
+        \item Lack of information on topology ($\rightarrow$ multifurcations)
+        \item Lack of information of states of some leaf nodes
+      \end{itemize}
+  \end{enumerate}
+
 %---------------------------------------------------------------------------------------------------
@@
 \chapter{Methods}
-  As stated in the introduction, in this thesis, a maximum parsimony algorithm is applied to the 
-    whole tree of life to obtain an ancestral state reconstruction of free-living versus parasite 
-    states. \\
-  So far, these reconstructions have been made mainly on binary trees with better data availability. 
-    Therefore, a simulation is first performed to evaluate existing algorithms and decide how they 
-    may be adapted to our given problem. This is to perform the ancestral state reconstruction for a 
-    multifurcated (non-binary) tree using binary states. \\
-  Accordingly, in addition to the necessary data sets (GloBI, OTL), the chosen algorithm and the 
-    evaluation of its results, this chapter also deals with the previously performed simulation and 
-    the evaluation of the various algorithms and their parameters. \\
+  In this thesis, a maximum parsimony algorithm is applied to the Eukaryota tree to obtain an 
+    ancestral state reconstruction of free-living versus parasite states. \\
+  This chapter is divided into the following sections: the description of the data sources 
+    (section \ref{sec:methods - data sources}) used and the analysis of these data as a preparation 
+    for the simulation (section \ref{sec:methods - metadata analysis}). A description of the 
+    analyzed methods for the ancestral state reconstruction (section 
+    \ref{sec:methods - ancestral state reconstruction}) and then an explanation of how they fit the 
+    problem at hand (section \ref{sec:methods - simulation}). And at the end, the real data analysis 
+    with the Sankoff method (section \ref{sec:methods - real data analysis}). \\
   Figure \ref{fig:workflow} briefly outlines these relationships. A more detailed view of the 
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Description of data sets}
+  \section{Data sources} \label{sec:methods - data sources}
     Two types of data are needed for an ancestral state reconstruction: a tree and information about 
-      the states. \\
-    For the tree Open Tree of Life (OTL) is used \cite{Hinchliff2015} and for the state information 
-      the Global Biotic Interactions database (GloBI) is taken \cite{Poelen2014}. \\
-    % These are presented below.
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{OTL}
-      For this project a large database for phylogenetic trees and also for a taxonomic tree is needed. 
-        Since an ancestral state reconstruction algorithm is applied to the phylogenetic tree, and for 
-        the assessment and other properties the taxonomy provides much more information. \\
-      OTL gives a synthesis of phylogenetic trees (currently 819 trees) and a taxonomic tree\footnote{
+      the states.
+
+    For the subsequent analyzes on the Eukaryote tree the database of Open Tree of Life (OTL) was used 
+      (downloaded on 16.02.2018) \cite{Hinchliff2015}. This database gives a synthesis of phylogenetic 
+      trees (currently 819 trees) and a taxonomic tree\footnote{
         \hyperlink{https://tree.opentreeoflife.org/about/synthesis-release/v9.1}
         {https://tree.opentreeoflife.org/about/synthesis-release/v9.1}; Last checked: 22.03.2018.
-        }. OTL also 
-        includes the large phylogenetic database TreeBASE \cite{Hinchliff2015}. \\
-      \todo{Das steht auf der Website nicht in dem Paper...} \\
-      % For taxonomic data, there are at least five big data collections, namely:
-      % \begin{itemize}
-      %   \item ITIS (Integrated Taxonomic Information System) \cite{ITIS}
-      %   \item NCBI (National Center for Biotechnology Information) \cite{NCBI1988}
-      %   \item WORMS (World Register of Marine Species) \cite{WoRMS2018}
-      %   \item GBIF (Global Biodiversity Information Facility) \cite{GBIF}
-      %   \item OTT (OpenTreeOfLife-Taxonomy) \cite{Hinchliff2015}
-      % \end{itemize}
-      % ITIS is only a small set of 100\% confirmed and named species. GBIF is not composed with the help 
-      %   of phylogeny, the same is valid for the NCBI taxonomy. The WORMS taxonomy is a way too small 
-      %   dataset of mostly marine species. \\
-      Here the taxonomy from OTL is used because it is including most of the known taxonomies and is 
-        synthesised by preffering taxonomies that match with available phylogenetic data. Furthermore 
-        the team from OTL preferre a maximum number of species \cite{Hinchliff2015}. This is resulting 
-        in somekind of hybrid between taxonomy and phylogeny. \anmerkungstext{Wie genau ist das ein 
-        Hybrid? Genauer beschreiben, was Du damit meinst... (Thilo)} \\
-
-      A closer look is being made to some of the features of the synthesis tree. On the one hand the 
-        distribution of the taxa and on the other the distribution of the nodes on the taxa. Since this 
-        is not directly relevant for this study, there is a section in the appendix 
-        \ref{sec:otl analysis}.
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{GloBI}
-      The most big interaction databases are offline or outdated. For example: IWDB (Interaction Web 
-        Database) \cite{IWDB2003}, Webs on the Web \cite{WOW2004}, Animal Diversity Web \cite{Myers2003} 
-        and ecoweb \cite{Cohen2010}. GloBI is including most of the known ones and is still growing 
-        actively \cite{Poelen2014}. So the question was answered rather quickly which interaction 
-        database could be used. \\
-
+      }. OTL also  includes the large phylogenetic database TreeBASE \cite{Hinchliff2015}.
+
+    Furthermore the Open Tree Taxonomy (OTT) from OTL is used because it includes most of the known 
+      taxonomies and is synthesised by prefering taxonomies that match with available phylogenetic 
+      data. The team from OTL prefer a maximum number of species \cite{Hinchliff2015}, this results 
+      in the synthesis between taxonomy and phylogeny.
+
+    For the state information the Global Biotic Interactions database (GloBI) is taken 
+      \cite{Poelen2014} (downloaded on 29.01.2018). \\
     This database consists of entries of the form: species A (source) interacts with B (target). \\
@@
       }{https://github.com/jhpoelen/eol-globi-data/.../InteractType.java}; Last checked: 22.03.2018.}
-        , including those that the species source or target has become a parasite or a free-living 
-        species from the biological perspective. These are the following:
+      , including those indicating whether the species source or target has become a parasite or a 
+      free-living species from the biological perspective. They are the following:
     \begin{itemize}
@@
     Of these interactions, e.g. species A parasitize species B, the state of the species is 
-        determined, here is species A parasitic and species B free-living. The case a parasite 
+      determined, here is species A parasitic and species B free-living. In the case that a parasite 
       conquers (parasitizes) another parasite yields conflicting states for the second species. 
       This is solved by preferring parasitic. \\
-      For each species known IDs are stored in GloBI. This includes OTT (the taxonomy of OTL). All 
-        species that have stored an OTT id and have a matching interaction are formed into two lists: 
-        parasites and free-livings.
-
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  \section{Metadata analysis}
-    In order to generate a realistic simulation, influencing parameters are investigated. \\
-    Since the transitions are minimized in an ancestral state reconstruction, this is an important 
-      parameter to consider. On the other hand, the completeness of our input data are influencing 
-      values. Therefore, two major types are distinguished:
-    \begin{enumerate}
-      \item Biological parameters (A result of the evolutionary process.):
-        \begin{itemize}
-          \item transition probabilities
-        \end{itemize}
-      \item Distribution of the loss of information:
-        \begin{itemize}
-          \item Loss of topology ($\rightarrow$ mutlifurcations)
-          \item Unknown information about states of some leaf nodes
-        \end{itemize}
-    \end{enumerate}
-    The influence of these parameters are tested on our result using our simulation (section 
-      \ref{sec:methods - simulation}).
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{Transition probabilities}
-      As mentioned above, in an ancestral state reconstruction, transitions are minimized, with 
-        transition probabilities playing a role. \\
-      This subsection deals with these transition probabilities from free-living (hereinafter / as a 
-        formula FL) to parasitic (hereinafter P) and vice versa: $\mathcal{P}(FL \rightarrow P)$, 
-        $\mathcal{P}(P \rightarrow FL)$. \\
-      Different parasite types have different transition probabilities. It is very difficult to make a 
-        statement about these probabilities. It is generally assumed in this work that there are 40\% 
-        parasites and 60\% free-livings which is based on the estimates by Windsor \cite{Windsor1998} 
-        and $\mathcal{P}(FL \rightarrow P) = \mathcal{P}(P \rightarrow FL)$, as a result of the 
-        diversity of parasites and the lack of general determinations for this. These parameters are 
-        debated in subsection \ref{sec:discussion - transition probabilities} of the discussion. \\
-
-      For the maximum parsimony analysis of the real data, all transition probabilities are equated.
-        However, the used castor package \cite{Louca2017} offers the possibility to enter different 
-        transition probabilities.
-      \begin{wrapfigure}{r}{0.5\textwidth}
-        \begin{center}
-          \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.45\textwidth]{Figures/40-60.png}
-        \end{center}
-        \caption{Simulated distributions of the states: \\
-          60\% Free-living - 40\% Parasites \\
-          red: parasites, blue: free-living, \\
-          the threshold is at 0.4}
-        \label{fig:Beta distribution}
-      \end{wrapfigure}
-
-      In the simulation two beta distributions have been chosen and a threshold that indicates the change 
-        between states. \\
-      Different thresholds with different beta distributions are simulated, with different distributions 
-        of parasites and free-livings:
-        \begin{itemize}
-          \item 50\% P to 50\% FL,
-          \item 40\% P to 60\% FL,
-          \item 30\% P to 70\% FL and 
-          \item 20\% P to 80\% FL
-        \end{itemize}
-        (\todo{see results simulation, ref...}). Figure \ref{fig:Beta distribution} 
-        shows one example of these. \\
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{Missing information} \label{sec:methods - missing information}
-
-      A binary tree with $n$ leaf nodes has $n-1$ internal nodes. The present Eukaryota tree of OTL has 
-        2,293,463 leaf nodes and only 41,974 internal nodes, that is:
-      $$100-\frac{100}{(2293463-1) \times 41974} \approx 98.16 \%$$
-        missing internal nodes. This means that there is a lack of information about the underlying 
-        phylogeny. Instead of a binary tree this tree is highly multifurcated. \\
-
-      % \anmerkungstext{Nested models were compared using likelihood ratio tests, models using different 
-      %   predictors were compared according to their deviance and AIC. (Emanuel)} \\
-
-      For the present Eukaryota tree with 2,293,463 leaf nodes, 34,869 free-livings and 25,962 parasites 
-        are found, which are
-        $$100-\frac{100}{2293463 \times (34860+25962)} \approx 97.34 \%$$
-        unknown states of leaf nodes. \\
-
-      In the simulation, the influence of the multifurcation and missing data in leaf nodes on the 
-        predictive accuracy of the ancestral state reconstruction algorithms is tested. \\
-      For the real data, generalized linear models are compared with poisson respectively binomial 
+    For each species known identifyers are stored in GloBI. This includes OTT (the taxonomy of OTL). 
+      All species that have stored an OTT indentifyer and have a matching interaction are divided into 
+      two lists: parasites and free-livings.
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Metadata analysis} \label{sec:methods - metadata analysis}
+    Based on the input data, generalized linear models are compared with poisson respectively binomial 
       regression according to their residuals. In order to compare models of different complexity, the 
-        BIC (Bayesian Information Criterion) values were calculated in addition to the residuals.\\
+      BIC (Bayesian Information Criterion) values were calculated in addition to the residuals. \\
     There are two different information criteria: AIC (Akaike Information Criteria) and BIC. \\
@@
       advantageous for large samples. \\
-
-      For each node, depth, min, max and mean height were noted. Where the depth of a node is the 
-        distance (number of edges) to the root node and the height of a knot is described as the 
-        largest distance to a leaf node. In this work, a distinction is made between minimum, maximum 
-        and average distance ($\rightarrow$ min, max and mean height). \\
-      The influence in the modeling of these parameters was tested, additive as well as multiplicative. \\
-
     For all these calculations, the following R functions were used: \textit{glm()}, \textit{anova()} 
@@
 
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  \section{Ancestral state reconstruction methods} \label{sec:ancestral state reconstruction}
-    As presented in the introduction, there are some methods for ancestral state reconstruction. For 
-      this purpose, various studied methods and their advantages and disadvantages are compared below. \\
-
-  % The first methods were only brute force \cite{Camin1965} 
-  %   Next came a set of parsimony algorithms such as: Fitch-parsimony \cite{Fitch1971}, 
-  %   Wagner-parsimony \cite{Swofford1987} ... \todo{weitere?}. \\
-  %   With more and more data, there is now the possibility to use more information to calculate the 
-  %   probabilities of the ancestral states. In addition to the states of the leafs, algorithms could 
-  %   also use branch lengths. The likelihood based algorithms came more in interest. \\
-
-    Royer-Carenzi et al. distinguishes two major classes of ancestral state reconstruction methods: \\
-    The first is to explain the current state with the least number of state changes between an 
-      ancestor and his child, this is called parsimonious. \\
-    The other class she presents involves modeling the character evolution as a stochastic process and 
-      using the likelihoods to compute the possible ancestral character states. This is generally done 
-      with a continuous time Markov model \cite{RoyerCarenzi2013}. \\
-
-    One of the major disadvantages of parsimony methods is that, unlike likelihood approaches, they 
-      can not take divergece times (branch length) into account. Since the OTL does not include 
-      development times of species, this is irrelevant. \\
-    Another problem pointed out by Royer-Carenzi is that parsimony approaches are either based on 
-      predefined parameters (generalized parsimony) or on strong and often controversial assumptions, 
-      like irreversibility of transitions for dollo parsimony. Again, this problem is unimportant to 
-      the problem at hand, because in the analysis of the entire Eukaryota tree only generalized 
-      models make sense. \\
-
-    Parsimony-based methods are used in this work, since they are fully sufficient for the presented 
-      use case here. Following the principle of the simpler model first. \\
-    \anmerkungstext{Nochmal darstellen warum und selbst wenn sie fully sufficient wäre, heißt es ja 
-      nicht, dass man sie nehmen muss. Also: motiviere! (Renard)} \\
-    Felsenstein \cite{Felsenstein2003} discusses in his book two algorithms that generalize all 
-      previous methods (from Camin and Sokal \cite{Camin1965}, \todo{Kluge and Farris} and Farris 
-      \cite{Farris1970}): Fitch parsimony \cite{Fitch1971} and Sankoff parsimony \cite{Sankoff1975}. \\
-    \anmerkungstext{Unter Farris war auch noch der Begriff Wagner trees in gebrauch, als 
-      Verallgemeinerung der parsimonious trees von Camin und Sokal. (Lydia)} \\
-    \todo{Wagner-parsimony \cite{Swofford1987}} \\
-
-    Thus, the methods used in this work are those of Fitch and Sankoff. For Fitch, the algorithm has 
-      been extended from binary to multifurcated trees. For the Sankoff algorithm, Louca and Doebeli 
-      have presented an implementation for non-binary trees published in an R package named 
-      \textit{castor} \cite{Louca2017}.
+    For each node, depth, min, max and mean height were noted. The node depth was calculated as the
+      distance (number of edges) to the root node. The node height was calculated in three different 
+      ways: min, max and mean height refers to the (mininmal, maximal, mean) distance to a leaf node. \\
+    The influence in the modeling of these parameters was tested, additively as well as 
+      multiplicatively to the models.
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Ancestral state reconstruction methods} \label{sec:methods - ancestral state reconstruction}
+    The methods used to reconstruct the ancestral states are Fitch parsimony \cite{Fitch1971} and 
+      Sankoff parsimony \cite{Sankoff1975}, which are explained in the following subsections.
 
@@
     \subsection{Fitch maximum parsimony}
-      Fitch maximum parsimony is an algorithm for rooted, binary trees and describes an ancestral state 
-        reconstruction for discrete states \cite{Fitch1971} by minimizing transitions between states. \\
-      Note, the original Fitch algorithm has the sole purpose of minimizing the number of transitions 
-        and not reconstructing the ancestral nodes. Felsenstein \cite{Felsenstein2003} describes a 
-        simple extension for the reconstruction. Cunningham et al. \cite{Cunningham1998} have refined 
-        these. \todotext{Wir haben mit ein paar kleinen änderungen optimiert... und schließlich auf 
-        multifurcated angepasst...} \todotext{eigentlich ist Cunningham 'nur' eine kritische 
-        Neubewertung. Sie beziehen ihren Algortihmus auf Swofford und Maddison...} \\
-      To understand the differences to the multifurcated case, the algorithm for the binary case is 
-        briefly explained and referred to the extension. \\
+      Based on the work of Cunningham et al. \cite{Cunningham1998} the Fitch method \cite{Fitch1971} 
+        was implemented and extended by us for the multifurcated tree case. To understand the 
+        differences to the multifurcated case, the algorithm for the binary case is briefly explained 
+        and referred to the extension.
 
@@
         has only one. Leaf nodes have their state as a set (e.g. \{FL\} or \{P\}, unknown leaf nodes the 
-        union of all possible states (\{FL, P\}). \\
+        union of all possible states (\{FL, P\}).
 
       The algorithm traverses three times through the tree and fills these sets. \\
-      In each step, two sets are considered and their intersect formed. There are two cases:
+      In each step, two sets are considered and their intersection is formed. There are two cases:
       \begin{enumerate}
@@
       \end{enumerate}
-      \begin{wrapfigure}{r}{0.5\textwidth}
+      First traverse from the leaf nodes to the root: each internal node is formed from its child nodes, 
+        where the only information lies at the beginning. \\
+      Second traverse from the root node to the leafs: each internal node is formed from its parent node 
+        and its sibling node. \\
+      Last traversion (direction does not matter): build the final state for every node. It is formed 
+        from the sets of previous traversals.
+
+      (The original Fitch algorithm was designed to minimize transitions without predicting actual states 
+        of internal nodes, so it was just the first traversal.) \\
+        \begin{wrapfigure}[20]{r}{0.5\textwidth}
           \centering
@@
         \end{wrapfigure}
-      First traverse from the leaf nodes to the root / move down the tree / postorder tree traversal.
-
-        Each internal node is formed from its child nodes, where at the beginning the only information
-        lies. \\
-      Second traverse from the root node to the leafs. Each internal node is formed from its father node 
-        and its sibling node. \\
-      Last traversion (direction does not matter): Build the final state for every node. It is formed 
-        from the sets of previous traversals. \\
-      (The original Fitch algorithm was designed to minimize transitions without predicting actual states 
-        of internal nodes, so it was just the first traversal.) \\
       The extension to the non-binary case is quite obvious, but holds some opportunities. In this case, 
@@
       \begin{itemize}
-        \item The father node has (except for the root node) two state sets, because he came through 
+        \item The parent node has (except for the root node) two state sets, because he came through 
           the up-traversing previously. Are both sets used or only the first traversing?
-        \item Since there are several siblings, do \colorbox{red}{you} first of all make the cut or union, 
-          or directly in the whole with the father node?
+        \item If there are several siblings, is the cut or union made first of these, or is everything 
+          made directly including the parent node.
       \end{itemize}
@@
         both possibilities of the three sets. \\
-      Cunningham uses only the first state set of the father node \cite{Cunningham1998}. \\
+      Cunningham uses only the first state set of the parent node \cite{Cunningham1998}. \\
       From these two points four different versions of Fitch were formed:
       \begin{enumerate}
-        \item Fitch 1: First state set of father node; intersection/union of siblings first.
-        \item Fitch 2: First state set of father node; intersection/union of siblings together with father node.
-        \item Fitch 3: Both state sets of father node; intersection/union of siblings first.
-        \item Fitch 4: Both state sets of father node; intersection/union of siblings together with father node sets.
+        \item Fitch 1: First state set of parent node; intersection/union of siblings first.
+        \item Fitch 2: First state set of parent node; intersection/union of siblings together with parent node.
+        \item Fitch 3: Both state sets of parent node; intersection/union of siblings first.
+        \item Fitch 4: Both state sets of parent node; intersection/union of siblings together with parent node sets.
       \end{enumerate}
-      \begin{figure}
+
+      \begin{figure}[h!]
         \centering
-        \includegraphics[width=0.8\textwidth]{Figures/simulation_fitch_evaluation.png}
-        \caption{Test of Fitch Versions.}
+        \includegraphics[trim = 24mm 0mm 28mm 14mm, clip, width=\textwidth]{Figures/simulation_fitch_evaluation.png}
+        \caption{Test of Fitch Versions. \todo{beschriften!!}}
         \label{fig:Fitch versions}
       \end{figure}
-      These four versions were tested in the simulation with 100 trees and 10000 leaf nodes and a
-        distribution of 60\% FL to 40\% P. Figure \ref{fig:Fitch versions} shows this over all unknown 
-        node percentage. \\
+      These four versions were tested in the simulation with 100 trees and 10000 leaf nodes and
+        distributions of 70\% FL to 30\% P and 60\% FL to 40\% P. Figure \ref{fig:Fitch versions} shows 
+        this over all unknown node percentage. \\
       % At 90\% unknown nodes and 90\% of multifurcation of the internal nodes, version 1 was 89.26\%, 
@@
     \subsubsection{Sankoff}
-      Maximum parsimony algorithm from Sankoff implemented in the R package castor \cite{Louca2017}. \\
-      \todo{transition probabilities: all equal}
+      Maximum parsimony algorithm from Sankoff implemented in the R package castor \cite{Louca2017}.
+        From this the function \textit{$hsp\_max\_parsimony()$} is used with default settings including
+        $transition\_costs="all\_equal"$. \\
 
@@
   \section{Simulation}\label{sec:methods - simulation}
-    The simulation compares these different of ancestral state reconstruction algorithms with each 
+    The simulation compares these different ancestral state reconstruction algorithms with each 
       other. \\
@@
       them is compared with the implementation of the Sankoff algorithm of the \textit{Castor} package 
-      \cite{Louca2017}. \\
+      \cite{Louca2017}.
 
@@
       \centering
-      \includegraphics[width=1\textwidth]{Figures/Workflow-Simulation.png}
+      \includegraphics[width=0.95\textwidth]{Figures/Workflow-Simulation.png}
       \caption{A simulation was performed to compare different maximum parsimony algorithms. \\
@@
     The course of a simulation is shown in Figure \ref{fig:Simulation Workflow}. The individual steps 
-      are explained in the following. \\
-
-    A tree is needed to do a simulation of ancestral state reconstruction. It had to be decided whether 
-      to take the real tree or simulate a tree. In this simulation, trees are created randomly, as 
-      one can replicate a complete binary phylogentic tree. Thus, there is also the possibility to 
+      are explained in the following.
+
+    A tree is needed to perform a simulation of ancestral state reconstruction. It had to be decided 
+      whether to take the real tree or simulate a tree. In this simulation, trees are created randomly, 
+      as one can replicate a complete binary phylogentic tree. Thus, there is also the possibility to 
       simulate the multifurcation. \\
@@
         {https://github.com/biopython/biopython/blob/master/Bio/Phylo/BaseTree.py}
-      }. The credibility of this choice is examined in subsection 
-        \ref{sec:discussion - simulate phylogeny} of the discussion.\\
+      }.
 
     The next step is to simulate states for all nodes. \\
-    The root node is defined as ancestor of all subsequent species and in this case, determined to be
-      free-living. Therefore, a beta distribution for free-living is used at the beginning. Now 
-      traverse from the root to the leaf nodes, always pulling out of the current distribution until 
-      the randomly drawn number is above the threshold and the new node changes state. Figure 
-      \ref{fig:set node states} shows a part of this simulating states. \\
-    To ensure that the parameter of the binomial distribution is restricted to the [0,1] interval, it 
-      is modeled with a beta distribution as in Figure \ref{fig:set node states}. \\
-
-    After traversing through the tree, each state is saved in a nodelist associated with the  
-    \begin{wrapfigure}[21]{r}{0.65\textwidth}
+    Here the influence of the biological parameters as transition probabilities and distributions of
+      \begin{wrapfigure}[21]{r}{0.55\textwidth}
         \centering
-      \includegraphics[width=0.65\textwidth]{Figures/40-60_all.jpg}
+        \includegraphics[width=0.55\textwidth]{Figures/40-60_all.jpg}
         \caption{Set node states: Distribution of states (left); traversion through the tree (right). \\
@@
       \end{wrapfigure} 
-    node ID which is the OTT from OTL. \\
-
-% simulate loss of information
-    Here begins the simulation of the lost information. This is on the one hand the states and on the 
-      other the topology of the tree. \\
+      states is included. \\
+    Since there was no statement about general transition probabilities, these are all set the same: \\
+    $\mathcal{P}(FL \rightarrow P) = \mathcal{P}(P \rightarrow FL)$.
+
+    For the distributions of states different ratios of parasites (P) to free-livings (FL) are 
+      simulated with the help of beta distributions and a given threshold:
+      \begin{itemize}
+        \item 50\% P to 50\% FL,
+        \item 40\% P to 60\% FL,
+        \item 30\% P to 70\% FL and 
+        \item 20\% P to 80\% FL.
+      \end{itemize}
+
+    Procedure: The root node is defined as ancestor of all subsequent species and in this case, 
+      determined to be free-living. Therefore, the beta distribution for free-living is used at the 
+      beginning. Now traverse from the root to the leaf nodes, always pulling out of the current 
+      distribution until the randomly drawn number is above the threshold and the new node changes 
+      state. Figure \ref{fig:set node states} shows a part of this simulating states and the 
+      associated distributions.
+    % To ensure that the parameter of the binomial distribution is restricted to the [0,1] interval, it 
+    %   is modeled with a beta distribution as in Figure \ref{fig:set node states}. \\
+
+    After traversing through the tree, each state is saved in a nodelist associated with the node 
+      indentifyer which is the OTT from OTL.
+
+    Here begins the simulation of the lack of information, such as the lack of information on topology 
+      (multifurcation) and of states of some leaf nodes.
+    % = In the simulation, the influence of the multifurcation and missing data in leaf nodes on the 
+    %   predictive accuracy of the ancestral state reconstruction algorithms is tested.
 
@@
       nodes. And beyond only a small percentage of these. All information about the states of the 
-      internal node and one leaf node is 'forgotten' and stored in another column to the node. \\
+      internal node and one leaf node is removed and stored in another column to the node.
 
@@
       divisions in the tree are not known, so the real tree is not binary. This multifurcation is 
-      simulated by an equally distributed percentage of forgotten internal nodes. \\
-
-    Different percentages of forgetting information are simulated, see figure 
-      \ref{fig:influence of unknown data} in the results. \\
+      simulated by an equally distributed percentage of forgotten internal nodes.
+
+    Different percentages of removed information are simulated.
 
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Real data analysis}
+  \section{Real data analysis} \label{sec:methods - real data analysis}
     \todo{Evaluation section in methods?}
@@
     algorithms because they are best suited to the problem at hand. The reason for this can be found 
-    in section \ref{sec:ancestral state reconstruction}. We tested these on different simulations of 
-    the data and compared their predictive power (section \ref{sec:results - simulation}). \\
+    in section \ref{sec:methods - ancestral state reconstruction}. We tested these on different 
+    simulations of the data and compared their predictive power (section 
+    \ref{sec:results - simulation}). \\
   We used the Sankoff algorithm \cite{Sankoff1975} implemented by Louca et al. \cite{Louca2017}, 
@@
 %     of unknown states of leaf nodes. \\
-%    
+\todo{noch irgendwo einfügen:} \\
+The number of nodes in the tree corresponding to a taxonomic rank was tabulated. \\
+For the classical taxonomic ranks phylum, class, order, family, genus xyz was was found (appendix 5.2).
+% A closer look is taken at some of the features of the synthesis tree on the one hand the 
+% distribution of the taxa and on the other the distribution of the nodes on the taxa. Since this 
+% is \colorbox{red}{not directly relevant} for this study, this section has been moved to the appendix 
+% \ref{sec:otl analysis}.
+   
   %---------------------------------------------------------------------------------------------------
@@
   \section{Metadata analysis - Missing information} \label{sec:results - missing information}
-    As previously presented in the methods (section \ref{sec:methods - missing information}), we have 
+    As previously presented in the methods (section \ref{sec:methods - metadata analysis}), we have 
       two types of missing information: unknown states of leaf nodes and multifurcation. \\
@@
       missing nodes. \\
+
+      \todo{insert:} \\
+      A binary tree with $n$ leaf nodes has $n-1$ internal nodes. The present Eukaryota tree of OTL has 
+      2,293,463 leaf nodes and only 41,974 internal nodes, that is:
+    $$100-\frac{100}{(2293463-1) \times 41974} \approx 98.16 \%$$
+      missing internal nodes. This means that there is a lack of information about the underlying 
+      phylogeny. Instead of a binary tree this tree is highly multifurcated. \\
+
+    % \anmerkungstext{Nested models were compared using likelihood ratio tests, models using different 
+    %   predictors were compared according to their deviance and AIC. (Emanuel)} \\
+
+    For the present Eukaryota tree with 2,293,463 leaf nodes, 34,869 free-livings and 25,962 parasites 
+      are found, which are
+      $$100-\frac{100}{2293463 \times (34860+25962)} \approx 97.34 \%$$
+      unknown states of leaf nodes. \\
+    \todo{-----} \\
+
     We calculated these percentages of missing nodes and also missing state information for some 
@@
     We found also 57,352 (not distinct!) source species and 809,993 (not distinct!) target species 
-      without OTT ids. Since we currently use only OTT ids, we could not use this information. \\
+      without OTT indentifyers. Since we currently use only OTT indentifyers, we could not use this information. \\
     At this point there is thus the possibility to use more of the existing data, if one performs a 
-      matching with the other Ids.
+      matching with the other indentifyers.
 
@@
   \section{Simulation} \label{sec:discussion - simulation}
+
+\todo{einbauen....}
+  As mentioned above, in an ancestral state reconstruction, transitions are minimized, with 
+  transition probabilities playing a role. \\
+\colorbox{red}{This subsection deals with} these transition probabilities from free-living (hereinafter / as a 
+  formula FL) to parasitic (hereinafter P) and vice versa: $\mathcal{P}(FL \rightarrow P)$, 
+  $\mathcal{P}(P \rightarrow FL)$. \\
+Different parasite types have different transition probabilities. It is very difficult to make a 
+  statement about these probabilities. It is generally assumed in this work that there are 40\% 
+  parasites and 60\% free-livings which is based on the estimates by Windsor \cite{Windsor1998} 
+  and $\mathcal{P}(FL \rightarrow P) = \mathcal{P}(P \rightarrow FL)$, as a result of the 
+  diversity of parasites and the lack of general determinations for this. These parameters are 
+  debated in subsection \ref{sec:discussion - transition probabilities} of the discussion. \\
+
+  However, the used castor package \cite{Louca2017} offers the possibility to enter different 
+  transition probabilities.
+
+  Wieviele Übergänge gab es dabei? Hast du die gleich (ähnlich groß) gehalten?
+  Der Anteil von Parasiten und Freilebenden ist ja nicht gleich der Transition probability. Das sind zwei verschiedene Dinge...auch wenn die Transition probability den Anteil ergibt. 
+  neben dem Anteil der P/FL ist auch die Anzalhl der Übergänge zu berücksichtigen!
+  50/50 kann man in einem Baum mit 1000 nodes mit einem einzigen Übergan erreichen, der die eine Häfte des Baumes ändert.
+  50/50 kann man aber genauso gut mit einem Übergan auf JEDER edge erreichen. Dann würde sich immer ein P mit einem FL knoten abwechselnn....
+
+... für die Diskussion!
+
+\todo{-----}
+
     The aim of the simulation was to test the influence of various unknown or unsafe parameters in 

### 2018-03-29 Paper - Latex/Paper - Skizze - v4.tex
Thesis - part of Results...

@@
   % \todo{Wagner-parsimony \cite{Swofford1987}} \\
-   For Fitch, the algorithm has been extended from binary to multifurcated trees. For the Sankoff 
+   For Fitch, the algorithm has been extended from binary to non-binary trees. For the Sankoff 
     algorithm, Louca and Doebeli have presented an implementation for non-binary trees published in 
@@
   The present tree structure of OTL is not binary but multifurcated, meaning that each node has
-    multiple ($n >= 3$) children \cite{Felsenstein2003}. \\
+    multiple ($n > 2$) children or in other words its degree, number of adjacent nodes, is greater 
+    than 3 \cite{Felsenstein2003}. \\
   Parsimonious in phylogeny refers to favoring the tree that needs the least evolutionary change to 
@@
 
-    For the subsequent analyzes on the Eukaryote tree the database of Open Tree of Life (OTL) was used 
+    For the subsequent analyzes on the Eukaryote tree the database of Open Tree of Life (OTL) is used 
       (downloaded on 16.02.2018) \cite{Hinchliff2015}. This database gives a synthesis of phylogenetic 
@@
       regression according to their residuals. In order to compare models of different complexity, the 
-      BIC (Bayesian Information Criterion) values were calculated in addition to the residuals. \\
+      BIC (Bayesian Information Criterion) values are  calculated in addition to the residuals. \\
     There are two different information criteria: AIC (Akaike Information Criteria) and BIC. \\
@@
       advantageous for large samples. \\
-    For all these calculations, the following R functions were used: \textit{glm()}, \textit{anova()} 
+    For all these calculations, the following R functions are  used: \textit{glm()}, \textit{anova()} 
       and \textit{BIC()}.
@@
 
-    For each node, depth, min, max and mean height were noted. The node depth was calculated as the
-      distance (number of edges) to the root node. The node height was calculated in three different 
+    For each node, depth, min, max and mean height are  noted. The node depth is calculated as the
+      distance (number of edges) to the root node. The node height is calculated in three different 
       ways: min, max and mean height refers to the (mininmal, maximal, mean) distance to a leaf node. \\
-    The influence in the modeling of these parameters was tested, additively as well as 
+    The influence in the modeling of these parameters is tested, additively as well as 
       multiplicatively to the models.
@@
       Based on the work of Cunningham et al. \cite{Cunningham1998} the Fitch method \cite{Fitch1971} 
-        was implemented and extended by us for the multifurcated tree case. To understand the 
+        is implemented and extended by us for the multifurcated tree case. To understand the 
         differences to the multifurcated case, the algorithm for the binary case is briefly explained 
@@
 
-      (The original Fitch algorithm was designed to minimize transitions without predicting actual states 
-        of internal nodes, so it was just the first traversal.) \\
+      (The original Fitch algorithm is designed to minimize transitions without predicting actual states 
+        of internal nodes, so it is just the first traversal.) \\
         \begin{wrapfigure}[20]{r}{0.5\textwidth}
@@
         also be formed over more than two sets. Also in the second traversing, there may be several 
-        sibling nodes. However, there are several possibilities here that were all tested and compared 
+        sibling nodes. However, there are several possibilities here that are all tested and compared 
         in the simulation. Some of these options are already available in the binary case:
@@
       Cunningham uses only the first state set of the parent node \cite{Cunningham1998}. \\
-      From these two points four different versions of Fitch were formed:
+      From these two points four different versions of Fitch are formed:
       \begin{enumerate}
@@
       \end{figure}
-      These four versions were tested in the simulation with 100 trees and 10000 leaf nodes and
+      These four versions are tested in the simulation with 100 trees and 10000 leaf nodes and
         distributions of 70\% FL to 30\% P and 60\% FL to 40\% P. Figure \ref{fig:Fitch versions} shows 
         this over all unknown node percentage. \\
-      % At 90\% unknown nodes and 90\% of multifurcation of the internal nodes, version 1 was 89.26\%, 
-      %   version 2 was 89.26\%, version 3 was 89.35\%, and version 4 was 89.31\% correct. Therefore, 
-      %   only version 3 was used for all further simulations.
-      At 95\% unknown nodes and 95\% of multifurcation of the internal nodes, version 1 was 88.37\%, 
-        version 2 was 88.37\%, version 3 was 88.4\%, and version 4 was 88.39\% correct. Therefore, 
-        only version 3 was used for all further simulations.
+      % At 90\% unknown nodes and 90\% of multifurcation of the internal nodes, version 1 is 89.26\%, 
+      %   version 2 is 89.26\%, version 3 is 89.35\%, and version 4 is 89.31\% correct. Therefore, 
+      %   only version 3 is used for all further simulations.
+      At 95\% unknown nodes and 95\% of multifurcation of the internal nodes, version 1 is 88.37\%, 
+        version 2 is 88.37\%, version 3 is 88.4\%, and version 4 is 88.39\% correct. Therefore, 
+        only version 3 is used for all further simulations.
 
@@
       \includegraphics[width=0.95\textwidth]{Figures/Workflow-Simulation.png}
-      \caption{A simulation was performed to compare different maximum parsimony algorithms. \\
+      \caption{A simulation is performed to compare different maximum parsimony algorithms. \\
         The course of the simulation with influence of the metadata analysis from the real data can
@@
 
-    A tree is needed to perform a simulation of ancestral state reconstruction. It had to be decided 
+    A tree is needed to perform a simulation of ancestral state reconstruction. It has to be decided 
       whether to take the real tree or simulate a tree. In this simulation, trees are created randomly, 
@@
       states is included. \\
-    Since there was no statement about general transition probabilities, these are all set the same: \\
+    Since there is no statement about general transition probabilities, these are all set the same: \\
     $\mathcal{P}(FL \rightarrow P) = \mathcal{P}(P \rightarrow FL)$.
@@
   \section{Real data analysis} \label{sec:methods - real data analysis}
-    \todo{Evaluation section in methods?}
-    \begin{itemize}
-      \item Import tree
-      \item Import interactions
-      \item run castor algorithm / and others?
-      \item interprete results (leave-100-out cross-validation)
-    \end{itemize}
-    We then evaluated the results in two ways. On the one hand, we have examined the results of some 
-      subtrees for their credibility with the help of biological background knowledge. On the other 
-      hand, we performed a leave-100-out cross-validation.
+    For the evaluation of real data results, a leave-100-out cross-validation is performed. For this 
+      purpose 100 randomly distributed 100 states are left out.
+
+    Analogous to the missing leaf node states, generalized linear models with binomial regression are 
+      compared according to their residuals, based on the "true" / "false" prediction. \\
+    Again, in order to compare models of different complexity, the BIC (Bayesian Information Criterion) 
+      values are calculated in addition to the residuals. \\
+    For all these calculations, the following R functions are used: \textit{glm()}, \textit{anova()} 
+      and \textit{BIC()}.
 
@@
       \hyperlink{github.com/Irallia/IZW-HU-Parasites}{github.com/Irallia/IZW-HU-Parasites}. \\
-    Most of the code was written in Python. The analyzes and the use of the Castor package in R. There 
-      are some shell scripts to execute whole workflows.
+    Most of the code is written in Python, the analyzes and the use of the Castor package in R. Some 
+      shell scripts are used to execute whole workflows.
 
@@
 \chapter{Results}
-  This work deals with the ancestral state reconstruction of the entire Eukaryota relatives tree. \\
+  This work deals with the ancestral state reconstruction of the entire Eukaryota relatives tree.
 
   For this reconstruction, we first analyzed our data. This is the tree of OTL \cite{Hinchliff2015}
-    and the data for the leaf nodes (free-living or parasite states) from GloBI \cite{Poelen2014} 
-    (section \ref{sec:results - missing information}). \\
+    and the data for the leaf node states (free-living or parasite states) from GloBI 
+    \cite{Poelen2014} (section \ref{sec:results - missing information}), where we have determined 
+    that the entire Eukaryota tree is 89.45\% multifurcated (missing internal nodes) and that we do 
+    not have any state information for 97.34\% nodes. \\
+  In addition, we tested different models for these two paramters and found out that multifurcation 
+    can best be modeled with the taxa 'order' multiplied by the mean height of the knots. Also, the 
+    missing states could be modeled with the taxa 'order' and in this case multiplied by the depth 
+    of the nodes.
+
   Next we compared different possible methods. We decided to take a closer look at maximum parsimony 
-    algorithms because they are best suited to the problem at hand. The reason for this can be found 
-    in section \ref{sec:methods - ancestral state reconstruction}. We tested these on different 
-    simulations of the data and compared their predictive power (section 
+    algorithms because they are fast and best suited to the problem at hand. We tested these on 
+    different simulations of the data and compared their predictive power (section 
     \ref{sec:results - simulation}). \\
-  We used the Sankoff algorithm \cite{Sankoff1975} implemented by Louca et al. \cite{Louca2017}, 
-    which performs best, for the actual reconstruction on the real data. \\
-
-  We then evaluated the results in two ways. On the one hand, we have examined the results of some 
-    subtrees for their credibility with the help of biological background knowledge (subsection 
-    \ref{sec:results - biological view}). On the other hand, we performed a leave-100-out cross-validation
-    (Subsection \ref{sec:results - cross-validation}) and predicted approximately 98.17\% states 
-    correct.
-
-%   Otherwise, this chapter is mainly about the actual reconstruction of the states. This means, on 
-%     one hand investigation of origins and losses of the inner nodes and on the other, the prediction 
-%     of unknown states of leaf nodes. \\
-\todo{noch irgendwo einfügen:} \\
-The number of nodes in the tree corresponding to a taxonomic rank was tabulated. \\
-For the classical taxonomic ranks phylum, class, order, family, genus xyz was was found (appendix 5.2).
-% A closer look is taken at some of the features of the synthesis tree on the one hand the 
-% distribution of the taxa and on the other the distribution of the nodes on the taxa. Since this 
-% is \colorbox{red}{not directly relevant} for this study, this section has been moved to the appendix 
-% \ref{sec:otl analysis}.
-   
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  \section{Metadata analysis - Missing information} \label{sec:results - missing information}
-    As previously presented in the methods (section \ref{sec:methods - metadata analysis}), we have 
-      two types of missing information: unknown states of leaf nodes and multifurcation. \\
-
-    A tree is multifurcated if there are nodes that have more than two children. In the case of a 
-      phylogenetic tree, the ridge of multifurcation describes the amount of lack of information about 
-      the topology of the tree. A complete phylogenetic tree would be binary, meaning that the number 
-      of leaf nodes equals the number of internal nodes minus one. Since we only work with a 
-      artificially constructed tree (synthesis of several phylogenetic trees), this tree is strongly 
-      multifurcated: It has 241,974 internal nodes for 2,293,463 leaf nodes $\rightarrow$ 98.16 \% 
-      missing nodes. \\
-
-      \todo{insert:} \\
-      A binary tree with $n$ leaf nodes has $n-1$ internal nodes. The present Eukaryota tree of OTL has 
-      2,293,463 leaf nodes and only 41,974 internal nodes, that is:
-    $$100-\frac{100}{(2293463-1) \times 41974} \approx 98.16 \%$$
+  We compared them with the result that the Sankoff algorithm performs significantly better than 
+    Fitch. The multifurcation rate has little impact on Sankoff, but Fitch's prediction 
+    significantly breaks down at more than 60\% missing internal nodes. However, the amount of 
+    missing node state information has a linear impact on both, as does the ratio of free-living to 
+    parasitic (the more balanced, the worse is the prediction).
+
+  As a result, we used the Sankoff algorithm \cite{Sankoff1975} implemented by Louca et al. 
+    \cite{Louca2017}, which performed best, for the actual reconstruction on the real data. \\
+    \todo{... biological view}
+  %  On the one hand, we have examined the results of some 
+    % subtrees for their credibility with the help of biological background knowledge (subsection 
+    % \ref{sec:results - biological view}). On the other hand, we
+  We evaluated these by performing a leave-100-out cross-validation and predicted approximately 
+    98.17\% of the omitted states correct (subsection \ref{sec:results - cross-validation}). \\
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Availability of internal nodes and state information} \label{sec:results - missing information}
+    As previously presented, we have two types of missing information: unknown states of leaf nodes 
+      and multifurcation.
+
+    A tree is multifurcated if there are nodes that have more than two children. A binary tree with 
+      $n$ leaf nodes has $n-1$ internal nodes. The present Eukaryota tree of OTL has 2,293,463 leaf 
+      nodes and only 241,974 internal nodes, that is:
+    $$100-\frac{100}{(2293463-1) \times 241974} \approx 89.45\%$$
       missing internal nodes. This means that there is a lack of information about the underlying 
-      phylogeny. Instead of a binary tree this tree is highly multifurcated. \\
-
-    % \anmerkungstext{Nested models were compared using likelihood ratio tests, models using different 
-    %   predictors were compared according to their deviance and AIC. (Emanuel)} \\
-
-    For the present Eukaryota tree with 2,293,463 leaf nodes, 34,869 free-livings and 25,962 parasites 
-      are found, which are
-      $$100-\frac{100}{2293463 \times (34860+25962)} \approx 97.34 \%$$
-      unknown states of leaf nodes. \\
-    \todo{-----} \\
-
-    We calculated these percentages of missing nodes and also missing state information for some 
-      subtrees and plotted them in table \ref{table:percentage loss information subtrees}. \\
+      phylogeny. Instead of a binary tree this tree is highly multifurcated.
+
     \begin{table}[h!]
@@
           \hline \hline
-          Eukaryota       & 97.34\%  & 98.16\% \\
+          Eukaryota       & 97.34\%  & 89.45\% \\
           \hline \hline
@@
       \caption{Examination of subtrees regarding missing information. \\
-        The percentage values show the ratio of missing information of: unknown states (missing state 
+        The percentage values show the proportion of missing information of: unknown states (missing state 
           information of leaf nodes) and multifurcation (missing internal nodes). \\
@@
           (Insecta). \\
-        The two by far smallest values were highlighted in green.} 
+        The two by far smallest values are highlighted in green.} 
       \label{table:percentage loss information subtrees} 
@@
 
-    We also have for a first overview we collected for each node its number of children (degree $-1$), 
-      and plotted this in two histograms, see figure \ref{fig:childrenOfNodes}. \\
-    \begin{figure}
+    For the missing state information the present Eukaryota tree with 2,293,463 leaf nodes, 34,869 
+      free-livings and 25,962 parasites are found. This gives
+      $$100-\frac{100}{2293463 \times (34860+25962)} \approx 97.34\%$$
+      unknown states of leaf nodes.
+
+    We calculated these percentages of missing nodes and also missing state information for some 
+      subtrees and plotted them in table \ref{table:percentage loss information subtrees}.
+
+    \begin{figure}[h!]
       \centering
@@
         \includegraphics[trim = 0mm 0mm 30mm 0mm, clip, width=0.9\textwidth]{Figures/multifurc_small.pdf}
-        \caption{Histogram with $binwidth = 1$. Higher multifurcation than 30 has been cut off. \\ light blue: binary; \\ dark blue: multifurcation}
+        \caption{Histogram with $binwidth = 1$. Higher multifurcation than 30 has been cut off. \\
+          light blue: binary; \\ dark blue: multifurcation}
       \end{subfigure}
-      \caption{Histograms about the multifurcation of the internal nodes of the synthesis tree. \\
-        For each node, the number of children (degree $-1$) was collected. A node is multifurcated 
-        if it has more than two children, so we deducted two from each number of children. We have 
-        plotted this in two histograms: number of children $-2$ on the x-axis with log scale and the 
-        number of nodes with this amount on the y-axis.}
+      \caption{Histograms showing the multifurcation of the internal nodes of the synthesis tree. \\
+        For each node, the number of children (degree $-1$) is collected. A node is multifurcated 
+        if it has more than two children, so we deducted two from each number of children. The two 
+        histograms show: number of children $-2$ on the x-axis with log scale and the number of nodes 
+        with this amount on the y-axis.}
       \label{fig:childrenOfNodes}
     \end{figure}
+
+    For a first overview, we collected for each node its number of children (degree $-1$), 
+      and plotted this in two histograms, see figure \ref{fig:childrenOfNodes}.
+
     The multifurcation affects only the internal nodes. We collected the number of children $-2$ of 
-      every node (a node with two children is binary). That means it describes the number of nodes 
-      which we have lost from the real (binary) phylogenetic tree. \\
-    It can be recognized that we are very far from a binary tree. \\
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{Data artifacts}
-      At this point we also found out that there are nodes with only one child node (55,700 nodes). \\
-      The most of these nodes are next to a leaf node, others are deep in the tree (3,956 with height 
-        $>2$). They are probably a result from the fact that taxonomic information has been incorporated 
-        into a phylogeny. \\
-      \anmerkungstext{probably? Da ist eine Spekulation hier? Kann man das nicht herausfinden? 
-        Spekulieren solltest du am ehesten erst in der Diskussion. (Thilo)} \\
-      Some examples of these nodes are:
-      \begin{itemize}
-        \item Nephroselmidophyceae: (class) \\
-          https://tree.opentreeoflife.org/opentree/argus/ottol@1038762
-        \item Phrynocrinidae: (family) \\
-          https://tree.opentreeoflife.org/opentree/argus/ottol@3647979
-        \item Elaeocarpus sylvestris: \\
-          https://tree.opentreeoflife.org/opentree/argus/opentree9.1@ott166969
-      \end{itemize}
+      these nodes (because a node with two children is binary). That means it describes the number of 
+      nodes which we have lost from the real (binary) phylogenetic tree. \\
+    It can be recognized that we are very far from a binary tree.
 
@@
         \caption{BIC (Bayesian information criterion) values of the multifurcation models. \\
-          These models were created with the R function \textit{glm()} and compared with the 
+          These models are created with the R function \textit{glm()} and compared with the 
             \textit{BIC()} function. This results in the listed BIC values.}
@@
         the finest model available here is also the best one of these. Lower taxa than orders (e.g. 
-        family) were computationally too expensive to calculate. \\
+        family) are computationally too expensive to calculate. \\
       The model \textit{multifurc $\sim$ order * mean.height} turns out to be the best of our models, 
@@
         \caption{BIC (Bayesian information criterion) values unknown state information models. \\
-          These models were created with the R function \textit{glm()} and compared with the 
+          These models are created with the R function \textit{glm()} and compared with the 
             \textit{BIC()} function. This results in the listed BIC values.}
@@
     Since we have a lot of missing data in most subtrees (both internal nodes and state informations), 
-      the Sankoff gives a better prediction and was thus used for real data analysis.
+      the Sankoff gives a better prediction and is thus used for real data analysis.
 
@@
         \end{center}
-        \caption{Some selected phyla (subtrees), only leaf nodes, were examined for the evolution 
+        \caption{Some selected phyla (subtrees), only leaf nodes, are examined for the evolution 
           of the amount and percentage of given data to predicted data.}
@@
         \caption{Parasites of Phylum: Chordata. \\
-          All parasite data of the chordata were mapped into a rough taxonomy (phylum, class, order, 
+          All parasite data of the chordata are mapped into a rough taxonomy (phylum, class, order, 
             family) in order to understand their distribution and affiliation. \\
@@
         the Turbellaria are not monophyletic. But we will not go into that here. \\
-      For the Platyhelminthes we had more state information for the leaf nodes compared to the other 
+      For the Platyhelminthes we have more state information for the leaf nodes compared to the other 
         considered subtrees, see Table \ref{table:percentage loss information subtrees}. We start with 
@@
       The problem at this point, however, is: Hallan speaks of the fact that only 23,000 species 
-        were described by the Nematoda but is it assumed that one million or more species are in this 
+        are described by the Nematoda but is it assumed that one million or more species are in this 
         phylum.\footnote{J. Hallan, unpublished; 
@@
         \end{center}
-        \caption{Some selected phyla (subtrees), including internal nodes, were examined for the evolution 
+        \caption{Some selected phyla (subtrees), including internal nodes, are examined for the evolution 
         of the amount and percentage of given data to predicted data.}
@@
         \end{center}
-        \caption{All kingdoms (subtrees), only leaf nodes, were examined for the evolution of the 
+        \caption{All kingdoms (subtrees), only leaf nodes, are examined for the evolution of the 
           amount and percentage of given data to predicted data.}
@@
         \end{center}
-        \caption{All kingdoms (subtrees), inkluding internal nodes, were examined for the evolution of the 
+        \caption{All kingdoms (subtrees), inkluding internal nodes, are examined for the evolution of the 
         amount and percentage of given data to predicted data.}
@@
 
-      Of these 10,000 nodes, 9,238 were unique. From the unique nodes, we predicted approximately 
+      Of these 10,000 nodes, 9,238 are unique. From the unique nodes, we predicted approximately 
         98.17\% correct and thus 1.82\% wrong, with duplicate draws always having the same prediction 
@@
       We have again dealt with the question of how this data is best modeled. The influence of the taxa 
-        (kingdom, phylum, class) and the depth of the leaf nodes was re-modeled and the BICs compared 
-        (table \ref{table:BIC cross-validation}). Lower taxa than classes (e.g. order) were 
+        (kingdom, phylum, class) and the depth of the leaf nodes is re-modeled and the BICs compared 
+        (table \ref{table:BIC cross-validation}). Lower taxa than classes (e.g. order) are 
         computationally too expensive to calculate. \\
@@
         \caption{BIC (Bayesian information criterion) values of cross-validation prediction models. \\
-          These models were created with the R function \textit{glm()} and compared with the 
+          These models are created with the R function \textit{glm()} and compared with the 
             \textit{BIC()} function. This results in the listed BIC values.}
@@
         \caption{Statistics about the leave-100-out cross-validation \\
-          The distance between original and new states was calculated using the Euclidean metric. This 
-            was summed over all states / all leaf node states and all internal node states. \\
+          The distance between original and new states is calculated using the Euclidean metric. This 
+            is summed over all states / all leaf node states and all internal node states. \\
           The lower half of the table describes the distribution of the 'lost' states between parasites 
@@
 \chapter{Discussion}
+
+  \todo{Aus den models kann man auch schließen: highly variable throughout our tree}
+
+  \todo{noch irgendwo einfügen:} \\
+  The number of nodes in the tree corresponding to a taxonomic rank is tabulated. \\
+  For the classical taxonomic ranks phylum, class, order, family, genus xyz is found (appendix 5.2).
+  % A closer look is taken at some of the features of the synthesis tree on the one hand the 
+  % distribution of the taxa and on the other the distribution of the nodes on the taxa. Since this 
+  % is \colorbox{red}{not directly relevant} for this study, this section has been moved to the appendix 
+  % \ref{sec:otl analysis}.
+
   This chapter deals with the question of how trustworthy our result of the ancestral state 
@@
       misinformation. \\
-    We were able to report some of these directly to Globi.
+    We are able to report some of these directly to Globi.
 
@@
 
-    The aim of the simulation was to test the influence of various unknown or unsafe parameters in 
+    The aim of the simulation is to test the influence of various unknown or unsafe parameters in 
       order to test the credibility of the prediction. \\
@@
       be more subtaxa or 'unranked' nodes. But the closer we get to the root, the more the pure
-      taxonomic tree is reflected. If the tree were binary, the taxa would have to double. But the 
+      taxonomic tree is reflected. If the tree are binary, the taxa would have to double. But the 
       multipliers for some are much bigger and for others much smaller, which \colorbox{red}{you} can see in in figure 
@@
       \caption{Residuals of multifurcation models \\
-        These models were created with the R function \textit{glm()} and compared with the 
+        These models are created with the R function \textit{glm()} and compared with the 
           \textit{anova()} function. This results in the listed residuals.}
@@
       \caption{Residuals of unknown information models \\
-        These models were created with the R function \textit{glm()} and compared with the 
+        These models are created with the R function \textit{glm()} and compared with the 
           \textit{anova()} function. This results in the listed residuals.}
@@
       \caption{Residuals of cross-validation prediction \\
-        These models were created with the R function \textit{glm()} and compared with the 
+        These models are created with the R function \textit{glm()} and compared with the 
           \textit{anova()} function. This results in the listed residuals.}

### 2018-03-29 code/metadata/analyse_input.R

@@ -208,21 +208,21 @@ print('--------------------------------------------------')
 
 inner.taxa$multifurc <- inner.taxa$nr_children-1
 
-# ggplot(inner.taxa, aes(multifurc)) +
-#     geom_histogram(col="black") +
-#     scale_y_log10() +
-#     labs(x="number of children", y="number of nodes")
-# ggsave("multifurc.pdf")
+ggplot(inner.taxa, aes(multifurc)) +
+    geom_histogram(col="black") +
+    scale_y_log10() +
+    labs(x="number of children -2", y="number of nodes")
+ggsave("multifurc.pdf")
 
-# ggplot(inner.taxa, aes(multifurc)) +
-#     geom_histogram( 
-#         col="black", 
-#         binwidth = 1,
-#         aes(fill=..count..)) +
-#     xlim(0, 30) +
-#     scale_y_log10() +
-#     labs(x="number of children", y="number of nodes")
-# ggsave("multifurc_small.pdf")
+ggplot(inner.taxa, aes(multifurc)) +
+    geom_histogram( 
+        col="black", 
+        binwidth = 1,
+        aes(fill=..count..)) +
+    xlim(0, 30) +
+    scale_y_log10() +
+    labs(x="number of children -2", y="number of nodes")
+ggsave("multifurc_small.pdf")
 
 print('--------------------------------------------------')
 print('-------------------------multifurc data-------------------------')

### 2018-03-29 code/simulation/get_plots.py

@@ -77,20 +77,23 @@ def main():
     # ------------------------------------------------------------------------
 
     PLOT_NUMBER = 1
-    f, axs = plt.subplots(ROWS, 1, figsize=(4, 10))
-    plt.suptitle('Fitch Versions and Unknown Data', fontsize=12, y=1)
+    f, axs = plt.subplots(2, 2, figsize=(12, 5))
+    # plt.suptitle('Fitch Versions and Unknown Data', fontsize=12, y=1)
+    # filepath = 'data/simulation/30-fitch-unknown_plot.csv'
+    filepath = 'data/simulation/fitch_30-unknown.csv'
+    plt.subplot(2, 2, 1)
+    plot_fitch_versions(filepath, 30)
+    # filepath = 'data/simulation/40-fitch-unknown_plot.csv'
+    filepath = 'data/simulation/fitch_40-unknown.csv'
+    plt.subplot(2, 2, 2)
+    plot_fitch_versions(filepath, 40)
+    # filepath = 'data/simulation/50-fitch-unknown_plot.csv'
+    filepath = 'data/simulation/fitch_50-unknown.csv'
+    plt.subplot(2, 2, 3)
+    plot_fitch_versions(filepath, 50)
 
-    filepath = 'data/simulation/30-fitch-unknown_plot.csv'
-    plot_fitch_versions(filepath)
-    filepath = 'data/simulation/40-fitch-unknown_plot.csv'
-    plot_fitch_versions(filepath)
-    filepath = 'data/simulation/50-fitch-unknown_plot.csv'
-    plot_fitch_versions(filepath)
-
-    plt.tight_layout()
+    # plt.tight_layout()
     plt.show()
-
-    plot_depths()
 
     return
 
@@ -209,12 +212,8 @@ def plot_data_multifurc(percentage_parasites):
     plt.grid()
     return
 
-def plot_fitch_versions(filepath):
-    global PLOT_NUMBER
-    data = genfromtxt(filepath, delimiter=',', skip_header=1, skip_footer=0, names=['unknown', 'y_fitch1', 'y_fitch2', 'y_fitch3', 'y_fitch4'])
-
-    plt.subplot(ROWS, 1, PLOT_NUMBER)
-    PLOT_NUMBER += 2
+def plot_fitch_versions(filepath, percentage_parasites):
[…]

### 2018-03-30 Paper - Latex/Paper - Skizze - v4.tex
Thesis - Result table ....

@@
     information via phylogenetic trait prediction. We use the Global Biotic Interactions (GloBI) 
-    database to categorise 25,992 and 34,879 species as parasites and free-living, respectively and 
+    database to categorise 25,962 and 34,860 species as parasites and free-living, respectively and 
     predict states for over $\sim$2.3 million (97.34\%) leaf nodes without state information.
@@
   % For the 2,535,437 leaf nodes we could not gather much data. From the GloBI database 
-  %   \cite{Poelen2014} which we used, we could only collect 25,992 parasitic and 34,879 free-living 
+  %   \cite{Poelen2014} which we used, we could only collect 25,962 parasitic and 34,860 free-living 
   %   species. It follows that we have $\approx 2.4\%$ state information. \\
@@
     conclude that species A is parasitic and species B free-living. \\
-  From this data, we could specify $\sim$2.3 million leaf nodes 34,879 as free-living and 25,992 
+  From this data, we could specify $\sim$2.3 million leaf nodes 34,860 as free-living and 25,962 
     as parasitic.
@@
     point 2 consists of reconstructing the ancestral states and predicting the unknown leaf states 
-    with the aid of this algorithm. And then perform an evaluation of the results.
+    with the aid of this algorithm. And then perform an evaluation of the results. \\
 
@@
     to expandavailable information via phylogenetic trait prediction. As a basis for known states, 
-    we use the Global Biotic Interactions (GloBI) database, which cathegorises 34,879 and 25,992 
+    we use the Global Biotic Interactions (GloBI) database, which cathegorises 34,860 and 25,962 
     species as free-living and parasites. This data is used to perform an ancestral state 
@@
     For all these calculations, the following R functions are used: \textit{glm()}, \textit{anova()} 
-      and \textit{BIC()}.
+      and \textit{BIC()}. \\
 
@@
     %---------------------------------------------------------------------------------------------------
-    \subsection{Poisson regression of the multifurcation}
-      For a regression analysis of the multifurcation first set up a simple generalized linear model and 
-        then output the intercept of it:
-      \lstset{language=R}
-      \begin{lstlisting}[gobble=6]
-        kingdom.furc.mod <- glm(multifurc~kingdom, 
-                                    data=inner.taxa,
-                                        family="poisson")
-        # get the intercept:
-        summary(kingdom.furc.mod)
-      \end{lstlisting}
-      Since the multifurcation can also be 0, the intercept describes the expected mean value and thus, 
-        if it is greater than 0, it says that we have a multifurcation: $2.62 > 0$ $\Rightarrow$ there 
-        is a multifurcation. \\
-      We next compared the intercept of the different kingdoms and found that
-        $$1.22 \text{ (Fungi intercept)} > -0.11 \text{ (Metazoa intercept)} > -0.09 \text{ (Chloroplastida intercept)}$$
-        % Coefficients:
-        %                                         Estimate Std. Error z value Pr(>|z|)
-        % (Intercept)                             2.624897   0.003641  721.00   <2e-16
-        % kingdom['ott352914', 'Fungi']           1.224650   0.004054  302.10   <2e-16
-        % kingdom['ott361838', 'Chloroplastida'] -0.090993   0.003960  -22.98   <2e-16
-        % kingdom['ott691846', 'Metazoa']        -0.114873   0.003732  -30.78   <2e-16
-        that means the strength of the multifurcation \colorbox{red}{is the same/has the same size 
-        sorting}. \todo{kann das sein?} \\
-
-      We investigated several models that could describe multifurcation: \\
+    \subsection{Comparison of different models for multifurcation}
+      For the regression analysis of the multifurcation we set up several generalized linear models that 
+        could describe multifurcation. \\
       In doing so, we allowed the different influence of the taxa and the heights and depths of a node 
-        to be included. From this we got 9 times 4 models of different complexity levels (see first row 
-        of table \ref{table:BIC multifurcation}). \\
-      We first compared the models based on their residuals. These give us the error of the model. If 
-        the value is small, our data will be well modeled. These values are meaningful only for the same 
-        complexity, therefore we then calculated the BIC (Bayesian information criterion) values of the 
-        models and used them to evaluate the models. \\
-      % \lstset{language=R}
-      % \begin{lstlisting}[gobble=6]
-      %   anova(kingdom.furc.mod, phylum.furc.mod, class.furc.mod, 
-      %                 order.furc.mod, family.furc.mod, test="LRT")
-      %   BIC(kingdom.furc.mod)
-      %   ...
-      % \end{lstlisting}
-      The deviance table with the residuals can be found in the appendix (table 
-        \ref{table:Residuals multifurcation}). Table \ref{table:BIC multifurcation}. lists the BICs.
+        to be included. From this we got 9 times 4 models of different complexity levels (first row) and 
+        the associated BIC values (table \ref{table:BIC multifurcation}).
 
@@
         \caption{BIC (Bayesian information criterion) values of the multifurcation models. \\
-          These models are created with the R function \textit{glm()} and compared with the 
-            \textit{BIC()} function. This results in the listed BIC values.}
+          These models are created with the R function \textit{glm()} and compared with the \textit{BIC()} 
+            function. This results in the listed BIC values, presented in a heatmap colorization.}
         \label{table:BIC multifurcation} 
       \end{table}
-      % * Residuals: Fehler - wieviele Werte sind nicht gut modelliert. (umso kleiner umso besser - grün) \\
-      Within the every complexity class it can be seen that the mean height gives the best additional factor. \\
+      Within every complexity class it can be seen that the mean height gives the best additional factor. \\
       Despite higher complexity, the BIC values are getting smaller from model to model, meaning that 
@@
       The model \textit{multifurc $\sim$ order * mean.height} turns out to be the best of our models, 
-        whereby it is possible that e.g. \textit{multifurc $\sim$ family * mean.height} is better.
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{Binomial regression of the unknown state information}
-
-      Next to the problem of the multifurcation of the tree is the less of interaction data we have for 
-        the species. For the ancestral state reconstruction, we need information about the states 
+        whereby it is possible that e.g. \textit{multifurc $\sim$ family * mean.height} is better. \\
+
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \subsection{Comparison of different models for missing state information}
+      Next to the problem of the multifurcation of the tree is the little interaction data thet we have 
+        for the species. For the ancestral state reconstruction, we need information about the states 
         (free-living or parasite) in the leaf nodes. \\
       The eukaryotic synthesis tree has 293,463 leaf nodes. The GloBI database has 5,346,414 interactions 
-        (at 29.01.2018). Out of this data we got 51,337 distinct free-living species and 47,332 
-        distinct parasite species for the whole tree of life. From the Eukaryota we could determine 
-        25,992 and 34,879 species as parasites and free-living. With 2,293,463 leaf nodes we still have 
-        about 97.34\% unknown leaf nodes. In the discussion, section 
-        \ref{sec:discussion - data situation}, we will talk about ways to extend this data. \\
-
-      We also compared different models in terms of their BICs (Table: \ref{table:BIC unknown information}). 
-        The Residuals are not very meaningful here, since all models have different complexities. % /dimensions
-        For the sake of completeness, the associated deviance tables are located with the residuals in 
-        the appendix \ref{sec:Residuals unknown information}.
-
+        (at 29.01.2018). Out of this data we got 51,337 free-living species and 47,332 parasite species 
+        for the whole tree of life. From the Eukaryota we could determine 25,962 and 34,860 species as 
+        parasites and free-living. With 2,293,463 leaf nodes we still have about 97.34\% unknown leaf 
+        nodes.
+
+      We also compared different models in terms of their BICs (Table: \ref{table:BIC unknown information}). \\ 
       \begin{table}[h!]
@@
           These models are created with the R function \textit{glm()} and compared with the 
-            \textit{BIC()} function. This results in the listed BIC values.}
+            \textit{BIC()} function. This results in the listed BIC values, presented in a heatmap colorization.}
         \label{table:BIC unknown information} 
       \end{table}
+
       It also follows from this table that the most complex model is the best. In general, the BIC 
-        values are smaller than those of the multifurcation models. The modeling here is thus better. \\
-      Again, the calculation of finer models (e.g. order or family) was too expensive. \\
-
-      These missing data modeling results can be used to better simulate the data.
-
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  \section{Results of simulation / Influence of different parameters} \label{sec:results - simulation}
-
+        values are smaller than those of the multifurcation models. The modeling here is thus better.
+      Again, the calculation of finer models (e.g. family) was too expensive.
+
+      These missing data modeling results could be used to better simulate the data. \\
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Influence of different parameters on the prediction} \label{sec:results - simulation}
     As presented, we compare two methods in our simulation to their prediction accuracy: Fitch and 
-      Sankoff. \\
+      Sankoff.
+
+    First, we tested different distributions of parasites to free-livings including threshold (first 
+      column). It can be observed that the more balanced the percentages of free-livings and parasites, 
+      the worse the prediction of the algorithms (second and third column). \\
+    It can be seen that the predictive power of Sankoff is always greater or equal to the percentage
+      of free-living distribution, and therefore more accurate than guessing. \\
+    On the other hand, we examined the influence of missing internal nodes (ridge of multifurcation) 
+      and missing leaf node information (unknown leaf nodes). \\
+    Both factors have a relatively linear influence on the Sankoff method. Fitch, on the other hand, 
+      breaks significantly in his prediction from about 70\% unknown leaf nodes or mutifurcation. \\
     Figure \ref{fig:influence of unknown data} shows the results of examining various parameters.
+
+    Since we have a lot of missing data in most subtrees (both internal nodes and state informations), 
+      the Sankoff gives a better prediction and is thus used for real data analysis.
+
     \begin{figure}[h!]
@@
     \end{figure}
-    ~ \\ ~ \\ ~ \\
-    \begin{figure}
+    ~ \\
+    \begin{figure}[h!]
       \centering
@@
         The first column describes the distributions of free-livings and parasites with a given 
-          threshold for the respective simulations to the right. \\
+          threshold for the respective simulations to the right. Note, these distributions are chosen 
+          to form the specified proportions with the threshold, ignoring the number of state changes. \\
         The middle column investigates the influence of the unknown states, the right the influence of
@@
         Each point corresponds to the average of one hundred simulations, each with 10,000 leaf nodes. \\
-        For the middle column we set the strength of the multifurcations to 0.95\% similar to the 
+        For the middle column we set the strength of the multifurcations to 0.95\%, similar to the 
           real data and in the right column the amount of the unknowns to 0.95\% also similar to the 
@@
     \end{figure}
-    First, we tested different transition probability distributions including threshold (first column). 
-      It can be observed that the more balanced the percentages of free-livings and parasites, the 
-      worse the prediction of the algorithms (second and third column). \\
-    It can be seen that both algortithms are always over 50\% prediction and therefore better than 
-      guessing. Moreover, they are usually close to each other, with Sankoff always makes better 
-      predictions except for equally distributed states as Fitch. \\
-    On the other hand, we examined the influence of missing internal nodes (ridge of multifurcation) 
-      and missing leaf node information (unknown leaf nodes). \\
-    Both factors have a relatively linear influence on the Sankoff method. Fitch, on the other hand, 
-      breaks significantly in his prediction from about 70\% unknown leaf nodes or mutifurcation. \\
-
-    Since we have a lot of missing data in most subtrees (both internal nodes and state informations), 
-      the Sankoff gives a better prediction and is thus used for real data analysis.
 
@@
         role, which crystallize out in these examples. \\
-      An important factor here is that the credibility of the results. The accuracy of the input data 
+      An important factor here is the credibility of the results. The accuracy of the input data 
         stands and falls with the presence and the correctness of the data of GloBI. Errors of incorrect 
@@
 
+      \newcommand*\rot{\rotatebox{90}}
+
+      % \tiny	\scriptsize \footnotesize \small \normalsize \large \Large \LARGE \huge \Huge
       \begin{table}
         \begin{center}
-          \begin{tabular}{ |l|r||r|r||r|r|r|r| }
-            \hline
-            & & \multicolumn{2}{c||}{\bfseries original states} & \multicolumn{4}{c|}{\bfseries final states} \\
-            \bfseries Phylum & \bfseries \# nodes & \bfseries FL & \bfseries P & \bfseries 0 \bfseries (FL) & \bfseries 0.3 &\bfseries  0.5 & \bfseries 1 (P) \\
-            \hline \hline
-            Chordata & 91785        & 10451 & 18          & 91759 & 0 & 0 & 26 \\
-            &                       & 99.83\% & 0.49\%  & 99.97\% & & & 0.03\% \\ \hline
-            Nematoda & 30127        & 21 & 3289           & 1604 & 142 & 1196 & 27185 \\
-            &                       & 0.63\% & 99.37\%  & 5.32\% & 0.47\% & 3.97\% & 90.23\% \\ \hline
-            Platyhelminthes & 22683 & 7 & 7086            & 175 & & & 22508 \\
-            &                       & 0.1\% & 99.9\%    & 0.77\% & 0 & 0 & 99.23\% \\ \hline
-            Apicomplexa & 1863      & 1 & 255             & 1 & 0 & 0 & 1862 \\
-            &                       & 0.39\% & 99.61\%  & 0.05\% & & & 99.95\% \\
-            % \hline \hline
-            % Phylum & \# nodes & FL & P
-            %   & 0 (FL) & 0.4 & 0.5 & 0.67 & 0.75 & 1 (P) \\
-            % Arthropoda & 1198981 & 18912 & 11141 
-            %   & 1099509 & 1313 & 22478 & 4176 & 1665 & 70223 \\
-            % & & 62.93\% & 37.07\%
-            %   & 91.7\% & 0.11\% & 1.87\% & 0.35\% & 0.14\% & 5.86\% \\
+          \hspace*{-0.5cm}\begin{tabular}{|>{\scriptsize}c|>{\scriptsize}l|>{\scriptsize}r|>{\scriptsize}r||>{\scriptsize}r|>{\scriptsize}r||>{\scriptsize}r|>{\scriptsize}r|>{\scriptsize}r||>{\scriptsize}r|>{\scriptsize}r|>{\scriptsize}r| }
+            \hline
+            & \bfseries Taxa & \bfseries \#internal & \bfseries \#leaf 
+                & \multicolumn{2}{>{\scriptsize}c||}{\bfseries known states} & \multicolumn{3}{>{\scriptsize}c|}{\bfseries final states}
+                & \bfseries Root & \bfseries \#origins & \bfseries \#losses \\
+            & \bfseries subtree & \multicolumn{2}{>{\scriptsize}c||}{\bfseries nodes} & \bfseries FL & \bfseries P
+                & \bfseries [0, 0.5) & \bfseries 0.5 & \bfseries (0.5, 1]
+                & \bfseries node & \multicolumn{2}{>{\scriptsize}c|}{\bfseries (with rounding)} \\
+            & \bfseries & & & & 
+                & \bfseries FL & & \bfseries P 
+                & state & \bfseries FL $\rightarrow$ P & \bfseries P $\rightarrow$ FL \\
+            \hline \hline
+            \parbox[c][7mm][c]{1mm}{\multirow{2}{*}{\rot{\bfseries Domain~}}}
+            & Eukaryota & 241974 & 2293463      & 34860 & 25962     & 2053212 & 7775 & 474450     & 1 & 462 & 369 \\
+            & & &                               & 57.31\% & 42.69\% & 80.98\% & 0.31\% & 18.71\%  & P & & \\
+            \hline \hline
+            \parbox[c]{1mm}{\multirow{6}{*}{\rot{\bfseries Kingdom}}}
+            & Chloro- & 43486 & 416478          & 3519 & 77         & 410795 & 4182 & 1501        & 0.5 & 97 & 222 \\
+            & plastida & &                      & 97.86\% & 2.14\%  & 98.63\% & 1.00\% & 0.36\%   & & & \\ \cline{2-12}
+            & Fungi & 9534 & 31457              & 577 & 2983        & 38520 & 5723 & 266463       & 0 & 42 & 2 \\
+            & & &                               & 16.21\% & 83.79\% & 12.40\% & 1.84\% & 85.76\%  & FL & & \\ \cline{2-12}
+            & Metazoa & 179944 & 1491012        & 30758 & 22373     & 1329065 & 25535 & 136412    & 0.5 & 321 & 129 \\
+            & & &                               & 57.89\% & 42.11\% & 89.14\% & 1.71\% & 9.15\%   & & & \\
+            \hline \hline
+            \parbox[c]{1mm}{\multirow{10}{*}{\rot{\bfseries Phylum}}}
+            & Apicomplexa & 239 & 1863          & 1 & 255           & 1 & 0 & 1862                & 1 & 0 & 1 \\
+            & & &                               & 0.39\% & 99.61\%  & 0.05\% & 0\% & 99.95\%      & P & & \\ \cline{2-12}
+            & Arthropoda & 120479 & 1198981     & 18912 & 11141     & 1100822 & 22478 & 76064     & 0 & 281 & 108 \\
+            & & &                               & 62.93\% & 37.07\% & 91.78\% & 1.87\% & 6.34\%   & FL & & \\ \cline{2-12}
+            & Chordata & 30761 & 91785          & 10451 & 18        & 91759 & 0 & 26              & 0 & 12 & 1 \\
+            & & &                               & 99.83\% & 0.49\%  & 99.97\% & 0\% & 0.03\%      & FL & & \\ \cline{2-12}
+            & Nematoda & 3437 & 30127           & 21 & 3289         & 1746 & 1196 & 27185         & 1 & 2 & 11 \\
+            & & &                               & 0.63\% & 99.37\%  & 5.79\% & 3.97\% & 90.23\%   & P & & \\ \cline{2-12}
+            & Platyhel- & 4459 & 22683       & 7 & 7086          & 175 & 0 & 22508             & 0 & 0 & 5 \\
+            & minthes & &                          & 0.1\% & 99.9\%    & 0.77\% & 0\% & 99.23\%      & P & & \\
+            \hline \hline 
+            \parbox[c]{1mm}{\multirow{2}{*}{\rot{\bfseries Class~}}}
+            & Insecta & 91256 & 989572          & 17841 & 10734     & 1022747 & 976 & 57105       & 0 & 245 & 77 \\
+            & & &                               & 62.44\% & 37.56\% & 94.63\% & 0.09\% & 5.28\%   & FL & & \\ 
             \hline
@@
           of the amount and percentage of given data to predicted data.}
+          % \caption{All kingdoms (subtrees), only leaf nodes, are examined for the evolution of the 
+          % amount and percentage of given data to predicted data.}
+          % \caption{Origins and losses}
         \label{table:phylum leaf nodes states} 
+      \end{table}
+
+      \begin{table}[H]
+        \centering
+        \begin{tabular}{|c|l|r|r|r|r|}
+        \hline
+        & \multicolumn{1}{c|}{Text} & \multicolumn{1}{c|}{Text} & \multicolumn{1}{c|}{Text} & \multicolumn{1}{c|}{Text} & \multicolumn{1}{c|}{text}\\
+        \hline
+        \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{rota}}} & text &&&&\\
+        & text &&&&\\
+        & text &&&&\\
+        \hline
+        \end{tabular}
         \end{table}
@@
 
-      \begin{table}[h!]
-        \begin{center}
-          \begin{tabular}{ |l|r||r|r||r|r|r|r|r|r| }
-            \hline
-            & & \multicolumn{2}{c||}{\bfseries original states} & \multicolumn{6}{c|}{\bfseries final states} \\
-            \bfseries Phylum & \bfseries \# nodes & \bfseries FL & \bfseries P
-              & \bfseries 0 (FL) & \bfseries 0.4 & \bfseries 0.5 & \bfseries 0.67 & \bfseries 0.75 & \bfseries 1 (P) \\
-            \hline \hline
-            Chordata & 122546 & 10451 & 18 
-              & 122473 & 0 & 0 & 0 & 0 & 73 \\
-            Nematoda & 33564 & 21 & 3289 
-              & 846 & 0 & 1133 & 0 & 0 & 31585 \\
-            Platyhelminthes & 27142 & 7 & 7086 
-              & 1010 & 0 & 175 & 0 & 0 & 25957 \\
-            Apicomplexa & 2102 & 1 & 255 
-              & 1 & 0 & 0 & 0 & 0 & 2101 \\
-            % \hline
-            % Arthropoda & 1319460 & 18912 & 11141 
-            %   & 1207204 & 1313 & 25499 & 4852 & 1957 & 78635 \\
-            \hline
-          \end{tabular}
-        \end{center}
-        \caption{Some selected phyla (subtrees), including internal nodes, are examined for the evolution 
-        of the amount and percentage of given data to predicted data.}
-        \label{table:Phylum internal nodes}
-      \end{table}
-
-      \begin{table}[h!]
-        \begin{center}
-          \hspace*{-2cm}\begin{tabular}{ |l|r||r|r||r|r|r|r|r|r|r|r| }
-            \hline
-            & & \multicolumn{2}{c||}{\bfseries original states} & \multicolumn{8}{c|}{\bfseries final states} \\
-            \bfseries Kingdom & \bfseries \# nodes & \bfseries FL & \bfseries P
-              & \bfseries 0 (FL) & \bfseries 0.25 & \bfseries 0.33 & \bfseries 0.4 & \bfseries 0.5 & \bfseries 0.67 & \bfseries 0.75 & \bfseries 1 (P) \\
-            \hline \hline
-            none & 75446 & 45 & 529 
-              & 13426 & 220 & 24082 & 0 & 7792 & 5302 & 0 & 24493 \\
-            Fungi & 31457 & 577 & 2983
-              & 38520 & 0 & 0 & 0 & 5723 & 0 & 0 & 266463 \\
-            Chloroplastida & 416478 & 3519 & 77
-              & 410795 & 0 & 0 & 0 & 4182 & 0 & 0 & 1501 \\
-            Metazoa & 1491012 & 30758 & 22373
-              & 1328135 & 0 & 0 & 930 & 25535 & 4423 & 1665 & 130324 \\
-            \hline  
-          \end{tabular}
-        \end{center}
-        \caption{All kingdoms (subtrees), only leaf nodes, are examined for the evolution of the 
-          amount and percentage of given data to predicted data.}
-        \label{table:Kingdom leaf nodes}
-      \end{table}
-
-      \begin{table}[h!]
-        \begin{center}
-          \hspace*{-2cm}\begin{tabular}{ |l|r||r|r||r|r|r|r|r|r|r|r| }
-            \hline
-            & & \multicolumn{2}{c||}{\bfseries original states} & \multicolumn{8}{c|}{\bfseries final states} \\
-            \bfseries Kingdom & \bfseries \# nodes & \bfseries FL & \bfseries P
-              & \bfseries 0 (FL) & \bfseries 0.25 & \bfseries 0.33 & \bfseries 0.4 & \bfseries 0.5 & \bfseries 0.67 & \bfseries 0.75 & \bfseries 1 (P) \\
-            \hline \hline
-            none & 84456 & 45 & 529 
-              & 15035 & 243 & 25910 & 0 & 8764 & 6183 & 0 & 28140 \\
-            Fungi & 324105 & 577 & 2983
-              & 39088 & 0 & 0 & 0 & 5858 & 0 & 0 & 274803 \\
-            Chloroplastida & 460457 & 3519 & 77
-              & 454211 & 0 & 0 & 0 & 4688 & 0 & 0 & 1558 \\
-            Metazoa & 1670956 & 30758 & 22373
-              & 1485749 & 0 & 0 & 1313 & 29002 & 5102 & 1957 & 147833 \\
-            \hline  
-          \end{tabular}
-        \end{center}
-        \caption{All kingdoms (subtrees), inkluding internal nodes, are examined for the evolution of the 
-        amount and percentage of given data to predicted data.}
-        \label{table:Kingdom internal nodes}
-      \end{table}
-
       %---------------------------------------------------------------------------------------------------
@@
         % \end{lstlisting}
-
-        \begin{table} [h]
-          \begin{center}
-            \begin{tabular}{ |l|r|r||r|r|r| }
-              \hline
-              \bfseries Domain  & \bfseries \# internal & \bfseries \# leaf & \bfseries Rootnode & \multicolumn{2}{c|}{\bfseries without and with rounding} \\ 
-              \bfseries / Kingdom  & \multicolumn{2}{c||}{\bfseries nodes} & \bfseries state & \bfseries \# origins & \bfseries \# losses \\
-              \bfseries / Phylum / Class & & & & \bfseries (FL -> P) & \bfseries (P -> FL) \\
-              \hline \hline
-              Eukaryota & 241974 & 2293463 & 1.0 & 415 & 363 \\
-              & & & P & 462 & 369 \\
-              \hline \hline
-              Metazoa & 179944 & 1491012 & 0.5 & 294 & 123 \\
-              & & & & 321 & 129 \\ \hline
-              Fungi & 9534 & 314571 & 0.5 & 80 & 222 \\
-              & & & & 97 & 222 \\ \hline
-              Chloroplastida & 43486 & 412434 & 0.0 & 40 & 2 \\
-              & & & FL & 42 & 2 \\
-              \hline \hline            
-              Arthropoda & 120479 & 1198981 & 0.0 & 260 & 102 \\
-              & & & FL & 281 & 108 \\ \hline
-              Apicomplexa & 239 & 1863 & 1.0 & 0 & 1 \\
-              & & & P & 0 & 1 \\ \hline
-              Nematoda & 3437 & 30127 & 1.0 & 0 & 11 \\
-              & & & P & 2 & 11 \\ \hline
-              Chordata & 30761 & 91785 & 0.0 & 12 & 1 \\
-              & & & FL & 12 & 1 \\ \hline
-              Platyhelminthes & 4459 & 22683 & 1.0 & 0 & 5 \\
-              & & & P & 0 & 5 \\
-              \hline \hline            
-              Insecta & 91256 & 989572 & 0.0 & 234 & 77 \\
-              & & & FL & 245 & 77 \\ 
-              \hline  
-            \end{tabular}
-          \end{center}
-          \caption{Origins and losses}
-          \label{table:origins and losses} 
-        \end{table}
 
@@
         computationally too expensive to calculate. \\
-      The Residuals are included in the appendix (table \ref{table:Residuals cross-validation}) for the 
-        sake of completeness; here too, due to the different complexity, they do not have much meaning 
-        for the comparison of the models. \\
 
       \todo{table for these numbers?}
-      % 100/(25992+34879)*10000 = 16.43
-      % 100/(25992+34879)*9238 = 15.18
+      % 100/(25962+34860)*10000 = 16.44
+      % 100/(25962+34860)*9238 = 15.19
       % 10000 nodes 9238 unique
@@
           These models are created with the R function \textit{glm()} and compared with the 
-            \textit{BIC()} function. This results in the listed BIC values.}
+            \textit{BIC()} function. This results in the listed BIC values, presented in a heatmap colorization.}
         \label{table:BIC cross-validation} 
@@
     The used eukaryotic synthesis tree from OTL \cite{Hinchliff2015} has 241,974 internal nodes and 
-      293,463 leaf nodes. In addition, we could specify 25,992 parasitic and 34,879 free-living 
+      293,463 leaf nodes. In addition, we could specify 25,962 parasitic and 34,860 free-living 
       species from GloBI \cite{Poelen2014}. \\
@@
         in the context of this work.
+
+      \todotext{It should be noted that we have optimized the distributions to the proportions and thus the number of state changes will be relatively high.
+With a smaller number of state changes, the predictive power of both algorithms would be even better.}
+      % transition probability
 
@@
   %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  \section{Missing internal node modeling - Residual table} %\label{sec:Residuals unknown information}
+  \section{Results}
+
     \begin{table}[h!]
       \begin{center}
-          \begin{tabular}{ |l|r|r|r|r| }
-            \hline
-            \bfseries Model / Taxa & \bfseries Kingdom & \bfseries Phylum & \bfseries Class & \bfseries Order \\
-            \hline \hline
-            multifurc $\sim$ taxa & 7774454 & \cellcolor{green!10}7435700 & \cellcolor{green!15}7337241 & \cellcolor{green!30}7076068 \\
-            \hline
-            multifurc $\sim$ taxa + depth & 7752303 & \cellcolor{green!10}7431609 & \cellcolor{green!15}7334754 & \cellcolor{green!30}7027578 \\
-            multifurc $\sim$ taxa + max.height & 7730196 & \cellcolor{green!15}7375889 & \cellcolor{green!20}7275856 & \cellcolor{green!30}7005424 \\
-            multifurc $\sim$ taxa + min.height & \cellcolor{green!10}7472500 & \cellcolor{green!20}7233486 & \cellcolor{green!25}7144686 & \cellcolor{green!40}6890703 \\
-            multifurc $\sim$ taxa + mean.height & \cellcolor{green!15}7304402 & \cellcolor{green!25}7128318 & \cellcolor{green!30}7055313 & \cellcolor{green!40}6815271 \\
-            \hline
-            multifurc $\sim$ taxa * depth & 7714881 & \cellcolor{green!15}7335396 & \cellcolor{green!20}7250759 & \cellcolor{green!40}6843004 \\
-            multifurc $\sim$ taxa * max.height & \cellcolor{green!5}7692980 & \cellcolor{green!15}7311241 & \cellcolor{green!25}7187504 & \cellcolor{green!45}6795823 \\
-            multifurc $\sim$ taxa * min.height & \cellcolor{green!10}7442387 & \cellcolor{green!25}7177002 & \cellcolor{green!30}7094933 & \cellcolor{green!45}6795099 \\
-            multifurc $\sim$ taxa * mean.height & \cellcolor{green!20}7247309 & \cellcolor{green!30}7020258 & \cellcolor{green!35}6965794 & \cellcolor{green!50}6665565 \\
+        \begin{tabular}{ |l|r||r|r||r|r|r|r|r|r| }
+          \hline
+          & & \multicolumn{2}{c||}{\bfseries original states} & \multicolumn{6}{c|}{\bfseries final states} \\
+          \bfseries Phylum & \bfseries \# nodes & \bfseries FL & \bfseries P
+            & \bfseries 0 (FL) & \bfseries 0.4 & \bfseries 0.5 & \bfseries 0.67 & \bfseries 0.75 & \bfseries 1 (P) \\
+          \hline \hline
+          Chordata & 122546 & 10451 & 18 
+            & 122473 & 0 & 0 & 0 & 0 & 73 \\
+          Nematoda & 33564 & 21 & 3289 
+            & 846 & 0 & 1133 & 0 & 0 & 31585 \\
+          Platyhelminthes & 27142 & 7 & 7086 
+            & 1010 & 0 & 175 & 0 & 0 & 25957 \\
+          Apicomplexa & 2102 & 1 & 255 
+            & 1 & 0 & 0 & 0 & 0 & 2101 \\
+          % \hline
+          % Arthropoda & 1319460 & 18912 & 11141 
+          %   & 1207204 & 1313 & 25499 & 4852 & 1957 & 78635 \\
           \hline
@@
       \end{center}
-      \caption{Residuals of multifurcation models \\
-        These models are created with the R function \textit{glm()} and compared with the 
-          \textit{anova()} function. This results in the listed residuals.}
-      \label{table:Residuals multifurcation} 
+      \caption{Some selected phyla (subtrees), including internal nodes, are examined for the evolution 
+      of the amount and percentage of given data to predicted data.}
+      \label{table:Phylum internal nodes}
     \end{table}
 
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  \section{Missing leaf state modeling - Residual table}\label{sec:Residuals unknown information}
     \begin{table}[h!]
       \begin{center}
-        \begin{tabular}{ |l|r|r|r| }
-          \hline
-          \bfseries Model / Taxa & \bfseries Kingdom & \bfseries Phylum & \bfseries Class \\
-          \hline \hline
-          multifurc $\sim$ taxa & 545740 & \cellcolor{green!10}499227 & \cellcolor{green!30}482265 \\
-          \hline
-          multifurc $\sim$ taxa + depth & 544789 & \cellcolor{green!10}493017 & \cellcolor{green!50}478998 \\
-          \hline
-          multifurc $\sim$ taxa * depth & 544062 & \cellcolor{green!30}488366 & \cellcolor{green!50}476382 \\
+        \hspace*{-2cm}\begin{tabular}{ |l|r||r|r||r|r|r|r|r|r|r|r| }
+          \hline
+          & & \multicolumn{2}{c||}{\bfseries original states} & \multicolumn{8}{c|}{\bfseries final states} \\
+          \bfseries Kingdom & \bfseries \# nodes & \bfseries FL & \bfseries P
+            & \bfseries 0 (FL) & \bfseries 0.25 & \bfseries 0.33 & \bfseries 0.4 & \bfseries 0.5 & \bfseries 0.67 & \bfseries 0.75 & \bfseries 1 (P) \\
+          \hline \hline
+          none & 84456 & 45 & 529 
+            & 15035 & 243 & 25910 & 0 & 8764 & 6183 & 0 & 28140 \\
+          Fungi & 324105 & 577 & 2983
+            & 39088 & 0 & 0 & 0 & 5858 & 0 & 0 & 274803 \\
+          Chloroplastida & 460457 & 3519 & 77
+            & 454211 & 0 & 0 & 0 & 4688 & 0 & 0 & 1558 \\
+          Metazoa & 1670956 & 30758 & 22373
+            & 1485749 & 0 & 0 & 1313 & 29002 & 5102 & 1957 & 147833 \\
           \hline  
@@
       \end{center}
-      \caption{Residuals of unknown information models \\
-        These models are created with the R function \textit{glm()} and compared with the 
-          \textit{anova()} function. This results in the listed residuals.}
+      \caption{All kingdoms (subtrees), inkluding internal nodes, are examined for the evolution of the 
+      amount and percentage of given data to predicted data.}
+      \label{table:Kingdom internal nodes}
     \end{table}
 
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  \section{Cross-validation prediction - Residual table}
-    \begin{table}[h]
-      \begin{center}
-        \begin{tabular}{ |l|r|r|r| }
-          \hline
-          \bfseries Model / Taxa &\bfseries  Kingdom & \bfseries Phylum & \bfseries Class \\% & Order \\
-          \hline \hline
-          correctly predicted $\sim$ taxa & 117877 & \cellcolor{green!30}111466 & \cellcolor{green!45}108878 \\% & XXXXX \\
-          \hline
-          correctly predicted $\sim$ taxa + depth & 117703 & \cellcolor{green!35}110513 & \cellcolor{green!45}108403 \\% & XXXXX \\
-          \hline
-          correctly predicted $\sim$ taxa * depth & 117592 & \cellcolor{green!40}109827 & \cellcolor{green!50}107994 \\% & XXXXX \\
-          \hline
-        \end{tabular} 
-      \end{center}
-      \caption{Residuals of cross-validation prediction \\
-        These models are created with the R function \textit{glm()} and compared with the 
-          \textit{anova()} function. This results in the listed residuals.}
-      \label{table:Residuals cross-validation} 
-    \end{table}
-
 \end{document}

### 2018-03-30 code/evaluation/analyse_output.R

@@ -21,10 +21,10 @@ names(heights) <- c("min.height", "max.height", "mean.height")
 
 all.taxa <- cbind(all.taxa, heights)
 
-# print('------------all.taxa$originaltag------------------')
-# table(all.taxa$originaltag)
-# print('------------all.taxa$finaltag------------------')
-# table(all.taxa$finaltag)
+print('------------all.taxa$originaltag------------------')
+table(all.taxa$originaltag)
+print('------------all.taxa$finaltag------------------')
+table(all.taxa$finaltag)
 
 print('--------------------------------------------------')
 
@@ -32,17 +32,13 @@ leaf.taxa <-  all.taxa[all.taxa$nr_children==0, ]
 
 print('--------------------------------------------------')
 
-
-
-
-# print('-------------Are the changed originaltags?--------------')
+# print('-------------Are there changed originaltags?--------------')
 # table(leaf.taxa[leaf.taxa$finaltag+1 != leaf.taxa$originaltag, ]$kingdom)
-
 
 print('-----------Analyse some Phyla about their prediciton-------------')
 print('-----------Metazoa-------------')
 metazoa <- leaf.taxa[leaf.taxa$kingdom=="['ott691846', 'Metazoa']", ]
-# # table(metazoa$phylum, metazoa$originaltag)
+# table(metazoa$phylum, metazoa$originaltag)
 print('--------Leaf nodes:------------')
 # table(droplevels(all.taxa[all.taxa$nr_children==0, ]$phylum))
 print('----------Parasites / Free-livings - original states:---------------')
@@ -70,13 +66,26 @@ print('------------------------')
 print('-----------Apicomplexa-------------')
 apicomplexa <- leaf.taxa[leaf.taxa$phylum=="['ott422673', 'Apicomplexa']", ]
 table(apicomplexa$originaltag)
-table(apicomplexa[apicomplexa$originaltag==1, ]$name)
+# table(apicomplexa[apicomplexa$originaltag==1, ]$name)
 
 print('----------final:--------------')
 table(apicomplexa$finaltag)
 print('------------------------')
-table(apicomplexa[apicomplexa$finaltag==0, ]$name)
+# table(apicomplexa[apicomplexa$finaltag==0, ]$name)
 
+print('-----------Arthropoda-------------')
+arthropoda <- all.taxa[all.taxa$phylum=="['ott632179', 'Arthropoda']", ]
[…]

### 2018-03-30 code/metadata/analyse_input.R

@@ -208,21 +208,21 @@ print('--------------------------------------------------')
 
 inner.taxa$multifurc <- inner.taxa$nr_children-1
 
-ggplot(inner.taxa, aes(multifurc)) +
-    geom_histogram(col="black") +
-    scale_y_log10() +
-    labs(x="number of children -2", y="number of nodes")
-ggsave("multifurc.pdf")
+# ggplot(inner.taxa, aes(multifurc)) +
+#     geom_histogram(col="black") +
+#     scale_y_log10() +
+#     labs(x="number of children -2", y="number of nodes")
+# ggsave("multifurc.pdf")
 
-ggplot(inner.taxa, aes(multifurc)) +
-    geom_histogram( 
-        col="black", 
-        binwidth = 1,
-        aes(fill=..count..)) +
-    xlim(0, 30) +
-    scale_y_log10() +
-    labs(x="number of children -2", y="number of nodes")
-ggsave("multifurc_small.pdf")
+# ggplot(inner.taxa, aes(multifurc)) +
+#     geom_histogram( 
+#         col="black", 
+#         binwidth = 1,
+#         aes(fill=..count..)) +
+#     xlim(0, 30) +
+#     scale_y_log10() +
+#     labs(x="number of children -2", y="number of nodes")
+# ggsave("multifurc_small.pdf")
 
 print('--------------------------------------------------')
 print('-------------------------multifurc data-------------------------')
@@ -415,9 +415,10 @@ print('-------------------order * depth / min/max/mean.height-------------------
 #                    family="poisson")
 # print(c('BIC=',  BIC(orderTmaxHeightt.furc.mod)))
 
-# orderTmeanHeight.furc.mod <- glm(multifurc~order*mean.height, data=inner.taxa,
-#                    family="poisson")
+orderTmeanHeight.furc.mod <- glm(multifurc~order*mean.height, data=inner.taxa,
+                   family="poisson")
 # print(c('BIC=',  BIC(orderTmeanHeight.furc.mod)))
+summary(orderTmeanHeight.furc.mod)
 
 # anova(orderTdepth.furc.mod, orderTmaxHeightt.furc.mod, orderTminHeight.furc.mod, orderTmeanHeight.furc.mod, test="LRT")
 
@@ -552,7 +553,8 @@ print('-------------------class + depth / * depth-----------------------')
[…]

### 2018-03-30 scripts/castor_example/analyse_output.R

@@ -1,0 +1,20 @@
+library(data.table)
+# library(ggplot2)
+
+format(Sys.time(), "%a %b %d %X %Y")
+
+all.taxa <- fread("./Sarcopterygii-castor.csv")
+
+print('------------all.taxa$originaltag------------------')
+table(all.taxa$originaltag)
+print('------------all.taxa$finaltag------------------')
+table(all.taxa$finaltag)
+print('--------------------------------------------------')
+
+table(all.taxa[all.taxa$finaltag+1 != all.taxa$originaltag, ]$nr_children)
+
+
+
+print('--------------------------------------------------')
+
+format(Sys.time(), "%a %b %d %X %Y")

### 2018-03-30 Paper - Latex/Paper - Skizze - v4.tex
Thesis - describe table ...

@@
   \section{Real data analysis} \label{sec:methods - real data analysis}
-    For the evaluation of real data results, a leave-100-out cross-validation is performed. For this 
-      purpose 100 randomly distributed 100 states are left out.
-
-    Analogous to the missing leaf node states, generalized linear models with binomial regression are 
-      compared according to their residuals, based on the "true" / "false" prediction. \\
+    For the evaluation of real data results, some statistics are collected and a leave-100-out 
+      cross-validation is performed. For this purpose 100 randomly distributed 100 states are left out.
+
+    The statistics are collected over the entire Eukaryota tree and over some subtrees of different 
+      taxa. There are known states besides predicted states, the predicted root node state specified 
+      and origins and losses are counted by parasitism. \\
+    Since Sankoff predicts probabilities for states, we have rounded them to be able to count 
+      transitions from free-living (0) to parasitic (1) and vice versa. \\
+    In each case, a maximum of one changing transition from parent node to child node is counted for 
+      the origins (FL $\rightarrow$ P) or losses (P $\rightarrow$ FL).
+
+    For the leave-100-out cross-validation, analogous to the missing leaf node states, generalized 
+      linear models with binomial regression are compared according to their residuals, based on the 
+      "true" / "false" prediction. \\
     Again, in order to compare models of different complexity, the BIC (Bayesian Information Criterion) 
@@
     % subtrees for their credibility with the help of biological background knowledge (subsection 
-    % \ref{sec:results - biological view}). On the other hand, we
+    % \ref{subsec:results - statistics on predicted states}). On the other hand, we
   We evaluated these by performing a leave-100-out cross-validation and predicted approximately 
@@
   \section{Results of the real data analysis created with Sankoff}
-    This section is about evaluating the prediction of real data using the Sankoff method. \\
-    It is divided into two subsections. \ref{sec:results - biological view}: The analysis of some subtrees using 
-      biological background knowledge. \ref{sec:results - cross-validation}: Presentation of the results 
-      of the leave-100-out cross-validation.
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{Biological view} \label{sec:results - biological view}
-      To analyze the results, we have selected some phyla (subtrees) to evaluate our results 
-        selectively from the biological point of view: Chordata, Nematoda, Platyhelminthes and 
-        Apicomplexa. \\
-      In Table \ref{table:phylum leaf nodes states} we compare the given states with the predicted ones. \\
-      Several factors such as the distribution of existing input data via parasitics and free-livings, 
-        faulty input data from GloBI and reinforcement of errors by multifurcation play an important 
-        role, which crystallize out in these examples. \\
-      An important factor here is the credibility of the results. The accuracy of the input data 
-        stands and falls with the presence and the correctness of the data of GloBI. Errors of incorrect 
-        input data can be amplified by incorrect prediction of unknown species and can be reversed in 
-        order to improve the data situation of GloBI. \\
-      Since we look at such large trees we can not expect to know all the parasites, so we look at 
-        individual positives. This is positive in the sense that the majority have the opposite state.
-
-      \newcommand*\rot{\rotatebox{90}}
+    This section is about evaluating the prediction of real data using the Sankoff method. It is 
+      divided into two subsections. The analysis of some statistics on the predicted states, 
+      \todo{with the result...} (subsection \ref{subsec:results - statistics on predicted states}) and the presentation 
+      of the leave-100-out cross-validation results (subsection \ref{sec:results - cross-validation}).
+      \todo{This has revealed that ...} \\
+
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \subsection{Statistics on predicted states} \label{subsec:results - statistics on predicted states}
+      In the entire Eukaryota tree we start with 57.31\% free-living species and 42.69\% parasites. The 
+        prediction yields 80.98\% free-livings 0.31\% undefinable and 18.71\% parasites. In addition, 
+        there are 462 origins of parasitism and 369 losses distributed throughout the tree, with the 
+        root node predicted to be parasitic. \\
+      We have predicted significantly more free-livings than parasites, but parasitism has prevailed to 
+        the root node.
+
+      In table \ref{table:results of some selected taxa} we compare different subtrees of different taxa 
+        on these prediction results.
+
+      Similar to the Eukaryota it is with the Metazoa subtree, which accounts for most of the Eukayota 
+        (179,944 internal and 1,491,012 leaf nodes). However, here the root node is no longer calculated 
+        as parasitic but still as indefinable. \\
+      Strongly parasitic subtrees are for example the Apicomplexa, the Nematoda and the Platyhelminthes. 
+        For all three, the prediction is at a similar proportion between input values of the states and 
+        predicted states, e.g. In the Apicomplexa with 99.61\% known parasitic states, 99.95\% parasites 
+        were predicted. The same applies to the chordata, only that these mainly consist of free-living 
+        species.
 
@@
             \hline
-            & \bfseries Taxa & \bfseries \#internal & \bfseries \#leaf 
-                & \multicolumn{2}{>{\scriptsize}c||}{\bfseries known states} & \multicolumn{3}{>{\scriptsize}c|}{\bfseries final states}
+            \multirow{3}{*}{\rot{\bfseries $\leftarrow$ Taxa}}
+            & & \multicolumn{2}{>{\scriptsize}c||}{\bfseries number of}
+                & \multicolumn{2}{>{\scriptsize}c||}{\bfseries known states} & \multicolumn{3}{>{\scriptsize}c||}{\bfseries final states}
                 & \bfseries Root & \bfseries \#origins & \bfseries \#losses \\
-            & \bfseries subtree & \multicolumn{2}{>{\scriptsize}c||}{\bfseries nodes} & \bfseries FL & \bfseries P
+            & \bfseries Subtree & \bfseries internal & \bfseries leaf & \bfseries FL & \bfseries P
                 & \bfseries [0, 0.5) & \bfseries 0.5 & \bfseries (0.5, 1]
                 & \bfseries node & \multicolumn{2}{>{\scriptsize}c|}{\bfseries (with rounding)} \\
-            & \bfseries & & & & 
+            & \bfseries & \multicolumn{2}{>{\scriptsize}c||}{\bfseries nodes} & &
                 & \bfseries FL & & \bfseries P 
-                & state & \bfseries FL $\rightarrow$ P & \bfseries P $\rightarrow$ FL \\
+                & \bfseries state & \bfseries FL $\rightarrow$ P & \bfseries P $\rightarrow$ FL \\
             \hline \hline
@@
             \parbox[c]{1mm}{\multirow{6}{*}{\rot{\bfseries Kingdom}}}
-            & Chloro- & 43486 & 416478          & 3519 & 77         & 410795 & 4182 & 1501        & 0.5 & 97 & 222 \\
-            & plastida & &                      & 97.86\% & 2.14\%  & 98.63\% & 1.00\% & 0.36\%   & & & \\ \cline{2-12}
+            & Chloroplastida & 43486 & 416478   & 3519 & 77         & 410795 & 4182 & 1501        & 0.5 & 97 & 222 \\
+            & & &                               & 97.86\% & 2.14\%  & 98.63\% & 1.00\% & 0.36\%   & & & \\ \cline{2-12}
             & Fungi & 9534 & 31457              & 577 & 2983        & 38520 & 5723 & 266463       & 0 & 42 & 2 \\
@@
             & Apicomplexa & 239 & 1863          & 1 & 255           & 1 & 0 & 1862                & 1 & 0 & 1 \\
-            & & &                               & 0.39\% & 99.61\%  & 0.05\% & 0\% & 99.95\%      & P & & \\ \cline{2-12}
+            & {\tiny (Chloroplastida)\par} & &  & 0.39\% & 99.61\%  & 0.05\% & 0\% & 99.95\%      & P & & \\ \cline{2-12}
             & Arthropoda & 120479 & 1198981     & 18912 & 11141     & 1100822 & 22478 & 76064     & 0 & 281 & 108 \\
-            & & &                               & 62.93\% & 37.07\% & 91.78\% & 1.87\% & 6.34\%   & FL & & \\ \cline{2-12}
+            & {\tiny (Metazoa)\par} & &         & 62.93\% & 37.07\% & 91.78\% & 1.87\% & 6.34\%   & FL & & \\ \cline{2-12}
             & Chordata & 30761 & 91785          & 10451 & 18        & 91759 & 0 & 26              & 0 & 12 & 1 \\
-            & & &                               & 99.83\% & 0.49\%  & 99.97\% & 0\% & 0.03\%      & FL & & \\ \cline{2-12}
+            & {\tiny (Metazoa)\par} & &         & 99.83\% & 0.49\%  & 99.97\% & 0\% & 0.03\%      & FL & & \\ \cline{2-12}
             & Nematoda & 3437 & 30127           & 21 & 3289         & 1746 & 1196 & 27185         & 1 & 2 & 11 \\
-            & & &                               & 0.63\% & 99.37\%  & 5.79\% & 3.97\% & 90.23\%   & P & & \\ \cline{2-12}
-            & Platyhel- & 4459 & 22683       & 7 & 7086          & 175 & 0 & 22508             & 0 & 0 & 5 \\
-            & minthes & &                          & 0.1\% & 99.9\%    & 0.77\% & 0\% & 99.23\%      & P & & \\
+            & {\tiny (Metazoa)\par} & &         & 0.63\% & 99.37\%  & 5.79\% & 3.97\% & 90.23\%   & P & & \\ \cline{2-12}
+            & Platyhelminthes & 4459 & 22683    & 7 & 7086          & 175 & 0 & 22508             & 0 & 0 & 5 \\
+            & {\tiny (Metazoa)\par} & &         & 0.10\% & 99.9\%   & 0.77\% & 0\% & 99.23\%      & P & & \\
             \hline \hline 
@@
             & Insecta & 91256 & 989572          & 17841 & 10734     & 1022747 & 976 & 57105       & 0 & 245 & 77 \\
-            & & &                               & 62.44\% & 37.56\% & 94.63\% & 0.09\% & 5.28\%   & FL & & \\ 
+            & {\tiny (Arthropoda)\par} & &      & 62.44\% & 37.56\% & 94.63\% & 0.09\% & 5.28\%   & FL & & \\ 
             \hline
@@
         \end{center}
-        \caption{Some selected phyla (subtrees), only leaf nodes, are examined for the evolution 
-          of the amount and percentage of given data to predicted data.}
-          % \caption{All kingdoms (subtrees), only leaf nodes, are examined for the evolution of the 
-          % amount and percentage of given data to predicted data.}
-          % \caption{Origins and losses}
-        \label{table:phylum leaf nodes states} 
+        \caption{Results of some selected taxa (subtrees). \\
+          (1 + 2) subtree taxa and name; 
+          (3 + 4) number of internal nodes and leaf nodes; 
+          (5 + 6) number or percentage of known states; 
+          (7 - 9) number or percentage of predicted states; 
+          (10) predicted state of the root node of the subtree; 
+          (11 + 12) origins and losses with rounded states.}
+          \label{table:results of some selected taxa}
       \end{table}
 
-      \begin{table}[H]
-        \centering
-        \begin{tabular}{|c|l|r|r|r|r|}
-        \hline
-        & \multicolumn{1}{c|}{Text} & \multicolumn{1}{c|}{Text} & \multicolumn{1}{c|}{Text} & \multicolumn{1}{c|}{Text} & \multicolumn{1}{c|}{text}\\
-        \hline
-        \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{rota}}} & text &&&&\\
-        & text &&&&\\
-        & text &&&&\\
+      Weinstein and Kuris have been searching for origins of parasitism in Animalia \cite{Weinstein2016}. 
+        They identified 223 parasitic origins: 223 in Metazoa $\supset$ 143 in Arthropoda $\supset$ 87 
+        in Insecta. \\
+      In Table \ref{table:results of some selected taxa} we can see, that we found some more origins than 
+        Weinstein: 321 in Metazoa $\supset$ 281 in Arthropoda $\supset$ 245 in Insecta and on top of 
+        that some losses: 129 in Metazoa $\supset$ 108 in Arthropoda $\supset$ 77 in Insecta. The 
+        origins and losses calculated by Sankoff are thus closer to the leaves in the tree.
+
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \subsection{Leave-100-out cross-validation} \label{sec:results - cross-validation}
+      For a further validation of our results, we carried out a leave-100-out cross-validation. \\
+      In order to achieve about 15\% of the 60,871 input node states with a validation, 
+        we randomly left out 100 states 100 times. To make smaller amounts up to leave-one-out had too 
+        much computational effort. \todo{warum 15\%?}\\
+
+      Of these 10,000 nodes, 9,238 are unique. From the unique nodes, we predicted approximately 
+        98.17\% correct and thus 1.82\% wrong, with duplicate draws always having the same prediction 
+        (data not shown). \\
+
+      We have again dealt with the question of how this data is best modeled. The influence of the taxa 
+        (kingdom, phylum, class) and the depth of the leaf nodes is re-modeled and the BICs compared 
+        (table \ref{table:BIC cross-validation}). Lower taxa than classes (e.g. order) are 
+        computationally too expensive to calculate. \\
+
+      \todo{table for these numbers?}
+      % 100/(25962+34860)*10000 = 16.44
+      % 100/(25962+34860)*9238 = 15.19
+      % 10000 nodes 9238 unique
+      % 9060 nodes $\approx 98.17\%$ correctly predicted
+      % 169 ($\approx 1.82\%$) wrongly predicted
+
+      \begin{table}[h]
+        \begin{center}
+          \begin{tabular}{ |l|r|r|r| }
+            \hline
+            \bfseries Model / Taxa & \bfseries Kingdom & \bfseries Phylum & \bfseries Class \\% & Order \\
+            \hline \hline
+            correctly predicted $\sim$ taxa & 117936 & \cellcolor{green!40}112242 & \cellcolor{green!50}111733 \\% & XXXXX \\
+            \hline
+            correctly predicted $\sim$ taxa + depth & 117776 & \cellcolor{green!50}111304 & \cellcolor{green!50}111273 \\% & XXXXX \\
+            \hline
+            correctly predicted $\sim$ taxa * depth & 117709 & \cellcolor{green!50}111262 & \cellcolor{green!30}113135 \\% & XXXXX \\
             \hline
           \end{tabular} 
+        \end{center}
+        \caption{BIC (Bayesian information criterion) values of cross-validation prediction models. \\
+          These models are created with the R function \textit{glm()} and compared with the 
+            \textit{BIC()} function. This results in the listed BIC values, presented in a heatmap colorization.}
+        \label{table:BIC cross-validation} 
       \end{table}
+
+      The BIC values this time did not prove that the finest model is the best. Of our calculated models, 
+       \textit{correctly predicted $\sim$ phylum * depth} has the smallest value. \\
+
+      We examined the influence of the omitted data on the prediction. On average, about twice as many 
+        leaf nodes are predicted differently. \color{red}The variance is very high. This means that 
+        we have a high degree of dispersion and thus a stochastic situation exists. It also describes 
+        the width of the present probability function. The standard deviation is about five times as 
+        high as the number of omitted nodes, so the variability is quintupled. \color{black} Table 
+        \ref{table:statistics cross-validation} shows these results. \\
+      \begin{table}[h!]
+        \begin{center}
+          \begin{tabular}{ |cl||r|r|r|r|r| }
+            \hline
+            & & \bfseries min & \bfseries max & \bfseries mean & \bfseries variance ($\sigma^2$) & $\sigma$ \\
+            \hline \hline
+            \multirow{3}{*}{\bfseries distance} & \bfseries all     & 0 & 3587.70 & 224.96 & 313650.61 & 560.05 \\
+            & \bfseries leaf nodes                                  & 0 & 3021.12 & 208.69 & 248103.38 & 498.10 \\
+            & \bfseries internal nodes                              & 0 & 566.58 & 16.28 & 4927.95 & 70.20 \\ \hline
+            \multirow{3}{*}{\bfseries lost} & \bfseries all states  & 100 & 100 & 100 & 0 & 0 \\
+            & \bfseries FL states                                   & 44 & 66 & 57.25 & 19.50 & 4.42 \\
+            & \bfseries P states                                    & 34 & 56 & 42.75 & 19.50 & 4.42 \\
+            \hline
+          \end{tabular}
+        \end{center}
+        \caption{Statistics about the leave-100-out cross-validation \\
+          The distance between original and new states is calculated using the Euclidean metric. This 
+            is summed over all states / all leaf node states and all internal node states. \\
+          The lower half of the table describes the distribution of the 'lost' states between parasites 
+            (P) and free-livings (FL).}
+        \label{table:statistics cross-validation}
+      \end{table}
+
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+\chapter{Discussion}
+
+To analyze the results, we have selected some phyla (subtrees) to evaluate our results 
+selectively from the biological point of view: Chordata, Nematoda, Platyhelminthes and 
+Apicomplexa. \\
+
+Several factors such as the distribution of existing input data via parasitics and free-livings, 
+faulty input data from GloBI and reinforcement of errors by multifurcation play an important role which becomes evident in these examples. \\
+
+An important factor here is the credibility of the results. The accuracy of the input data 
+stands and falls with the presence and the correctness of the data of GloBI. Errors of incorrect 
+input data can be amplified by incorrect prediction of unknown species and can be reversed in 
+order to improve the data situation of GloBI. \\
+Since we look at such large trees we can not expect to know all the parasites, so we look at 
+individual positives. They are positive in the sense that the majority have the opposite state.
 
@@
         multifurcation) (see Table \ref{table:percentage loss information subtrees}). This results in 
-        less variance of errors. What is reflected in the results from the table 
-        \ref{table:phylum leaf nodes states}. There are 18 parasites as input data and only 8 more are 
+        less variance of errors. What is reflected in the results shown in table 
+        \ref{table:results of some selected taxa}. There are 18 parasites as input data and only 8 more are 
         predicted. The Chordata mostly consist of free-living species, so this seems believable. We 
@@
 
-      We mapped the few parasitic species in a \colorbox{red}{rough/simple} taxonomy (see Figure \ref{fig:ChordataParasites}): \\
-      Known parasitic birds belong to the order Sauria. Here we know from Rothschild  here there are 
+      We mapped the few parasitic species in a rough taxonomy (see Figure \ref{fig:ChordataParasites}): \\
+      Known parasitic birds belong to the order Sauria. Here we know from Rothschild here that are 
         breeding parasites, like the cuckoo and clepto-parasites as the skuas \cite{Rothschild1957}. We
@@
       It should be noted, however, that this classification is outdated, as it has been proven that 
-        the Turbellaria are not monophyletic. But we will not go into that here. \\
+        the Turbellaria are not monophyletic. But we will not go into detail here. \\
       For the Platyhelminthes we have more state information for the leaf nodes compared to the other 
@@
         found only 5.32\% of them. Blaxter et al. estimates the order of 25,000 parasites in the 
-        Nematoda \cite{Blaxter2015} and speaks of at least seven independently arosed parasitism 
+        Nematoda \cite{Blaxter2015} and speaks of at least seven independently arosen parasites 
         \cite{Blaxter1998}. In a recent article Blaxter identifies 18 origins \cite{Blaxter2015} in 
@@
       The problem at this point, however, is: Hallan speaks of the fact that only 23,000 species 
-        are described by the Nematoda but is it assumed that one million or more species are in this 
+        are described by the Nematoda but it is assumed that one million or more species are in this 
         phylum.\footnote{J. Hallan, unpublished; 
@@
         }. \todo{Link ist nicht erreichbar!} The parasites have been much more studied and thus we start 
-        with only 0.63\% (table \ref{table:phylum leaf nodes states}) free-living species. Against such 
+        with only 0.63\% (table \ref{table:results of some selected taxa}) free-living species. Against such 
         a shifted data situation, the algorithm is almost powerless to make correct predictions. And yet 
@@
 
-      \todotext{Im Folgenden folgen 3 weitere ähnliche tabellen. Einmal eine ähnliche Tabelle inklusive 
-        interner Knoten \ref{table:Phylum internal nodes}, zweimal die Übersicht über die Kingdoms 
-        Blattknoten \ref{table:Kingdom leaf nodes} bzw interne Knoten \ref{table:Kingdom internal nodes}. Welche 
-        nehmen wir? Rest Appendix oder ganz raus?}
-
-      %---------------------------------------------------------------------------------------------------
-      \subsubsection{Origins and Losses} \label{sec:results - origins and losses}
-
-        Weinstein and Kuris have been searching for origins of parasitism in Animalia \cite{Weinstein2016}. 
-          They identified 223 parasitic origins: 223 in Metazoa $\supset$ 143 in Arthropoda $\supset$ 87 
-          in Insecta. \\
-        This has led us to count the origins and losses of parasitism in our investigation as well. \\
-        We count only one origin / loss in a parent node with different children's nodes. \\
-        Here we have encountered a problem: The Castor algorithm gives us probabilities for states. That 
-          means there are also nodes with state like 0.3 or 0.5. The question is, how to count these state 
-          changes. We decided to round the values.
-        % \begin{lstlisting}[gobble=6]
-        %   possible states: 0, 0.333, 0.4, 0.5, 0.667, 0.75, 1
-        %   rounded to:    0  0      0    0    1      1     1
-        % \end{lstlisting}
-
-        In Table \ref{table:origins and losses} we can see, that we found some more origins than Weinstein 
-          and on top of that some losses. \\
-
-        When more closely regarding the same phyla as in the section before: Chordata, Nematoda, 
+      Origins: \\
+      We go back to the same phyla as in the previous section: Chordata, Nematoda, 
         Platyhelminthes and Apicomplexa. \\
@@
         mostly all species predicted as parasites. \\
-        Nematoda is again full of problems. The root node is predicted as a parasite and so we have more 
+      Nematoda is again \colorbox{red}{full of problems}. The root node is predicted as a parasite and so we have more 
         losses of parasitism for the less information of free-living species in this phylum. The rest 
@@
         \cite{Blaxter1998}. If we assume that the root node of Nematoda is free-living, then some 
-          losses would have to turn around and become Origins. So it could be that we end up in a similar 
+        losses would have to turn around and become Origins. So it could be that we end up with a similar 
         size as Blaxter.
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{Leave-100-out cross-validation} \label{sec:results - cross-validation}
-      For a further validation of our results, we carried out a leave-100-out cross-validation. \\
-      In order to achieve about 15\% of the 60,871 input node states with a validation, 
-        we randomly left out 100 states 100 times. To make smaller amounts up to leave-one-out had too 
-        much computational effort. \todo{warum 15\%?}\\
-
-      Of these 10,000 nodes, 9,238 are unique. From the unique nodes, we predicted approximately 
-        98.17\% correct and thus 1.82\% wrong, with duplicate draws always having the same prediction 
-        (data not shown). \\
-
-      We have again dealt with the question of how this data is best modeled. The influence of the taxa 
-        (kingdom, phylum, class) and the depth of the leaf nodes is re-modeled and the BICs compared 
-        (table \ref{table:BIC cross-validation}). Lower taxa than classes (e.g. order) are 
-        computationally too expensive to calculate. \\
-
-      \todo{table for these numbers?}
-      % 100/(25962+34860)*10000 = 16.44
-      % 100/(25962+34860)*9238 = 15.19
-      % 10000 nodes 9238 unique
-      % 9060 nodes $\approx 98.17\%$ correctly predicted
-      % 169 ($\approx 1.82\%$) wrongly predicted
-
-      \begin{table}[h]
-        \begin{center}
-          \begin{tabular}{ |l|r|r|r| }
-            \hline
-            \bfseries Model / Taxa & \bfseries Kingdom & \bfseries Phylum & \bfseries Class \\% & Order \\
-            \hline \hline
-            correctly predicted $\sim$ taxa & 117936 & \cellcolor{green!40}112242 & \cellcolor{green!50}111733 \\% & XXXXX \\
-            \hline
-            correctly predicted $\sim$ taxa + depth & 117776 & \cellcolor{green!50}111304 & \cellcolor{green!50}111273 \\% & XXXXX \\
-            \hline
-            correctly predicted $\sim$ taxa * depth & 117709 & \cellcolor{green!50}111262 & \cellcolor{green!30}113135 \\% & XXXXX \\
-            \hline
-          \end{tabular} 
-        \end{center}
-        \caption{BIC (Bayesian information criterion) values of cross-validation prediction models. \\
-          These models are created with the R function \textit{glm()} and compared with the 
-            \textit{BIC()} function. This results in the listed BIC values, presented in a heatmap colorization.}
-        \label{table:BIC cross-validation} 
-      \end{table}
-
-      The BIC values this time did not prove that the finest model is the best. Of our calculated models, 
-       \textit{correctly predicted $\sim$ phylum * depth} has the smallest value. \\
-
-      We examined the influence of the omitted data on the prediction. On average, about twice as many 
-        leaf nodes are predicted differently. \color{red}The variance is very high. This means that 
-        we have a high degree of dispersion and thus a stochastic situation exists. It also describes 
-        the width of the present probability function. The standard deviation is about five times as 
-        high as the number of omitted nodes, so the variability is quintupled. \color{black} Table 
-        \ref{table:statistics cross-validation} shows these results. \\
-      \begin{table}[h!]
-        \begin{center}
-          \begin{tabular}{ |cl||r|r|r|r|r| }
-            \hline
-            & & \bfseries min & \bfseries max & \bfseries mean & \bfseries variance ($\sigma^2$) & $\sigma$ \\
-            \hline \hline
-            \multirow{3}{*}{\bfseries distance} & \bfseries all     & 0 & 3587.70 & 224.96 & 313650.61 & 560.05 \\
-            & \bfseries leaf nodes                                  & 0 & 3021.12 & 208.69 & 248103.38 & 498.10 \\
-            & \bfseries internal nodes                              & 0 & 566.58 & 16.28 & 4927.95 & 70.20 \\ \hline
-            \multirow{3}{*}{\bfseries lost} & \bfseries all states  & 100 & 100 & 100 & 0 & 0 \\
-            & \bfseries FL states                                   & 44 & 66 & 57.25 & 19.50 & 4.42 \\
-            & \bfseries P states                                    & 34 & 56 & 42.75 & 19.50 & 4.42 \\
-            \hline
-          \end{tabular}
-        \end{center}
-        \caption{Statistics about the leave-100-out cross-validation \\
-          The distance between original and new states is calculated using the Euclidean metric. This 
-            is summed over all states / all leaf node states and all internal node states. \\
-          The lower half of the table describes the distribution of the 'lost' states between parasites 
-            (P) and free-livings (FL).}
-        \label{table:statistics cross-validation}
-      \end{table}
-
-%---------------------------------------------------------------------------------------------------
-%---------------------------------------------------------------------------------------------------
-%---------------------------------------------------------------------------------------------------
-%---------------------------------------------------------------------------------------------------
-\chapter{Discussion}
 
@@
       multifurcation and smaller value for unknown nodes. This is also confirmed by our biological 
-      analysis of the Chordata subtree (see subsection \ref{sec:results - biological view}). \\
+      analysis of the Chordata subtree (see subsection \ref{subsec:results - statistics on predicted states}). \\
     However, this means that the ancestral states' data in the direction of root node are probably 
@@
       Our comparison with the paper from Weinstein and Kuris \cite{Weinstein2016} (see subsection 
-      \ref{sec:results - origins and losses}), however, leaves us with optimism.
+      \ref{subsec:results - statistics on predicted states}), however, leaves us with optimism.
 
@@
 
-  %---------------------------------------------------------------------------------------------------
-  \section{Results}
-
-    \begin{table}[h!]
-      \begin{center}
-        \begin{tabular}{ |l|r||r|r||r|r|r|r|r|r| }
-          \hline
-          & & \multicolumn{2}{c||}{\bfseries original states} & \multicolumn{6}{c|}{\bfseries final states} \\
-          \bfseries Phylum & \bfseries \# nodes & \bfseries FL & \bfseries P
-            & \bfseries 0 (FL) & \bfseries 0.4 & \bfseries 0.5 & \bfseries 0.67 & \bfseries 0.75 & \bfseries 1 (P) \\
-          \hline \hline
-          Chordata & 122546 & 10451 & 18 
-            & 122473 & 0 & 0 & 0 & 0 & 73 \\
-          Nematoda & 33564 & 21 & 3289 
-            & 846 & 0 & 1133 & 0 & 0 & 31585 \\
-          Platyhelminthes & 27142 & 7 & 7086 
-            & 1010 & 0 & 175 & 0 & 0 & 25957 \\
-          Apicomplexa & 2102 & 1 & 255 
-            & 1 & 0 & 0 & 0 & 0 & 2101 \\
-          % \hline
-          % Arthropoda & 1319460 & 18912 & 11141 
-          %   & 1207204 & 1313 & 25499 & 4852 & 1957 & 78635 \\
-          \hline
-        \end{tabular}
-      \end{center}
-      \caption{Some selected phyla (subtrees), including internal nodes, are examined for the evolution 
-      of the amount and percentage of given data to predicted data.}
-      \label{table:Phylum internal nodes}
-    \end{table}
-
-    \begin{table}[h!]
-      \begin{center}
-        \hspace*{-2cm}\begin{tabular}{ |l|r||r|r||r|r|r|r|r|r|r|r| }
-          \hline
-          & & \multicolumn{2}{c||}{\bfseries original states} & \multicolumn{8}{c|}{\bfseries final states} \\
-          \bfseries Kingdom & \bfseries \# nodes & \bfseries FL & \bfseries P
-            & \bfseries 0 (FL) & \bfseries 0.25 & \bfseries 0.33 & \bfseries 0.4 & \bfseries 0.5 & \bfseries 0.67 & \bfseries 0.75 & \bfseries 1 (P) \\
-          \hline \hline
-          none & 84456 & 45 & 529 
-            & 15035 & 243 & 25910 & 0 & 8764 & 6183 & 0 & 28140 \\
-          Fungi & 324105 & 577 & 2983
-            & 39088 & 0 & 0 & 0 & 5858 & 0 & 0 & 274803 \\
-          Chloroplastida & 460457 & 3519 & 77
-            & 454211 & 0 & 0 & 0 & 4688 & 0 & 0 & 1558 \\
-          Metazoa & 1670956 & 30758 & 22373
-            & 1485749 & 0 & 0 & 1313 & 29002 & 5102 & 1957 & 147833 \\
-          \hline  
-        \end{tabular}
-      \end{center}
-      \caption{All kingdoms (subtrees), inkluding internal nodes, are examined for the evolution of the 
-      amount and percentage of given data to predicted data.}
-      \label{table:Kingdom internal nodes}
-    \end{table}
-
 \end{document}

### 2018-03-30 Paper - Latex/Paper - Skizze - v4.tex
Thesis - Results fertig

@@
       In order to achieve about 15\% of the 60,871 input node states with a validation, 
-        we randomly left out 100 states 100 times. To make smaller amounts up to leave-one-out had too 
-        much computational effort. \todo{warum 15\%?}\\
+        we randomly left out 100 states 100 times.Omit smaller amounts of states up to leave-one-out had 
+        too much computational effort.
 
       Of these 10,000 nodes, 9,238 are unique. From the unique nodes, we predicted approximately 
-        98.17\% correct and thus 1.82\% wrong, with duplicate draws always having the same prediction 
-        (data not shown). \\
-
-      We have again dealt with the question of how this data is best modeled. The influence of the taxa 
-        (kingdom, phylum, class) and the depth of the leaf nodes is re-modeled and the BICs compared 
-        (table \ref{table:BIC cross-validation}). Lower taxa than classes (e.g. order) are 
-        computationally too expensive to calculate. \\
-
-      \todo{table for these numbers?}
+        98.17\% correct and thus 1.82\% wrong, with duplicate draws always having the same prediction. 
+        The associated variance is 0.017, which means that no large amounts of input states have to be 
+        omitted.
+
+        We have again considered how this data can best be modeled to compare whether there is a lot 
+        of variability in the taxa and whether the depth is an influencing factor over our prediction. 
+        So, the influence of the taxa (kingdom, phylum, class) and the depth of the leaf nodes is 
+        re-modeled and the BICs compared (table \ref{table:BIC cross-validation}). Lower taxa than 
+        classes (e.g. order) are computationally too expensive to calculate.
+
+      % \todo{table for these numbers?}
       % 100/(25962+34860)*10000 = 16.44
@@
       % 169 ($\approx 1.82\%$) wrongly predicted
+      % variance is 0.017
 
@@
       We examined the influence of the omitted data on the prediction. On average, about twice as many 
-        leaf nodes are predicted differently. \color{red}The variance is very high. This means that 
-        we have a high degree of dispersion and thus a stochastic situation exists. It also describes 
-        the width of the present probability function. The standard deviation is about five times as 
-        high as the number of omitted nodes, so the variability is quintupled. \color{black} Table 
-        \ref{table:statistics cross-validation} shows these results. \\
+        leaf nodes are predicted differently. %\color{red}The variance is very high. This means that 
+        % we have a high degree of dispersion and thus a stochastic situation exists. It also describes 
+        % the width of the present probability function. The standard deviation is about five times as 
+        % high as the number of omitted nodes, so the variability is quintupled. \color{black} 
+        Table \ref{table:statistics cross-validation} shows these results. \\
       \begin{table}[h!]

### 2018-03-30 code/evaluation/analyse_cross-validation.R

@@ -19,80 +19,89 @@ leaf.taxa <-  all.taxa[all.taxa$nr_children==0, ]
 leaf.taxa <- as.data.frame(leaf.taxa)
 table(leaf.taxa$correct_predicted)[order(table(leaf.taxa$correct_predicted))]
 
+leaf.taxa$correct_predicted <- as.integer(leaf.taxa$correct_predicted)
+table(leaf.taxa$correct_predicted)[order(table(leaf.taxa$correct_predicted))]
+
+min(na.omit(leaf.taxa$correct_predicted))
+max(na.omit(leaf.taxa$correct_predicted))
+var(na.omit(leaf.taxa$correct_predicted))
+mean(na.omit(leaf.taxa$correct_predicted))
+
 leaf.taxa$correct_predicted <- !is.na(leaf.taxa$correct_predicted)
+table(leaf.taxa$correct_predicted)[order(table(leaf.taxa$correct_predicted))]
 
-null.correct_predicted.mod <- glm(correct_predicted~1, data=leaf.taxa, family="binomial")
+# null.correct_predicted.mod <- glm(correct_predicted~1, data=leaf.taxa, family="binomial")
 
-print('------------------------kingdom - phylum - class - order--------------------------')
+# print('------------------------kingdom - phylum - class - order--------------------------')
 
-kingdom.correct_predicted.mod <- glm(correct_predicted~kingdom, data=leaf.taxa, family="binomial")
-print(c('BIC=',  BIC(kingdom.correct_predicted.mod)))
-# effect("kingdom", kingdom.correct_predicted.mod)
-# anova(null.correct_predicted.mod, kingdom.correct_predicted.mod)
+# kingdom.correct_predicted.mod <- glm(correct_predicted~kingdom, data=leaf.taxa, family="binomial")
+# print(c('BIC=',  BIC(kingdom.correct_predicted.mod)))
+# # effect("kingdom", kingdom.correct_predicted.mod)
+# # anova(null.correct_predicted.mod, kingdom.correct_predicted.mod)
 
-# summary(kingdom.correct_predicted.mod)
+# # summary(kingdom.correct_predicted.mod)
 
-phylum.correct_predicted.mod <- glm(correct_predicted~phylum, data=leaf.taxa, family="binomial")
-print(c('BIC=',  BIC(phylum.correct_predicted.mod)))
-# effect("phylum", phylum.correct_predicted.mod)
[…]

### 2018-03-30 Paper - Latex/Paper - Skizze - v4.tex
Thesis - Schönheitskorrekturen

@@
     \cite{Louca2017}, which performed best, for the actual reconstruction on the real data. \\
-    \todo{... biological view}
-  %  On the one hand, we have examined the results of some 
-    % subtrees for their credibility with the help of biological background knowledge (subsection 
-    % \ref{subsec:results - statistics on predicted states}). On the other hand, we
-  We evaluated these by performing a leave-100-out cross-validation and predicted approximately 
-    98.17\% of the omitted states correct (subsection \ref{sec:results - cross-validation}). \\
+  We evaluated these on the one hand by analysing some statisitcs (subsection 
+    \ref{subsec:results - statistics on predicted states}) and on the other hand by performing a 
+    leave-100-out cross-validation. There we predicted approximately 98.17\% of the omitted states 
+    correct (subsection \ref{sec:results - cross-validation}). \\
 
@@
 
-      We also compared different models in terms of their BICs (Table: \ref{table:BIC unknown information}). \\ 
+      We also compared different models in terms of their BICs (table: \ref{table:BIC unknown information}). \\ 
       \begin{table}[h!]
@@
       These missing data modeling results could be used to better simulate the data. \\
+
+\newpage
 
@@
     Figure \ref{fig:influence of unknown data} shows the results of examining various parameters.
-
-    Since we have a lot of missing data in most subtrees (both internal nodes and state informations), 
-      the Sankoff gives a better prediction and is thus used for real data analysis.
 
@@
 
+    Since we have a lot of missing data in most subtrees (both internal nodes and state informations), 
+      the Sankoff gives a better prediction and is thus used for real data analysis.
+
   %---------------------------------------------------------------------------------------------------
@@
   \section{Results of the real data analysis created with Sankoff}
-    This section is about evaluating the prediction of real data using the Sankoff method. It is 
-      divided into two subsections. The analysis of some statistics on the predicted states, 
-      \todo{with the result...} (subsection \ref{subsec:results - statistics on predicted states}) and the presentation 
-      of the leave-100-out cross-validation results (subsection \ref{sec:results - cross-validation}).
-      \todo{This has revealed that ...} \\
+    This section is about evaluating the prediction of real data using the Sankoff method and is 
+      divided into two subsections. \\
+    The analysis of some statistics on the predicted states, with the result that we predict a total 
+      of significantly more free-livings than parasites despite almost 50:50 distributed input states 
+      (subsection \ref{subsec:results - statistics on predicted states}) and the presentation of the 
+      leave-100-out cross-validation results (subsection \ref{sec:results - cross-validation}) This 
+      has revealed that we predicted approximately 98.17\% correct with a small variance.
 
@@
 
+~ \\
+
       Weinstein and Kuris have been searching for origins of parasitism in Animalia \cite{Weinstein2016}. 
@@
         in Insecta. \\
-      In Table \ref{table:results of some selected taxa} we can see, that we found some more origins than 
-        Weinstein: 321 in Metazoa $\supset$ 281 in Arthropoda $\supset$ 245 in Insecta and on top of 
-        that some losses: 129 in Metazoa $\supset$ 108 in Arthropoda $\supset$ 77 in Insecta. The 
-        origins and losses calculated by Sankoff are thus closer to the leaves in the tree.
+      In the last columns of the table \ref{table:results of some selected taxa} we can see, that we 
+        found some more origins than Weinstein: 321 in Metazoa $\supset$ 281 in Arthropoda $\supset$ 245 
+        in Insecta and on top of that some losses: 129 in Metazoa $\supset$ 108 in Arthropoda $\supset$ 
+        77 in Insecta. The origins and losses calculated by Sankoff are thus closer to the leaves in the tree.
 
@@
       The BIC values this time did not prove that the finest model is the best. Of our calculated models, 
-       \textit{correctly predicted $\sim$ phylum * depth} has the smallest value. \\
+       \textit{correctly predicted $\sim$ phylum * depth} has the smallest value.
 
@@
 In contrast to the other phyla examined, the phylogeny in the Chordata is more pronounced (less 
-        multifurcation) (see Table \ref{table:percentage loss information subtrees}). This results in 
+        multifurcation) (see table \ref{table:percentage loss information subtrees}). This results in 
         less variance of errors. What is reflected in the results shown in table 
@@
       For the Platyhelminthes we have more state information for the leaf nodes compared to the other 
-        considered subtrees, see Table \ref{table:percentage loss information subtrees}. We start with 
+        considered subtrees, see table \ref{table:percentage loss information subtrees}. We start with 
         0.1\% free-livings and predicted 0.77\% as free-living species. \\
@@
       \ref{fig:taxaTable2}. \\
-      ... (see Table \ref{table:...})
+      ... (see table \ref{table:...})
 
@@
     Mithilfe des taxonomischen Baums von OTL haben wir die Knoten ihren Kingdoms, Phyla und Classes 
-      zugeteilt (see Table \ref{table:...}). \\
+      zugeteilt (see table \ref{table:...}). \\
 

### 2018-03-31 Paper - Latex/Paper - Skizze - v4.tex
Thesis - Discussion

@@
-\input{arbeit-vorlage-praeambel.tex} % Importiere die Einstellungen aus der Präambel
-% hier beginnt der eigentliche Inhalt
+\input{arbeit-vorlage-praeambel.tex}
 
@@
 \begin{document}
-  % Titelseite
   \begin{titlepage}
@@
     partners, the parasite, lives in or on the other, the host. The parasite draws food from its 
-    host and harms it in the process. According to estimates, above 40\% of all eukaryotes are 
+    host and harms it in the process. According to estimates, above 40\% of all Eukaryota are 
     parasites. Nevertheless, it is computationally difficult to obtain information whether a 
@@
   This represents, to our knowledge, the first comprehensive computational reconstruction of the 
-    emergence of parasitism in eukaryotes. We argue that such an approach is necessary to allow 
+    emergence of parasitism in Eukaryota. We argue that such an approach is necessary to allow 
     further incorporation of parasitism as an important trait in species interaction databases and 
-    in individual studies on eukaryotes e.g. in the microbiome.
+    in individual studies on Eukaryota e.g. in the microbiome.
 
@@
     only been done for Bacteria and Archaea for binary traits by Goberna and Verdú \cite{Goberna2015}.
-    However, this differs from eukaryotes in the sense that complex traits such as parasitism depend
+    However, this differs from Eukaryota in the sense that complex traits such as parasitism depend
     on more than one gene.
@@
   The objectives of this work are the following points: (1) Find a suitable ancestral state 
-    reconstruction method. (2) Accomplish reconstructing on the Eucaryotic synthesis tree of OTL. \\
+    reconstruction method. (2) Accomplish reconstructing on the Eukaryota synthesis tree of OTL. \\
   The goal of Point 1 is to evaluate the possible methods based on a simulation of our data 
@@
     our data. Hereby, we want to find out how far it is possible to use the Open Tree of Life (OTL) 
-    to expandavailable information via phylogenetic trait prediction. As a basis for known states, 
-    we use the Global Biotic Interactions (GloBI) database, which cathegorises 34,860 and 25,962 
+    to expand available information via phylogenetic trait prediction. As a basis for known states, 
+    we use the Global Biotic Interactions (GloBI) database, which categorises 34,860 and 25,962 
     species as free-living and parasites. This data is used to perform an ancestral state 
@@
       (1) Retrieve phylogenentic tree data as input for the tree (OTL) and the state information (GloBI).
-      (2) Get metadata of these for a realisitc simulation of the maximum parsimony algorithms (Fitch \& Sankoff).
+      (2) Get metadata of these for a realistic simulation of the maximum parsimony algorithms (Fitch \& Sankoff).
       (3) Build and run the simulation.
@@
       (6) Run the resulting algorithm on the original data.
-      (7) Evalute and interprete the results. %$\rightarrow$ Origins etc...
+      (7) Evaluate and interpret the results. %$\rightarrow$ Origins etc...
     }
@@
     Furthermore the Open Tree Taxonomy (OTT) from OTL is used because it includes most of the known 
-      taxonomies and is synthesised by prefering taxonomies that match with available phylogenetic 
+      taxonomies and is synthesised by preferring taxonomies that match with available phylogenetic 
       data. The team from OTL prefer a maximum number of species \cite{Hinchliff2015}, this results 
@@
       This is solved by preferring parasitic. \\
-    For each species known identifyers are stored in GloBI. This includes OTT (the taxonomy of OTL). 
-      All species that have stored an OTT indentifyer and have a matching interaction are divided into 
+    For each species known identifiers are stored in GloBI. This includes OTT (the taxonomy of OTL). 
+      All species that have stored an OTT identifier and have a matching interaction are divided into 
       two lists: parasites and free-livings.
@@
 
-      Input: A rooted, binary tree, with state informations in the leaf nodes. Each node is depicted as 
+      Input: A rooted, binary tree, with state information in the leaf nodes. Each node is depicted as 
         a set of states. There are only two states in this thesis, free-living (FL) and parasitic (P). 
@@
           \caption{Fitch algorithm for binary trees. \\
-            The unknown leaf node is discribed with both states. Computed internal nodes (exclusive the 
+            The unknown leaf node is described with both states. Computed internal nodes (exclusive the 
             root node) consists of three sets, where the last set is the final one (bold). \\
@@
       The extension to the non-binary case is quite obvious, but holds some opportunities. In this case, 
-        more than two children may be present for the first traversal, but the incision or union may 
+        more than two children may be present for the first traversal, but the intersection or union may 
         also be formed over more than two sets. Also in the second traversing, there may be several 
@@
           (3) The number drawn is above the threshold. $\rightarrow$ The node state changes to parasitic (P: blue). \\
-          (4) Now draw random numbers from the parasite distribution (red) until one number lies unter the threshold. Then change back.}
+          (4) Now draw random numbers from the parasite distribution (red) until one number lies under the threshold. Then change back.}
         \label{fig:set node states}
@@
     After traversing through the tree, each state is saved in a nodelist associated with the node 
-      indentifyer which is the OTT from OTL.
+      identifier which is the OTT from OTL.
 
@@
 \chapter{Results}
+  In the first part of this work, we were able to provide the proof of concept for the Sankoff 
+    algorithm to perform an ancestral state reconstruction of the present Eukaryota tree. We will 
+    therefore discuss in the following how significant the result of this reconstruction is.
+
+    To do so, we first look at the input data we have: the use of Open Tree of Life for the tree 
+      gives us the greatest approximation to a phylogeny of the Eukaryota. Since such a large 
+      phylogeny has not been completely dissected, this is only a synthesis of phylogenetic trees 
+      with a taxonomy as a backbone. As a result, the tree is far from binary, we found a 
+      multifurcation of 89.45 \%. However, this is highly variable and therefore the reconstruction 
+      is still very good on wide parts of the tree. \\
+    On the other hand, we used the Global Biotic Interactions (GloBI) database to get the state 
+    information for the leaf nodes. However, we were able to extract only 2.66\% of the node 
+    information from GloBI. However, we found out that there are more data in GloBI that could be 
+    taken away with some work.
+
+    % One last limitation also exists in the data situation itself. We have pointed out in various 
+    %   sections that we have a strong multifurcation and only a few data about leaf node states.
+
+    Next, let's consider the limitations of the simulation that led to the choice of the Sankoff 
+      algorithm. Our own main point of criticism is that we did not simulate the transition 
+      probabilities and estimate an unrealistically high number of transitions (origins and losses). 
+      The Sankoff algorithm is very well scored despite this increased difficulty (more transitions 
+      means more complex predictions) and its proven feasibility.
+
+    Finally, we analyze the validation of our ancestral state reconstruction results. We will do a 
+      selective analysis from a biological perspective and discuss the leave-100-out 
+      cross-validation. \\
+    Above all, the 'biological view' gives a first impression of the credibility of the results. But 
+      it can not make any statistical statements. Here the interested researcher may have to analyze 
+      the subtrees of being relevant to him for himself. \\
+    Of course, cross-validation can be expanded. With more computing power, a leave-1-out 
+      cross-validation could be performed. However, our result on this point is 98.17\% correct. \\
+
+\todo{old:}
+
   This work deals with the ancestral state reconstruction of the entire Eukaryota relatives tree.
@@
           \hline \hline
-          Metazoa         & 96.44\%  & 87.93\% \\ \hline
+          Chloroplastida  & 99.14\%  & 89.46\% \\ \hline
           Fungi           & 98.87\%  & 96.97\% \\ \hline
-          Chloroplastida  & 99.14\%  & 89.46\% \\
+          Metazoa         & 96.44\%  & 87.93\% \\
           \hline \hline
-          % Arthropoda      & 97.49\%  & 89.95\% \\ \hline
           Apicomplexa     & 86.26\%  & 87.16\% \\ \hline
+          Arthropoda      & 97.49\%  & 89.95\% \\ \hline
+          Chordata        & 88.59\%  & \cellcolor{green!50}66.49\% \\ \hline
           Nematoda        & 89.01\%  & 88.59\% \\ \hline
-          Chordata        & 88.59\%  & \cellcolor{green!50}66.49\% \\ \hline
           Platyhelminthes & \cellcolor{green!50}68.73\%  & 80.34\% \\
@@
         (free-living or parasite) in the leaf nodes. \\
-      The eukaryotic synthesis tree has 293,463 leaf nodes. The GloBI database has 5,346,414 interactions 
+      The Eukaryota synthesis tree has 293,463 leaf nodes. The GloBI database has 5,346,414 interactions 
         (at 29.01.2018). Out of this data we got 51,337 free-living species and 47,332 parasite species 
@@
 
-    Since we have a lot of missing data in most subtrees (both internal nodes and state informations), 
+    Since we have a lot of missing data in most subtrees (both internal nodes and state information), 
       the Sankoff gives a better prediction and is thus used for real data analysis.
@@
             & \bfseries internal nodes                              & 0 & 566.58 & 16.28 & 4927.95 & 70.20 \\ \hline
-            \multirow{3}{*}{\bfseries lost} & \bfseries all states  & 100 & 100 & 100 & 0 & 0 \\
-            & \bfseries FL states                                   & 44 & 66 & 57.25 & 19.50 & 4.42 \\
-            & \bfseries P states                                    & 34 & 56 & 42.75 & 19.50 & 4.42 \\
-            \hline
+            % \multirow{3}{*}{\bfseries lost} & \bfseries all states  & 100 & 100 & 100 & 0 & 0 \\
+            % & \bfseries FL states                                   & 44 & 66 & 57.25 & 19.50 & 4.42 \\
+            % & \bfseries P states                                    & 34 & 56 & 42.75 & 19.50 & 4.42 \\
+            % \hline
           \end{tabular}
@@
           The distance between original and new states is calculated using the Euclidean metric. This 
-            is summed over all states / all leaf node states and all internal node states. \\
-          The lower half of the table describes the distribution of the 'lost' states between parasites 
-            (P) and free-livings (FL).}
+            is summed over all states, all leaf node states and all internal node states.}
+          % The lower half of the table describes the distribution of the 'lost' states between parasites 
+            % (P) and free-livings (FL).}
         \label{table:statistics cross-validation}
@@
 \chapter{Discussion}
-
-To analyze the results, we have selected some phyla (subtrees) to evaluate our results 
-selectively from the biological point of view: Chordata, Nematoda, Platyhelminthes and 
-Apicomplexa. \\
-
-Several factors such as the distribution of existing input data via parasitics and free-livings, 
-faulty input data from GloBI and reinforcement of errors by multifurcation play an important role which becomes evident in these examples. \\
-
-An important factor here is the credibility of the results. The accuracy of the input data 
-stands and falls with the presence and the correctness of the data of GloBI. Errors of incorrect 
-input data can be amplified by incorrect prediction of unknown species and can be reversed in 
-order to improve the data situation of GloBI. \\
+  This chapter deals with the question of how trustworthy our result of the ancestral state 
+    reconstruction of the Eukaryota tree is. And further on how well our simulation can simulate the 
+    real problem and thus make statements about the predictive power of the applied Sankoff algorithm.
+
+  We have pursued this question in various investigations and yet, of course, further possibilities 
+    for improvement remain. Despite these possibilities for improvement, our reconstruction gives a 
+    first good assessment of the whole tree.
+
+  In the first part of this work, we were able to provide the proof of concept for the Sankoff 
+    algorithm to perform an ancestral state reconstruction of the present Eukaryota tree. In the 
+    following, we will first discuss the data situation and the simulation that led to the selection 
+    of the Sankoff algorithm, and then discuss how significant the result of this reconstruction is.
+
+  We evaluated our ancestral state reconstruction and the relational state prediction using a 
+    leave-100-out cross-validation. In addition, in this chapter, we will take a closer look at some 
+    subtrees and discuss their credibility from a biological perspective.
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Data situation} \label{sec:discussion - data situation}
+    The used Eukaryota synthesis tree from OTL \cite{Hinchliff2015} has 241,974 internal nodes and 
+      293,463 leaf nodes. In addition, we could specify 25,962 parasitic and 34,860 free-living 
+      species from GloBI \cite{Poelen2014}. \\
+    This gives us a high number of missing internal nodes (high multifurcation) and a low number of 
+      node states of the leaf nodes in the entire tree.
+    We suspect that this lack of information is not equally distributed in both cases. We conclude 
+      this from various observations.
+
+    For one thing, there were a few subtrees of higher ranks whose information share was much higher. 
+      In the Chordata there is only 66.49\% multifurcation and in the Platyhelminthes only 68.73\% 
+      missing state information. \\
+    Furthermore, we know that OTL is a synthesis of 819 phylogenetic trees. This suggests that just 
+      these parts of the tree are very well resolved and the remainder consists only of the rough 
+      taxonomy. \\
+    \todotext{
+    For a review of this underlying taxonomy, we have compiled a list of all taxa and drawn them in 
+      relation to their distribution (see appendix section \ref{sec:otl analysis}).
+    The number of nodes in the tree corresponding to a taxonomic rank is tabulated. \\
+    For the classical taxonomic ranks phylum, class, order, family, genus xyz is found (appendix 
+      \ref{sec:otl analysis}). \\
+    A closer look is taken at some of the features of the synthesis tree on the one hand the 
+      distribution of the taxa and on the other the distribution of the nodes on the taxa. Since 
+      this is \colorbox{red}{not directly relevant} for this study, this section has been moved to 
+      the appendix \ref{sec:otl analysis}.}
+
+    % The investigation of the taxonomy revealed that the OTL tree has three kingdoms: Chloroplastida, 
+    %   Metazoa, Fungi, 53 phyla, 195 classes and 924 orders. \\
+    % Since the analysis of the tree is not part of this work, it should be mentioned here that, 
+    %   according to recent findings, this is not complete and we lack some taxa in every rank. For 
+    %   example, Cavalier-Smith says that one distinguishes between seven and nine kingdoms 
+    %   \cite{CavalierSmith1981}. \\
+
+    From GloBI we got very little information about leaf node states compared to their number in the 
+      Eukaryota tree. Nevertheless, the prediction of leave-100-out cross-validation was very good. 
+      This also leads to the conclusion that the information is very clustered.
+
+    As a last point, we would like to cite the modeling of the missing information. The fact that this 
+      is getting better, the lower ordered taxa (smaller subtrees) we are looking at, also suggests a 
+      high variability of the data.
+
+    We would like to mention a few other aspects of the GloBI database here. \\
+    Of course, such large data sets are flawed. We found some misinformation and were able to report 
+      some of these directly to GloBI. \\
+    We also found that there is some unused information in GloBI. We therefore found some more source 
+      species and target species without OTT identifiers. Since we currently use only OTT 
+      identifiers, we could not use this information. At this point there is thus the possibility to 
+      use more of the existing data, if one performs a matching with the other identifiers.
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Simulation} \label{sec:discussion - simulation}
+    The aim of the simulation is to test the influence of various unknown or uncertain parameters on 
+      some selected algorithms in order to test the credibility of the prediction of these for the 
+      given problem.
+
+    We assume that different parasite types have different transition probabilities. It is therefore 
+      difficult to establish a common distribution across the Eukaryota tree. \\
+    Based on the estimates of Windsor \cite{Windsor1998}, we have assumed a distribution of 40\% 
+      parasites to 60\% free-livings in this work. As a result of the diversity of parasites and the 
+      lack of generalizations, we have generally stated that 
+      $\mathcal{P}(FL \rightarrow P) = \mathcal{P}(P \rightarrow FL)$. But it is also reasonable to 
+      assume that in general $\mathcal{P}(FL \rightarrow P) > \mathcal{P}(P \rightarrow FL)$, because 
+      a reverse mutation is usually less likely. However, one would have to determine how much this 
+      difference is and thus discuss another parameter.
+
+    In the simulation, we found that this combination has a significant influence on the predictive 
+      power of the algorithms. \\
+    We have adapted the combination of distributions and threshold to a high probability of achieving 
+      the given proportions on initial attempts. However, this means that we prefer high transition 
+      probabilities for both transitions and thus the simulated trees have a large number of 
+      transitions. It can be assumed that this may not correspond to the real data and thus means a 
+      limitation of our simulation. Further we assume that with less number of state changes, the 
+      predictive power of both algorithms would be even better, thus this limitation is probably not 
+      very restrictive. \\
+    At this point it would be possible to test other distributions with equal threshold values. this 
+      would be more computationally expensive, but would result in fewer transitions.
+
+    % With these further simulations you could find out if the issue of distributions plays a big role. 
+    %   Conversely, one could estimate possible distributions based on the data location in the tree. 
+    %   However, this is likely to be very difficult given the poor data. For this reason, we have 
+    %   decided in this work to accept very general values and not to speculate much. \\
+
+    The used castor package \cite{Louca2017} offers the possibility to enter different transition 
+      probabilities, so with information about these probabilities, you might be able to improve the 
+      prediction here.
+
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Biological view}
+    To analyze the results, we have selected some phyla (subtrees) to evaluate our results selectively 
+      from the biological point of view: Chordata, Nematoda, Platyhelminthes and Apicomplexa.
+
+    Several factors such as the distribution of existing input data via parasites and free-livings, 
+      faulty input data from GloBI and reinforcement of errors by multifurcation play an important 
+      role which becomes evident in these examples.
+
+    The accuracy of our results stands and falls with the presence and the correctness of the data of 
+      GloBI. Errors of incorrect input data can be amplified by incorrect prediction of unknown 
+      species and can be reversed in order to improve the data situation of GloBI. \\
     Since we look at such large trees we can not expect to know all the parasites, so we look at 
@@
     In contrast to the other phyla examined, the phylogeny in the Chordata is more pronounced (less 
-        multifurcation) (see table \ref{table:percentage loss information subtrees}). This results in 
-        less variance of errors. What is reflected in the results shown in table 
-        \ref{table:results of some selected taxa}. There are 18 parasites as input data and only 8 more are 
-        predicted. The Chordata mostly consist of free-living species, so this seems believable. We 
-        started with 99.83\%  species and predict 99.97\% species as free-living (including already 
-        known nodes).
-
-      \begin{figure}
-        \centering
-        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.85\textwidth]{Figures/ChordataParasites.png}
-        \caption{Parasites of Phylum: Chordata. \\
-          All parasite data of the chordata are mapped into a rough taxonomy (phylum, class, order, 
-            family) in order to understand their distribution and affiliation. \\
-          The internal nodes are the wanted taxa from OTL (with the addition of \# input parasites to 
-            $\rightarrow$ \# predicted parasites). \\
-          The leaf nodes are the input parasites (green) and the predicted parasites (white $\rightarrow$ 
-            green).}
-        \label{fig:ChordataParasites}
-      \end{figure}
-
-      We mapped the few parasitic species in a rough taxonomy (see Figure \ref{fig:ChordataParasites}): \\
-      Known parasitic birds belong to the order Sauria. Here we know from Rothschild here that are 
-        breeding parasites, like the cuckoo and clepto-parasites as the skuas \cite{Rothschild1957}. We
-        got 6 input parasites from GloBI and there are no predictions: A woodpecker - 
-        \textit{Sphyrapicus varius} and a duck - \textit{Aix sponsa}, a cow bird - \textit{Molothrus ate} 
-        known as broodparasite and some others. \\
-      An example of the amplification of mistakes here are the carp. There is a paper from which GloBI 
-        concludes: Grass carp (\textit{Ctenopharyngodon idella)} has Pathogen common carp 
-        (\textit{Cyprinus carpio})\footnote{
-          \hyperlink{https://www.globalbioticinteractions.org/?interactionType=hasParasite&targetTaxon=Cyprinus\%20carpio}
-          {https://www.globalbioticinteractions.org/?interactionType=hasParasite\&targetTaxon=Cyprinus\%20carpio}
-        }. Since there is hardly any information about free-living, it follows that all siblings are 
-        also predicted to be parasitic. \\
-        % Other birds: Columba livia, Nestor meridionalis, Sphyrapicus varius \\
-        % Snake: Storeria dekayi (probably caused by wrong input data.)
-      % \begin{itemize}
-      %   \item Order Acanthomorphata(3):, one slime fish (family Blenniidae) and two others without family
-      %   \item Order Anura (1): a toad (Family Bufonidae) - there exists some parasitic species in here, 
-      %     they eat fin or pieces of larger fish.
-      %   \item Order Siluriformes (1): a catfish (Family Loricariidae) - there exists some parasitic 
-      %     species in here.
-      % \end{itemize}
-
-      The Apicomplexa are a parasitic phylum. We found only one input organism: Stemonitis fusca as a 
-        free-living species. In GloBI it is listed as being parasitized by Nectria candicans and Nectriopsis 
-        sporangiicola\footnote{
+      multifurcation). This leads to a lower variance of errors, which is reflected in the results. 
+      There are 18 parasites as input data and only 8 more are predicted. The Chordata mostly consist 
+      of free-living species, so this seems believable. We started with 99.83\%  species and predict 
+      99.97\% species as free-living (including already known nodes). \\
+    For a detailed view we have created and described a tree with all known and predicted parasites 
+      (see appendix \ref{sec:parasites in chordata}).
+
+    The Apicomplexa are a parasitic phylum. We found only one input organism: \textit{Stemonitis fusca} 
+      as a free-living species. In GloBI it is listed as being parasitized by Nectria candicans and 
+      Nectriopsis sporangiicola\footnote{
         \hyperlink{https://www.globalbioticinteractions.org/?interactionType=parasiteOf&targetTaxon=Stemonitis\%20fusca}
         {https://www.globalbioticinteractions.org/?interactionType=parasiteOf\&targetTaxon=Stemonitis\%20fusca}
-        }. The algorithm has not predicted new free-livings. \\
+      }. The algorithm has not predicted new free-livings.
 
@@
     For the Platyhelminthes we have more state information for the leaf nodes compared to the other 
-        considered subtrees, see table \ref{table:percentage loss information subtrees}. We start with 
-        0.1\% free-livings and predicted 0.77\% as free-living species. \\
+      considered subtrees. We start with 0.1\% free-livings and predicted 0.77\% as free-living 
+      species.
 
     With the Nematoda it looks more complicated. Large parts of Nematoda are free-living, but we 
-        found only 5.32\% of them. Blaxter et al. estimates the order of 25,000 parasites in the 
-        Nematoda \cite{Blaxter2015} and speaks of at least seven independently arosen parasites 
-        \cite{Blaxter1998}. In a recent article Blaxter identifies 18 origins \cite{Blaxter2015} in 
-        Nematoda. \\
-      The problem at this point, however, is: Hallan speaks of the fact that only 23,000 species 
-        are described by the Nematoda but it is assumed that one million or more species are in this 
-        phylum.\footnote{J. Hallan, unpublished; 
-          \hyperlink{https://insects.tamu.edu/research/collection/hallan/}
-          {https://insects.tamu.edu/research/collection/hallan/}
-        }. \todo{Link ist nicht erreichbar!} The parasites have been much more studied and thus we start 
-        with only 0.63\% (table \ref{table:results of some selected taxa}) free-living species. Against such 
-        a shifted data situation, the algorithm is almost powerless to make correct predictions. And yet 
-        the percentage has increased to 5.34\%. \\
-
-      % \anmerkungstext{Das sind schonmal vier große Kontraste, wenn dann noch Zeit bleibt, die 
-      %   schwirigen... Arthropoden, Fungi, Pflanzen... (Emanuel)} \\
-
-      Origins: \\
-      We go back to the same phyla as in the previous section: Chordata, Nematoda, 
-        Platyhelminthes and Apicomplexa. \\
-      Chordata are full of free-living species and so we see only a few origins of parasitism. The root
-      and mostly all species are predicted as free-living. \\
-      In Apicomplexa and the Platyhelminthes also look credible. Our algorithm gives us only one loss of
-        parasitism in Apicomplexa and five in the Platyhelminthes. They are both from the root over
-        mostly all species predicted as parasites. \\
-      Nematoda is again \colorbox{red}{full of problems}. The root node is predicted as a parasite and so we have more 
-        losses of parasitism for the less information of free-living species in this phylum. The rest 
-        is parasitic \\
-      As we have already mentioned Blaxter et al. found at least seven origins of parasitism 
-        \cite{Blaxter1998}. If we assume that the root node of Nematoda is free-living, then some 
-        losses would have to turn around and become Origins. So it could be that we end up with a similar 
-        size as Blaxter.
-
-  \todo{Aus den models kann man auch schließen: highly variable throughout our tree}
-
-  \todo{noch irgendwo einfügen:} \\
-  The number of nodes in the tree corresponding to a taxonomic rank is tabulated. \\
-  For the classical taxonomic ranks phylum, class, order, family, genus xyz is found (appendix 5.2).
-  % A closer look is taken at some of the features of the synthesis tree on the one hand the 
-  % distribution of the taxa and on the other the distribution of the nodes on the taxa. Since this 
-  % is \colorbox{red}{not directly relevant} for this study, this section has been moved to the appendix 
-  % \ref{sec:otl analysis}.
-
-  This chapter deals with the question of how trustworthy our result of the ancestral state 
-    reconstruction of the Eukaryota tree is. And further on how well our simulation can simulate the 
-    real problem and thus make statements about the predictive power of the applied Sankoff algorithm.
-
-  We have pursued this question in various investigations and yet, of course, further possibilities 
-    for improvement remain. Despite these possibilities for improvement, our reconstruction gives a 
-    first good assessment of the whole tree.
-
-  \todo{Why is the study important?} \\
-  \todo{How does this study relate to previous studies?}
-
-  We evaluated our ancestral state reconstruction and the relational state prediction using three 
-    methods: a simulation, a selective analysis from a biological perspective and a leave-100-out 
-    cross-validation.
-
-  Each theme has its own limitations. \\
-  There are various expansion options and points of criticism for the simulation, which in 
-    particular revolve around the question of how well we can simulate our real data. We dedicate 
-    this question to the subsection \ref{sec:discussion - simulation}. \\
-  Above all, the 'biological view' gives a first impression of the credibility of the results. But 
-    he can not make any statistical statements. Here the interested researcher may have to analyze 
-    the subtrees of relevant to him for himself. \\
-   Of course, cross-validation can be expanded. With more computing power, a leave-1-out cross 
-    validation could also be performed. However, our result on this point yields a strong result 
-    with 98.17\% correct prediction that this does not seem necessary. \\
-  One last limitation also exists in the data situation itself. We have pointed out in various 
-    sections that we have a strong multifurcation and only a few data about leaf node states. In 
-    figure \ref{fig:influence of unknown data} you can see how the predictive power can improve if 
-    we have more data available. We discuss this point in section 
-    \ref{sec:discussion - data situation}.
-
-  % Wieviele Origins haben wir gefunden, was bedeutet diese Zahl? \\
-
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  \section{Data situation} \label{sec:discussion - data situation}
-    The used eukaryotic synthesis tree from OTL \cite{Hinchliff2015} has 241,974 internal nodes and 
-      293,463 leaf nodes. In addition, we could specify 25,962 parasitic and 34,860 free-living 
-      species from GloBI \cite{Poelen2014}. \\
-    This gives us a high number of missing internal nodes (high multifurcation) and a low number of 
-      node states of the leaf nodes. In table \ref{table:percentage loss information subtrees} we have 
-      written down this percentage including some subtrees. \\
-
-    The investigation of the taxonomy revealed that the OTL tree has three kingdoms: Chloroplastida, 
-      Metazoa, Fungi, 53 phyla, 195 classes and 924 orders. \\
-    Since the analysis of the tree is not part of this work, it should be mentioned here that, 
-      according to recent findings, this is not complete and we lack some taxa in every rank. For 
-      example, Cavalier-Smith says that one distinguishes between seven and nine kingdoms 
-      \cite{CavalierSmith1981}. \\
-    In \colorbox{red}{section/page} \pageref{subsec:listPhyla} of the appendix is a list of all phyla. \\
-
-    Also, the global database is not infallible. We found out (section \colorbox{red}{x}) that there is some 
-      misinformation. \\
-    We are able to report some of these directly to Globi.
-
-    We found also 57,352 (not distinct!) source species and 809,993 (not distinct!) target species 
-      without OTT indentifyers. Since we currently use only OTT indentifyers, we could not use this information. \\
-    At this point there is thus the possibility to use more of the existing data, if one performs a 
-      matching with the other indentifyers.
-
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  \section{Simulation} \label{sec:discussion - simulation}
-
-\todo{einbauen....}
-  As mentioned above, in an ancestral state reconstruction, transitions are minimized, with 
-  transition probabilities playing a role. \\
-\colorbox{red}{This subsection deals with} these transition probabilities from free-living (hereinafter / as a 
-  formula FL) to parasitic (hereinafter P) and vice versa: $\mathcal{P}(FL \rightarrow P)$, 
-  $\mathcal{P}(P \rightarrow FL)$. \\
-Different parasite types have different transition probabilities. It is very difficult to make a 
-  statement about these probabilities. It is generally assumed in this work that there are 40\% 
-  parasites and 60\% free-livings which is based on the estimates by Windsor \cite{Windsor1998} 
-  and $\mathcal{P}(FL \rightarrow P) = \mathcal{P}(P \rightarrow FL)$, as a result of the 
-  diversity of parasites and the lack of general determinations for this. These parameters are 
-  debated in subsection \ref{sec:discussion - transition probabilities} of the discussion. \\
-
-  However, the used castor package \cite{Louca2017} offers the possibility to enter different 
-  transition probabilities.
-
-  Wieviele Übergänge gab es dabei? Hast du die gleich (ähnlich groß) gehalten?
-  Der Anteil von Parasiten und Freilebenden ist ja nicht gleich der Transition probability. Das sind zwei verschiedene Dinge...auch wenn die Transition probability den Anteil ergibt. 
-  neben dem Anteil der P/FL ist auch die Anzalhl der Übergänge zu berücksichtigen!
-  50/50 kann man in einem Baum mit 1000 nodes mit einem einzigen Übergan erreichen, der die eine Häfte des Baumes ändert.
-  50/50 kann man aber genauso gut mit einem Übergan auf JEDER edge erreichen. Dann würde sich immer ein P mit einem FL knoten abwechselnn....
-
-... für die Diskussion!
-
-\todo{-----}
-
-    The aim of the simulation is to test the influence of various unknown or unsafe parameters in 
-      order to test the credibility of the prediction. \\
-    Some of these influences could not be tested: Firstly, the distribution of parasites and 
-      free-livings in the tree produces various parameters that we could not test all (see subsection 
-      \ref{sec:discussion - transition probabilities}) and, secondly, we discuss the simulation of a 
-      phylogenetic tree on which the evaluation based on certain parts (see subsection 
-      \ref{sec:discussion - simulate phylogeny}).
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{Transition probabilities} \label{sec:discussion - transition probabilities}
-      We assume that different parasite types have different transition probabilities. Establishing a 
-        common distribution across the eukaryotic tree is therefore difficult. \\
-      Based on the estimates of Windsor \cite{Windsor1998}, we have assumed a distribution of 40\% 
-        parasites to 60\% free livings in this work. As a result of the diversity of parasites and the 
-        lack of generalizations, we have generally stated that 
-        $\mathcal{P}(FL \rightarrow P) = \mathcal{P}(P \rightarrow FL)$. But it is also reasonable to 
-        assume that in general $\mathcal{P}(FL \rightarrow P) > \mathcal{P}(P \rightarrow FL)$, because 
-        a reverse mutation is usually less likely. However, one would have to determine how much this 
-        difference is and thus discuss another parameter. \\
-
-      In the simulation, we tested different beta distributions with different thresholds and found that 
-        this combination has a considerable influence on the predictive power of the algorithms. \\
-      At this point it would be possible to test other distributions with equal threshold values or 
-        different threshold values with equal distributions. \\
-      However, if you choose a strong free-living distribution and balance it with the threshold to 
-        achieve a 40:60 parasite free-living distribution, for example, this could be very 
-        computationally expensive. \\
-
-      With these further simulations you could find out if the issue of distributions plays a big role. 
-        Conversely, one could estimate possible distributions based on the data location in the tree. 
-        However, this is likely to be very difficult given the poor data. For this reason, we have 
-        decided in this work to accept very general values and not to speculate much. \\
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{Simulation of a phylogeny} \label{sec:discussion - simulate phylogeny}
-      In our simulation, we start with the simulation of a phylogeny and then depict our data situation. \\
-      For this first step we use the \textit{randomized()} function of the phylo package from biopython
-        \cite{Cock2009}. The question is how close is such a randomized tree to a phylogeny. \\
-
-      The problems that can arise are that different species develop at different rates. This means that 
-        there could be sections in the tree with many branches (for example, subtrees of unicellular 
-        species), ie with high depths and opposite sections (of very complex species, for example). It 
-        can thus be assumed that the tree is not balanced. \\
-      For more precise statements, one would have to take deeper undercurrents, which was not possible 
-        in the context of this work.
-
-      \todotext{It should be noted that we have optimized the distributions to the proportions and thus the number of state changes will be relatively high.
-With a smaller number of state changes, the predictive power of both algorithms would be even better.}
-      % transition probability
+      found only 5.32\% of them. Blaxter and Koutsovoulos estimate the order of 25,000 parasites in 
+      the Nematoda and and speak of at 18 independently arosen parasites in Nematoda 
+      \cite{Blaxter2015}. \\
+    % The problem at this point, however, is: Hallan speaks of the fact that only 23,000 species are 
+    %   described by the Nematoda but it is assumed that one million or more species are in this 
+    %   phylum.\footnote{J. Hallan, unpublished; 
+    %     \hyperlink{https://insects.tamu.edu/research/collection/hallan/}
+    %     {https://insects.tamu.edu/research/collection/hallan/}
+    %   }. \todo{Link ist nicht erreichbar!} 
+    We assume that the parasites have been much more studied and thus we start with only 0.63\% 
+      free-living species. Against such a shifted data situation, the algorithm is almost powerless to 
+      make correct predictions. And yet the percentage has increased to 5.34\%. \\
+    The root node of the Nematoda is predicted as a parasite and so we got 11 losses of parasitism 
+      and only 2 origins in this phylum. If we assume that the root node of Nematoda is free-living, 
+      then some losses would have to turn around and become Origins. So it could be that we end up 
+      with a similar size as Blaxter and Koutsovoulos \cite{Blaxter2015}.
 
@@
     From the simulation, we can conclude that we predict correctly about 60\% of the nodes in the 
-      present data situation (see section \ref{sec:results - simulation}).
-    The leave-100-out cross-validation even showed that we predict the omitted nodes to be 98.17\%  
-      percent correct (see section \ref{sec:results - cross-validation}). \\
+      present data situation. The leave-100-out cross-validation even showed that we predict the 
+      omitted nodes to be 98.17\% percent correct. \\
     This allows for the assumption that the data is grouped and not uniformly distributed and thus 
       smaller subtrees are present in which data are to be found in the simulation with smaller 
-      multifurcation and smaller value for unknown nodes. This is also confirmed by our biological 
-      analysis of the Chordata subtree (see subsection \ref{subsec:results - statistics on predicted states}). \\
+      multifurcation and smaller value for unknown nodes. This is also confirmed by our statistical 
+      and biological analysis of the considered subtrees: Chordata, Nematoda, Platyhelminthes and 
+      Apicomplexa. \\
     However, this means that the ancestral states' data in the direction of root node are probably 
-      particularly unbelievable. Which makes the localization of Origins direction root node 
-      difficult. The question remains, how much this affects the estimation of the number of origins. 
-      Our comparison with the paper from Weinstein and Kuris \cite{Weinstein2016} (see subsection 
-      \ref{subsec:results - statistics on predicted states}), however, leaves us with optimism.
+      particularly unbelievable. This makes the localization of origins in the direction of the root 
+      node difficult. The question remains, how much this affects the estimation of the number of 
+      origins. Our comparison with the paper from Weinstein and Kuris \cite{Weinstein2016} an with
+      Blaxter and Koutsovoulos \cite{Blaxter2015} showed similar numbers of origins in some subtrees, 
+      which leaves us with optimism.
 
@@
 
+\newpage
+
   %---------------------------------------------------------------------------------------------------
@@
     %---------------------------------------------------------------------------------------------------
-    \subsubsection{Distribution of Taxa}
-    - In the tree we can distinguish 28 different Taxa with the OTL taxonomic tree. \\
-    - The most of them are hardly represented. The major taxonomic groups are: ... \\
-    - Here \colorbox{red}{you} can see some characteristics of the Multifurcation of the tree. \\
+    \subsection{Distribution of Taxa}
+    In the tree we can distinguish 28 different Taxa with the OTL taxonomic tree.
     \begin{figure}[h!]
@@
     \end{figure}
-    In a phylogeny, the taxonomic division of the tree is far too coarse, meaning that there should 
-      be more subtaxa or 'unranked' nodes. But the closer we get to the root, the more the pure
-      taxonomic tree is reflected. If the tree are binary, the taxa would have to double. But the 
-      multipliers for some are much bigger and for others much smaller, which \colorbox{red}{you} can see in in figure 
-      \ref{fig:taxaTable2}. \\
-      ... (see table \ref{table:...})
 
@@
   %---------------------------------------------------------------------------------------------------
-  \subsubsection{Distribution of data in the taxa}
+  \subsection{Distribution of data in the taxa}
     Mithilfe des taxonomischen Baums von OTL haben wir die Knoten ihren Kingdoms, Phyla und Classes 
@@
 
-    \begin{table}[h]
+    \begin{table}[h!]
       \begin{center}
@@
           & & Cycliophora & 11 & 5 \\ 
-          % 1465207-(1170539+106650+80022+27141+24564+14878+11737+10654+8631+3093+1793+1654+1596+1055+633+360+196+11) = 0          \hline
+          % 1465207-(1170539+106650+80022+27141+24564+14878+11737+10654+8631+3093+1793+1654+1596+1055+633+360+196+11) = 0
+          \hline
           Fungi & 254 871 & Ascomycota & 157 045 & 19 \\ 
@@
 
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Parasites in Chordata} \label{sec:parasites in chordata}
+
+    \begin{figure}
+      \centering
+      \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.85\textwidth]{Figures/ChordataParasites.png}
+      \caption{Parasites of Phylum: Chordata. \\
+        All parasite data of the chordata are mapped into a rough taxonomy (phylum, class, order, 
+          family) in order to understand their distribution and affiliation. \\
+        The internal nodes are the wanted taxa from OTL (with the addition of \# input parasites to 
+          $\rightarrow$ \# predicted parasites). \\
+        The leaf nodes are the input parasites (green) and the predicted parasites (white $\rightarrow$ 
+          green).}
+      \label{fig:ChordataParasites}
+    \end{figure}
+
+    We mapped the few parasitic species in a rough taxonomy (see Figure \ref{fig:ChordataParasites}): \\
+    Known parasitic birds belong to the order Sauria. Here we know from Rothschild here that are 
+      breeding parasites, like the cuckoo and clepto-parasites as the skuas \cite{Rothschild1957}. We
+      got 6 input parasites from GloBI and there are no predictions: A woodpecker - 
+      \textit{Sphyrapicus varius} and a duck - \textit{Aix sponsa}, a cow bird - \textit{Molothrus ate} 
+      known as broodparasite and some others. \\
+    An example of the amplification of mistakes here are the carp. There is a paper from which GloBI 
+      concludes: Grass carp (\textit{Ctenopharyngodon idella)} has Pathogen common carp 
+      (\textit{Cyprinus carpio})\footnote{
+        \hyperlink{https://www.globalbioticinteractions.org/?interactionType=hasParasite&targetTaxon=Cyprinus\%20carpio}
+        {https://www.globalbioticinteractions.org/?interactionType=hasParasite\&targetTaxon=Cyprinus\%20carpio}
+      }. Since there is hardly any information about free-living, it follows that all siblings are 
+      also predicted to be parasitic.
+
 \end{document}

### 2018-04-01 Paper - Latex/Paper - Skizze - v4.tex
Thesis - Appendix

@@
      	\vspace{3cm}
-      \textbf{Supervisor:} \\
+      \textbf{Supervisors:} \\
       Prof. Dr. Bernhard Y. Renard \\
@@
     predefined parameters (generalized parsimony) or on strong and often controversial assumptions, 
-    like irreversibility of transitions for dollo parsimony. This problem is unimportant to the 
+    like irreversibility of transitions for Dollo parsimony. This problem is unimportant to the 
     present task because in the analysis of the entire Eukaryota tree only generalized models are 
@@
       {ontobee.org/ontology/RO?iri=http://purl.obolibrary.org/obo/RO\_000244}; Last checked: 22.03.2018.
-    }. This definition includes: ecto- and endoparasites, parasitoids, kleptoparasites and pathogenes. \\
+    }. This definition includes: ecto- and endoparasites, parasitoids, kleptoparasites and pathogens. \\
 
@@
     not have any state information for 97.34\% nodes. \\
-  In addition, we tested different models for these two paramters and found out that multifurcation 
+  In addition, we tested different models for these two parameters and found out that multifurcation 
     can best be modeled with the taxa 'order' multiplied by the mean height of the knots. Also, the 
@@
     \cite{Louca2017}, which performed best, for the actual reconstruction on the real data. \\
-  We evaluated these on the one hand by analysing some statisitcs (subsection 
+  We evaluated these on the one hand by analysing some statistics (subsection 
     \ref{subsec:results - statistics on predicted states}) and on the other hand by performing a 
@@
             \hline \hline
-            multifurc $\sim$ taxa & 8273333 & \cellcolor{green!15}7937828 & \cellcolor{green!20}7842157 & \cellcolor{green!30}7644249 \\
-            multifurc $\sim$ taxa & 8257680 & \cellcolor{green!15}7922207 & \cellcolor{green!20}7826490 & \cellcolor{green!35}7574154 \\
-            \hline
-            multifurc $\sim$ taxa + depth & 8273318 & \cellcolor{green!15}7934322 & \cellcolor{green!20}7839364 & \cellcolor{green!35}7539999 \\
-            multifurc $\sim$ taxa + max.height & \cellcolor{green!15}7993515 & \cellcolor{green!25}7749121 & \cellcolor{green!30}7661817 & \cellcolor{green!40}7416211 \\
-            multifurc $\sim$ taxa + min.height & 8251211 & \cellcolor{green!20}7875521  & \cellcolor{green!25}7778327 & \cellcolor{green!35}7516883 \\
-            multifurc $\sim$ taxa + mean.height & \cellcolor{green!20}7825417 & \cellcolor{green!30}7644249 & \cellcolor{green!35}7572474 & \cellcolor{green!45}7340741 \\
-            \hline
-            multifurc $\sim$ taxa * depth & 8235932 & \cellcolor{green!20}7836755 & \cellcolor{green!25}7757688 & \cellcolor{green!45}7383808 \\
-            multifurc $\sim$ taxa * max.height & \cellcolor{green!15}7963438 & \cellcolor{green!30}7693555 & \cellcolor{green!30}7614820 & \cellcolor{green!45}7335338 \\
-            multifurc $\sim$ taxa * min.height & 8214030 & \cellcolor{green!20}7808940 & \cellcolor{green!30}7690618 & \cellcolor{green!45}7336627\\
-            multifurc $\sim$ taxa * mean.height & \cellcolor{green!25}7768360 & \cellcolor{green!35}7536296 & \cellcolor{green!50}7484953 & \cellcolor{green!50}7206369 \\
+            multifurcation $\sim$ taxa & 8273333 & \cellcolor{green!15}7937828 & \cellcolor{green!20}7842157 & \cellcolor{green!30}7644249 \\
+            multifurcation $\sim$ taxa & 8257680 & \cellcolor{green!15}7922207 & \cellcolor{green!20}7826490 & \cellcolor{green!35}7574154 \\
+            \hline
+            multifurcation $\sim$ taxa + depth & 8273318 & \cellcolor{green!15}7934322 & \cellcolor{green!20}7839364 & \cellcolor{green!35}7539999 \\
+            multifurcation $\sim$ taxa + max.height & \cellcolor{green!15}7993515 & \cellcolor{green!25}7749121 & \cellcolor{green!30}7661817 & \cellcolor{green!40}7416211 \\
+            multifurcation $\sim$ taxa + min.height & 8251211 & \cellcolor{green!20}7875521  & \cellcolor{green!25}7778327 & \cellcolor{green!35}7516883 \\
+            multifurcation $\sim$ taxa + mean.height & \cellcolor{green!20}7825417 & \cellcolor{green!30}7644249 & \cellcolor{green!35}7572474 & \cellcolor{green!45}7340741 \\
+            \hline
+            multifurcation $\sim$ taxa * depth & 8235932 & \cellcolor{green!20}7836755 & \cellcolor{green!25}7757688 & \cellcolor{green!45}7383808 \\
+            multifurcation $\sim$ taxa * max.height & \cellcolor{green!15}7963438 & \cellcolor{green!30}7693555 & \cellcolor{green!30}7614820 & \cellcolor{green!45}7335338 \\
+            multifurcation $\sim$ taxa * min.height & 8214030 & \cellcolor{green!20}7808940 & \cellcolor{green!30}7690618 & \cellcolor{green!45}7336627\\
+            multifurcation $\sim$ taxa * mean.height & \cellcolor{green!25}7768360 & \cellcolor{green!35}7536296 & \cellcolor{green!50}7484953 & \cellcolor{green!50}7206369 \\
             \hline
@@
         family) are computationally too expensive to calculate. \\
-      The model \textit{multifurc $\sim$ order * mean.height} turns out to be the best of our models, 
-        whereby it is possible that e.g. \textit{multifurc $\sim$ family * mean.height} is better. \\
+      The model \textit{multifurcation $\sim$ order * mean.height} turns out to be the best of our models, 
+        whereby it is possible that e.g. \textit{multifurcation $\sim$ family * mean.height} is better. \\
 
@@
     \subsection{Comparison of different models for missing state information}
-      Next to the problem of the multifurcation of the tree is the little interaction data thet we have 
+      Next to the problem of the multifurcation of the tree is the little interaction data that we have 
         for the species. For the ancestral state reconstruction, we need information about the states 
@@
             \hline \hline
-            multifurc $\sim$ taxa & \cellcolor{green!15}545799 & \cellcolor{green!35}500004 & \cellcolor{green!45}485121 & \cellcolor{green!45}484681 \\
-            \hline
-            multifurc $\sim$ taxa + depth & \cellcolor{green!15}544862 & \cellcolor{green!40}493808 & \cellcolor{green!45}481869 & \cellcolor{green!50}478851 \\
-            \hline
-            multifurc $\sim$ taxa * depth & \cellcolor{green!15}544179 & \cellcolor{green!45}489845 & \cellcolor{green!45}481494 & \cellcolor{green!50}478188 \\
+            multifurcation $\sim$ taxa & \cellcolor{green!15}545799 & \cellcolor{green!35}500004 & \cellcolor{green!45}485121 & \cellcolor{green!45}484681 \\
+            \hline
+            multifurcation $\sim$ taxa + depth & \cellcolor{green!15}544862 & \cellcolor{green!40}493808 & \cellcolor{green!45}481869 & \cellcolor{green!50}478851 \\
+            \hline
+            multifurcation $\sim$ taxa * depth & \cellcolor{green!15}544179 & \cellcolor{green!45}489845 & \cellcolor{green!45}481494 & \cellcolor{green!50}478188 \\
             \hline
@@
 
-      Similar to the Eukaryota it is with the Metazoa subtree, which accounts for most of the Eukayota 
+      Similar to the Eukaryota it is with the Metazoa subtree, which accounts for most of the Eukaryota 
         (179,944 internal and 1,491,012 leaf nodes). However, here the root node is no longer calculated 
@@
         \begin{center}
-          \hspace*{-0.5cm}\begin{tabular}{|>{\scriptsize}c|>{\scriptsize}l|>{\scriptsize}r|>{\scriptsize}r||>{\scriptsize}r|>{\scriptsize}r||>{\scriptsize}r|>{\scriptsize}r|>{\scriptsize}r||>{\scriptsize}r|>{\scriptsize}r|>{\scriptsize}r| }
+          \hspace*{-0.5cm}\begin{tabular}
+              {|>{\scriptsize}c|>{\scriptsize}l|>{\scriptsize}r|>{\scriptsize}r||>{\scriptsize}r|>{\scriptsize}r||
+                >{\scriptsize}r|>{\scriptsize}r|>{\scriptsize}r||>{\scriptsize}r|>{\scriptsize}r|>{\scriptsize}r| }
             \hline
@@
       these parts of the tree are very well resolved and the remainder consists only of the rough 
-      taxonomy. \\
-    \todotext{
-    For a review of this underlying taxonomy, we have compiled a list of all taxa and drawn them in 
-      relation to their distribution (see appendix section \ref{sec:otl analysis}).
-    The number of nodes in the tree corresponding to a taxonomic rank is tabulated. \\
-    For the classical taxonomic ranks phylum, class, order, family, genus xyz is found (appendix 
-      \ref{sec:otl analysis}). \\
-    A closer look is taken at some of the features of the synthesis tree on the one hand the 
-      distribution of the taxa and on the other the distribution of the nodes on the taxa. Since 
-      this is \colorbox{red}{not directly relevant} for this study, this section has been moved to 
-      the appendix \ref{sec:otl analysis}.}
+      taxonomy. For a review of this underlying taxonomy, we have compiled a list of all taxa and 
+      plottet them in relation to their distribution (see appendix section \ref{sec:otl analysis}). 
+      There the number of nodes in the tree corresponding to a taxonomic rank is tabulated.
 
@@
 
-\newpage
-
   %---------------------------------------------------------------------------------------------------
@@
     \subsection{Distribution of Taxa}
-    In the tree we can distinguish 28 different Taxa with the OTL taxonomic tree.
+      In the tree we can distinguish 28 different Taxa in the OTL taxonomic tree. We have all Taxa 
+        sorted by rank into a table and counted their occurrences as internal nodes and leaf nodes
+        (see table \ref{table:taxa}) and plotted them as a diagram (see figure \ref{fig:taxa}).
     \begin{figure}[h!]
       \centering
-      \includegraphics[width=0.9\textwidth]{Figures/TaxaTable2.JPG}
+      \includegraphics[width=\textwidth]{Figures/TaxaTable2.JPG}
       \caption{Distribution of Nodes in Rank-Cathegories}
-      \label{fig:taxaTable2}
+      \label{fig:taxa}
     \end{figure}
@@
         % \begin{tabular}{ |>{\rowmac}l|>{\rowmac}r|<{\clearrow} }
-        \begin{tabular}{ |l|r||r|r|r| }
-          \hline
-          \bfseries Taxa & \bfseries Number of Nodes & \bfseries Internal Nodes & \bfseries Leaf Nodes & \bfseries Terminal Leaf Nodes \\
+        \begin{tabular}{ |l|r||r|r| }
+          \hline
+          \bfseries Taxa & \bfseries Number of Nodes & \bfseries Internal Nodes & \bfseries Leaf Nodes \\
           \hline \hline
-          \setrow{\bfseries}domain & 1 & 1 & &  \\ \hline
-          \setrow{\bfseries}kingdom & 3 & 3 & &  \\
-          subkingdom & 2 & 2 & & \\
-          infrakingdom & 5 & 5 & & \\
-          superphylum & 2 & 2 & & \\ \hline
-          \setrow{\bfseries}phylum & 57 & 54 & 3 & \\
-          subphylum & 22 & 20 & 2 & \\
-          infraphylum & 2 & 2 & & \\
-          superclass & 8 & 8 & & \\ \hline
-          \setrow{\bfseries}class & 209 & 175 & 34 & \\
-          subclass & 120 & 106 & 14 & \\
-          infraclass & 14 & 11 & 3 & \\
-          superorder & 40 & 37 & 3 & \\ \hline
-          \setrow{\bfseries}order & 1014 & 772 & 242 & \\
-          suborder & 285 & 222 & 63 & \\
-          infraorder & 95 & 78 & 17 & \\
-          parvorder & 14 & 12 & 2 & \\
-          superfamily & 829 & 626 & 203 & \\ \hline
-          \setrow{\bfseries}family & 8449 & 6143 & 2306 & \\
-          subfamily & 3090 & 2250 & 840 & \\
-          supertribe & 1 & 0 & 1 & \\
-          tribe & 1764 & 1285 & 479 & \\
-          subtribe & 435 & 359 & 77 & \\ \hline
-          \setrow{\bfseries}genus & 164656 & 105452 & 59204 & \\
-          subgenus & 1266 & 869 & 397 & \\
-          section & 3 & 2 & 1 & \\
-          subsection & 1 & 1 & 0 & \\
-          species group & 365 & 288 & 77 & \\
-          species subgroup & 123 & 100 & 23 & \\ \hline
-          \setrow{\bfseries}species & 2247251 & 7423 & 2239828 & 2228993 \\
-          subspecies & 22437 & 75 & 22362 & 22239 \\
-          variety & 1755 & 7 & 1748 & 1726 \\
-          varietas & 5970 & 19 & 5951 & 5909 \\
-          forma & 1181 & & 1181 & 1181 \\
+          \setrow{\bfseries}domain & 1        & 1 & - \\ \hline
+          \setrow{\bfseries}kingdom & 3       & 3 & - \\
+          subkingdom & 2                      & 2 & - \\
+          infrakingdom & 5                    & 5 & - \\
+          superphylum & 2                     & 2 & - \\ \hline
+          \setrow{\bfseries}phylum & 57       & 57 & - \\
+          subphylum & 22                      & 22 & - \\
+          infraphylum & 2                     & 2 & - \\
+          superclass & 8                      & 8 & - \\ \hline
+          \setrow{\bfseries}class & 209       & 209 & - \\
+          subclass & 120                      & 120 & - \\
+          infraclass & 14                     & 14 & - \\
+          superorder & 40                     & 40 & - \\ \hline
+          \setrow{\bfseries}order & 1013      & 1013 & - \\
+          suborder & 285                      & 285 & - \\
+          infraorder & 95                     & 95 & - \\
+          parvorder & 14                      & 14 & - \\
+          superfamily & 829                   & 829 & - \\ \hline
+          \setrow{\bfseries}family & 8442     & 8442 & - \\
+          subfamily & 3090                    & 3090 & - \\
+          supertribe & 1                      & 1 & - \\
+          tribe & 1764                        & 1764 & - \\
+          subtribe & 435                      & 435 & - \\ \hline
+          \setrow{\bfseries}genus & 164592    & 164592 & - \\
+          subgenus & 1266                     & 1266 & - \\
+          section & 3                         & 3 & - \\
+          subsection & 1                      & 1 & - \\
+          species group & 308                 & 308 & - \\
+          species subgroup & 108              & 108 & - \\ \hline
+          \setrow{\bfseries}species & 2243241 & 18197 & 2225044 \\
+          subspecies & 22378                  & 196 & 22182 \\
+          variety & 1755                      & 29 & 1726 \\
+          varietas & 5935                     & 61 & 5874 \\
+          forma & 1179                        & & 1179 \\
           \hline \hline
-          no rank & 954 & 719 & 235 & 7 \\
-          no rank - terminal & 37452 & & 37452 & 37452 \\
-          (no entry) & 40099 & 40099 & & \\
+          no rank & 951                       & 944 & 7 \\
+          no rank - terminal & 37451          & - & 37451 \\
+          (no entry) & 39816                  & 39816 & - \\
           \hline  
         \end{tabular}
-        \caption{\todo{...}}
-        \label{table:...} 
+        \caption{Distribution of Nodes in Rank-Cathegories}
+        \label{table:taxa} 
       \end{center}  
     \end{table}
-    extended leaf nodes (real leaf nodes)
-
-  %---------------------------------------------------------------------------------------------------
-  \subsection{Distribution of data in the taxa}
-    Mithilfe des taxonomischen Baums von OTL haben wir die Knoten ihren Kingdoms, Phyla und Classes 
-      zugeteilt (see table \ref{table:...}). \\
-
-    \begin{table}[h!]
-      \begin{center}
-        \begin{tabular}{ |l|r|l|r|r| }
-          \hline
-          \bfseries Kingdom (3) & \bfseries Number of Nodes & \bfseries Phylum (25) & \bfseries Number of Nodes & \bfseries max max height \\
-          \hline \hline
-          Metazoa & 1 465 207 & Arthropoda & 1 170 539 & 54 \\
-          & & Chordata & 106 650 & 74 \\
-          & & Mollusca & 80 022 & 22 \\
-          & & Platyhelminthes & 27 141 & 9 \\
-          & & Nematoda & 24 564 & 23 \\
-          & & Cnidaria & 14 878 & 36 \\
-          & & Porifera & 11 737 & 26 \\
-          & & Echinodermata & 10 654 & 14 \\
-          & & Bryozoa & 8 631 & 11 \\
-          & & Rotifera & 3 093 & 7 \\
-          & & Nemertea & 1 793 & 7 \\
-          & & Tardigrada & 1 654 & 7 \\
-          & & Acanthocephala & 1 596 & 6 \\
-          & & Brachiopoda & 1 055 & 9 \\
-          & & Nematomorpha & 633 & 7 \\
-          & & Chaetognatha & 360 & 7 \\
-          & & Hemichordata & 196 & 5 \\ 
-          & & Cycliophora & 11 & 5 \\ 
-          % 1465207-(1170539+106650+80022+27141+24564+14878+11737+10654+8631+3093+1793+1654+1596+1055+633+360+196+11) = 0
-          \hline
-          Fungi & 254 871 & Ascomycota & 157 045 & 19 \\ 
-          & & Basidiomycota & 92 931 & 18 \\
-          & & Microsporidia & 1 949 & 6 \\ 
-          & & Glomeromycota & 1 490 & 6 \\
-          & & Chytridiomycota & 1 456 & 6 \\
-          % 254871-157045-92931-1949-1490-1456 = 0
-          \hline
-          Chloroplastida & 121 239 & Streptophyta & 120 731 & 49 \\
-          & & Chlorophyta & 508 & 6 \\
-          % 121239-120731-508 = 0
-          \hline  
-        \end{tabular}
-        \caption{\todo{...}}
-        \label{table:...} 
-      \end{center}  
-    \end{table}
+
+\newpage
 
@@
   \section{Parasites in Chordata} \label{sec:parasites in chordata}
-
-    \begin{figure}
-      \centering
-      \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.85\textwidth]{Figures/ChordataParasites.png}
-      \caption{Parasites of Phylum: Chordata. \\
-        All parasite data of the chordata are mapped into a rough taxonomy (phylum, class, order, 
-          family) in order to understand their distribution and affiliation. \\
-        The internal nodes are the wanted taxa from OTL (with the addition of \# input parasites to 
-          $\rightarrow$ \# predicted parasites). \\
-        The leaf nodes are the input parasites (green) and the predicted parasites (white $\rightarrow$ 
-          green).}
-      \label{fig:ChordataParasites}
-    \end{figure}
-
     We mapped the few parasitic species in a rough taxonomy (see Figure \ref{fig:ChordataParasites}): \\
@@
 
+    \begin{figure}[h!]
+      \centering
+      \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.85\textwidth]{Figures/ChordataParasites.png}
+      \caption{Parasites of Phylum: Chordata. \\
+        All parasite data of the chordata are mapped into a rough taxonomy (phylum, class, order, 
+          family) in order to understand their distribution and affiliation. \\
+        The internal nodes are the wanted taxa from OTL (with the addition of \# input parasites to 
+          $\rightarrow$ \# predicted parasites). \\
+        The leaf nodes are the input parasites (green) and the predicted parasites (white $\rightarrow$ 
+          green).}
+      \label{fig:ChordataParasites}
+    \end{figure}
+
 \end{document}

### 2018-04-01 code/metadata/analyse_input.R

@@ -33,24 +33,22 @@ all.taxa <- cbind(all.taxa, heights)
 ## [Min. 1st Qu.  Median    Mean 3rd Qu.    Max. ] over all phyla - max height
 # tapply(all.taxa$max.height, all.taxa$phylum, summary)
 
-### all nodes sorted by rank
-# table(all.taxa$rank)[order(table(all.taxa$rank))]
+## all nodes sorted by rank
+table(all.taxa$rank)[order(table(all.taxa$rank))]
 
 print('--------------------------------------------------')
 
 leaf.taxa <-  all.taxa[all.taxa$nr_children==0, ]
+all.inner.taxa <- all.taxa[all.taxa$nr_children>0, ]
 inner.taxa <- all.taxa[all.taxa$nr_children>1, ]
-extendedInner.taxa <- all.taxa[all.taxa$nr_children>0, ]
 
 print('----------------------- leaf.taxa$rank ---------------------------')
 leaf.taxa <- as.data.frame(leaf.taxa)
-# table(leaf.taxa$rank)[order(table(leaf.taxa$rank))]
-print('----------------------- inner.taxa$rank ---------------------------')
-inner.taxa <- as.data.frame(inner.taxa)
-# table(inner.taxa$rank)[order(table(inner.taxa$rank))]
-print('----------------------- extendedInner.taxa$rank ---------------------------')
-extendedInner.taxa <- as.data.frame(extendedInner.taxa)
-# table(extendedLeaf.taxa$rank)[order(table(extendedLeaf.taxa$rank))]
+table(leaf.taxa$rank)[order(table(leaf.taxa$rank))]
+print('----------------------- all.inner.taxa$rank ---------------------------')
+all.inner.taxa <- as.data.frame(all.inner.taxa)
+table(all.inner.taxa$rank)[order(table(all.inner.taxa$rank))]
+
 print('--------------------------------------------------')
 print('--------------------------------------------------')
 print('----------------------- data of subtrees ---------------------------')

### 2018-04-01 Paper - Latex/Paper - Skizze - v4.tex
Thesis - Abstact + Intro

@@
     simulation at 60-80\% overall, while strongly varying between clades. The cross-validation 
-    results in an accuracy of 98.17\% which is explained by the fact that the data are not uniformly 
+    results in an accuracy of 98.17\% which is explained by the fact that the data is not uniformly 
     distributed. We describe this variation across taxa as associated with available state and 
-    topology information. We compare our results with several smaller scale studies, which used 
+    topology information. We compare our results with several smaller scale studies which used 
     manual expert curation and conclude that computationally inferred state changes largely agree in 
@@
   % We performed an analysis of existing algorithms and selected a Sankoff maximum parsimony algorithm 
-  %   using the R package \textit{Castor} \cite{Louca2017}. \\
+  %   using the R package \textit{castor} \cite{Louca2017}. \\
   % Nevertheless, the results are convincing and even though this is a purely computational approach 
@@
   For about 50 years, people have been working on ancestral state reconstruction, the inference of 
-    evolution that leads to the given data. \\
-  One of the first papers was written by Camin and Sokal, who in 1965 were working on algorithms for 
-    discrete-state data \cite{Camin1965}. Different methods have been developed and the question is 
-    which method is the most suitable for the problem at hand: the ancestral state reconstruction 
-    for a huge non-binary tree with two discrete states.
-
-% The first methods were only brute force \cite{Camin1965} 
-%   Next came a set of parsimony algorithms such as: Fitch-parsimony \cite{Fitch1971}, 
-%   Wagner-parsimony \cite{Swofford1987} ... \todo{weitere?}. \\
-%   With more and more data, there is now the possibility to use more information to calculate the 
-%   probabilities of the ancestral states. In addition to the states of the leafs, algorithms could 
-%   also use branch lengths. The likelihood based algorithms came more in interest. \\
-
-  Royer-Carenzi et al. distinguish two major classes of ancestral state reconstruction methods: \\
-  The first is maximum parsimony: explain the current state with the least number of state changes 
-    between the child and its ancestor. \\
-  The other class they present describes modeling the character evolution as a stochastic process 
-    and using the likelihoods to compute the possible ancestral character states. This is generally 
-    done with a continuous time Markov model \cite{RoyerCarenzi2013}. \\
-  \todo{Pasqualin et al. unterscheiden noch eine weitere Methode: stochastic mapping...}
-
-  One of the major disadvantages of parsimony methods is that, unlike likelihood approaches, they 
-    can not take divergence times (branch length) into account. Since the OTL does not include 
-    development times of species, this can not be considered here. \\
-  Another problem pointed out by Royer-Carenzi is that parsimony approaches are either based on 
-    predefined parameters (generalized parsimony) or on strong and often controversial assumptions, 
-    like irreversibility of transitions for Dollo parsimony. This problem is unimportant to the 
-    present task because in the analysis of the entire Eukaryota tree only generalized models are 
-    meaningful. \\
-  % Comparing the methods, we find that parsimony are methods in which you can not include information 
-  %   such as branch length (development time of the species). This is also their main disadvantage 
-  %   compared to the more complex likelihood based models. Since there are no branch lengths or other 
-  %   information available for the present relationship tree, and we can thus not take advantage of 
-  %   the other models. \\
-  The comparison of methods gives us the maximum parsimony method as the simplest and fastest method 
-    that meets all our requirements.
-  % Parsimony-based methods are used in this work, since they are fast and fully sufficient for the 
-  %   presented use case here, following the principle of the simpler model first. \\
+    evolution that leads to the given data. One of the first papers was written by Camin and Sokal, 
+    who were working on algorithms for discrete-state data in 1965 \cite{Camin1965}. Different 
+    methods have been developed and the question is which method is the most suitable for the 
+    problem at hand: the ancestral state reconstruction for a huge non-binary tree with two discrete 
+    states.
+
+  Royer-Carenzi et al. distinguish two major classes of ancestral state reconstruction methods: The
+    first is maximum parsimony: explain the current state with the least number of state changes 
+    between the child and its ancestor. The other class they present describes the modeling of 
+    character evolution as a stochastic process and uses the likelihoods to compute the possible 
+    ancestral character states. This is generally done with a continuous time Markov model 
+    \cite{RoyerCarenzi2013}.
+
+  One of the major disadvantages of parsimony methods is that, in contrast to likelihood approaches, 
+    they can not take divergence times (branch length) into account. Since the OTL does not include 
+    development times of species, this can not be considered here. Another problem pointed out by 
+    Royer-Carenzi is that parsimony approaches are either based on predefined parameters 
+    (generalized parsimony) or on strong and often controversial assumptions, like irreversibility 
+    of transitions (Dollo parsimony). This problem is unimportant to the present task because in the 
+    analysis of the entire Eukaryota tree only generalized models are meaningful. The comparison of 
+    methods gives us the maximum parsimony method as the simplest and fastest method that meets all 
+    our requirements.
 
@@
     Fitch parsimony \cite{Fitch1971} and Sankoff parsimony \cite{Sankoff1975}. Therefore, these are 
-    the methods used in this work. \\
-  % \anmerkungstext{Unter Farris war auch noch der Begriff Wagner trees in gebrauch, als 
-  %   Verallgemeinerung der parsimonious trees von Camin und Sokal. (Lydia)} \\
-  % \todo{Wagner-parsimony \cite{Swofford1987}} \\
-   For Fitch, the algorithm has been extended from binary to non-binary trees. For the Sankoff 
-    algorithm, Louca and Doebeli have presented an implementation for non-binary trees published in 
-    an R package named \textit{castor} \cite{Louca2017}.
+    the methods used in this work. For Fitch, the algorithm has been extended from binary to 
+    non-binary trees. For the Sankoff algorithm, Louca and Doebeli have presented an implementation 
+    for non-binary trees published in an R package named \textit{castor} \cite{Louca2017}.
 
   For an ancestral reconstruction on the phylogeny of Eukaryota, we use Open Tree of Life (OTL) 
-    \cite{Hinchliff2015}. \\
-  Phylogeny describes the evolution of species, while the taxonomy is a classification according to 
-    certain criteria in so-called taxa. \\
-  OTL is a comprehensive, dynamic and digitally available tree of life constructed from published 
-    phylogenetic trees along with a backbone of taxonomic data. Besides this, Hinchliff et al. also 
-    offer an OpenTreeOfLife-Taxonomy (OTT) with the help of which we identify the individual nodes. \\
-  It follows that the biggest 'phylogenetic tree' is this synthesis of phylogenetic trees filled 
-    with a taxonomic trees given by OTL.
+    \cite{Hinchliff2015}. Phylogeny describes the evolution of species, while the taxonomy is a 
+    classification according to certain criteria in so-called taxa. OTL is a comprehensive, dynamic 
+    and digitally available tree of life constructed from published phylogenetic trees along with a 
+    backbone of taxonomic data. Besides this, Hinchliff et al. also offer an OpenTreeOfLife-Taxonomy 
+    (OTT) with the help of which we identify the individual nodes. It follows that the biggest 
+    'phylogenetic tree' is this synthesis of phylogenetic trees filled with a taxonomic trees given 
+    by OTL.
 
@@
     multiple ($n > 2$) children or in other words its degree, number of adjacent nodes, is greater 
-    than 3 \cite{Felsenstein2003}. \\
-  Parsimonious in phylogeny refers to favoring the tree that needs the least evolutionary change to 
-    explain the observed data. Maximum parsimony methods have been developed for phylogenies, which 
-    are usually depicted as binary trees. Therefore, the selected parsimony methods are not directly 
-    applicable, as they were specifically applied to much smaller subtrees, where all splits are 
-    known. \\
-  We will extend and test the existing maximum parsimony algorithms of Fitch \cite{Fitch1971} and 
-    Sankoff \cite{Sankoff1975} for this task and estimate their predictive power.
-
-  The Sankoff method is implemented by Louca et al. for the non-binary case and is available as an R 
-    package called \textit{Castor} \cite{Louca2017}. \\
+    than 3 \cite{Felsenstein2003}. Parsimonious in phylogeny refers to favoring the tree that needs 
+    the least evolutionary change to explain the observed data. Maximum parsimony methods have been 
+    developed for phylogenies, which are usually depicted as binary trees. Therefore, the selected 
+    parsimony methods are not directly applicable, as they were specifically applied to much smaller 
+    subtrees, where all splits are known. We will extend and test the existing maximum parsimony 
+    algorithms of Fitch \cite{Fitch1971} and Sankoff \cite{Sankoff1975} for this task and estimate 
+    their predictive power.
+
   Note, the original Fitch algorithm has the sole purpose of minimizing the number of transitions 
-    and not reconstructing the ancestral nodes. Felsenstein \cite{Felsenstein2003} describes a 
-    simple extension for the reconstruction. In this work, the algorithm extended to reconstruction 
-    is adapted to multifurcated trees, based on the critical reevaluation of this extension by 
-    Cunningham et al. \cite{Cunningham1998}.  
-  % In addition, we have implemented the Fitch 
-  %   method \cite{Fitch1971} \todo{hier vll die andere quelle nutzen nach der wir uns gerichtet haben?}and adapted it for multifurcated trees.
-\\% to make it usable and comparable for our current problem.
-  % This achieves that we can predict ancestral states and unknown states of living species for large 
-  %   non-binary trees.
-
-  To accomplish this task, next to the phylogenetic tree information about the current species' 
-    states is needed. \\
-  Most of the largest interaction databases are offline or outdated. For example: IWDB (Interaction 
+    and not the reconstruction of the ancestral nodes. Felsenstein \cite{Felsenstein2003} describes 
+    a simple extension for the reconstruction. In this work, the algorithm extended to 
+    reconstruction is adapted to multifurcated trees, based on the critical reevaluation of this 
+    extension by Cunningham et al. \cite{Cunningham1998}.
+
+  To accomplish this task, information about the states of the current species is needed in addition 
+    to the phylogenetic tree.  Most of the largest interaction databases (e. g. IWDB (Interaction 
     Web Database) \cite{IWDB2003}, Webs on the Web \cite{WOW2004}, Animal Diversity Web 
-    \cite{Myers2003} and ecoweb \cite{Cohen2010}. \\
-  We use the interaction database Global Biotic Interactions (GloBI) \cite{Poelen2014} because it is 
-    including most of the known databases and is still growing actively \cite{Poelen2014}. \\
-  The data in GloBI are stored as interactions e.g.  species A parasitize species B. From this we 
-    conclude that species A is parasitic and species B free-living. \\
-  From this data, we could specify $\sim$2.3 million leaf nodes 34,860 as free-living and 25,962 
-    as parasitic.
+    \cite{Myers2003} and ecoweb \cite{Cohen2010}) are offline or outdated. We use the interaction 
+    database Global Biotic Interactions (GloBI) \cite{Poelen2014} because it is including most of 
+    the known databases and is still growing actively \cite{Poelen2014}. The data in GloBI is stored 
+    as interactions e.g. species A parasitizes species B. We conclude that species A is parasitic 
+    and species B free-living. From this data, we could specify $\sim$2.3 million leaf nodes 34,860 
+    as free-living and 25,962 as parasitic.
 
   There are many different ways to define parasitism. Since we use GloBI to classify species, we use 
-    their definition of parasitism. Again, in GloBi, Ontobee definitions are used \cite{Xiang2011}. \\
-  The interaction \textit{has parasite} is defined as: "An interaction relationship between two 
+    their definition of parasitism. In GloBi, Ontobee definitions are used \cite{Xiang2011}. The 
+    interaction \textit{has parasite} is defined as: "An interaction relationship between two 
     organisms living together in more or less intimate association in a relationship in which 
@@
   The objectives of this work are the following points: (1) Find a suitable ancestral state 
-    reconstruction method. (2) Accomplish reconstructing on the Eukaryota synthesis tree of OTL. \\
-  The goal of Point 1 is to evaluate the possible methods based on a simulation of our data 
-    situation. \\
+    reconstruction method. (2) Accomplish reconstruction on the Eukaryota synthesis tree of OTL. The 
+    goal of point 1 is to evaluate the possible methods based on a simulation of our data situation. 
     The Sankoff algorithm implemented by Louca et al. is the best in our comparisons. Therefore,
-    point 2 consists of reconstructing the ancestral states and predicting the unknown leaf states 
-    with the aid of this algorithm. And then perform an evaluation of the results. \\
+    point 2 consists of reconstructing the ancestral states, predicting the unknown leaf states with 
+    the aid of this algorithm and perform an evaluation of the results.
 
@@
     %---------------------------------------------------------------------------------------------------
-    \subsubsection{Sankoff}
-      Maximum parsimony algorithm from Sankoff implemented in the R package castor \cite{Louca2017}.
+    %---------------------------------------------------------------------------------------------------
+    \subsection{Sankoff maximum parsimony}
+      Maximum parsimony algorithm from Sankoff implemented in the R package \textit{castor} \cite{Louca2017}.
         From this the function \textit{$hsp\_max\_parsimony()$} is used with default settings including
@@
     First different implementations of the Fitch maximum parsimony are compared and then the best of 
-      them is compared with the implementation of the Sankoff algorithm of the \textit{Castor} package 
+      them is compared with the implementation of the Sankoff algorithm of the \textit{castor} package 
       \cite{Louca2017}.
@@
       \hyperlink{github.com/Irallia/IZW-HU-Parasites}{github.com/Irallia/IZW-HU-Parasites}. \\
-    Most of the code is written in Python, the analyzes and the use of the Castor package in R. Some 
+    Most of the code is written in Python, the analyzes and the use of the \textit{castor} package in R. Some 
       shell scripts are used to execute whole workflows.
@@
 
-    The used castor package \cite{Louca2017} offers the possibility to enter different transition 
+    The used \textit{castor} package \cite{Louca2017} offers the possibility to enter different transition 
       probabilities, so with information about these probabilities, you might be able to improve the 

### 2018-04-01 Paper - Latex/Paper - Skizze - v4.tex
Thesis - Aims, Methods again...

@@
 \chapter{Aims}
-  The aim of this thesis is the application of maximum parsimony algorithms to non-binary trees and 
-    very large data sets to predict unknown leaf node states. \\
+  The primary objective of this thesis is the application of maximum parsimony algorithms to 
+    non-binary trees and very large data sets to predict unknown leaf node states.
+
   We discuss different ancestral state reconstruction methods and test the most appropriate ones on 
@@
 
-  In order to generate a realistic simulation, influencing parameters are investigated. \\
-  Since the transitions are minimized in an ancestral state reconstruction, this is an important 
-    parameter to consider. On the other hand, the completeness of our input data is an influencing 
-    value. Therefore, two major types are distinguished:
+  In order to generate a realistic simulation, influencing parameters are investigated. Since the 
+    transitions are minimized in an ancestral state reconstruction, this is an important parameter 
+    to consider. On the other hand, the completeness of our input data affects our data enormously.
+    Therefore, two major types are distinguished:
   \begin{enumerate}
@@
   In this thesis, a maximum parsimony algorithm is applied to the Eukaryota tree to obtain an 
-    ancestral state reconstruction of free-living versus parasite states. \\
-  This chapter is divided into the following sections: the description of the data sources 
-    (section \ref{sec:methods - data sources}) used and the analysis of these data as a preparation 
-    for the simulation (section \ref{sec:methods - metadata analysis}). A description of the 
-    analyzed methods for the ancestral state reconstruction (section 
-    \ref{sec:methods - ancestral state reconstruction}) and then an explanation of how they fit the 
-    problem at hand (section \ref{sec:methods - simulation}). And at the end, the real data analysis 
-    with the Sankoff method (section \ref{sec:methods - real data analysis}). \\
-  Figure \ref{fig:workflow} briefly outlines these relationships. A more detailed view of the 
-    workflow can be found in the appendix \ref{fig:BigWorkflow}.
+    ancestral state reconstruction of free-living versus parasite states. This chapter is divided 
+    into the following sections: the description of the used data sources and the analysis of these 
+    data as a preparation for the simulation. A description of the analyzed methods for the 
+    ancestral state reconstruction and then an explanation of how they fit the problem at hand. And 
+    at the end, the real data analysis with the Sankoff method. Figure \ref{fig:workflow} briefly 
+    outlines these relationships. A more detailed view of the workflow can be found in the appendix 
+    \ref{fig:BigWorkflow}.
+
   \begin{figure}[h!]
     \centering
-    \includegraphics[width=0.6\textwidth]{Figures/Workflow-overview.png}
+    \includegraphics[width=0.49\textwidth]{Figures/Workflow-overview.png}
     \caption{The Workflow of the resulting procedure with the following steps: \\
@@
       (6) Run the resulting algorithm on the original data.
-      (7) Evaluate and interpret the results. %$\rightarrow$ Origins etc...
+      (7) Evaluate and interpret the results.
     }
@@
 
-    For the subsequent analyzes on the Eukaryote tree the database of Open Tree of Life (OTL) is used 
+    The database of Open Tree of Life (OTL) is used for the subsequent analysis of the Eukaryota tree
       (downloaded on 16.02.2018) \cite{Hinchliff2015}. This database gives a synthesis of phylogenetic 
@@
       taxonomies and is synthesised by preferring taxonomies that match with available phylogenetic 
-      data. The team from OTL prefer a maximum number of species \cite{Hinchliff2015}, this results 
-      in the synthesis between taxonomy and phylogeny.
-
-    For the state information the Global Biotic Interactions database (GloBI) is taken 
-      \cite{Poelen2014} (downloaded on 29.01.2018). \\
-    This database consists of entries of the form: species A (source) interacts with B (target). \\
-    A number of interactions have been identified\footnote{\hyperlink{
+      data. The team of OTL prefers a maximum number of species \cite{Hinchliff2015}, this results in 
+      the synthesis between taxonomy and phylogeny.
+
+    For the state information the Global Biotic Interactions database (GloBI) is being used
+      \cite{Poelen2014} (downloaded on 29.01.2018). This database consists of interactions: species A 
+      (source) interacts with B (target). A number of interactions has been 
+      identified\footnote{\hyperlink{
         https://github.com/jhpoelen/eol-globi-data/blob/master/eol-globi-lib/src/main/java/org/eol/globi/domain/InteractType.java
-      }{https://github.com/jhpoelen/eol-globi-data/.../InteractType.java}; Last checked: 22.03.2018.}
-      , including those indicating whether the species source or target has become a parasite or a 
+        }{https://github.com/jhpoelen/eol-globi-data/blob/master/eol-globi-lib/src/main/java/org/eol/globi/ \\ domain/InteractType.java}; Last checked: 22.03.2018.
+      }, including those indicating whether the species source or target has become a parasite or a 
       free-living species from the biological perspective. They are the following:
@@
     \end{itemize}
-    Of these interactions, e.g. species A parasitize species B, the state of the species is 
-      determined, here is species A parasitic and species B free-living. In the case that a parasite 
-      conquers (parasitizes) another parasite yields conflicting states for the second species. 
-      This is solved by preferring parasitic. \\
+
+    Of these interactions (e.g. species A parasitizes species B) the state of the species is 
+      determined (species A is parasitic, species B is free-living). In the case that one parasite 
+      conquers another parasite (parasitizes), conflicting conditions arise for the second species.
+      This is solved by preferring the parasitic state.
+
     For each species known identifiers are stored in GloBI. This includes OTT (the taxonomy of OTL). 
@@
       regression according to their residuals. In order to compare models of different complexity, the 
-      BIC (Bayesian Information Criterion) values are calculated in addition to the residuals. \\
-    There are two different information criteria: AIC (Akaike Information Criteria) and BIC. \\
-    The advantage of the BIC is that the penalty is dependent on the sample size and is therefore 
-      advantageous for large samples. \\
+      BIC (Bayesian Information Criterion) values are calculated in addition to the residuals.
+
+    There are two different information criteria: AIC (Akaike Information Criteria) and BIC. The 
+    advantage of the BIC is that the penalty is dependent on the sample size and is therefore 
+      advantageous for large samples.
+
     For all these calculations, the following R functions are  used: \textit{glm()}, \textit{anova()} 
@@
       distance (number of edges) to the root node. The node height is calculated in three different 
-      ways: min, max and mean height refers to the (mininmal, maximal, mean) distance to a leaf node. \\
-    The influence in the modeling of these parameters is tested, additively as well as 
-      multiplicatively to the models.
+      ways: min, max and mean height refers to the (mininmal, maximal, mean) distance to a leaf node.
+      The influence in the modeling of these parameters is tested both additively and multiplicatively 
+      on the models.
 
@@
         differences to the multifurcated case, the algorithm for the binary case is briefly explained 
-        and referred to the extension.
-
-      Input: A rooted, binary tree, with state information in the leaf nodes. Each node is depicted as 
+        and referred to the extension. \\
+        \begin{wrapfigure}[17]{r}{0.5\textwidth}
+          \centering
+          \includegraphics[width=0.4\textwidth]{Figures/Fitch1.png}
+          \caption{Fitch algorithm for binary trees. \\
+            The unknown leaf node is described with both states. Computed internal nodes (except for the 
+            root node) consist of three sets, where the last set is the final one (bold). \\
+            From the second internal node (seen from the root node) there are several possibilities to 
+            create the second and third set.}
+          \label{fig: binary Fitch}
+        \end{wrapfigure}
+      Input: A rooted binary tree with state information in the leaf nodes. Each node is depicted as 
         a set of states. There are only two states in this thesis, free-living (FL) and parasitic (P).
-        Internal nodes have three sets, which are empty at the beginning, excluding the root node, it 
-        has only one. Leaf nodes have their state as a set (e.g. \{FL\} or \{P\}, unknown leaf nodes the 
-        union of all possible states (\{FL, P\}).
-
-      The algorithm traverses three times through the tree and fills these sets. \\
-      In each step, two sets are considered and their intersection is formed. There are two cases:
+        Internal nodes have three sets that are empty at the beginning, except for the root node, which
+        has only one. Leaf nodes have their state as a set (e.g. \{FL\} or \{P\}, unknown leaf nodes 
+        have the union of all possible states (\{FL, P\}).
+
+      The algorithm traverses three times through the tree and fills these sets. In each step, two sets 
+        are considered and their intersection is formed. There are two cases:
       \begin{enumerate}
@@
       \end{enumerate}
-      First traverse from the leaf nodes to the root: each internal node is formed from its child nodes, 
-        where the only information lies at the beginning. \\
-      Second traverse from the root node to the leafs: each internal node is formed from its parent node 
-        and its sibling node. \\
-      Last traversion (direction does not matter): build the final state for every node. It is formed 
-        from the sets of previous traversals.
+      The first traversion goes from the leaf nodes to the root: each internal node is formed by its 
+        child nodes, where the only information lies at the beginning. The Second traversion goes from 
+        the root node to the leafs: each internal node is formed from its parent node and its sibling 
+        node. Last traversion (direction does not matter): the final state is builded for every node. It 
+        is formed from the sets of previous traversals.
 
       (The original Fitch algorithm is designed to minimize transitions without predicting actual states 
-        of internal nodes, so it is just the first traversal.) \\
-        \begin{wrapfigure}[20]{r}{0.5\textwidth}
-          \centering
-          \includegraphics[width=0.4\textwidth]{Figures/Fitch1.png}
-          \caption{Fitch algorithm for binary trees. \\
-            The unknown leaf node is described with both states. Computed internal nodes (exclusive the 
-            root node) consists of three sets, where the last set is the final one (bold). \\
-            From the second internal node (seen from the root node) there are several possibilities to 
-            create the second and third set.}
-          \label{fig: binary Fitch}
-        \end{wrapfigure}
+        of internal nodes, so it is just the first traversal.)
+
       The extension to the non-binary case is quite obvious, but holds some opportunities. In this case, 
-        more than two children may be present for the first traversal, but the intersection or union may 
-        also be formed over more than two sets. Also in the second traversing, there may be several 
-        sibling nodes. However, there are several possibilities here that are all tested and compared 
-        in the simulation. Some of these options are already available in the binary case:
+        more than two children may be present for the first traversal, but the intersection or union can 
+        also be formed over more than two sets. There may also be several sibling nodes in the second 
+        traversing. However, there are several possibilities here that are all tested and compared in 
+        the simulation. Some of these options are already available in the binary case:
       \begin{itemize}
-        \item The parent node has (except for the root node) two state sets, because he came through 
+        \item The parent node has two state sets (except for the root node), because it came through 
           the up-traversing previously. Are both sets used or only the first traversing?
-        \item If there are several siblings, is the cut or union made first of these, or is everything 
-          made directly including the parent node.
+        \item If there are several siblings, the cut or union could made first of these, or directly 
+          including the parent node.
       \end{itemize}
       The first point already has an effect on the binary case. Figure \ref{fig: binary Fitch} shows 
-        both possibilities of the three sets. \\
-      Cunningham uses only the first state set of the parent node \cite{Cunningham1998}. \\
-      From these two points four different versions of Fitch are formed:
+        both possibilities of the three sets. Cunningham uses only the first state set of the parent 
+        node \cite{Cunningham1998}. From these two points four different versions of Fitch are formed:
       \begin{enumerate}
@@
         \includegraphics[trim = 24mm 0mm 28mm 14mm, clip, width=\textwidth]{Figures/simulation_fitch_evaluation.png}
-        \caption{Test of Fitch Versions. \todo{beschriften!!}}
+        \caption{Test of Fitch Versions. \\
+          Each point corresponds to a simulation of 100 trees with 10000 leaf nodes for each proportion 
+            (30:70 and 40:60) with equally distributed lack of leaf state information (percentage 
+            unknown). The multifurcation probability per node is calculated with: 
+            $\frac{1}{max~height(node)}$.}
         \label{fig:Fitch versions}
@@
       These four versions are tested in the simulation with 100 trees and 10000 leaf nodes and 
-        distributions of 70\% FL to 30\% P and 60\% FL to 40\% P. Figure \ref{fig:Fitch versions} shows 
-        this over all unknown node percentage. \\
-      % At 90\% unknown nodes and 90\% of multifurcation of the internal nodes, version 1 is 89.26\%, 
-      %   version 2 is 89.26\%, version 3 is 89.35\%, and version 4 is 89.31\% correct. Therefore, 
-      %   only version 3 is used for all further simulations.
-      At 95\% unknown nodes and 95\% of multifurcation of the internal nodes, version 1 is 88.37\%, 
-        version 2 is 88.37\%, version 3 is 88.4\%, and version 4 is 88.39\% correct. Therefore, 
-        only version 3 is used for all further simulations.
-
-    % Fitch versions:
-    % | 88.37 % | 88.37 % | 88.4 % |88.39 % |
+        distributions of 70\% FL to 30\% P and 60\% FL to 40\% P. At 95\% unknown nodes and 95\% of 
+        multifurcation of the internal nodes, version 1 is 88.37\%, version 2 is 88.37\%, version 3 is 
+        88.4\%, and version 4 is 88.39\% correct.
+
+      There was a more visible difference in the calculations with no equally distributed multifurcation. 
+        The probability of forgetting each node was chosen $\frac{1}{max~height(node)}$. Figure 
+        \ref{fig:Fitch versions} shows this for different unknown node percentages.
+
+      Therefore, only version 3 is used for all further simulations.
 
@@
     The simulation compares these different ancestral state reconstruction algorithms with each 
-      other. \\
-    First different implementations of the Fitch maximum parsimony are compared and then the best of 
-      them is compared with the implementation of the Sankoff algorithm of the \textit{castor} package 
-      \cite{Louca2017}.
+      other. First, different implementations of the Fitch maximum parsimony are collated and then the 
+      best of them is compared with the implementation of the Sankoff algorithm of the \textit{castor} 
+      package \cite{Louca2017}.
 
@@
           be seen: \\
-        (1) A phylogenetic tree is created randomly. (2) Simulate node states for all nodes. (3) 
+        (1) Create a phylogenetic tree randomly. (2) Simulate node states for all nodes. (3) 
           'Forget' internal states and some leaf node states. (4) 'Lose' phylogeny information. (5) 
@@
     The course of a simulation is shown in Figure \ref{fig:Simulation Workflow}. The individual steps 
-      are explained in the following.
+      are explained hereinafter.
 
@@
         \hyperlink{https://github.com/biopython/biopython/blob/master/Bio/Phylo/BaseTree.py}
-        {https://github.com/biopython/biopython/blob/master/Bio/Phylo/BaseTree.py}
-      }.
-
-    The next step is to simulate states for all nodes. \\
-    Here the influence of the biological parameters as transition probabilities and distributions of
+        {https://github.com/biopython/biopython/blob/master/Bio/Phylo/BaseTree.py};
+        Last checked: 22.03.2018.}.
+
+    The next step is to simulate states for all nodes. Here, the influence of the biological  
       \begin{wrapfigure}[21]{r}{0.55\textwidth}
@@
           Start with a free-living root node (FL: red). \\
-          (1) + (2) Draw random numbers for its children from the free-living distribution (red), the numbers are under the threshold 
-          $\rightarrow$ the nodes are again free-living; go on with the children. \\
-          (3) The number drawn is above the threshold. $\rightarrow$ The node state changes to parasitic (P: blue). \\
-          (4) Now draw random numbers from the parasite distribution (red) until one number lies under the threshold. Then change back.}
+          (1) + (2) Draw random numbers for its children from the free-living distribution (red), the 
+            numbers are under the threshold $\rightarrow$ the nodes are again free-living; go on with 
+            the children. \\
+          (3) The number drawn is above the threshold. $\rightarrow$ The node state changes to 
+            parasitic (P: blue). \\
+          (4) Now draw random numbers from the parasite distribution (red) until one number lies under 
+            the threshold. Then change back.}
         \label{fig:set node states}
       \end{wrapfigure} 
-      states is included. \\
+      parameters as transition probabilities and distributions of states is included.
+
     Since there is no statement about general transition probabilities, these are all set the same: \\
@@
 
-    For the distributions of states different ratios of parasites (P) to free-livings (FL) are 
-      simulated with the help of beta distributions and a given threshold:
+    To these distributions different ratios of parasites (P) to free-livings (FL) are simulated with 
+      the help of beta distributions and a given threshold:
       \begin{itemize}
@@
       determined to be free-living. Therefore, the beta distribution for free-living is used at the 
-      beginning. Now traverse from the root to the leaf nodes, always pulling out of the current 
-      distribution until the randomly drawn number is above the threshold and the new node changes 
-      state. Figure \ref{fig:set node states} shows a part of this simulating states and the 
+      beginning. A traversion from the root to the leaf nodes sets the states, always pulling out of 
+      the current distribution until the randomly drawn number is above the threshold and the new node 
+      changes state. Figure \ref{fig:set node states} shows a part of these simulating states and the 
       associated distributions.
@@
     The statistics are collected over the entire Eukaryota tree and over some subtrees of different 
-      taxa. There are known states besides predicted states, the predicted root node state specified 
-      and origins and losses are counted by parasitism. \\
+      taxa. There are known states listed besides predicted states, the predicted root node state 
+      specified and origins and losses of parasitism are counted.
+
     Since Sankoff predicts probabilities for states, we have rounded them to be able to count 
-      transitions from free-living (0) to parasitic (1) and vice versa. \\
-    In each case, a maximum of one changing transition from parent node to child node is counted for 
-      the origins (FL $\rightarrow$ P) or losses (P $\rightarrow$ FL).
+      transitions from free-living (0) to parasitic (1) and vice versa. In each case, a maximum of one 
+      changing transition from parent node to child node is counted for the origins (FL $\rightarrow$ 
+      P) or losses (P $\rightarrow$ FL).
 
@@
       \hyperlink{github.com/Irallia/IZW-HU-Parasites}{github.com/Irallia/IZW-HU-Parasites}. \\
-    Most of the code is written in Python, the analyzes and the use of the \textit{castor} package in R. Some 
-      shell scripts are used to execute whole workflows.
+
+    Most of the code is written in Python. The analyzes and the use of the \textit{castor} package 
+      are partly implemented in R. Some shell scripts are used to execute whole workflows.
 
@@
 
-    To do so, we first look at the input data we have: the use of Open Tree of Life for the tree 
+    To do so, we first look at the input data we have: the use of Open Tree of Life (OTL) for the tree 
       gives us the greatest approximation to a phylogeny of the Eukaryota. Since such a large 
@@
         \hyperlink{https://www.globalbioticinteractions.org/?interactionType=parasiteOf&targetTaxon=Stemonitis\%20fusca}
-        {https://www.globalbioticinteractions.org/?interactionType=parasiteOf\&targetTaxon=Stemonitis\%20fusca}
+        {https://www.globalbioticinteractions.org/?interactionType=parasiteOf\&targetTaxon=Stemonitis\%20fusca};
+        Last checked: 22.03.2018.
       }. The algorithm has not predicted new free-livings.
@@
         \hyperlink{https://www.globalbioticinteractions.org/?interactionType=hasParasite&targetTaxon=Cyprinus\%20carpio}
-        {https://www.globalbioticinteractions.org/?interactionType=hasParasite\&targetTaxon=Cyprinus\%20carpio}
+        {https://www.globalbioticinteractions.org/?interactionType=hasParasite\&targetTaxon=Cyprinus\%20carpio};
+        Last checked: 22.03.2018.
       }. Since there is hardly any information about free-living, it follows that all siblings are 

### 2018-04-02 Paper - Latex/Paper - Skizze - v4.tex
Thesis - Results 1. Hälfte again

@@
 \chapter{Results}
-  In the first part of this work, we were able to provide the proof of concept for the Sankoff 
+  In the first part of this study, we were able to provide the proof of concept for the Sankoff 
     algorithm to perform an ancestral state reconstruction of the present Eukaryota tree. We will 
-    therefore discuss in the following how significant the result of this reconstruction is.
-
-    To do so, we first look at the input data we have: the use of Open Tree of Life (OTL) for the tree 
-      gives us the greatest approximation to a phylogeny of the Eukaryota. Since such a large 
-      phylogeny has not been completely dissected, this is only a synthesis of phylogenetic trees 
-      with a taxonomy as a backbone. As a result, the tree is far from binary, we found a 
-      multifurcation of 89.45 \%. However, this is highly variable and therefore the reconstruction 
-      is still very good on wide parts of the tree. \\
+    therefore discuss hereinafter how significant the result of this reconstruction is.
+
+  For this reconstruction, we first analyzed our input data. The use of Open Tree of Life (OTL) for
+    the tree gives us the greatest approximation to a phylogeny of the Eukaryota. Since such a large
+    phylogeny has not been completely dissected, this is only a synthesis of phylogenetic trees with
+    a taxonomy as a backbone. Therefore, the tree is far from binary, resulting in a multifurcation 
+    of 89.45 \%. However, this is highly variable and therefore the reconstruction is still very 
+    good on wide parts of the tree.
+
   On the other hand, we used the Global Biotic Interactions (GloBI) database to get the state 
@@
 
-    % One last limitation also exists in the data situation itself. We have pointed out in various 
-    %   sections that we have a strong multifurcation and only a few data about leaf node states.
-
-    Next, let's consider the limitations of the simulation that led to the choice of the Sankoff 
-      algorithm. Our own main point of criticism is that we did not simulate the transition 
-      probabilities and estimate an unrealistically high number of transitions (origins and losses). 
-      The Sankoff algorithm is very well scored despite this increased difficulty (more transitions 
-      means more complex predictions) and its proven feasibility.
+  Next, we consider the limitations of the simulation that led to the choice of the Sankoff 
+    algorithm. Our main criticism is that we did not simulate the transition probabilities and 
+    estimate an unrealistically high number of transitions (origins and losses). The Sankoff 
+    algorithm is very well scored despite this increased difficulty (more transitions means more 
+    complex predictions) and its proven feasibility.
 
   Finally, we analyze the validation of our ancestral state reconstruction results. We will do a 
-      selective analysis from a biological perspective and discuss the leave-100-out 
-      cross-validation. \\
-    Above all, the 'biological view' gives a first impression of the credibility of the results. But 
-      it can not make any statistical statements. Here the interested researcher may have to analyze 
-      the subtrees of being relevant to him for himself. \\
-    Of course, cross-validation can be expanded. With more computing power, a leave-1-out 
-      cross-validation could be performed. However, our result on this point is 98.17\% correct. \\
-
-\todo{old:}
-
-  This work deals with the ancestral state reconstruction of the entire Eukaryota relatives tree.
-
-  For this reconstruction, we first analyzed our data. This is the tree of OTL \cite{Hinchliff2015}
-    and the data for the leaf node states (free-living or parasite states) from GloBI 
-    \cite{Poelen2014} (section \ref{sec:results - missing information}), where we have determined 
-    that the entire Eukaryota tree is 89.45\% multifurcated (missing internal nodes) and that we do 
-    not have any state information for 97.34\% nodes. \\
-  In addition, we tested different models for these two parameters and found out that multifurcation 
-    can best be modeled with the taxa 'order' multiplied by the mean height of the knots. Also, the 
-    missing states could be modeled with the taxa 'order' and in this case multiplied by the depth 
-    of the nodes.
-
-  Next we compared different possible methods. We decided to take a closer look at maximum parsimony 
-    algorithms because they are fast and best suited to the problem at hand. We tested these on 
-    different simulations of the data and compared their predictive power (section 
-    \ref{sec:results - simulation}). \\
-  We compared them with the result that the Sankoff algorithm performs significantly better than 
-    Fitch. The multifurcation rate has little impact on Sankoff, but Fitch's prediction 
-    significantly breaks down at more than 60\% missing internal nodes. However, the amount of 
-    missing node state information has a linear impact on both, as does the ratio of free-living to 
-    parasitic (the more balanced, the worse is the prediction).
-
-  As a result, we used the Sankoff algorithm \cite{Sankoff1975} implemented by Louca et al. 
-    \cite{Louca2017}, which performed best, for the actual reconstruction on the real data. \\
-  We evaluated these on the one hand by analysing some statistics (subsection 
-    \ref{subsec:results - statistics on predicted states}) and on the other hand by performing a 
-    leave-100-out cross-validation. There we predicted approximately 98.17\% of the omitted states 
-    correct (subsection \ref{sec:results - cross-validation}). \\
+    statistical analysis from the tree and some selected subtrees and consider the leave-100-out 
+    cross-validation. Of these omitted nodes, we predict 98.17\% correctly. \\
+    % Here, interested researchers may have to analyze the subtrees that are relevant to them. \\
 
@@
       missing internal nodes. This means that there is a lack of information about the underlying 
-      phylogeny. Instead of a binary tree this tree is highly multifurcated.
-
+      phylogeny. Instead of being binary, this tree is highly multifurcated. \\
     \begin{table}[h!]
@@
           Arthropoda      & 97.49\%  & 89.95\% \\ \hline
-          Chordata        & 88.59\%  & \cellcolor{green!50}66.49\% \\ \hline
+          Chordata        & 88.59\%  & {\cellcolor{green!50}}66.49\% \\ \hline
           Nematoda        & 89.01\%  & 88.59\% \\ \hline
-          Platyhelminthes & \cellcolor{green!50}68.73\%  & 80.34\% \\
+          Platyhelminthes & {\cellcolor{green!50}}68.73\%  & 80.34\% \\
           \hline \hline            
@@
       \caption{Examination of subtrees regarding missing information. \\
-        The percentage values show the proportion of missing information of: unknown states (missing state 
-          information of leaf nodes) and multifurcation (missing internal nodes). \\
+        The percentage values show the proportion of missing information of: unknown states (missing 
+          state information of leaf nodes) and multifurcation (missing internal nodes). \\
         The subtrees are from different taxa: domain (Eukaryota), kingdom (Metazoa, Fungi, 
@@
       \label{table:percentage loss information subtrees} 
-    \end{table}
-
-    For the missing state information the present Eukaryota tree with 2,293,463 leaf nodes, 34,869 
-      free-livings and 25,962 parasites are found. This gives
+    \end{table} \\
+
+    For the present Eukaryota tree with 2,293,463 leaf nodes, 34,869 free-livings and 25,962 parasites 
+      are found. This gives
       $$100-\frac{100}{2293463 \times (34860+25962)} \approx 97.34\%$$
@@
 
-    We calculated these percentages of missing nodes and also missing state information for some 
-      subtrees and plotted them in table \ref{table:percentage loss information subtrees}.
+    We calculated these percentages of missing internal nodes and of missing state information for 
+      some subtrees and plotted them in table \ref{table:percentage loss information subtrees}.
 
@@
       \caption{Histograms showing the multifurcation of the internal nodes of the synthesis tree. \\
-        For each node, the number of children (degree $-1$) is collected. A node is multifurcated 
-        if it has more than two children, so we deducted two from each number of children. The two 
-        histograms show: number of children $-2$ on the x-axis with log scale and the number of nodes 
-        with this amount on the y-axis.}
+        For each node, the number of children (degree $-1$) is collected. A node is multifurcated if it
+        has more than two children, so we deducted two from each number of children. The two histograms 
+        show the number of children $-2$ on the x-axis with log scale and the number of nodes with this 
+        amount on the y-axis.}
       \label{fig:childrenOfNodes}
@@
 
-    For a first overview, we collected for each node its number of children (degree $-1$), 
-      and plotted this in two histograms, see figure \ref{fig:childrenOfNodes}.
-
-    The multifurcation affects only the internal nodes. We collected the number of children $-2$ of 
-      these nodes (because a node with two children is binary). That means it describes the number of 
-      nodes which we have lost from the real (binary) phylogenetic tree. \\
-    It can be recognized that we are very far from a binary tree.
+    The multifurcation affects only the internal nodes. We collected the number of children (degree $-1$) 
+      of these nodes and than subtract two of each value (because a node with two children is binary). 
+      That means this value describes the number of nodes which we have lost from the real (binary) 
+      phylogenetic tree. We plotted this in two histograms, see figure \ref{fig:childrenOfNodes}. It can 
+      be recognized that we are very far from a binary tree.
 
@@
       For the regression analysis of the multifurcation we set up several generalized linear models that 
-        could describe multifurcation. \\
+        could describe multifurcation.
+
       In doing so, we allowed the different influence of the taxa and the heights and depths of a node 
@@
             \hline \hline
-            multifurcation $\sim$ taxa & 8273333 & \cellcolor{green!15}7937828 & \cellcolor{green!20}7842157 & \cellcolor{green!30}7644249 \\
-            multifurcation $\sim$ taxa & 8257680 & \cellcolor{green!15}7922207 & \cellcolor{green!20}7826490 & \cellcolor{green!35}7574154 \\
-            \hline
-            multifurcation $\sim$ taxa + depth & 8273318 & \cellcolor{green!15}7934322 & \cellcolor{green!20}7839364 & \cellcolor{green!35}7539999 \\
-            multifurcation $\sim$ taxa + max.height & \cellcolor{green!15}7993515 & \cellcolor{green!25}7749121 & \cellcolor{green!30}7661817 & \cellcolor{green!40}7416211 \\
-            multifurcation $\sim$ taxa + min.height & 8251211 & \cellcolor{green!20}7875521  & \cellcolor{green!25}7778327 & \cellcolor{green!35}7516883 \\
-            multifurcation $\sim$ taxa + mean.height & \cellcolor{green!20}7825417 & \cellcolor{green!30}7644249 & \cellcolor{green!35}7572474 & \cellcolor{green!45}7340741 \\
-            \hline
-            multifurcation $\sim$ taxa * depth & 8235932 & \cellcolor{green!20}7836755 & \cellcolor{green!25}7757688 & \cellcolor{green!45}7383808 \\
-            multifurcation $\sim$ taxa * max.height & \cellcolor{green!15}7963438 & \cellcolor{green!30}7693555 & \cellcolor{green!30}7614820 & \cellcolor{green!45}7335338 \\
-            multifurcation $\sim$ taxa * min.height & 8214030 & \cellcolor{green!20}7808940 & \cellcolor{green!30}7690618 & \cellcolor{green!45}7336627\\
-            multifurcation $\sim$ taxa * mean.height & \cellcolor{green!25}7768360 & \cellcolor{green!35}7536296 & \cellcolor{green!50}7484953 & \cellcolor{green!50}7206369 \\
+            multifurcation $\sim$ taxa & 8273333 & {\cellcolor{green!15}}7937828 & {\cellcolor{green!20}}7842157 & {\cellcolor{green!30}}7644249 \\
+            multifurcation $\sim$ taxa & 8257680 & {\cellcolor{green!15}}7922207 & {\cellcolor{green!20}}7826490 & {\cellcolor{green!35}}7574154 \\
+            \hline
+            multifurcation $\sim$ taxa + depth & 8273318 & {\cellcolor{green!15}}7934322 & {\cellcolor{green!20}}7839364 & {\cellcolor{green!35}}7539999 \\
+            multifurcation $\sim$ taxa + max.height & {\cellcolor{green!15}}7993515 & {\cellcolor{green!25}}7749121 & {\cellcolor{green!30}}7661817 & {\cellcolor{green!40}}7416211 \\
+            multifurcation $\sim$ taxa + min.height & 8251211 & {\cellcolor{green!20}}7875521  & {\cellcolor{green!25}}7778327 & {\cellcolor{green!35}}7516883 \\
+            multifurcation $\sim$ taxa + mean.height & {\cellcolor{green!20}}7825417 & {\cellcolor{green!30}}7644249 & {\cellcolor{green!35}}7572474 & {\cellcolor{green!45}}7340741 \\
+            \hline
+            multifurcation $\sim$ taxa * depth & 8235932 & {\cellcolor{green!20}}7836755 & {\cellcolor{green!25}}7757688 & {\cellcolor{green!45}}7383808 \\
+            multifurcation $\sim$ taxa * max.height & {\cellcolor{green!15}}7963438 & {\cellcolor{green!30}}7693555 & {\cellcolor{green!30}}7614820 & {\cellcolor{green!45}}7335338 \\
+            multifurcation $\sim$ taxa * min.height & 8214030 & {\cellcolor{green!20}}7808940 & {\cellcolor{green!30}}7690618 & {\cellcolor{green!45}}7336627\\
+            multifurcation $\sim$ taxa * mean.height & {\cellcolor{green!25}}7768360 & {\cellcolor{green!35}}7536296 & {\cellcolor{green!50}}7484953 & {\cellcolor{green!50}}7206369 \\
             \hline
@@
         \end{center}
-        \caption{BIC (Bayesian information criterion) values of the multifurcation models. \\
+        \caption{BIC values of the multifurcation models. \\
           These models are created with the R function \textit{glm()} and compared with the \textit{BIC()} 
-            function. This results in the listed BIC values, presented in a heatmap colorization.}
+            function. These results are the listed BIC values, presented in a heatmap colorization.}
         \label{table:BIC multifurcation} 
       \end{table}
-      Within every complexity class it can be seen that the mean height gives the best additional factor. \\
+      Within every complexity class it can be seen that the mean height gives the best additional factor.
         Despite higher complexity, the BIC values are getting smaller from model to model, meaning that 
-        the finest model available here is also the best one of these. Lower taxa than orders (e.g. 
-        family) are computationally too expensive to calculate. \\
+        the finest model available here is also the best one of these. Lower order taxa e.g. family are 
+        computationally too expensive to calculate.
+
       The model \textit{multifurcation $\sim$ order * mean.height} turns out to be the best of our models, 
@@
         for the species. For the ancestral state reconstruction, we need information about the states 
-        (free-living or parasite) in the leaf nodes. \\
+        (free-living or parasite) of the leaf nodes.
+
       The Eukaryota synthesis tree has 293,463 leaf nodes. The GloBI database has 5,346,414 interactions 
-        (at 29.01.2018). Out of this data we got 51,337 free-living species and 47,332 parasite species 
-        for the whole tree of life. From the Eukaryota we could determine 25,962 and 34,860 species as 
-        parasites and free-living. With 2,293,463 leaf nodes we still have about 97.34\% unknown leaf 
-        nodes.
+        (at 29.01.2018). Out of this data we recieved 51,337 free-living species and 47,332 parasite 
+        species for the whole tree of life. For the Eukaryota we could determine 25,962 and 34,860 
+        species as parasites and free-living. With 2,293,463 leaf nodes we still have about 97.34\% 
+        unknown leaf nodes.
 
@@
             \hline \hline
-            multifurcation $\sim$ taxa & \cellcolor{green!15}545799 & \cellcolor{green!35}500004 & \cellcolor{green!45}485121 & \cellcolor{green!45}484681 \\
-            \hline
-            multifurcation $\sim$ taxa + depth & \cellcolor{green!15}544862 & \cellcolor{green!40}493808 & \cellcolor{green!45}481869 & \cellcolor{green!50}478851 \\
-            \hline
-            multifurcation $\sim$ taxa * depth & \cellcolor{green!15}544179 & \cellcolor{green!45}489845 & \cellcolor{green!45}481494 & \cellcolor{green!50}478188 \\
+            multifurcation $\sim$ taxa & {\cellcolor{green!15}}545799 & {\cellcolor{green!35}}500004 & {\cellcolor{green!45}}485121 & {\cellcolor{green!45}}484681 \\
+            \hline
+            multifurcation $\sim$ taxa + depth & {\cellcolor{green!15}}544862 & {\cellcolor{green!40}}493808 & {\cellcolor{green!45}}481869 & {\cellcolor{green!50}}478851 \\
+            \hline
+            multifurcation $\sim$ taxa * depth & {\cellcolor{green!15}}544179 & {\cellcolor{green!45}}489845 & {\cellcolor{green!45}}481494 & {\cellcolor{green!50}}478188 \\
             \hline
@@
         \end{center}
-        \caption{BIC (Bayesian information criterion) values unknown state information models. \\
+        \caption{BIC values unknown state information models. \\
           These models are created with the R function \textit{glm()} and compared with the 
@@
 
-      These missing data modeling results could be used to better simulate the data. \\
+      These missing data modeling results could be used to improve the simulated data. \\
 
@@
         So, the influence of the taxa (kingdom, phylum, class) and the depth of the leaf nodes is 
-        re-modeled and the BICs compared (table \ref{table:BIC cross-validation}). Lower taxa than 
+        re-modeled and the BICs compared (table \ref{table:BIC cross-validation}). Lower order taxa than 
         classes (e.g. order) are computationally too expensive to calculate.
@@
             \hline \hline
-            correctly predicted $\sim$ taxa & 117936 & \cellcolor{green!40}112242 & \cellcolor{green!50}111733 \\% & XXXXX \\
-            \hline
-            correctly predicted $\sim$ taxa + depth & 117776 & \cellcolor{green!50}111304 & \cellcolor{green!50}111273 \\% & XXXXX \\
-            \hline
-            correctly predicted $\sim$ taxa * depth & 117709 & \cellcolor{green!50}111262 & \cellcolor{green!30}113135 \\% & XXXXX \\
+            correctly predicted $\sim$ taxa & 117936 & {\cellcolor{green!40}}112242 & {\cellcolor{green!50}}111733 \\% & XXXXX \\
+            \hline
+            correctly predicted $\sim$ taxa + depth & 117776 & {\cellcolor{green!50}}111304 & {\cellcolor{green!50}}111273 \\% & XXXXX \\
+            \hline
+            correctly predicted $\sim$ taxa * depth & 117709 & {\cellcolor{green!50}}111262 & {\cellcolor{green!30}}113135 \\% & XXXXX \\
             \hline
@@
         \end{center}
-        \caption{BIC (Bayesian information criterion) values of cross-validation prediction models. \\
+        \caption{BIC values of cross-validation prediction models. \\
           These models are created with the R function \textit{glm()} and compared with the 
@@
     \subsection{Distribution of Taxa}
-      In the tree we can distinguish 28 different Taxa in the OTL taxonomic tree. We have all Taxa 
+      In the tree we can distinguish 28 different taxa in the OTL taxonomic tree. We have all taxa 
         sorted by rank into a table and counted their occurrences as internal nodes and leaf nodes

### 2018-04-02 Paper - Latex/Paper - Skizze - v4.tex
Thesis - Results 2. Hälfte again

@@
   %---------------------------------------------------------------------------------------------------
-  \section{Data sources} \label{sec:methods - data sources}
+  \section{Data sources}
     Two types of data are needed for an ancestral state reconstruction: a tree and information about 
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Metadata analysis} \label{sec:methods - metadata analysis}
+  \section{Metadata analysis}
     Based on the input data, generalized linear models are compared with poisson respectively binomial 
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Ancestral state reconstruction methods} \label{sec:methods - ancestral state reconstruction}
+  \section{Ancestral state reconstruction methods}
     The methods used to reconstruct the ancestral states are Fitch parsimony \cite{Fitch1971} and 
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Simulation}\label{sec:methods - simulation}
+  \section{Simulation}
     The simulation compares these different ancestral state reconstruction algorithms with each 
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Real data analysis} \label{sec:methods - real data analysis}
+  \section{Real data analysis}
     For the evaluation of real data results, some statistics are collected and a leave-100-out 
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Availability of internal nodes and state information} \label{sec:results - missing information}
+  \section{Availability of internal nodes and state information}
     As previously presented, we have two types of missing information: unknown states of leaf nodes 
@@
 
-\newpage
-
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  %---------------------------------------------------------------------------------------------------
-  \section{Influence of different parameters on the prediction} \label{sec:results - simulation}
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
+  \section{Influence of different parameters on the prediction}
     As presented, we compare two methods in our simulation to their prediction accuracy: Fitch and 
@@
     First, we tested different distributions of parasites to free-livings including threshold (first 
-      column). It can be observed that the more balanced the percentages of free-livings and parasites, 
-      the worse the prediction of the algorithms (second and third column). \\
-    It can be seen that the predictive power of Sankoff is always greater or equal to the percentage
-      of free-living distribution, and therefore more accurate than guessing. \\
+      column).We observe: the more balanced the percentages of free-livings and parasites, the worse 
+      the prediction of the algorithms (second and third column). It can be seen that the predictive 
+      power of Sankoff is always greater or equal to the percentage of free-living distribution, and 
+      therefore more accurate than guessing.
+
     On the other hand, we examined the influence of missing internal nodes (ridge of multifurcation) 
-      and missing leaf node information (unknown leaf nodes). \\
-    Both factors have a relatively linear influence on the Sankoff method. Fitch, on the other hand, 
-      breaks significantly in his prediction from about 70\% unknown leaf nodes or mutifurcation. \\
+      and missing leaf node information (unknown leaf nodes). Both factors have a relatively linear 
+      influence on the Sankoff method. Fitch, on the other hand, breaks significantly in his 
+      prediction from about 70\% unknown leaf nodes or mutifurcation.
+
     Figure \ref{fig:influence of unknown data} shows the results of examining various parameters.
@@
       \centering
-      \includegraphics[trim = 0mm 100mm 0mm 0mm, clip, width=\textwidth]{Figures/simulation_evaluation_1.png}
+      \includegraphics[trim = 0mm 108mm 0mm 0mm, clip, width=\textwidth]{Figures/simulation_evaluation_1.png}
     \end{figure}
-    ~ \\
     \begin{figure}[h!]
@@
           the strength of the multifurcation. \\
-        The y-axes indicate the percentage of correctly predicted states (including known states). On 
-          the x-axis the percentage of forgotten states or missing internal nodes. \\
-        Each point corresponds to the average of one hundred simulations, each with 10,000 leaf nodes. \\
+        The y-axes indicate the percentage of correctly predicted states (including known states). The 
+          x-axis describes the percentage of forgotten states or missing internal nodes. \\
+        Each point corresponds to the average of 100 simulations, each with 10,000 leaf nodes. \\
         For the middle column we set the strength of the multifurcations to 0.95\%, similar to the 
-          real data and in the right column the amount of the unknowns to 0.95\% also similar to the 
+          real data and in the right column the amount of the unknowns to 0.95\%, also similar to the 
           real data.}
@@
     Since we have a lot of missing data in most subtrees (both internal nodes and state information), 
-      the Sankoff gives a better prediction and is thus used for real data analysis.
+      the Sankoff gives a better prediction and is thus used for the real data analysis. \\
 
@@
     This section is about evaluating the prediction of real data using the Sankoff method and is 
-      divided into two subsections. \\
-    The analysis of some statistics on the predicted states, with the result that we predict a total 
-      of significantly more free-livings than parasites despite almost 50:50 distributed input states 
-      (subsection \ref{subsec:results - statistics on predicted states}) and the presentation of the 
-      leave-100-out cross-validation results (subsection \ref{sec:results - cross-validation}) This 
-      has revealed that we predicted approximately 98.17\% correct with a small variance.
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{Statistics on predicted states} \label{subsec:results - statistics on predicted states}
+      divided into two subsections.
+
+    First comes the analysis of some statistics on the predicted states, with the result that we 
+      predict a total of significantly more free-livings than parasites despite almost 50:50 
+      distributed input states, and second, we present the leave-100-out cross-validation results. This 
+      revealed that we predicted approximately 98.17\% correct with a small variance.
+
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \subsection{Statistics on predicted states}
       In the entire Eukaryota tree we start with 57.31\% free-living species and 42.69\% parasites. The 
@@
         there are 462 origins of parasitism and 369 losses distributed throughout the tree, with the 
-        root node predicted to be parasitic. \\
-      We have predicted significantly more free-livings than parasites, but parasitism has prevailed to 
-        the root node.
+        root node predicted to be parasitic. We have predicted significantly more free-livings than 
+        parasites, but parasitism has prevailed to the root node.
 
@@
       Similar to the Eukaryota it is with the Metazoa subtree, which accounts for most of the Eukaryota 
-        (179,944 internal and 1,491,012 leaf nodes). However, here the root node is no longer calculated 
-        as parasitic but still as indefinable. \\
-      Strongly parasitic subtrees are for example the Apicomplexa, the Nematoda and the Platyhelminthes. 
+        (179,944 internal and 1,491,012 leaf nodes). However, the root node here is no longer calculated 
+        as parasitic but still as indefinable.
+
+      Strongly parasitic subtrees are, for example, the Apicomplexa, the Nematoda and the Platyhelminthes. 
         For all three, the prediction is at a similar proportion between input values of the states and 
-        predicted states, e.g. In the Apicomplexa with 99.61\% known parasitic states, 99.95\% parasites 
+        predicted states. In the Apicomplexa with 99.61\% known parasitic states, 99.95\% parasites 
         were predicted. The same applies to the chordata, only that these mainly consist of free-living 
@@
         They identified 223 parasitic origins: 223 in Metazoa $\supset$ 143 in Arthropoda $\supset$ 87 
-        in Insecta. \\
-      In the last columns of the table \ref{table:results of some selected taxa} we can see, that we 
-        found some more origins than Weinstein: 321 in Metazoa $\supset$ 281 in Arthropoda $\supset$ 245 
-        in Insecta and on top of that some losses: 129 in Metazoa $\supset$ 108 in Arthropoda $\supset$ 
-        77 in Insecta. The origins and losses calculated by Sankoff are thus closer to the leaves in the tree.
-
-    %---------------------------------------------------------------------------------------------------
-    %---------------------------------------------------------------------------------------------------
-    \subsection{Leave-100-out cross-validation} \label{sec:results - cross-validation}
-      For a further validation of our results, we carried out a leave-100-out cross-validation. \\
-      In order to achieve about 15\% of the 60,871 input node states with a validation, 
-        we randomly left out 100 states 100 times.Omit smaller amounts of states up to leave-one-out had 
-        too much computational effort.
+        in Insecta. In the last columns of the table \ref{table:results of some selected taxa} we see 
+        that we found more origins than Weinstein: 321 in Metazoa $\supset$ 281 in Arthropoda $\supset$ 
+        245 in Insecta and on top of that some losses: 129 in Metazoa $\supset$ 108 in Arthropoda 
+        $\supset$ 77 in Insecta. The origins and losses calculated by Sankoff are thus closer to the 
+        leaves in the tree.
+
+    %---------------------------------------------------------------------------------------------------
+    %---------------------------------------------------------------------------------------------------
+    \subsection{Leave-100-out cross-validation}
+      For a further validation of our results, we carried out a leave-100-out cross-validation. In order 
+        to achieve about 15\% of the 60,871 input node states with a validation, we randomly left out 
+        100 states 100 times. Omitting smaller amounts of states up to leave-one-out had too much 
+        computational effort.
 
@@
         of variability in the taxa and whether the depth is an influencing factor over our prediction. 
-        So, the influence of the taxa (kingdom, phylum, class) and the depth of the leaf nodes is 
-        re-modeled and the BICs compared (table \ref{table:BIC cross-validation}). Lower order taxa than 
-        classes (e.g. order) are computationally too expensive to calculate.
+        The influence of the taxa (kingdom, phylum, class) and the depth of the leaf nodes is remodeled 
+        and the BICs compared (table \ref{table:BIC cross-validation}). Lower order taxa than classes 
+        (e.g. order) are computationally too expensive to calculate.
 
@@
       taxonomy. For a review of this underlying taxonomy, we have compiled a list of all taxa and 
-      plottet them in relation to their distribution (see appendix section \ref{sec:otl analysis}). 
+      plottet them in relation to their distribution (see appendix section \ref{sec:appendix - otl analysis}). 
       There the number of nodes in the tree corresponding to a taxonomic rank is tabulated.
@@
   %---------------------------------------------------------------------------------------------------
-  \section{OTL analysis}\label{sec:otl analysis}
+  \section{OTL analysis}\label{sec:appendix - otl analysis}
 

### 2018-04-02 Paper - Latex/Paper - Skizze - v4.tex
Thesis - Discussion again

@@
       The Eukaryota synthesis tree has 293,463 leaf nodes. The GloBI database has 5,346,414 interactions 
-        (at 29.01.2018). Out of this data we recieved 51,337 free-living species and 47,332 parasite 
+        (at 29.01.2018). Out of this data we received 51,337 free-living species and 47,332 parasite 
         species for the whole tree of life. For the Eukaryota we could determine 25,962 and 34,860 
@@
 \chapter{Discussion}
-  This chapter deals with the question of how trustworthy our result of the ancestral state 
-    reconstruction of the Eukaryota tree is. And further on how well our simulation can simulate the 
-    real problem and thus make statements about the predictive power of the applied Sankoff algorithm.
-
-  We have pursued this question in various investigations and yet, of course, further possibilities 
-    for improvement remain. Despite these possibilities for improvement, our reconstruction gives a 
-    first good assessment of the whole tree.
+  This chapter is about how trustworthy our result of the ancestral state reconstruction of the 
+    Eukaryota tree is and how good our simulation is in order to make statements about the predictive 
+    power of the applied Sankoff algorithm.
+
+  We pursued this question in various investigations and yet, of course, further possibilities for 
+    improvement remain. Despite these improvement opportunities, our reconstruction gives a first 
+    good assessment of the whole tree.
 
   In the first part of this work, we were able to provide the proof of concept for the Sankoff 
-    algorithm to perform an ancestral state reconstruction of the present Eukaryota tree. In the 
-    following, we will first discuss the data situation and the simulation that led to the selection 
-    of the Sankoff algorithm, and then discuss how significant the result of this reconstruction is.
+    algorithm to perform an ancestral state reconstruction of the present Eukaryota tree. Hereinafter,
+
+    we will first discuss the data situation and the simulation that led to the selection of the 
+    Sankoff algorithm, followed by a discussion about the significance of the result of this 
+    reconstruction.
 
@@
   %---------------------------------------------------------------------------------------------------
-  \section{Data situation} \label{sec:discussion - data situation}
+  \section{Data situation}
     The used Eukaryota synthesis tree from OTL \cite{Hinchliff2015} has 241,974 internal nodes and 
@@
     This gives us a high number of missing internal nodes (high multifurcation) and a low number of 
-      node states of the leaf nodes in the entire tree.
+      states of the leaf nodes in the entire tree.
     We suspect that this lack of information is not equally distributed in both cases. We conclude 
-      this from various observations.
-
-    For one thing, there were a few subtrees of higher ranks whose information share was much higher. 
-      In the Chordata there is only 66.49\% multifurcation and in the Platyhelminthes only 68.73\% 
-      missing state information. \\
+      this from various observations:
+
+    For one, there were a few subtrees of higher ranks whose information share was much greater. In 
+      the Chordata there is only 66.49\% multifurcation and in the Platyhelminthes only 68.73\% 
+      missing state information.
+
     Furthermore, we know that OTL is a synthesis of 819 phylogenetic trees. This suggests that just 
@@
       taxonomy. For a review of this underlying taxonomy, we have compiled a list of all taxa and 
-      plottet them in relation to their distribution (see appendix section \ref{sec:appendix - otl analysis}). 
-      There the number of nodes in the tree corresponding to a taxonomic rank is tabulated.
+      plotted them in relation to their distribution (see appendix section \ref{sec:appendix - otl analysis}). 
+      In this list, the number of nodes in the tree corresponding to a taxonomic rank is tabulated.
 
@@
 
-    From GloBI we got very little information about leaf node states compared to their number in the 
-      Eukaryota tree. Nevertheless, the prediction of leave-100-out cross-validation was very good. 
-      This also leads to the conclusion that the information is very clustered.
+    From GloBI we received very little information about leaf node states compared to their quantity 
+      in the Eukaryota tree. Nevertheless, the prediction of the leave-100-out cross-validation was 
+      very good. This also leads to the conclusion that the information is very clustered.
 
     As a last point, we would like to cite the modeling of the missing information. The fact that this 
-      is getting better, the lower ordered taxa (smaller subtrees) we are looking at, also suggests a 
-      high variability of the data.
-
-    We would like to mention a few other aspects of the GloBI database here. \\
-    Of course, such large data sets are flawed. We found some misinformation and were able to report 
-      some of these directly to GloBI. \\
-    We also found that there is some unused information in GloBI. We therefore found some more source 
-      species and target species without OTT identifiers. Since we currently use only OTT 
+      gets better, the lower the taxa (smaller subtrees) we are looking at, also indicates a high 
+      variability of the data.
+
+    We would like to mention a few other aspects of the GloBI database here. Of course, such large 
+      data sets are flawed. We found some misinformation and were able to report some of these 
+      directly to GloBI. We also noticed that there is some unused information in GloBI. We found some 
+      source species and target species without OTT identifiers. Since we currently use only OTT 
       identifiers, we could not use this information. At this point there is thus the possibility to 
@@
     We assume that different parasite types have different transition probabilities. It is therefore 
-      difficult to establish a common distribution across the Eukaryota tree. \\
-    Based on the estimates of Windsor \cite{Windsor1998}, we have assumed a distribution of 40\% 
-      parasites to 60\% free-livings in this work. As a result of the diversity of parasites and the 
-      lack of generalizations, we have generally stated that 
+      difficult to establish a common distribution across the Eukaryota tree. Based on the estimates 
+      of Windsor \cite{Windsor1998}, we have assumed a distribution of 40\% parasites to 60\% 
+      free-livings in this study. As a result of the diversity of parasites and the lack of 
+      generalizations, we have stated that 
       $\mathcal{P}(FL \rightarrow P) = \mathcal{P}(P \rightarrow FL)$. But it is also reasonable to 
@@
     In the simulation, we found that this combination has a significant influence on the predictive 
-      power of the algorithms. \\
-    We have adapted the combination of distributions and threshold to a high probability of achieving 
-      the given proportions on initial attempts. However, this means that we prefer high transition 
-      probabilities for both transitions and thus the simulated trees have a large number of 
-      transitions. It can be assumed that this may not correspond to the real data and thus means a 
-      limitation of our simulation. Further we assume that with less number of state changes, the 
-      predictive power of both algorithms would be even better, thus this limitation is probably not 
-      very restrictive. \\
-    At this point it would be possible to test other distributions with equal threshold values. this 
-      would be more computationally expensive, but would result in fewer transitions.
+      power of the algorithms. We have adapted the combination of distributions and threshold to a 
+      high probability of achieving the given proportions on initial attempts. However, this means 
+      that we prefer high transition probabilities for both transitions and thus the simulated trees 
+      have a large number of transitions. It can be assumed that this may not correspond to the real 
+      data and thus means a limitation of our simulation. Furthermore we assume that with a lower 
+      number of state changes, the predictive power of both algorithms would be even better, thus this 
+      limitation is probably not very restrictive. At this point it would be possible to test other 
+      distributions with equal threshold values. This would be more computationally expensive, but 
+      would result in fewer transitions.
 
@@
 
-    The used \textit{castor} package \cite{Louca2017} offers the possibility to enter different transition 
-      probabilities, so with information about these probabilities, you might be able to improve the 
-      prediction here.
+    The used \textit{castor} package \cite{Louca2017} offers the possibility to enter different 
+      transition probabilities, so with information about these probabilities, one might be able to 
+      improve the prediction here.
 
@@
   \section{Biological view}
-    To analyze the results, we have selected some phyla (subtrees) to evaluate our results selectively 
-      from the biological point of view: Chordata, Nematoda, Platyhelminthes and Apicomplexa.
-
-    Several factors such as the distribution of existing input data via parasites and free-livings, 
-      faulty input data from GloBI and reinforcement of errors by multifurcation play an important 
-      role which becomes evident in these examples.
+    We have selected some phyla (subtrees) to evaluate our results selectively 
+      from the biological point of view: Chordata, Nematoda, Platyhelminthes and Apicomplexa. Various 
+      factors such as the distribution of existing input data about parasites and free-livings, 
+      erroneous input data from GloBI, and the amplification of these errors due to multifurcation 
+      play an important role, which becomes clear in these examples.
 
     The accuracy of our results stands and falls with the presence and the correctness of the data of 
-      GloBI. Errors of incorrect input data can be amplified by incorrect prediction of unknown 
-      species and can be reversed in order to improve the data situation of GloBI. \\
-    Since we look at such large trees we can not expect to know all the parasites, so we look at 
-      individual positives. They are positive in the sense that the majority have the opposite state.
+      GloBI. Errors that result from incorrect data can be amplified by incorrect prediction of unknown 
+      species and can be reversed in order to improve the data situation of GloBI. Since we look at 
+      such large trees we can not expect to know all the parasites, so we look at individual positives. 
+      They are positive in the sense that the majority have the opposite state.
 
@@
       There are 18 parasites as input data and only 8 more are predicted. The Chordata mostly consist 
-      of free-living species, so this seems believable. We started with 99.83\%  species and predict 
-      99.97\% species as free-living (including already known nodes). \\
-    For a detailed view we have created and described a tree with all known and predicted parasites 
-      (see appendix \ref{sec:parasites in chordata}).
+      of free-living species, so this seems credible. We started with 99.83\%  species and predicted
+      99.97\% species as free-living (including already known nodes). For a detailed view we created 
+      and described a tree with all known and predicted parasites (see appendix 
+      \ref{sec:parasites in chordata}).
 
     The Apicomplexa are a parasitic phylum. We found only one input organism: \textit{Stemonitis fusca} 
-      as a free-living species. In GloBI it is listed as being parasitized by Nectria candicans and 
+      is a free-living species. It is listed in GloBI as being parasitized by Nectria candicans and 
       Nectriopsis sporangiicola\footnote{
@@
       is one class (Rhabditophora) that contains all but one single exception of free-living species 
-      of this phylum, which includes the Turbellaria. \\
-    It should be noted, however, that this classification is outdated, as it has been proven that 
-      the Turbellaria are not monophyletic. But we will not go into detail here. \\
-    For the Platyhelminthes we have more state information for the leaf nodes compared to the other 
-      considered subtrees. We start with 0.1\% free-livings and predicted 0.77\% as free-living 
-      species.
-
-    With the Nematoda it looks more complicated. Large parts of Nematoda are free-living, but we 
-      found only 5.32\% of them. Blaxter and Koutsovoulos estimate the order of 25,000 parasites in 
-      the Nematoda and and speak of at 18 independently arosen parasites in Nematoda 
-      \cite{Blaxter2015}. \\
-    % The problem at this point, however, is: Hallan speaks of the fact that only 23,000 species are 
-    %   described by the Nematoda but it is assumed that one million or more species are in this 
-    %   phylum.\footnote{J. Hallan, unpublished; 
-    %     \hyperlink{https://insects.tamu.edu/research/collection/hallan/}
-    %     {https://insects.tamu.edu/research/collection/hallan/}
-    %   }. \todo{Link ist nicht erreichbar!} 
-    We assume that the parasites have been much more studied and thus we start with only 0.63\% 
-      free-living species. Against such a shifted data situation, the algorithm is almost powerless to 
-      make correct predictions. And yet the percentage has increased to 5.34\%. \\
-    The root node of the Nematoda is predicted as a parasite and so we got 11 losses of parasitism 
+      of this phylum, which includes the Turbellaria. For the Platyhelminthes we have proportionally 
+      more state information for the leaf nodes compared to the other considered subtrees. We start 
+      with 0.1\% free-livings and predicted 0.77\% as free-living species.
+
+    The Nematoda are more complicated. Large parts of Nematoda are free-living, but we found only 
+      5.32\% of them. Blaxter and Koutsovoulos estimate the order of 25,000 parasites in the Nematoda 
+      and speak of 18 independently arosen parasites in Nematoda \cite{Blaxter2015}. We assume that 
+      the parasites have been much more studied and thus we start with only 0.63\% free-living species. 
+      Against such a shifted data situation, the algorithm is almost powerless to make correct 
+      predictions. And yet the percentage has increased to 5.34\%.
+
+    The root node of the Nematoda is predicted as a parasite and so we received 11 losses of parasitism 
       and only 2 origins in this phylum. If we assume that the root node of Nematoda is free-living, 
@@
 
-    From the simulation, we can conclude that we predict correctly about 60\% of the nodes in the 
-      present data situation. The leave-100-out cross-validation even showed that we predict the 
-      omitted nodes to be 98.17\% percent correct. \\
+    From the simulation, we can conclude that we predict about 60\% of the nodes in the present data 
+      situation correctly. The leave-100-out cross-validation even showed that we predict the omitted 
+      nodes to be 98.17\% percent correct.
+
     This allows for the assumption that the data is grouped and not uniformly distributed and thus 
@@
       and biological analysis of the considered subtrees: Chordata, Nematoda, Platyhelminthes and 
-      Apicomplexa. \\
-    However, this means that the ancestral states' data in the direction of root node are probably 
-      particularly unbelievable. This makes the localization of origins in the direction of the root 
-      node difficult. The question remains, how much this affects the estimation of the number of 
-      origins. Our comparison with the paper from Weinstein and Kuris \cite{Weinstein2016} an with
-      Blaxter and Koutsovoulos \cite{Blaxter2015} showed similar numbers of origins in some subtrees, 
-      which leaves us with optimism.
+      Apicomplexa.
+
+    However, it follows that the ancestral states' data in the direction of root node are probably 
+      particularly unreliable. This makes the localization of origins in direction of the root node 
+      difficult. The question remains, how much this affects the estimation of the number of origins. 
+      Our comparison with the paper from Weinstein and Kuris \cite{Weinstein2016} an with Blaxter and 
+      Koutsovoulos \cite{Blaxter2015} showed similar numbers of origins in some subtrees, which 
+      leaves us with optimism.
 

### 2018-04-02 Paper - Latex/Paper - Skizze - v4.tex
Thesis - appendix again

@@
         predicted states. In the Apicomplexa with 99.61\% known parasitic states, 99.95\% parasites 
-        were predicted. The same applies to the chordata, only that these mainly consist of free-living 
+        were predicted. The same applies to the Chordata, only that these mainly consist of free-living 
         species.
@@
       Picozoa, Placozoa, Platyhelminthes, Porifera, Priapulida, Rhodophyta, Rhombozoa, Rotifera, 
-      Streptophyta, Tardigrada, Xanthophyceae \\
-    Wobei von Streptophyta -> Anthocerotophyta, Marchantiophyta, Bryophyta, Tracheophyta als
-      Phylum im Phylum gefunden und nicht einbezogen wurden und Magnoliophyta als Phylum in 
-      Tracheophyta ebenfalls nicht. \\
+      Streptophyta, Tardigrada, Xanthophyceae.
+
+      Anthocerotophyta, Marchantiophyta, Bryophyta, Tracheophyta were found as phylum in the phylum 
+        Streptophyta and Magnoliophyta as phylum in Tracheophyta and thus not included.
 
@@
     \subsection{Distribution of Taxa}
-      In the tree we can distinguish 28 different taxa in the OTL taxonomic tree. We have all taxa 
-        sorted by rank into a table and counted their occurrences as internal nodes and leaf nodes
-        (see table \ref{table:taxa}) and plotted them as a diagram (see figure \ref{fig:taxa}).
+      In the tree we can distinguish 28 different taxa in the OTL taxonomic tree. We sorted all taxa by
+        rank into a table, counted their occurrences as internal nodes and leaf nodes (see table 
+        \ref{table:taxa}) and plotted them as a diagram (see figure \ref{fig:taxa}).
     \begin{figure}[h!]
@@
   \section{Parasites in Chordata} \label{sec:parasites in chordata}
-    We mapped the few parasitic species in a rough taxonomy (see Figure \ref{fig:ChordataParasites}): \\
-    Known parasitic birds belong to the order Sauria. Here we know from Rothschild here that are 
-      breeding parasites, like the cuckoo and clepto-parasites as the skuas \cite{Rothschild1957}. We
-      got 6 input parasites from GloBI and there are no predictions: A woodpecker - 
+    We mapped the few parasitic species in a rough taxonomy (see Figure \ref{fig:ChordataParasites}): 
+      Known parasitic birds belong to the order Sauria. Here we know from Rothschild that there are 
+      breeding parasites like the cuckoo and clepto-parasites like the skua  \cite{Rothschild1957}. We
+      received 6 input parasites from GloBI and got no predictions: A woodpecker - 
       \textit{Sphyrapicus varius} and a duck - \textit{Aix sponsa}, a cow bird - \textit{Molothrus ate} 
-      known as broodparasite and some others. \\
-    An example of the amplification of mistakes here are the carp. There is a paper from which GloBI 
-      concludes: Grass carp (\textit{Ctenopharyngodon idella)} has Pathogen common carp 
+      known as broodparasite and some others.
+
+    An example of the amplification of mistakes are the carp. There is a paper from which GloBI 
+      concludes: the Grass carp (\textit{Ctenopharyngodon idella)} has as pathogen the common carp 
       (\textit{Cyprinus carpio})\footnote{
@@
       \caption{Parasites of Phylum: Chordata. \\
-        All parasite data of the chordata are mapped into a rough taxonomy (phylum, class, order, 
-          family) in order to understand their distribution and affiliation. \\
+        All parasite data of the Chordata is mapped into a rough taxonomy (phylum, class, order, 
+          family) in order to understand its distribution and affiliation. \\
         The internal nodes are the wanted taxa from OTL (with the addition of \# input parasites to 

### 2018-04-02 Paper - Latex/Thesis - Lydia Buntrock.tex
Thesis :)

--- 2018-04-02 Paper - Latex/Paper - Skizze - v4.tex
@@
 %---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
 \bibliography{bibliographie}
 
+%---------------------------------------------------------------------------------------------------
 %---------------------------------------------------------------------------------------------------
@@
   %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
   \section{OTL analysis}\label{sec:appendix - otl analysis}
 
+    %---------------------------------------------------------------------------------------------------
     %---------------------------------------------------------------------------------------------------
@@
   %---------------------------------------------------------------------------------------------------
+  %---------------------------------------------------------------------------------------------------
   \section{Parasites in Chordata} \label{sec:parasites in chordata}
@@
 
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+\chapter*{Eigenständigkeitserklärung}
+  Hiermit versichere ich, dass ich die vorliegende Masterarbeit selbständig verfasst habe. \\
+  Ich versichere, dass ich keine anderen als die angegebenen Quellen benutzt und alle wörtlich oder 
+    sinngemäß aus anderen Werken übernommenen Aussagen als solche gekennzeichnet habe, und dass die 
+    eingereichte Arbeit weder vollständig noch in wesentlichen Teilen Gegenstand eines anderen 
+    Prüfungsverfahren gewesen ist. \\
+  \vspace{2 cm} \\
+  (Datum und Unterschrift)
+
 \end{document}
